### 2017-06-30 Manuscript.Rmd
Added manuscript

---
title: "Manuscript"
output:
  html_notebook:
    code_folding: hide
bibliography: references.bib
---

# Title page

**Title:** Biometry of the invasive lionfish (*Pterois volitans*) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range

**Name of author:** Juan Carlos Villaseñor-Derbez

**Affiliation:** Bren School of Environmental Sciences and Management

**Full postal address:** University of California Santa Barbara, Santa Barbara,  CA 93106, USA

**Running title:** Length - weigth parameters for *Pterois volitans*

*Corresponding author information:*

Juan Carlos Villaseñor-Derbez

4312 Bren Hall

Santa Barbara, CA

93106

jvillasenor@bren.ucsb.edu

+1 (207) 205 8435

\clearpage

**Title**

**Abstract**

300 words

**Key words**

lionfish, biometry, length-weight relationship, Mexico

___________________

**Resumen**

**Palabras clave**

pez león, biometría, relación lopngitud-peso, México

\clearpage

# Introduction

# Materials and Methods

```{r}

suppressPackageStartupMessages({
  library(RColorBrewer)
  library(colorRamps)
  library(stargazer)
  library(sandwich)
  library(lmtest)
  library(broom)
  library(tidyverse)
  library(RefManageR)
})

windowsFonts(Times=windowsFont("TT Times New Roman"))

```

```{r}
fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
  summarize(Length = 10*mean(TotalLength_cm),
            Weight = mean(TotalWeigth_gr),
            Stomach = mean(StomachLength_cm)) %>% 
  ungroup()
```

## Area of study

## Fish sampling

## Data analysis

# Results

## Length-weight relationship

```{r, results = "asis"}
fish %>% 
  select(Length, Weight, Stomach, Depth_m) %>% 
  as.data.frame() %>% 
  stargazer(header = F, type = "html", digits = 2)
```

```{r, fig.width = 5, fig.height = 7}
length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
  geom_density(fill = "gray", alpha = 0.5) +
  theme_bw() +
  ggExtra::removeGrid() +
  labs(x = "Total Length (mm)", y = "Density") +
  geom_text(label = "a)", x = 310, y = 0.007) +
  theme(text = element_text(family = "Times"))

weight_hist <- ggplot(data = fish, mapping = aes(x = Weight)) +
  geom_density(fill = "gray", alpha = 0.5) +
  theme_bw() +
  ggExtra::removeGrid() +
  labs(x = "Total weight (gr)", y = "Density") +
  geom_text(label = "b)", x = 400, y = 0.017) +
  theme(text = element_text(family = "Times"))

gridExtra::grid.arrange(length_hist, weight_hist)
```

```{r}
model <- lm(log(Weight) ~ log(Length), data = fish)
```

```{r, results = "asis"}
TidyModel <- model%>%
  lmtest::coeftest(vcov = sandwich::vcovHC(., type = "HC1")) %>%
  broom::tidy()

robust_se <- TidyModel$std.error %>%
  set_names(TidyModel$term)

wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))
f_string <- c(paste0("F Statistic (df = 1, ",dim(fish)[1]-2,")"), formatC(wald_results$F[2], digits = 2, format = "f"))

stargazer(model,
          header = F,
          se = list(robust_se),
          type = "html",
          t.auto = T,
          p.auto = T,
          intercept.bottom = F,
          single.row = T,
          report = "vcs*",
          omit.stat = "rsq",
          add.lines = list(f_string))
```

```{r}

a <- coefficients(model)[[1]]
b <- coefficients(model)[[2]]

predicted <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
  mutate(Weight = exp((b*log(Length)) + a))

ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
  geom_line(data = predicted, mapping = aes(x = Length, y = Weight), size = 1) +
  geom_point(size = 2, alpha = 0.25) +
  theme_bw() +
  ggExtra::removeGrid() +
  labs(x = "Total length (mm)", y = "Total Weight (g)") +
  theme(text = element_text(family = "Times"))

```

## Comparison of allometric parameters

```{r}
review <- read_csv("biometric_review.csv", col_types = cols())

knitr::kable(review, digits = 2, row.names = F, align = "l")
```

# Discussion and Conclusions

# Aknowledgements

# References

# Raw data

### 2017-07-06 update_ref.R
Added function that automatically updates references

@@ -1,0 +1,13 @@
+update_ref <- function(ref_name = "references.bib"){
+  
+  refs <- RefManageR::ReadBib(ref_name) %>% 
+    as.data.frame()
+  
+  ids <- substr(row.names(as.data.frame(refs)), 1, nchar(row.names(as.data.frame(refs)))-3)
+  
+  refs <- magrittr::set_rownames(refs, ids) %>% 
+    dplyr::mutate(key = ids) %>% 
+    RefManageR::as.BibEntry()
+  
+  RefManageR::WriteBib(bib = refs, file = ref_name)
+}

### 2017-07-06 Manuscript.Rmd
Updated the manuscript

@@
     code_folding: hide
+  word_document: default
 bibliography: references.bib
@@
 
-**Running title:** Length - weigth parameters for *Pterois volitans*
+**Running title:** Length - weight parameters for *Pterois volitans*
 
@@
 
+Lionfish
+
+Lionfish impacts
+
+Studies quantifying biomass from visual surveys
+
+Objectives
+
+  - Provide a new site-specific pair of growth parameters
+  - Highlight the relevance of using site-specific parameters
+  - Provide a review of existing growth parameters
+
 # Materials and Methods
@@
   library(broom)
+  library(tmap)
+  library(tmaptools)
+  library(rgdal)
+  library(sp)
+  library(RefManageR)
   library(tidyverse)
-  library(RefManageR)
 })
@@
 windowsFonts(Times=windowsFont("TT Times New Roman"))
+
+# source('./update_ref.R')
+# update_ref()
 
@@
 
+The present study took place off the coasts of Playa del Carmen, in the coasts of the Mexican Caribbean.
+The region represents the northernmost section of the Mesoamerican reef, which extends from coast of Cancun south to Honduras (**reference**).
+Coral reefs and mangroves are important habitats distributed along the cost, and represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism (**reference**), the main source of income to the local economy.
+
+Coral reefs in the region are characterized by X, Y, Z. Descripcion general de los arrecifes.
+
+```{r}
+# Load shapefiles
+proj <- CRS("+proj=longlat +datum=NAD27")
+
+stat <- readOGR(dsn = "./Spatial", layer = "states", verbose = F)
+
+qroo <- readOGR(dsn = "./Spatial", layer = "muni_2015gw", verbose = F)
+
+qroo <-qroo[qroo$NOM_ENT == "Quintana Roo",]
+
+#Small shapefile for region of interest
+xy1 <- data.frame(X = mean(-87.30662, -87.19194), Y = mean(20.39283, 20.51278))
+coordinates(xy1) <- c("X", "Y")
+proj4string(xy1) <- proj
+res1 <- spTransform(xy1, proj)
+
+#Create shapefile for sampling locations
+sample_points <- fish %>%
+  group_by(Location) %>%
+  summarize(latitude = mean(Latitude, na.rm = T),
+            longitude = mean(Longitude, na.rm = T)) %>%
+  ungroup()
+
+xy <- data.frame(X = -1*abs(sample_points$longitude), Y = sample_points$latitude)
+coordinates(xy) <- c("X", "Y")
+proj4string(xy) <- proj  ## for example
+res <- spTransform(xy, proj)
+b <- SpatialPointsDataFrame(coords = res, data = sample_points, proj4string = proj)
+
+# Create shapefile for relevant communities
+Communities <- data.frame(Longitude = c(-87.24),
+                           Latitude = c(20.5),
+                           Location = c("Pto. Aventuras"),
+                           stringsAsFactors = F)
+
+xy2 <- data.frame(X = -1*abs(Communities$Longitude), Y = Communities$Latitude)
+coordinates(xy2) <- c("X", "Y")
+proj4string(xy2) <- proj  ## for example
+res2 <- spTransform(xy2, proj)
+c <- SpatialPointsDataFrame(coords = res2, data = Communities, proj4string = proj)
+
+pen_map <- tm_shape(stat, bbox = bb(xlim = c(-89.29656, -86.71074), ylim = c(17.89399, 21.60525))) +
+  tm_polygons() +
+  tm_shape(res1) +
+  tm_symbols(shape = 5, size = 2, border.col = "black", col = "black", border.lwd = 2) +
+  tm_grid() +
+  tm_scale_bar()
+
+study_area <- tm_shape(qroo, bbox = bb(xlim = c(-87.30662, -87.19194), ylim = c(20.39283, 20.51278))) +
+  tm_polygons() +
+  tm_shape(b) +
+  tm_symbols(size = 0.125, border.col = "black", col = "black") +
+  tm_shape(c) +
+  tm_symbols(shape = 18, col = "black", border.col = "black", size = 0.5) +
+  tm_compass() +
+  tm_scale_bar()
+
+tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
+
+```
+
 ## Fish sampling
 
+The present study uses samples obtained by Villaseñor-Derbez & Herrera-Pérez [-@villaseorderbez_2014] for stomach content analysis between May and August of 2010.
+A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along 14 Km of coast between Puerto Aventuras and Akumal (Fig.
+1, Table 1).
+All observed organisms (n = `r dim(fish)[1]`) were collected using hand nets -to avoid weight loss due to bleeding- and numbered collection bottles.
+Information on Depth and other comments were recorded in an underwater slide.
+Depth was recorded by dive gauges held by divers as safety procedures during the collections.
+Samples were frozen within 30 mins of completing the dive and stored for posterior analysis in the lab.
+Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
+For every organism Total Length (TL; mm) and Total Weight (TW; gr) were recorded in the lab.
+
+```{r, results = "asis"}
+total <- data.frame(Location = "Total", Latitude = "", Longitude = "", N = 109, stringsAsFactors = F)
+
+fish %>% 
+  group_by(Location) %>% 
+  summarize(Latitude = formatC(mean(Latitude), digits = 3, format = "f"),
+            Longitude = formatC(mean(Longitude), digits = 3, format = "f"),
+            N = n()) %>% 
+  rbind(total) %>% 
+  stargazer(type = "html", header = F, summary = F, add.lines = list(c("Total", "", "", 109)), rownames = F)
+```
+
 ## Data analysis
+
+The weight at length relationship between the observed variables was calculated with the allometric growth function:
+
+$$TW = aTL^b$$
+
+Where $TW$ is the Total Weight (gr), $TL$ is the observed Total Length (mm), $a$ is the scaling parameter and $b$ is the exponent (**revisar**).
+The dependent and independent variables were transformed via base-10 logarithms so that the equation is then:
+
+$$log_{10}(TW) = blog_{10}TL + log{10}(a)$$
+
+To simplify this equation, we can re-write it as:
+
+$$Y = mX + c$$
+Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$.
+This equation was used to estimate the coefficients ($a$ and $b$), which were estimated via an Ordinary Least Square Regression and heteroskedastic-robust; Standard Errors were calculated to account for **lo que sea que Olivier dijo que era importante**.
+
+  - Conversions to biomass
+
+  -Lit review
+
+When reviewing other length-weight relationships, it was noticed that some papers indistinctly use $a$ to report either the multiplying coefficient in **eq.
+1** or the y-intercept ($c$) in **eq.
+2**, which might sometimes be overlooked.
+Furthermore, some studies report their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicates that they were estimated as cm-to-gr conversions (Fig.
+A1).
+Here, both parameters ($a$ and $c$) are reported for the present findings and, when ever required, coefficients from other studies are converted.
+All coefficients are reported as mm to gr conversions.
 
@@
 ```{r}
-model <- lm(log(Weight) ~ log(Length), data = fish)
+model <- lm(log10(Weight) ~ log10(Length), data = fish)
 ```
@@
 wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))
-f_string <- c(paste0("F Statistic (df = 1, ",dim(fish)[1]-2,")"), formatC(wald_results$F[2], digits = 2, format = "f"))
+f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))
 
@@
           report = "vcs*",
-          omit.stat = "rsq",
-          add.lines = list(f_string))
-```
-
-```{r}
-
-a <- coefficients(model)[[1]]
-b <- coefficients(model)[[2]]
-
-predicted <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
-  mutate(Weight = exp((b*log(Length)) + a))
-
-ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
-  geom_line(data = predicted, mapping = aes(x = Length, y = Weight), size = 1) +
-  geom_point(size = 2, alpha = 0.25) +
-  theme_bw() +
-  ggExtra::removeGrid() +
-  labs(x = "Total length (mm)", y = "Total Weight (g)") +
-  theme(text = element_text(family = "Times"))
-
+          omit.stat = c("rsq", "f"),
+          add.lines = list(f_string),
+          ci = T)
 ```
@@
 
+```{r}
+
+a <- coefficients(model)[[1]]
+b <- coefficients(model)[[2]]
+
+predicted_this_study <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
+  mutate(Weight = 10^a*Length^b)
+
+plot_fit_this_study <-  ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
+  geom_line(data = predicted_this_study, mapping = aes(x = Length, y = Weight), size = 1) +
+  geom_point(size = 2, alpha = 0.25, color = "black") +
+  theme_bw() +
+  ggExtra::removeGrid() +
+  labs(x = "Total length (mm)", y = "Total Weight (g)") +
+  theme(text = element_text(family = "Times")) +
+  scale_color_brewer(palette = "Set3") +
+  theme(text=element_text(family="Times"))
+
+plot_fit_this_study
+```
+
+```{r, fig.height = 9.5, fig.width = 6}
+predicted_all <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
+  mutate(This = 10^a*Length^b, 
+         APA = (10^review$a[1]) * ((Length/10)^review$b[1]),
+         APF = (10^review$a[2]) * (Length^review$b[2]),
+         APM = (10^review$a[3]) * (Length^review$b[3]),
+         Sandel = review$a[4] * ((Length/10)^review$b[4]),
+         Chin = (10^review$a[5]) * (Length^review$b[5]),
+         Barbour = review$a[6] * Length^review$b[6],
+         deLeon = review$a[7] * Length^review$b[7],
+         FoggA = (10^review$a[8]) * (Length^review$b[8]),
+         FoggM = (10^review$a[9]) * (Length^review$b[9]),
+         FoggF = (10^review$a[10]) * (Length^review$b[10]),
+         Edwards = review$a[11] * Length^review$b[11],
+         Sabido = review$a[12] * ((Length/10)^review$b[12]),
+         FishBase = review$a[13] * ((Length/10)^review$b[13])) %>%
+  gather(Study_id, Weight, -Length) %>% 
+  left_join(review, by ="Study_id") %>% 
+  mutate(ThisStudy = ifelse(Study_id == "This", "Actual", "Other"))
+
+plot_fit_all_studies <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
+  geom_line(data = predicted_all, mapping = aes(x = Length, y = Weight, linetype = Gender, color = Study), size = 1) +
+  geom_point(size = 2, alpha = 0.25, color = "black") +
+  theme_bw() +
+  ggExtra::removeGrid() +
+  labs(x = "Total length (mm)", y = "Total Weight (g)") +
+  theme(text = element_text(family = "Times"),
+        legend.justification=c(0,1),
+        legend.position=c(0.01, 0.99)) +
+  guides(color = guide_legend(title=NULL)) +
+  scale_color_brewer(palette = "Paired")
+
+plot_fit_all_studies_log <- ggplot(data = fish, mapping = aes(x = Length, y = log10(Weight))) +
+  geom_line(data = predicted_all, mapping = aes(x = Length, y = log10(Weight), linetype = Gender, color = Study), size = 1) +
+  geom_point(size = 2, alpha = 0.25, color = "black") +
+  theme_bw() +
+  ggExtra::removeGrid() +
+  labs(x = "Total length (mm)", y = "log10(TW)") +
+  theme(text = element_text(family = "Times"),
+        legend.position = "None")+
+  scale_x_continuous(expand=c(0,0))+
+  scale_y_continuous(expand=c(0,0))
+
+gridExtra::grid.arrange(plot_fit_all_studies, plot_fit_all_studies_log)
+
+```
+
 # Discussion and Conclusions
+
+Not using spear poles allows us to have a full sample of fish with a wider range of sizes and weights, ideal for visual census. Also, there is no loss in body mass due to bleeding.
 

### 2017-07-07 Manuscript.Rmd
Updated manuscript

@@
 ---
-title: "Manuscript"
+title: "Biometry of the invasive lionfish (*Pterois volitans*) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range"
+header-includes:
+- \usepackage{setspace}
+- \doublespacing
+- \usepackage{lineno}
+- \linenumbers
 output:
-  html_notebook:
-    code_folding: hide
-  word_document: default
+  pdf_document:
+    fig_caption: yes
+fontsize: 12pt
 bibliography: references.bib
@@
 
-# Title page
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = F)
 
-**Title:** Biometry of the invasive lionfish (*Pterois volitans*) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range
+windowsFonts(Times=windowsFont("TT Times New Roman"))
 
-**Name of author:** Juan Carlos Villaseñor-Derbez
+# source('./update_ref.R')
+# update_ref()
+```
 
-**Affiliation:** Bren School of Environmental Sciences and Management
+```{r, load packages}
 
-**Full postal address:** University of California Santa Barbara, Santa Barbara,  CA 93106, USA
+suppressPackageStartupMessages({
+  library(RColorBrewer)
+  library(colorRamps)
+  library(stargazer)
+  library(sandwich)
+  library(lmtest)
+  library(broom)
+  library(tmap)
+  library(tmaptools)
+  library(rgdal)
+  library(sp)
+  library(RefManageR)
+  library(tidyverse)
+})
 
-**Running title:** Length - weight parameters for *Pterois volitans*
+```
+
+Juan Carlos Villaseñor-Derbez^1^\
+
+^1^ Bren School of Environmental Sciences and Management, University of California Santa Barbara\
+
+**Full postal address:**
+4312 Bren Hall, Santa Barbara, CA, 93106\
+
+**Running title:** Length - weight parameters for *Pterois volitans* \
 
@@
 Juan Carlos Villaseñor-Derbez   
-
 4312 Bren Hall  
-
 Santa Barbara, CA   
-
 93106   
-
 jvillasenor@bren.ucsb.edu   
-
 +1 (207) 205 8435
@@
 
-**Title**
+**Title of the contribution:** Biometry of the invasive lionfish (*Pterois volitans*) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range\
 
@@
 
-300 words
+300 words\
 
@@
 
-lionfish, biometry, length-weight relationship, Mexico
-
-___________________
+lionfish, biometry, length-weight relationship, Mexico\
 
@@
 
+300 palabras\
+
 **Palabras clave**
 
-pez león, biometría, relación lopngitud-peso, México
+pez león, biometría, relación lopngitud-peso, México\
 
@@
 
-```{r}
-
-suppressPackageStartupMessages({
-  library(RColorBrewer)
-  library(colorRamps)
-  library(stargazer)
-  library(sandwich)
-  library(lmtest)
-  library(broom)
-  library(tmap)
-  library(tmaptools)
-  library(rgdal)
-  library(sp)
-  library(RefManageR)
-  library(tidyverse)
-})
-
-windowsFonts(Times=windowsFont("TT Times New Roman"))
-
-# source('./update_ref.R')
-# update_ref()
-
-```
-
-```{r}
+```{r load fish data, include = F}
 fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
@@
 
-```{r}
+```{r create map, include = F}
 # Load shapefiles
@@
 
-```{r, results = "asis"}
-total <- data.frame(Location = "Total", Latitude = "", Longitude = "", N = 109, stringsAsFactors = F)
+```{r table of locations, include = F}
+total <- data.frame(Location = "Total", Latitude = "", Longitude = "", minD = min(fish$Depth_m), maxD = max(fish$Depth_m), meanD = formatC(mean(fish$Depth_m), digits = 1, format = "f"), n = 109, stringsAsFactors = F)
 
-fish %>% 
+location_table <- fish %>% 
   group_by(Location) %>% 
@@
             Longitude = formatC(mean(Longitude), digits = 3, format = "f"),
-            N = n()) %>% 
+            minD = formatC(min(Depth_m), digits = 1, format = "f"),
+            maxD = formatC(max(Depth_m), digits = 1, format = "f"),
+            meanD = formatC(mean(Depth_m), digits = 1, format = "f"),
+            n = n()) %>% 
   rbind(total) %>% 
-  stargazer(type = "html", header = F, summary = F, add.lines = list(c("Total", "", "", 109)), rownames = F)
+  knitr::kable(row.names = F, caption = "Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.
+n = sample size.", col.names = c("Location", "Latitude", "Longitude", "Minimum Depth (m)", "Maximum Depth (m)", "Mean Depth (m)", "n"))
+
+location_table
 ```
@@
 
-```{r, results = "asis"}
-fish %>% 
-  select(Length, Weight, Stomach, Depth_m) %>% 
+```{r summary table, include = F}
+summary_table <- fish %>% 
+  select(Length, Weight) %>% 
   as.data.frame() %>% 
-  stargazer(header = F, type = "html", digits = 2)
+  stargazer(header = F, type = "latex", digits = 2, title = "Summary statistics of Length and Weight of sampled organisms.")
 ```
 
-```{r, fig.width = 5, fig.height = 7}
+```{r histogram figures, include = F}
 length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
@@
 
-```{r}
+```{r model fitting}
 model <- lm(log10(Weight) ~ log10(Length), data = fish)
@@
 
-```{r, results = "asis"}
+```{r regression table, include = F}
 TidyModel <- model%>%
@@
 
-stargazer(model,
+regression_table <- stargazer(model,
           header = F,
           se = list(robust_se),
-          type = "html",
+          type = "latex",
           t.auto = T,
@@
 ```
+\clearpage
 
@@
 
-```{r}
+```{r, include = F}
 review <- read_csv("biometric_review.csv", col_types = cols())
 
-knitr::kable(review, digits = 2, row.names = F, align = "l")
+review_table <- review %>% 
+  select(Reference, n = N, a, c, b, r2, Gender, minD, maxD, Spear) %>% 
+  knitr::kable(digits = 4, row.names = F, caption = "Allometric growth parameters for eight published papers, Fishbase (Froese and Pauly 2016), and this study.
+All parameters have been adjusted to convert from millimiters to grams.
+n = Sample size, a = scaling parameter for eq.
+1, c = y-intercept for eq.
+3, b = exponent or slope for eq.
+1 or eq.
+2, respectively.")
+
+review_table
 ```
 
-```{r}
+```{r scatter plot, include = F}
 
@@
   theme_bw() +
-  ggExtra::removeGrid() +
   labs(x = "Total length (mm)", y = "Total Weight (g)") +
@@
 
-```{r, fig.height = 9.5, fig.width = 6}
+```{r review plots, include = F}
 predicted_all <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
-  mutate(This = 10^a*Length^b, 
-         APA = (10^review$a[1]) * ((Length/10)^review$b[1]),
-         APF = (10^review$a[2]) * (Length^review$b[2]),
-         APM = (10^review$a[3]) * (Length^review$b[3]),
-         Sandel = review$a[4] * ((Length/10)^review$b[4]),
-         Chin = (10^review$a[5]) * (Length^review$b[5]),
-         Barbour = review$a[6] * Length^review$b[6],
-         deLeon = review$a[7] * Length^review$b[7],
-         FoggA = (10^review$a[8]) * (Length^review$b[8]),
-         FoggM = (10^review$a[9]) * (Length^review$b[9]),
-         FoggF = (10^review$a[10]) * (Length^review$b[10]),
-         Edwards = review$a[11] * Length^review$b[11],
-         Sabido = review$a[12] * ((Length/10)^review$b[12]),
-         FishBase = review$a[13] * ((Length/10)^review$b[13])) %>%
+  mutate(This = review$a[14] * (Length^review$b[14]), 
+         APA = review$a[1] * (Length^review$b[1]),
+         APF = review$a[2] * (Length^review$b[2]),
+         APM = review$a[3] * (Length^review$b[3]),
+         Sandel = review$a[4] * (Length^review$b[4]),
+         Chin = review$a[5] * (Length^review$b[4]),
+         Barbour = review$a[6] * (Length^review$b[6]),
+         deLeon = review$a[7] * (Length^review$b[7]),
+         FoggA = review$a[8] * (Length^review$b[8]),
+         FoggM = review$a[9] * (Length^review$b[9]),
+         FoggF = review$a[10] * (Length^review$b[10]),
+         Edwards = review$a[11] * (Length^review$b[11]),
+         Sabido = review$a[12] * (Length^review$b[12]),
+         FishBase = review$a[13] * (Length^review$b[13])) %>%
   gather(Study_id, Weight, -Length) %>% 
@@
   geom_line(data = predicted_all, mapping = aes(x = Length, y = Weight, linetype = Gender, color = Study), size = 1) +
-  geom_point(size = 2, alpha = 0.25, color = "black") +
   theme_bw() +
-  ggExtra::removeGrid() +
   labs(x = "Total length (mm)", y = "Total Weight (g)") +
@@
         legend.justification=c(0,1),
-        legend.position=c(0.01, 0.99)) +
+        legend.position=c(0.01, 0.99),
+        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted")) +
   guides(color = guide_legend(title=NULL)) +
@@
   geom_line(data = predicted_all, mapping = aes(x = Length, y = log10(Weight), linetype = Gender, color = Study), size = 1) +
-  geom_point(size = 2, alpha = 0.25, color = "black") +
   theme_bw() +
-  ggExtra::removeGrid() +
   labs(x = "Total length (mm)", y = "log10(TW)") +
@@
 
+\clearpage
+
+# Tables
+
+## Location table
+
+```{r}
+location_table
+```
+
+\clearpage
+
+## Summary table
+
+```{r, results = "asis"}
+cat(summary_table)
+```
+
+\clearpage
+
+## Regression table
+
+```{r, results = "asis"}
+cat(regression_table)
+```
+
+\clearpage
+
+## Review table
+
+```{r}
+review_table
+```
+
+\clearpage
+
+# Figures
+
+## Map
+
+```{r}
+tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
+```
+
+\clearpage
+
+## Histograms
+
+```{r, fig.width = 5, fig.height = 7}
+gridExtra::grid.arrange(length_hist, weight_hist)
+```
+
+## Scatter plot
+
+```{r}
+plot_fit_this_study
+```
+
+## Review plots
+
+```{r, fig.height = 9.5, fig.width = 6}
+gridExtra::grid.arrange(plot_fit_all_studies, plot_fit_all_studies_log)
+```
+
 # References
-
-# Raw data

### 2017-07-08 Manuscript.Rmd
Fixed size of title text

@@
 ---
-title: "Biometry of the invasive lionfish (*Pterois volitans*) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range"
+title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range}
 header-includes:

### 2017-07-08 Manuscript.Rmd
Added equation numbering

@@
 
+<script type="text/x-mathjax-config">
+MathJax.Hub.Config({
+  TeX: { 
+      equationNumbers: { 
+            autoNumber: "all",
+            formatNumber: function (n) {return '9.'+n}
+      } 
+  }
+});
+</script>
+
 ```{r setup, include=FALSE}
@@
 windowsFonts(Times=windowsFont("TT Times New Roman"))
-
-# source('./update_ref.R')
-# update_ref()
 ```
 
-```{r, load packages}
-
+```{r load packages}
 suppressPackageStartupMessages({
@@
 
-$$TW = aTL^b$$
+\begin{equation}TW = aTL^b\end{equation}
 
@@
 
-$$log_{10}(TW) = blog_{10}TL + log{10}(a)$$
+\begin{equation}log_{10}(TW) = blog_{10}TL + log{10}(a)\end{equation}
 
@@
 
-$$Y = mX + c$$
+\begin{equation}Y = mX + c\end{equation}
+
 Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$.

### 2017-07-08 Manuscript.Rmd
Added first part of introduction

@@
 
+# source('./update_ref.R')
+# update_ref()
 ```
@@
 
-Lionfish impacts
+Lionfish (*Pterois volitans - miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean.
+They are the first marine vertebrates to establish in North Atlantic [@schofield_2009: @schofield_2010] and Caribbean coasts.
+Their presence in these waters has been labeled as a major marine invasion due to its threat to local biodiversity, the veolocity of its invasion, and the difficulty of management [@hixon_2016].
 
-Studies quantifying biomass from visual surveys
+Liofnish have been prooven to reduce recruitment of local reef fish species [@albins_2008].
+Their diet focuses on small demersal reef-associated fish and crustaceans [@morris_2009; @villaseorderbez_2014].
+
+Lionfish were first recorded in Mexican waters in 2010 [@aguilarperera_2010].
+
+Studies quantifying biomass from visual surveys / Ecosim simulations / stock assessments
+
+Significant efforts have been made to understand the possible impacts of the invasion by X (cita de X), y (cita de Y) y z (cita de Z).
+An important pair of parameters often used in these studies are those which allow researchers to convert observed lengths into weights (*i.e.* weight-at-length parameters) to estimate biomass.
+Having presission of these parameters is important, because small changes in any of them can result in important over- or unnderestimation of biomass levels.
+This becomes particularly important when research involves, for example, identifying the total biomass available for harvest by fishers (as invasion management programs).
 
@@
 
-  - Provide a new site-specific pair of growth parameters
-  - Highlight the relevance of using site-specific parameters
-  - Provide a review of existing growth parameters
+The objectives of this study include providing site-specific weight-at-length parameters for the invasive lionfish in the Mexican Caribbean region.
+At the same time, we highlight the importance of using site-specific parameters by using those from other studies and comparing predicted weights to those found in this study.
+Finaly, we provide a review of and summarize other weight-at-length studies presented, making them readily accessible for future research.
 

### 2017-07-08 Manuscript.Rmd
Predicted biomass for each site

@@
 
+```{r Predicted biomass for each site}
+Predicted_biomass <- fish %>% 
+  mutate(This = review$a[14] * (Length^review$b[14]), 
+         APA = review$a[1] * (Length^review$b[1]),
+         APF = review$a[2] * (Length^review$b[2]),
+         APM = review$a[3] * (Length^review$b[3]),
+         Sandel = review$a[4] * (Length^review$b[4]),
+         Chin = review$a[5] * (Length^review$b[4]),
+         Barbour = review$a[6] * (Length^review$b[6]),
+         deLeon = review$a[7] * (Length^review$b[7]),
+         FoggA = review$a[8] * (Length^review$b[8]),
+         FoggM = review$a[9] * (Length^review$b[9]),
+         FoggF = review$a[10] * (Length^review$b[10]),
+         Edwards = review$a[11] * (Length^review$b[11]),
+         Sabido = review$a[12] * (Length^review$b[12]),
+         FishBase = review$a[13] * (Length^review$b[13])) %>% 
+  group_by(Location) %>% 
+  summarize(Observed = sum(Weight),
+            This = sum(This)/Observed,
+            APA = sum(APA)/Observed,
+            APF = sum(APF)/Observed,
+            APM = sum(APM)/Observed, 
+            Sandel = sum(Sandel)/Observed,
+            Chin = sum(Chin)/Observed,
+            Barbour = sum(Barbour)/Observed,
+            deLeon = sum(deLeon)/Observed,
+            FoggA = sum(FoggA)/Observed,
+            FoggM = sum(FoggM)/Observed,
+            FoggF = sum(FoggF)/Observed,
+            Edwards = sum(Edwards)/Observed,
+            Sabido = sum(Sabido)/Observed,
+            FishBase = sum(FishBase)/Observed) %>% 
+  ungroup() %>% 
+  gather(Study, Biomass, -Location)
+```
+
+```{r plot comparing predictions, include = F}
+Predicted_biomass_plot <-   Predicted_biomass %>% 
+  filter(!Study == "Observed") %>% 
+  ggplot(aes(x = Study, y = Biomass)) +
+  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0, size = 1) +
+  stat_summary(geom = "point", fun.y = "mean", fill = "blue", size = 3, shape = 21) +
+  geom_hline(yintercept = 1, linetype = "dashed") +
+  labs(y = "Biomass (Predicted / Observed)") +
+  coord_flip() +
+  theme_bw() +
+  theme(text = element_text(family = "Times"))
+
+Predicted_biomass_plot
+```
+
 # Discussion and Conclusions

### 2017-07-12 Manuscript.Rmd
Added final plots
Included first part of results and updated package references

--- 2017-07-08 Manuscript.Rmd
@@
 fontsize: 12pt
-bibliography: references.bib
+bibliography: [references.bib, packages.bib]
 ---
@@
 suppressPackageStartupMessages({
-  library(RColorBrewer)
-  library(colorRamps)
+  # library(RColorBrewer)
+  # library(colorRamps)
+  library(e1071)
   library(stargazer)
@@
 
-Lionfish
+At least 84% of the marine eco-regions have reported the presence of an invasive species [@molnar_2008].
+The presence of invasive alien species represents a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries [@bax_2003].
+By 2005, the economic cost of invasive species to the United States was  estimated at \$120 billion per year and nearly 42% of species that have been included in the Endangered or Threatened species list have been labeled as such due to presence of invasive species [@pimentel_2005].
+Invasive species may threaten native species through competition [@davis_2003] or predation.
+This highlightes the importance of understanding, managing, and preventing ecological invasions.
 
-Lionfish impacts
+Lionfish (*Pterois volitans - miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean likely introduced through libreation of aquarium-kept organisms [@betancurr_2011].
+They are the first marine vertebrates to establish in North Atlantic [@schofield_2009: @schofield_2010] and Caribbean coasts.
+Lionfish have been recorded in coral reefs [@aguilarperera_2010], but also in other habitats like estuaries [@jud_2011], mangroves [@barbour_2010] and hard-bottom reefs [@muoz_2011].
+Their presence in these waters has been labeled as a major marine invasion due to its threat to local biodiversity, the veolocity of its invasion, and its difficulty of management [@hixon_2016].
 
-Studies quantifying biomass from visual surveys
+As ways to reduce the abundance of this invasive species local authorities have promoted removal programs incentivized consumption of this invasive species [@chin_2016].
+Lionfish removals have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales [@sandel_2015, @chin_2016, @deleon_2013].
+While complete erradication through fishing effort is unlikely to be a solution due to the rapid recovery rates exhibited by the species [@barbour_2011], further incentivizing its consumption might create a market demand big enough to promote a fishery [@chin_2016].
 
-Objectives
+A significant amount of research has been done on lionfish feeding ecology in North Carolina [@muoz_2011], the Bahamas [@morris_2009; @cote_2013], Northern Gulf of Mexico [@dahl_2014], Mexican Caribbean [@valdezmoreno_2012; @villaseorderbez_2014], and Costa Rica [@sandel_2015].
+It has been identified that lionfish can reduce recruitment [@albins_2008] and population sizes [@green_2012] of native reef-fish species, and further the endangerement of critically endangered reef fish [@rocha_2015].
+This information has been useful in predicting the trophic impacts of lionfish [@ariasgonzalez_2011].
+Significant efforts have also been made to understand the possible impacts of the invasion by keeping track of the invasion range through time [@schofield_2009; @schofield_2010] and predicting invasion ranges under climate change scenarios (@grieve_2016).
 
-  - Provide a new site-specific pair of growth parameters
-  - Highlight the relevance of using site-specific parameters
-  - Provide a review of existing growth parameters
+Biomass is a standard indicator used to measure the state or size of a population.
+Biomass has been used in lionfish research to convert individual fish length observations into fish weight.
+In order to do this, researchers must find growth parameters thad describe the growth of their species for a particular region or location.
+Having precision of these parameters is important, because small changes in any of them can result in important over- or underestimation of biomass levels.
+This becomes particularly important when research involves, for example, identifying the total biomass available for harvest by fishers -as invasion management programs- or the efficacy of lionfish removals.
+
+The objectives of this study include providing site-specific weight-at-length parameters for the invasive lionfish in the Mexican Caribbean region.
+At the same time, we highlight the importance of using site-specific parameters by estimating biomass with parameters from other regions across the invasion range and comparing them to observed biomasses.
+Finally, we summarize other weight-at-length studies presented, making them readily accessible for future research.
 
@@
 
-The present study uses samples obtained by Villaseñor-Derbez & Herrera-Pérez [-@villaseorderbez_2014] for stomach content analysis between May and August of 2010.
+The present study used samples obtained by @villaseorderbez_2014 for stomach content analysis between May and August of 2010.
 A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along 14 Km of coast between Puerto Aventuras and Akumal (Fig.
 1, Table 1).
+Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
 All observed organisms (n = `r dim(fish)[1]`) were collected using hand nets -to avoid weight loss due to bleeding- and numbered collection bottles.
-Information on Depth and other comments were recorded in an underwater slide.
+Information on depth and other comments were recorded in an underwater slide.
 Depth was recorded by dive gauges held by divers as safety procedures during the collections.
-Samples were frozen within 30 mins of completing the dive and stored for posterior analysis in the lab.
-Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
-For every organism Total Length (TL; mm) and Total Weight (TW; gr) were recorded in the lab.
+Samples were frozen within 30 minutes of completing the dive and stored for posterior analysis in the lab.
+For every organism, Total Length (TL; mm) and Total Weight (TW; gr) were recorded in the lab.
 
@@
   knitr::kable(row.names = F, caption = "Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.
-n = sample size.", col.names = c("Location", "Latitude", "Longitude", "Minimum Depth (m)", "Maximum Depth (m)", "Mean Depth (m)", "n"))
+n = sample size.", col.names = c("Location", "Lat.", "Long.", "Min.
+Depth", "Max.
+Depth", "Mean Depth", "n"))
 
@@
 
-Where $TW$ is the Total Weight (gr), $TL$ is the observed Total Length (mm), $a$ is the scaling parameter and $b$ is the exponent (**revisar**).
+Where $TW$ is the Total Weight (gr), $TL$ is the observed Total Length (mm), $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
+When $b = 3$, it is said that the organism exhibits a perfect isometric growth.
 The dependent and independent variables were transformed via base-10 logarithms so that the equation is then:
@@
 Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$.
-This equation was used to estimate the coefficients ($a$ and $b$), which were estimated via an Ordinary Least Square Regression and heteroskedastic-robust; Standard Errors were calculated to account for **lo que sea que Olivier dijo que era importante**.
+The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard errors.
+Both coefficients were tested agains the null hypothesis of no change (*i.e.* $h_0: c = 0$ and $h_0: b = 0$).
+Additionally, the allometric parameter was tested against the null hypothesis of isometric growth ($H_0: b = 3$).
+Coefficient testing was made with a two-tailed Student's t-test.
+The significance of the regression was corroborated with an F-test.
 
-  - Conversions to biomass
-
-  -Lit review
-
-When reviewing other length-weight relationships, it was noticed that some papers indistinctly use $a$ to report either the multiplying coefficient in **eq.
+Other growth parameters were extracted from published research from North Carolina [@barbour_2011], Northern [@fogg_2013] and Southern [@aguilarperera_2016] Gulf of Mexico, the Southern Mexican Caribbean [@sabidoitza_2016], Little Cayman [@edwards_2014], Jamaica [@chin_2016], Bonaire [@deleon_2013] and Costa Rica [@sandel_2015].
+Additionally, parameters from Fishbase [@froese_website_2016] were also included in this study.
+When available, information on sampling methods, location, and depth ranges of each study was retreived.
+During this review process, it was noticed that some papers indistinctly use $a$ to report either the ponderal index in **eq.
 1** or the y-intercept ($c$) in **eq.
 2**, which might sometimes be overlooked.
-Furthermore, some studies report their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicates that they were estimated as cm-to-gr conversions (Fig.
-A1).
-Here, both parameters ($a$ and $c$) are reported for the present findings and, when ever required, coefficients from other studies are converted.
+Furthermore, some studies report their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicates that they were estimated as cm-to-gr conversions.
+Here, both parameters ($a$ and $c$) are reported for the present findings and, when ever required, values from other studies are converted for consistency.
 All coefficients are reported as mm to gr conversions.
 
+Observed biomass was calculated as the sum of all observed organisms for each location.
+Expected biomass for each organism was calculated with the growth parameteres estimated in this study, as well as those retreived from additional literature.
+Then, total expected biomass was calculated for each surveyed site as the sum of expected biomasses previously calculated.
+For each study and site, biomass was divided by the corresponding observed biomass to obtain a ratio that allowed rapid identification of over- or underestimation.
+Therefore, values lower than 1 indicate that the parameters used underestimate the biomass.
+On the other side, values larger than 1 indicate that the parameteres used overestimate biomass.
+Mean expected-to-observed biomass ratios were calculated by averaging across all sites for each study.
+
+All hypothesis testing was performed with a confidence level of $\alpha = 0.01$ and performed in R version 3.4.0 [@rcore_2017].
+Data wrangling was performed with the tidyverse package [@tidyverse_2017].
+Maps were created with a mix of functions from the sp [@sp_2017], rgdal [@rgdal_2017], tmap [@tmap_2017], and tmaptools [@tmaptools_2017] packages.
+Correction for heteroskedastic-robust standard errors was done with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
+Models were manipulated with with the broom package [@broom_2017].
+Stargazer [@stargazer_2015] was used to produce the tables, and refmanager [@RefManager_2014] was used to keep track of citations.
+The manuscript was written in rmarkdown [@rmarkdown_2017] and processed with the knitr package [@knitr_2017].
+
 # Results
+
+A summary of Total Lengths and Total Weights of the the `r dim(fish)[1]` sampled organisms is presented in Table 1.
+The smallest organism (TL = `r formatC(min(fish$Length), digits = 2, format = "f")`) was also the lightest organism (TW = `r formatC(min(fish$Weight), digits = 2, format = "f")`).
+However, the largest organism (TL = `r formatC(max(fish$Length), digits = 2, format = "f")`) was not the heaviest (TW = `r formatC(fish$Weight[fish$Length == max(fish$Length)], digits = 2, format = "f")`), and the heaviest organism (TW = `r formatC(max(fish$Weight), digits = 2, format = "f")`) was `r formatC(fish$Length[fish$Weight == max(fish$Weight)], digits = 2, format = "f")` mm in total length.
+Kernell density plots (Fig.
+2) show the distribution for TL and TW.
+Both measures were positively skewed, with skewness of `r formatC(skewness(fish$Length), digits = 2, format = "f")` for TL and `r formatC(skewness(fish$Weight), digits = 2, format = "f")` for TW.
 
@@
 ```
-\clearpage
+
+```{r}
+test_intercept <- 2*pt(abs(coef(model)[[1]]/robust_se[[1]]), df = 107, lower.tail = F)
+
+test_slope <- 2*pt(abs(coef(model)[[2]]/robust_se[[2]]), df = 107, lower.tail = F)
+
+test_slope_3 <- 2*pt(abs((coef(model)[[2]]-3)/robust_se[[2]]), df = 107, lower.tail = F)
+
+```
+
+The model adjusted to eq.
+3 estimated the coefficient values at $m = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
+The intercept and slope were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
+Additionally, the allometric factor was significantly different from zero ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$).
+More information on model fit and confidence intervals of estimated coefficients is presented in Table 3.
 
@@
   gather(Study_id, Weight, -Length) %>% 
-  left_join(review, by ="Study_id") %>% 
-  mutate(ThisStudy = ifelse(Study_id == "This", "Actual", "Other"))
+  left_join(review, by ="Study_id")
 
@@
 
+```
+
+```{r Predicted biomass for each site}
+Predicted_biomass <- fish %>% 
+  mutate(This = review$a[14] * (Length^review$b[14]), 
+         APA = review$a[1] * (Length^review$b[1]),
+         APF = review$a[2] * (Length^review$b[2]),
+         APM = review$a[3] * (Length^review$b[3]),
+         Sandel = review$a[4] * (Length^review$b[4]),
+         Chin = review$a[5] * (Length^review$b[4]),
+         Barbour = review$a[6] * (Length^review$b[6]),
+         deLeon = review$a[7] * (Length^review$b[7]),
+         FoggA = review$a[8] * (Length^review$b[8]),
+         FoggM = review$a[9] * (Length^review$b[9]),
+         FoggF = review$a[10] * (Length^review$b[10]),
+         Edwards = review$a[11] * (Length^review$b[11]),
+         Sabido = review$a[12] * (Length^review$b[12]),
+         FishBase = review$a[13] * (Length^review$b[13])) %>% 
+  group_by(Location) %>% 
+  summarize(Observed = sum(Weight),
+            This = sum(This)/Observed,
+            APA = sum(APA)/Observed,
+            APF = sum(APF)/Observed,
+            APM = sum(APM)/Observed, 
+            Sandel = sum(Sandel)/Observed,
+            Chin = sum(Chin)/Observed,
+            Barbour = sum(Barbour)/Observed,
+            deLeon = sum(deLeon)/Observed,
+            FoggA = sum(FoggA)/Observed,
+            FoggM = sum(FoggM)/Observed,
+            FoggF = sum(FoggF)/Observed,
+            Edwards = sum(Edwards)/Observed,
+            Sabido = sum(Sabido)/Observed,
+            FishBase = sum(FishBase)/Observed) %>% 
+  ungroup() %>% 
+  gather(Study_id, Biomass, -Location) %>% 
+  left_join(review, by ="Study_id")
+```
+
+```{r plot comparing predictions, include = F}
+Predicted_biomass_plot <-   Predicted_biomass %>% 
+  filter(!Study == "Observed") %>% 
+  transform(Study_id = reorder(Study_id, -Biomass)) %>% 
+  ggplot(aes(x = Study_id, y = Biomass)) +
+  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0, size = 1) +
+  stat_summary(geom = "point", fun.y = "mean", fill = "blue", size = 3, shape = 21) +
+  geom_hline(yintercept = 1, linetype = "dashed") +
+  labs(y = "Biomass (Predicted / Observed)", x = "Study") +
+  coord_flip() +
+  theme_bw() +
+  theme(text = element_text(family = "Times"))
+
+Predicted_biomass_plot
 ```
@@
 
-```{r}
+```{r, fig.cap = "Map of the study area.
+The black inset on the left indicates the location where study sites are distributed.
+On the right, circular markers indicate sampling sites and the black romboid indicates location of Puerto Aventuras."}
 tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
@@
 
-```{r, fig.width = 5, fig.height = 7}
+```{r, fig.width = 5, fig.height = 6, fig.cap = "Kernell density plots for a) Total length (mm) and b) Total weight (gr) for 109 lionfish sampled off the coast of Puerto Aventuras, Mexico."}
 gridExtra::grid.arrange(length_hist, weight_hist)
@@
 
+\clearpage
+
 ## Scatter plot
 
-```{r}
+```{r, fig.cap = "Weight-at-length relationship for 109 lionfish sampled off the coast of Puerto Aventuras, Mexico."}
 plot_fit_this_study
@@
 
+\clearpage
+
 ## Review plots
 
-```{r, fig.height = 9.5, fig.width = 6}
-gridExtra::grid.arrange(plot_fit_all_studies, plot_fit_all_studies_log)
+```{r, fig.height = 4.5, fig.width = 6, fig.cap = "Weight-at-length relationships (n = 14) for eight studies, this study, and FishBase parameters.
+Colors indicate studies from which the parameters were extracted.
+Solid lines indicate that the fit was performed for males and females pooled together.
+Dotted lines indicate that the regression was performed on females, and dashed lines indicate it was performed for males."}
+plot_fit_all_studies
 ```
 
+\clearpage
+
+## Predictions plot
+
+```{r, fig.cap = "Mean predicted to observed biomass ratios for eight studies, this study, and FishBase parameters. Error bars indicate +/- 1 Standard Error."}
+Predicted_biomass_plot
+```
+
+\clearpage
+
 # References

### 2017-07-14 Manuscript.Rmd
Added full results and outline of discussion

@@
 ---
-title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range}
+title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in
+  Playa del Carmen, Mexico and a review of length - weight parameters across the invasion
+  range}
+csl: apa.csl
+fontsize: 12pt
+output:
+  pdf_document:
+    fig_caption: yes
 header-includes:
@@
 - \linenumbers
-output:
-  pdf_document:
-    fig_caption: yes
-fontsize: 12pt
-bibliography: [references.bib, packages.bib]
+bibliography:
+- references.bib
+- packages.bib
 ---
@@
 Additionally, parameters from Fishbase [@froese_website_2016] were also included in this study.
-When available, information on sampling methods, location, and depth ranges of each study was retreived.
+When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retreived.
+Whenever gender was not specified, it was assumed that the results were presented for both genders pooled together.
 During this review process, it was noticed that some papers indistinctly use $a$ to report either the ponderal index in **eq.
@@
 
-Observed biomass was calculated as the sum of all observed organisms for each location.
+Mean observed biomass was calculated as the average Total Weight of all observed organisms.
 Expected biomass for each organism was calculated with the growth parameteres estimated in this study, as well as those retreived from additional literature.
-Then, total expected biomass was calculated for each surveyed site as the sum of expected biomasses previously calculated.
-For each study and site, biomass was divided by the corresponding observed biomass to obtain a ratio that allowed rapid identification of over- or underestimation.
+Then, mean expected biomass was calculated for each study.
+All expected biomass values were divided by the observed biomass to obtain a ratio that allowed rapid identification of over- or underestimation with respect to the observed biomass in this study.
 Therefore, values lower than 1 indicate that the parameters used underestimate the biomass.
 On the other side, values larger than 1 indicate that the parameteres used overestimate biomass.
-Mean expected-to-observed biomass ratios were calculated by averaging across all sites for each study.
+Median and mean expected to observed biomass ratios were calculated across all sites for each study.
 
@@
 
-A summary of Total Lengths and Total Weights of the the `r dim(fish)[1]` sampled organisms is presented in Table 1.
-The smallest organism (TL = `r formatC(min(fish$Length), digits = 2, format = "f")`) was also the lightest organism (TW = `r formatC(min(fish$Weight), digits = 2, format = "f")`).
-However, the largest organism (TL = `r formatC(max(fish$Length), digits = 2, format = "f")`) was not the heaviest (TW = `r formatC(fish$Weight[fish$Length == max(fish$Length)], digits = 2, format = "f")`), and the heaviest organism (TW = `r formatC(max(fish$Weight), digits = 2, format = "f")`) was `r formatC(fish$Length[fish$Weight == max(fish$Weight)], digits = 2, format = "f")` mm in total length.
+A summary of Total Lengths and Total Weights of the the sampled organisms (n = `r dim(fish)[1]`) is presented in Table 2.
+The smallest organism (TL = `r formatC(min(fish$Length), digits = 2, format = "f")` mm) was also the lightest organism (TW = `r formatC(min(fish$Weight), digits = 2, format = "f")` gr).
+However, the largest organism (TL = `r formatC(max(fish$Length), digits = 2, format = "f")` mm) was not the heaviest (TW = `r formatC(fish$Weight[fish$Length == max(fish$Length)], digits = 2, format = "f")` gr), and the heaviest organism (TW = `r formatC(max(fish$Weight), digits = 2, format = "f")` gr) was `r formatC(fish$Length[fish$Weight == max(fish$Weight)], digits = 2, format = "f")` mm in total length.
 Kernell density plots (Fig.
@@
 Both measures were positively skewed, with skewness of `r formatC(skewness(fish$Length), digits = 2, format = "f")` for TL and `r formatC(skewness(fish$Weight), digits = 2, format = "f")` for TW.
-
-## Length-weight relationship
 
@@
 
+## Length-weight relationship
+
 ```{r model fitting}
 model <- lm(log10(Weight) ~ log10(Length), data = fish)
-```
 
-```{r regression table, include = F}
 TidyModel <- model%>%
@@
 
+```
+
+```{r testing coefficients}
+test_intercept <- 2*pt(abs(coef(model)[[1]]/robust_se[[1]]), df = 107, lower.tail = F)
+
+test_slope <- 2*pt(abs(coef(model)[[2]]/robust_se[[2]]), df = 107, lower.tail = F)
+
+test_slope_3 <- 2*pt(abs((coef(model)[[2]]-3)/robust_se[[2]]), df = 107, lower.tail = F)
+```
+
+The model adjusted to eq.
+3 estimated the coefficient values at $m = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
+The intercept and slope were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
+Additionally, the allometric factor was significantly different from zero ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$).
+More information on model fit and confidence intervals for the estimated coefficients are presented in Table 3.
+The relationship between Total Length and Total Weight is presented in Figure 3.
+
+```{r regression table, include = F}
 regression_table <- stargazer(model,
@@
           ci = T)
-```
-
-```{r}
-test_intercept <- 2*pt(abs(coef(model)[[1]]/robust_se[[1]]), df = 107, lower.tail = F)
-
-test_slope <- 2*pt(abs(coef(model)[[2]]/robust_se[[2]]), df = 107, lower.tail = F)
-
-test_slope_3 <- 2*pt(abs((coef(model)[[2]]-3)/robust_se[[2]]), df = 107, lower.tail = F)
-
-```
-
-The model adjusted to eq.
-3 estimated the coefficient values at $m = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
-The intercept and slope were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
-Additionally, the allometric factor was significantly different from zero ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$).
-More information on model fit and confidence intervals of estimated coefficients is presented in Table 3.
-
-## Comparison of allometric parameters
-
-```{r, include = F}
-review <- read_csv("biometric_review.csv", col_types = cols())
-
-review_table <- review %>% 
-  select(Reference, n = N, a, c, b, r2, Gender, minD, maxD, Spear) %>% 
-  knitr::kable(digits = 4, row.names = F, caption = "Allometric growth parameters for eight published papers, Fishbase (Froese and Pauly 2016), and this study.
-All parameters have been adjusted to convert from millimiters to grams.
-n = Sample size, a = scaling parameter for eq.
-1, c = y-intercept for eq.
-3, b = exponent or slope for eq.
-1 or eq.
-2, respectively.")
-
-review_table
 ```
@@
 ```
+
+## Comparison of allometric parameters
+
+```{r, include = F}
+review <- read_csv("biometric_review.csv", col_types = cols())
+
+review_table <- review %>% 
+  select(Reference, n = N, a, c, b, r2, Gender, minD, maxD, Spear) %>% 
+  knitr::kable(row.names = F, caption = "Allometric growth parameters for eight published papers, Fishbase (Froese and Pauly 2016), and this study.
+All parameters have been adjusted to convert from millimiters to grams.
+n = Sample size, a = scaling parameter for eq.
+1, c = y-intercept for eq.
+3, b = exponent or slope for eq.
+1 or eq.
+2, respectively.", digits =  c(1, 0, 6, 4, 4, 4, 0, 1, 1))
+
+review_table
+```
+
+From the eight peer-reviewd studies including information on growth parameters for *P.
+volitans* and FishBase [@froese_website_2016], `r dim(review)[1]-1` parameters were identified.
+Two studies [@aguilarperera_2016; @fogg_2013] reported gender-level and pooled parameters, while the rest of the studies always presented pooled results.
+The smallest coefficient of determination was presented by @chin_2016 with $R^2 = `r min(review[,12], na.rm = T)`$, while @sabidoitza_2016 reported the highest value at $R^2 = `r min(review[,12], na.rm = T)`$.
+These studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` meters.
+Two studies [@aguilarperera_2016; @chin_2016] explicitly stated that their organisms were sampled with pole spears.
+Five studies [@sandel_2015; @barbour_2011; @fogg_2013; @edwards_2014; @sabidoitza_2016] mentioned that some of their organisms were obtained with pole spears (or other type of harpoon).
+A single study [@deleon_2013] did not specify how samples were obtained.
+
+Parameters from models fit to males or females exclusively tend to have a higher steapness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "M"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "M"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "F"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "F"]), digits = 2, format = "f")`$, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
+In the case of the ponderal index ($a$) and its $log_{10}$ transformed parameter ($c$), values were higher for parameters for pooled genders.
+The trends in $a$, $c$, and $b$ indicate that some models will tend to estimate Total Weights differently.
+Figure 4 shows the predicted weights for organisms within the size range of these study using the 14 parameters previously described.
 
@@
 
-plot_fit_all_studies_log <- ggplot(data = fish, mapping = aes(x = Length, y = log10(Weight))) +
-  geom_line(data = predicted_all, mapping = aes(x = Length, y = log10(Weight), linetype = Gender, color = Study), size = 1) +
-  theme_bw() +
-  labs(x = "Total length (mm)", y = "log10(TW)") +
-  theme(text = element_text(family = "Times"),
-        legend.position = "None")+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))
-
-gridExtra::grid.arrange(plot_fit_all_studies, plot_fit_all_studies_log)
-
+plot_fit_all_studies
 ```
 
-```{r Predicted biomass for each site}
+```{r}
 Predicted_biomass <- fish %>% 
-  mutate(This = review$a[14] * (Length^review$b[14]), 
-         APA = review$a[1] * (Length^review$b[1]),
-         APF = review$a[2] * (Length^review$b[2]),
-         APM = review$a[3] * (Length^review$b[3]),
-         Sandel = review$a[4] * (Length^review$b[4]),
-         Chin = review$a[5] * (Length^review$b[4]),
-         Barbour = review$a[6] * (Length^review$b[6]),
-         deLeon = review$a[7] * (Length^review$b[7]),
-         FoggA = review$a[8] * (Length^review$b[8]),
-         FoggM = review$a[9] * (Length^review$b[9]),
-         FoggF = review$a[10] * (Length^review$b[10]),
-         Edwards = review$a[11] * (Length^review$b[11]),
-         Sabido = review$a[12] * (Length^review$b[12]),
-         FishBase = review$a[13] * (Length^review$b[13])) %>% 
-  group_by(Location) %>% 
-  summarize(Observed = sum(Weight),
-            This = sum(This)/Observed,
-            APA = sum(APA)/Observed,
-            APF = sum(APF)/Observed,
-            APM = sum(APM)/Observed, 
-            Sandel = sum(Sandel)/Observed,
-            Chin = sum(Chin)/Observed,
-            Barbour = sum(Barbour)/Observed,
-            deLeon = sum(deLeon)/Observed,
-            FoggA = sum(FoggA)/Observed,
-            FoggM = sum(FoggM)/Observed,
-            FoggF = sum(FoggF)/Observed,
-            Edwards = sum(Edwards)/Observed,
-            Sabido = sum(Sabido)/Observed,
-            FishBase = sum(FishBase)/Observed) %>% 
-  ungroup() %>% 
-  gather(Study_id, Biomass, -Location) %>% 
+  select(Length, Weight) %>% 
+  mutate(This = review$a[14] * (Length^review$b[14])/Weight, 
+         APA = review$a[1] * (Length^review$b[1])/Weight,
+         APF = review$a[2] * (Length^review$b[2])/Weight,
+         APM = review$a[3] * (Length^review$b[3])/Weight,
+         Sandel = review$a[4] * (Length^review$b[4])/Weight,
+         Chin = review$a[5] * (Length^review$b[4])/Weight,
+         Barbour = review$a[6] * (Length^review$b[6])/Weight,
+         deLeon = review$a[7] * (Length^review$b[7])/Weight,
+         FoggA = review$a[8] * (Length^review$b[8])/Weight,
+         FoggM = review$a[9] * (Length^review$b[9])/Weight,
+         FoggF = review$a[10] * (Length^review$b[10])/Weight,
+         Edwards = review$a[11] * (Length^review$b[11])/Weight,
+         Sabido = review$a[12] * (Length^review$b[12])/Weight,
+         FishBase = review$a[13] * (Length^review$b[13])/Weight) %>% 
+  gather(Study_id, Biomass_ratio, -c(Length, Weight)) %>% 
   left_join(review, by ="Study_id")
@@
 
+From all allometric parameters reviewed, those of @edwards_2014 slightly underestimated the observed biomass, with median (`r filter(Predicted_biomass, Study_id == "Edwards") %$% median(Biomass_ratio) %>% formatC(digits = 2, format = "f")`) and mean (`r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")`) bellow one.
+There is no significance in comparing the parameters estimated in this study since, by definition, they are the pair of parameters for which residual sum of squares was minimized with values of median =`r filter(Predicted_biomass, Study_id == "This") %$% median(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and mean (`r filter(Predicted_biomass, Study_id == "This") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")`).
+For all the other studies, the 95% confidence interval fell further away from a value of 1, indicating overestimation.
+Predicted to observed biomass ratios are presented in Figure 5.
+
 ```{r plot comparing predictions, include = F}
 Predicted_biomass_plot <-   Predicted_biomass %>% 
-  filter(!Study == "Observed") %>% 
-  transform(Study_id = reorder(Study_id, -Biomass)) %>% 
-  ggplot(aes(x = Study_id, y = Biomass)) +
-  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0, size = 1) +
-  stat_summary(geom = "point", fun.y = "mean", fill = "blue", size = 3, shape = 21) +
+  transform(Study_id = reorder(Study_id, -Biomass_ratio)) %>%
+  ggplot(aes(x = Study_id, y = Biomass_ratio)) +
+  geom_boxplot(aes(fill = Gender), outlier.size = 1, notch = T) +
+  stat_summary(geom = "point", fun.y = "mean", size = 3) +
   geom_hline(yintercept = 1, linetype = "dashed") +
@@
   theme_bw() +
-  theme(text = element_text(family = "Times"))
+  theme(text = element_text(family = "Times")) +
+  scale_fill_brewer(palette = "Greys") +
+  theme(text = element_text(family = "Times"),
+        legend.justification=c(1,1),
+        legend.position=c(0.99, 0.99),
+        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted"))
 
@@
 
-Not using spear poles allows us to have a full sample of fish with a wider range of sizes and weights, ideal for visual census. Also, there is no loss in body mass due to bleeding.
+Wider range sizes
+
+Model fit and this model
+
+No spear doesnt seem to be a determinant factor in weight, but spear doesnt allow catching small organisms.
+Not using spear poles allows us to have a full sample of fish with a wider range of sizes and weights, ideal for visual census.
+Also, there is no loss in body mass due to bleeding.
+
+Gender-level overestimates and is steaper because it lacks small organisms to pull the curve
 
@@
 
-```{r, fig.cap = "Weight-at-length relationship for 109 lionfish sampled off the coast of Puerto Aventuras, Mexico."}
+```{r, fig.cap = "Weight-at-length relationship for 109 lionfish sampled off the coast of Puerto Aventuras, Mexico. Points indicate samples, solid line indicates curve of best fit."}
 plot_fit_this_study
@@
 
-```{r, fig.cap = "Mean predicted to observed biomass ratios for eight studies, this study, and FishBase parameters. Error bars indicate +/- 1 Standard Error."}
+```{r, fig.cap = ".
+Box and whiskers plot showing the distribution of predicted to observed Total Weight ratios for 14 pairs of allometric parameters.
+Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers."}
 Predicted_biomass_plot

### 2017-07-29 Manuscript.Rmd
Added study area section and some discussion

@@
 title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in
-  Playa del Carmen, Mexico and a review of length - weight parameters across the invasion
+  Playa del Carmen, Mexico and a review of allometric growth parameters across the invasion
   range}
-csl: apa.csl
 fontsize: 12pt
@@
 At least 84% of the marine eco-regions have reported the presence of an invasive species [@molnar_2008].
-The presence of invasive alien species represents a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries [@bax_2003].
+These represents a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries [@bax_2003].
+Invasive species may also threaten native species through competition [@davis_2003] or predation.
 By 2005, the economic cost of invasive species to the United States was  estimated at \$120 billion per year and nearly 42% of species that have been included in the Endangered or Threatened species list have been labeled as such due to presence of invasive species [@pimentel_2005].
-Invasive species may threaten native species through competition [@davis_2003] or predation.
 This highlightes the importance of understanding, managing, and preventing ecological invasions.
 
-Lionfish (*Pterois volitans - miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean likely introduced through libreation of aquarium-kept organisms [@betancurr_2011].
-They are the first marine vertebrates to establish in North Atlantic [@schofield_2009: @schofield_2010] and Caribbean coasts.
-Lionfish have been recorded in coral reefs [@aguilarperera_2010], but also in other habitats like estuaries [@jud_2011], mangroves [@barbour_2010] and hard-bottom reefs [@muoz_2011].
-Their presence in these waters has been labeled as a major marine invasion due to its threat to local biodiversity, the veolocity of its invasion, and its difficulty of management [@hixon_2016].
+Lionfish (*Pterois volitans - miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through libreation of aquarium-kept organisms [@betancurr_2011].
+They are the first marine vertebrates to establish in North Atlantic [@schofield_2009; @schofield_2010] and Caribbean coasts [@sabidoitza_2016].
+Lionfish have been widely reported in coral reefs [@aguilarperera_2010], but also in other habitats such as estuaries [@jud_2011], mangroves [@barbour_2010], areas with hard-bottoms [@muoz_2011], and mesophotic reefs [@andradibrown_2017].
+Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion  [@hixon_2016].
 
-As ways to reduce the abundance of this invasive species local authorities have promoted removal programs incentivized consumption of this invasive species [@chin_2016].
+A significant amount of research has been done to describe lionfish feeding ecology in North Carolina [@muoz_2011], the Bahamas [@morris_2009; @cote_2013], Northern Gulf of Mexico [@dahl_2014], Mexican Caribbean [@valdezmoreno_2012; @villaseorderbez_2014], and Costa Rica [@sandel_2015].
+Their feeding behaviour and high consumption rates can reduce recruitment [@albins_2008] and population sizes [@green_2012] of native reef-fish species, and further the endangerement of critically endangered reef fish [@rocha_2015].
+Major efforts have also been made to understand the possible impacts of the invasion by keeping track of its range through time [@schofield_2009; @schofield_2010] and predicting invasion ranges under climate change scenarios (@grieve_2016).
+By combining these information, researchers have been ableto predict the trophic impacts of lionfish [@ariasgonzalez_2011], which can then be translated into ecosystem-level impacts.
+
+Seeking to reduce the abundance of this invasive species, local authorities have promoted removal programs ands incentivized its consumption [@chin_2016].
 Lionfish removals have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales [@sandel_2015, @chin_2016, @deleon_2013].
-While complete erradication through fishing effort is unlikely to be a solution due to the rapid recovery rates exhibited by the species [@barbour_2011], further incentivizing its consumption might create a market demand big enough to promote a fishery [@chin_2016].
+The rapid recovery rates exhibited by lionfish make of complete erradication through fishing effort an unlikely solution [@barbour_2011].
+However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery [@chin_2016], which can reduce local abundances and control -not erradicate- the invasion.
 
-A significant amount of research has been done on lionfish feeding ecology in North Carolina [@muoz_2011], the Bahamas [@morris_2009; @cote_2013], Northern Gulf of Mexico [@dahl_2014], Mexican Caribbean [@valdezmoreno_2012; @villaseorderbez_2014], and Costa Rica [@sandel_2015].
-It has been identified that lionfish can reduce recruitment [@albins_2008] and population sizes [@green_2012] of native reef-fish species, and further the endangerement of critically endangered reef fish [@rocha_2015].
-This information has been useful in predicting the trophic impacts of lionfish [@ariasgonzalez_2011].
-Significant efforts have also been made to understand the possible impacts of the invasion by keeping track of the invasion range through time [@schofield_2009; @schofield_2010] and predicting invasion ranges under climate change scenarios (@grieve_2016).
+Research focused on erradication and management effectivenes must be based on sound biological information, highlighting the importance of both fields.
+Management effectiveness often identified the gains associated to the invested effort, like biomass extracted per dollar.
+Among fish, biomass is often used as a standard measure of the state or size of a population.
+By deffinition, biomass is the sum of the weight of all organisms.
+In some cases, a fish's weight is directly measured, in others,  weight can be calculated from length data.
+In order to do this, researchers must find allometric parameters that describe the weight-at-length for their species of interest at a particular region.
+Having precision of these parameters is important, because small changes in any of them can result in over- or underestimation of an organisms weight, and therefore total biomass.
+This becomes particularly important when research involves, for example, identifying the total biomass available for harvest by fishers [@chin_2016] or the efficacy of lionfish removals [@barbour_2011].
 
-Biomass is a standard indicator used to measure the state or size of a population.
-Biomass has been used in lionfish research to convert individual fish length observations into fish weight.
-In order to do this, researchers must find growth parameters thad describe the growth of their species for a particular region or location.
-Having precision of these parameters is important, because small changes in any of them can result in important over- or underestimation of biomass levels.
-This becomes particularly important when research involves, for example, identifying the total biomass available for harvest by fishers -as invasion management programs- or the efficacy of lionfish removals.
-
-The objectives of this study include providing site-specific weight-at-length parameters for the invasive lionfish in the Mexican Caribbean region.
-At the same time, we highlight the importance of using site-specific parameters by estimating biomass with parameters from other regions across the invasion range and comparing them to observed biomasses.
-Finally, we summarize other weight-at-length studies presented, making them readily accessible for future research.
+Here, I provide site-specific allometric growth parameters for the invasive lionfish in the central Mexican Caribbean region, where no studies have been published.
+At the same time, I highlight the importance of using site-specific parameters by estimating biomass with parameters from other regions across the invasion range and comparing them to observed biomass.
+Finally, I provide a review of other weight-at-length studies -making them readily accessible for future research- and provide a set of guidelines to standardize the way in which allometric parameters should be reported to facilitate their use.
 
@@
 
-The present study took place off the coasts of Playa del Carmen, in the coasts of the Mexican Caribbean.
-The region represents the northernmost section of the Mesoamerican reef, which extends from coast of Cancun south to Honduras (**reference**).
-Coral reefs and mangroves are important habitats distributed along the cost, and represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism (**reference**), the main source of income to the local economy.
+The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean (**Fig.
+1**).
+The region represents the northernmost section of the Mesoamerican Barrier Reef System [@ruiz-zarate_2003].
+Coral reefs and mangroves are localy important habitats that represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism, the main source of income to the local economy [@murray_2007].
 
-Coral reefs in the region are characterized by X, Y, Z. Descripcion general de los arrecifes.
+In the region, reef profile has been described by @ariasgonzales_1998, where the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
+The reef becomes deeper, leading to the reef front often found at 700 m from the coastline end extends for an additional 300 m.
+At approximately 1000 m away from shore and 30 - 40 m depth, the reef leads to a drop-off.
+Along a perpendicular profile to the coast, bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18 m deep.
+Along the coast, these reefs have been reported to be under significant antrhopogenic pressure, likely causing a shift in structure and function [@Bozec_2008].
 
@@
   tm_symbols(shape = 5, size = 2, border.col = "black", col = "black", border.lwd = 2) +
-  tm_grid() +
   tm_scale_bar()
@@
 
-The present study used samples obtained by @villaseorderbez_2014 for stomach content analysis between May and August of 2010.
+Organisms sampled by @villaseorderbez_2014 for stomach content analysis between May and August of 2010 were used in this work.
 A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along 14 Km of coast between Puerto Aventuras and Akumal (Fig.
@@
 
-All hypothesis testing was performed with a confidence level of $\alpha = 0.01$ and performed in R version 3.4.0 [@rcore_2017].
+All hypothesis testing was performed with a confidence level of $\alpha = 0.01$ in R version 3.4.0 [@rcore_2017].
 Data wrangling was performed with the tidyverse package [@tidyverse_2017].
 Maps were created with a mix of functions from the sp [@sp_2017], rgdal [@rgdal_2017], tmap [@tmap_2017], and tmaptools [@tmaptools_2017] packages.
-Correction for heteroskedastic-robust standard errors was done with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
+Callculation of heteroskedastic-robust standard errors was done with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
 Models were manipulated with with the broom package [@broom_2017].
@@
 The manuscript was written in rmarkdown [@rmarkdown_2017] and processed with the knitr package [@knitr_2017].
+Raw data and code used in this work is available at [github.com/jcvdav/lionfish_biometry](github.com/jcvdav/lionfish_biometry).
 
@@
 
+Here, I provide site-specific allometric growth parameters for the invasive lionfish in the central Mexican Caribbean region, where no studies have been published.
+
+Other studies have provided allometric growth parameters of lionfish in Mexican waters, specifically for the Alacranes Reef, in the Gulf of Mexico [@aguilarperera_2018], and further south in the Caribbean for the Xcalak National Park [@sabidoitza_2016], but no information for the central region of the Mexican Caribbean coast had been provided.
+Furthermore by using hand nets instead of spears, we are able to sample a wider range of sizes, extending the lower length classes to smaller organisms often not sampled with spears.
+Thus, this study is the first to provide allometric growth parameters for lionfish in the central region of the Mexican Caribbean and includes a wider range of total lengths, allowing us to calculate -with certainty- a wider range of weights.
+
+The parameters estimated in this study were within the range of studies in other regions, however using other parameters resulted in important differences in expected biomass.
+These differences can have major implications in management, especially when estimating biomass availabe for harvest or predicting population size and effects on local ecosystems.
+Using site-specific values provides a more aqurate estimate of fish biomass.
+Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results.
+At the same time, this higlights the need for mor basic research that can describe allometric growth parameters -and other biologically important information- of lionfish throughout its invasion range.
+
+While performing the lietrature review, it was often unclear if parameters presented for **eq.1** or **eq.
+3**.
+Sometimes, they were even misslabeled and yielded senseless results when using the suggested conversion equation.
+On some others, parameters were said to be reported for mm to gr conversions, when they were actually reported as cm to gr conversions.
+Perhaps these minor discrepancies can be easily solved by any researcher, but why should they exist in the first place?
+It is important that we report our information in a standard way, making it readily available for other researchers but also managers.
+In this particular case, I provide my humble opinion in X simple guidelines to report allometric parameters:
+
+1.
+
+2.
+Be explicit in the methods section.
+What may seem obvious to you as an author -because you have been deeply immersed throughout the process- may not be clear to the reader.
+Specify any transformation performed on the data; When using log-transformations, mention the base used to transform.
+Do not asume that "data were log-transformed" means $log_{10}(X)$.
+These assumptions vary across disciplines and softwares.
+For example, in biology we often assume log-transformed indicates the use of base 10, however in R the command is log10() and not log(), which uses base $e$.
+
+3. Use heteroskedastic-robust standard errors.
+
+4.
+At the least, specify the equation for which parameters are presented and try include an explicit example with the parameters substituted into it, as done by [X Y y Z].
+If possible, present the parameters in their exponential and linear form.
+
+5.
+Report standard errors and confidence intervals arround the obtained estimates.
+Given that small changes in $a$, $c$,  and $b$ can result in important changes in estimated weight, it is important that we report uncertainty arround each parameter and not just general model fit (*i.e.* R^2^).
+Additionally, make every possible effort to report at least 4 decimal points.
+If the journal has style guidelines about this, include full estimates in a table as supplementary material.
+
+6.
+Make your data -and code- available.
+Even if this is not requited by the journal or publisher, you can use free cloud data storage services to make your research accessible to others.
+In times and countries where resources are limited, it is important that we take advantage of all open science tools that promote the advancement of knowledge.
+Ultimately, this fosters transparency, allows replicability of research, and can lead to collaborations.
+
+While in this work I make reference to allometric growth parameters, these guidelines can easily be applied to other areas and disciplines. It is important
+
 Wider range sizes
@@
 Gender-level overestimates and is steaper because it lacks small organisms to pull the curve
+
+Finally, I provide a review of other weight-at-length studies -making them readily accessible for future research- and provide a set of guidelines to standardize the way in which allometric parameters should be reported to facilitate their use.
 

### 2017-08-04 Manuscript.Rmd
Updated manuscript for submission

--- 2017-07-14 Manuscript.Rmd
@@
 ---
-title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in
-  Playa del Carmen, Mexico and a review of length - weight parameters across the invasion
-  range}
-csl: apa.csl
+title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}
 fontsize: 12pt
@@
     fig_caption: yes
+    keep_tex: yes
 header-includes:
@@
 - packages.bib
+csl: huct.csl
 ---
-
 <script type="text/x-mathjax-config">
@@
 knitr::opts_chunk$set(echo = F)
+
+options(knitr.table.format = "latex")
 
@@
 
-Juan Carlos Villaseñor-Derbez^1^\
+Juan Carlos Villaseñor-Derbez^1^
 
-^1^ Bren School of Environmental Sciences and Management, University of California Santa Barbara\
+^1^ Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S.
 
-**Full postal address:**
-4312 Bren Hall, Santa Barbara, CA, 93106\
+**Full postal address**   
+Bren Hall   
+University of California at Santa Barbara   
+Santa Barbara   
+CA, 93106
 
-**Running title:** Length - weight parameters for *Pterois volitans* \
+**Corresponding author information:**   
+Juan Carlos Villaseñor-Derbez   
+Bren Hall   
+University of California at Santa Barbara   
+Santa Barbara   
+CA, 93106
+jvillasenor@bren.ucsb.edu
++1 207 205 8435
 
-*Corresponding author information:*
-
-Juan Carlos Villaseñor-Derbez   
-4312 Bren Hall  
-Santa Barbara, CA   
-93106   
-jvillasenor@bren.ucsb.edu   
-+1 (207) 205 8435
+**Running title**    
+Allometric growth of Pterois volitans
 
@@
 
-**Title of the contribution:** Biometry of the invasive lionfish (*Pterois volitans*) in Playa del Carmen, Mexico and a review of length - weight parameters across the invasion range\
+**Title of contribution**: Biometry of the invasive lionfish (*Pterois volitans*) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range
 
 **Abstract**    
-
-300 words\
+Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms.
+Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion.
+In order to better manage the invasion, inform lionfish removal programs, predict their possible impacts, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass.
+This study reports allometric growth parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the central portion of the Mexican Caribbean.
+It also identifies that, for a given length, organisms from the Caribbean tend to have lower weights than those from the Gulf of Mexicoand Atlantic, indicating that weight-at-length is spacialy variable.
+In addition to the new pair of parameters provided in this study, other 13 pairs of allometric growth parameters were used to calculate expected biomass from total length observations.
+Mean expected-to-observed biomass ratios by study ranged between 0.98 and 1.75, with overall values ranging from 0.44 to 3.51.
+The large differences between observed and expected biomass when using parameters from other locations highlights the importance of using site-specific parameters to estimate biomass from length observations.
+This becomes increasingly important when estimating biomass available for harvest or effectiveness of lionfish removal efforts.
+Additionally, guidelines on reporting allometric parameters are provided as a suggestion for future research are provided.
 
 **Key words**   
-
-lionfish, biometry, length-weight relationship, Mexico\
+lionfish, Pterois volitans, length-weight relationship, allometric growth, Mexico
 
 **Resumen**   
-
-300 palabras\
+Los peces león (*Pterois volitans/miles*) son una especiei nvasora en el Atlántico Noroeste y el Caribe, probablemente introducidos por medio de la liberación de organismos de ornato.
+Dada la amenaza que estos representan para la biodiversidad local, la velocidad de su invasión y dificultad de manejo, su presencia ha sido catalogada como una importante invasión marina.
+Para manejar mejor la invasión, proveer información a los programas de remoción, predecir los posibles impactos y estimar biomasa disponible para la extracción, debemos ser capaces de estimar su biomasa con precisión.
+Este estudio presenta parámetros de crecimiento alométrico ($a = 3.2056\times 10^{-6}; b = 3.235$) para organismos muestreados en la porción central del Caribe Mexicano.
+También identifica que para una misma longitud, los organismos del Caribe tienden a ser menos pesados que aquellos del Golfo de México y Atlántico, indicando variaciones espaciales en la relación peso-longitud.
+Además de los parámetros descritos en este estudio, se utilizaron otros 13 pares de parámetros de crecimiento alométrico para estimar biomasa a partir de observaciones de talla.
+La razón entre biomasa observada y biomasa esperada varió, en promedio por estudio, entre 0.98 y 1.75, con valores extremos de 0.44 y 3.51.
+Las grandes diferencias entre biomasa observada y esperada al usar parámetros de otras regiones resalta la importancia de utilizar parámetros específicos a la zona para estimar biomasa a partir de observaciones de talla.
+Adicionalmente, se proveen sugerencias para estandarizar la manera en que los parámetros de crecimiento alométrico se reportan.
 
 **Palabras clave**
-
-pez león, biometría, relación lopngitud-peso, México\
+pez león, Pterois volitans, relación longitud-peso, crecimiento alométrico, México
 
@@
 At least 84% of the marine eco-regions have reported the presence of an invasive species [@molnar_2008].
-The presence of invasive alien species represents a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries [@bax_2003].
+These represent a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries [@bax_2003].
+Invasive species may also threaten native species through competition [@davis_2003] or predation.
 By 2005, the economic cost of invasive species to the United States was  estimated at \$120 billion per year and nearly 42% of species that have been included in the Endangered or Threatened species list have been labeled as such due to presence of invasive species [@pimentel_2005].
-Invasive species may threaten native species through competition [@davis_2003] or predation.
-This highlightes the importance of understanding, managing, and preventing ecological invasions.
+This highlights the importance of understanding, managing, and preventing ecological invasions.
 
-Lionfish (*Pterois volitans - miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean likely introduced through libreation of aquarium-kept organisms [@betancurr_2011].
-They are the first marine vertebrates to establish in North Atlantic [@schofield_2009: @schofield_2010] and Caribbean coasts.
-Lionfish have been recorded in coral reefs [@aguilarperera_2010], but also in other habitats like estuaries [@jud_2011], mangroves [@barbour_2010] and hard-bottom reefs [@muoz_2011].
-Their presence in these waters has been labeled as a major marine invasion due to its threat to local biodiversity, the veolocity of its invasion, and its difficulty of management [@hixon_2016].
+Lionfish (*Pterois volitans/miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms [@betancurr_2011].
+They are the first marine vertebrates to establish in North Atlantic [@schofield_2009; @schofield_2010] and Caribbean coasts [@sabidoitza_2016].
+Lionfish have been widely reported in coral reefs [@aguilarperera_2010], but also in other habitats such as estuaries [@jud_2011], mangroves [@barbour_2010], areas with hard-bottoms [@muoz_2011], and mesophotic reefs [@andradibrown_2017].
+Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion  [@hixon_2016].
 
-As ways to reduce the abundance of this invasive species local authorities have promoted removal programs incentivized consumption of this invasive species [@chin_2016].
-Lionfish removals have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales [@sandel_2015, @chin_2016, @deleon_2013].
-While complete erradication through fishing effort is unlikely to be a solution due to the rapid recovery rates exhibited by the species [@barbour_2011], further incentivizing its consumption might create a market demand big enough to promote a fishery [@chin_2016].
+A significant amount of research has been done to describe lionfish feeding ecology in North Carolina [@muoz_2011], the Bahamas [@morris_2009; @cote_2013], Northern Gulf of Mexico [@dahl_2014], Mexican Caribbean [@valdezmoreno_2012; @villaseorderbez_2014], Belize [@hackerott_2017], and Costa Rica [@sandel_2015].
+Their feeding behavior and high consumption rates can reduce recruitment [@albins_2008] and population sizes [@green_2012] of native reef-fish species, and further the endangerment of critically endangered reef fish [@rocha_2015].
+(However, see @hackerott_2017 for a case where there was no evidence that lionfish affected the density, richness, or composition of prey fishes).
+Major efforts have also been made to understand the possible impacts of the invasion by keeping track of its range through time [@schofield_2009; @schofield_2010] and predicting invasion ranges under climate change scenarios [@grieve_2016].
+By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish [@ariasgonzalez_2011], which can then be translated into ecosystem-level and economic impacts.
 
-A significant amount of research has been done on lionfish feeding ecology in North Carolina [@muoz_2011], the Bahamas [@morris_2009; @cote_2013], Northern Gulf of Mexico [@dahl_2014], Mexican Caribbean [@valdezmoreno_2012; @villaseorderbez_2014], and Costa Rica [@sandel_2015].
-It has been identified that lionfish can reduce recruitment [@albins_2008] and population sizes [@green_2012] of native reef-fish species, and further the endangerement of critically endangered reef fish [@rocha_2015].
-This information has been useful in predicting the trophic impacts of lionfish [@ariasgonzalez_2011].
-Significant efforts have also been made to understand the possible impacts of the invasion by keeping track of the invasion range through time [@schofield_2009; @schofield_2010] and predicting invasion ranges under climate change scenarios (@grieve_2016).
+Seeking to reduce lionfish densities, governments and non-profit organizations have promoted removal programs and incentivized its consumption [@chin_2016].
+In some cases, these have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales [@sandel_2015, @chin_2016, @deleon_2013].
+The rapid recovery rates exhibited by lionfish [@barbour_2011] and the persistent populations in mesophotic coral ecosystems [@andradibrown_2017] -which can contribute with recruitment to shallow-water populations- make of complete eradication through fishing effort an unlikely solution.
+However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery [@chin_2016], which can reduce local abundances and control -not eradicate- the invasion while providing alternative livelihoods.
 
-Biomass is a standard indicator used to measure the state or size of a population.
-Biomass has been used in lionfish research to convert individual fish length observations into fish weight.
-In order to do this, researchers must find growth parameters thad describe the growth of their species for a particular region or location.
-Having precision of these parameters is important, because small changes in any of them can result in important over- or underestimation of biomass levels.
-This becomes particularly important when research involves, for example, identifying the total biomass available for harvest by fishers -as invasion management programs- or the efficacy of lionfish removals.
+The feasibility of lionfish removal programs has been extensively evaluated through field observations[@usseglio_2017; @sandel_2015, @chin_2016, @deleon_2013] and empirical modeling [@barbour_2011; @morris_2011; @johnston_2015].
+The latter measure changes in biomass or density [@barbour_2011; @johnston_2015] in response to increased mortality (*i.e.* lionfish removal).
+In this case, biomass represents the sum of all fish's individual weight.
+Total Weight (TW) can be estimated from Total Length (TL) observations using the allometric growth equation ($TW = aTL^b$).
+Parameters $a$ and $b$ for this equation exist for North Carolina [@barbour_2011], Northern [@fogg_2013] and Southern Gulf of Mexico [@aguilarperera_2016], the Southern Mexican Caribbean [@sabidoitza_2016], Little Cayman [@edwards_2014], Jamaica [@chin_2016], Bonaire [@deleon_2013] and Costa Rica [@sandel_2015], but remain unavailable for the central Mexican Caribbean.
+The weight-at-length of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions [@johnson_2016].
+Thus, when using biomass-informed models or estimating biomass from length observations, it is important to use site-specific parameters to obtain an accurate estimate.
+This is especially important when research involves identifying the total biomass available for harvest by fishers [@chin_2016] or the efficacy of lionfish removals [@barbour_2011; @morris_2011; @johnston_2015].
 
-The objectives of this study include providing site-specific weight-at-length parameters for the invasive lionfish in the Mexican Caribbean region.
-At the same time, we highlight the importance of using site-specific parameters by estimating biomass with parameters from other regions across the invasion range and comparing them to observed biomasses.
-Finally, we summarize other weight-at-length studies presented, making them readily accessible for future research.
+Here, I provide the first allometric growth parameters for the invasive lionfish in the central Mexican Caribbean region.
+At the same time, I highlight the importance of using site-specific parameters by estimating biomass with parameters from other regions across the invasion range and comparing them to observed biomass.
+I also provide other 13 standardized parameters from eight studies through the invasion range, making them readily accessible for future research.
+Finally, I discuss the way in which allometric parameters are reported, and call for standardization to facilitate their use.
 
@@
 
-The present study took place off the coasts of Playa del Carmen, in the coasts of the Mexican Caribbean.
-The region represents the northernmost section of the Mesoamerican reef, which extends from coast of Cancun south to Honduras (**reference**).
-Coral reefs and mangroves are important habitats distributed along the cost, and represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism (**reference**), the main source of income to the local economy.
+The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean (**Fig.
+1**).
+The region represents the northernmost section of the Mesoamerican Barrier Reef System [@ruizzarate_2004].
+Coral reefs and mangroves are locally important habitats that represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism, the main source of income to the local economy [@murray_2007].
 
-Coral reefs in the region are characterized by X, Y, Z. Descripcion general de los arrecifes.
+In the region, the reef profile has been described by @ariasgonzalez_1998, indicating that the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
+The reef becomes deeper, leading to the reef front often found at 700 m from the coastline end extends for an additional 300 m.
+At approximately 1000 m away from shore and 30 - 40 m depth, the reef leads to a drop-off.
+Along a perpendicular profile to the coast, bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18 m deep.
+Along the coast, these reefs have been reported to be under significant anthropogenic pressure, likely causing a shift in structure and function [@bozec_2008].
 
@@
 
-The present study used samples obtained by @villaseorderbez_2014 for stomach content analysis between May and August of 2010.
-A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along 14 Km of coast between Puerto Aventuras and Akumal (Fig.
+Organisms sampled by @villaseorderbez_2014 for stomach content analysis between May and August of 2010 were used in this work.
+A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along the coast (Fig.
 1, Table 1).
 Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
-All observed organisms (n = `r dim(fish)[1]`) were collected using hand nets -to avoid weight loss due to bleeding- and numbered collection bottles.
+All observed organisms (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
+The use of hand nets prevents any weight loss due to bleeding(when collected with spears), and increases the range of sizes that can be sampled, providing a representative sample of the population.
 Information on depth and other comments were recorded in an underwater slide.
@@
 Samples were frozen within 30 minutes of completing the dive and stored for posterior analysis in the lab.
-For every organism, Total Length (TL; mm) and Total Weight (TW; gr) were recorded in the lab.
+For every organism Total Length (TL; mm) and Total Weight (TW; gr) were recorded in the lab.
 
@@
   rbind(total) %>% 
-  knitr::kable(row.names = F, caption = "Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.
-n = sample size.", col.names = c("Location", "Lat.", "Long.", "Min.
-Depth", "Max.
-Depth", "Mean Depth", "n"))
+  knitr::kable(row.names = F,
+               col.names = c("Location", "Lat.", "Long.", "Min. Depth", "Max. Depth", "Mean Depth", "n"),
+               booktabs = T)
 
@@
 
-The weight at length relationship between the observed variables was calculated with the allometric growth function:
+The weight at length relationship between the observed variables is described by the allometric growth function:
 
@@
 
-\begin{equation}log_{10}(TW) = blog_{10}TL + log{10}(a)\end{equation}
+\begin{equation}log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\end{equation}
 
@@
 Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$.
+Since $b == m$, we will only use $b$ throughout the paper for simplicity.
 The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard errors.
-Both coefficients were tested agains the null hypothesis of no change (*i.e.* $h_0: c = 0$ and $h_0: b = 0$).
+Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$).
 Additionally, the allometric parameter was tested against the null hypothesis of isometric growth ($H_0: b = 3$).
-Coefficient testing was made with a two-tailed Student's t-test.
+Coefficients were tested with a two-tailed Student's t-test.
 The significance of the regression was corroborated with an F-test.
 
-Other growth parameters were extracted from published research from North Carolina [@barbour_2011], Northern [@fogg_2013] and Southern [@aguilarperera_2016] Gulf of Mexico, the Southern Mexican Caribbean [@sabidoitza_2016], Little Cayman [@edwards_2014], Jamaica [@chin_2016], Bonaire [@deleon_2013] and Costa Rica [@sandel_2015].
+Other allometric growth parameters were obtained from peer-reviewed literature.
+Parameters were obtained forNorth Carolina [@barbour_2011], Northern [@fogg_2013] and Southern Gulf of Mexico [@aguilarperera_2016], the Southern Mexican Caribbean [@sabidoitza_2016], Little Cayman [@edwards_2014], Jamaica [@chin_2016], Bonaire [@deleon_2013] and Costa Rica [@sandel_2015].
 Additionally, parameters from Fishbase [@froese_website_2016] were also included in this study.
-When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retreived.
+When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retrieved.
 Whenever gender was not specified, it was assumed that the results were presented for both genders pooled together.
-During this review process, it was noticed that some papers indistinctly use $a$ to report either the ponderal index in **eq.
-1** or the y-intercept ($c$) in **eq.
-2**, which might sometimes be overlooked.
+During the review process, it was noticed that some papers indistinctly use $a$ to report either the ponderal index in eq.
+1 or the y-intercept ($c$) in eq.
+3, which might sometimes be overlooked.
 Furthermore, some studies report their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicates that they were estimated as cm-to-gr conversions.
-Here, both parameters ($a$ and $c$) are reported for the present findings and, when ever required, values from other studies are converted for consistency.
-All coefficients are reported as mm to gr conversions.
+Here, all parameters are reported as TL(mm) to TW(gr) conversions.
+When required, values from other studies are transformed for consistency.
 
-Mean observed biomass was calculated as the average Total Weight of all observed organisms.
-Expected biomass for each organism was calculated with the growth parameteres estimated in this study, as well as those retreived from additional literature.
-Then, mean expected biomass was calculated for each study.
-All expected biomass values were divided by the observed biomass to obtain a ratio that allowed rapid identification of over- or underestimation with respect to the observed biomass in this study.
-Therefore, values lower than 1 indicate that the parameters used underestimate the biomass.
-On the other side, values larger than 1 indicate that the parameteres used overestimate biomass.
-Median and mean expected to observed biomass ratios were calculated across all sites for each study.
+Since standard errors or confidence intervals were not provided for many studies, it was impossible to test for statistical differences across studies.
+Thus expected biomass for each organism was calculated with the growth parameters estimated in this study, as well as those retrieved from additional literature.
+All expected biomass values were divided by the observed biomass to obtain a ratio that allowed rapid identification of over- or underestimation with respect to the observed biomass.
+Therefore, values lower than 1 indicate that the parameters underestimate biomass, and values larger than 1 indicate overestimation.
+Median and mean expected to observed biomass ratios were calculated for each study.
 
-All hypothesis testing was performed with a confidence level of $\alpha = 0.01$ and performed in R version 3.4.0 [@rcore_2017].
+All hypothesis testing was performed with a confidence level of $\alpha = 0.01$ in R version 3.4.0 [@rcore_2017].
 Data wrangling was performed with the tidyverse package [@tidyverse_2017].
 Maps were created with a mix of functions from the sp [@sp_2017], rgdal [@rgdal_2017], tmap [@tmap_2017], and tmaptools [@tmaptools_2017] packages.
-Correction for heteroskedastic-robust standard errors was done with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
+Calculation of heteroskedastic-robust standard errors was done with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
 Models were manipulated with with the broom package [@broom_2017].
-Stargazer [@stargazer_2015] was used to produce the tables, and refmanager [@RefManager_2014] was used to keep track of citations.
-The manuscript was written in rmarkdown [@rmarkdown_2017] and processed with the knitr package [@knitr_2017].
+Stargazer [@stargazer_2015], knitr [@knitr_2017], and kableExtra [@kableExtra_2017] were used to produce the tables, and RefManageR [@RefManager_2014] was used to keep track of citations.
+The manuscript was written in r markdown [@rmarkdown_2017] and processed with the knitr package [@knitr_2017].
+Raw data and code used in this work is available at [github.com/jcvdav/lionfish_biometry](github.com/jcvdav/lionfish_biometry).
 
@@
 
-A summary of Total Lengths and Total Weights of the the sampled organisms (n = `r dim(fish)[1]`) is presented in Table 2.
+Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7 gr.
 The smallest organism (TL = `r formatC(min(fish$Length), digits = 2, format = "f")` mm) was also the lightest organism (TW = `r formatC(min(fish$Weight), digits = 2, format = "f")` gr).
@@
 Both measures were positively skewed, with skewness of `r formatC(skewness(fish$Length), digits = 2, format = "f")` for TL and `r formatC(skewness(fish$Weight), digits = 2, format = "f")` for TW.
-
-```{r summary table, include = F}
-summary_table <- fish %>% 
-  select(Length, Weight) %>% 
-  as.data.frame() %>% 
-  stargazer(header = F, type = "latex", digits = 2, title = "Summary statistics of Length and Weight of sampled organisms.")
-```
 
@@
 wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))
+
 f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))
@@
 The model adjusted to eq.
-3 estimated the coefficient values at $m = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
-The intercept and slope were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
-Additionally, the allometric factor was significantly different from zero ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$).
-More information on model fit and confidence intervals for the estimated coefficients are presented in Table 3.
+3 estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
+Thus, TW (gr) can be calculated from TL (mm) as a linear equation: $log_{10}(TW) = `r coef(model)[[2]]`\times log_{10}(TL) `r coef(model)[[1]]`$ or its exponential form: $TW = `r 10^coef(model)[[1]]`\times TL^{`r coef(model)[[2]]`}$.
+The intercept ($c$) and slope $(b)$ were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
+Additionally, the allometric factor ($m = b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$), indicating that lionfish present allometric growth.
+More information on model fit and confidence intervals for the estimated coefficients is presented in Table 2.
 The relationship between Total Length and Total Weight is presented in Figure 3.
-
-```{r regression table, include = F}
-regression_table <- stargazer(model,
-          header = F,
-          se = list(robust_se),
-          type = "latex",
-          t.auto = T,
-          p.auto = T,
-          intercept.bottom = F,
-          single.row = T,
-          report = "vcs*",
-          omit.stat = c("rsq", "f"),
-          add.lines = list(f_string),
-          ci = T)
-```
 
@@
 ```{r, include = F}
-review <- read_csv("biometric_review.csv", col_types = cols())
+review <- read_csv("biometric_review.csv", col_types = cols(), na = "-")
 
 review_table <- review %>% 
-  select(Reference, n = N, a, c, b, r2, Gender, minD, maxD, Spear) %>% 
-  knitr::kable(row.names = F, caption = "Allometric growth parameters for eight published papers, Fishbase (Froese and Pauly 2016), and this study.
-All parameters have been adjusted to convert from millimiters to grams.
-n = Sample size, a = scaling parameter for eq.
-1, c = y-intercept for eq.
-3, b = exponent or slope for eq.
-1 or eq.
-2, respectively.", digits =  c(1, 0, 6, 4, 4, 4, 0, 1, 1))
-
-review_table
+  select(Reference = Study, Sex = Gender, n = N, a, c, b, r2, minD, maxD, Spear) %>% 
+  mutate(r2 = ifelse(is.na(r2), "-", r2),
+         minD = ifelse(is.na(minD), "-", minD),
+         maxD = ifelse(is.na(maxD), "-", maxD)) %>% 
+  knitr::kable(row.names = F,
+               digits =  c(1, 0, 6, 4, 4, 4, 0, 1, 1),
+               booktabs = T,
+               col.names = c("Reference", "n", "a", "c", "b", "R2", "Sex", "mDepth", "MDepth", "Spear")) %>% 
+  kableExtra::kable_styling(latex_options = c("scale_down")) 
 ```
 
-From the eight peer-reviewd studies including information on growth parameters for *P.
-volitans* and FishBase [@froese_website_2016], `r dim(review)[1]-1` parameters were identified.
+From the eight peer-reviewed studies including information on growth parameters for *P.
+volitans* and Fishbase [@froese_website_2016], `r dim(review)[1]-1` parameters were identified (Table 3).
 Two studies [@aguilarperera_2016; @fogg_2013] reported gender-level and pooled parameters, while the rest of the studies always presented pooled results.
-The smallest coefficient of determination was presented by @chin_2016 with $R^2 = `r min(review[,12], na.rm = T)`$, while @sabidoitza_2016 reported the highest value at $R^2 = `r min(review[,12], na.rm = T)`$.
-These studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` meters.
+The smallest coefficient of determination was presented by @chin_2016 with $R^2 = `r min(review[,12], na.rm = T)`$, while @sabidoitza_2016 reported the highest value at $R^2 = `r max(review[,12], na.rm = T)`$.
+These studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
 Two studies [@aguilarperera_2016; @chin_2016] explicitly stated that their organisms were sampled with pole spears.
@@
 
-Parameters from models fit to males or females exclusively tend to have a higher steapness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "M"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "M"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "F"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "F"]), digits = 2, format = "f")`$, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
+Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ males and females respectively, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
 In the case of the ponderal index ($a$) and its $log_{10}$ transformed parameter ($c$), values were higher for parameters for pooled genders.
-The trends in $a$, $c$, and $b$ indicate that some models will tend to estimate Total Weights differently.
 Figure 4 shows the predicted weights for organisms within the size range of these study using the 14 parameters previously described.
@@
 From all allometric parameters reviewed, those of @edwards_2014 slightly underestimated the observed biomass, with median (`r filter(Predicted_biomass, Study_id == "Edwards") %$% median(Biomass_ratio) %>% formatC(digits = 2, format = "f")`) and mean (`r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")`) bellow one.
-There is no significance in comparing the parameters estimated in this study since, by definition, they are the pair of parameters for which residual sum of squares was minimized with values of median =`r filter(Predicted_biomass, Study_id == "This") %$% median(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and mean (`r filter(Predicted_biomass, Study_id == "This") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")`).
-For all the other studies, the 95% confidence interval fell further away from a value of 1, indicating overestimation.
+There is no significance in comparing the parameters estimated in this study since, by definition, they are the pair of parameters for which residual sum of squares was minimized with values of median =`r filter(Predicted_biomass, Study_id == "This") %$% median(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and mean =`r filter(Predicted_biomass, Study_id == "This") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
+For all the other studies, the 95% confidence interval around the mean fell further away from a value of 1, indicating overestimation.
 Predicted to observed biomass ratios are presented in Figure 5.
@@
 Predicted_biomass_plot <-   Predicted_biomass %>% 
-  transform(Study_id = reorder(Study_id, -Biomass_ratio)) %>%
-  ggplot(aes(x = Study_id, y = Biomass_ratio)) +
+  mutate(Study = paste0(Study, " (", Gender, ")")) %>% 
+  transform(Study= reorder(Study, -Biomass_ratio)) %>%
+  ggplot(aes(x = Study, y = Biomass_ratio)) +
   geom_boxplot(aes(fill = Gender), outlier.size = 1, notch = T) +
@@
 
-# Discussion and Conclusions
+# Discussion
 
-Wider range sizes
+This study provides the first pair of allometric growth parameters specific to the Central Mexican Caribbean, complementing other studies performed in Mexican waters in the Alacranes Reef [@aguilarperera_2016] and Xcalak National Park [@sabidoitza_2016].
+By using hand nets instead of spears, we are able to sample a wider range of sizes often ignored by pole spear samples, allowing us to include smaller organisms.
+Estimating parameters by including smaller organisms ensures better estimatio of weight for smaller sizes.
+This is especially important when biomass is calculated from visual census, where small organisms can be registered.
+Thus, this study is the first to provide allometric growth parameters for lionfish in the central region of the Mexican Caribbean and increases certainty in weight estimation of small organisms.
 
-Model fit and this model
+The parameters estimated in this study were within the range of studies in other regions [@barbour_2011; @fogg_2013; @aguilarperera_2016; @sabidoitza_2016; @edwards_2014; @chin_2016; @deleon_2013; @sandel_2015].
+As compared to other parameters, the ones presented here tend to provide lower weight estimates for a same length.
+Until about TL = 200 mm, there are no appreciable differences between the parameters described in this study and those for little Cayman [@edwards_2014] and Jamaica [@chin_2016].
+Yet, for larger organisms (TL > 270 mm) parameters from Costa Rica [@sandel_2015] and Bonaire [@deleon_2013] provide similar estimates to those from this study.
+Conversely, these same studies tend to overestimate weight -as compared to the ones reported here- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
+When ever possible, future works should consider the use of hand nets to obtain the samples not only for studies on weight-at-length, but also diet, behavior and life history, where length can be an important factor.
 
-No spear doesnt seem to be a determinant factor in weight, but spear doesnt allow catching small organisms.
-Not using spear poles allows us to have a full sample of fish with a wider range of sizes and weights, ideal for visual census.
-Also, there is no loss in body mass due to bleeding.
+There are evident differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
+Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic [@barbour_2011; @fogg_2013; @aguilarperera_2016; @sabidoitza_2016] tend to be higher than those from the Caribbean [@edwards_2014; @chin_2016; @deleon_2013; @sandel_2015], except for the ones from Xcalak National Park, Mexico [@sabidoitza_2016].
+This indicates that there are differences between lionfish across the invasion range, pattern that has also been reported for age and growth parameters [@fogg_2015].
+These differences can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
+Using site-specific values provides a more accurate estimate of fish biomass.
+Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results.
+At the same time, this highlights the need for more basic research.
+To have a better invasion management, we must perform research that can describe biologically important information of lionfish throughout its invasion range [@johnson_2016].
 
-Gender-level overestimates and is steaper because it lacks small organisms to pull the curve
+While performing the literature review, it was often unclear if parameters were presented for eq.1 or eq.
+3.
+Sometimes, they were even mislabeled and yielded senseless results when using the suggested conversion equation.
+On some others, parameters were said to be reported for mm to gr conversions, when they were actually reported as cm to gr conversions.
+Perhaps these minor discrepancies can be easily solved by any researcher, but why should they exist in the first place?
+It is important that we report our information in a standard way, making it readily available for other researchers and managers.
+In this particular case, I provide my humble opinion through 5 guidelines to report allometric parameters:
+
+1.
+Be explicit in the methods section.
+What may seem obvious to you as an author -because you have been deeply immersed throughout the process- may not be clear to the reader.
+Specify any transformation performed on the data.
+When using log-transformations, mention the base used to transform.
+Do not assume that "data were log-transformed" means $log_{10}(X)$.
+These assumptions vary across disciplines and software and can be a source of confusion.
+For example, in biology we often assume "log-transformed" indicates the use of base 10, however in R the proper command is `log10()` and not `log()`, which uses base $e$.
+
+2.
+Use mm and gr to measure TL and TW, respectively.
+While conversion is always possible, we should aim at using standard units to report these parameters.
+If you prefer to use cm to gr conversions, that is certainly valid, but make sure to explicitly mention units when presenting the parameters.
+
+3.
+Specify the equation for which parameters are presented by including an explicit example with the parameters substituted into it, as done by some of the papers reviewed [@chin_2016; @sandel_2015; @deleon_2013; @sabidoitza_2016].
+If possible, present the parameters in their exponential (eq.
+1) and linear (eq.
+3) forms.
+
+4.
+Report standard errors and/or confidence intervals around the obtained estimates.
+Given that small changes in $a$, $c$,  and $b$ can result in important changes in estimated weight, it is important that we report uncertainty around each parameter and not just general model fit and significance.
+Reporting uncertainty around parameters allows researchers and managers to include upper and lower bounds in their predictions.
+
+5.
+Make your data -and code- available.
+Even if this is not requited by the journal or publisher, you can use free cloud data storage services or third-party repositories to make your research accessible to others.
+Resources will always be limited and budget will never be enough.
+It is important that we take advantage of open science tools that promote the advancement of knowledge and foster collaboration.
+Ultimately, this promotes transparency allows replicability of research and advances science.
+
+As final conclusion statements 1) A new pair of allometric growth parameters are provided for lionfish from the central Mexican Caribbean, where they exhibit different weight-at-length, as compared to other regions.
+2) Given the differences in weight-at-length patterns through the invasion range, it is important to use site-specific parameters.
+3) When possible, collect organisms with hand nets to obtain a representative sample of the population that includes small organisms.
+4) Report allometric parameters (and other life history parameters) in a way that is readily available for non-experts, and make your research available to advance science.
 
 # Aknowledgements
+
+I would like to thank thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
+I would also like to (anticipatedly) thank the editor and reviewers, who significantly improved the quality of this work.
+This research was partially funded by the "Consejo Nacional de Ciencias y Tecnología" (CONACyT) and the Latin American Fisheries Fellowship Program.
+
+\clearpage
+
+# References
+
+<div id="refs"></div>
+
+\clearpage
 
@@
 
-## Location table
+Table 1: Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.
 
-```{r}
+```{r, results = "asis"}
 location_table
@@
 
-## Summary table
+Table 2: Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
+Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.
+The asterisks (\*) indicate the statistical significance.
+95% Confidence intervals are provided for each parameter.
 
 ```{r, results = "asis"}
-cat(summary_table)
+
+ci_c <- c("95\\% CI for c", paste0("(", formatC(a-(1.96*robust_se[[1]]), digits = 3, format = "f"),"-", formatC(a+(1.96*robust_se[[1]]), digits = 3, format = "f"),")"))
+
+ci_b <- c("85\\% CI for b", paste0("(", formatC(b-(1.96*robust_se[[2]]), digits = 3, format = "f"),"-", formatC(b+(1.96*robust_se[[2]]), digits = 3, format = "f"),")"))
+
+regression_table <- stargazer(model,
+          header = F,
+          se = list(robust_se),
+          type = "latex",
+          t.auto = T,
+          p.auto = T,
+          intercept.bottom = F,
+          single.row = T,
+          report = "vcs*",
+          omit.stat = c("rsq", "f"),
+          add.lines = list(ci_c, ci_b, f_string),
+          covariate.labels = c("c", "b"),
+          dep.var.labels = "log10(TW)")
 ```
@@
 
-## Regression table
+Table 3: Summary of 13 allometric growth parameters available for lionfish in the invaded range from eight peer-reviewed papers, Fishbase [@froese_website_2016], and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, a = scaling parameter for eq.
+1, c = y-intercept for eq.
+3, b = exponent or slope for eq.
+1 or eq.
+3, respectively.
+The R^2^ column indicates reported model fit.
+mDepth and MDepth indicate minimum and maximum depths (m), respectively, at which organisms were sampled.
+The Spear column indicates if the study collected organisms with pole spears.
+An asterisk (\*) indicates that some portion of organisms were sampled with pole spears.
 
 ```{r, results = "asis"}
-cat(regression_table)
-```
-
-\clearpage
-
-## Review table
-
-```{r}
 review_table
@@
 
-## Map
-
 ```{r, fig.cap = "Map of the study area.
-The black inset on the left indicates the location where study sites are distributed.
-On the right, circular markers indicate sampling sites and the black romboid indicates location of Puerto Aventuras."}
+The black inset on the left (Yucatan Peninsula) indicates the location where study sites are distributed.
+On the right, circular markers indicate sampling sites and the black romboid indicates location of Puerto Aventuras, Mexico."}
 tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
@@
 
-## Histograms
-
-```{r, fig.width = 5, fig.height = 6, fig.cap = "Kernell density plots for a) Total length (mm) and b) Total weight (gr) for 109 lionfish sampled off the coast of Puerto Aventuras, Mexico."}
+```{r, fig.width = 5, fig.height = 6, fig.cap = "Kernell density plots for a) Total length (mm) and b) Total weight (gr) for 109 lionfish sampled in the central Mexican Caribbean."}
 gridExtra::grid.arrange(length_hist, weight_hist)
@@
 
-## Scatter plot
-
-```{r, fig.cap = "Weight-at-length relationship for 109 lionfish sampled off the coast of Puerto Aventuras, Mexico. Points indicate samples, solid line indicates curve of best fit."}
+```{r, fig.cap = "Weight-at-length relationship for 109 lionfish sampled in the central Mexican Caribbean. Points indicate samples, solid line indicates curve of best fit."}
 plot_fit_this_study
@@
 \clearpage
-
-## Review plots
 
@@
 
-## Predictions plot
-
 ```{r, fig.cap = ".
-Box and whiskers plot showing the distribution of predicted to observed Total Weight ratios for 14 pairs of allometric parameters.
+Box and whiskers plot showing the distribution of predicted to observed biomass ratios for 14 pairs of allometric parameters.
 Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers."}
@@
 ```
-
-\clearpage
-
-# References

### 2017-08-04 Manuscript.tex
Updated manuscript for submission

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{\normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers

\begin{document}
\maketitle

Juan Carlos Villaseñor-Derbez\textsuperscript{1}

\textsuperscript{1} Bren School of Environmental Sciences and
Management, University of California Santa Barbara, Santa Barbara,
California, U.S.

\textbf{Full postal address}\\
Bren Hall\\
University of California at Santa Barbara\\
Santa Barbara\\
CA, 93106

\textbf{Corresponding author information:}\\
Juan Carlos Villaseñor-Derbez\\
Bren Hall\\
University of California at Santa Barbara\\
Santa Barbara\\
CA, 93106
\href{mailto:jvillasenor@bren.ucsb.edu}{\nolinkurl{jvillasenor@bren.ucsb.edu}}
+1 207 205 8435

\textbf{Running title}\\
Allometric growth of Pterois volitans

\clearpage

\textbf{Title of contribution}: Biometry of the invasive lionfish
(\emph{Pterois volitans}) in the Central Mexican Caribbean, and a review
of allometric growth parameters across the invasion range

\textbf{Abstract}\\
Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
North-Western Atlantic and the Caribbean, likely introduced through
liberation of aquarium-kept organisms. Due to its threat to local
biodiversity, the speed of their spread, and its difficulty of
management, their presence in these waters has been labeled as a major
marine invasion. In order to better manage the invasion, inform lionfish
removal programs, predict their possible impacts, and estimate biomass
available for harvest, we must be able to accurately estimate their
total biomass. This study reports allometric growth parameters
(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
central portion of the Mexican Caribbean. It also identifies that, for a
given length, organisms from the Caribbean tend to have lower weights
than those from the Gulf of Mexicoand Atlantic, indicating that
weight-at-length is spacialy variable. In addition to the new pair of
parameters provided in this study, other 13 pairs of allometric growth
parameters were used to calculate expected biomass from total length
observations. Mean expected-to-observed biomass ratios by study ranged
between 0.98 and 1.75, with overall values ranging from 0.44 to 3.51.
The large differences between observed and expected biomass when using
parameters from other locations highlights the importance of using
site-specific parameters to estimate biomass from length observations.
This becomes increasingly important when estimating biomass available
for harvest or effectiveness of lionfish removal efforts. Additionally,
guidelines on reporting allometric parameters are provided as a
suggestion for future research are provided.

\textbf{Key words}\\
lionfish, Pterois volitans, length-weight relationship, allometric
growth, Mexico

\textbf{Resumen}\\
Los peces león (\emph{Pterois volitans/miles}) son una especiei nvasora
en el Atlántico Noroeste y el Caribe, probablemente introducidos por
medio de la liberación de organismos de ornato. Dada la amenaza que
estos representan para la biodiversidad local, la velocidad de su
invasión y dificultad de manejo, su presencia ha sido catalogada como
una importante invasión marina. Para manejar mejor la invasión, proveer
información a los programas de remoción, predecir los posibles impactos
y estimar biomasa disponible para la extracción, debemos ser capaces de
estimar su biomasa con precisión. Este estudio presenta parámetros de
crecimiento alométrico (\(a = 3.2056\times 10^{-6}; b = 3.235\)) para
organismos muestreados en la porción central del Caribe Mexicano.
También identifica que para una misma longitud, los organismos del
Caribe tienden a ser menos pesados que aquellos del Golfo de México y
Atlántico, indicando variaciones espaciales en la relación
peso-longitud. Además de los parámetros descritos en este estudio, se
utilizaron otros 13 pares de parámetros de crecimiento alométrico para
estimar biomasa a partir de observaciones de talla. La razón entre
biomasa observada y biomasa esperada varió, en promedio por estudio,
entre 0.98 y 1.75, con valores extremos de 0.44 y 3.51. Las grandes
diferencias entre biomasa observada y esperada al usar parámetros de
otras regiones resalta la importancia de utilizar parámetros específicos
a la zona para estimar biomasa a partir de observaciones de talla.
Adicionalmente, se proveen sugerencias para estandarizar la manera en
que los parámetros de crecimiento alométrico se reportan.

\textbf{Palabras clave} pez león, Pterois volitans, relación
longitud-peso, crecimiento alométrico, México

\clearpage

\section{Introduction}\label{introduction}

At least 84\% of the marine eco-regions have reported the presence of an
invasive species (Molnar et al., 2008). These represent a major threat
to local biodiversity and the economic activities that depend on it,
like tourism or fisheries (Bax et al., 2003). Invasive species may also
threaten native species through competition (DAVIS, 2003) or predation.
By 2005, the economic cost of invasive species to the United States was
estimated at \$120 billion per year and nearly 42\% of species that have
been included in the Endangered or Threatened species list have been
labeled as such due to presence of invasive species (Pimentel, Zuniga \&
Morrison, 2005). This highlights the importance of understanding,
managing, and preventing ecological invasions.

Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
in the North-Western Atlantic and the Caribbean, likely introduced
through liberation of aquarium-kept organisms (Betancur-R et al., 2011).
They are the first marine vertebrates to establish in North Atlantic
(Schofield, 2009, 2010) and Caribbean coasts (Sabido-Itza et al., 2016).
Lionfish have been widely reported in coral reefs (Aguilar-Perera \&
Tuz-Sulub, 2010), but also in other habitats such as estuaries (Jud et
al., 2011), mangroves (Barbour et al., 2010), areas with hard-bottoms
(Muñoz, Currin \& Whitfield, 2011), and mesophotic reefs (Andradi-Brown
et al., 2017). Due to its threat to local biodiversity, the speed of
their spread, and its difficulty of management, their presence in these
waters has been labeled as a major marine invasion (Hixon et al., 2016).

A significant amount of research has been done to describe lionfish
feeding ecology in North Carolina (Muñoz, Currin \& Whitfield, 2011),
the Bahamas (Morris \& Akins, 2009; Cote et al., 2013), Northern Gulf of
Mexico (Dahl \& Patterson, 2014), Mexican Caribbean (Valdez-Moreno et
al., 2012; Villaseñor-Derbez \& Herrera-P\a'erez, 2014), Belize
(Hackerott et al., 2017), and Costa Rica (Sandel et al., 2015). Their
feeding behavior and high consumption rates can reduce recruitment
(Albins \& Hixon, 2008) and population sizes (Green et al., 2012) of
native reef-fish species, and further the endangerment of critically
endangered reef fish (Rocha et al., 2015). (However, see Hackerott et
al. (2017) for a case where there was no evidence that lionfish affected
the density, richness, or composition of prey fishes). Major efforts
have also been made to understand the possible impacts of the invasion
by keeping track of its range through time (Schofield, 2009, 2010) and
predicting invasion ranges under climate change scenarios (Grieve,
Curchitser \& Rykaczewski, 2016). By combining information from these
disciplines, researchers have been able to predict the trophic impacts
of lionfish (Arias-Gonzalez et al., 2011), which can then be translated
into ecosystem-level and economic impacts.

Seeking to reduce lionfish densities, governments and non-profit
organizations have promoted removal programs and incentivized its
consumption (Chin, Aiken \& Buddo, 2016). In some cases, these have
shown to significantly reduce -but not quite eliminate- lionfish
abundances at local scales (Sandel et al., 2015, Chin, Aiken \& Buddo
(2016), de Leon et al. (2013)). The rapid recovery rates exhibited by
lionfish (Barbour et al., 2011) and the persistent populations in
mesophotic coral ecosystems (Andradi-Brown et al., 2017) -which can
contribute with recruitment to shallow-water populations- make of
complete eradication through fishing effort an unlikely solution.
However, further incentivizing its consumption might create a demand big
enough to promote and sustain a stable fishery (Chin, Aiken \& Buddo,
2016), which can reduce local abundances and control -not eradicate- the
invasion while providing alternative livelihoods.

The feasibility of lionfish removal programs has been extensively
evaluated through field observations(Sandel et al., 2015, Chin, Aiken \&
Buddo (2016), de Leon et al. (2013); Usseglio et al., 2017) and
empirical modeling (Barbour et al., 2011; Morris, Shertzer \& Rice,
2011; Johnston \& Purkis, 2015). The latter measure changes in biomass
or density (Barbour et al., 2011; Johnston \& Purkis, 2015) in response
to increased mortality (\emph{i.e.} lionfish removal). In this case,
biomass represents the sum of all fish's individual weight. Total Weight
(TW) can be estimated from Total Length (TL) observations using the
allometric growth equation (\(TW = aTL^b\)). Parameters \(a\) and \(b\)
for this equation exist for North Carolina (Barbour et al., 2011),
Northern (Fogg et al., 2013) and Southern Gulf of Mexico (Aguilar-Perera
\& Quijano-Puerto, 2016), the Southern Mexican Caribbean (Sabido-Itza et
al., 2016), Little Cayman (Edwards, Frazer \& Jacoby, 2014), Jamaica
(Chin, Aiken \& Buddo, 2016), Bonaire (de Leon et al., 2013) and Costa
Rica (Sandel et al., 2015), but remain unavailable for the central
Mexican Caribbean. The weight-at-length of a species can vary across
regions as a response to biotic (\emph{e.g.} local food availability)
and abiotic (\emph{e.g.} water temperature) conditions (Johnson \&
Swenarton, 2016). Thus, when using biomass-informed models or estimating
biomass from length observations, it is important to use site-specific
parameters to obtain an accurate estimate. This is especially important
when research involves identifying the total biomass available for
harvest by fishers (Chin, Aiken \& Buddo, 2016) or the efficacy of
lionfish removals (Barbour et al., 2011; Morris, Shertzer \& Rice, 2011;
Johnston \& Purkis, 2015).

Here, I provide the first allometric growth parameters for the invasive
lionfish in the central Mexican Caribbean region. At the same time, I
highlight the importance of using site-specific parameters by estimating
biomass with parameters from other regions across the invasion range and
comparing them to observed biomass. I also provide other 13 standardized
parameters from eight studies through the invasion range, making them
readily accessible for future research. Finally, I discuss the way in
which allometric parameters are reported, and call for standardization
to facilitate their use.

\section{Materials and Methods}\label{materials-and-methods}

\subsection{Area of study}\label{area-of-study}

The study took place off the coasts of Playa del Carmen, in the Mexican
Caribbean (\textbf{Fig. 1}). The region represents the northernmost
section of the Mesoamerican Barrier Reef System (Ruiz-Zarate \&
Arias-Gonzalez, 2004). Coral reefs and mangroves are locally important
habitats that represent important sources of income in terms of
extractive (\emph{e.g.} recreational fishing) and non-extractive
(\emph{e.g.} SCUBA diving) activities related to tourism, the main
source of income to the local economy (Murray, 2007).

In the region, the reef profile has been described by Arias-Gonzalez
(1998), indicating that the reef lagoon extends about 500 m from the
coast, until the reef crest is reached. The reef becomes deeper, leading
to the reef front often found at 700 m from the coastline end extends
for an additional 300 m. At approximately 1000 m away from shore and 30
- 40 m depth, the reef leads to a drop-off. Along a perpendicular
profile to the coast, bands of reef are interrupted by sand patches at 8
- 12 m deep and 16-18 m deep. Along the coast, these reefs have been
reported to be under significant anthropogenic pressure, likely causing
a shift in structure and function (Bozec et al., 2008).

\subsection{Fish sampling}\label{fish-sampling}

Organisms sampled by Villaseñor-Derbez \& Herrera-P\a'erez (2014) for
stomach content analysis between May and August of 2010 were used in
this work. A total of 33 SCUBA immersions were performed in 10 sampling
sites along the coast (Fig. 1, Table 1). Sampling locations included
wall and carpet reefs at depths between 5.7 m and 38.1 m. All observed
organisms (n = 109) were collected using hand nets and numbered
collection bottles. The use of hand nets prevents any weight loss due to
bleeding(when collected with spears), and increases the range of sizes
that can be sampled, providing a representative sample of the
population. Information on depth and other comments were recorded in an
underwater slide. Depth was recorded by dive gauges held by divers as
safety procedures during the collections. Samples were frozen within 30
minutes of completing the dive and stored for posterior analysis in the
lab. For every organism Total Length (TL; mm) and Total Weight (TW; gr)
were recorded in the lab.

\subsection{Data analysis}\label{data-analysis}

The weight at length relationship between the observed variables is
described by the allometric growth function:

\begin{equation}TW = aTL^b\end{equation}

Where \(TW\) is the Total Weight (gr), \(TL\) is the observed Total
Length (mm), \(a\) is the ponderal index and \(b\) is the scaling
exponent or allometric parameter. When \(b = 3\), it is said that the
organism exhibits a perfect isometric growth. The dependent and
independent variables were transformed via base-10 logarithms so that
the equation is then:

\begin{equation}log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\end{equation}

To simplify this equation, we can re-write it as:

\begin{equation}Y = mX + c\end{equation}

Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), \(m = b\), and
\(c = log_{10}(a)\). Since \(b == m\), we will only use \(b\) throughout
the paper for simplicity. The coefficients (\(c\) and \(b\)) were
estimated with an Ordinary Least Square Regression and
heteroskedastic-robust standard errors. Both coefficients were tested
against the null hypothesis of no change (\emph{i.e.} \(H_0: c = 0\) and
\(H_0: b = 0\)). Additionally, the allometric parameter was tested
against the null hypothesis of isometric growth (\(H_0: b = 3\)).
Coefficients were tested with a two-tailed Student's t-test. The
significance of the regression was corroborated with an F-test.

Other allometric growth parameters were obtained from peer-reviewed
literature. Parameters were obtained forNorth Carolina (Barbour et al.,
2011), Northern (Fogg et al., 2013) and Southern Gulf of Mexico
(Aguilar-Perera \& Quijano-Puerto, 2016), the Southern Mexican Caribbean
(Sabido-Itza et al., 2016), Little Cayman (Edwards, Frazer \& Jacoby,
2014), Jamaica (Chin, Aiken \& Buddo, 2016), Bonaire (de Leon et al.,
2013) and Costa Rica (Sandel et al., 2015). Additionally, parameters
from Fishbase (Froese \& Pauly, 2016) were also included in this study.
When available, information on sampling methods, gender differentiation,
location, and depth ranges of each study was retrieved. Whenever gender
was not specified, it was assumed that the results were presented for
both genders pooled together. During the review process, it was noticed
that some papers indistinctly use \(a\) to report either the ponderal
index in eq. 1 or the y-intercept (\(c\)) in eq. 3, which might
sometimes be overlooked. Furthermore, some studies report their
parameters as mm-to-gr conversions, but a rapid evaluation of such
parameters indicates that they were estimated as cm-to-gr conversions.
Here, all parameters are reported as TL(mm) to TW(gr) conversions. When
required, values from other studies are transformed for consistency.

Since standard errors or confidence intervals were not provided for many
studies, it was impossible to test for statistical differences across
studies. Thus expected biomass for each organism was calculated with the
growth parameters estimated in this study, as well as those retrieved
from additional literature. All expected biomass values were divided by
the observed biomass to obtain a ratio that allowed rapid identification
of over- or underestimation with respect to the observed biomass.
Therefore, values lower than 1 indicate that the parameters
underestimate biomass, and values larger than 1 indicate overestimation.
Median and mean expected to observed biomass ratios were calculated for
each study.

All hypothesis testing was performed with a confidence level of
\(\alpha = 0.01\) in R version 3.4.0 (R Core Team, 2017). Data wrangling
was performed with the tidyverse package (Wickham, 2017). Maps were
created with a mix of functions from the sp (Pebesma \& Bivand, 2005),
rgdal (Bivand, Keitt \& Rowlingson, 2017), tmap (Tennekes, 2017a), and
tmaptools (Tennekes, 2017b) packages. Calculation of
heteroskedastic-robust standard errors was done with the sandwich
(Zeileis, 2004) and lmtest (Zeileis \& Hothorn, 2002) packages. Models
were manipulated with with the broom package (Robinson, 2017). Stargazer
(Hlavac, 2015), knitr (Xie, 2017), and kableExtra (Zhu, 2017) were used
to produce the tables, and RefManageR (McLean, 2014) was used to keep
track of citations. The manuscript was written in r markdown (Allaire et
al., 2017) and processed with the knitr package (Xie, 2017). Raw data
and code used in this work is available at
\url{github.com/jcvdav/lionfish_biometry}.

\section{Results}\label{results}

Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7
gr. The smallest organism (TL = 34.00 mm) was also the lightest organism
(TW = 0.30 gr). However, the largest organism (TL = 310.00 mm) was not
the heaviest (TW = 303.70 gr), and the heaviest organism (TW = 397.70
gr) was 292.00 mm in total length. Kernell density plots (Fig. 2) show
the distribution for TL and TW. Both measures were positively skewed,
with skewness of 0.85 for TL and 2.19 for TW.

\subsection{Length-weight
relationship}\label{length-weight-relationship}

The model adjusted to eq. 3 estimated the coefficient values at
\(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
calculated from TL (mm) as a linear equation:
\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\) or its
exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
The intercept (\(c\)) and slope \((b)\) were significantly different
from zero (\(t(107) = -66.17; p<0.01\) and \(t(107) = 83.24; p<0.01\),
respectively), rejecting the null hypothesis of no change. Additionally,
the allometric factor (\(m = b\)) was significantly different from the
value of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)),
indicating that lionfish present allometric growth. More information on
model fit and confidence intervals for the estimated coefficients is
presented in Table 2. The relationship between Total Length and Total
Weight is presented in Figure 3.

\subsection{Comparison of allometric
parameters}\label{comparison-of-allometric-parameters}

From the eight peer-reviewed studies including information on growth
parameters for \emph{P. volitans} and Fishbase (Froese \& Pauly, 2016),
13 parameters were identified (Table 3). Two studies (Fogg et al., 2013;
Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and pooled
parameters, while the rest of the studies always presented pooled
results. The smallest coefficient of determination was presented by
Chin, Aiken \& Buddo (2016) with \(R^2 = 0.8715\), while Sabido-Itza et
al. (2016) reported the highest value at \(R^2 = 0.9907\). These studies
presented information for organisms obtained at depths between 0.5 and
57 m. Two studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken
\& Buddo, 2016) explicitly stated that their organisms were sampled with
pole spears. Five studies (Barbour et al., 2011; Fogg et al., 2013;
Edwards, Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et
al., 2016) mentioned that some of their organisms were obtained with
pole spears (or other type of harpoon). A single study (de Leon et al.,
2013) did not specify how samples were obtained.

Parameters from models fit to males or females exclusively tend to have
a higher steepness (\emph{i.e.} higher allometric parameter), with mean
\(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
\(b = 3.31 \pm 0.23\) males and females respectively, compared to
parameters from models for pooled genders with a mean \(\pm\) standard
deviation value of \(b = 3.09 \pm 0.22\). In the case of the ponderal
index (\(a\)) and its \(log_{10}\) transformed parameter (\(c\)), values
were higher for parameters for pooled genders. Figure 4 shows the
predicted weights for organisms within the size range of these study
using the 14 parameters previously described.

From all allometric parameters reviewed, those of Edwards, Frazer \&
Jacoby (2014) slightly underestimated the observed biomass, with median
(0.96) and mean (0.98) bellow one. There is no significance in comparing
the parameters estimated in this study since, by definition, they are
the pair of parameters for which residual sum of squares was minimized
with values of median =1.00 and mean =1.03. For all the other studies,
the 95\% confidence interval around the mean fell further away from a
value of 1, indicating overestimation. Predicted to observed biomass
ratios are presented in Figure 5.

\section{Discussion}\label{discussion}

This study provides the first pair of allometric growth parameters
specific to the Central Mexican Caribbean, complementing other studies
performed in Mexican waters in the Alacranes Reef (Aguilar-Perera \&
Quijano-Puerto, 2016) and Xcalak National Park (Sabido-Itza et al.,
2016). By using hand nets instead of spears, we are able to sample a
wider range of sizes often ignored by pole spear samples, allowing us to
include smaller organisms. Estimating parameters by including smaller
organisms ensures better estimatio of weight for smaller sizes. This is
especially important when biomass is calculated from visual census,
where small organisms can be registered. Thus, this study is the first
to provide allometric growth parameters for lionfish in the central
region of the Mexican Caribbean and increases certainty in weight
estimation of small organisms.

The parameters estimated in this study were within the range of studies
in other regions (Barbour et al., 2011; de Leon et al., 2013; Fogg et
al., 2013; Edwards, Frazer \& Jacoby, 2014; Sandel et al., 2015;
Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken \& Buddo, 2016;
Sabido-Itza et al., 2016). As compared to other parameters, the ones
presented here tend to provide lower weight estimates for a same length.
Until about TL = 200 mm, there are no appreciable differences between
the parameters described in this study and those for little Cayman
(Edwards, Frazer \& Jacoby, 2014) and Jamaica (Chin, Aiken \& Buddo,
2016). Yet, for larger organisms (TL \textgreater{} 270 mm) parameters
from Costa Rica (Sandel et al., 2015) and Bonaire (de Leon et al., 2013)
provide similar estimates to those from this study. Conversely, these
same studies tend to overestimate weight -as compared to the ones
reported here- for smaller organisms, likely due to the lack of small
organisms in the samples used to estimate their parameters. When ever
possible, future works should consider the use of hand nets to obtain
the samples not only for studies on weight-at-length, but also diet,
behavior and life history, where length can be an important factor.

There are evident differences in weight-at-length between organisms from
the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight
estimates with parameters from the Gulf of Mexico and North-Western
Atlantic (Barbour et al., 2011; Fogg et al., 2013; Aguilar-Perera \&
Quijano-Puerto, 2016; Sabido-Itza et al., 2016) tend to be higher than
those from the Caribbean (de Leon et al., 2013; Edwards, Frazer \&
Jacoby, 2014; Sandel et al., 2015; Chin, Aiken \& Buddo, 2016), except
for the ones from Xcalak National Park, Mexico (Sabido-Itza et al.,
2016). This indicates that there are differences between lionfish across
the invasion range, pattern that has also been reported for age and
growth parameters (Fogg et al., 2015). These differences can have major
implications in management, especially when estimating biomass available
for harvest or predicting effects on local ecosystems, or evaluating the
effectiveness of removal programs. Using site-specific values provides a
more accurate estimate of fish biomass. Future research should try to
use, to the extent possible, parameters calculated for their region, or
use different parameters to provide upper and lower bounds in their
results. At the same time, this highlights the need for more basic
research. To have a better invasion management, we must perform research
that can describe biologically important information of lionfish
throughout its invasion range (Johnson \& Swenarton, 2016).

While performing the literature review, it was often unclear if
parameters were presented for eq.1 or eq. 3. Sometimes, they were even
mislabeled and yielded senseless results when using the suggested
conversion equation. On some others, parameters were said to be reported
for mm to gr conversions, when they were actually reported as cm to gr
conversions. Perhaps these minor discrepancies can be easily solved by
any researcher, but why should they exist in the first place? It is
important that we report our information in a standard way, making it
readily available for other researchers and managers. In this particular
case, I provide my humble opinion through 5 guidelines to report
allometric parameters:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Be explicit in the methods section. What may seem obvious to you as an
  author -because you have been deeply immersed throughout the process-
  may not be clear to the reader. Specify any transformation performed
  on the data. When using log-transformations, mention the base used to
  transform. Do not assume that ``data were log-transformed'' means
  \(log_{10}(X)\). These assumptions vary across disciplines and
  software and can be a source of confusion. For example, in biology we
  often assume ``log-transformed'' indicates the use of base 10, however
  in R the proper command is \texttt{log10()} and not \texttt{log()},
  which uses base \(e\).
\item
  Use mm and gr to measure TL and TW, respectively. While conversion is
  always possible, we should aim at using standard units to report these
  parameters. If you prefer to use cm to gr conversions, that is
  certainly valid, but make sure to explicitly mention units when
  presenting the parameters.
\item
  Specify the equation for which parameters are presented by including
  an explicit example with the parameters substituted into it, as done
  by some of the papers reviewed (de Leon et al., 2013; Sandel et al.,
  2015; Chin, Aiken \& Buddo, 2016; Sabido-Itza et al., 2016). If
  possible, present the parameters in their exponential (eq. 1) and
  linear (eq. 3) forms.
\item
  Report standard errors and/or confidence intervals around the obtained
  estimates. Given that small changes in \(a\), \(c\), and \(b\) can
  result in important changes in estimated weight, it is important that
  we report uncertainty around each parameter and not just general model
  fit and significance. Reporting uncertainty around parameters allows
  researchers and managers to include upper and lower bounds in their
  predictions.
\item
  Make your data -and code- available. Even if this is not requited by
  the journal or publisher, you can use free cloud data storage services
  or third-party repositories to make your research accessible to
  others. Resources will always be limited and budget will never be
  enough. It is important that we take advantage of open science tools
  that promote the advancement of knowledge and foster collaboration.
  Ultimately, this promotes transparency allows replicability of
  research and advances science.
\end{enumerate}

As final conclusion statements 1) A new pair of allometric growth
parameters are provided for lionfish from the central Mexican Caribbean,
where they exhibit different weight-at-length, as compared to other
regions. 2) Given the differences in weight-at-length patterns through
the invasion range, it is important to use site-specific parameters. 3)
When possible, collect organisms with hand nets to obtain a
representative sample of the population that includes small organisms.
4) Report allometric parameters (and other life history parameters) in a
way that is readily available for non-experts, and make your research
available to advance science.

\section{Aknowledgements}\label{aknowledgements}

I would like to thank thank Nils Van Der Haar and Michael Doodey from
Dive Aventuras as well as Guillermo Lotz-Cador who provided help to
collect samples. I would also like to (anticipatedly) thank the editor
and reviewers, who significantly improved the quality of this work. This
research was partially funded by the ``Consejo Nacional de Ciencias y
Tecnología'' (CONACyT) and the Latin American Fisheries Fellowship
Program.

\clearpage

\section{References}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-aguilarperera_2016}{}
Aguilar-Perera, A. \& Quijano-Puerto, L. 2016. Relations between fish
length to weight, and otolith length and weight, of the lionfish pterois
volitans in the parque nacional arrecife alacranes, southern gulf of
mexico. \emph{Rev. biol. mar. oceanogr.} 51(2):469--474. DOI:
\href{https://doi.org/10.4067/S0718-19572016000200025}{10.4067/S0718-19572016000200025}.

\hypertarget{ref-aguilarperera_2010}{}
Aguilar-Perera, A. \& Tuz-Sulub, A. 2010. Non-native, invasive red
lionfish (pterois volitans {[}linnaeus, 1758{]}: Scorpaenidae), is first
recorded in the southern gulf of mexico, off the northern yucatan
peninsula, mexico. \emph{AI}. 5(Supplement 1):S9--S12. DOI:
\href{https://doi.org/10.3391/ai.2010.5.S1.003}{10.3391/ai.2010.5.S1.003}.

\hypertarget{ref-albins_2008}{}
Albins, M. \& Hixon, M. 2008. Invasive indo-pacific lionfish pterois
volitans reduce recruitment of atlantic coral-reef fishes. \emph{Mar.
Ecol. Prog. Ser.} 367:233--238. DOI:
\href{https://doi.org/10.3354/meps07620}{10.3354/meps07620}.

\hypertarget{ref-rmarkdown_2017}{}
Allaire, J., Cheng, J., Xie, Y., McPherson, J., Chang, W., Allen, J.,
Wickham, H., Atkins, A., et al. 2017. \emph{Rmarkdown: Dynamic documents
for r}. ed. (nos.). Available:
\url{https://CRAN.R-project.org/package=rmarkdown}.

\hypertarget{ref-andradibrown_2017}{}
Andradi-Brown, D.A., Grey, R., Hendrix, A., Hitchner, D., Hunt, C.L.,
Gress, E., Madej, K., Parry, R.L., et al. 2017. Depth-dependent effects
of culling-do mesophotic lionfish populations undermine current
management? \emph{R Soc Open Sci}. 4(5):170027. DOI:
\href{https://doi.org/10.1098/rsos.170027}{10.1098/rsos.170027}.

\hypertarget{ref-ariasgonzalez_1998}{}
Arias-Gonzalez, J.E. 1998. Trophic models of protected and unprotected
coral reef ecosystems in the south of the mexican caribbean. \emph{J
Fish Biol}. 53(sa):236--255. DOI:
\href{https://doi.org/10.1111/j.1095-8649.1998.tb01030.x}{10.1111/j.1095-8649.1998.tb01030.x}.

\hypertarget{ref-ariasgonzalez_2011}{}
Arias-Gonzalez, J.E., Gonzalez-Gandara, C., Luis Cabrera, J. \&
Christensen, V. 2011. Predicted impact of the invasive lionfish pterois
volitans on the food web of a caribbean coral reef. \emph{Environ Res}.
111(7):917--925. DOI:
\href{https://doi.org/10.1016/j.envres.2011.07.008}{10.1016/j.envres.2011.07.008}.

\hypertarget{ref-barbour_2010}{}
Barbour, A., Montgomery, M., Adamson, A., D?az-Ferguson, E. \& Silliman,
B. 2010. Mangrove use by the invasive lionfish pterois volitans.
\emph{Mar. Ecol. Prog. Ser.} 401:291--294. DOI:
\href{https://doi.org/10.3354/meps08373}{10.3354/meps08373}.

\hypertarget{ref-barbour_2011}{}
Barbour, A.B., Allen, M.S., Frazer, T.K. \& Sherman, K.D. 2011.
Evaluating the potential efficacy of invasive lionfish (pterois
volitans) removals. \emph{PLoS ONE}. 6(5):e19666. DOI:
\href{https://doi.org/10.1371/journal.pone.0019666}{10.1371/journal.pone.0019666}.

\hypertarget{ref-bax_2003}{}
Bax, N., Williamson, A., Aguero, M., Gonzalez, E. \& Geeves, W. 2003.
Marine invasive alien species: A threat to global biodiversity.
\emph{Marine Policy}. 27(4):313--323. DOI:
\href{https://doi.org/10.1016/S0308-597X(03)00041-1}{10.1016/S0308-597X(03)00041-1}.

\hypertarget{ref-betancurr_2011}{}
Betancur-R, R., Hines, A., Acero, A., Orti, G., Wilbur, A. \&
Freshwater, D. 2011. Reconstructing the lionfish invasion: Insights into
greater caribbean biogeography. \emph{J Biogeography}. 38:1281--1293.
DOI:
\href{https://doi.org/10.1111/j.1365-2699.2011.02496.x}{10.1111/j.1365-2699.2011.02496.x}.

\hypertarget{ref-rgdal_2017}{}
Bivand, R., Keitt, T. \& Rowlingson, B. 2017. \emph{Rgdal: Bindings for
the geospatial data abstraction library}. ed. (nos.). Available:
\url{https://CRAN.R-project.org/package=rgdal}.

\hypertarget{ref-bozec_2008}{}
Bozec, Y., Acosta-Gonz\a'alez, G., N\a'uñez-Lara, E. \&
Arias-Gonz\a'alez, J. 2008. Impacts of coastal development on ecosystem
structure and function of yucatan coral reefs, mexico. In
\emph{Proceedings of the 11th international coral reef symposium}. ed.
I.C.R.S. ICRF, Ed. (nos.). Ft. Lauderdale, Florida: 11th International
Coral Reef Symposium.

\hypertarget{ref-chin_2016}{}
Chin, D.A., Aiken, K.A. \& Buddo, D. 2016. Lionfish population density
in discovery bay, jamaica. \emph{International Journal of Scientific \&
Engineering Research}. 7(12):1327--1331.

\hypertarget{ref-cote_2013}{}
Cote, I., Green, S., Morris, J., Akins, J. \& Steinke, D. 2013. Diet
richness of invasive indo-pacific lionfish revealed by dna barcoding.
\emph{Mar. Ecol. Prog. Ser.} 472:249--256. DOI:
\href{https://doi.org/10.3354/meps09992}{10.3354/meps09992}.

\hypertarget{ref-dahl_2014}{}
Dahl, K.A. \& Patterson, W.F. 2014. Habitat-specific density and diet of
rapidly expanding invasive red lionfish, pterois volitans, populations
in the northern gulf of mexico. \emph{PLoS ONE}. 9(8):e105852. DOI:
\href{https://doi.org/10.1371/journal.pone.0105852}{10.1371/journal.pone.0105852}.

\hypertarget{ref-davis_2003}{}
DAVIS, M.A. 2003. Biotic globalization: Does competition from introduced
species threaten biodiversity? \emph{Bioscience}. 53(5):481. DOI:
\href{https://doi.org/10.1641/0006-3568(2003)053\%5B0481:BGDCFI\%5D2.0.CO;2}{10.1641/0006-3568(2003)053{[}0481:BGDCFI{]}2.0.CO;2}.

\hypertarget{ref-deleon_2013}{}
de Leon, R., Vane, K., Bertuol, P., Chamberland, V.C., Simal, F., Imms,
E. \& Vermeij, M.J.A. 2013. Effectiveness of lionfish removal efforts in
the southern caribbean. \emph{Endanger Species Res}. 22(2):175--182.
DOI: \href{https://doi.org/10.3354/esr00542}{10.3354/esr00542}.

\hypertarget{ref-edwards_2014}{}
Edwards, M.A., Frazer, T.K. \& Jacoby, C.A. 2014. Age and growth of
invasive lionfish (pterois spp.) in the caribbean sea, with implications
for management. \emph{BMS}. 90(4):953--966. DOI:
\href{https://doi.org/10.5343/bms.2014.1022}{10.5343/bms.2014.1022}.

\hypertarget{ref-fogg_2015}{}
Fogg, A.Q., Evans, J.T., Ingram JR, G.W., Peterson, M.S. \&
Brown-Peterson, N.J. 2015. Comparing age and growth patterns of invasive
lionfish among three ecoregions of the northern gulf of mexico. In
\emph{Proceedings of the 68 th gulf and caribbean fisheries institute}.
ed. G. GCFI \& C.F. Institute, Eds. (nos.). Panama City: Gulf; Caribbean
Fisheries Institute.

\hypertarget{ref-fogg_2013}{}
Fogg, A.Q., Hoffmayer, E.R., Driggers, W.B., Campbell, M.D., Pellegrin,
G.J. \& Stein, W. 2013. Distribution and length frequency of invasive
lionfish (pterois sp.) in the northern gulf of mexico. \emph{GCR}. 25.
DOI: \href{https://doi.org/10.18785/gcr.2501.08}{10.18785/gcr.2501.08}.

\hypertarget{ref-froese_website_2016}{}
Froese, R. \& Pauly, D. 2016. Available: \url{http://www.fishbase.org/}
{[}2016, December 15{]}.

\hypertarget{ref-green_2012}{}
Green, S.J., Akins, J.L., Maljkovi\a'c, A. \& Côt\a'e, I.M. 2012.
Invasive lionfish drive atlantic coral reef fish declines. \emph{PLoS
ONE}. 7(3):e32596. DOI:
\href{https://doi.org/10.1371/journal.pone.0032596}{10.1371/journal.pone.0032596}.

\hypertarget{ref-grieve_2016}{}
Grieve, B., Curchitser, E. \& Rykaczewski, R. 2016. Range expansion of
the invasive lionfish in the northwest atlantic with climate change.
\emph{Mar. Ecol. Prog. Ser.} 546:225--237. DOI:
\href{https://doi.org/10.3354/meps11638}{10.3354/meps11638}.

\hypertarget{ref-hackerott_2017}{}
Hackerott, S., Valdivia, A., Cox, C.E., Silbiger, N.J. \& Bruno, J.F.
2017. Invasive lionfish had no measurable effect on prey fish community
structure across the belizean barrier reef. \emph{PeerJ}. 5:e3270. DOI:
\href{https://doi.org/10.7717/peerj.3270}{10.7717/peerj.3270}.

\hypertarget{ref-hixon_2016}{}
Hixon, M., Green, S., Albins, M., Akins, J. \& Morris, J. 2016.
Lionfish: A major marine invasion. \emph{Mar. Ecol. Prog. Ser.}
558:161--165. DOI:
\href{https://doi.org/10.3354/meps11909}{10.3354/meps11909}.

\hypertarget{ref-stargazer_2015}{}
Hlavac, M. 2015. \emph{Stargazer: Well-formatted regression and summary
statistics tables}. ed. (nos.). Cambridge, USA: Harvard University.
Available: \url{http://CRAN.R-project.org/package=stargazer}.

\hypertarget{ref-johnson_2016}{}
Johnson, E.G. \& Swenarton, M.K. 2016. Age, growth and population
structure of invasive lionfish (pterois volitans/miles) in northeast
florida using a length-based, age-structured population model.
\emph{PeerJ}. 4:e2730. DOI:
\href{https://doi.org/10.7717/peerj.2730}{10.7717/peerj.2730}.

\hypertarget{ref-johnston_2015}{}
Johnston, M. \& Purkis, S. 2015. A coordinated and sustained
international strategy is required to turn the tide on the atlantic
lionfish invasion. \emph{Mar. Ecol. Prog. Ser.} 533:219--235. DOI:
\href{https://doi.org/10.3354/meps11399}{10.3354/meps11399}.

\hypertarget{ref-jud_2011}{}
Jud, Z., Layman, C., Lee, J. \& Arrington, D. 2011. Recent invasion of a
florida (usa) estuarine system by lionfish pterois volitans / p. miles~.
\emph{Aquat. Biol.} 13(1):21--26. DOI:
\href{https://doi.org/10.3354/ab00351}{10.3354/ab00351}.

\hypertarget{ref-RefManager_2014}{}
McLean, M.W. 2014. \emph{Straightforward bibliography management in r
using the refmanager package}. ed. (nos.). Available:
\url{http://arxiv.org/abs/1403.2036}.

\hypertarget{ref-molnar_2008}{}
Molnar, J.L., Gamboa, R.L., Revenga, C. \& Spalding, M.D. 2008.
Assessing the global threat of invasive species to marine biodiversity.
\emph{Frontiers in Ecology and the Environment}. 6(9):485--492. DOI:
\href{https://doi.org/10.1890/070064}{10.1890/070064}.

\hypertarget{ref-morris_2009}{}
Morris, J.A. \& Akins, J.L. 2009. Feeding ecology of invasive lionfish
(pterois volitans) in the bahamian archipelago. \emph{Environ. Biol.
Fishes}. 86(3):389--398. DOI:
\href{https://doi.org/10.1007/s10641-009-9538-8}{10.1007/s10641-009-9538-8}.

\hypertarget{ref-morris_2011}{}
Morris, J.A., Shertzer, K.W. \& Rice, J.A. 2011. A stage-based matrix
population model of invasive lionfish with implications for control.
\emph{Biol Invasions}. 13(1):7--12. DOI:
\href{https://doi.org/10.1007/s10530-010-9786-8}{10.1007/s10530-010-9786-8}.

\hypertarget{ref-muoz_2011}{}
Muñoz, R., Currin, C. \& Whitfield, P. 2011. Diet of invasive lionfish
on hard bottom reefs of the southeast usa: Insights from stomach
contents and stable isotopes. \emph{Mar. Ecol. Prog. Ser.} 432:181--193.
DOI: \href{https://doi.org/10.3354/meps09154}{10.3354/meps09154}.

\hypertarget{ref-murray_2007}{}
Murray, G. 2007. Constructing paradise: The impacts of big tourism in
the mexican coastal zone. \emph{Coastal Management}. 35(2-3):339--355.
DOI:
\href{https://doi.org/10.1080/08920750601169600}{10.1080/08920750601169600}.

\hypertarget{ref-sp_2017}{}
Pebesma, E.J. \& Bivand, R.S. 2005. Classes and methods for spatial data
in R. \emph{R News}. 5(2):9--13. Available:
\url{https://CRAN.R-project.org/doc/Rnews/}.

\hypertarget{ref-pimentel_2005}{}
Pimentel, D., Zuniga, R. \& Morrison, D. 2005. Update on the
environmental and economic costs associated with alien-invasive species
in the united states. \emph{Ecological Economics}. 52(3):273--288. DOI:
\href{https://doi.org/10.1016/j.ecolecon.2004.10.002}{10.1016/j.ecolecon.2004.10.002}.

\hypertarget{ref-rcore_2017}{}
R Core Team. 2017. \emph{R: A language and environment for statistical
computing}. ed. (nos.). Vienna, Austria: R Foundation for Statistical
Computing. Available: \url{https://www.R-project.org/}.

\hypertarget{ref-broom_2017}{}
Robinson, D. 2017. \emph{Broom: Convert statistical analysis objects
into tidy data frames}. ed. (nos.). Available:
\url{https://CRAN.R-project.org/package=broom}.

\hypertarget{ref-rocha_2015}{}
Rocha, L.A., Rocha, C.R., Baldwin, C.C., Weigt, L.A. \& McField, M.
2015. Invasive lionfish preying on critically endangered reef fish.
\emph{Coral Reefs}. 34(3):803--806. DOI:
\href{https://doi.org/10.1007/s00338-015-1293-z}{10.1007/s00338-015-1293-z}.

\hypertarget{ref-ruizzarate_2004}{}
Ruiz-Zarate, M. \& Arias-Gonzalez, J. 2004. Spatial study of juvenile
corals in the northern region of the mesoamerican barrier reef system
(mbrs). \emph{Coral Reefs}. (September, 9). DOI:
\href{https://doi.org/10.1007/s00338-004-0420-z}{10.1007/s00338-004-0420-z}.

\hypertarget{ref-sabidoitza_2016}{}
Sabido-Itza, M., Medina-Quej, A., De Jesus-Navarrete, A., Gomez-Poot, J.
\& Garcia-Rivas, M. 2016. Uso de la estructura de tallas como evidencia
del establecimiento poblacional del pez le?n pterois volitans
(scorpaeniformes: Scorpaenidae) en el sur del caribe mexicano.
\emph{RBT}. 64(1):353. DOI:
\href{https://doi.org/10.15517/rbt.v64i1.18943}{10.15517/rbt.v64i1.18943}.

\hypertarget{ref-sandel_2015}{}
Sandel, V., Mart\a'inez-Fern\a'andez, D., Wangpraseurt, D. \& Sierra, L.
2015. Ecology and management of the invasive lionfish pterois
volitans/miles complex (perciformes: Scorpaenidae) in southern costa
rica. \emph{Rev Biol Trop}. 63(1):213--221. Available:
\url{http://www.ncbi.nlm.nih.gov/pubmed/26299126} {[}2017, June 27{]}.

\hypertarget{ref-schofield_2009}{}
Schofield, P. 2009. Geographic extent and chronology of the invasion of
non-native lionfish (pterois volitans {[}linnaeus 1758{]} and p. miles
{[}bennett 1828{]}) in the western north atlantic and caribbean sea.
\emph{AI}. 4(3):473--479. DOI:
\href{https://doi.org/10.3391/ai.2009.4.3.5}{10.3391/ai.2009.4.3.5}.

\hypertarget{ref-schofield_2010}{}
Schofield, P. 2010. Update on geographic spread of invasive lionfishes
(pterois volitans {[}linnaeus, 1758{]} and p. miles {[}bennett, 1828{]})
in the western north atlantic ocean, caribbean sea and gulf of mexico.
\emph{AI}. 5(Supplement 1):S117--S122. DOI:
\href{https://doi.org/10.3391/ai.2010.5.S1.024}{10.3391/ai.2010.5.S1.024}.

\hypertarget{ref-tmap_2017}{}
Tennekes, M. 2017a. \emph{Tmap: Thematic maps}. ed. (nos.). Available:
\url{https://CRAN.R-project.org/package=tmap}.

\hypertarget{ref-tmaptools_2017}{}
Tennekes, M. 2017b. \emph{Tmaptools: Thematic map tools}. ed. (nos.).
Available: \url{https://CRAN.R-project.org/package=tmaptools}.

\hypertarget{ref-usseglio_2017}{}
Usseglio, P., Selwyn, J.D., Downey-Wall, A.M. \& Hogan, J.D. 2017.
Effectiveness of removals of the invasive lionfish: How many dives are
needed to deplete a reef? \emph{PeerJ}. 5:e3043. DOI:
\href{https://doi.org/10.7717/peerj.3043}{10.7717/peerj.3043}.

\hypertarget{ref-valdezmoreno_2012}{}
Valdez-Moreno, M., Quintal-Lizama, C., G\a'omez-Lozano, R. \&
Garc\a'ia-Rivas, M.D.C. 2012. Monitoring an alien invasion: DNA
barcoding and the identification of lionfish and their prey on coral
reefs of the mexican caribbean. \emph{PLoS ONE}. 7(6):e36636. DOI:
\href{https://doi.org/10.1371/journal.pone.0036636}{10.1371/journal.pone.0036636}.

\hypertarget{ref-villaseorderbez_2014}{}
Villaseñor-Derbez, J.C. \& Herrera-P\a'erez, R. 2014. Brief description
of prey selectivity and ontogenetic changes in the diet of the invasive
lionfish pterois volitans (actinopterygii, scorpaenidae) in the mexican
caribbean. \emph{PANAMJAS}. 9(2):131--135.

\hypertarget{ref-tidyverse_2017}{}
Wickham, H. 2017. \emph{Tidyverse: Easily install and load 'tidyverse'
packages}. ed. (nos.). Available:
\url{https://CRAN.R-project.org/package=tidyverse}.

\hypertarget{ref-knitr_2017}{}
Xie, Y. 2017. \emph{Knitr: A general-purpose package for dynamic report
generation in r}. ed. (nos.). Available: \url{http://yihui.name/knitr/}.

\hypertarget{ref-sandwich_2014}{}
Zeileis, A. 2004. Econometric computing with hc and hac covariance
matrix estimators. \emph{Journal of Statistical Software}. 11(10):1--17.
Available: \url{http://www.jstatsoft.org/v11/i10/}.

\hypertarget{ref-lmtest_2002}{}
Zeileis, A. \& Hothorn, T. 2002. Diagnostic checking in regression
relationships. \emph{R News}. 2(3):7--10. Available:
\url{https://CRAN.R-project.org/doc/Rnews/}.

\hypertarget{ref-kableExtra_2017}{}
Zhu, H. 2017. \emph{KableExtra: Construct complex table with 'kable' and
pipe syntax}. ed. (nos.). Available:
\url{https://CRAN.R-project.org/package=kableExtra}.

\clearpage

\clearpage

\section{Tables}\label{tables}

Table 1: Coordinates, minimum, maximum and mean depth (m), and number of
samples for each location.

\begin{tabular}{llllllr}
\toprule
Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth & n\\
\midrule
Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\\
Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\\
Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\\
Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\\
Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\\
\addlinespace
Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\\
Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\\
Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\\
Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\\
Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\\
Total &  &  & 5.7 & 38.1 & 18.6 & 109\\
\bottomrule
\end{tabular}

\clearpage

Table 2: Regression table for the linear model fit between
log10-transformed Total Weight (dependent variable) and Total Length
(independent variable). Numbers in parentheses next to coefficient
estimates indicate heteroskedastic-robust standard errors. The asterisks
(*) indicate the statistical significance. 95\% Confidence intervals are
provided for each parameter.

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & log10(TW) \\ 
\hline \\[-1.8ex] 
 c & $-$5.494 (0.083)$^{***}$ \\ 
  b & 3.235 (0.039)$^{***}$ \\ 
 \hline \\[-1.8ex] 
95\% CI for c & (-5.657--5.331) \\ 
85\% CI for b & (3.159-3.311) \\ 
F Statistic & 6928.67*** (df = 1; 107) \\ 
Observations & 109 \\ 
Adjusted R$^{2}$ & 0.976 \\ 
Residual Std. Error & 0.096 (df = 107) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\clearpage

Table 3: Summary of 13 allometric growth parameters available for
lionfish in the invaded range from eight peer-reviewed papers, Fishbase
(Froese \& Pauly, 2016), and this study. All parameters have been
adjusted to convert from millimeters to grams. n = Sample size, a =
scaling parameter for eq. 1, c = y-intercept for eq. 3, b = exponent or
slope for eq. 1 or eq. 3, respectively. The R\textsuperscript{2} column
indicates reported model fit. mDepth and MDepth indicate minimum and
maximum depths (m), respectively, at which organisms were sampled. The
Spear column indicates if the study collected organisms with pole
spears. An asterisk (*) indicates that some portion of organisms were
sampled with pole spears.

\begin{table}[!h]
\centering
\resizebox{\linewidth}{!}{\begin{tabular}{lllrrrllll}
\toprule
Reference & n & a & c & b & R2 & Sex & mDepth & MDepth & Spear\\
\midrule
Aguilar-Perera \& Quijano-Puerto, 2016 & Both & 472 & 0 & -5.5400 & 3.3000 & 0.95 & 5 & 20 & Yes\\
Aguilar-Perera \& Quijano-Puerto, 2016 & Female & 67 & 0 & -5.9300 & 3.4700 & 0.95 & 5 & 20 & Yes\\
Aguilar-Perera \& Quijano-Puerto, 2016 & Male & 59 & 0 & -5.3800 & 3.2300 & 0.95 & 5 & 20 & Yes\\
Sandel et al., 2015 & Both & 458 & 0 & -4.4400 & 2.8100 & - & - & - & Yes*\\
Chin et al 2016 & Both & 419 & 0 & -4.5600 & 2.8500 & 0.8715 & 18.3 & 18.3 & Yes\\
\addlinespace
Brbour et al 2011 & Both & 774 & 0 & -4.5391 & 2.8900 & - & 27 & 45 & Yes*\\
de Leon et al., 2013 & Both & 1450 & 0 & -4.6411 & 2.8900 & 0.96 & - & - & NA\\
Fogg et al., 2013 & Both & 582 & 0 & -5.8600 & 3.4349 & 0.99 & - & - & Yes*\\
Fogg et al., 2013 & Male & 119 & 0 & -5.5700 & 3.3100 & 0.97 & - & - & Yes*\\
Fogg et al., 2013 & Female & 115 & 0 & -5.1700 & 3.1437 & 0.94 & - & - & Yes*\\
\addlinespace
Edwards et al., 2014 & Both & 1887 & 0 & -5.5229 & 3.2400 & 0.97 & 15 & 30 & Yes*\\
Sabido-Itza et al., 2016 & Both & 2143 & 0 & -5.2828 & 3.1832 & 0.9907 & 0.5 & 57 & Yes*\\
Fishbase & Both & NA & 0 & -5.0293 & 3.0900 & - & - & - & NA\\
This study & Both & 109 & 0 & -5.4941 & 3.2347 & 0.9766 & 5.7 & 38.1 & No\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\section{Figures}\label{figures}

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Map of the study area. The black inset on the left (Yucatan
Peninsula) indicates the location where study sites are distributed. On
the right, circular markers indicate sampling sites and the black
romboid indicates location of Puerto Aventuras, Mexico.}
\end{figure}

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{Kernell density plots for a) Total length (mm) and b) Total
weight (gr) for 109 lionfish sampled in the central Mexican Caribbean.}
\end{figure}

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{Weight-at-length relationship for 109 lionfish sampled in the
central Mexican Caribbean. Points indicate samples, solid line indicates
curve of best fit.}
\end{figure}

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{Weight-at-length relationships (n = 14) for eight studies, this
study, and FishBase parameters. Colors indicate studies from which the
parameters were extracted. Solid lines indicate that the fit was
performed for males and females pooled together. Dotted lines indicate
that the regression was performed on females, and dashed lines indicate
it was performed for males.}
\end{figure}

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{. Box and whiskers plot showing the distribution of predicted
to observed biomass ratios for 14 pairs of allometric parameters. Lines
indicate median values, circles indicate mean values, notches represent
95\% confidence intervals arround the median, lower and upper hinges
correspond to the first and third quartiles, whiskers extend to the
largest and lowes values within 1.5 inter-quartile range of the hinge,
small points represent outliers further away than the whiskers.}
\end{figure}

\end{document}

### 2017-08-29 Manuscript.Rmd
Modified manuscript, included anova and tukeys HSD

@@
 ---
-title: \normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}
+title: \Large{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central
+  Mexican Caribbean, and a review of allometric growth parameters across the invasion range}
 fontsize: 12pt
@@
     keep_tex: yes
+  word_document:
+    fig_caption: yes
+    keep_md: yes
 header-includes:
@@
 - \linenumbers
+subtitle: '**Running title**: Allometric growth of Pterois volitans'
 bibliography:
@@
 
-options(knitr.table.format = "latex")
+# options(knitr.table.format = "latex")
 
@@
   library(e1071)
+  library(stringr)
+  library(agricolae)
+  library(magrittr)
   library(stargazer)
@@
 
-Juan Carlos Villaseñor-Derbez^1^
+Juan Carlos VILLASEÑOR-DERBEZ^1^
 
@@
 
-**Full postal address**   
-Bren Hall   
-University of California at Santa Barbara   
-Santa Barbara   
-CA, 93106
-
-**Corresponding author information:**   
-Juan Carlos Villaseñor-Derbez   
-Bren Hall   
-University of California at Santa Barbara   
-Santa Barbara   
-CA, 93106
-jvillasenor@bren.ucsb.edu
-+1 207 205 8435
-
-**Running title**    
-Allometric growth of Pterois volitans
+\* Correspondence: Juan Carlos Villaseñor-Derbez, Bren Hall, University of California at Santa Barbara, 
+Santa Barbara, CA, 93106, US phone: +1 207 205 8435, e-mail: jvillasenor@bren.ucsb.edu
 
@@
 
-**Title of contribution**: Biometry of the invasive lionfish (*Pterois volitans*) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range
+**Background.** Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean.
+In order to better manage the invasion, inform lionfish removal programs, predict their possible impacts, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass.
+Previous work has identified that lionfish age-at-length relationships are spatially variable across the invasion range.
+This work had two main objectives: i) compare length-weight relationships of the invasive lionfish through the invasion range; and ii) Report the length-weight frequency for lionfish in the Central Meixcan Caribbean.
 
-**Abstract**    
-Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms.
-Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion.
-In order to better manage the invasion, inform lionfish removal programs, predict their possible impacts, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass.
-This study reports allometric growth parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the central portion of the Mexican Caribbean.
-It also identifies that, for a given length, organisms from the Caribbean tend to have lower weights than those from the Gulf of Mexicoand Atlantic, indicating that weight-at-length is spacialy variable.
-In addition to the new pair of parameters provided in this study, other 13 pairs of allometric growth parameters were used to calculate expected biomass from total length observations.
-Mean expected-to-observed biomass ratios by study ranged between 0.98 and 1.75, with overall values ranging from 0.44 to 3.51.
-The large differences between observed and expected biomass when using parameters from other locations highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This becomes increasingly important when estimating biomass available for harvest or effectiveness of lionfish removal efforts.
-Additionally, guidelines on reporting allometric parameters are provided as a suggestion for future research are provided.
+**Materials and methods.** A total of 13 length-weight relationships reported in eight peer-reviewed studies and FishBase were used to calculate expected biomass of organisms (n = 109) sampled from the Central Mexican Caribbean, whose Total Length (TL) and Total Weight (TW) were known.
+For each length-weight relationship, expected-to-observed weight ratio was calculated for each organism.
+Differences in mean expected-to-observed weight ratios were tested with a one-way ANOVA; Tukey's HSD was used as a post-hoc test to identify groups of non-statistically significant differences.
+Additionally, the length-weight relationship of the 109 organisms was calculated.
+Total Length (TL) and Total weight (TW) were log10-transformed to fit a linear model describing the linearized length-weight relationship.
+The model was fit using Ordinary Least Squares and Heteroskedastik-robust standard errors were computed.
+
+**Results.** Expected-to-observed weight ratios ranged from 0.44 to 3.51, and dfferences in weight-at-length were spatially consistent.
+For a given length, parameters from the Caribbean yielded lower weights than those from the Gulf of Mexico and Atlantic, indicating that weight-at-length is spatially variable.
+This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean.
+
+**Conclusion.** The large differences between observed and expected biomass when using parameters from other locations highlights the importance of using site-specific parameters to estimate biomass from length observations.
+Findings from this work can aid managers and decision makers to better select length-weight parameters when these are not available for their region of interest.
 
@@
 
-**Resumen**   
-Los peces león (*Pterois volitans/miles*) son una especiei nvasora en el Atlántico Noroeste y el Caribe, probablemente introducidos por medio de la liberación de organismos de ornato.
-Dada la amenaza que estos representan para la biodiversidad local, la velocidad de su invasión y dificultad de manejo, su presencia ha sido catalogada como una importante invasión marina.
-Para manejar mejor la invasión, proveer información a los programas de remoción, predecir los posibles impactos y estimar biomasa disponible para la extracción, debemos ser capaces de estimar su biomasa con precisión.
-Este estudio presenta parámetros de crecimiento alométrico ($a = 3.2056\times 10^{-6}; b = 3.235$) para organismos muestreados en la porción central del Caribe Mexicano.
-También identifica que para una misma longitud, los organismos del Caribe tienden a ser menos pesados que aquellos del Golfo de México y Atlántico, indicando variaciones espaciales en la relación peso-longitud.
-Además de los parámetros descritos en este estudio, se utilizaron otros 13 pares de parámetros de crecimiento alométrico para estimar biomasa a partir de observaciones de talla.
-La razón entre biomasa observada y biomasa esperada varió, en promedio por estudio, entre 0.98 y 1.75, con valores extremos de 0.44 y 3.51.
-Las grandes diferencias entre biomasa observada y esperada al usar parámetros de otras regiones resalta la importancia de utilizar parámetros específicos a la zona para estimar biomasa a partir de observaciones de talla.
-Adicionalmente, se proveen sugerencias para estandarizar la manera en que los parámetros de crecimiento alométrico se reportan.
-
-**Palabras clave**
-pez león, Pterois volitans, relación longitud-peso, crecimiento alométrico, México
-
 \clearpage
 
-# Introduction
+# INTRODUCTION
 
@@
 
-# Materials and Methods
+\clearpage
+
+# MATERIALS AND METHODS
 
@@
 
-## Area of study
-
-The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean (**Fig.
+**Area of study.** The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean (**Fig.
 1**).
@@
 
-In the region, the reef profile has been described by @ariasgonzalez_1998, indicating that the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
-The reef becomes deeper, leading to the reef front often found at 700 m from the coastline end extends for an additional 300 m.
+The reef profile has been described by @ariasgonzalez_1998, indicating that the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
+The reef becomes deeper, leading to the reef front often found at 700 m from the coastline and extends for an additional 300 m.
 At approximately 1000 m away from shore and 30 - 40 m depth, the reef leads to a drop-off.
@@
 
-stat <- readOGR(dsn = "./Spatial", layer = "states", verbose = F)
-
-qroo <- readOGR(dsn = "./Spatial", layer = "muni_2015gw", verbose = F)
-
-qroo <-qroo[qroo$NOM_ENT == "Quintana Roo",]
+load("./Spatial/coastline_mx.Rda")
 
@@
 
-pen_map <- tm_shape(stat, bbox = bb(xlim = c(-89.29656, -86.71074), ylim = c(17.89399, 21.60525))) +
+pen_map <- tm_shape(baja2, bbox = bb(xlim = c(-89.29656, -86.71074), ylim = c(17.89399, 21.60525))) +
   tm_polygons() +
@@
 
-study_area <- tm_shape(qroo, bbox = bb(xlim = c(-87.30662, -87.19194), ylim = c(20.39283, 20.51278))) +
+study_area <- tm_shape(baja2, bbox = bb(xlim = c(-87.30662, -87.19194), ylim = c(20.39283, 20.51278))) +
   tm_polygons() +
@@
 
-## Fish sampling
-
-Organisms sampled by @villaseorderbez_2014 for stomach content analysis between May and August of 2010 were used in this work.
-A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along the coast (Fig.
+**Fish sampling.** A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along the coast in 2010 (Fig.
 1, Table 1).
@@
 All observed organisms (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevents any weight loss due to bleeding(when collected with spears), and increases the range of sizes that can be sampled, providing a representative sample of the population.
-Information on depth and other comments were recorded in an underwater slide.
-Depth was recorded by dive gauges held by divers as safety procedures during the collections.
-Samples were frozen within 30 minutes of completing the dive and stored for posterior analysis in the lab.
-For every organism Total Length (TL; mm) and Total Weight (TW; gr) were recorded in the lab.
+The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes, often ignored due to gear selectivity when spearing.
+Organisms were euthanized and frozen within 30 minutes of completing the dive and stored for posterior analysis.
+Total Length (TL; mm) and Total Weight (TW; gr) were recorded for all organisms.
 
@@
 
-## Data analysis
+**Data analysis.** The weight at length relationship between the observed variables is described by the allometric growth function:
 
-The weight at length relationship between the observed variables is described by the allometric growth function:
+$$TW = aTL^b$$
 
-\begin{equation}TW = aTL^b\end{equation}
+Where $TW$ is the Total Weight (gr), $TL$ is the Total Length (mm), $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
+When $b = 3$, it is said that the organism exhibits a perfect isometric growth.
+The dependent and independent variables were transformed via base-10 logarithms, thus the equation becomes:
 
-Where $TW$ is the Total Weight (gr), $TL$ is the observed Total Length (mm), $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
-When $b = 3$, it is said that the organism exhibits a perfect isometric growth.
-The dependent and independent variables were transformed via base-10 logarithms so that the equation is then:
+$$log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)$$
 
-\begin{equation}log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\end{equation}
+This can be simplified and re-written as:
 
-To simplify this equation, we can re-write it as:
-
-\begin{equation}Y = mX + c\end{equation}
+$$Y = mX + c$$
 
 Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$.
-Since $b == m$, we will only use $b$ throughout the paper for simplicity.
-The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard errors.
+Since $b = m$, we will only use $b$ throughout the paper for simplicity.
+The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction was performed.
 Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$).
@@
 
-Other allometric growth parameters were obtained from peer-reviewed literature.
-Parameters were obtained forNorth Carolina [@barbour_2011], Northern [@fogg_2013] and Southern Gulf of Mexico [@aguilarperera_2016], the Southern Mexican Caribbean [@sabidoitza_2016], Little Cayman [@edwards_2014], Jamaica [@chin_2016], Bonaire [@deleon_2013] and Costa Rica [@sandel_2015].
-Additionally, parameters from Fishbase [@froese_website_2016] were also included in this study.
+Other length-weight relationships (n = 13) were extracted from peer-reviewed literature.
+Parameters were obtained for North Carolina [n = 1; @barbour_2011], Northern [n = 3; @fogg_2013] and Southern Gulf of Mexico [n = 3; @aguilarperera_2016], the Southern Mexican Caribbean [n = 1; @sabidoitza_2016], Little Cayman [n = 1; @edwards_2014], Jamaica [n = 1; @chin_2016], Bonaire [n = 1; @deleon_2013] and Costa Rica [n = 1; @sandel_2015] and Fishbase [n = 1; @froese_website_2016] were also included.
 When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retrieved.
-Whenever gender was not specified, it was assumed that the results were presented for both genders pooled together.
-During the review process, it was noticed that some papers indistinctly use $a$ to report either the ponderal index in eq.
+Whenever gender was not specified, it was assumed that the results were presented for pooled genders.
+
+During the review process, some papers indistinctly used $a$ to report either the ponderal index in eq.
 1 or the y-intercept ($c$) in eq.
 3, which might sometimes be overlooked.
-Furthermore, some studies report their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicates that they were estimated as cm-to-gr conversions.
+Furthermore, some studies reported their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicated that they were estimated as cm-to-gr conversions.
 Here, all parameters are reported as TL(mm) to TW(gr) conversions.
-When required, values from other studies are transformed for consistency.
+When required, values from other studies were transformed for consistency.
 
-Since standard errors or confidence intervals were not provided for many studies, it was impossible to test for statistical differences across studies.
-Thus expected biomass for each organism was calculated with the growth parameters estimated in this study, as well as those retrieved from additional literature.
-All expected biomass values were divided by the observed biomass to obtain a ratio that allowed rapid identification of over- or underestimation with respect to the observed biomass.
-Therefore, values lower than 1 indicate that the parameters underestimate biomass, and values larger than 1 indicate overestimation.
-Median and mean expected to observed biomass ratios were calculated for each study.
+Since uncertainty arround estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships.
+Instead, the 13 length-weight relationships were usd to calculate expected weight for the organisms sampled in the Central Mexican Caribbean (n = 109).
+Expected weights were divided by the observed weights to obtain a ratio.
+Difference in mean weight ratios across studies were tested with a one-way Analysis of Variance (ANOVA).
 
-All hypothesis testing was performed with a confidence level of $\alpha = 0.01$ in R version 3.4.0 [@rcore_2017].
-Data wrangling was performed with the tidyverse package [@tidyverse_2017].
+All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 [@rcore_2017].
+Data wrangling was done with the tidyverse package [@tidyverse_2017].
 Maps were created with a mix of functions from the sp [@sp_2017], rgdal [@rgdal_2017], tmap [@tmap_2017], and tmaptools [@tmaptools_2017] packages.
-Calculation of heteroskedastic-robust standard errors was done with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
-Models were manipulated with with the broom package [@broom_2017].
-Stargazer [@stargazer_2015], knitr [@knitr_2017], and kableExtra [@kableExtra_2017] were used to produce the tables, and RefManageR [@RefManager_2014] was used to keep track of citations.
-The manuscript was written in r markdown [@rmarkdown_2017] and processed with the knitr package [@knitr_2017].
+Heteroskedastic-robust standard errors were calculated with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
+Models were manipulated with the broom package [@broom_2017].
+RefManageR [@RefManager_2014] was used to keep track of citations.
 Raw data and code used in this work is available at [github.com/jcvdav/lionfish_biometry](github.com/jcvdav/lionfish_biometry).
 
-# Results
+# RESULTS
 
@@
 Kernell density plots (Fig.
-2) show the distribution for TL and TW.
+2) show the distribution for TL and TW for all sampled organisms.
 Both measures were positively skewed, with skewness of `r formatC(skewness(fish$Length), digits = 2, format = "f")` for TL and `r formatC(skewness(fish$Weight), digits = 2, format = "f")` for TW.
@@
   labs(x = "Total Length (mm)", y = "Density") +
-  geom_text(label = "a)", x = 310, y = 0.007) +
+  geom_text(label = "A", x = 310, y = 0.007) +
   theme(text = element_text(family = "Times"))
@@
   labs(x = "Total weight (gr)", y = "Density") +
-  geom_text(label = "b)", x = 400, y = 0.017) +
+  geom_text(label = "B", x = 400, y = 0.017) +
   theme(text = element_text(family = "Times"))
@@
 ```
-
-## Length-weight relationship
 
@@
 
-The model adjusted to eq.
+**Length-weight relationship.** The model adjusted to eq.
 3 estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
-Thus, TW (gr) can be calculated from TL (mm) as a linear equation: $log_{10}(TW) = `r coef(model)[[2]]`\times log_{10}(TL) `r coef(model)[[1]]`$ or its exponential form: $TW = `r 10^coef(model)[[1]]`\times TL^{`r coef(model)[[2]]`}$.
+Thus, TW (gr) can be calculated from TL (mm) as a linear equation: $log_{10}(TW) = `r coef(model)[[2]]`\times log_{10}(TL) `r coef(model)[[1]]`$, or its exponential form: $TW = `r 10^coef(model)[[1]]`\times TL^{`r coef(model)[[2]]`}$.
 The intercept ($c$) and slope $(b)$ were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
-Additionally, the allometric factor ($m = b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$), indicating that lionfish present allometric growth.
+Additionally, the allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$), indicating that lionfish present allometric growth.
 More information on model fit and confidence intervals for the estimated coefficients is presented in Table 2.
@@
   theme_bw() +
-  labs(x = "Total length (mm)", y = "Total Weight (g)") +
+  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
   theme(text = element_text(family = "Times")) +
@@
 
-## Comparison of allometric parameters
-
 ```{r, include = F}
@@
 
+my.df <- data.frame(Study = unique(review$Study), Reference_no = seq(1 : length(unique(review$Study))), stringsAsFactors = F)
+
 review_table <- review %>% 
-  select(Reference = Study, Sex = Gender, n = N, a, c, b, r2, minD, maxD, Spear) %>% 
+  left_join(my.df, by = "Study") %>% 
+  select(Reference = Reference_no, Region = Study_site, Sex = Gender, n = N, a, c, b, r2, minD, maxD, Spear) %>% 
   mutate(r2 = ifelse(is.na(r2), "-", r2),
@@
          maxD = ifelse(is.na(maxD), "-", maxD)) %>% 
-  knitr::kable(row.names = F,
+  knitr::kable(format = "latex",
+               row.names = F,
                digits =  c(1, 0, 6, 4, 4, 4, 0, 1, 1),
                booktabs = T,
-               col.names = c("Reference", "n", "a", "c", "b", "R2", "Sex", "mDepth", "MDepth", "Spear")) %>% 
+               col.names = c("Reference", "Region", "Sex", "a", "c", "b", "R2", "n", "mDepth", "MDepth", "Spear")) %>% 
   kableExtra::kable_styling(latex_options = c("scale_down"))
@@
 
-From the eight peer-reviewed studies including information on growth parameters for *P.
+**Comparison of allometric parameters.** From the eight peer-reviewed studies including information on growth parameters for *P.
 volitans* and Fishbase [@froese_website_2016], `r dim(review)[1]-1` parameters were identified (Table 3).
-Two studies [@aguilarperera_2016; @fogg_2013] reported gender-level and pooled parameters, while the rest of the studies always presented pooled results.
-The smallest coefficient of determination was presented by @chin_2016 with $R^2 = `r min(review[,12], na.rm = T)`$, while @sabidoitza_2016 reported the highest value at $R^2 = `r max(review[,12], na.rm = T)`$.
-These studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
+Two studies [@aguilarperera_2016; @fogg_2013] reported gender-level and pooled parameters, while the rest presented pooled results.
+The smallest coefficient of determination was presented by @chin_2016 with $R^2 = `r min(review[,13], na.rm = T)`$, while @sabidoitza_2016 reported the highest value at $R^2 = `r max(review[,13], na.rm = T)`$.
+Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
 Two studies [@aguilarperera_2016; @chin_2016] explicitly stated that their organisms were sampled with pole spears.
 Five studies [@sandel_2015; @barbour_2011; @fogg_2013; @edwards_2014; @sabidoitza_2016] mentioned that some of their organisms were obtained with pole spears (or other type of harpoon).
-A single study [@deleon_2013] did not specify how samples were obtained.
+A single study [@deleon_2013] did not specify how organisms were sampled.
 
-Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ males and females respectively, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
+Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
 In the case of the ponderal index ($a$) and its $log_{10}$ transformed parameter ($c$), values were higher for parameters for pooled genders.
@@
   theme_bw() +
-  labs(x = "Total length (mm)", y = "Total Weight (g)") +
+  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
   theme(text = element_text(family = "Times"),
@@
   left_join(review, by ="Study_id")
+
+anova <- aov(Biomass_ratio ~ Study_id, Predicted_biomass)
+groups <- HSD.test(y = anova, trt = "Study_id")
+
+groups$groups$Study_id <- str_replace_all(as.character(groups$groups$trt), " ", "")
+
+Predicted_biomass %<>% 
+  left_join(groups$groups, by = "Study_id")
+
 ```
 
-From all allometric parameters reviewed, those of @edwards_2014 slightly underestimated the observed biomass, with median (`r filter(Predicted_biomass, Study_id == "Edwards") %$% median(Biomass_ratio) %>% formatC(digits = 2, format = "f")`) and mean (`r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")`) bellow one.
-There is no significance in comparing the parameters estimated in this study since, by definition, they are the pair of parameters for which residual sum of squares was minimized with values of median =`r filter(Predicted_biomass, Study_id == "This") %$% median(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and mean =`r filter(Predicted_biomass, Study_id == "This") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
-For all the other studies, the 95% confidence interval around the mean fell further away from a value of 1, indicating overestimation.
-Predicted to observed biomass ratios are presented in Figure 5.
+There were significant differences in expected-to-observed weight ratios estimated for each pair of parameters (F(13, 1512) = 39.28; p < 0.05).
+From all allometric parameters reviewed, those of @edwards_2014 provided the lowest weight estimates, with an expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
+On the other hand, @barbour_2011 yielded the highest weight estimates, with a mean ($\pm$ SD) expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
+Predicted-to-observed weight ratios and groups identified by Tukey's HSD ($\alpha = 0.05$) are presented in Figure 5.
 
@@
         legend.justification=c(1,1),
-        legend.position=c(0.99, 0.99),
-        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted"))
+        legend.position=c(0.9, 0.99),
+        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted")) +
+  geom_text(aes(y = 3.6, label = M), family = "Times", fontface = "plain") +
+  scale_y_continuous(limits = c(NA, 3.6))
 
@@
 
-# Discussion
+# DISCUSSION
 
@@
 By using hand nets instead of spears, we are able to sample a wider range of sizes often ignored by pole spear samples, allowing us to include smaller organisms.
-Estimating parameters by including smaller organisms ensures better estimatio of weight for smaller sizes.
+Estimating parameters by including smaller organisms ensures better estimation of weight for smaller sizes.
 This is especially important when biomass is calculated from visual census, where small organisms can be registered.
-Thus, this study is the first to provide allometric growth parameters for lionfish in the central region of the Mexican Caribbean and increases certainty in weight estimation of small organisms.
+Thus, this study also increases certainty in weight estimation of small organisms.
 
-The parameters estimated in this study were within the range of studies in other regions [@barbour_2011; @fogg_2013; @aguilarperera_2016; @sabidoitza_2016; @edwards_2014; @chin_2016; @deleon_2013; @sandel_2015].
-As compared to other parameters, the ones presented here tend to provide lower weight estimates for a same length.
-Until about TL = 200 mm, there are no appreciable differences between the parameters described in this study and those for little Cayman [@edwards_2014] and Jamaica [@chin_2016].
+The length-weight coefficients estimated in this study were within the range identified by studies in other regions [@barbour_2011; @fogg_2013; @aguilarperera_2016; @sabidoitza_2016; @edwards_2014; @chin_2016; @deleon_2013; @sandel_2015].
+However, the ones presented here provide lower weight estimates for a same length.
+Until about TL = 200 mm, there are no appreciable differences between the parameters for organisms from the Mexican Caribbean and those for little Cayman [@edwards_2014] and Jamaica [@chin_2016].
 Yet, for larger organisms (TL > 270 mm) parameters from Costa Rica [@sandel_2015] and Bonaire [@deleon_2013] provide similar estimates to those from this study.
-Conversely, these same studies tend to overestimate weight -as compared to the ones reported here- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
+Conversely, these same studies tend to estimate higher weights ---as compared to the ones reported here--- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
 When ever possible, future works should consider the use of hand nets to obtain the samples not only for studies on weight-at-length, but also diet, behavior and life history, where length can be an important factor.
@@
 Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic [@barbour_2011; @fogg_2013; @aguilarperera_2016; @sabidoitza_2016] tend to be higher than those from the Caribbean [@edwards_2014; @chin_2016; @deleon_2013; @sandel_2015], except for the ones from Xcalak National Park, Mexico [@sabidoitza_2016].
-This indicates that there are differences between lionfish across the invasion range, pattern that has also been reported for age and growth parameters [@fogg_2015].
+This indicates that there are differences between lionfish across the invasion range.
+Similar regional variation exist for age-at-length relationships of lionfish [@fogg_2015].
 These differences can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
@@
 Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results.
-At the same time, this highlights the need for more basic research.
-To have a better invasion management, we must perform research that can describe biologically important information of lionfish throughout its invasion range [@johnson_2016].
+At the same time, this highlights the need for more basic research that furthers our understanding of lionfish biology.
+To better manageme the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range [@johnson_2016].
 
@@
 Sometimes, they were even mislabeled and yielded senseless results when using the suggested conversion equation.
-On some others, parameters were said to be reported for mm to gr conversions, when they were actually reported as cm to gr conversions.
-Perhaps these minor discrepancies can be easily solved by any researcher, but why should they exist in the first place?
+On other cases, parameters were said to be reported for mm-to-gr conversions, when they were actually reported as cm-to-gr conversions.
+Perhaps these minor discrepancies can be easily solved by the trained eye, but why should they exist in the first place?
 It is important that we report our information in a standard way, making it readily available for other researchers and managers.
@@
 Be explicit in the methods section.
-What may seem obvious to you as an author -because you have been deeply immersed throughout the process- may not be clear to the reader.
+What may seem obvious to you as an author ---because you have been deeply immersed throughout the process--- may not be clear to the reader.
 Specify any transformation performed on the data.
@@
 Specify the equation for which parameters are presented by including an explicit example with the parameters substituted into it, as done by some of the papers reviewed [@chin_2016; @sandel_2015; @deleon_2013; @sabidoitza_2016].
-If possible, present the parameters in their exponential (eq.
+If possible, present the relationship in their exponential (eq.
 1) and linear (eq.
@@
 Report standard errors and/or confidence intervals around the obtained estimates.
-Given that small changes in $a$, $c$,  and $b$ can result in important changes in estimated weight, it is important that we report uncertainty around each parameter and not just general model fit and significance.
+Given that small changes in $a$, $c$, and $b$ can result in important changes in estimated weight, it is important that we report uncertainty around each parameter and not just general model fit and coefficient significance.
 Reporting uncertainty around parameters allows researchers and managers to include upper and lower bounds in their predictions.
@@
 5.
-Make your data -and code- available.
+Make your data and code available.
 Even if this is not requited by the journal or publisher, you can use free cloud data storage services or third-party repositories to make your research accessible to others.
-Resources will always be limited and budget will never be enough.
+Resources will always be limited and budget will rarely be enough.
 It is important that we take advantage of open science tools that promote the advancement of knowledge and foster collaboration.
-Ultimately, this promotes transparency allows replicability of research and advances science.
+Ultimately, this promotes transparency, allows replicability of research, and advances science.
 
-As final conclusion statements 1) A new pair of allometric growth parameters are provided for lionfish from the central Mexican Caribbean, where they exhibit different weight-at-length, as compared to other regions.
-2) Given the differences in weight-at-length patterns through the invasion range, it is important to use site-specific parameters.
-3) When possible, collect organisms with hand nets to obtain a representative sample of the population that includes small organisms.
-4) Report allometric parameters (and other life history parameters) in a way that is readily available for non-experts, and make your research available to advance science.
+This study provides a new pair of allometric growth parameters for lionfish from the central Mexican Caribbean, where they exhibit different weight-at-length.
+Furthermore, regional differences in length-weight relationships were identified, highlighting the importance of using site-specific parameters.
 
-# Aknowledgements
+# AKNOWLEDGEMENTES
 
@@
 
-\clearpage
-
-# References
+# REFERENCES
 
@@
 
-\clearpage
-
-# Tables
+# TABLES
 
@@
 An asterisk (\*) indicates that some portion of organisms were sampled with pole spears.
+1 = @aguilarperera_2016, 2 = @sandel_2015, 3 = @chin_2016, 4 = @barbour_2011, 5 = @deleon_2013, 6 = @fogg_2013, 7 = @edwards_2014, 8 = @sabidoitza_2016, 9 = @froese_website_2016, 10 = This study.
 
@@
 
-```{r, fig.cap = "Weight-at-length relationship for 109 lionfish sampled in the central Mexican Caribbean. Points indicate samples, solid line indicates curve of best fit."}
+```{r, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
+Points indicate samples, solid line indicates curve of best fit."}
 plot_fit_this_study
@@
 
-```{r, fig.height = 4.5, fig.width = 6, fig.cap = "Weight-at-length relationships (n = 14) for eight studies, this study, and FishBase parameters.
+```{r, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationships (n = 14) for eight studies, this study, and Fishbase.
 Colors indicate studies from which the parameters were extracted.
@@
 
-```{r, fig.cap = ".
+```{r, fig.height = 4.5, fig.width = 6, fig.cap = ".
 Box and whiskers plot showing the distribution of predicted to observed biomass ratios for 14 pairs of allometric parameters.
-Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers."}
+Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers.
+Like letters indicate values that do not differ significantly (Tukey's HSD; p < 0.05)."}
 Predicted_biomass_plot

### 2017-08-29 Manuscript.tex
Modified manuscript, included anova and tukeys HSD

@@
 \urlstyle{same}  % don't use monospace font for urls
+\usepackage{longtable,booktabs}
 \usepackage{graphicx,grffile}
@@
 \setlength{\droptitle}{-2em}
-  \title{\normalsize{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
+  \title{\Large{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
   \pretitle{\vspace{\droptitle}\centering\huge}
   \posttitle{\par}
+\subtitle{\textbf{Running title}: Allometric growth of Pterois volitans}
   \author{}
@@
 
-Juan Carlos Villaseñor-Derbez\textsuperscript{1}
+Juan Carlos VILLASEÑOR-DERBEZ\textsuperscript{1}
 
@@
 
-\textbf{Full postal address}\\
-Bren Hall\\
-University of California at Santa Barbara\\
-Santa Barbara\\
-CA, 93106
-
-\textbf{Corresponding author information:}\\
-Juan Carlos Villaseñor-Derbez\\
-Bren Hall\\
-University of California at Santa Barbara\\
-Santa Barbara\\
-CA, 93106
+* Correspondence: Juan Carlos Villaseñor-Derbez, Bren Hall, University
+of California at Santa Barbara, Santa Barbara, CA, 93106, US phone: +1
+207 205 8435, e-mail:
 \href{mailto:jvillasenor@bren.ucsb.edu}{\nolinkurl{jvillasenor@bren.ucsb.edu}}
-+1 207 205 8435
-
-\textbf{Running title}\\
-Allometric growth of Pterois volitans
 
@@
 
-\textbf{Title of contribution}: Biometry of the invasive lionfish
-(\emph{Pterois volitans}) in the Central Mexican Caribbean, and a review
-of allometric growth parameters across the invasion range
-
-\textbf{Abstract}\\
-Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
-North-Western Atlantic and the Caribbean, likely introduced through
-liberation of aquarium-kept organisms. Due to its threat to local
-biodiversity, the speed of their spread, and its difficulty of
-management, their presence in these waters has been labeled as a major
-marine invasion. In order to better manage the invasion, inform lionfish
-removal programs, predict their possible impacts, and estimate biomass
-available for harvest, we must be able to accurately estimate their
-total biomass. This study reports allometric growth parameters
+\textbf{Background.} Lionfish (\emph{Pterois volitans/miles}) are an
+invasive species in the North-Western Atlantic and the Caribbean. In
+order to better manage the invasion, inform lionfish removal programs,
+predict their possible impacts, and estimate biomass available for
+harvest, we must be able to accurately estimate their total biomass.
+Previous work has identified that lionfish age-at-length relationships
+are spatially variable across the invasion range. This work had two main
+objectives: i) compare length-weight relationships of the invasive
+lionfish through the invasion range; and ii) Report the length-weight
+frequency for lionfish in the Central Meixcan Caribbean.
+
+\textbf{Materials and methods.} A total of 13 length-weight
+relationships reported in eight peer-reviewed studies and FishBase were
+used to calculate expected biomass of organisms (n = 109) sampled from
+the Central Mexican Caribbean, whose Total Length (TL) and Total Weight
+(TW) were known. For each length-weight relationship,
+expected-to-observed weight ratio was calculated for each organism.
+Differences in mean expected-to-observed weight ratios were tested with
+a one-way ANOVA; Tukey's HSD was used as a post-hoc test to identify
+groups of non-statistically significant differences. Additionally, the
+length-weight relationship of the 109 organisms was calculated. Total
+Length (TL) and Total weight (TW) were log10-transformed to fit a linear
+model describing the linearized length-weight relationship. The model
+was fit using Ordinary Least Squares and Heteroskedastik-robust standard
+errors were computed.
+
+\textbf{Results.} Expected-to-observed weight ratios ranged from 0.44 to
+3.51, and dfferences in weight-at-length were spatially consistent. For
+a given length, parameters from the Caribbean yielded lower weights than
+those from the Gulf of Mexico and Atlantic, indicating that
+weight-at-length is spatially variable. This study also reports a new
+pair of length-weight parameters
 (\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
-central portion of the Mexican Caribbean. It also identifies that, for a
-given length, organisms from the Caribbean tend to have lower weights
-than those from the Gulf of Mexicoand Atlantic, indicating that
-weight-at-length is spacialy variable. In addition to the new pair of
-parameters provided in this study, other 13 pairs of allometric growth
-parameters were used to calculate expected biomass from total length
-observations. Mean expected-to-observed biomass ratios by study ranged
-between 0.98 and 1.75, with overall values ranging from 0.44 to 3.51.
-The large differences between observed and expected biomass when using
-parameters from other locations highlights the importance of using
-site-specific parameters to estimate biomass from length observations.
-This becomes increasingly important when estimating biomass available
-for harvest or effectiveness of lionfish removal efforts. Additionally,
-guidelines on reporting allometric parameters are provided as a
-suggestion for future research are provided.
+Central Mexican Caribbean.
+
+\textbf{Conclusion.} The large differences between observed and expected
+biomass when using parameters from other locations highlights the
+importance of using site-specific parameters to estimate biomass from
+length observations. Findings from this work can aid managers and
+decision makers to better select length-weight parameters when these are
+not available for their region of interest.
 
@@
 
-\textbf{Resumen}\\
-Los peces león (\emph{Pterois volitans/miles}) son una especiei nvasora
-en el Atlántico Noroeste y el Caribe, probablemente introducidos por
-medio de la liberación de organismos de ornato. Dada la amenaza que
-estos representan para la biodiversidad local, la velocidad de su
-invasión y dificultad de manejo, su presencia ha sido catalogada como
-una importante invasión marina. Para manejar mejor la invasión, proveer
-información a los programas de remoción, predecir los posibles impactos
-y estimar biomasa disponible para la extracción, debemos ser capaces de
-estimar su biomasa con precisión. Este estudio presenta parámetros de
-crecimiento alométrico (\(a = 3.2056\times 10^{-6}; b = 3.235\)) para
-organismos muestreados en la porción central del Caribe Mexicano.
-También identifica que para una misma longitud, los organismos del
-Caribe tienden a ser menos pesados que aquellos del Golfo de México y
-Atlántico, indicando variaciones espaciales en la relación
-peso-longitud. Además de los parámetros descritos en este estudio, se
-utilizaron otros 13 pares de parámetros de crecimiento alométrico para
-estimar biomasa a partir de observaciones de talla. La razón entre
-biomasa observada y biomasa esperada varió, en promedio por estudio,
-entre 0.98 y 1.75, con valores extremos de 0.44 y 3.51. Las grandes
-diferencias entre biomasa observada y esperada al usar parámetros de
-otras regiones resalta la importancia de utilizar parámetros específicos
-a la zona para estimar biomasa a partir de observaciones de talla.
-Adicionalmente, se proveen sugerencias para estandarizar la manera en
-que los parámetros de crecimiento alométrico se reportan.
-
-\textbf{Palabras clave} pez león, Pterois volitans, relación
-longitud-peso, crecimiento alométrico, México
-
 \clearpage
 
-\section{Introduction}\label{introduction}
+\section{INTRODUCTION}\label{introduction}
 
@@
 
-\section{Materials and Methods}\label{materials-and-methods}
-
-\subsection{Area of study}\label{area-of-study}
-
-The study took place off the coasts of Playa del Carmen, in the Mexican
-Caribbean (\textbf{Fig. 1}). The region represents the northernmost
-section of the Mesoamerican Barrier Reef System (Ruiz-Zarate \&
-Arias-Gonzalez, 2004). Coral reefs and mangroves are locally important
-habitats that represent important sources of income in terms of
-extractive (\emph{e.g.} recreational fishing) and non-extractive
-(\emph{e.g.} SCUBA diving) activities related to tourism, the main
-source of income to the local economy (Murray, 2007).
-
-In the region, the reef profile has been described by Arias-Gonzalez
-(1998), indicating that the reef lagoon extends about 500 m from the
-coast, until the reef crest is reached. The reef becomes deeper, leading
-to the reef front often found at 700 m from the coastline end extends
-for an additional 300 m. At approximately 1000 m away from shore and 30
-- 40 m depth, the reef leads to a drop-off. Along a perpendicular
-profile to the coast, bands of reef are interrupted by sand patches at 8
-- 12 m deep and 16-18 m deep. Along the coast, these reefs have been
-reported to be under significant anthropogenic pressure, likely causing
-a shift in structure and function (Bozec et al., 2008).
-
-\subsection{Fish sampling}\label{fish-sampling}
-
-Organisms sampled by Villaseñor-Derbez \& Herrera-P\a'erez (2014) for
-stomach content analysis between May and August of 2010 were used in
-this work. A total of 33 SCUBA immersions were performed in 10 sampling
-sites along the coast (Fig. 1, Table 1). Sampling locations included
-wall and carpet reefs at depths between 5.7 m and 38.1 m. All observed
-organisms (n = 109) were collected using hand nets and numbered
-collection bottles. The use of hand nets prevents any weight loss due to
-bleeding(when collected with spears), and increases the range of sizes
-that can be sampled, providing a representative sample of the
-population. Information on depth and other comments were recorded in an
-underwater slide. Depth was recorded by dive gauges held by divers as
-safety procedures during the collections. Samples were frozen within 30
-minutes of completing the dive and stored for posterior analysis in the
-lab. For every organism Total Length (TL; mm) and Total Weight (TW; gr)
-were recorded in the lab.
-
-\subsection{Data analysis}\label{data-analysis}
-
-The weight at length relationship between the observed variables is
-described by the allometric growth function:
-
-\begin{equation}TW = aTL^b\end{equation}
-
-Where \(TW\) is the Total Weight (gr), \(TL\) is the observed Total
-Length (mm), \(a\) is the ponderal index and \(b\) is the scaling
-exponent or allometric parameter. When \(b = 3\), it is said that the
-organism exhibits a perfect isometric growth. The dependent and
-independent variables were transformed via base-10 logarithms so that
-the equation is then:
-
-\begin{equation}log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\end{equation}
-
-To simplify this equation, we can re-write it as:
-
-\begin{equation}Y = mX + c\end{equation}
+\clearpage
+
+\section{MATERIALS AND METHODS}\label{materials-and-methods}
+
+\textbf{Area of study.} The study took place off the coasts of Playa del
+Carmen, in the Mexican Caribbean (\textbf{Fig. 1}). The region
+represents the northernmost section of the Mesoamerican Barrier Reef
+System (Ruiz-Zarate \& Arias-Gonzalez, 2004). Coral reefs and mangroves
+are locally important habitats that represent important sources of
+income in terms of extractive (\emph{e.g.} recreational fishing) and
+non-extractive (\emph{e.g.} SCUBA diving) activities related to tourism,
+the main source of income to the local economy (Murray, 2007).
+
+The reef profile has been described by Arias-Gonzalez (1998), indicating
+that the reef lagoon extends about 500 m from the coast, until the reef
+crest is reached. The reef becomes deeper, leading to the reef front
+often found at 700 m from the coastline and extends for an additional
+300 m. At approximately 1000 m away from shore and 30 - 40 m depth, the
+reef leads to a drop-off. Along a perpendicular profile to the coast,
+bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18
+m deep. Along the coast, these reefs have been reported to be under
+significant anthropogenic pressure, likely causing a shift in structure
+and function (Bozec et al., 2008).
+
+\textbf{Fish sampling.} A total of 33 SCUBA immersions were performed in
+10 sampling sites along the coast in 2010 (Fig. 1, Table 1). Sampling
+locations included wall and carpet reefs at depths between 5.7 m and
+38.1 m. All observed organisms (n = 109) were collected using hand nets
+and numbered collection bottles. The use of hand nets prevented any
+weight loss due to bleeding and allowed a better representation of small
+sizes, often ignored due to gear selectivity when spearing. Organisms
+were euthanized and frozen within 30 minutes of completing the dive and
+stored for posterior analysis. Total Length (TL; mm) and Total Weight
+(TW; gr) were recorded for all organisms.
+
+\textbf{Data analysis.} The weight at length relationship between the
+observed variables is described by the allometric growth function:
+
+\[TW = aTL^b\]
+
+Where \(TW\) is the Total Weight (gr), \(TL\) is the Total Length (mm),
+\(a\) is the ponderal index and \(b\) is the scaling exponent or
+allometric parameter. When \(b = 3\), it is said that the organism
+exhibits a perfect isometric growth. The dependent and independent
+variables were transformed via base-10 logarithms, thus the equation
+becomes:
+
+\[log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\]
+
+This can be simplified and re-written as:
+
+\[Y = mX + c\]
 
 Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), \(m = b\), and
-\(c = log_{10}(a)\). Since \(b == m\), we will only use \(b\) throughout
+\(c = log_{10}(a)\). Since \(b = m\), we will only use \(b\) throughout
 the paper for simplicity. The coefficients (\(c\) and \(b\)) were
 estimated with an Ordinary Least Square Regression and
-heteroskedastic-robust standard errors. Both coefficients were tested
-against the null hypothesis of no change (\emph{i.e.} \(H_0: c = 0\) and
-\(H_0: b = 0\)). Additionally, the allometric parameter was tested
-against the null hypothesis of isometric growth (\(H_0: b = 3\)).
-Coefficients were tested with a two-tailed Student's t-test. The
-significance of the regression was corroborated with an F-test.
-
-Other allometric growth parameters were obtained from peer-reviewed
-literature. Parameters were obtained forNorth Carolina (Barbour et al.,
-2011), Northern (Fogg et al., 2013) and Southern Gulf of Mexico
-(Aguilar-Perera \& Quijano-Puerto, 2016), the Southern Mexican Caribbean
-(Sabido-Itza et al., 2016), Little Cayman (Edwards, Frazer \& Jacoby,
-2014), Jamaica (Chin, Aiken \& Buddo, 2016), Bonaire (de Leon et al.,
-2013) and Costa Rica (Sandel et al., 2015). Additionally, parameters
-from Fishbase (Froese \& Pauly, 2016) were also included in this study.
-When available, information on sampling methods, gender differentiation,
-location, and depth ranges of each study was retrieved. Whenever gender
-was not specified, it was assumed that the results were presented for
-both genders pooled together. During the review process, it was noticed
-that some papers indistinctly use \(a\) to report either the ponderal
-index in eq. 1 or the y-intercept (\(c\)) in eq. 3, which might
-sometimes be overlooked. Furthermore, some studies report their
-parameters as mm-to-gr conversions, but a rapid evaluation of such
-parameters indicates that they were estimated as cm-to-gr conversions.
+heteroskedastic-robust standard error correction was performed. Both
+coefficients were tested against the null hypothesis of no change
+(\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)). Additionally, the
+allometric parameter was tested against the null hypothesis of isometric
+growth (\(H_0: b = 3\)). Coefficients were tested with a two-tailed
+Student's t-test. The significance of the regression was corroborated
+with an F-test.
+
+Other length-weight relationships (n = 13) were extracted from
+peer-reviewed literature. Parameters were obtained for North Carolina (n
+= 1; Barbour et al., 2011), Northern (n = 3; Fogg et al., 2013) and
+Southern Gulf of Mexico (n = 3; Aguilar-Perera \& Quijano-Puerto, 2016),
+the Southern Mexican Caribbean (n = 1; Sabido-Itza et al., 2016), Little
+Cayman (n = 1; Edwards, Frazer \& Jacoby, 2014), Jamaica (n = 1; Chin,
+Aiken \& Buddo, 2016), Bonaire (n = 1; de Leon et al., 2013) and Costa
+Rica (n = 1; Sandel et al., 2015) and Fishbase (n = 1; Froese \& Pauly,
+2016) were also included. When available, information on sampling
+methods, gender differentiation, location, and depth ranges of each
+study was retrieved. Whenever gender was not specified, it was assumed
+that the results were presented for pooled genders.
+
+During the review process, some papers indistinctly used \(a\) to report
+either the ponderal index in eq. 1 or the y-intercept (\(c\)) in eq. 3,
+which might sometimes be overlooked. Furthermore, some studies reported
+their parameters as mm-to-gr conversions, but a rapid evaluation of such
+parameters indicated that they were estimated as cm-to-gr conversions.
 Here, all parameters are reported as TL(mm) to TW(gr) conversions. When
-required, values from other studies are transformed for consistency.
-
-Since standard errors or confidence intervals were not provided for many
-studies, it was impossible to test for statistical differences across
-studies. Thus expected biomass for each organism was calculated with the
-growth parameters estimated in this study, as well as those retrieved
-from additional literature. All expected biomass values were divided by
-the observed biomass to obtain a ratio that allowed rapid identification
-of over- or underestimation with respect to the observed biomass.
-Therefore, values lower than 1 indicate that the parameters
-underestimate biomass, and values larger than 1 indicate overestimation.
-Median and mean expected to observed biomass ratios were calculated for
-each study.
-
-All hypothesis testing was performed with a confidence level of
-\(\alpha = 0.01\) in R version 3.4.0 (R Core Team, 2017). Data wrangling
-was performed with the tidyverse package (Wickham, 2017). Maps were
+required, values from other studies were transformed for consistency.
+
+Since uncertainty arround estimated relationships was not reported in
+some of the reviewed studies, it was not possible to test for
+statistical differences between relationships. Instead, the 13
+length-weight relationships were usd to calculate expected weight for
+the organisms sampled in the Central Mexican Caribbean (n = 109).
+Expected weights were divided by the observed weights to obtain a ratio.
+Difference in mean weight ratios across studies were tested with a
+one-way Analysis of Variance (ANOVA).
+
+All hypothesis testing was performed with an \emph{a priori} confidence
+level of \(\alpha = 0.01\) in R version 3.4.0 (R Core Team, 2017). Data
+wrangling was done with the tidyverse package (Wickham, 2017). Maps were
 created with a mix of functions from the sp (Pebesma \& Bivand, 2005),
 rgdal (Bivand, Keitt \& Rowlingson, 2017), tmap (Tennekes, 2017a), and
-tmaptools (Tennekes, 2017b) packages. Calculation of
-heteroskedastic-robust standard errors was done with the sandwich
-(Zeileis, 2004) and lmtest (Zeileis \& Hothorn, 2002) packages. Models
-were manipulated with with the broom package (Robinson, 2017). Stargazer
-(Hlavac, 2015), knitr (Xie, 2017), and kableExtra (Zhu, 2017) were used
-to produce the tables, and RefManageR (McLean, 2014) was used to keep
-track of citations. The manuscript was written in r markdown (Allaire et
-al., 2017) and processed with the knitr package (Xie, 2017). Raw data
-and code used in this work is available at
-\url{github.com/jcvdav/lionfish_biometry}.
-
-\section{Results}\label{results}
+tmaptools (Tennekes, 2017b) packages. Heteroskedastic-robust standard
+errors were calculated with the sandwich (Zeileis, 2004) and lmtest
+(Zeileis \& Hothorn, 2002) packages. Models were manipulated with the
+broom package (Robinson, 2017). RefManageR (McLean, 2014) was used to
+keep track of citations. Raw data and code used in this work is
+available at \url{github.com/jcvdav/lionfish_biometry}.
+
+\section{RESULTS}\label{results}
 
@@
 gr) was 292.00 mm in total length. Kernell density plots (Fig. 2) show
-the distribution for TL and TW. Both measures were positively skewed,
-with skewness of 0.85 for TL and 2.19 for TW.
-
-\subsection{Length-weight
-relationship}\label{length-weight-relationship}
-
-The model adjusted to eq. 3 estimated the coefficient values at
-\(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
-calculated from TL (mm) as a linear equation:
-\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\) or its
+the distribution for TL and TW for all sampled organisms. Both measures
+were positively skewed, with skewness of 0.87 for TL and 2.25 for TW.
+
+\textbf{Length-weight relationship.} The model adjusted to eq. 3
+estimated the coefficient values at \(b = 3.2347391\) and
+\(c = -5.4940866\). Thus, TW (gr) can be calculated from TL (mm) as a
+linear equation:
+\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
 exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
@@
 respectively), rejecting the null hypothesis of no change. Additionally,
-the allometric factor (\(m = b\)) was significantly different from the
-value of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)),
-indicating that lionfish present allometric growth. More information on
-model fit and confidence intervals for the estimated coefficients is
-presented in Table 2. The relationship between Total Length and Total
-Weight is presented in Figure 3.
-
-\subsection{Comparison of allometric
-parameters}\label{comparison-of-allometric-parameters}
-
-From the eight peer-reviewed studies including information on growth
-parameters for \emph{P. volitans} and Fishbase (Froese \& Pauly, 2016),
-13 parameters were identified (Table 3). Two studies (Fogg et al., 2013;
+the allometric factor (\(b\)) was significantly different from the value
+of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)), indicating
+that lionfish present allometric growth. More information on model fit
+and confidence intervals for the estimated coefficients is presented in
+Table 2. The relationship between Total Length and Total Weight is
+presented in Figure 3.
+
+\textbf{Comparison of allometric parameters.} From the eight
+peer-reviewed studies including information on growth parameters for
+\emph{P. volitans} and Fishbase (Froese \& Pauly, 2016), 13 parameters
+were identified (Table 3). Two studies (Fogg et al., 2013;
 Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and pooled
-parameters, while the rest of the studies always presented pooled
-results. The smallest coefficient of determination was presented by
-Chin, Aiken \& Buddo (2016) with \(R^2 = 0.8715\), while Sabido-Itza et
-al. (2016) reported the highest value at \(R^2 = 0.9907\). These studies
-presented information for organisms obtained at depths between 0.5 and
-57 m. Two studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken
-\& Buddo, 2016) explicitly stated that their organisms were sampled with
-pole spears. Five studies (Barbour et al., 2011; Fogg et al., 2013;
-Edwards, Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et
-al., 2016) mentioned that some of their organisms were obtained with
-pole spears (or other type of harpoon). A single study (de Leon et al.,
-2013) did not specify how samples were obtained.
+parameters, while the rest presented pooled results. The smallest
+coefficient of determination was presented by Chin, Aiken \& Buddo
+(2016) with \(R^2 = 0.8715\), while Sabido-Itza et al. (2016) reported
+the highest value at \(R^2 = 0.9907\). Reviewed studies presented
+information for organisms obtained at depths between 0.5 and 57 m. Two
+studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken \& Buddo,
+2016) explicitly stated that their organisms were sampled with pole
+spears. Five studies (Barbour et al., 2011; Fogg et al., 2013; Edwards,
+Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et al., 2016)
+mentioned that some of their organisms were obtained with pole spears
+(or other type of harpoon). A single study (de Leon et al., 2013) did
+not specify how organisms were sampled.
 
@@
 \(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
-\(b = 3.31 \pm 0.23\) males and females respectively, compared to
+\(b = 3.31 \pm 0.23\) for males and females respectively, compared to
 parameters from models for pooled genders with a mean \(\pm\) standard
@@
 
-From all allometric parameters reviewed, those of Edwards, Frazer \&
-Jacoby (2014) slightly underestimated the observed biomass, with median
-(0.96) and mean (0.98) bellow one. There is no significance in comparing
-the parameters estimated in this study since, by definition, they are
-the pair of parameters for which residual sum of squares was minimized
-with values of median =1.00 and mean =1.03. For all the other studies,
-the 95\% confidence interval around the mean fell further away from a
-value of 1, indicating overestimation. Predicted to observed biomass
-ratios are presented in Figure 5.
-
-\section{Discussion}\label{discussion}
+There were significant differences in expected-to-observed weight ratios
+estimated for each pair of parameters (F(13, 1512) = 39.28; p
+\textless{} 0.05). From all allometric parameters reviewed, those of
+Edwards, Frazer \& Jacoby (2014) provided the lowest weight estimates,
+with an expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean
+\(\pm\) SD). On the other hand, Barbour et al. (2011) yielded the
+highest weight estimates, with a mean (\(\pm\) SD) expected-to-observed
+weight ratio of 1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios
+and groups identified by Tukey's HSD (\(\alpha = 0.05\)) are presented
+in Figure 5.
+
+\section{DISCUSSION}\label{discussion}
 
@@
 include smaller organisms. Estimating parameters by including smaller
-organisms ensures better estimatio of weight for smaller sizes. This is
+organisms ensures better estimation of weight for smaller sizes. This is
 especially important when biomass is calculated from visual census,
-where small organisms can be registered. Thus, this study is the first
-to provide allometric growth parameters for lionfish in the central
-region of the Mexican Caribbean and increases certainty in weight
-estimation of small organisms.
-
-The parameters estimated in this study were within the range of studies
-in other regions (Barbour et al., 2011; de Leon et al., 2013; Fogg et
-al., 2013; Edwards, Frazer \& Jacoby, 2014; Sandel et al., 2015;
-Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken \& Buddo, 2016;
-Sabido-Itza et al., 2016). As compared to other parameters, the ones
-presented here tend to provide lower weight estimates for a same length.
-Until about TL = 200 mm, there are no appreciable differences between
-the parameters described in this study and those for little Cayman
+where small organisms can be registered. Thus, this study also increases
+certainty in weight estimation of small organisms.
+
+The length-weight coefficients estimated in this study were within the
+range identified by studies in other regions (Barbour et al., 2011; de
+Leon et al., 2013; Fogg et al., 2013; Edwards, Frazer \& Jacoby, 2014;
+Sandel et al., 2015; Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken
+\& Buddo, 2016; Sabido-Itza et al., 2016). However, the ones presented
+here provide lower weight estimates for a same length. Until about TL =
+200 mm, there are no appreciable differences between the parameters for
+organisms from the Mexican Caribbean and those for little Cayman
 (Edwards, Frazer \& Jacoby, 2014) and Jamaica (Chin, Aiken \& Buddo,
@@
 provide similar estimates to those from this study. Conversely, these
-same studies tend to overestimate weight -as compared to the ones
-reported here- for smaller organisms, likely due to the lack of small
+same studies tend to estimate higher weights ---as compared to the ones
+reported here--- for smaller organisms, likely due to the lack of small
 organisms in the samples used to estimate their parameters. When ever
@@
 2016). This indicates that there are differences between lionfish across
-the invasion range, pattern that has also been reported for age and
-growth parameters (Fogg et al., 2015). These differences can have major
-implications in management, especially when estimating biomass available
-for harvest or predicting effects on local ecosystems, or evaluating the
-effectiveness of removal programs. Using site-specific values provides a
-more accurate estimate of fish biomass. Future research should try to
-use, to the extent possible, parameters calculated for their region, or
-use different parameters to provide upper and lower bounds in their
-results. At the same time, this highlights the need for more basic
-research. To have a better invasion management, we must perform research
-that can describe biologically important information of lionfish
-throughout its invasion range (Johnson \& Swenarton, 2016).
+the invasion range. Similar regional variation exist for age-at-length
+relationships of lionfish (Fogg et al., 2015). These differences can
+have major implications in management, especially when estimating
+biomass available for harvest or predicting effects on local ecosystems,
+or evaluating the effectiveness of removal programs. Using site-specific
+values provides a more accurate estimate of fish biomass. Future
+research should try to use, to the extent possible, parameters
+calculated for their region, or use different parameters to provide
+upper and lower bounds in their results. At the same time, this
+highlights the need for more basic research that furthers our
+understanding of lionfish biology. To better manageme the invasion, we
+must perform research that can describe biologically important
+information of lionfish throughout its invasion range (Johnson \&
+Swenarton, 2016).
 
@@
 mislabeled and yielded senseless results when using the suggested
-conversion equation. On some others, parameters were said to be reported
-for mm to gr conversions, when they were actually reported as cm to gr
+conversion equation. On other cases, parameters were said to be reported
+for mm-to-gr conversions, when they were actually reported as cm-to-gr
 conversions. Perhaps these minor discrepancies can be easily solved by
-any researcher, but why should they exist in the first place? It is
+the trained eye, but why should they exist in the first place? It is
 important that we report our information in a standard way, making it
@@
   Be explicit in the methods section. What may seem obvious to you as an
-  author -because you have been deeply immersed throughout the process-
-  may not be clear to the reader. Specify any transformation performed
-  on the data. When using log-transformations, mention the base used to
-  transform. Do not assume that ``data were log-transformed'' means
-  \(log_{10}(X)\). These assumptions vary across disciplines and
-  software and can be a source of confusion. For example, in biology we
-  often assume ``log-transformed'' indicates the use of base 10, however
-  in R the proper command is \texttt{log10()} and not \texttt{log()},
-  which uses base \(e\).
+  author ---because you have been deeply immersed throughout the
+  process--- may not be clear to the reader. Specify any transformation
+  performed on the data. When using log-transformations, mention the
+  base used to transform. Do not assume that ``data were
+  log-transformed'' means \(log_{10}(X)\). These assumptions vary across
+  disciplines and software and can be a source of confusion. For
+  example, in biology we often assume ``log-transformed'' indicates the
+  use of base 10, however in R the proper command is \texttt{log10()}
+  and not \texttt{log()}, which uses base \(e\).
 \item
@@
   2015; Chin, Aiken \& Buddo, 2016; Sabido-Itza et al., 2016). If
-  possible, present the parameters in their exponential (eq. 1) and
+  possible, present the relationship in their exponential (eq. 1) and
   linear (eq. 3) forms.
@@
   we report uncertainty around each parameter and not just general model
-  fit and significance. Reporting uncertainty around parameters allows
-  researchers and managers to include upper and lower bounds in their
-  predictions.
+  fit and coefficient significance. Reporting uncertainty around
+  parameters allows researchers and managers to include upper and lower
+  bounds in their predictions.
 \item
-  Make your data -and code- available. Even if this is not requited by
-  the journal or publisher, you can use free cloud data storage services
-  or third-party repositories to make your research accessible to
-  others. Resources will always be limited and budget will never be
-  enough. It is important that we take advantage of open science tools
-  that promote the advancement of knowledge and foster collaboration.
-  Ultimately, this promotes transparency allows replicability of
-  research and advances science.
+  Make your data and code available. Even if this is not requited by the
+  journal or publisher, you can use free cloud data storage services or
+  third-party repositories to make your research accessible to others.
+  Resources will always be limited and budget will rarely be enough. It
+  is important that we take advantage of open science tools that promote
+  the advancement of knowledge and foster collaboration. Ultimately,
+  this promotes transparency, allows replicability of research, and
+  advances science.
 \end{enumerate}
 
-As final conclusion statements 1) A new pair of allometric growth
-parameters are provided for lionfish from the central Mexican Caribbean,
-where they exhibit different weight-at-length, as compared to other
-regions. 2) Given the differences in weight-at-length patterns through
-the invasion range, it is important to use site-specific parameters. 3)
-When possible, collect organisms with hand nets to obtain a
-representative sample of the population that includes small organisms.
-4) Report allometric parameters (and other life history parameters) in a
-way that is readily available for non-experts, and make your research
-available to advance science.
-
-\section{Aknowledgements}\label{aknowledgements}
+This study provides a new pair of allometric growth parameters for
+lionfish from the central Mexican Caribbean, where they exhibit
+different weight-at-length. Furthermore, regional differences in
+length-weight relationships were identified, highlighting the importance
+of using site-specific parameters.
+
+\section{AKNOWLEDGEMENTES}\label{aknowledgementes}
 
@@
 
-\clearpage
-
-\section{References}\label{references}
+\section{REFERENCES}\label{references}
 
@@
 
-\hypertarget{ref-rmarkdown_2017}{}
-Allaire, J., Cheng, J., Xie, Y., McPherson, J., Chang, W., Allen, J.,
-Wickham, H., Atkins, A., et al. 2017. \emph{Rmarkdown: Dynamic documents
-for r}. ed. (nos.). Available:
-\url{https://CRAN.R-project.org/package=rmarkdown}.
-
 \hypertarget{ref-andradibrown_2017}{}
@@
 
-\hypertarget{ref-stargazer_2015}{}
-Hlavac, M. 2015. \emph{Stargazer: Well-formatted regression and summary
-statistics tables}. ed. (nos.). Cambridge, USA: Harvard University.
-Available: \url{http://CRAN.R-project.org/package=stargazer}.
-
 \hypertarget{ref-johnson_2016}{}
@@
 
-\hypertarget{ref-knitr_2017}{}
-Xie, Y. 2017. \emph{Knitr: A general-purpose package for dynamic report
-generation in r}. ed. (nos.). Available: \url{http://yihui.name/knitr/}.
-
 \hypertarget{ref-sandwich_2014}{}
@@
 
-\hypertarget{ref-kableExtra_2017}{}
-Zhu, H. 2017. \emph{KableExtra: Construct complex table with 'kable' and
-pipe syntax}. ed. (nos.). Available:
-\url{https://CRAN.R-project.org/package=kableExtra}.
-
 \clearpage
 
-\clearpage
-
-\section{Tables}\label{tables}
+\section{TABLES}\label{tables}
 
@@
 
-\begin{tabular}{llllllr}
+\begin{longtable}[]{@{}llllllr@{}}
 \toprule
-Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth & n\\
+Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
+n\tabularnewline
 \midrule
-Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\\
-Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\\
-Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\\
-Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\\
-Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\\
-\addlinespace
-Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\\
-Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\\
-Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\\
-Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\\
-Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\\
-Total &  &  & 5.7 & 38.1 & 18.6 & 109\\
+\endhead
+Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\tabularnewline
+Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\tabularnewline
+Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\tabularnewline
+Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\tabularnewline
+Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\tabularnewline
+Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\tabularnewline
+Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\tabularnewline
+Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\tabularnewline
+Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\tabularnewline
+Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\tabularnewline
+Total & & & 5.7 & 38.1 & 18.6 & 109\tabularnewline
 \bottomrule
-\end{tabular}
+\end{longtable}
 
@@
 spears. An asterisk (*) indicates that some portion of organisms were
-sampled with pole spears.
+sampled with pole spears. 1 = Aguilar-Perera \& Quijano-Puerto (2016), 2
+= Sandel et al. (2015), 3 = Chin, Aiken \& Buddo (2016), 4 = Barbour et
+al. (2011), 5 = de Leon et al. (2013), 6 = Fogg et al. (2013), 7 =
+Edwards, Frazer \& Jacoby (2014), 8 = Sabido-Itza et al. (2016), 9 =
+Froese \& Pauly (2016), 10 = This study.
 
@@
 \centering
-\resizebox{\linewidth}{!}{\begin{tabular}{lllrrrllll}
+\resizebox{\linewidth}{!}{\begin{tabular}{rlllrrrllll}
 \toprule
-Reference & n & a & c & b & R2 & Sex & mDepth & MDepth & Spear\\
+Reference & Region & Sex & a & c & b & R2 & n & mDepth & MDepth & Spear\\
 \midrule
-Aguilar-Perera \& Quijano-Puerto, 2016 & Both & 472 & 0 & -5.5400 & 3.3000 & 0.95 & 5 & 20 & Yes\\
-Aguilar-Perera \& Quijano-Puerto, 2016 & Female & 67 & 0 & -5.9300 & 3.4700 & 0.95 & 5 & 20 & Yes\\
-Aguilar-Perera \& Quijano-Puerto, 2016 & Male & 59 & 0 & -5.3800 & 3.2300 & 0.95 & 5 & 20 & Yes\\
-Sandel et al., 2015 & Both & 458 & 0 & -4.4400 & 2.8100 & - & - & - & Yes*\\
-Chin et al 2016 & Both & 419 & 0 & -4.5600 & 2.8500 & 0.8715 & 18.3 & 18.3 & Yes\\
+1 & Arrecife Alacranes, Mexico & Both & 472 & 0 & -5.5400 & 3 & 0.95 & 5 & 20 & Yes\\
+1 & Arrecife Alacranes, Mexico & Female & 67 & 0 & -5.9300 & 3 & 0.95 & 5 & 20 & Yes\\
+1 & Arrecife Alacranes, Mexico & Male & 59 & 0 & -5.3800 & 3 & 0.95 & 5 & 20 & Yes\\
+2 & Southern Caribbean Coast of Costa Rica & Both & 458 & 0 & -4.4400 & 3 & - & - & - & Yes*\\
+3 & Discovery Bay, Jamaica & Both & 419 & 0 & -4.5600 & 3 & 0.8715 & 18.3 & 18.3 & Yes\\
 \addlinespace
-Brbour et al 2011 & Both & 774 & 0 & -4.5391 & 2.8900 & - & 27 & 45 & Yes*\\
-de Leon et al., 2013 & Both & 1450 & 0 & -4.6411 & 2.8900 & 0.96 & - & - & NA\\
-Fogg et al., 2013 & Both & 582 & 0 & -5.8600 & 3.4349 & 0.99 & - & - & Yes*\\
-Fogg et al., 2013 & Male & 119 & 0 & -5.5700 & 3.3100 & 0.97 & - & - & Yes*\\
-Fogg et al., 2013 & Female & 115 & 0 & -5.1700 & 3.1437 & 0.94 & - & - & Yes*\\
+4 & North Carolina & Both & 774 & 0 & -4.5391 & 3 & - & 27 & 45 & Yes*\\
+5 & Bonaire & Both & 1450 & 0 & -4.6411 & 3 & 0.96 & - & - & NA\\
+6 & Northern Gulf of Mexico & Both & 582 & 0 & -5.8600 & 3 & 0.99 & - & - & Yes*\\
+6 & Northern Gulf of Mexico & Male & 119 & 0 & -5.5700 & 3 & 0.97 & - & - & Yes*\\
+6 & Northern Gulf of Mexico & Female & 115 & 0 & -5.1700 & 3 & 0.94 & - & - & Yes*\\
 \addlinespace
-Edwards et al., 2014 & Both & 1887 & 0 & -5.5229 & 3.2400 & 0.97 & 15 & 30 & Yes*\\
-Sabido-Itza et al., 2016 & Both & 2143 & 0 & -5.2828 & 3.1832 & 0.9907 & 0.5 & 57 & Yes*\\
-Fishbase & Both & NA & 0 & -5.0293 & 3.0900 & - & - & - & NA\\
-This study & Both & 109 & 0 & -5.4941 & 3.2347 & 0.9766 & 5.7 & 38.1 & No\\
+7 & Little Cayman & Both & 1887 & 0 & -5.5229 & 3 & 0.97 & 15 & 30 & Yes*\\
+8 & Parque Nacional Arrecifes de Xcalak, Mexico & Both & 2143 & 0 & -5.2828 & 3 & 0.9907 & 0.5 & 57 & Yes*\\
+9 & NA & Both & NA & 0 & -5.0293 & 3 & - & - & - & NA\\
+10 & Puerto Aventuras, Mexico & Both & 109 & 0 & -5.4941 & 3 & 0.9766 & 5.7 & 38.1 & No\\
 \bottomrule
@@
 \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{Weight-at-length relationship for 109 lionfish sampled in the
+\caption{Length-weight relationship for 109 lionfish sampled in the
 central Mexican Caribbean. Points indicate samples, solid line indicates
@@
 \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{Weight-at-length relationships (n = 14) for eight studies, this
-study, and FishBase parameters. Colors indicate studies from which the
-parameters were extracted. Solid lines indicate that the fit was
-performed for males and females pooled together. Dotted lines indicate
-that the regression was performed on females, and dashed lines indicate
-it was performed for males.}
+\caption{Length-weight relationships (n = 14) for eight studies, this
+study, and Fishbase. Colors indicate studies from which the parameters
+were extracted. Solid lines indicate that the fit was performed for
+males and females pooled together. Dotted lines indicate that the
+regression was performed on females, and dashed lines indicate it was
+performed for males.}
 \end{figure}
@@
 largest and lowes values within 1.5 inter-quartile range of the hinge,
-small points represent outliers further away than the whiskers.}
+small points represent outliers further away than the whiskers. Like
+letters indicate values that do not differ significantly (Tukey's HSD; p
+\textless{} 0.05).}
 \end{figure}

### 2017-09-29 Manuscript.Rmd
Manuscript finalized

@@
 ---
-title: \Large{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central
-  Mexican Caribbean, and a review of allometric growth parameters across the invasion range}
+title: \Large{Weight-at-length of the invasive lionfish \textit{Pterois volitans} (Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}
 fontsize: 12pt
 output:
-  pdf_document:
-    fig_caption: yes
-    keep_tex: yes
   word_document:
@@
 - \doublespacing
-- \usepackage{lineno}
-- \linenumbers
-subtitle: '**Running title**: Allometric growth of Pterois volitans'
+# - \usepackage{lineno}
+# - \linenumbers
+subtitle: '**Running title**: Length-Weight relationships of lionfish'
 bibliography:
@@
 
-Juan Carlos VILLASEÑOR-DERBEZ^1^
+Juan Carlos Villaseñor-Derbez^1^
 
@@
 
-**Background.** Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean.
-In order to better manage the invasion, inform lionfish removal programs, predict their possible impacts, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass.
-Previous work has identified that lionfish age-at-length relationships are spatially variable across the invasion range.
-This work had two main objectives: i) compare length-weight relationships of the invasive lionfish through the invasion range; and ii) Report the length-weight frequency for lionfish in the Central Meixcan Caribbean.
+**Abstract**
 
-**Materials and methods.** A total of 13 length-weight relationships reported in eight peer-reviewed studies and FishBase were used to calculate expected biomass of organisms (n = 109) sampled from the Central Mexican Caribbean, whose Total Length (TL) and Total Weight (TW) were known.
-For each length-weight relationship, expected-to-observed weight ratio was calculated for each organism.
-Differences in mean expected-to-observed weight ratios were tested with a one-way ANOVA; Tukey's HSD was used as a post-hoc test to identify groups of non-statistically significant differences.
-Additionally, the length-weight relationship of the 109 organisms was calculated.
-Total Length (TL) and Total weight (TW) were log10-transformed to fit a linear model describing the linearized length-weight relationship.
-The model was fit using Ordinary Least Squares and Heteroskedastik-robust standard errors were computed.
-
-**Results.** Expected-to-observed weight ratios ranged from 0.44 to 3.51, and dfferences in weight-at-length were spatially consistent.
+Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean.
+In order to better manage the invasion, inform lionfish removal programs, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass, frequently from length observations.
+This work compares length-weight relationships of the invasive lionfish through the invasion range and reports the length--weight relationship for lionfish in the Central Mexican Caribbean.
+A review of 13 length--weight relationships reported in eight peer-reviewed studies and FishBase is provided.
+These parameters were used to identify spatial variation in weight-at-length.
 For a given length, parameters from the Caribbean yielded lower weights than those from the Gulf of Mexico and Atlantic, indicating that weight-at-length is spatially variable.
+This highlights the importance of using site-specific parameters to estimate biomass from length observations.
 This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean.
-
-**Conclusion.** The large differences between observed and expected biomass when using parameters from other locations highlights the importance of using site-specific parameters to estimate biomass from length observations.
 Findings from this work can aid managers and decision makers to better select length-weight parameters when these are not available for their region of interest.
 
+**Resumen**
+
+El pez león (*Pterois volitans/miles*) es una especie invasora en el Atlántico Noroeste y el Mar Caribe.
+Para tener un mejor manejo de la invasión, informar programas de remoción y estimar la biomasa disponible para aprovechamiento, debemos ser capaces de estimar la biomasa disponible con presisión, frecuentemente a partir de observaciones de tallas.
+Este trabajo compara la relación longitud--peso del pez león a través del rango de invasión, y reporta un nuevo par de parámetros de crecimiento alométrico para la zona central del Caribe Mexicano.
+El trabajo presenta revisión de 13 relaciones longitud--peso reportadas reportadas en ocho estudios publicados en revistas arbitradas y FishBase.
+Para una misma talla, los parámetros del Caribe indican un mejor peso que los parámetros del Golfo de México y el Atlántico, indicando una variabilidad espacial en la relación longitud peso.
+Esta variabilidad resalta la importancia de utilizar parámetros específicos a un sitio al estimar biomasa a partir de observaciones de tallas.
+Este estudio también reporta una nueva relación longitud--peso ($a = 3.2056\times 10^{-6}; b = 3.235$) para organismos muestreados en la costa central del Caribe Mexicano.
+Los resultados de este trabajo pueden ayudar a tomadores de decisiones en la selección de relaciones longitud-peso cuando éstas no están disponibles para su zona de interés.
+
 **Key words**   
-lionfish, Pterois volitans, length-weight relationship, allometric growth, Mexico
+biometry, invasive species, spatial variability, allometric growth, Mexico
 
@@
 
-# INTRODUCTION
+# Introduction
 
@@
 
-# MATERIALS AND METHODS
+# Materials and Methods
 
@@
 
-**Area of study.** The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean (**Fig.
+*Area of study*
+
+The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean (**Fig.
 1**).
@@
 
-```{r create map, include = F}
+```{r create map, fig.cap = "Map of the study area.
+The black inset on the left (Yucatan Peninsula) indicates the location where study sites are distributed.
+On the right, circular markers indicate sampling sites and the black romboid indicates location of Puerto Aventuras, Mexico."}
 # Load shapefiles
@@
 
-**Fish sampling.** A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along the coast in 2010 (Fig.
-1, Table 1).
+*Fish sampling*
+
+A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along the coast in 2010 (Fig.
+1, Table I).
 Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
@@
 
-```{r table of locations, include = F}
+```{r table of locations, results = "asis"}
 total <- data.frame(Location = "Total", Latitude = "", Longitude = "", minD = min(fish$Depth_m), maxD = max(fish$Depth_m), meanD = formatC(mean(fish$Depth_m), digits = 1, format = "f"), n = 109, stringsAsFactors = F)
 
-location_table <- fish %>% 
+fish %>% 
   group_by(Location) %>% 
@@
                col.names = c("Location", "Lat.", "Long.", "Min. Depth", "Max. Depth", "Mean Depth", "n"),
-               booktabs = T)
-
-location_table
+               booktabs = T, caption = c("Coordinates, minimum, maximum and mean depth (m), and number of samples for each location."))
 ```
 
-**Data analysis.** The weight at length relationship between the observed variables is described by the allometric growth function:
+*Data analysis*
+
+The weight at length relationship between the observed variables is described by the allometric growth function:
 
@@
 
-# RESULTS
+# Results
 
@@
 
-```{r histogram figures, include = F}
+```{r histogram figures, fig.width = 5, fig.height = 6, fig.cap = "Kernell density plots for a) Total length (mm) and b) Total weight (gr) for 109 lionfish sampled in the central Mexican Caribbean."}
 length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
@@
 
-**Length-weight relationship.** The model adjusted to eq.
+*Length-weight relationship*
+
+The model adjusted to eq.
 3 estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
@@
 Additionally, the allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$), indicating that lionfish present allometric growth.
-More information on model fit and confidence intervals for the estimated coefficients is presented in Table 2.
+More information on model fit and confidence intervals for the estimated coefficients is presented in Table II.
 The relationship between Total Length and Total Weight is presented in Figure 3.
 
-```{r scatter plot, include = F}
+```{r scatter plot, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
+Points indicate samples, solid line indicates curve of best fit."}
 
@@
 
-```{r, include = F}
+```{r, results = "asis"}
+
+ci_c <- c("95\\% CI for c", paste0("(", formatC(a-(1.96*robust_se[[1]]), digits = 3, format = "f"),"-", formatC(a+(1.96*robust_se[[1]]), digits = 3, format = "f"),")"))
+
+ci_b <- c("85\\% CI for b", paste0("(", formatC(b-(1.96*robust_se[[2]]), digits = 3, format = "f"),"-", formatC(b+(1.96*robust_se[[2]]), digits = 3, format = "f"),")"))
+
+regression_table <- stargazer(model,
+          header = F,
+          se = list(robust_se),
+          type = "latex",
+          t.auto = T,
+          p.auto = T,
+          intercept.bottom = F,
+          single.row = T,
+          report = "vcs*",
+          omit.stat = c("rsq", "f"),
+          add.lines = list(ci_c, ci_b, f_string),
+          covariate.labels = c("c", "b"),
+          dep.var.labels = "log10(TW)", title = "Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
+Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.")
+```
+
+```{r, results = "asis"}
 review <- read_csv("biometric_review.csv", col_types = cols(), na = "-")
@@
                booktabs = T,
-               col.names = c("Reference", "Region", "Sex", "a", "c", "b", "R2", "n", "mDepth", "MDepth", "Spear")) %>% 
+               col.names = c("Reference", "Region", "Sex", "a", "c", "b", "R2", "n", "mDepth", "MDepth", "Spear"),
+               caption = c("Summary of 13 allometric growth parameters available for lionfish in the invaded range from eight peer-reviewed papers, Fishbase [@froese_website_2016], and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, a = scaling parameter for eq.
+1, c = y-intercept for eq.
+3, b = exponent or slope for eq.
+1 or eq.
+3, respectively.
+The R^2^ column indicates reported model fit.
+mDepth and MDepth indicate minimum and maximum depths (m), respectively, at which organisms were sampled.
+The Spear column indicates if the study collected organisms with pole spears.
+An asterisk indicates that some portion of organisms were sampled with pole spears.
+1 = @aguilarperera_2016, 2 = @sandel_2015, 3 = @chin_2016, 4 = @barbour_2011, 5 = @deleon_2013, 6 = @fogg_2013, 7 = @edwards_2014, 8 = @sabidoitza_2016, 9 = @froese_website_2016, 10 = This study.")) %>%
   kableExtra::kable_styling(latex_options = c("scale_down"))
@@
 
-**Comparison of allometric parameters.** From the eight peer-reviewed studies including information on growth parameters for *P.
-volitans* and Fishbase [@froese_website_2016], `r dim(review)[1]-1` parameters were identified (Table 3).
+*Comparison of allometric parameters*
+
+From the eight peer-reviewed studies including information on growth parameters for *P.
+volitans* and Fishbase [@froese_website_2016], `r dim(review)[1]-1` parameters were identified (Table III).
 Two studies [@aguilarperera_2016; @fogg_2013] reported gender-level and pooled parameters, while the rest presented pooled results.
@@
 
-```{r review plots, include = F}
+```{r review plots, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationships (n = 14) for eight studies, this study, and Fishbase.
+Colors indicate studies from which the parameters were extracted.
+Solid lines indicate that the fit was performed for males and females pooled together.
+Dotted lines indicate that the regression was performed on females, and dashed lines indicate it was performed for males."}
+
 predicted_all <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
@@
 
-```{r plot comparing predictions, include = F}
+```{r plot comparing predictions, fig.height = 4.5, fig.width = 6, fig.cap = ".
+Box and whiskers plot showing the distribution of predicted to observed biomass ratios for 14 pairs of allometric parameters.
+Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers.
+Like letters indicate values that do not differ significantly (Tukey's HSD; p < 0.05)."}
 Predicted_biomass_plot <- Predicted_biomass %>% 
@@
 
-# DISCUSSION
+# Discussion
 
@@
 
-# AKNOWLEDGEMENTES
+# Aknowledgements
 
@@
 
-# REFERENCES
-
-<div id="refs"></div>
-
-\clearpage
-
-# TABLES
-
-Table 1: Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.
-
-```{r, results = "asis"}
-location_table
-```
-
-\clearpage
-
-Table 2: Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
-Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.
-The asterisks (\*) indicate the statistical significance.
-95% Confidence intervals are provided for each parameter.
-
-```{r, results = "asis"}
-
-ci_c <- c("95\\% CI for c", paste0("(", formatC(a-(1.96*robust_se[[1]]), digits = 3, format = "f"),"-", formatC(a+(1.96*robust_se[[1]]), digits = 3, format = "f"),")"))
-
-ci_b <- c("85\\% CI for b", paste0("(", formatC(b-(1.96*robust_se[[2]]), digits = 3, format = "f"),"-", formatC(b+(1.96*robust_se[[2]]), digits = 3, format = "f"),")"))
-
-regression_table <- stargazer(model,
-          header = F,
-          se = list(robust_se),
-          type = "latex",
-          t.auto = T,
-          p.auto = T,
-          intercept.bottom = F,
-          single.row = T,
-          report = "vcs*",
-          omit.stat = c("rsq", "f"),
-          add.lines = list(ci_c, ci_b, f_string),
-          covariate.labels = c("c", "b"),
-          dep.var.labels = "log10(TW)")
-```
-
-\clearpage
-
-Table 3: Summary of 13 allometric growth parameters available for lionfish in the invaded range from eight peer-reviewed papers, Fishbase [@froese_website_2016], and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, a = scaling parameter for eq.
-1, c = y-intercept for eq.
-3, b = exponent or slope for eq.
-1 or eq.
-3, respectively.
-The R^2^ column indicates reported model fit.
-mDepth and MDepth indicate minimum and maximum depths (m), respectively, at which organisms were sampled.
-The Spear column indicates if the study collected organisms with pole spears.
-An asterisk (\*) indicates that some portion of organisms were sampled with pole spears.
-1 = @aguilarperera_2016, 2 = @sandel_2015, 3 = @chin_2016, 4 = @barbour_2011, 5 = @deleon_2013, 6 = @fogg_2013, 7 = @edwards_2014, 8 = @sabidoitza_2016, 9 = @froese_website_2016, 10 = This study.
-
-```{r, results = "asis"}
-review_table
-```
-
-\clearpage
-
-# Figures
-
-```{r, fig.cap = "Map of the study area.
-The black inset on the left (Yucatan Peninsula) indicates the location where study sites are distributed.
-On the right, circular markers indicate sampling sites and the black romboid indicates location of Puerto Aventuras, Mexico."}
-tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
-```
-
-\clearpage
-
-```{r, fig.width = 5, fig.height = 6, fig.cap = "Kernell density plots for a) Total length (mm) and b) Total weight (gr) for 109 lionfish sampled in the central Mexican Caribbean."}
-gridExtra::grid.arrange(length_hist, weight_hist)
-```
-
-\clearpage
-
-```{r, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit."}
-plot_fit_this_study
-```
-
-\clearpage
-
-```{r, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationships (n = 14) for eight studies, this study, and Fishbase.
-Colors indicate studies from which the parameters were extracted.
-Solid lines indicate that the fit was performed for males and females pooled together.
-Dotted lines indicate that the regression was performed on females, and dashed lines indicate it was performed for males."}
-plot_fit_all_studies
-```
-
-\clearpage
-
-```{r, fig.height = 4.5, fig.width = 6, fig.cap = ".
-Box and whiskers plot showing the distribution of predicted to observed biomass ratios for 14 pairs of allometric parameters.
-Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers.
-Like letters indicate values that do not differ significantly (Tukey's HSD; p < 0.05)."}
-Predicted_biomass_plot
-```
+# References

### 2017-09-29 Manuscript.tex
Manuscript finalized

@@
 \setlength{\droptitle}{-2em}
-  \title{\Large{Biometry of the invasive lionfish (\textit{Pterois volitans}) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
+  \title{\Large{Weight-at-length of the invasive lionfish \textit{Pterois volitans} (Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
   \pretitle{\vspace{\droptitle}\centering\huge}
   \posttitle{\par}
-\subtitle{\textbf{Running title}: Allometric growth of Pterois volitans}
+\subtitle{\textbf{Running title}: Length-Weight relationships of lionfish}
   \author{}
@@
 \doublespacing
-\usepackage{lineno}
-\linenumbers
 
@@
 
-Juan Carlos VILLASEÑOR-DERBEZ\textsuperscript{1}
+Juan Carlos Villaseñor-Derbez\textsuperscript{1}
 
@@
 
-\textbf{Background.} Lionfish (\emph{Pterois volitans/miles}) are an
-invasive species in the North-Western Atlantic and the Caribbean. In
-order to better manage the invasion, inform lionfish removal programs,
-predict their possible impacts, and estimate biomass available for
-harvest, we must be able to accurately estimate their total biomass.
-Previous work has identified that lionfish age-at-length relationships
-are spatially variable across the invasion range. This work had two main
-objectives: i) compare length-weight relationships of the invasive
-lionfish through the invasion range; and ii) Report the length-weight
-frequency for lionfish in the Central Meixcan Caribbean.
-
-\textbf{Materials and methods.} A total of 13 length-weight
-relationships reported in eight peer-reviewed studies and FishBase were
-used to calculate expected biomass of organisms (n = 109) sampled from
-the Central Mexican Caribbean, whose Total Length (TL) and Total Weight
-(TW) were known. For each length-weight relationship,
-expected-to-observed weight ratio was calculated for each organism.
-Differences in mean expected-to-observed weight ratios were tested with
-a one-way ANOVA; Tukey's HSD was used as a post-hoc test to identify
-groups of non-statistically significant differences. Additionally, the
-length-weight relationship of the 109 organisms was calculated. Total
-Length (TL) and Total weight (TW) were log10-transformed to fit a linear
-model describing the linearized length-weight relationship. The model
-was fit using Ordinary Least Squares and Heteroskedastik-robust standard
-errors were computed.
-
-\textbf{Results.} Expected-to-observed weight ratios ranged from 0.44 to
-3.51, and dfferences in weight-at-length were spatially consistent. For
-a given length, parameters from the Caribbean yielded lower weights than
-those from the Gulf of Mexico and Atlantic, indicating that
-weight-at-length is spatially variable. This study also reports a new
-pair of length-weight parameters
-(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
-Central Mexican Caribbean.
-
-\textbf{Conclusion.} The large differences between observed and expected
-biomass when using parameters from other locations highlights the
-importance of using site-specific parameters to estimate biomass from
-length observations. Findings from this work can aid managers and
-decision makers to better select length-weight parameters when these are
-not available for their region of interest.
+\textbf{Abstract}
+
+Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
+North-Western Atlantic and the Caribbean. In order to better manage the
+invasion, inform lionfish removal programs, and estimate biomass
+available for harvest, we must be able to accurately estimate their
+total biomass, frequently from length observations. This work compares
+length-weight relationships of the invasive lionfish through the
+invasion range and reports the length--weight relationship for lionfish
+in the Central Mexican Caribbean. A review of 13 length--weight
+relationships reported in eight peer-reviewed studies and FishBase is
+provided. These parameters were used to identify spatial variation in
+weight-at-length. For a given length, parameters from the Caribbean
+yielded lower weights than those from the Gulf of Mexico and Atlantic,
+indicating that weight-at-length is spatially variable. This highlights
+the importance of using site-specific parameters to estimate biomass
+from length observations. This study also reports a new pair of
+length-weight parameters (\(a = 3.2056\times 10^{-6}; b = 3.235\)) for
+organisms sampled in the Central Mexican Caribbean. Findings from this
+work can aid managers and decision makers to better select length-weight
+parameters when these are not available for their region of interest.
+
+\textbf{Resumen}
+
+El pez león (\emph{Pterois volitans/miles}) es una especie invasora en
+el Atlántico Noroeste y el Mar Caribe. Para tener un mejor manejo de la
+invasión, informar programas de remoción y estimar la biomasa disponible
+para aprovechamiento, debemos ser capaces de estimar la biomasa
+disponible con presisión, frecuentemente a partir de observaciones de
+tallas. Este trabajo compara la relación longitud--peso del pez león a
+través del rango de invasión, y reporta un nuevo par de parámetros de
+crecimiento alométrico para la zona central del Caribe Mexicano. El
+trabajo presenta revisión de 13 relaciones longitud--peso reportadas
+reportadas en ocho estudios publicados en revistas arbitradas y
+FishBase. Para una misma talla, los parámetros del Caribe indican un
+mejor peso que los parámetros del Golfo de México y el Atlántico,
+indicando una variabilidad espacial en la relación longitud peso. Esta
+variabilidad resalta la importancia de utilizar parámetros específicos a
+un sitio al estimar biomasa a partir de observaciones de tallas. Este
+estudio también reporta una nueva relación longitud--peso
+(\(a = 3.2056\times 10^{-6}; b = 3.235\)) para organismos muestreados en
+la costa central del Caribe Mexicano. Los resultados de este trabajo
+pueden ayudar a tomadores de decisiones en la selección de relaciones
+longitud-peso cuando éstas no están disponibles para su zona de interés.
 
 \textbf{Key words}\\
-lionfish, Pterois volitans, length-weight relationship, allometric
-growth, Mexico
+biometry, invasive species, spatial variability, allometric growth,
+Mexico
 
@@
 
-\section{INTRODUCTION}\label{introduction}
+\section{Introduction}\label{introduction}
 
@@
 
-\section{MATERIALS AND METHODS}\label{materials-and-methods}
-
-\textbf{Area of study.} The study took place off the coasts of Playa del
-Carmen, in the Mexican Caribbean (\textbf{Fig. 1}). The region
-represents the northernmost section of the Mesoamerican Barrier Reef
-System (Ruiz-Zarate \& Arias-Gonzalez, 2004). Coral reefs and mangroves
-are locally important habitats that represent important sources of
-income in terms of extractive (\emph{e.g.} recreational fishing) and
-non-extractive (\emph{e.g.} SCUBA diving) activities related to tourism,
-the main source of income to the local economy (Murray, 2007).
+\section{Materials and Methods}\label{materials-and-methods}
+
+\emph{Area of study}
+
+The study took place off the coasts of Playa del Carmen, in the Mexican
+Caribbean (\textbf{Fig. 1}). The region represents the northernmost
+section of the Mesoamerican Barrier Reef System (Ruiz-Zarate \&
+Arias-Gonzalez, 2004). Coral reefs and mangroves are locally important
+habitats that represent important sources of income in terms of
+extractive (\emph{e.g.} recreational fishing) and non-extractive
+(\emph{e.g.} SCUBA diving) activities related to tourism, the main
+source of income to the local economy (Murray, 2007).
 
@@
 
-\textbf{Fish sampling.} A total of 33 SCUBA immersions were performed in
-10 sampling sites along the coast in 2010 (Fig. 1, Table 1). Sampling
-locations included wall and carpet reefs at depths between 5.7 m and
-38.1 m. All observed organisms (n = 109) were collected using hand nets
-and numbered collection bottles. The use of hand nets prevented any
-weight loss due to bleeding and allowed a better representation of small
-sizes, often ignored due to gear selectivity when spearing. Organisms
-were euthanized and frozen within 30 minutes of completing the dive and
-stored for posterior analysis. Total Length (TL; mm) and Total Weight
-(TW; gr) were recorded for all organisms.
-
-\textbf{Data analysis.} The weight at length relationship between the
-observed variables is described by the allometric growth function:
+\begin{figure}[htbp]
+\centering
+\includegraphics{Manuscript_files/figure-latex/create map-1.pdf}
+\caption{Map of the study area. The black inset on the left (Yucatan
+Peninsula) indicates the location where study sites are distributed. On
+the right, circular markers indicate sampling sites and the black
+romboid indicates location of Puerto Aventuras, Mexico.}
+\end{figure}
+
+\emph{Fish sampling}
+
+A total of 33 SCUBA immersions were performed in 10 sampling sites along
+the coast in 2010 (Fig. 1, Table I). Sampling locations included wall
+and carpet reefs at depths between 5.7 m and 38.1 m. All observed
+organisms (n = 109) were collected using hand nets and numbered
+collection bottles. The use of hand nets prevented any weight loss due
+to bleeding and allowed a better representation of small sizes, often
+ignored due to gear selectivity when spearing. Organisms were euthanized
+and frozen within 30 minutes of completing the dive and stored for
+posterior analysis. Total Length (TL; mm) and Total Weight (TW; gr) were
+recorded for all organisms.
+
+\begin{longtable}[]{@{}llllllr@{}}
+\caption{Coordinates, minimum, maximum and mean depth (m), and number of
+samples for each location.}\tabularnewline
+\toprule
+Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
+n\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
+n\tabularnewline
+\midrule
+\endhead
+Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\tabularnewline
+Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\tabularnewline
+Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\tabularnewline
+Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\tabularnewline
+Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\tabularnewline
+Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\tabularnewline
+Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\tabularnewline
+Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\tabularnewline
+Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\tabularnewline
+Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\tabularnewline
+Total & & & 5.7 & 38.1 & 18.6 & 109\tabularnewline
+\bottomrule
+\end{longtable}
+
+\emph{Data analysis}
+
+The weight at length relationship between the observed variables is
+described by the allometric growth function:
 
@@
 
-\section{RESULTS}\label{results}
+\section{Results}\label{results}
 
@@
 
-\textbf{Length-weight relationship.} The model adjusted to eq. 3
-estimated the coefficient values at \(b = 3.2347391\) and
-\(c = -5.4940866\). Thus, TW (gr) can be calculated from TL (mm) as a
-linear equation:
+\begin{figure}[htbp]
+\centering
+\includegraphics{Manuscript_files/figure-latex/histogram figures-1.pdf}
+\caption{Kernell density plots for a) Total length (mm) and b) Total
+weight (gr) for 109 lionfish sampled in the central Mexican Caribbean.}
+\end{figure}
+
+\emph{Length-weight relationship}
+
+The model adjusted to eq. 3 estimated the coefficient values at
+\(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
+calculated from TL (mm) as a linear equation:
 \(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
@@
 and confidence intervals for the estimated coefficients is presented in
-Table 2. The relationship between Total Length and Total Weight is
+Table II. The relationship between Total Length and Total Weight is
 presented in Figure 3.
 
-\textbf{Comparison of allometric parameters.} From the eight
-peer-reviewed studies including information on growth parameters for
-\emph{P. volitans} and Fishbase (Froese \& Pauly, 2016), 13 parameters
-were identified (Table 3). Two studies (Fogg et al., 2013;
-Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and pooled
-parameters, while the rest presented pooled results. The smallest
+\begin{figure}[htbp]
+\centering
+\includegraphics{Manuscript_files/figure-latex/scatter plot-1.pdf}
+\caption{Length-weight relationship for 109 lionfish sampled in the
+central Mexican Caribbean. Points indicate samples, solid line indicates
+curve of best fit.}
+\end{figure}
+
+\begin{table}[!htbp] \centering 
+  \caption{Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
+Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.}
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] & log10(TW) \\ 
+\hline \\[-1.8ex] 
+ c & $-$5.494 (0.083)$^{***}$ \\ 
+  b & 3.235 (0.039)$^{***}$ \\ 
+ \hline \\[-1.8ex] 
+95\% CI for c & (-5.657--5.331) \\ 
+85\% CI for b & (3.159-3.311) \\ 
+F Statistic & 6928.67*** (df = 1; 107) \\ 
+Observations & 109 \\ 
+Adjusted R$^{2}$ & 0.976 \\ 
+Residual Std. Error & 0.096 (df = 107) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\emph{Comparison of allometric parameters}
+
+From the eight peer-reviewed studies including information on growth
+parameters for \emph{P. volitans} and Fishbase (Froese \& Pauly, 2016),
+13 parameters were identified (Table III). Two studies (Fogg et al.,
+2013; Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and
+pooled parameters, while the rest presented pooled results. The smallest
 coefficient of determination was presented by Chin, Aiken \& Buddo
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics{Manuscript_files/figure-latex/review plots-1.pdf}
+\caption{Length-weight relationships (n = 14) for eight studies, this
+study, and Fishbase. Colors indicate studies from which the parameters
+were extracted. Solid lines indicate that the fit was performed for
+males and females pooled together. Dotted lines indicate that the
+regression was performed on females, and dashed lines indicate it was
+performed for males.}
+\end{figure}
+
 There were significant differences in expected-to-observed weight ratios
@@
 
-\section{DISCUSSION}\label{discussion}
+\begin{figure}[htbp]
+\centering
+\includegraphics{Manuscript_files/figure-latex/plot comparing predictions-1.pdf}
+\caption{. Box and whiskers plot showing the distribution of predicted
+to observed biomass ratios for 14 pairs of allometric parameters. Lines
+indicate median values, circles indicate mean values, notches represent
+95\% confidence intervals arround the median, lower and upper hinges
+correspond to the first and third quartiles, whiskers extend to the
+largest and lowes values within 1.5 inter-quartile range of the hinge,
+small points represent outliers further away than the whiskers. Like
+letters indicate values that do not differ significantly (Tukey's HSD; p
+\textless{} 0.05).}
+\end{figure}
+
+\section{Discussion}\label{discussion}
 
@@
 
-\section{AKNOWLEDGEMENTES}\label{aknowledgementes}
+\section{Aknowledgements}\label{aknowledgements}
 
@@
 
-\section{REFERENCES}\label{references}
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
 
@@
 
-\clearpage
-
-\section{TABLES}\label{tables}
-
-Table 1: Coordinates, minimum, maximum and mean depth (m), and number of
-samples for each location.
-
-\begin{longtable}[]{@{}llllllr@{}}
-\toprule
-Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
-n\tabularnewline
-\midrule
-\endhead
-Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\tabularnewline
-Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\tabularnewline
-Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\tabularnewline
-Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\tabularnewline
-Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\tabularnewline
-Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\tabularnewline
-Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\tabularnewline
-Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\tabularnewline
-Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\tabularnewline
-Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\tabularnewline
-Total & & & 5.7 & 38.1 & 18.6 & 109\tabularnewline
-\bottomrule
-\end{longtable}
-
-\clearpage
-
-Table 2: Regression table for the linear model fit between
-log10-transformed Total Weight (dependent variable) and Total Length
-(independent variable). Numbers in parentheses next to coefficient
-estimates indicate heteroskedastic-robust standard errors. The asterisks
-(*) indicate the statistical significance. 95\% Confidence intervals are
-provided for each parameter.
-
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & log10(TW) \\ 
-\hline \\[-1.8ex] 
- c & $-$5.494 (0.083)$^{***}$ \\ 
-  b & 3.235 (0.039)$^{***}$ \\ 
- \hline \\[-1.8ex] 
-95\% CI for c & (-5.657--5.331) \\ 
-85\% CI for b & (3.159-3.311) \\ 
-F Statistic & 6928.67*** (df = 1; 107) \\ 
-Observations & 109 \\ 
-Adjusted R$^{2}$ & 0.976 \\ 
-Residual Std. Error & 0.096 (df = 107) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\clearpage
-
-Table 3: Summary of 13 allometric growth parameters available for
-lionfish in the invaded range from eight peer-reviewed papers, Fishbase
-(Froese \& Pauly, 2016), and this study. All parameters have been
-adjusted to convert from millimeters to grams. n = Sample size, a =
-scaling parameter for eq. 1, c = y-intercept for eq. 3, b = exponent or
-slope for eq. 1 or eq. 3, respectively. The R\textsuperscript{2} column
-indicates reported model fit. mDepth and MDepth indicate minimum and
-maximum depths (m), respectively, at which organisms were sampled. The
-Spear column indicates if the study collected organisms with pole
-spears. An asterisk (*) indicates that some portion of organisms were
-sampled with pole spears. 1 = Aguilar-Perera \& Quijano-Puerto (2016), 2
-= Sandel et al. (2015), 3 = Chin, Aiken \& Buddo (2016), 4 = Barbour et
-al. (2011), 5 = de Leon et al. (2013), 6 = Fogg et al. (2013), 7 =
-Edwards, Frazer \& Jacoby (2014), 8 = Sabido-Itza et al. (2016), 9 =
-Froese \& Pauly (2016), 10 = This study.
-
-\begin{table}[!h]
-\centering
-\resizebox{\linewidth}{!}{\begin{tabular}{rlllrrrllll}
-\toprule
-Reference & Region & Sex & a & c & b & R2 & n & mDepth & MDepth & Spear\\
-\midrule
-1 & Arrecife Alacranes, Mexico & Both & 472 & 0 & -5.5400 & 3 & 0.95 & 5 & 20 & Yes\\
-1 & Arrecife Alacranes, Mexico & Female & 67 & 0 & -5.9300 & 3 & 0.95 & 5 & 20 & Yes\\
-1 & Arrecife Alacranes, Mexico & Male & 59 & 0 & -5.3800 & 3 & 0.95 & 5 & 20 & Yes\\
-2 & Southern Caribbean Coast of Costa Rica & Both & 458 & 0 & -4.4400 & 3 & - & - & - & Yes*\\
-3 & Discovery Bay, Jamaica & Both & 419 & 0 & -4.5600 & 3 & 0.8715 & 18.3 & 18.3 & Yes\\
-\addlinespace
-4 & North Carolina & Both & 774 & 0 & -4.5391 & 3 & - & 27 & 45 & Yes*\\
-5 & Bonaire & Both & 1450 & 0 & -4.6411 & 3 & 0.96 & - & - & NA\\
-6 & Northern Gulf of Mexico & Both & 582 & 0 & -5.8600 & 3 & 0.99 & - & - & Yes*\\
-6 & Northern Gulf of Mexico & Male & 119 & 0 & -5.5700 & 3 & 0.97 & - & - & Yes*\\
-6 & Northern Gulf of Mexico & Female & 115 & 0 & -5.1700 & 3 & 0.94 & - & - & Yes*\\
-\addlinespace
-7 & Little Cayman & Both & 1887 & 0 & -5.5229 & 3 & 0.97 & 15 & 30 & Yes*\\
-8 & Parque Nacional Arrecifes de Xcalak, Mexico & Both & 2143 & 0 & -5.2828 & 3 & 0.9907 & 0.5 & 57 & Yes*\\
-9 & NA & Both & NA & 0 & -5.0293 & 3 & - & - & - & NA\\
-10 & Puerto Aventuras, Mexico & Both & 109 & 0 & -5.4941 & 3 & 0.9766 & 5.7 & 38.1 & No\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\clearpage
-
-\section{Figures}\label{figures}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Map of the study area. The black inset on the left (Yucatan
-Peninsula) indicates the location where study sites are distributed. On
-the right, circular markers indicate sampling sites and the black
-romboid indicates location of Puerto Aventuras, Mexico.}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{Kernell density plots for a) Total length (mm) and b) Total
-weight (gr) for 109 lionfish sampled in the central Mexican Caribbean.}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{Length-weight relationship for 109 lionfish sampled in the
-central Mexican Caribbean. Points indicate samples, solid line indicates
-curve of best fit.}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{Length-weight relationships (n = 14) for eight studies, this
-study, and Fishbase. Colors indicate studies from which the parameters
-were extracted. Solid lines indicate that the fit was performed for
-males and females pooled together. Dotted lines indicate that the
-regression was performed on females, and dashed lines indicate it was
-performed for males.}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{. Box and whiskers plot showing the distribution of predicted
-to observed biomass ratios for 14 pairs of allometric parameters. Lines
-indicate median values, circles indicate mean values, notches represent
-95\% confidence intervals arround the median, lower and upper hinges
-correspond to the first and third quartiles, whiskers extend to the
-largest and lowes values within 1.5 inter-quartile range of the hinge,
-small points represent outliers further away than the whiskers. Like
-letters indicate values that do not differ significantly (Tukey's HSD; p
-\textless{} 0.05).}
-\end{figure}
-
 \end{document}

### 2018-02-24 Manuscript.Rmd
Need to work a lot more on this, the reviewers gave good comments but it needs A LOT more work

@@
 ---
-title: \Large{Weight-at-length of the invasive lionfish \textit{Pterois volitans} (Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}
-fontsize: 12pt
+title: "Allometric growth parameters for invasive lionfish *Pterois volitans* (Actinopterygii, Scorpaenidae) in the Western Atlantic"
+author: "Juan Carlos Villaseñor-Derbez"
+institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
+abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean.
+In order to better manage the invasion, inform lionfish removal programs, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass, frequently from length observations.
+This work compares length-weight relationships of the invasive lionfish through the invasion range and reports the length--weight relationship for lionfish in the Central Mexican Caribbean.
+A review of 13 length--weight relationships reported in eight peer-reviewed studies and FishBase is provided.
+These parameters were used to identify spatial variation in weight-at-length.
+For a given length, parameters from the Caribbean yielded lower weights than those from the Gulf of Mexico and Atlantic, indicating that weight-at-length is spatially variable.
+This highlights the importance of using site-specific parameters to estimate biomass from length observations.
+This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean.
+Findings from this work can aid managers and decision makers to better select length-weight parameters when these are not available for their region of interest."
 output:
-  word_document:
-    fig_caption: yes
-    keep_md: yes
-header-includes:
-- \usepackage{setspace}
-- \doublespacing
-# - \usepackage{lineno}
-# - \linenumbers
-subtitle: '**Running title**: Length-Weight relationships of lionfish'
-bibliography:
-- references.bib
-- packages.bib
-csl: huct.csl
+  bookdown::pdf_document2:
+    keep_tex: yes
+    template: peerj_template.tex
 ---
-<script type="text/x-mathjax-config">
-MathJax.Hub.Config({
-  TeX: { 
-      equationNumbers: { 
-            autoNumber: "all",
-            formatNumber: function (n) {return '9.'+n}
-      } 
-  }
-});
-</script>
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F)
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = F, warning = F, message = F)
 
@@
 })
-
-# source('./update_ref.R')
-# update_ref()
 ```
-
-Juan Carlos Villaseñor-Derbez^1^
-
-^1^ Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S.
-
-\* Correspondence: Juan Carlos Villaseñor-Derbez, Bren Hall, University of California at Santa Barbara, 
-Santa Barbara, CA, 93106, US phone: +1 207 205 8435, e-mail: jvillasenor@bren.ucsb.edu
-
-\clearpage
-
-**Abstract**
-
-Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean.
-In order to better manage the invasion, inform lionfish removal programs, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass, frequently from length observations.
-This work compares length-weight relationships of the invasive lionfish through the invasion range and reports the length--weight relationship for lionfish in the Central Mexican Caribbean.
-A review of 13 length--weight relationships reported in eight peer-reviewed studies and FishBase is provided.
-These parameters were used to identify spatial variation in weight-at-length.
-For a given length, parameters from the Caribbean yielded lower weights than those from the Gulf of Mexico and Atlantic, indicating that weight-at-length is spatially variable.
-This highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean.
-Findings from this work can aid managers and decision makers to better select length-weight parameters when these are not available for their region of interest.
-
-**Resumen**
-
-El pez león (*Pterois volitans/miles*) es una especie invasora en el Atlántico Noroeste y el Mar Caribe.
-Para tener un mejor manejo de la invasión, informar programas de remoción y estimar la biomasa disponible para aprovechamiento, debemos ser capaces de estimar la biomasa disponible con presisión, frecuentemente a partir de observaciones de tallas.
-Este trabajo compara la relación longitud--peso del pez león a través del rango de invasión, y reporta un nuevo par de parámetros de crecimiento alométrico para la zona central del Caribe Mexicano.
-El trabajo presenta revisión de 13 relaciones longitud--peso reportadas reportadas en ocho estudios publicados en revistas arbitradas y FishBase.
-Para una misma talla, los parámetros del Caribe indican un mejor peso que los parámetros del Golfo de México y el Atlántico, indicando una variabilidad espacial en la relación longitud peso.
-Esta variabilidad resalta la importancia de utilizar parámetros específicos a un sitio al estimar biomasa a partir de observaciones de tallas.
-Este estudio también reporta una nueva relación longitud--peso ($a = 3.2056\times 10^{-6}; b = 3.235$) para organismos muestreados en la costa central del Caribe Mexicano.
-Los resultados de este trabajo pueden ayudar a tomadores de decisiones en la selección de relaciones longitud-peso cuando éstas no están disponibles para su zona de interés.
-
-**Key words**   
-biometry, invasive species, spatial variability, allometric growth, Mexico
-
-\clearpage
 
@@
 
-At least 84% of the marine eco-regions have reported the presence of an invasive species [@molnar_2008].
-These represent a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries [@bax_2003].
-Invasive species may also threaten native species through competition [@davis_2003] or predation.
-By 2005, the economic cost of invasive species to the United States was  estimated at \$120 billion per year and nearly 42% of species that have been included in the Endangered or Threatened species list have been labeled as such due to presence of invasive species [@pimentel_2005].
+At least 84% of the marine eco-regions have reported the presence of an invasive species \citep{molnar_2008}.
+These represent a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries \citep{bax_2003}.
+Invasive species may also threaten native species through competition \citep{davis_2003} or predation.
+By 2005, the economic cost of invasive species to the United States was  estimated at \$120 billion per year and nearly 42% of species that have been included in the Endangered or Threatened species list have been labeled as such due to presence of invasive species \citep{pimentel_2005}.
 This highlights the importance of understanding, managing, and preventing ecological invasions.
 
-Lionfish (*Pterois volitans/miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms [@betancurr_2011].
-They are the first marine vertebrates to establish in North Atlantic [@schofield_2009; @schofield_2010] and Caribbean coasts [@sabidoitza_2016].
-Lionfish have been widely reported in coral reefs [@aguilarperera_2010], but also in other habitats such as estuaries [@jud_2011], mangroves [@barbour_2010], areas with hard-bottoms [@muoz_2011], and mesophotic reefs [@andradibrown_2017].
-Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion  [@hixon_2016].
+Lionfish (*Pterois volitans/miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
+They are the first marine vertebrates to establish in North Atlantic \citep{schofield_2009,schofield_2010} and Caribbean coasts \citep{sabidoitza_2016}.
+Lionfish have been widely reported in coral reefs \citep{aguilarperera_2010}, but also in other habitats such as estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with hard-bottoms \citep{muoz_2011}, and mesophotic reefs \citep{andradibrown_2017}.
+Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion  \citep{hixon_2016}.
 
-A significant amount of research has been done to describe lionfish feeding ecology in North Carolina [@muoz_2011], the Bahamas [@morris_2009; @cote_2013], Northern Gulf of Mexico [@dahl_2014], Mexican Caribbean [@valdezmoreno_2012; @villaseorderbez_2014], Belize [@hackerott_2017], and Costa Rica [@sandel_2015].
-Their feeding behavior and high consumption rates can reduce recruitment [@albins_2008] and population sizes [@green_2012] of native reef-fish species, and further the endangerment of critically endangered reef fish [@rocha_2015].
-(However, see @hackerott_2017 for a case where there was no evidence that lionfish affected the density, richness, or composition of prey fishes).
-Major efforts have also been made to understand the possible impacts of the invasion by keeping track of its range through time [@schofield_2009; @schofield_2010] and predicting invasion ranges under climate change scenarios [@grieve_2016].
-By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish [@ariasgonzalez_2011], which can then be translated into ecosystem-level and economic impacts.
+A significant amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
+Their feeding behavior and high consumption rates can reduce recruitment \citep{albins_2008} and population sizes \citep{green_2012} of native reef-fish species, and further the endangerment of critically endangered reef fish \citep{rocha_2015}.
+(However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or composition of prey fishes).
+Major efforts have also been made to understand the possible impacts of the invasion by keeping track of its range through time \citep{schofield_2009,schofield_2010} and predicting invasion ranges under climate change scenarios \citep{grieve_2016}.
+By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish \citep{ariasgonzalez_2011}, which can then be translated into ecosystem-level and economic impacts.
 
-Seeking to reduce lionfish densities, governments and non-profit organizations have promoted removal programs and incentivized its consumption [@chin_2016].
-In some cases, these have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales [@sandel_2015, @chin_2016, @deleon_2013].
-The rapid recovery rates exhibited by lionfish [@barbour_2011] and the persistent populations in mesophotic coral ecosystems [@andradibrown_2017] -which can contribute with recruitment to shallow-water populations- make of complete eradication through fishing effort an unlikely solution.
-However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery [@chin_2016], which can reduce local abundances and control -not eradicate- the invasion while providing alternative livelihoods.
+Seeking to reduce lionfish densities, governments and non-profit organizations have promoted removal programs and incentivized its consumption \citep{chin_2016}.
+In some cases, these have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
+The rapid recovery rates exhibited by lionfish \citep{barbour_2011} and the persistent populations in mesophotic coral ecosystems \citep{andradibrown_2017} -which can contribute with recruitment to shallow-water populations- make of complete eradication through fishing effort an unlikely solution.
+However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery \citep{chin_2016}, which can reduce local abundances and control -not eradicate- the invasion while providing alternative livelihoods.
 
-The feasibility of lionfish removal programs has been extensively evaluated through field observations[@usseglio_2017; @sandel_2015, @chin_2016, @deleon_2013] and empirical modeling [@barbour_2011; @morris_2011; @johnston_2015].
-The latter measure changes in biomass or density [@barbour_2011; @johnston_2015] in response to increased mortality (*i.e.* lionfish removal).
+The feasibility of lionfish removal programs has been extensively evaluated through field observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}.
+The latter measure changes in biomass or density \citep{barbour_2011,johnston_2015} in response to increased mortality (*i.e.* lionfish removal).
 In this case, biomass represents the sum of all fish's individual weight.
 Total Weight (TW) can be estimated from Total Length (TL) observations using the allometric growth equation ($TW = aTL^b$).
-Parameters $a$ and $b$ for this equation exist for North Carolina [@barbour_2011], Northern [@fogg_2013] and Southern Gulf of Mexico [@aguilarperera_2016], the Southern Mexican Caribbean [@sabidoitza_2016], Little Cayman [@edwards_2014], Jamaica [@chin_2016], Bonaire [@deleon_2013] and Costa Rica [@sandel_2015], but remain unavailable for the central Mexican Caribbean.
-The weight-at-length of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions [@johnson_2016].
+Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean.
+The weight-at-length of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
 Thus, when using biomass-informed models or estimating biomass from length observations, it is important to use site-specific parameters to obtain an accurate estimate.
-This is especially important when research involves identifying the total biomass available for harvest by fishers [@chin_2016] or the efficacy of lionfish removals [@barbour_2011; @morris_2011; @johnston_2015].
+This is especially important when research involves identifying the total biomass available for harvest by fishers \citep{chin_2016} or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015}.
 
@@
 
-The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean (**Fig.
-1**).
-The region represents the northernmost section of the Mesoamerican Barrier Reef System [@ruizzarate_2004].
-Coral reefs and mangroves are locally important habitats that represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism, the main source of income to the local economy [@murray_2007].
+The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean Figure \ref{fig:map}.
+The region represents the northernmost section of the Mesoamerican Barrier Reef System \citep{ruizzarate_2004}.
+Coral reefs and mangroves are locally important habitats that represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism, the main source of income to the local economy \citep{murray_2007}.
 
-The reef profile has been described by @ariasgonzalez_1998, indicating that the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
+The reef profile has been described by \citet{ariasgonzalez_1998}, indicating that the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
 The reef becomes deeper, leading to the reef front often found at 700 m from the coastline and extends for an additional 300 m.
@@
 Along a perpendicular profile to the coast, bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18 m deep.
-Along the coast, these reefs have been reported to be under significant anthropogenic pressure, likely causing a shift in structure and function [@bozec_2008].
+Along the coast, these reefs have been reported to be under significant anthropogenic pressure, likely causing a shift in structure and function \citep{bozec_2008}.
 
-```{r create map, fig.cap = "Map of the study area.
+```{r fig.cap = "\\label{fig:map}Map of the study area.
 The black inset on the left (Yucatan Peninsula) indicates the location where study sites are distributed.
@@
 
-$$TW = aTL^b$$
+\begin{equation}
+\label{eq:allometric}
+TW = aTL^b
+\end{equation}
 
@@
 
-$$log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)$$
+\begin{equation}
+\label{eq:log-alo}
+log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)
+\end{equation}
 
@@
 
-$$Y = mX + c$$
+\begin{equation}
+\label{eq:log-alo-trans}
+Y = mX + c
+\end{equation}
 
@@
 Other length-weight relationships (n = 13) were extracted from peer-reviewed literature.
-Parameters were obtained for North Carolina [n = 1; @barbour_2011], Northern [n = 3; @fogg_2013] and Southern Gulf of Mexico [n = 3; @aguilarperera_2016], the Southern Mexican Caribbean [n = 1; @sabidoitza_2016], Little Cayman [n = 1; @edwards_2014], Jamaica [n = 1; @chin_2016], Bonaire [n = 1; @deleon_2013] and Costa Rica [n = 1; @sandel_2015] and Fishbase [n = 1; @froese_website_2016] were also included.
+Parameters were obtained for North Carolina [n = 1,barbour_2011], Northern [n = 3,fogg_2013] and Southern Gulf of Mexico [n = 3,aguilarperera_2016], the Southern Mexican Caribbean [n = 1,sabidoitza_2016], Little Cayman [n = 1,edwards_2014], Jamaica [n = 1,chin_2016], Bonaire [n = 1,deleon_2013] and Costa Rica [n = 1,sandel_2015] and Fishbase [n = 1,froese_website_2016] were also included.
 When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retrieved.
@@
 
-All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 [@rcore_2017].
-Data wrangling was done with the tidyverse package [@tidyverse_2017].
-Maps were created with a mix of functions from the sp [@sp_2017], rgdal [@rgdal_2017], tmap [@tmap_2017], and tmaptools [@tmaptools_2017] packages.
-Heteroskedastic-robust standard errors were calculated with the sandwich [@sandwich_2014] and lmtest [@lmtest_2002] packages.
-Models were manipulated with the broom package [@broom_2017].
-RefManageR [@RefManager_2014] was used to keep track of citations.
-Raw data and code used in this work is available at [github.com/jcvdav/lionfish_biometry](github.com/jcvdav/lionfish_biometry).
+All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 \citep{rcore_2017}.
+Data wrangling was done with the tidyverse package \citep{tidyverse_2017}.
+Maps were created with a mix of functions from the sp \citep{sp_2017}, rgdal \citep{rgdal_2017}, tmap \citep{tmap_2017}, and tmaptools \citep{tmaptools_2017} packages.
+Heteroskedastic-robust standard errors were calculated with the sandwich \citep{sandwich_2014} and lmtest \citep{lmtest_2002} packages.
+Models were manipulated with the broom package \citep{broom_2017}.
+Raw data and code used in this work is available at github.com/jcvdav/lionfish_biometry.
 
@@
                col.names = c("Reference", "Region", "Sex", "a", "c", "b", "R2", "n", "mDepth", "MDepth", "Spear"),
-               caption = c("Summary of 13 allometric growth parameters available for lionfish in the invaded range from eight peer-reviewed papers, Fishbase [@froese_website_2016], and this study.
+               caption = c("Summary of 13 allometric growth parameters available for lionfish in the invaded range from eight peer-reviewed papers, Fishbase \\citep{froese_website_2016}, and this study.
 All parameters have been adjusted to convert from millimeters to grams.
@@
 An asterisk indicates that some portion of organisms were sampled with pole spears.
-1 = @aguilarperera_2016, 2 = @sandel_2015, 3 = @chin_2016, 4 = @barbour_2011, 5 = @deleon_2013, 6 = @fogg_2013, 7 = @edwards_2014, 8 = @sabidoitza_2016, 9 = @froese_website_2016, 10 = This study.")) %>%
+1 = \\citet{aguilarperera_2016}, 2 = \\citet{sandel_2015}, 3 = \\citet{chin_2016}, 4 = \\citet{barbour_2011}, 5 = \\citet{deleon_2013}, 6 = \\citet{fogg_2013}, 7 = \\citet{edwards_2014}, 8 = \\citet{sabidoitza_2016}, 9 = \\citet{froese_website_2016}, 10 = This study.")) %>%
   kableExtra::kable_styling(latex_options = c("scale_down"))
@@
 From the eight peer-reviewed studies including information on growth parameters for *P.
-volitans* and Fishbase [@froese_website_2016], `r dim(review)[1]-1` parameters were identified (Table III).
-Two studies [@aguilarperera_2016; @fogg_2013] reported gender-level and pooled parameters, while the rest presented pooled results.
-The smallest coefficient of determination was presented by @chin_2016 with $R^2 = `r min(review[,13], na.rm = T)`$, while @sabidoitza_2016 reported the highest value at $R^2 = `r max(review[,13], na.rm = T)`$.
+volitans* and Fishbase \citep{froese_website_2016}, `r dim(review)[1]-1` parameters were identified (Table III).
+Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
+The smallest coefficient of determination was presented by \citet{chin_2016} with $R^2 = `r min(review[,13], na.rm = T)`$, while \citet{sabidoitza_2016} reported the highest value at $R^2 = `r max(review[,13], na.rm = T)`$.
 Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
-Two studies [@aguilarperera_2016; @chin_2016] explicitly stated that their organisms were sampled with pole spears.
-Five studies [@sandel_2015; @barbour_2011; @fogg_2013; @edwards_2014; @sabidoitza_2016] mentioned that some of their organisms were obtained with pole spears (or other type of harpoon).
-A single study [@deleon_2013] did not specify how organisms were sampled.
+Two studies \citep{aguilarperera_2016,chin_2016} explicitly stated that their organisms were sampled with pole spears.
+Five studies \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016} mentioned that some of their organisms were obtained with pole spears (or other type of harpoon).
+A single study \citep{deleon_2013} did not specify how organisms were sampled.
 
@@
 
-predicted_all <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
+predicted_all <- data.frame(Length = seq(1, 300, by = 1)) %>% 
   mutate(This = review$a[14] * (Length^review$b[14]), 
@@
 
-groups$groups$Study_id <- str_replace_all(as.character(groups$groups$trt), " ", "")
+groups$groups%<>%
+  mutate(Study_id = rownames(.)) %>% 
+  select(-Biomass_ratio)
 
@@
   left_join(groups$groups, by = "Study_id")
-
 ```
@@
 There were significant differences in expected-to-observed weight ratios estimated for each pair of parameters (F(13, 1512) = 39.28; p < 0.05).
-From all allometric parameters reviewed, those of @edwards_2014 provided the lowest weight estimates, with an expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-On the other hand, @barbour_2011 yielded the highest weight estimates, with a mean ($\pm$ SD) expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
+From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
+On the other hand,barbour_2011 yielded the highest weight estimates, with a mean ($\pm$ SD) expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
 Predicted-to-observed weight ratios and groups identified by Tukey's HSD ($\alpha = 0.05$) are presented in Figure 5.
@@
         legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted")) +
-  geom_text(aes(y = 3.6, label = M), family = "Times", fontface = "plain") +
+  geom_text(aes(y = 3.6, label = groups), family = "Times", fontface = "plain") +
   scale_y_continuous(limits = c(NA, 3.6))
@@
 
-This study provides the first pair of allometric growth parameters specific to the Central Mexican Caribbean, complementing other studies performed in Mexican waters in the Alacranes Reef [@aguilarperera_2016] and Xcalak National Park [@sabidoitza_2016].
+This study provides the first pair of allometric growth parameters specific to the Central Mexican Caribbean, complementing other studies performed in Mexican waters in the Alacranes Reef \citep{aguilarperera_2016} and Xcalak National Park \citep{sabidoitza_2016}.
 By using hand nets instead of spears, we are able to sample a wider range of sizes often ignored by pole spear samples, allowing us to include smaller organisms.
@@
 
-The length-weight coefficients estimated in this study were within the range identified by studies in other regions [@barbour_2011; @fogg_2013; @aguilarperera_2016; @sabidoitza_2016; @edwards_2014; @chin_2016; @deleon_2013; @sandel_2015].
+The length-weight coefficients estimated in this study were within the range identified by studies in other regions \citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016,edwards_2014,chin_2016,deleon_2013,sandel_2015}.
 However, the ones presented here provide lower weight estimates for a same length.
-Until about TL = 200 mm, there are no appreciable differences between the parameters for organisms from the Mexican Caribbean and those for little Cayman [@edwards_2014] and Jamaica [@chin_2016].
-Yet, for larger organisms (TL > 270 mm) parameters from Costa Rica [@sandel_2015] and Bonaire [@deleon_2013] provide similar estimates to those from this study.
+Until about TL = 200 mm, there are no appreciable differences between the parameters for organisms from the Mexican Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica \citep{chin_2016}.
+Yet, for larger organisms (TL > 270 mm) parameters from Costa Rica \citep{sandel_2015} and Bonaire \citep{deleon_2013} provide similar estimates to those from this study.
 Conversely, these same studies tend to estimate higher weights ---as compared to the ones reported here--- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
@@
 There are evident differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
-Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic [@barbour_2011; @fogg_2013; @aguilarperera_2016; @sabidoitza_2016] tend to be higher than those from the Caribbean [@edwards_2014; @chin_2016; @deleon_2013; @sandel_2015], except for the ones from Xcalak National Park, Mexico [@sabidoitza_2016].
+Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic \citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016} tend to be higher than those from the Caribbean \citep{edwards_2014,chin_2016,deleon_2013,sandel_2015}, except for the ones from Xcalak National Park, Mexico \citep{sabidoitza_2016}.
 This indicates that there are differences between lionfish across the invasion range.
-Similar regional variation exist for age-at-length relationships of lionfish [@fogg_2015].
+Similar regional variation exist for age-at-length relationships of lionfish \citep{fogg_2015}.
 These differences can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
@@
 At the same time, this highlights the need for more basic research that furthers our understanding of lionfish biology.
-To better manageme the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range [@johnson_2016].
+To better manageme the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range \citep{johnson_2016}.
 
@@
 3.
-Specify the equation for which parameters are presented by including an explicit example with the parameters substituted into it, as done by some of the papers reviewed [@chin_2016; @sandel_2015; @deleon_2013; @sabidoitza_2016].
+Specify the equation for which parameters are presented by including an explicit example with the parameters substituted into it, as done by some of the papers reviewed \citep{chin_2016,sandel_2015,deleon_2013,sabidoitza_2016}.
 If possible, present the relationship in their exponential (eq.
@@
 
-# References
+\bibliography{references}

### 2018-02-24 Manuscript.tex
Need to work a lot more on this, the reviewers gave good comments but it needs A LOT more work

@@
-\documentclass[12pt,]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{longtable,booktabs}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+%% Submissions for peer-review must enable line-numbering 
+%% using the lineno option in the \documentclass command.
+%%
+%% Preprints and camera-ready submissions do not need 
+%% line numbers, and should have this option removed.
+%%
+%% Please note that the line numbering option requires
+%% version 1.1 or newer of the wlpeerj.cls file, and
+%% the corresponding author info requires v1.2
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+\documentclass[fleqn,10pt,lineno]{wlpeerj} % for journal submissions
+% \documentclass[fleqn,10pt]{wlpeerj} % for preprint submissions
 
-%%% Change title format to be more compact
-\usepackage{titling}
+\title{Allometric growth parameters for invasive lionfish \emph{Pterois
+volitans} (Actinopterygii, Scorpaenidae) in the Western Atlantic}
 
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
+\author[1]{Juan Carlos Villaseñor-Derbez}
+\affil[1]{Bren School of Environmental Sciences and Management, University of
+California Santa Barbara, Santa Barbara, California, U.S.}
+\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@bren.ucsb.edu}
 
-\setlength{\droptitle}{-2em}
-  \title{\Large{Weight-at-length of the invasive lionfish \textit{Pterois volitans} (Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range}}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-\subtitle{\textbf{Running title}: Length-Weight relationships of lionfish}
-  \author{}
-  \preauthor{}\postauthor{}
-  \date{}
-  \predate{}\postdate{}
+% \keywords{Keyword1, Keyword2, Keyword3}
 
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage[table]{xcolor}
-\usepackage{wrapfig}
-\usepackage{setspace}
-\doublespacing
-
-\begin{document}
-\maketitle
-
-Juan Carlos Villaseñor-Derbez\textsuperscript{1}
-
-\textsuperscript{1} Bren School of Environmental Sciences and
-Management, University of California Santa Barbara, Santa Barbara,
-California, U.S.
-
-* Correspondence: Juan Carlos Villaseñor-Derbez, Bren Hall, University
-of California at Santa Barbara, Santa Barbara, CA, 93106, US phone: +1
-207 205 8435, e-mail:
-\href{mailto:jvillasenor@bren.ucsb.edu}{\nolinkurl{jvillasenor@bren.ucsb.edu}}
-
-\clearpage
-
-\textbf{Abstract}
-
+\begin{abstract}
 Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
@@
 from length observations. This study also reports a new pair of
-length-weight parameters (\(a = 3.2056\times 10^{-6}; b = 3.235\)) for
+length-weight parameters (\(a = 3.2056 imes 10^{-6}; b = 3.235\)) for
 organisms sampled in the Central Mexican Caribbean. Findings from this
@@
 parameters when these are not available for their region of interest.
+\end{abstract}
 
-\textbf{Resumen}
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\theoremstyle{definition}
+\newtheorem{example}{Example}[section]
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}[section]
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
 
-El pez león (\emph{Pterois volitans/miles}) es una especie invasora en
-el Atlántico Noroeste y el Mar Caribe. Para tener un mejor manejo de la
-invasión, informar programas de remoción y estimar la biomasa disponible
-para aprovechamiento, debemos ser capaces de estimar la biomasa
-disponible con presisión, frecuentemente a partir de observaciones de
-tallas. Este trabajo compara la relación longitud--peso del pez león a
-través del rango de invasión, y reporta un nuevo par de parámetros de
-crecimiento alométrico para la zona central del Caribe Mexicano. El
-trabajo presenta revisión de 13 relaciones longitud--peso reportadas
-reportadas en ocho estudios publicados en revistas arbitradas y
-FishBase. Para una misma talla, los parámetros del Caribe indican un
-mejor peso que los parámetros del Golfo de México y el Atlántico,
-indicando una variabilidad espacial en la relación longitud peso. Esta
-variabilidad resalta la importancia de utilizar parámetros específicos a
-un sitio al estimar biomasa a partir de observaciones de tallas. Este
-estudio también reporta una nueva relación longitud--peso
-(\(a = 3.2056\times 10^{-6}; b = 3.235\)) para organismos muestreados en
-la costa central del Caribe Mexicano. Los resultados de este trabajo
-pueden ayudar a tomadores de decisiones en la selección de relaciones
-longitud-peso cuando éstas no están disponibles para su zona de interés.
-
-\textbf{Key words}\\
-biometry, invasive species, spatial variability, allometric growth,
-Mexico
-
-\clearpage
+\flushbottom
+\maketitle
+\thispagestyle{empty}
 
@@
 At least 84\% of the marine eco-regions have reported the presence of an
-invasive species (Molnar et al., 2008). These represent a major threat
-to local biodiversity and the economic activities that depend on it,
-like tourism or fisheries (Bax et al., 2003). Invasive species may also
-threaten native species through competition (DAVIS, 2003) or predation.
-By 2005, the economic cost of invasive species to the United States was
-estimated at \$120 billion per year and nearly 42\% of species that have
-been included in the Endangered or Threatened species list have been
-labeled as such due to presence of invasive species (Pimentel, Zuniga \&
-Morrison, 2005). This highlights the importance of understanding,
+invasive species \citep{molnar_2008}. These represent a major threat to
+local biodiversity and the economic activities that depend on it, like
+tourism or fisheries \citep{bax_2003}. Invasive species may also
+threaten native species through competition \citep{davis_2003} or
+predation. By 2005, the economic cost of invasive species to the United
+States was estimated at \$120 billion per year and nearly 42\% of
+species that have been included in the Endangered or Threatened species
+list have been labeled as such due to presence of invasive species
+\citep{pimentel_2005}. This highlights the importance of understanding,
 managing, and preventing ecological invasions.
@@
 in the North-Western Atlantic and the Caribbean, likely introduced
-through liberation of aquarium-kept organisms (Betancur-R et al., 2011).
+through liberation of aquarium-kept organisms \citep{betancurr_2011}.
 They are the first marine vertebrates to establish in North Atlantic
-(Schofield, 2009, 2010) and Caribbean coasts (Sabido-Itza et al., 2016).
-Lionfish have been widely reported in coral reefs (Aguilar-Perera \&
-Tuz-Sulub, 2010), but also in other habitats such as estuaries (Jud et
-al., 2011), mangroves (Barbour et al., 2010), areas with hard-bottoms
-(Muñoz, Currin \& Whitfield, 2011), and mesophotic reefs (Andradi-Brown
-et al., 2017). Due to its threat to local biodiversity, the speed of
-their spread, and its difficulty of management, their presence in these
-waters has been labeled as a major marine invasion (Hixon et al., 2016).
+\citep{schofield_2009,schofield_2010} and Caribbean coasts
+\citep{sabidoitza_2016}. Lionfish have been widely reported in coral
+reefs \citep{aguilarperera_2010}, but also in other habitats such as
+estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with
+hard-bottoms \citep{muoz_2011}, and mesophotic reefs
+\citep{andradibrown_2017}. Due to its threat to local biodiversity, the
+speed of their spread, and its difficulty of management, their presence
+in these waters has been labeled as a major marine invasion
+\citep{hixon_2016}.
 
 A significant amount of research has been done to describe lionfish
-feeding ecology in North Carolina (Muñoz, Currin \& Whitfield, 2011),
-the Bahamas (Morris \& Akins, 2009; Cote et al., 2013), Northern Gulf of
-Mexico (Dahl \& Patterson, 2014), Mexican Caribbean (Valdez-Moreno et
-al., 2012; Villaseñor-Derbez \& Herrera-P\a'erez, 2014), Belize
-(Hackerott et al., 2017), and Costa Rica (Sandel et al., 2015). Their
+feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas
+\citep{morris_2009,cote_2013}, Northern Gulf of Mexico
+\citep{dahl_2014}, Mexican Caribbean
+\citep{valdezmoreno_2012,villaseorderbez_2014}, Belize
+\citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}. Their
 feeding behavior and high consumption rates can reduce recruitment
-(Albins \& Hixon, 2008) and population sizes (Green et al., 2012) of
-native reef-fish species, and further the endangerment of critically
-endangered reef fish (Rocha et al., 2015). (However, see Hackerott et
-al. (2017) for a case where there was no evidence that lionfish affected
-the density, richness, or composition of prey fishes). Major efforts
-have also been made to understand the possible impacts of the invasion
-by keeping track of its range through time (Schofield, 2009, 2010) and
-predicting invasion ranges under climate change scenarios (Grieve,
-Curchitser \& Rykaczewski, 2016). By combining information from these
-disciplines, researchers have been able to predict the trophic impacts
-of lionfish (Arias-Gonzalez et al., 2011), which can then be translated
-into ecosystem-level and economic impacts.
+\citep{albins_2008} and population sizes \citep{green_2012} of native
+reef-fish species, and further the endangerment of critically endangered
+reef fish \citep{rocha_2015}. (However, see \citet{hackerott_2017} for a
+case where there was no evidence that lionfish affected the density,
+richness, or composition of prey fishes). Major efforts have also been
+made to understand the possible impacts of the invasion by keeping track
+of its range through time \citep{schofield_2009,schofield_2010} and
+predicting invasion ranges under climate change scenarios
+\citep{grieve_2016}. By combining information from these disciplines,
+researchers have been able to predict the trophic impacts of lionfish
+\citep{ariasgonzalez_2011}, which can then be translated into
+ecosystem-level and economic impacts.
 
@@
 organizations have promoted removal programs and incentivized its
-consumption (Chin, Aiken \& Buddo, 2016). In some cases, these have
-shown to significantly reduce -but not quite eliminate- lionfish
-abundances at local scales (Sandel et al., 2015, Chin, Aiken \& Buddo
-(2016), de Leon et al. (2013)). The rapid recovery rates exhibited by
-lionfish (Barbour et al., 2011) and the persistent populations in
-mesophotic coral ecosystems (Andradi-Brown et al., 2017) -which can
-contribute with recruitment to shallow-water populations- make of
-complete eradication through fishing effort an unlikely solution.
-However, further incentivizing its consumption might create a demand big
-enough to promote and sustain a stable fishery (Chin, Aiken \& Buddo,
-2016), which can reduce local abundances and control -not eradicate- the
-invasion while providing alternative livelihoods.
+consumption \citep{chin_2016}. In some cases, these have shown to
+significantly reduce -but not quite eliminate- lionfish abundances at
+local scales \citep{sandel_2015,chin_2016,deleon_2013}. The rapid
+recovery rates exhibited by lionfish \citep{barbour_2011} and the
+persistent populations in mesophotic coral ecosystems
+\citep{andradibrown_2017} -which can contribute with recruitment to
+shallow-water populations- make of complete eradication through fishing
+effort an unlikely solution. However, further incentivizing its
+consumption might create a demand big enough to promote and sustain a
+stable fishery \citep{chin_2016}, which can reduce local abundances and
+control -not eradicate- the invasion while providing alternative
+livelihoods.
 
 The feasibility of lionfish removal programs has been extensively
-evaluated through field observations(Sandel et al., 2015, Chin, Aiken \&
-Buddo (2016), de Leon et al. (2013); Usseglio et al., 2017) and
-empirical modeling (Barbour et al., 2011; Morris, Shertzer \& Rice,
-2011; Johnston \& Purkis, 2015). The latter measure changes in biomass
-or density (Barbour et al., 2011; Johnston \& Purkis, 2015) in response
-to increased mortality (\emph{i.e.} lionfish removal). In this case,
-biomass represents the sum of all fish's individual weight. Total Weight
-(TW) can be estimated from Total Length (TL) observations using the
-allometric growth equation (\(TW = aTL^b\)). Parameters \(a\) and \(b\)
-for this equation exist for North Carolina (Barbour et al., 2011),
-Northern (Fogg et al., 2013) and Southern Gulf of Mexico (Aguilar-Perera
-\& Quijano-Puerto, 2016), the Southern Mexican Caribbean (Sabido-Itza et
-al., 2016), Little Cayman (Edwards, Frazer \& Jacoby, 2014), Jamaica
-(Chin, Aiken \& Buddo, 2016), Bonaire (de Leon et al., 2013) and Costa
-Rica (Sandel et al., 2015), but remain unavailable for the central
-Mexican Caribbean. The weight-at-length of a species can vary across
-regions as a response to biotic (\emph{e.g.} local food availability)
-and abiotic (\emph{e.g.} water temperature) conditions (Johnson \&
-Swenarton, 2016). Thus, when using biomass-informed models or estimating
-biomass from length observations, it is important to use site-specific
-parameters to obtain an accurate estimate. This is especially important
-when research involves identifying the total biomass available for
-harvest by fishers (Chin, Aiken \& Buddo, 2016) or the efficacy of
-lionfish removals (Barbour et al., 2011; Morris, Shertzer \& Rice, 2011;
-Johnston \& Purkis, 2015).
+evaluated through field
+observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and
+empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}. The
+latter measure changes in biomass or density
+\citep{barbour_2011,johnston_2015} in response to increased mortality
+(\emph{i.e.} lionfish removal). In this case, biomass represents the sum
+of all fish's individual weight. Total Weight (TW) can be estimated from
+Total Length (TL) observations using the allometric growth equation
+(\(TW = aTL^b\)). Parameters \(a\) and \(b\) for this equation exist for
+North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013} and
+Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican
+Caribbean \citep{sabidoitza_2016}, Little Cayman \citep{edwards_2014},
+Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} and Costa Rica
+\citep{sandel_2015}, but remain unavailable for the central Mexican
+Caribbean. The weight-at-length of a species can vary across regions as
+a response to biotic (\emph{e.g.} local food availability) and abiotic
+(\emph{e.g.} water temperature) conditions \citep{johnson_2016}. Thus,
+when using biomass-informed models or estimating biomass from length
+observations, it is important to use site-specific parameters to obtain
+an accurate estimate. This is especially important when research
+involves identifying the total biomass available for harvest by fishers
+\citep{chin_2016} or the efficacy of lionfish removals
+\citep{barbour_2011,morris_2011,johnston_2015}.
 
@@
 The study took place off the coasts of Playa del Carmen, in the Mexican
-Caribbean (\textbf{Fig. 1}). The region represents the northernmost
-section of the Mesoamerican Barrier Reef System (Ruiz-Zarate \&
-Arias-Gonzalez, 2004). Coral reefs and mangroves are locally important
-habitats that represent important sources of income in terms of
-extractive (\emph{e.g.} recreational fishing) and non-extractive
-(\emph{e.g.} SCUBA diving) activities related to tourism, the main
-source of income to the local economy (Murray, 2007).
+Caribbean Figure \ref{fig:map}. The region represents the northernmost
+section of the Mesoamerican Barrier Reef System \citep{ruizzarate_2004}.
+Coral reefs and mangroves are locally important habitats that represent
+important sources of income in terms of extractive (\emph{e.g.}
+recreational fishing) and non-extractive (\emph{e.g.} SCUBA diving)
+activities related to tourism, the main source of income to the local
+economy \citep{murray_2007}.
 
-The reef profile has been described by Arias-Gonzalez (1998), indicating
-that the reef lagoon extends about 500 m from the coast, until the reef
-crest is reached. The reef becomes deeper, leading to the reef front
-often found at 700 m from the coastline and extends for an additional
-300 m. At approximately 1000 m away from shore and 30 - 40 m depth, the
-reef leads to a drop-off. Along a perpendicular profile to the coast,
-bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18
-m deep. Along the coast, these reefs have been reported to be under
-significant anthropogenic pressure, likely causing a shift in structure
-and function (Bozec et al., 2008).
+The reef profile has been described by \citet{ariasgonzalez_1998},
+indicating that the reef lagoon extends about 500 m from the coast,
+until the reef crest is reached. The reef becomes deeper, leading to the
+reef front often found at 700 m from the coastline and extends for an
+additional 300 m. At approximately 1000 m away from shore and 30 - 40 m
+depth, the reef leads to a drop-off. Along a perpendicular profile to
+the coast, bands of reef are interrupted by sand patches at 8 - 12 m
+deep and 16-18 m deep. Along the coast, these reefs have been reported
+to be under significant anthropogenic pressure, likely causing a shift
+in structure and function \citep{bozec_2008}.
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
-\includegraphics{Manuscript_files/figure-latex/create map-1.pdf}
-\caption{Map of the study area. The black inset on the left (Yucatan
-Peninsula) indicates the location where study sites are distributed. On
-the right, circular markers indicate sampling sites and the black
-romboid indicates location of Puerto Aventuras, Mexico.}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
+\caption{\label{fig:unnamed-chunk-1}\label{fig:map}Map of the study area.
+The black inset on the left (Yucatan Peninsula) indicates the location
+where study sites are distributed. On the right, circular markers
+indicate sampling sites and the black romboid indicates location of
+Puerto Aventuras, Mexico.}
 \end{figure}
@@
 
-\begin{longtable}[]{@{}llllllr@{}}
-\caption{Coordinates, minimum, maximum and mean depth (m), and number of
-samples for each location.}\tabularnewline
+\begin{table}
+
+\caption{(\#tab:table of locations)Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.}
+\centering
+\begin{tabular}[t]{llllllr}
 \toprule
-Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
-n\tabularnewline
+Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth & n\\
 \midrule
-\endfirsthead
-\toprule
-Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth &
-n\tabularnewline
-\midrule
-\endhead
-Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\tabularnewline
-Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\tabularnewline
-Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\tabularnewline
-Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\tabularnewline
-Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\tabularnewline
-Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\tabularnewline
-Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\tabularnewline
-Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\tabularnewline
-Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\tabularnewline
-Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\tabularnewline
-Total & & & 5.7 & 38.1 & 18.6 & 109\tabularnewline
+Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\\
+Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\\
+Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\\
+Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\\
+Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\\
+\addlinespace
+Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\\
+Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\\
+Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\\
+Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\\
+Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\\
+Total &  &  & 5.7 & 38.1 & 18.6 & 109\\
 \bottomrule
-\end{longtable}
+\end{tabular}
+\end{table}
 
@@
 
-\[TW = aTL^b\]
+\begin{equation}
+\label{eq:allometric}
+TW = aTL^b
+\end{equation}
 
@@
 
-\[log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)\]
+\begin{equation}
+\label{eq:log-alo}
+log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)
+\end{equation}
 
@@
 
-\[Y = mX + c\]
+\begin{equation}
+\label{eq:log-alo-trans}
+Y = mX + c
+\end{equation}
 
@@
 Other length-weight relationships (n = 13) were extracted from
-peer-reviewed literature. Parameters were obtained for North Carolina (n
-= 1; Barbour et al., 2011), Northern (n = 3; Fogg et al., 2013) and
-Southern Gulf of Mexico (n = 3; Aguilar-Perera \& Quijano-Puerto, 2016),
-the Southern Mexican Caribbean (n = 1; Sabido-Itza et al., 2016), Little
-Cayman (n = 1; Edwards, Frazer \& Jacoby, 2014), Jamaica (n = 1; Chin,
-Aiken \& Buddo, 2016), Bonaire (n = 1; de Leon et al., 2013) and Costa
-Rica (n = 1; Sandel et al., 2015) and Fishbase (n = 1; Froese \& Pauly,
-2016) were also included. When available, information on sampling
-methods, gender differentiation, location, and depth ranges of each
-study was retrieved. Whenever gender was not specified, it was assumed
-that the results were presented for pooled genders.
+peer-reviewed literature. Parameters were obtained for North Carolina
+{[}n = 1,barbour\_2011{]}, Northern {[}n = 3,fogg\_2013{]} and Southern
+Gulf of Mexico {[}n = 3,aguilarperera\_2016{]}, the Southern Mexican
+Caribbean {[}n = 1,sabidoitza\_2016{]}, Little Cayman {[}n =
+1,edwards\_2014{]}, Jamaica {[}n = 1,chin\_2016{]}, Bonaire {[}n =
+1,deleon\_2013{]} and Costa Rica {[}n = 1,sandel\_2015{]} and Fishbase
+{[}n = 1,froese\_website\_2016{]} were also included. When available,
+information on sampling methods, gender differentiation, location, and
+depth ranges of each study was retrieved. Whenever gender was not
+specified, it was assumed that the results were presented for pooled
+genders.
 
@@
 All hypothesis testing was performed with an \emph{a priori} confidence
-level of \(\alpha = 0.01\) in R version 3.4.0 (R Core Team, 2017). Data
-wrangling was done with the tidyverse package (Wickham, 2017). Maps were
-created with a mix of functions from the sp (Pebesma \& Bivand, 2005),
-rgdal (Bivand, Keitt \& Rowlingson, 2017), tmap (Tennekes, 2017a), and
-tmaptools (Tennekes, 2017b) packages. Heteroskedastic-robust standard
-errors were calculated with the sandwich (Zeileis, 2004) and lmtest
-(Zeileis \& Hothorn, 2002) packages. Models were manipulated with the
-broom package (Robinson, 2017). RefManageR (McLean, 2014) was used to
-keep track of citations. Raw data and code used in this work is
-available at \url{github.com/jcvdav/lionfish_biometry}.
+level of \(\alpha = 0.01\) in R version 3.4.0 \citep{rcore_2017}. Data
+wrangling was done with the tidyverse package \citep{tidyverse_2017}.
+Maps were created with a mix of functions from the sp \citep{sp_2017},
+rgdal \citep{rgdal_2017}, tmap \citep{tmap_2017}, and tmaptools
+\citep{tmaptools_2017} packages. Heteroskedastic-robust standard errors
+were calculated with the sandwich \citep{sandwich_2014} and lmtest
+\citep{lmtest_2002} packages. Models were manipulated with the broom
+package \citep{broom_2017}. Raw data and code used in this work is
+available at github.com/jcvdav/lionfish\_biometry.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
 \includegraphics{Manuscript_files/figure-latex/histogram figures-1.pdf}
-\caption{Kernell density plots for a) Total length (mm) and b) Total
-weight (gr) for 109 lionfish sampled in the central Mexican Caribbean.}
+\caption{(\#fig:histogram figures)Kernell density plots for a) Total
+length (mm) and b) Total weight (gr) for 109 lionfish sampled in the
+central Mexican Caribbean.}
 \end{figure}
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
 \includegraphics{Manuscript_files/figure-latex/scatter plot-1.pdf}
-\caption{Length-weight relationship for 109 lionfish sampled in the
-central Mexican Caribbean. Points indicate samples, solid line indicates
-curve of best fit.}
+\caption{(\#fig:scatter plot)Length-weight relationship for 109 lionfish
+sampled in the central Mexican Caribbean. Points indicate samples, solid
+line indicates curve of best fit.}
 \end{figure}
@@
 From the eight peer-reviewed studies including information on growth
-parameters for \emph{P. volitans} and Fishbase (Froese \& Pauly, 2016),
-13 parameters were identified (Table III). Two studies (Fogg et al.,
-2013; Aguilar-Perera \& Quijano-Puerto, 2016) reported gender-level and
-pooled parameters, while the rest presented pooled results. The smallest
-coefficient of determination was presented by Chin, Aiken \& Buddo
-(2016) with \(R^2 = 0.8715\), while Sabido-Itza et al. (2016) reported
-the highest value at \(R^2 = 0.9907\). Reviewed studies presented
+parameters for \emph{P. volitans} and Fishbase
+\citep{froese_website_2016}, 13 parameters were identified (Table III).
+Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level
+and pooled parameters, while the rest presented pooled results. The
+smallest coefficient of determination was presented by \citet{chin_2016}
+with \(R^2 = 0.8715\), while \citet{sabidoitza_2016} reported the
+highest value at \(R^2 = 0.9907\). Reviewed studies presented
 information for organisms obtained at depths between 0.5 and 57 m. Two
-studies (Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken \& Buddo,
-2016) explicitly stated that their organisms were sampled with pole
-spears. Five studies (Barbour et al., 2011; Fogg et al., 2013; Edwards,
-Frazer \& Jacoby, 2014; Sandel et al., 2015; Sabido-Itza et al., 2016)
+studies \citep{aguilarperera_2016,chin_2016} explicitly stated that
+their organisms were sampled with pole spears. Five studies
+\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016}
 mentioned that some of their organisms were obtained with pole spears
-(or other type of harpoon). A single study (de Leon et al., 2013) did
-not specify how organisms were sampled.
+(or other type of harpoon). A single study \citep{deleon_2013} did not
+specify how organisms were sampled.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
 \includegraphics{Manuscript_files/figure-latex/review plots-1.pdf}
-\caption{Length-weight relationships (n = 14) for eight studies, this
-study, and Fishbase. Colors indicate studies from which the parameters
-were extracted. Solid lines indicate that the fit was performed for
-males and females pooled together. Dotted lines indicate that the
-regression was performed on females, and dashed lines indicate it was
-performed for males.}
+\caption{(\#fig:review plots)Length-weight relationships (n = 14) for
+eight studies, this study, and Fishbase. Colors indicate studies from
+which the parameters were extracted. Solid lines indicate that the fit
+was performed for males and females pooled together. Dotted lines
+indicate that the regression was performed on females, and dashed lines
+indicate it was performed for males.}
 \end{figure}
@@
 \textless{} 0.05). From all allometric parameters reviewed, those of
-Edwards, Frazer \& Jacoby (2014) provided the lowest weight estimates,
-with an expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean
-\(\pm\) SD). On the other hand, Barbour et al. (2011) yielded the
-highest weight estimates, with a mean (\(\pm\) SD) expected-to-observed
-weight ratio of 1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios
-and groups identified by Tukey's HSD (\(\alpha = 0.05\)) are presented
-in Figure 5.
+\citet{edwards_2014} provided the lowest weight estimates, with an
+expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
+SD). On the other hand,barbour\_2011 yielded the highest weight
+estimates, with a mean (\(\pm\) SD) expected-to-observed weight ratio of
+1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
+identified by Tukey's HSD (\(\alpha = 0.05\)) are presented in Figure 5.
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
 \includegraphics{Manuscript_files/figure-latex/plot comparing predictions-1.pdf}
-\caption{. Box and whiskers plot showing the distribution of predicted
-to observed biomass ratios for 14 pairs of allometric parameters. Lines
-indicate median values, circles indicate mean values, notches represent
-95\% confidence intervals arround the median, lower and upper hinges
-correspond to the first and third quartiles, whiskers extend to the
-largest and lowes values within 1.5 inter-quartile range of the hinge,
-small points represent outliers further away than the whiskers. Like
-letters indicate values that do not differ significantly (Tukey's HSD; p
-\textless{} 0.05).}
+\caption{(\#fig:plot comparing predictions). Box and whiskers plot
+showing the distribution of predicted to observed biomass ratios for 14
+pairs of allometric parameters. Lines indicate median values, circles
+indicate mean values, notches represent 95\% confidence intervals
+arround the median, lower and upper hinges correspond to the first and
+third quartiles, whiskers extend to the largest and lowes values within
+1.5 inter-quartile range of the hinge, small points represent outliers
+further away than the whiskers. Like letters indicate values that do not
+differ significantly (Tukey's HSD; p \textless{} 0.05).}
 \end{figure}
@@
 specific to the Central Mexican Caribbean, complementing other studies
-performed in Mexican waters in the Alacranes Reef (Aguilar-Perera \&
-Quijano-Puerto, 2016) and Xcalak National Park (Sabido-Itza et al.,
-2016). By using hand nets instead of spears, we are able to sample a
-wider range of sizes often ignored by pole spear samples, allowing us to
-include smaller organisms. Estimating parameters by including smaller
-organisms ensures better estimation of weight for smaller sizes. This is
-especially important when biomass is calculated from visual census,
-where small organisms can be registered. Thus, this study also increases
-certainty in weight estimation of small organisms.
+performed in Mexican waters in the Alacranes Reef
+\citep{aguilarperera_2016} and Xcalak National Park
+\citep{sabidoitza_2016}. By using hand nets instead of spears, we are
+able to sample a wider range of sizes often ignored by pole spear
+samples, allowing us to include smaller organisms. Estimating parameters
+by including smaller organisms ensures better estimation of weight for
+smaller sizes. This is especially important when biomass is calculated
+from visual census, where small organisms can be registered. Thus, this
+study also increases certainty in weight estimation of small organisms.
 
 The length-weight coefficients estimated in this study were within the
-range identified by studies in other regions (Barbour et al., 2011; de
-Leon et al., 2013; Fogg et al., 2013; Edwards, Frazer \& Jacoby, 2014;
-Sandel et al., 2015; Aguilar-Perera \& Quijano-Puerto, 2016; Chin, Aiken
-\& Buddo, 2016; Sabido-Itza et al., 2016). However, the ones presented
-here provide lower weight estimates for a same length. Until about TL =
-200 mm, there are no appreciable differences between the parameters for
-organisms from the Mexican Caribbean and those for little Cayman
-(Edwards, Frazer \& Jacoby, 2014) and Jamaica (Chin, Aiken \& Buddo,
-2016). Yet, for larger organisms (TL \textgreater{} 270 mm) parameters
-from Costa Rica (Sandel et al., 2015) and Bonaire (de Leon et al., 2013)
-provide similar estimates to those from this study. Conversely, these
-same studies tend to estimate higher weights ---as compared to the ones
-reported here--- for smaller organisms, likely due to the lack of small
-organisms in the samples used to estimate their parameters. When ever
-possible, future works should consider the use of hand nets to obtain
-the samples not only for studies on weight-at-length, but also diet,
-behavior and life history, where length can be an important factor.
+range identified by studies in other regions
+\citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016,edwards_2014,chin_2016,deleon_2013,sandel_2015}.
+However, the ones presented here provide lower weight estimates for a
+same length. Until about TL = 200 mm, there are no appreciable
+differences between the parameters for organisms from the Mexican
+Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica
+\citep{chin_2016}. Yet, for larger organisms (TL \textgreater{} 270 mm)
+parameters from Costa Rica \citep{sandel_2015} and Bonaire
+\citep{deleon_2013} provide similar estimates to those from this study.
+Conversely, these same studies tend to estimate higher weights ---as
+compared to the ones reported here--- for smaller organisms, likely due
+to the lack of small organisms in the samples used to estimate their
+parameters. When ever possible, future works should consider the use of
+hand nets to obtain the samples not only for studies on
+weight-at-length, but also diet, behavior and life history, where length
+can be an important factor.
 
@@
 estimates with parameters from the Gulf of Mexico and North-Western
-Atlantic (Barbour et al., 2011; Fogg et al., 2013; Aguilar-Perera \&
-Quijano-Puerto, 2016; Sabido-Itza et al., 2016) tend to be higher than
-those from the Caribbean (de Leon et al., 2013; Edwards, Frazer \&
-Jacoby, 2014; Sandel et al., 2015; Chin, Aiken \& Buddo, 2016), except
-for the ones from Xcalak National Park, Mexico (Sabido-Itza et al.,
-2016). This indicates that there are differences between lionfish across
-the invasion range. Similar regional variation exist for age-at-length
-relationships of lionfish (Fogg et al., 2015). These differences can
-have major implications in management, especially when estimating
-biomass available for harvest or predicting effects on local ecosystems,
-or evaluating the effectiveness of removal programs. Using site-specific
+Atlantic
+\citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016} tend
+to be higher than those from the Caribbean
+\citep{edwards_2014,chin_2016,deleon_2013,sandel_2015}, except for the
+ones from Xcalak National Park, Mexico \citep{sabidoitza_2016}. This
+indicates that there are differences between lionfish across the
+invasion range. Similar regional variation exist for age-at-length
+relationships of lionfish \citep{fogg_2015}. These differences can have
+major implications in management, especially when estimating biomass
+available for harvest or predicting effects on local ecosystems, or
+evaluating the effectiveness of removal programs. Using site-specific
 values provides a more accurate estimate of fish biomass. Future
@@
 must perform research that can describe biologically important
-information of lionfish throughout its invasion range (Johnson \&
-Swenarton, 2016).
+information of lionfish throughout its invasion range
+\citep{johnson_2016}.
 
@@
   an explicit example with the parameters substituted into it, as done
-  by some of the papers reviewed (de Leon et al., 2013; Sandel et al.,
-  2015; Chin, Aiken \& Buddo, 2016; Sabido-Itza et al., 2016). If
+  by some of the papers reviewed
+  \citep{chin_2016,sandel_2015,deleon_2013,sabidoitza_2016}. If
   possible, present the relationship in their exponential (eq. 1) and
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\hypertarget{ref-aguilarperera_2016}{}
-Aguilar-Perera, A. \& Quijano-Puerto, L. 2016. Relations between fish
-length to weight, and otolith length and weight, of the lionfish pterois
-volitans in the parque nacional arrecife alacranes, southern gulf of
-mexico. \emph{Rev. biol. mar. oceanogr.} 51(2):469--474. DOI:
-\href{https://doi.org/10.4067/S0718-19572016000200025}{10.4067/S0718-19572016000200025}.
-
-\hypertarget{ref-aguilarperera_2010}{}
-Aguilar-Perera, A. \& Tuz-Sulub, A. 2010. Non-native, invasive red
-lionfish (pterois volitans {[}linnaeus, 1758{]}: Scorpaenidae), is first
-recorded in the southern gulf of mexico, off the northern yucatan
-peninsula, mexico. \emph{AI}. 5(Supplement 1):S9--S12. DOI:
-\href{https://doi.org/10.3391/ai.2010.5.S1.003}{10.3391/ai.2010.5.S1.003}.
-
-\hypertarget{ref-albins_2008}{}
-Albins, M. \& Hixon, M. 2008. Invasive indo-pacific lionfish pterois
-volitans reduce recruitment of atlantic coral-reef fishes. \emph{Mar.
-Ecol. Prog. Ser.} 367:233--238. DOI:
-\href{https://doi.org/10.3354/meps07620}{10.3354/meps07620}.
-
-\hypertarget{ref-andradibrown_2017}{}
-Andradi-Brown, D.A., Grey, R., Hendrix, A., Hitchner, D., Hunt, C.L.,
-Gress, E., Madej, K., Parry, R.L., et al. 2017. Depth-dependent effects
-of culling-do mesophotic lionfish populations undermine current
-management? \emph{R Soc Open Sci}. 4(5):170027. DOI:
-\href{https://doi.org/10.1098/rsos.170027}{10.1098/rsos.170027}.
-
-\hypertarget{ref-ariasgonzalez_1998}{}
-Arias-Gonzalez, J.E. 1998. Trophic models of protected and unprotected
-coral reef ecosystems in the south of the mexican caribbean. \emph{J
-Fish Biol}. 53(sa):236--255. DOI:
-\href{https://doi.org/10.1111/j.1095-8649.1998.tb01030.x}{10.1111/j.1095-8649.1998.tb01030.x}.
-
-\hypertarget{ref-ariasgonzalez_2011}{}
-Arias-Gonzalez, J.E., Gonzalez-Gandara, C., Luis Cabrera, J. \&
-Christensen, V. 2011. Predicted impact of the invasive lionfish pterois
-volitans on the food web of a caribbean coral reef. \emph{Environ Res}.
-111(7):917--925. DOI:
-\href{https://doi.org/10.1016/j.envres.2011.07.008}{10.1016/j.envres.2011.07.008}.
-
-\hypertarget{ref-barbour_2010}{}
-Barbour, A., Montgomery, M., Adamson, A., D?az-Ferguson, E. \& Silliman,
-B. 2010. Mangrove use by the invasive lionfish pterois volitans.
-\emph{Mar. Ecol. Prog. Ser.} 401:291--294. DOI:
-\href{https://doi.org/10.3354/meps08373}{10.3354/meps08373}.
-
-\hypertarget{ref-barbour_2011}{}
-Barbour, A.B., Allen, M.S., Frazer, T.K. \& Sherman, K.D. 2011.
-Evaluating the potential efficacy of invasive lionfish (pterois
-volitans) removals. \emph{PLoS ONE}. 6(5):e19666. DOI:
-\href{https://doi.org/10.1371/journal.pone.0019666}{10.1371/journal.pone.0019666}.
-
-\hypertarget{ref-bax_2003}{}
-Bax, N., Williamson, A., Aguero, M., Gonzalez, E. \& Geeves, W. 2003.
-Marine invasive alien species: A threat to global biodiversity.
-\emph{Marine Policy}. 27(4):313--323. DOI:
-\href{https://doi.org/10.1016/S0308-597X(03)00041-1}{10.1016/S0308-597X(03)00041-1}.
-
-\hypertarget{ref-betancurr_2011}{}
-Betancur-R, R., Hines, A., Acero, A., Orti, G., Wilbur, A. \&
-Freshwater, D. 2011. Reconstructing the lionfish invasion: Insights into
-greater caribbean biogeography. \emph{J Biogeography}. 38:1281--1293.
-DOI:
-\href{https://doi.org/10.1111/j.1365-2699.2011.02496.x}{10.1111/j.1365-2699.2011.02496.x}.
-
-\hypertarget{ref-rgdal_2017}{}
-Bivand, R., Keitt, T. \& Rowlingson, B. 2017. \emph{Rgdal: Bindings for
-the geospatial data abstraction library}. ed. (nos.). Available:
-\url{https://CRAN.R-project.org/package=rgdal}.
-
-\hypertarget{ref-bozec_2008}{}
-Bozec, Y., Acosta-Gonz\a'alez, G., N\a'uñez-Lara, E. \&
-Arias-Gonz\a'alez, J. 2008. Impacts of coastal development on ecosystem
-structure and function of yucatan coral reefs, mexico. In
-\emph{Proceedings of the 11th international coral reef symposium}. ed.
-I.C.R.S. ICRF, Ed. (nos.). Ft. Lauderdale, Florida: 11th International
-Coral Reef Symposium.
-
-\hypertarget{ref-chin_2016}{}
-Chin, D.A., Aiken, K.A. \& Buddo, D. 2016. Lionfish population density
-in discovery bay, jamaica. \emph{International Journal of Scientific \&
-Engineering Research}. 7(12):1327--1331.
-
-\hypertarget{ref-cote_2013}{}
-Cote, I., Green, S., Morris, J., Akins, J. \& Steinke, D. 2013. Diet
-richness of invasive indo-pacific lionfish revealed by dna barcoding.
-\emph{Mar. Ecol. Prog. Ser.} 472:249--256. DOI:
-\href{https://doi.org/10.3354/meps09992}{10.3354/meps09992}.
-
-\hypertarget{ref-dahl_2014}{}
-Dahl, K.A. \& Patterson, W.F. 2014. Habitat-specific density and diet of
-rapidly expanding invasive red lionfish, pterois volitans, populations
-in the northern gulf of mexico. \emph{PLoS ONE}. 9(8):e105852. DOI:
-\href{https://doi.org/10.1371/journal.pone.0105852}{10.1371/journal.pone.0105852}.
-
-\hypertarget{ref-davis_2003}{}
-DAVIS, M.A. 2003. Biotic globalization: Does competition from introduced
-species threaten biodiversity? \emph{Bioscience}. 53(5):481. DOI:
-\href{https://doi.org/10.1641/0006-3568(2003)053\%5B0481:BGDCFI\%5D2.0.CO;2}{10.1641/0006-3568(2003)053{[}0481:BGDCFI{]}2.0.CO;2}.
-
-\hypertarget{ref-deleon_2013}{}
-de Leon, R., Vane, K., Bertuol, P., Chamberland, V.C., Simal, F., Imms,
-E. \& Vermeij, M.J.A. 2013. Effectiveness of lionfish removal efforts in
-the southern caribbean. \emph{Endanger Species Res}. 22(2):175--182.
-DOI: \href{https://doi.org/10.3354/esr00542}{10.3354/esr00542}.
-
-\hypertarget{ref-edwards_2014}{}
-Edwards, M.A., Frazer, T.K. \& Jacoby, C.A. 2014. Age and growth of
-invasive lionfish (pterois spp.) in the caribbean sea, with implications
-for management. \emph{BMS}. 90(4):953--966. DOI:
-\href{https://doi.org/10.5343/bms.2014.1022}{10.5343/bms.2014.1022}.
-
-\hypertarget{ref-fogg_2015}{}
-Fogg, A.Q., Evans, J.T., Ingram JR, G.W., Peterson, M.S. \&
-Brown-Peterson, N.J. 2015. Comparing age and growth patterns of invasive
-lionfish among three ecoregions of the northern gulf of mexico. In
-\emph{Proceedings of the 68 th gulf and caribbean fisheries institute}.
-ed. G. GCFI \& C.F. Institute, Eds. (nos.). Panama City: Gulf; Caribbean
-Fisheries Institute.
-
-\hypertarget{ref-fogg_2013}{}
-Fogg, A.Q., Hoffmayer, E.R., Driggers, W.B., Campbell, M.D., Pellegrin,
-G.J. \& Stein, W. 2013. Distribution and length frequency of invasive
-lionfish (pterois sp.) in the northern gulf of mexico. \emph{GCR}. 25.
-DOI: \href{https://doi.org/10.18785/gcr.2501.08}{10.18785/gcr.2501.08}.
-
-\hypertarget{ref-froese_website_2016}{}
-Froese, R. \& Pauly, D. 2016. Available: \url{http://www.fishbase.org/}
-{[}2016, December 15{]}.
-
-\hypertarget{ref-green_2012}{}
-Green, S.J., Akins, J.L., Maljkovi\a'c, A. \& Côt\a'e, I.M. 2012.
-Invasive lionfish drive atlantic coral reef fish declines. \emph{PLoS
-ONE}. 7(3):e32596. DOI:
-\href{https://doi.org/10.1371/journal.pone.0032596}{10.1371/journal.pone.0032596}.
-
-\hypertarget{ref-grieve_2016}{}
-Grieve, B., Curchitser, E. \& Rykaczewski, R. 2016. Range expansion of
-the invasive lionfish in the northwest atlantic with climate change.
-\emph{Mar. Ecol. Prog. Ser.} 546:225--237. DOI:
-\href{https://doi.org/10.3354/meps11638}{10.3354/meps11638}.
-
-\hypertarget{ref-hackerott_2017}{}
-Hackerott, S., Valdivia, A., Cox, C.E., Silbiger, N.J. \& Bruno, J.F.
-2017. Invasive lionfish had no measurable effect on prey fish community
-structure across the belizean barrier reef. \emph{PeerJ}. 5:e3270. DOI:
-\href{https://doi.org/10.7717/peerj.3270}{10.7717/peerj.3270}.
-
-\hypertarget{ref-hixon_2016}{}
-Hixon, M., Green, S., Albins, M., Akins, J. \& Morris, J. 2016.
-Lionfish: A major marine invasion. \emph{Mar. Ecol. Prog. Ser.}
-558:161--165. DOI:
-\href{https://doi.org/10.3354/meps11909}{10.3354/meps11909}.
-
-\hypertarget{ref-johnson_2016}{}
-Johnson, E.G. \& Swenarton, M.K. 2016. Age, growth and population
-structure of invasive lionfish (pterois volitans/miles) in northeast
-florida using a length-based, age-structured population model.
-\emph{PeerJ}. 4:e2730. DOI:
-\href{https://doi.org/10.7717/peerj.2730}{10.7717/peerj.2730}.
-
-\hypertarget{ref-johnston_2015}{}
-Johnston, M. \& Purkis, S. 2015. A coordinated and sustained
-international strategy is required to turn the tide on the atlantic
-lionfish invasion. \emph{Mar. Ecol. Prog. Ser.} 533:219--235. DOI:
-\href{https://doi.org/10.3354/meps11399}{10.3354/meps11399}.
-
-\hypertarget{ref-jud_2011}{}
-Jud, Z., Layman, C., Lee, J. \& Arrington, D. 2011. Recent invasion of a
-florida (usa) estuarine system by lionfish pterois volitans / p. miles~.
-\emph{Aquat. Biol.} 13(1):21--26. DOI:
-\href{https://doi.org/10.3354/ab00351}{10.3354/ab00351}.
-
-\hypertarget{ref-RefManager_2014}{}
-McLean, M.W. 2014. \emph{Straightforward bibliography management in r
-using the refmanager package}. ed. (nos.). Available:
-\url{http://arxiv.org/abs/1403.2036}.
-
-\hypertarget{ref-molnar_2008}{}
-Molnar, J.L., Gamboa, R.L., Revenga, C. \& Spalding, M.D. 2008.
-Assessing the global threat of invasive species to marine biodiversity.
-\emph{Frontiers in Ecology and the Environment}. 6(9):485--492. DOI:
-\href{https://doi.org/10.1890/070064}{10.1890/070064}.
-
-\hypertarget{ref-morris_2009}{}
-Morris, J.A. \& Akins, J.L. 2009. Feeding ecology of invasive lionfish
-(pterois volitans) in the bahamian archipelago. \emph{Environ. Biol.
-Fishes}. 86(3):389--398. DOI:
-\href{https://doi.org/10.1007/s10641-009-9538-8}{10.1007/s10641-009-9538-8}.
-
-\hypertarget{ref-morris_2011}{}
-Morris, J.A., Shertzer, K.W. \& Rice, J.A. 2011. A stage-based matrix
-population model of invasive lionfish with implications for control.
-\emph{Biol Invasions}. 13(1):7--12. DOI:
-\href{https://doi.org/10.1007/s10530-010-9786-8}{10.1007/s10530-010-9786-8}.
-
-\hypertarget{ref-muoz_2011}{}
-Muñoz, R., Currin, C. \& Whitfield, P. 2011. Diet of invasive lionfish
-on hard bottom reefs of the southeast usa: Insights from stomach
-contents and stable isotopes. \emph{Mar. Ecol. Prog. Ser.} 432:181--193.
-DOI: \href{https://doi.org/10.3354/meps09154}{10.3354/meps09154}.
-
-\hypertarget{ref-murray_2007}{}
-Murray, G. 2007. Constructing paradise: The impacts of big tourism in
-the mexican coastal zone. \emph{Coastal Management}. 35(2-3):339--355.
-DOI:
-\href{https://doi.org/10.1080/08920750601169600}{10.1080/08920750601169600}.
-
-\hypertarget{ref-sp_2017}{}
-Pebesma, E.J. \& Bivand, R.S. 2005. Classes and methods for spatial data
-in R. \emph{R News}. 5(2):9--13. Available:
-\url{https://CRAN.R-project.org/doc/Rnews/}.
-
-\hypertarget{ref-pimentel_2005}{}
-Pimentel, D., Zuniga, R. \& Morrison, D. 2005. Update on the
-environmental and economic costs associated with alien-invasive species
-in the united states. \emph{Ecological Economics}. 52(3):273--288. DOI:
-\href{https://doi.org/10.1016/j.ecolecon.2004.10.002}{10.1016/j.ecolecon.2004.10.002}.
-
-\hypertarget{ref-rcore_2017}{}
-R Core Team. 2017. \emph{R: A language and environment for statistical
-computing}. ed. (nos.). Vienna, Austria: R Foundation for Statistical
-Computing. Available: \url{https://www.R-project.org/}.
-
-\hypertarget{ref-broom_2017}{}
-Robinson, D. 2017. \emph{Broom: Convert statistical analysis objects
-into tidy data frames}. ed. (nos.). Available:
-\url{https://CRAN.R-project.org/package=broom}.
-
-\hypertarget{ref-rocha_2015}{}
-Rocha, L.A., Rocha, C.R., Baldwin, C.C., Weigt, L.A. \& McField, M.
-2015. Invasive lionfish preying on critically endangered reef fish.
-\emph{Coral Reefs}. 34(3):803--806. DOI:
-\href{https://doi.org/10.1007/s00338-015-1293-z}{10.1007/s00338-015-1293-z}.
-
-\hypertarget{ref-ruizzarate_2004}{}
-Ruiz-Zarate, M. \& Arias-Gonzalez, J. 2004. Spatial study of juvenile
-corals in the northern region of the mesoamerican barrier reef system
-(mbrs). \emph{Coral Reefs}. (September, 9). DOI:
-\href{https://doi.org/10.1007/s00338-004-0420-z}{10.1007/s00338-004-0420-z}.
-
-\hypertarget{ref-sabidoitza_2016}{}
-Sabido-Itza, M., Medina-Quej, A., De Jesus-Navarrete, A., Gomez-Poot, J.
-\& Garcia-Rivas, M. 2016. Uso de la estructura de tallas como evidencia
-del establecimiento poblacional del pez le?n pterois volitans
-(scorpaeniformes: Scorpaenidae) en el sur del caribe mexicano.
-\emph{RBT}. 64(1):353. DOI:
-\href{https://doi.org/10.15517/rbt.v64i1.18943}{10.15517/rbt.v64i1.18943}.
-
-\hypertarget{ref-sandel_2015}{}
-Sandel, V., Mart\a'inez-Fern\a'andez, D., Wangpraseurt, D. \& Sierra, L.
-2015. Ecology and management of the invasive lionfish pterois
-volitans/miles complex (perciformes: Scorpaenidae) in southern costa
-rica. \emph{Rev Biol Trop}. 63(1):213--221. Available:
-\url{http://www.ncbi.nlm.nih.gov/pubmed/26299126} {[}2017, June 27{]}.
-
-\hypertarget{ref-schofield_2009}{}
-Schofield, P. 2009. Geographic extent and chronology of the invasion of
-non-native lionfish (pterois volitans {[}linnaeus 1758{]} and p. miles
-{[}bennett 1828{]}) in the western north atlantic and caribbean sea.
-\emph{AI}. 4(3):473--479. DOI:
-\href{https://doi.org/10.3391/ai.2009.4.3.5}{10.3391/ai.2009.4.3.5}.
-
-\hypertarget{ref-schofield_2010}{}
-Schofield, P. 2010. Update on geographic spread of invasive lionfishes
-(pterois volitans {[}linnaeus, 1758{]} and p. miles {[}bennett, 1828{]})
-in the western north atlantic ocean, caribbean sea and gulf of mexico.
-\emph{AI}. 5(Supplement 1):S117--S122. DOI:
-\href{https://doi.org/10.3391/ai.2010.5.S1.024}{10.3391/ai.2010.5.S1.024}.
-
-\hypertarget{ref-tmap_2017}{}
-Tennekes, M. 2017a. \emph{Tmap: Thematic maps}. ed. (nos.). Available:
-\url{https://CRAN.R-project.org/package=tmap}.
-
-\hypertarget{ref-tmaptools_2017}{}
-Tennekes, M. 2017b. \emph{Tmaptools: Thematic map tools}. ed. (nos.).
-Available: \url{https://CRAN.R-project.org/package=tmaptools}.
-
-\hypertarget{ref-usseglio_2017}{}
-Usseglio, P., Selwyn, J.D., Downey-Wall, A.M. \& Hogan, J.D. 2017.
-Effectiveness of removals of the invasive lionfish: How many dives are
-needed to deplete a reef? \emph{PeerJ}. 5:e3043. DOI:
-\href{https://doi.org/10.7717/peerj.3043}{10.7717/peerj.3043}.
-
-\hypertarget{ref-valdezmoreno_2012}{}
-Valdez-Moreno, M., Quintal-Lizama, C., G\a'omez-Lozano, R. \&
-Garc\a'ia-Rivas, M.D.C. 2012. Monitoring an alien invasion: DNA
-barcoding and the identification of lionfish and their prey on coral
-reefs of the mexican caribbean. \emph{PLoS ONE}. 7(6):e36636. DOI:
-\href{https://doi.org/10.1371/journal.pone.0036636}{10.1371/journal.pone.0036636}.
-
-\hypertarget{ref-villaseorderbez_2014}{}
-Villaseñor-Derbez, J.C. \& Herrera-P\a'erez, R. 2014. Brief description
-of prey selectivity and ontogenetic changes in the diet of the invasive
-lionfish pterois volitans (actinopterygii, scorpaenidae) in the mexican
-caribbean. \emph{PANAMJAS}. 9(2):131--135.
-
-\hypertarget{ref-tidyverse_2017}{}
-Wickham, H. 2017. \emph{Tidyverse: Easily install and load 'tidyverse'
-packages}. ed. (nos.). Available:
-\url{https://CRAN.R-project.org/package=tidyverse}.
-
-\hypertarget{ref-sandwich_2014}{}
-Zeileis, A. 2004. Econometric computing with hc and hac covariance
-matrix estimators. \emph{Journal of Statistical Software}. 11(10):1--17.
-Available: \url{http://www.jstatsoft.org/v11/i10/}.
-
-\hypertarget{ref-lmtest_2002}{}
-Zeileis, A. \& Hothorn, T. 2002. Diagnostic checking in regression
-relationships. \emph{R News}. 2(3):7--10. Available:
-\url{https://CRAN.R-project.org/doc/Rnews/}.
+\bibliography{references}
 

### 2018-02-24 test.Rmd
Need to work a lot more on this, the reviewers gave good comments but it needs A LOT more work

--- 2018-02-24 Manuscript.Rmd
@@
 ---
-title: "Allometric growth parameters for invasive lionfish *Pterois volitans* (Actinopterygii, Scorpaenidae) in the Western Atlantic"
+title: "Weight-at-length of the invasive lionfish *Pterois volitans* (Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a review of allometric growth parameters across the invasion range"
 author: "Juan Carlos Villaseñor-Derbez"
@@
 
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F)
-
-# options(knitr.table.format = "latex")
-
-windowsFonts(Times=windowsFont("TT Times New Roman"))
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = F)
 ```
 
-```{r load packages}
-suppressPackageStartupMessages({
-  # library(RColorBrewer)
-  # library(colorRamps)
-  library(e1071)
-  library(stringr)
-  library(agricolae)
-  library(magrittr)
-  library(stargazer)
-  library(sandwich)
-  library(lmtest)
-  library(broom)
-  library(tmap)
-  library(tmaptools)
-  library(rgdal)
-  library(sp)
-  library(RefManageR)
-  library(tidyverse)
-})
+## R Markdown
+
+\citep{pimentel_2005}
+
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+You can embed an R code chunk like this:
+
+```{r cars}
+summary(cars)
 ```
 
-# Introduction
+## Including Plots
 
-At least 84% of the marine eco-regions have reported the presence of an invasive species \citep{molnar_2008}.
-These represent a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries \citep{bax_2003}.
-Invasive species may also threaten native species through competition \citep{davis_2003} or predation.
-By 2005, the economic cost of invasive species to the United States was  estimated at \$120 billion per year and nearly 42% of species that have been included in the Endangered or Threatened species list have been labeled as such due to presence of invasive species \citep{pimentel_2005}.
-This highlights the importance of understanding, managing, and preventing ecological invasions.
+You can also embed plots, for example:
 
-Lionfish (*Pterois volitans/miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
-They are the first marine vertebrates to establish in North Atlantic \citep{schofield_2009,schofield_2010} and Caribbean coasts \citep{sabidoitza_2016}.
-Lionfish have been widely reported in coral reefs \citep{aguilarperera_2010}, but also in other habitats such as estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with hard-bottoms \citep{muoz_2011}, and mesophotic reefs \citep{andradibrown_2017}.
-Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion  \citep{hixon_2016}.
-
-A significant amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
-Their feeding behavior and high consumption rates can reduce recruitment \citep{albins_2008} and population sizes \citep{green_2012} of native reef-fish species, and further the endangerment of critically endangered reef fish \citep{rocha_2015}.
-(However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or composition of prey fishes).
-Major efforts have also been made to understand the possible impacts of the invasion by keeping track of its range through time \citep{schofield_2009,schofield_2010} and predicting invasion ranges under climate change scenarios \citep{grieve_2016}.
-By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish \citep{ariasgonzalez_2011}, which can then be translated into ecosystem-level and economic impacts.
-
-Seeking to reduce lionfish densities, governments and non-profit organizations have promoted removal programs and incentivized its consumption \citep{chin_2016}.
-In some cases, these have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
-The rapid recovery rates exhibited by lionfish \citep{barbour_2011} and the persistent populations in mesophotic coral ecosystems \citep{andradibrown_2017} -which can contribute with recruitment to shallow-water populations- make of complete eradication through fishing effort an unlikely solution.
-However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery \citep{chin_2016}, which can reduce local abundances and control -not eradicate- the invasion while providing alternative livelihoods.
-
-The feasibility of lionfish removal programs has been extensively evaluated through field observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}.
-The latter measure changes in biomass or density \citep{barbour_2011,johnston_2015} in response to increased mortality (*i.e.* lionfish removal).
-In this case, biomass represents the sum of all fish's individual weight.
-Total Weight (TW) can be estimated from Total Length (TL) observations using the allometric growth equation ($TW = aTL^b$).
-Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean.
-The weight-at-length of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Thus, when using biomass-informed models or estimating biomass from length observations, it is important to use site-specific parameters to obtain an accurate estimate.
-This is especially important when research involves identifying the total biomass available for harvest by fishers \citep{chin_2016} or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015}.
-
-Here, I provide the first allometric growth parameters for the invasive lionfish in the central Mexican Caribbean region.
-At the same time, I highlight the importance of using site-specific parameters by estimating biomass with parameters from other regions across the invasion range and comparing them to observed biomass.
-I also provide other 13 standardized parameters from eight studies through the invasion range, making them readily accessible for future research.
-Finally, I discuss the way in which allometric parameters are reported, and call for standardization to facilitate their use.
-
-\clearpage
-
-# Materials and Methods
-
-```{r load fish data, include = F}
-fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
-  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
-  summarize(Length = 10*mean(TotalLength_cm),
-            Weight = mean(TotalWeigth_gr),
-            Stomach = mean(StomachLength_cm)) %>% 
-  ungroup()
+```{r pressure, echo=FALSE, fig.cap = "My Caption"}
+plot(pressure)
 ```
 
-*Area of study*
-
-The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean Figure \ref{fig:map}.
-The region represents the northernmost section of the Mesoamerican Barrier Reef System \citep{ruizzarate_2004}.
-Coral reefs and mangroves are locally important habitats that represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism, the main source of income to the local economy \citep{murray_2007}.
-
-The reef profile has been described by \citet{ariasgonzalez_1998}, indicating that the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
-The reef becomes deeper, leading to the reef front often found at 700 m from the coastline and extends for an additional 300 m.
-At approximately 1000 m away from shore and 30 - 40 m depth, the reef leads to a drop-off.
-Along a perpendicular profile to the coast, bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18 m deep.
-Along the coast, these reefs have been reported to be under significant anthropogenic pressure, likely causing a shift in structure and function \citep{bozec_2008}.
-
-```{r fig.cap = "\\label{fig:map}Map of the study area.
-The black inset on the left (Yucatan Peninsula) indicates the location where study sites are distributed.
-On the right, circular markers indicate sampling sites and the black romboid indicates location of Puerto Aventuras, Mexico."}
-# Load shapefiles
-proj <- CRS("+proj=longlat +datum=NAD27")
-
-load("./Spatial/coastline_mx.Rda")
-
-#Small shapefile for region of interest
-xy1 <- data.frame(X = mean(-87.30662, -87.19194), Y = mean(20.39283, 20.51278))
-coordinates(xy1) <- c("X", "Y")
-proj4string(xy1) <- proj
-res1 <- spTransform(xy1, proj)
-
-#Create shapefile for sampling locations
-sample_points <- fish %>%
-  group_by(Location) %>%
-  summarize(latitude = mean(Latitude, na.rm = T),
-            longitude = mean(Longitude, na.rm = T)) %>%
-  ungroup()
-
-xy <- data.frame(X = -1*abs(sample_points$longitude), Y = sample_points$latitude)
-coordinates(xy) <- c("X", "Y")
-proj4string(xy) <- proj  ## for example
-res <- spTransform(xy, proj)
-b <- SpatialPointsDataFrame(coords = res, data = sample_points, proj4string = proj)
-
-# Create shapefile for relevant communities
-Communities <- data.frame(Longitude = c(-87.24),
-                           Latitude = c(20.5),
-                           Location = c("Pto. Aventuras"),
-                           stringsAsFactors = F)
-
-xy2 <- data.frame(X = -1*abs(Communities$Longitude), Y = Communities$Latitude)
-coordinates(xy2) <- c("X", "Y")
-proj4string(xy2) <- proj  ## for example
-res2 <- spTransform(xy2, proj)
-c <- SpatialPointsDataFrame(coords = res2, data = Communities, proj4string = proj)
-
-pen_map <- tm_shape(baja2, bbox = bb(xlim = c(-89.29656, -86.71074), ylim = c(17.89399, 21.60525))) +
-  tm_polygons() +
-  tm_shape(res1) +
-  tm_symbols(shape = 5, size = 2, border.col = "black", col = "black", border.lwd = 2) +
-  tm_scale_bar()
-
-study_area <- tm_shape(baja2, bbox = bb(xlim = c(-87.30662, -87.19194), ylim = c(20.39283, 20.51278))) +
-  tm_polygons() +
-  tm_shape(b) +
-  tm_symbols(size = 0.125, border.col = "black", col = "black") +
-  tm_shape(c) +
-  tm_symbols(shape = 18, col = "black", border.col = "black", size = 0.5) +
-  tm_compass() +
-  tm_scale_bar()
-
-tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
-
-```
-
-*Fish sampling*
-
-A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along the coast in 2010 (Fig.
-1, Table I).
-Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
-All observed organisms (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes, often ignored due to gear selectivity when spearing.
-Organisms were euthanized and frozen within 30 minutes of completing the dive and stored for posterior analysis.
-Total Length (TL; mm) and Total Weight (TW; gr) were recorded for all organisms.
-
-```{r table of locations, results = "asis"}
-total <- data.frame(Location = "Total", Latitude = "", Longitude = "", minD = min(fish$Depth_m), maxD = max(fish$Depth_m), meanD = formatC(mean(fish$Depth_m), digits = 1, format = "f"), n = 109, stringsAsFactors = F)
-
-fish %>% 
-  group_by(Location) %>% 
-  summarize(Latitude = formatC(mean(Latitude), digits = 3, format = "f"),
-            Longitude = formatC(mean(Longitude), digits = 3, format = "f"),
-            minD = formatC(min(Depth_m), digits = 1, format = "f"),
-            maxD = formatC(max(Depth_m), digits = 1, format = "f"),
-            meanD = formatC(mean(Depth_m), digits = 1, format = "f"),
-            n = n()) %>% 
-  rbind(total) %>% 
-  knitr::kable(row.names = F,
-               col.names = c("Location", "Lat.", "Long.", "Min. Depth", "Max. Depth", "Mean Depth", "n"),
-               booktabs = T, caption = c("Coordinates, minimum, maximum and mean depth (m), and number of samples for each location."))
-```
-
-*Data analysis*
-
-The weight at length relationship between the observed variables is described by the allometric growth function:
-
-\begin{equation}
-\label{eq:allometric}
-TW = aTL^b
-\end{equation}
-
-Where $TW$ is the Total Weight (gr), $TL$ is the Total Length (mm), $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
-When $b = 3$, it is said that the organism exhibits a perfect isometric growth.
-The dependent and independent variables were transformed via base-10 logarithms, thus the equation becomes:
-
-\begin{equation}
-\label{eq:log-alo}
-log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)
-\end{equation}
-
-This can be simplified and re-written as:
-
-\begin{equation}
-\label{eq:log-alo-trans}
-Y = mX + c
-\end{equation}
-
-Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$.
-Since $b = m$, we will only use $b$ throughout the paper for simplicity.
-The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction was performed.
-Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$).
-Additionally, the allometric parameter was tested against the null hypothesis of isometric growth ($H_0: b = 3$).
-Coefficients were tested with a two-tailed Student's t-test.
-The significance of the regression was corroborated with an F-test.
-
-Other length-weight relationships (n = 13) were extracted from peer-reviewed literature.
-Parameters were obtained for North Carolina [n = 1,barbour_2011], Northern [n = 3,fogg_2013] and Southern Gulf of Mexico [n = 3,aguilarperera_2016], the Southern Mexican Caribbean [n = 1,sabidoitza_2016], Little Cayman [n = 1,edwards_2014], Jamaica [n = 1,chin_2016], Bonaire [n = 1,deleon_2013] and Costa Rica [n = 1,sandel_2015] and Fishbase [n = 1,froese_website_2016] were also included.
-When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retrieved.
-Whenever gender was not specified, it was assumed that the results were presented for pooled genders.
-
-During the review process, some papers indistinctly used $a$ to report either the ponderal index in eq.
-1 or the y-intercept ($c$) in eq.
-3, which might sometimes be overlooked.
-Furthermore, some studies reported their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicated that they were estimated as cm-to-gr conversions.
-Here, all parameters are reported as TL(mm) to TW(gr) conversions.
-When required, values from other studies were transformed for consistency.
-
-Since uncertainty arround estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships.
-Instead, the 13 length-weight relationships were usd to calculate expected weight for the organisms sampled in the Central Mexican Caribbean (n = 109).
-Expected weights were divided by the observed weights to obtain a ratio.
-Difference in mean weight ratios across studies were tested with a one-way Analysis of Variance (ANOVA).
-
-All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 \citep{rcore_2017}.
-Data wrangling was done with the tidyverse package \citep{tidyverse_2017}.
-Maps were created with a mix of functions from the sp \citep{sp_2017}, rgdal \citep{rgdal_2017}, tmap \citep{tmap_2017}, and tmaptools \citep{tmaptools_2017} packages.
-Heteroskedastic-robust standard errors were calculated with the sandwich \citep{sandwich_2014} and lmtest \citep{lmtest_2002} packages.
-Models were manipulated with the broom package \citep{broom_2017}.
-Raw data and code used in this work is available at github.com/jcvdav/lionfish_biometry.
-
-# Results
-
-Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7 gr.
-The smallest organism (TL = `r formatC(min(fish$Length), digits = 2, format = "f")` mm) was also the lightest organism (TW = `r formatC(min(fish$Weight), digits = 2, format = "f")` gr).
-However, the largest organism (TL = `r formatC(max(fish$Length), digits = 2, format = "f")` mm) was not the heaviest (TW = `r formatC(fish$Weight[fish$Length == max(fish$Length)], digits = 2, format = "f")` gr), and the heaviest organism (TW = `r formatC(max(fish$Weight), digits = 2, format = "f")` gr) was `r formatC(fish$Length[fish$Weight == max(fish$Weight)], digits = 2, format = "f")` mm in total length.
-Kernell density plots (Fig.
-2) show the distribution for TL and TW for all sampled organisms.
-Both measures were positively skewed, with skewness of `r formatC(skewness(fish$Length), digits = 2, format = "f")` for TL and `r formatC(skewness(fish$Weight), digits = 2, format = "f")` for TW.
-
-```{r histogram figures, fig.width = 5, fig.height = 6, fig.cap = "Kernell density plots for a) Total length (mm) and b) Total weight (gr) for 109 lionfish sampled in the central Mexican Caribbean."}
-length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
-  geom_density(fill = "gray", alpha = 0.5) +
-  theme_bw() +
-  ggExtra::removeGrid() +
-  labs(x = "Total Length (mm)", y = "Density") +
-  geom_text(label = "A", x = 310, y = 0.007) +
-  theme(text = element_text(family = "Times"))
-
-weight_hist <- ggplot(data = fish, mapping = aes(x = Weight)) +
-  geom_density(fill = "gray", alpha = 0.5) +
-  theme_bw() +
-  ggExtra::removeGrid() +
-  labs(x = "Total weight (gr)", y = "Density") +
-  geom_text(label = "B", x = 400, y = 0.017) +
-  theme(text = element_text(family = "Times"))
-
-gridExtra::grid.arrange(length_hist, weight_hist)
-```
-
-```{r model fitting}
-model <- lm(log10(Weight) ~ log10(Length), data = fish)
-
-TidyModel <- model%>%
-  lmtest::coeftest(vcov = sandwich::vcovHC(., type = "HC1")) %>%
-  broom::tidy()
-
-robust_se <- TidyModel$std.error %>%
-  set_names(TidyModel$term)
-
-wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))
-
-f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))
-
-```
-
-```{r testing coefficients}
-test_intercept <- 2*pt(abs(coef(model)[[1]]/robust_se[[1]]), df = 107, lower.tail = F)
-
-test_slope <- 2*pt(abs(coef(model)[[2]]/robust_se[[2]]), df = 107, lower.tail = F)
-
-test_slope_3 <- 2*pt(abs((coef(model)[[2]]-3)/robust_se[[2]]), df = 107, lower.tail = F)
-```
-
-*Length-weight relationship*
-
-The model adjusted to eq.
-3 estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
-Thus, TW (gr) can be calculated from TL (mm) as a linear equation: $log_{10}(TW) = `r coef(model)[[2]]`\times log_{10}(TL) `r coef(model)[[1]]`$, or its exponential form: $TW = `r 10^coef(model)[[1]]`\times TL^{`r coef(model)[[2]]`}$.
-The intercept ($c$) and slope $(b)$ were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
-Additionally, the allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$), indicating that lionfish present allometric growth.
-More information on model fit and confidence intervals for the estimated coefficients is presented in Table II.
-The relationship between Total Length and Total Weight is presented in Figure 3.
-
-```{r scatter plot, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit."}
-
-a <- coefficients(model)[[1]]
-b <- coefficients(model)[[2]]
-
-predicted_this_study <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
-  mutate(Weight = 10^a*Length^b)
-
-plot_fit_this_study <-  ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
-  geom_line(data = predicted_this_study, mapping = aes(x = Length, y = Weight), size = 1) +
-  geom_point(size = 2, alpha = 0.25, color = "black") +
-  theme_bw() +
-  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
-  theme(text = element_text(family = "Times")) +
-  scale_color_brewer(palette = "Set3") +
-  theme(text=element_text(family="Times"))
-
-plot_fit_this_study
-```
-
-```{r, results = "asis"}
-
-ci_c <- c("95\\% CI for c", paste0("(", formatC(a-(1.96*robust_se[[1]]), digits = 3, format = "f"),"-", formatC(a+(1.96*robust_se[[1]]), digits = 3, format = "f"),")"))
-
-ci_b <- c("85\\% CI for b", paste0("(", formatC(b-(1.96*robust_se[[2]]), digits = 3, format = "f"),"-", formatC(b+(1.96*robust_se[[2]]), digits = 3, format = "f"),")"))
-
-regression_table <- stargazer(model,
-          header = F,
-          se = list(robust_se),
-          type = "latex",
-          t.auto = T,
-          p.auto = T,
-          intercept.bottom = F,
-          single.row = T,
-          report = "vcs*",
-          omit.stat = c("rsq", "f"),
-          add.lines = list(ci_c, ci_b, f_string),
-          covariate.labels = c("c", "b"),
-          dep.var.labels = "log10(TW)", title = "Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
-Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.")
-```
-
-```{r, results = "asis"}
-review <- read_csv("biometric_review.csv", col_types = cols(), na = "-")
-
-my.df <- data.frame(Study = unique(review$Study), Reference_no = seq(1 : length(unique(review$Study))), stringsAsFactors = F)
-
-review_table <- review %>% 
-  left_join(my.df, by = "Study") %>% 
-  select(Reference = Reference_no, Region = Study_site, Sex = Gender, n = N, a, c, b, r2, minD, maxD, Spear) %>% 
-  mutate(r2 = ifelse(is.na(r2), "-", r2),
-         minD = ifelse(is.na(minD), "-", minD),
-         maxD = ifelse(is.na(maxD), "-", maxD)) %>% 
-  knitr::kable(format = "latex",
-               row.names = F,
-               digits =  c(1, 0, 6, 4, 4, 4, 0, 1, 1),
-               booktabs = T,
-               col.names = c("Reference", "Region", "Sex", "a", "c", "b", "R2", "n", "mDepth", "MDepth", "Spear"),
-               caption = c("Summary of 13 allometric growth parameters available for lionfish in the invaded range from eight peer-reviewed papers, Fishbase \\citep{froese_website_2016}, and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, a = scaling parameter for eq.
-1, c = y-intercept for eq.
-3, b = exponent or slope for eq.
-1 or eq.
-3, respectively.
-The R^2^ column indicates reported model fit.
-mDepth and MDepth indicate minimum and maximum depths (m), respectively, at which organisms were sampled.
-The Spear column indicates if the study collected organisms with pole spears.
-An asterisk indicates that some portion of organisms were sampled with pole spears.
-1 = \\citet{aguilarperera_2016}, 2 = \\citet{sandel_2015}, 3 = \\citet{chin_2016}, 4 = \\citet{barbour_2011}, 5 = \\citet{deleon_2013}, 6 = \\citet{fogg_2013}, 7 = \\citet{edwards_2014}, 8 = \\citet{sabidoitza_2016}, 9 = \\citet{froese_website_2016}, 10 = This study.")) %>%
-  kableExtra::kable_styling(latex_options = c("scale_down"))
-```
-
-*Comparison of allometric parameters*
-
-From the eight peer-reviewed studies including information on growth parameters for *P.
-volitans* and Fishbase \citep{froese_website_2016}, `r dim(review)[1]-1` parameters were identified (Table III).
-Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
-The smallest coefficient of determination was presented by \citet{chin_2016} with $R^2 = `r min(review[,13], na.rm = T)`$, while \citet{sabidoitza_2016} reported the highest value at $R^2 = `r max(review[,13], na.rm = T)`$.
-Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
-Two studies \citep{aguilarperera_2016,chin_2016} explicitly stated that their organisms were sampled with pole spears.
-Five studies \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016} mentioned that some of their organisms were obtained with pole spears (or other type of harpoon).
-A single study \citep{deleon_2013} did not specify how organisms were sampled.
-
-Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
-In the case of the ponderal index ($a$) and its $log_{10}$ transformed parameter ($c$), values were higher for parameters for pooled genders.
-Figure 4 shows the predicted weights for organisms within the size range of these study using the 14 parameters previously described.
-
-```{r review plots, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationships (n = 14) for eight studies, this study, and Fishbase.
-Colors indicate studies from which the parameters were extracted.
-Solid lines indicate that the fit was performed for males and females pooled together.
-Dotted lines indicate that the regression was performed on females, and dashed lines indicate it was performed for males."}
-
-predicted_all <- data.frame(Length = seq(1, 300, by = 1)) %>% 
-  mutate(This = review$a[14] * (Length^review$b[14]), 
-         APA = review$a[1] * (Length^review$b[1]),
-         APF = review$a[2] * (Length^review$b[2]),
-         APM = review$a[3] * (Length^review$b[3]),
-         Sandel = review$a[4] * (Length^review$b[4]),
-         Chin = review$a[5] * (Length^review$b[4]),
-         Barbour = review$a[6] * (Length^review$b[6]),
-         deLeon = review$a[7] * (Length^review$b[7]),
-         FoggA = review$a[8] * (Length^review$b[8]),
-         FoggM = review$a[9] * (Length^review$b[9]),
-         FoggF = review$a[10] * (Length^review$b[10]),
-         Edwards = review$a[11] * (Length^review$b[11]),
-         Sabido = review$a[12] * (Length^review$b[12]),
-         FishBase = review$a[13] * (Length^review$b[13])) %>%
-  gather(Study_id, Weight, -Length) %>% 
-  left_join(review, by ="Study_id")
-
-plot_fit_all_studies <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
-  geom_line(data = predicted_all, mapping = aes(x = Length, y = Weight, linetype = Gender, color = Study), size = 1) +
-  theme_bw() +
-  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
-  theme(text = element_text(family = "Times"),
-        legend.justification=c(0,1),
-        legend.position=c(0.01, 0.99),
-        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted")) +
-  guides(color = guide_legend(title=NULL)) +
-  scale_color_brewer(palette = "Paired")
-
-plot_fit_all_studies
-```
-
-```{r}
-Predicted_biomass <- fish %>% 
-  select(Length, Weight) %>% 
-  mutate(This = review$a[14] * (Length^review$b[14])/Weight, 
-         APA = review$a[1] * (Length^review$b[1])/Weight,
-         APF = review$a[2] * (Length^review$b[2])/Weight,
-         APM = review$a[3] * (Length^review$b[3])/Weight,
-         Sandel = review$a[4] * (Length^review$b[4])/Weight,
-         Chin = review$a[5] * (Length^review$b[4])/Weight,
-         Barbour = review$a[6] * (Length^review$b[6])/Weight,
-         deLeon = review$a[7] * (Length^review$b[7])/Weight,
-         FoggA = review$a[8] * (Length^review$b[8])/Weight,
-         FoggM = review$a[9] * (Length^review$b[9])/Weight,
-         FoggF = review$a[10] * (Length^review$b[10])/Weight,
-         Edwards = review$a[11] * (Length^review$b[11])/Weight,
-         Sabido = review$a[12] * (Length^review$b[12])/Weight,
-         FishBase = review$a[13] * (Length^review$b[13])/Weight) %>% 
-  gather(Study_id, Biomass_ratio, -c(Length, Weight)) %>% 
-  left_join(review, by ="Study_id")
-
-anova <- aov(Biomass_ratio ~ Study_id, Predicted_biomass)
-groups <- HSD.test(y = anova, trt = "Study_id")
-
-groups$groups%<>%
-  mutate(Study_id = rownames(.)) %>% 
-  select(-Biomass_ratio)
-
-Predicted_biomass %<>% 
-  left_join(groups$groups, by = "Study_id")
-```
-
-There were significant differences in expected-to-observed weight ratios estimated for each pair of parameters (F(13, 1512) = 39.28; p < 0.05).
-From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-On the other hand,barbour_2011 yielded the highest weight estimates, with a mean ($\pm$ SD) expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
-Predicted-to-observed weight ratios and groups identified by Tukey's HSD ($\alpha = 0.05$) are presented in Figure 5.
-
-```{r plot comparing predictions, fig.height = 4.5, fig.width = 6, fig.cap = ".
-Box and whiskers plot showing the distribution of predicted to observed biomass ratios for 14 pairs of allometric parameters.
-Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers.
-Like letters indicate values that do not differ significantly (Tukey's HSD; p < 0.05)."}
-Predicted_biomass_plot <- Predicted_biomass %>% 
-  mutate(Study = paste0(Study, " (", Gender, ")")) %>% 
-  transform(Study= reorder(Study, -Biomass_ratio)) %>%
-  ggplot(aes(x = Study, y = Biomass_ratio)) +
-  geom_boxplot(aes(fill = Gender), outlier.size = 1, notch = T) +
-  stat_summary(geom = "point", fun.y = "mean", size = 3) +
-  geom_hline(yintercept = 1, linetype = "dashed") +
-  labs(y = "Biomass (Predicted / Observed)", x = "Study") +
-  coord_flip() +
-  theme_bw() +
-  theme(text = element_text(family = "Times")) +
-  scale_fill_brewer(palette = "Greys") +
-  theme(text = element_text(family = "Times"),
-        legend.justification=c(1,1),
-        legend.position=c(0.9, 0.99),
-        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted")) +
-  geom_text(aes(y = 3.6, label = groups), family = "Times", fontface = "plain") +
-  scale_y_continuous(limits = c(NA, 3.6))
-
-Predicted_biomass_plot
-```
-
-# Discussion
-
-This study provides the first pair of allometric growth parameters specific to the Central Mexican Caribbean, complementing other studies performed in Mexican waters in the Alacranes Reef \citep{aguilarperera_2016} and Xcalak National Park \citep{sabidoitza_2016}.
-By using hand nets instead of spears, we are able to sample a wider range of sizes often ignored by pole spear samples, allowing us to include smaller organisms.
-Estimating parameters by including smaller organisms ensures better estimation of weight for smaller sizes.
-This is especially important when biomass is calculated from visual census, where small organisms can be registered.
-Thus, this study also increases certainty in weight estimation of small organisms.
-
-The length-weight coefficients estimated in this study were within the range identified by studies in other regions \citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016,edwards_2014,chin_2016,deleon_2013,sandel_2015}.
-However, the ones presented here provide lower weight estimates for a same length.
-Until about TL = 200 mm, there are no appreciable differences between the parameters for organisms from the Mexican Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica \citep{chin_2016}.
-Yet, for larger organisms (TL > 270 mm) parameters from Costa Rica \citep{sandel_2015} and Bonaire \citep{deleon_2013} provide similar estimates to those from this study.
-Conversely, these same studies tend to estimate higher weights ---as compared to the ones reported here--- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
-When ever possible, future works should consider the use of hand nets to obtain the samples not only for studies on weight-at-length, but also diet, behavior and life history, where length can be an important factor.
-
-There are evident differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
-Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic \citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016} tend to be higher than those from the Caribbean \citep{edwards_2014,chin_2016,deleon_2013,sandel_2015}, except for the ones from Xcalak National Park, Mexico \citep{sabidoitza_2016}.
-This indicates that there are differences between lionfish across the invasion range.
-Similar regional variation exist for age-at-length relationships of lionfish \citep{fogg_2015}.
-These differences can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
-Using site-specific values provides a more accurate estimate of fish biomass.
-Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results.
-At the same time, this highlights the need for more basic research that furthers our understanding of lionfish biology.
-To better manageme the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range \citep{johnson_2016}.
-
-While performing the literature review, it was often unclear if parameters were presented for eq.1 or eq.
-3.
-Sometimes, they were even mislabeled and yielded senseless results when using the suggested conversion equation.
-On other cases, parameters were said to be reported for mm-to-gr conversions, when they were actually reported as cm-to-gr conversions.
-Perhaps these minor discrepancies can be easily solved by the trained eye, but why should they exist in the first place?
-It is important that we report our information in a standard way, making it readily available for other researchers and managers.
-In this particular case, I provide my humble opinion through 5 guidelines to report allometric parameters:
-
-1.
-Be explicit in the methods section.
-What may seem obvious to you as an author ---because you have been deeply immersed throughout the process--- may not be clear to the reader.
-Specify any transformation performed on the data.
-When using log-transformations, mention the base used to transform.
-Do not assume that "data were log-transformed" means $log_{10}(X)$.
-These assumptions vary across disciplines and software and can be a source of confusion.
-For example, in biology we often assume "log-transformed" indicates the use of base 10, however in R the proper command is `log10()` and not `log()`, which uses base $e$.
-
-2.
-Use mm and gr to measure TL and TW, respectively.
-While conversion is always possible, we should aim at using standard units to report these parameters.
-If you prefer to use cm to gr conversions, that is certainly valid, but make sure to explicitly mention units when presenting the parameters.
-
-3.
-Specify the equation for which parameters are presented by including an explicit example with the parameters substituted into it, as done by some of the papers reviewed \citep{chin_2016,sandel_2015,deleon_2013,sabidoitza_2016}.
-If possible, present the relationship in their exponential (eq.
-1) and linear (eq.
-3) forms.
-
-4.
-Report standard errors and/or confidence intervals around the obtained estimates.
-Given that small changes in $a$, $c$, and $b$ can result in important changes in estimated weight, it is important that we report uncertainty around each parameter and not just general model fit and coefficient significance.
-Reporting uncertainty around parameters allows researchers and managers to include upper and lower bounds in their predictions.
-
-5.
-Make your data and code available.
-Even if this is not requited by the journal or publisher, you can use free cloud data storage services or third-party repositories to make your research accessible to others.
-Resources will always be limited and budget will rarely be enough.
-It is important that we take advantage of open science tools that promote the advancement of knowledge and foster collaboration.
-Ultimately, this promotes transparency, allows replicability of research, and advances science.
-
-This study provides a new pair of allometric growth parameters for lionfish from the central Mexican Caribbean, where they exhibit different weight-at-length.
-Furthermore, regional differences in length-weight relationships were identified, highlighting the importance of using site-specific parameters.
-
-# Aknowledgements
-
-I would like to thank thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
-I would also like to (anticipatedly) thank the editor and reviewers, who significantly improved the quality of this work.
-This research was partially funded by the "Consejo Nacional de Ciencias y Tecnología" (CONACyT) and the Latin American Fisheries Fellowship Program.
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
 

### 2018-02-24 test.tex
Need to work a lot more on this, the reviewers gave good comments but it needs A LOT more work

--- 2018-02-24 Manuscript.tex
@@
 
-\title{Allometric growth parameters for invasive lionfish \emph{Pterois
-volitans} (Actinopterygii, Scorpaenidae) in the Western Atlantic}
+\title{Weight-at-length of the invasive lionfish \emph{Pterois volitans}
+(Actinopterygii, Scorpaenidae) in the Central Mexican Caribbean, and a
+review of allometric growth parameters across the invasion range}
 
@@
 
-\section{Introduction}\label{introduction}
+\subsection{R Markdown}\label{r-markdown}
 
-At least 84\% of the marine eco-regions have reported the presence of an
-invasive species \citep{molnar_2008}. These represent a major threat to
-local biodiversity and the economic activities that depend on it, like
-tourism or fisheries \citep{bax_2003}. Invasive species may also
-threaten native species through competition \citep{davis_2003} or
-predation. By 2005, the economic cost of invasive species to the United
-States was estimated at \$120 billion per year and nearly 42\% of
-species that have been included in the Endangered or Threatened species
-list have been labeled as such due to presence of invasive species
-\citep{pimentel_2005}. This highlights the importance of understanding,
-managing, and preventing ecological invasions.
+\citep{pimentel_2005}
 
-Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
-in the North-Western Atlantic and the Caribbean, likely introduced
-through liberation of aquarium-kept organisms \citep{betancurr_2011}.
-They are the first marine vertebrates to establish in North Atlantic
-\citep{schofield_2009,schofield_2010} and Caribbean coasts
-\citep{sabidoitza_2016}. Lionfish have been widely reported in coral
-reefs \citep{aguilarperera_2010}, but also in other habitats such as
-estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with
-hard-bottoms \citep{muoz_2011}, and mesophotic reefs
-\citep{andradibrown_2017}. Due to its threat to local biodiversity, the
-speed of their spread, and its difficulty of management, their presence
-in these waters has been labeled as a major marine invasion
-\citep{hixon_2016}.
+When you click the \textbf{Knit} button a document will be generated
+that includes both content as well as the output of any embedded R code
+chunks within the document. You can embed an R code chunk like this:
 
-A significant amount of research has been done to describe lionfish
-feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas
-\citep{morris_2009,cote_2013}, Northern Gulf of Mexico
-\citep{dahl_2014}, Mexican Caribbean
-\citep{valdezmoreno_2012,villaseorderbez_2014}, Belize
-\citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}. Their
-feeding behavior and high consumption rates can reduce recruitment
-\citep{albins_2008} and population sizes \citep{green_2012} of native
-reef-fish species, and further the endangerment of critically endangered
-reef fish \citep{rocha_2015}. (However, see \citet{hackerott_2017} for a
-case where there was no evidence that lionfish affected the density,
-richness, or composition of prey fishes). Major efforts have also been
-made to understand the possible impacts of the invasion by keeping track
-of its range through time \citep{schofield_2009,schofield_2010} and
-predicting invasion ranges under climate change scenarios
-\citep{grieve_2016}. By combining information from these disciplines,
-researchers have been able to predict the trophic impacts of lionfish
-\citep{ariasgonzalez_2011}, which can then be translated into
-ecosystem-level and economic impacts.
+\begin{verbatim}
+##      speed           dist       
+##  Min.   : 4.0   Min.   :  2.00  
+##  1st Qu.:12.0   1st Qu.: 26.00  
+##  Median :15.0   Median : 36.00  
+##  Mean   :15.4   Mean   : 42.98  
+##  3rd Qu.:19.0   3rd Qu.: 56.00  
+##  Max.   :25.0   Max.   :120.00
+\end{verbatim}
 
-Seeking to reduce lionfish densities, governments and non-profit
-organizations have promoted removal programs and incentivized its
-consumption \citep{chin_2016}. In some cases, these have shown to
-significantly reduce -but not quite eliminate- lionfish abundances at
-local scales \citep{sandel_2015,chin_2016,deleon_2013}. The rapid
-recovery rates exhibited by lionfish \citep{barbour_2011} and the
-persistent populations in mesophotic coral ecosystems
-\citep{andradibrown_2017} -which can contribute with recruitment to
-shallow-water populations- make of complete eradication through fishing
-effort an unlikely solution. However, further incentivizing its
-consumption might create a demand big enough to promote and sustain a
-stable fishery \citep{chin_2016}, which can reduce local abundances and
-control -not eradicate- the invasion while providing alternative
-livelihoods.
+\subsection{Including Plots}\label{including-plots}
 
-The feasibility of lionfish removal programs has been extensively
-evaluated through field
-observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and
-empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}. The
-latter measure changes in biomass or density
-\citep{barbour_2011,johnston_2015} in response to increased mortality
-(\emph{i.e.} lionfish removal). In this case, biomass represents the sum
-of all fish's individual weight. Total Weight (TW) can be estimated from
-Total Length (TL) observations using the allometric growth equation
-(\(TW = aTL^b\)). Parameters \(a\) and \(b\) for this equation exist for
-North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013} and
-Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican
-Caribbean \citep{sabidoitza_2016}, Little Cayman \citep{edwards_2014},
-Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} and Costa Rica
-\citep{sandel_2015}, but remain unavailable for the central Mexican
-Caribbean. The weight-at-length of a species can vary across regions as
-a response to biotic (\emph{e.g.} local food availability) and abiotic
-(\emph{e.g.} water temperature) conditions \citep{johnson_2016}. Thus,
-when using biomass-informed models or estimating biomass from length
-observations, it is important to use site-specific parameters to obtain
-an accurate estimate. This is especially important when research
-involves identifying the total biomass available for harvest by fishers
-\citep{chin_2016} or the efficacy of lionfish removals
-\citep{barbour_2011,morris_2011,johnston_2015}.
-
-Here, I provide the first allometric growth parameters for the invasive
-lionfish in the central Mexican Caribbean region. At the same time, I
-highlight the importance of using site-specific parameters by estimating
-biomass with parameters from other regions across the invasion range and
-comparing them to observed biomass. I also provide other 13 standardized
-parameters from eight studies through the invasion range, making them
-readily accessible for future research. Finally, I discuss the way in
-which allometric parameters are reported, and call for standardization
-to facilitate their use.
-
-\clearpage
-
-\section{Materials and Methods}\label{materials-and-methods}
-
-\emph{Area of study}
-
-The study took place off the coasts of Playa del Carmen, in the Mexican
-Caribbean Figure \ref{fig:map}. The region represents the northernmost
-section of the Mesoamerican Barrier Reef System \citep{ruizzarate_2004}.
-Coral reefs and mangroves are locally important habitats that represent
-important sources of income in terms of extractive (\emph{e.g.}
-recreational fishing) and non-extractive (\emph{e.g.} SCUBA diving)
-activities related to tourism, the main source of income to the local
-economy \citep{murray_2007}.
-
-The reef profile has been described by \citet{ariasgonzalez_1998},
-indicating that the reef lagoon extends about 500 m from the coast,
-until the reef crest is reached. The reef becomes deeper, leading to the
-reef front often found at 700 m from the coastline and extends for an
-additional 300 m. At approximately 1000 m away from shore and 30 - 40 m
-depth, the reef leads to a drop-off. Along a perpendicular profile to
-the coast, bands of reef are interrupted by sand patches at 8 - 12 m
-deep and 16-18 m deep. Along the coast, these reefs have been reported
-to be under significant anthropogenic pressure, likely causing a shift
-in structure and function \citep{bozec_2008}.
+You can also embed plots, for example:
 
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\label{fig:map}Map of the study area.
-The black inset on the left (Yucatan Peninsula) indicates the location
-where study sites are distributed. On the right, circular markers
-indicate sampling sites and the black romboid indicates location of
-Puerto Aventuras, Mexico.}
+\includegraphics{test_files/figure-latex/pressure-1.pdf}
+\caption{\label{fig:pressure}My Caption}
 \end{figure}
 
-\emph{Fish sampling}
-
-A total of 33 SCUBA immersions were performed in 10 sampling sites along
-the coast in 2010 (Fig. 1, Table I). Sampling locations included wall
-and carpet reefs at depths between 5.7 m and 38.1 m. All observed
-organisms (n = 109) were collected using hand nets and numbered
-collection bottles. The use of hand nets prevented any weight loss due
-to bleeding and allowed a better representation of small sizes, often
-ignored due to gear selectivity when spearing. Organisms were euthanized
-and frozen within 30 minutes of completing the dive and stored for
-posterior analysis. Total Length (TL; mm) and Total Weight (TW; gr) were
-recorded for all organisms.
-
-\begin{table}
-
-\caption{(\#tab:table of locations)Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.}
-\centering
-\begin{tabular}[t]{llllllr}
-\toprule
-Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth & n\\
-\midrule
-Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\\
-Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\\
-Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\\
-Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\\
-Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\\
-\addlinespace
-Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\\
-Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\\
-Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\\
-Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\\
-Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\\
-Total &  &  & 5.7 & 38.1 & 18.6 & 109\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\emph{Data analysis}
-
-The weight at length relationship between the observed variables is
-described by the allometric growth function:
-
-\begin{equation}
-\label{eq:allometric}
-TW = aTL^b
-\end{equation}
-
-Where \(TW\) is the Total Weight (gr), \(TL\) is the Total Length (mm),
-\(a\) is the ponderal index and \(b\) is the scaling exponent or
-allometric parameter. When \(b = 3\), it is said that the organism
-exhibits a perfect isometric growth. The dependent and independent
-variables were transformed via base-10 logarithms, thus the equation
-becomes:
-
-\begin{equation}
-\label{eq:log-alo}
-log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)
-\end{equation}
-
-This can be simplified and re-written as:
-
-\begin{equation}
-\label{eq:log-alo-trans}
-Y = mX + c
-\end{equation}
-
-Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), \(m = b\), and
-\(c = log_{10}(a)\). Since \(b = m\), we will only use \(b\) throughout
-the paper for simplicity. The coefficients (\(c\) and \(b\)) were
-estimated with an Ordinary Least Square Regression and
-heteroskedastic-robust standard error correction was performed. Both
-coefficients were tested against the null hypothesis of no change
-(\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)). Additionally, the
-allometric parameter was tested against the null hypothesis of isometric
-growth (\(H_0: b = 3\)). Coefficients were tested with a two-tailed
-Student's t-test. The significance of the regression was corroborated
-with an F-test.
-
-Other length-weight relationships (n = 13) were extracted from
-peer-reviewed literature. Parameters were obtained for North Carolina
-{[}n = 1,barbour\_2011{]}, Northern {[}n = 3,fogg\_2013{]} and Southern
-Gulf of Mexico {[}n = 3,aguilarperera\_2016{]}, the Southern Mexican
-Caribbean {[}n = 1,sabidoitza\_2016{]}, Little Cayman {[}n =
-1,edwards\_2014{]}, Jamaica {[}n = 1,chin\_2016{]}, Bonaire {[}n =
-1,deleon\_2013{]} and Costa Rica {[}n = 1,sandel\_2015{]} and Fishbase
-{[}n = 1,froese\_website\_2016{]} were also included. When available,
-information on sampling methods, gender differentiation, location, and
-depth ranges of each study was retrieved. Whenever gender was not
-specified, it was assumed that the results were presented for pooled
-genders.
-
-During the review process, some papers indistinctly used \(a\) to report
-either the ponderal index in eq. 1 or the y-intercept (\(c\)) in eq. 3,
-which might sometimes be overlooked. Furthermore, some studies reported
-their parameters as mm-to-gr conversions, but a rapid evaluation of such
-parameters indicated that they were estimated as cm-to-gr conversions.
-Here, all parameters are reported as TL(mm) to TW(gr) conversions. When
-required, values from other studies were transformed for consistency.
-
-Since uncertainty arround estimated relationships was not reported in
-some of the reviewed studies, it was not possible to test for
-statistical differences between relationships. Instead, the 13
-length-weight relationships were usd to calculate expected weight for
-the organisms sampled in the Central Mexican Caribbean (n = 109).
-Expected weights were divided by the observed weights to obtain a ratio.
-Difference in mean weight ratios across studies were tested with a
-one-way Analysis of Variance (ANOVA).
-
-All hypothesis testing was performed with an \emph{a priori} confidence
-level of \(\alpha = 0.01\) in R version 3.4.0 \citep{rcore_2017}. Data
-wrangling was done with the tidyverse package \citep{tidyverse_2017}.
-Maps were created with a mix of functions from the sp \citep{sp_2017},
-rgdal \citep{rgdal_2017}, tmap \citep{tmap_2017}, and tmaptools
-\citep{tmaptools_2017} packages. Heteroskedastic-robust standard errors
-were calculated with the sandwich \citep{sandwich_2014} and lmtest
-\citep{lmtest_2002} packages. Models were manipulated with the broom
-package \citep{broom_2017}. Raw data and code used in this work is
-available at github.com/jcvdav/lionfish\_biometry.
-
-\section{Results}\label{results}
-
-Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7
-gr. The smallest organism (TL = 34.00 mm) was also the lightest organism
-(TW = 0.30 gr). However, the largest organism (TL = 310.00 mm) was not
-the heaviest (TW = 303.70 gr), and the heaviest organism (TW = 397.70
-gr) was 292.00 mm in total length. Kernell density plots (Fig. 2) show
-the distribution for TL and TW for all sampled organisms. Both measures
-were positively skewed, with skewness of 0.87 for TL and 2.25 for TW.
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/histogram figures-1.pdf}
-\caption{(\#fig:histogram figures)Kernell density plots for a) Total
-length (mm) and b) Total weight (gr) for 109 lionfish sampled in the
-central Mexican Caribbean.}
-\end{figure}
-
-\emph{Length-weight relationship}
-
-The model adjusted to eq. 3 estimated the coefficient values at
-\(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
-calculated from TL (mm) as a linear equation:
-\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
-exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
-The intercept (\(c\)) and slope \((b)\) were significantly different
-from zero (\(t(107) = -66.17; p<0.01\) and \(t(107) = 83.24; p<0.01\),
-respectively), rejecting the null hypothesis of no change. Additionally,
-the allometric factor (\(b\)) was significantly different from the value
-of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)), indicating
-that lionfish present allometric growth. More information on model fit
-and confidence intervals for the estimated coefficients is presented in
-Table II. The relationship between Total Length and Total Weight is
-presented in Figure 3.
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/scatter plot-1.pdf}
-\caption{(\#fig:scatter plot)Length-weight relationship for 109 lionfish
-sampled in the central Mexican Caribbean. Points indicate samples, solid
-line indicates curve of best fit.}
-\end{figure}
-
-\begin{table}[!htbp] \centering 
-  \caption{Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
-Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.}
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & log10(TW) \\ 
-\hline \\[-1.8ex] 
- c & $-$5.494 (0.083)$^{***}$ \\ 
-  b & 3.235 (0.039)$^{***}$ \\ 
- \hline \\[-1.8ex] 
-95\% CI for c & (-5.657--5.331) \\ 
-85\% CI for b & (3.159-3.311) \\ 
-F Statistic & 6928.67*** (df = 1; 107) \\ 
-Observations & 109 \\ 
-Adjusted R$^{2}$ & 0.976 \\ 
-Residual Std. Error & 0.096 (df = 107) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\emph{Comparison of allometric parameters}
-
-From the eight peer-reviewed studies including information on growth
-parameters for \emph{P. volitans} and Fishbase
-\citep{froese_website_2016}, 13 parameters were identified (Table III).
-Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level
-and pooled parameters, while the rest presented pooled results. The
-smallest coefficient of determination was presented by \citet{chin_2016}
-with \(R^2 = 0.8715\), while \citet{sabidoitza_2016} reported the
-highest value at \(R^2 = 0.9907\). Reviewed studies presented
-information for organisms obtained at depths between 0.5 and 57 m. Two
-studies \citep{aguilarperera_2016,chin_2016} explicitly stated that
-their organisms were sampled with pole spears. Five studies
-\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016}
-mentioned that some of their organisms were obtained with pole spears
-(or other type of harpoon). A single study \citep{deleon_2013} did not
-specify how organisms were sampled.
-
-Parameters from models fit to males or females exclusively tend to have
-a higher steepness (\emph{i.e.} higher allometric parameter), with mean
-\(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
-\(b = 3.31 \pm 0.23\) for males and females respectively, compared to
-parameters from models for pooled genders with a mean \(\pm\) standard
-deviation value of \(b = 3.09 \pm 0.22\). In the case of the ponderal
-index (\(a\)) and its \(log_{10}\) transformed parameter (\(c\)), values
-were higher for parameters for pooled genders. Figure 4 shows the
-predicted weights for organisms within the size range of these study
-using the 14 parameters previously described.
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/review plots-1.pdf}
-\caption{(\#fig:review plots)Length-weight relationships (n = 14) for
-eight studies, this study, and Fishbase. Colors indicate studies from
-which the parameters were extracted. Solid lines indicate that the fit
-was performed for males and females pooled together. Dotted lines
-indicate that the regression was performed on females, and dashed lines
-indicate it was performed for males.}
-\end{figure}
-
-There were significant differences in expected-to-observed weight ratios
-estimated for each pair of parameters (F(13, 1512) = 39.28; p
-\textless{} 0.05). From all allometric parameters reviewed, those of
-\citet{edwards_2014} provided the lowest weight estimates, with an
-expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
-SD). On the other hand,barbour\_2011 yielded the highest weight
-estimates, with a mean (\(\pm\) SD) expected-to-observed weight ratio of
-1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
-identified by Tukey's HSD (\(\alpha = 0.05\)) are presented in Figure 5.
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/plot comparing predictions-1.pdf}
-\caption{(\#fig:plot comparing predictions). Box and whiskers plot
-showing the distribution of predicted to observed biomass ratios for 14
-pairs of allometric parameters. Lines indicate median values, circles
-indicate mean values, notches represent 95\% confidence intervals
-arround the median, lower and upper hinges correspond to the first and
-third quartiles, whiskers extend to the largest and lowes values within
-1.5 inter-quartile range of the hinge, small points represent outliers
-further away than the whiskers. Like letters indicate values that do not
-differ significantly (Tukey's HSD; p \textless{} 0.05).}
-\end{figure}
-
-\section{Discussion}\label{discussion}
-
-This study provides the first pair of allometric growth parameters
-specific to the Central Mexican Caribbean, complementing other studies
-performed in Mexican waters in the Alacranes Reef
-\citep{aguilarperera_2016} and Xcalak National Park
-\citep{sabidoitza_2016}. By using hand nets instead of spears, we are
-able to sample a wider range of sizes often ignored by pole spear
-samples, allowing us to include smaller organisms. Estimating parameters
-by including smaller organisms ensures better estimation of weight for
-smaller sizes. This is especially important when biomass is calculated
-from visual census, where small organisms can be registered. Thus, this
-study also increases certainty in weight estimation of small organisms.
-
-The length-weight coefficients estimated in this study were within the
-range identified by studies in other regions
-\citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016,edwards_2014,chin_2016,deleon_2013,sandel_2015}.
-However, the ones presented here provide lower weight estimates for a
-same length. Until about TL = 200 mm, there are no appreciable
-differences between the parameters for organisms from the Mexican
-Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica
-\citep{chin_2016}. Yet, for larger organisms (TL \textgreater{} 270 mm)
-parameters from Costa Rica \citep{sandel_2015} and Bonaire
-\citep{deleon_2013} provide similar estimates to those from this study.
-Conversely, these same studies tend to estimate higher weights ---as
-compared to the ones reported here--- for smaller organisms, likely due
-to the lack of small organisms in the samples used to estimate their
-parameters. When ever possible, future works should consider the use of
-hand nets to obtain the samples not only for studies on
-weight-at-length, but also diet, behavior and life history, where length
-can be an important factor.
-
-There are evident differences in weight-at-length between organisms from
-the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight
-estimates with parameters from the Gulf of Mexico and North-Western
-Atlantic
-\citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016} tend
-to be higher than those from the Caribbean
-\citep{edwards_2014,chin_2016,deleon_2013,sandel_2015}, except for the
-ones from Xcalak National Park, Mexico \citep{sabidoitza_2016}. This
-indicates that there are differences between lionfish across the
-invasion range. Similar regional variation exist for age-at-length
-relationships of lionfish \citep{fogg_2015}. These differences can have
-major implications in management, especially when estimating biomass
-available for harvest or predicting effects on local ecosystems, or
-evaluating the effectiveness of removal programs. Using site-specific
-values provides a more accurate estimate of fish biomass. Future
-research should try to use, to the extent possible, parameters
-calculated for their region, or use different parameters to provide
-upper and lower bounds in their results. At the same time, this
-highlights the need for more basic research that furthers our
-understanding of lionfish biology. To better manageme the invasion, we
-must perform research that can describe biologically important
-information of lionfish throughout its invasion range
-\citep{johnson_2016}.
-
-While performing the literature review, it was often unclear if
-parameters were presented for eq.1 or eq. 3. Sometimes, they were even
-mislabeled and yielded senseless results when using the suggested
-conversion equation. On other cases, parameters were said to be reported
-for mm-to-gr conversions, when they were actually reported as cm-to-gr
-conversions. Perhaps these minor discrepancies can be easily solved by
-the trained eye, but why should they exist in the first place? It is
-important that we report our information in a standard way, making it
-readily available for other researchers and managers. In this particular
-case, I provide my humble opinion through 5 guidelines to report
-allometric parameters:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Be explicit in the methods section. What may seem obvious to you as an
-  author ---because you have been deeply immersed throughout the
-  process--- may not be clear to the reader. Specify any transformation
-  performed on the data. When using log-transformations, mention the
-  base used to transform. Do not assume that ``data were
-  log-transformed'' means \(log_{10}(X)\). These assumptions vary across
-  disciplines and software and can be a source of confusion. For
-  example, in biology we often assume ``log-transformed'' indicates the
-  use of base 10, however in R the proper command is \texttt{log10()}
-  and not \texttt{log()}, which uses base \(e\).
-\item
-  Use mm and gr to measure TL and TW, respectively. While conversion is
-  always possible, we should aim at using standard units to report these
-  parameters. If you prefer to use cm to gr conversions, that is
-  certainly valid, but make sure to explicitly mention units when
-  presenting the parameters.
-\item
-  Specify the equation for which parameters are presented by including
-  an explicit example with the parameters substituted into it, as done
-  by some of the papers reviewed
-  \citep{chin_2016,sandel_2015,deleon_2013,sabidoitza_2016}. If
-  possible, present the relationship in their exponential (eq. 1) and
-  linear (eq. 3) forms.
-\item
-  Report standard errors and/or confidence intervals around the obtained
-  estimates. Given that small changes in \(a\), \(c\), and \(b\) can
-  result in important changes in estimated weight, it is important that
-  we report uncertainty around each parameter and not just general model
-  fit and coefficient significance. Reporting uncertainty around
-  parameters allows researchers and managers to include upper and lower
-  bounds in their predictions.
-\item
-  Make your data and code available. Even if this is not requited by the
-  journal or publisher, you can use free cloud data storage services or
-  third-party repositories to make your research accessible to others.
-  Resources will always be limited and budget will rarely be enough. It
-  is important that we take advantage of open science tools that promote
-  the advancement of knowledge and foster collaboration. Ultimately,
-  this promotes transparency, allows replicability of research, and
-  advances science.
-\end{enumerate}
-
-This study provides a new pair of allometric growth parameters for
-lionfish from the central Mexican Caribbean, where they exhibit
-different weight-at-length. Furthermore, regional differences in
-length-weight relationships were identified, highlighting the importance
-of using site-specific parameters.
-
-\section{Aknowledgements}\label{aknowledgements}
-
-I would like to thank thank Nils Van Der Haar and Michael Doodey from
-Dive Aventuras as well as Guillermo Lotz-Cador who provided help to
-collect samples. I would also like to (anticipatedly) thank the editor
-and reviewers, who significantly improved the quality of this work. This
-research was partially funded by the ``Consejo Nacional de Ciencias y
-Tecnología'' (CONACyT) and the Latin American Fisheries Fellowship
-Program.
+Note that the \texttt{echo\ =\ FALSE} parameter was added to the code
+chunk to prevent printing of the R code that generated the plot.
 

### 2018-02-25 Manuscript.Rmd
Added new version of manuscript

@@
 ---
-title: "Allometric growth parameters for invasive lionfish *Pterois volitans* (Actinopterygii, Scorpaenidae) in the Western Atlantic"
+title: "Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic"
 author: "Juan Carlos Villaseñor-Derbez"
@@
 In order to better manage the invasion, inform lionfish removal programs, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass, frequently from length observations.
-This work compares length-weight relationships of the invasive lionfish through the invasion range and reports the length--weight relationship for lionfish in the Central Mexican Caribbean.
-A review of 13 length--weight relationships reported in eight peer-reviewed studies and FishBase is provided.
-These parameters were used to identify spatial variation in weight-at-length.
-For a given length, parameters from the Caribbean yielded lower weights than those from the Gulf of Mexico and Atlantic, indicating that weight-at-length is spatially variable.
+This work compares length-weight relationships of the invasive lionfish through the invasion with the addition of parameters for the Central Mexican Caribbean.
+A review of 15 length-weight relationships reported in 10 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length.
+The reviewed parameters indicate that, for the same length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf of Mexico.
 This highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean.
+This study also reports a new pair of length-weight parameters ($a = 3.2056\\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean.
 Findings from this work can aid managers and decision makers to better select length-weight parameters when these are not available for their region of interest."
+header-includes: #allows you to add in your own Latex packages
+- \usepackage{float} #use the 'float' package
+- \floatplacement{figure}{H} #make every figure with caption = h
 output:
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F)
+knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 5.5)
 
-# options(knitr.table.format = "latex")
+options(knitr.table.format = "latex")
 
@@
   library(tmap)
-  library(tmaptools)
   library(rgdal)
-  library(sp)
-  library(RefManageR)
+  library(sf)
+  library(cowplot)
   library(tidyverse)
@@
 
-At least 84% of the marine eco-regions have reported the presence of an invasive species \citep{molnar_2008}.
-These represent a major threat to local biodiversity and the economic activities that depend on it, like tourism or fisheries \citep{bax_2003}.
-Invasive species may also threaten native species through competition \citep{davis_2003} or predation.
-By 2005, the economic cost of invasive species to the United States was  estimated at \$120 billion per year and nearly 42% of species that have been included in the Endangered or Threatened species list have been labeled as such due to presence of invasive species \citep{pimentel_2005}.
-This highlights the importance of understanding, managing, and preventing ecological invasions.
+At least 84% of the marine eco-regions have reported the presence of an invasive species \citep{molnar_2008}, which represent a major threat to local biodiversity and the economic activities that depend on it \citep{bax_2003}.
+Invasive species may threaten native species through predation, competition, or indirect habitat effects \citep{davis_2003, gurevitch_2004}.
+By 2005, the economic cost of invasive species to the United States was  estimated at USD\$120 billion per year\citep{pimentel_2005}.
 
-Lionfish (*Pterois volitans/miles* complex) are an invasive species in the North-Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
+Lionfish (*Pterois volitans/miles* complex) are an invasive species in the Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
 They are the first marine vertebrates to establish in North Atlantic \citep{schofield_2009,schofield_2010} and Caribbean coasts \citep{sabidoitza_2016}.
 Lionfish have been widely reported in coral reefs \citep{aguilarperera_2010}, but also in other habitats such as estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with hard-bottoms \citep{muoz_2011}, and mesophotic reefs \citep{andradibrown_2017}.
-Due to its threat to local biodiversity, the speed of their spread, and its difficulty of management, their presence in these waters has been labeled as a major marine invasion  \citep{hixon_2016}.
+Due to their threat to local biodiversity, the speed of their spread, and difficulty of management, their presence in these waters has been labeled as a major marine invasion  \citep{hixon_2016}.
 
@@
 Their feeding behavior and high consumption rates can reduce recruitment \citep{albins_2008} and population sizes \citep{green_2012} of native reef-fish species, and further the endangerment of critically endangered reef fish \citep{rocha_2015}.
-(However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or composition of prey fishes).
-Major efforts have also been made to understand the possible impacts of the invasion by keeping track of its range through time \citep{schofield_2009,schofield_2010} and predicting invasion ranges under climate change scenarios \citep{grieve_2016}.
+(However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes).
+Major efforts have been made to understand the possible impacts of the invasion by keeping track of its range through time \citep{schofield_2009,schofield_2010} and predicting invasion ranges under future climates \citep{grieve_2016}.
 By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish \citep{ariasgonzalez_2011}, which can then be translated into ecosystem-level and economic impacts.
@@
 Seeking to reduce lionfish densities, governments and non-profit organizations have promoted removal programs and incentivized its consumption \citep{chin_2016}.
-In some cases, these have shown to significantly reduce -but not quite eliminate- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
-The rapid recovery rates exhibited by lionfish \citep{barbour_2011} and the persistent populations in mesophotic coral ecosystems \citep{andradibrown_2017} -which can contribute with recruitment to shallow-water populations- make of complete eradication through fishing effort an unlikely solution.
-However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery \citep{chin_2016}, which can reduce local abundances and control -not eradicate- the invasion while providing alternative livelihoods.
+In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
+The rapid recovery rates exhibited by lionfish \citep{barbour_2011} and the persistent populations in mesophotic coral ecosystems \citep{andradibrown_2017} --which can contribute with recruitment to shallow-water populations-- make of complete eradication through fishing effort an unlikely solution.
+However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery \citep{chin_2016}, which can reduce local abundances and control the invasion while providing alternative livelihoods.
 
 The feasibility of lionfish removal programs has been extensively evaluated through field observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}.
-The latter measure changes in biomass or density \citep{barbour_2011,johnston_2015} in response to increased mortality (*i.e.* lionfish removal).
+The latter approeach models changes in biomass in response to changes in mortality (*i.e.* culling).
 In this case, biomass represents the sum of all fish's individual weight.
-Total Weight (TW) can be estimated from Total Length (TL) observations using the allometric growth equation ($TW = aTL^b$).
-Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean.
+The individual weight of an organism (Total Weight; TW) can be estimated from its Total Length (TL) using the allometric growth equation ($TW = aTL^b$).
+Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean.
 The weight-at-length of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Thus, when using biomass-informed models or estimating biomass from length observations, it is important to use site-specific parameters to obtain an accurate estimate.
+Thus, when using biomass-informed models or estimating weights from length observations, it is important to use site-specific parameters.
 This is especially important when research involves identifying the total biomass available for harvest by fishers \citep{chin_2016} or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015}.
 
-Here, I provide the first allometric growth parameters for the invasive lionfish in the central Mexican Caribbean region.
-At the same time, I highlight the importance of using site-specific parameters by estimating biomass with parameters from other regions across the invasion range and comparing them to observed biomass.
-I also provide other 13 standardized parameters from eight studies through the invasion range, making them readily accessible for future research.
-Finally, I discuss the way in which allometric parameters are reported, and call for standardization to facilitate their use.
-
-\clearpage
+This study reviews lionfish allometric growth throughout the invasion range, and provides a new pair of parameters specific to the central Meixcan Caribbean.
+The results suggest there are important regional-scale variations in allometric growth patterns of lionfish.
+The observed differences highlight the importance of using site-specific parameters, especially when informing invasion management strategies.
 
@@
   ungroup()
+
+review <- read.csv("biometric_review.csv", stringsAsFactors = F, strip.white = T, blank.lines.skip = T) %>% 
+  mutate(c = log10(a),
+         Gender2 = case_when(Gender == "Male" ~ "M",
+                             Gender == "Female" ~ "F",
+                             TRUE ~"B"))
+
 ```
 
-*Area of study*
+The main objective of this work was to compare allometric growth of lionfish throughout the invasion range.
+Allometric parameters were retreived from scientific literature, and an additional pair of parameters was calculated from filed observations in the central Mexican Caribbean.
 
-The study took place off the coasts of Playa del Carmen, in the Mexican Caribbean Figure \ref{fig:map}.
-The region represents the northernmost section of the Mesoamerican Barrier Reef System \citep{ruizzarate_2004}.
-Coral reefs and mangroves are locally important habitats that represent important sources of income in terms of extractive (*e.g.* recreational fishing) and non-extractive (*e.g.* SCUBA diving) activities related to tourism, the main source of income to the local economy \citep{murray_2007}.
+Length-weight relationships (n = 15) identified in literature were obtained for North Carolina (n = 1, \citet{barbour_2011}), Northern (n = 3, \citet{fogg_2013}) and Southern Gulf of Mexico (n = 3, \citet{aguilarperera_2016}), the Southern Mexican Caribbean (n = 1, \citet{sabidoitza_2016}), Little Cayman (n = 1,\citet{edwards_2014}), Jamaica (n = 1, \citet{chin_2016}), Bonaire (n = 1, \citet{deleon_2013}) and Costa Rica (n = 1, \citet{sandel_2015}).
+Locations with allometric parameters are shown in Figure \ref{fig:map}.
+When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retrieved.
+Whenever gender was not specified, it was assumed that the results were presented for pooled genders.
 
-The reef profile has been described by \citet{ariasgonzalez_1998}, indicating that the reef lagoon extends about 500 m from the coast, until the reef crest is reached.
-The reef becomes deeper, leading to the reef front often found at 700 m from the coastline and extends for an additional 300 m.
-At approximately 1000 m away from shore and 30 - 40 m depth, the reef leads to a drop-off.
-Along a perpendicular profile to the coast, bands of reef are interrupted by sand patches at 8 - 12 m deep and 16-18 m deep.
-Along the coast, these reefs have been reported to be under significant anthropogenic pressure, likely causing a shift in structure and function \citep{bozec_2008}.
+Parameters from the central Mexican Caribbean were obtaines from data collected in `r length(unique(fish$Location))` sampling sites along the Mexican Caribbean coast in 2010 (Table S1).
+Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
+All observed lionfish (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
+The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes by eliminating gear selectivity.
+Organisms were euthanized (via pithing) and Total Length (TL; mm) and Total Weight (TW; gr) were recorded before freezing organisms.
 
-```{r fig.cap = "\\label{fig:map}Map of the study area.
-The black inset on the left (Yucatan Peninsula) indicates the location where study sites are distributed.
-On the right, circular markers indicate sampling sites and the black romboid indicates location of Puerto Aventuras, Mexico."}
-# Load shapefiles
+\clearpage
+
+```{r, fig.cap = "\\label{fig:map}Locations where allometric growth of lionfish (*Pterois spp*) have been reported.
+Sizes indicate sample size of each study, colors indicate the b coefficient in Eq \\ref{eq:allometric}"}
+
 proj <- CRS("+proj=longlat +datum=NAD27")
 
-load("./Spatial/coastline_mx.Rda")
+# Load coastline for Mexico and World
+coastline <- ("./Spatial/coastline_mx.rds")
+
+data(World)
+W <- spTransform(World, proj) %>% 
+  st_as_sf()
 
@@
 proj4string(xy1) <- proj
-res1 <- spTransform(xy1, proj)
+res1 <- spTransform(xy1, proj) %>% 
+  st_as_sf()
 
@@
 
-pen_map <- tm_shape(baja2, bbox = bb(xlim = c(-89.29656, -86.71074), ylim = c(17.89399, 21.60525))) +
-  tm_polygons() +
-  tm_shape(res1) +
-  tm_symbols(shape = 5, size = 2, border.col = "black", col = "black", border.lwd = 2) +
-  tm_scale_bar()
+# Map with SF
 
-study_area <- tm_shape(baja2, bbox = bb(xlim = c(-87.30662, -87.19194), ylim = c(20.39283, 20.51278))) +
-  tm_polygons() +
-  tm_shape(b) +
-  tm_symbols(size = 0.125, border.col = "black", col = "black") +
-  tm_shape(c) +
-  tm_symbols(shape = 18, col = "black", border.col = "black", size = 0.5) +
-  tm_compass() +
-  tm_scale_bar()
-
-tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
-
+ggplot() +
+  geom_sf(data = W, aes(label = name)) +
+  geom_point(data = review[review$Gender == "Both", ], aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
+  theme_classic() +
+  scale_fill_gradientn(colors = colorRamps::matlab.like(20)) +
+  theme(legend.justification = c(0, 1),
+        legend.position = c(0, 1),
+        legend.background = element_blank()) +
+  guides(colorbar = guide_legend(order = 0),
+         size = guide_legend(order = 1, direction = "horizontal", title.position = "top")) +
+lims(x = c(-106, -60), y = c(9, 36))
 ```
 
-*Fish sampling*
-
-A total of 33 SCUBA immersions were performed in `r length(unique(fish$Location))` sampling sites along the coast in 2010 (Fig.
-1, Table I).
-Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
-All observed organisms (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes, often ignored due to gear selectivity when spearing.
-Organisms were euthanized and frozen within 30 minutes of completing the dive and stored for posterior analysis.
-Total Length (TL; mm) and Total Weight (TW; gr) were recorded for all organisms.
-
-```{r table of locations, results = "asis"}
-total <- data.frame(Location = "Total", Latitude = "", Longitude = "", minD = min(fish$Depth_m), maxD = max(fish$Depth_m), meanD = formatC(mean(fish$Depth_m), digits = 1, format = "f"), n = 109, stringsAsFactors = F)
-
-fish %>% 
-  group_by(Location) %>% 
-  summarize(Latitude = formatC(mean(Latitude), digits = 3, format = "f"),
-            Longitude = formatC(mean(Longitude), digits = 3, format = "f"),
-            minD = formatC(min(Depth_m), digits = 1, format = "f"),
-            maxD = formatC(max(Depth_m), digits = 1, format = "f"),
-            meanD = formatC(mean(Depth_m), digits = 1, format = "f"),
-            n = n()) %>% 
-  rbind(total) %>% 
-  knitr::kable(row.names = F,
-               col.names = c("Location", "Lat.", "Long.", "Min. Depth", "Max. Depth", "Mean Depth", "n"),
-               booktabs = T, caption = c("Coordinates, minimum, maximum and mean depth (m), and number of samples for each location."))
-```
-
-*Data analysis*
-
-The weight at length relationship between the observed variables is described by the allometric growth function:
+The weight at length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function:
 
@@
 Since $b = m$, we will only use $b$ throughout the paper for simplicity.
-The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction was performed.
+The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
 Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$).
@@
 
-Other length-weight relationships (n = 13) were extracted from peer-reviewed literature.
-Parameters were obtained for North Carolina [n = 1,barbour_2011], Northern [n = 3,fogg_2013] and Southern Gulf of Mexico [n = 3,aguilarperera_2016], the Southern Mexican Caribbean [n = 1,sabidoitza_2016], Little Cayman [n = 1,edwards_2014], Jamaica [n = 1,chin_2016], Bonaire [n = 1,deleon_2013] and Costa Rica [n = 1,sandel_2015] and Fishbase [n = 1,froese_website_2016] were also included.
-When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retrieved.
-Whenever gender was not specified, it was assumed that the results were presented for pooled genders.
-
-During the review process, some papers indistinctly used $a$ to report either the ponderal index in eq.
-1 or the y-intercept ($c$) in eq.
-3, which might sometimes be overlooked.
-Furthermore, some studies reported their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicated that they were estimated as cm-to-gr conversions.
+During the review process, some studies indistinctly used $a$ to report either the ponderal index in \ref{eq:allometric} or the y-intercept ($c$) in \ref{eq:log-alo-trans}.
+Others reported their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicated that they were estimated as cm-to-gr conversions.
 Here, all parameters are reported as TL(mm) to TW(gr) conversions.
@@
 
-Since uncertainty arround estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships.
-Instead, the 13 length-weight relationships were usd to calculate expected weight for the organisms sampled in the Central Mexican Caribbean (n = 109).
+Since uncertainty around estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships.
+Instead, the 16 length-weight relationships were used to calculate expected weight length observations of the organisms sampled from the Central Mexican Caribbean (n = 109).
 Expected weights were divided by the observed weights to obtain a ratio.
@@
 
-All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 \citep{rcore_2017}.
-Data wrangling was done with the tidyverse package \citep{tidyverse_2017}.
-Maps were created with a mix of functions from the sp \citep{sp_2017}, rgdal \citep{rgdal_2017}, tmap \citep{tmap_2017}, and tmaptools \citep{tmaptools_2017} packages.
-Heteroskedastic-robust standard errors were calculated with the sandwich \citep{sandwich_2014} and lmtest \citep{lmtest_2002} packages.
-Models were manipulated with the broom package \citep{broom_2017}.
-Raw data and code used in this work is available at github.com/jcvdav/lionfish_biometry.
+All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 \citep{rcore_2017}. Raw data and code used in this work is available at dryad.org.
 
-# Results
-
-Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7 gr.
-The smallest organism (TL = `r formatC(min(fish$Length), digits = 2, format = "f")` mm) was also the lightest organism (TW = `r formatC(min(fish$Weight), digits = 2, format = "f")` gr).
-However, the largest organism (TL = `r formatC(max(fish$Length), digits = 2, format = "f")` mm) was not the heaviest (TW = `r formatC(fish$Weight[fish$Length == max(fish$Length)], digits = 2, format = "f")` gr), and the heaviest organism (TW = `r formatC(max(fish$Weight), digits = 2, format = "f")` gr) was `r formatC(fish$Length[fish$Weight == max(fish$Weight)], digits = 2, format = "f")` mm in total length.
-Kernell density plots (Fig.
-2) show the distribution for TL and TW for all sampled organisms.
-Both measures were positively skewed, with skewness of `r formatC(skewness(fish$Length), digits = 2, format = "f")` for TL and `r formatC(skewness(fish$Weight), digits = 2, format = "f")` for TW.
-
-```{r histogram figures, fig.width = 5, fig.height = 6, fig.cap = "Kernell density plots for a) Total length (mm) and b) Total weight (gr) for 109 lionfish sampled in the central Mexican Caribbean."}
+```{r, include = F}
 length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
   geom_density(fill = "gray", alpha = 0.5) +
-  theme_bw() +
-  ggExtra::removeGrid() +
+  theme_cowplot() +
   labs(x = "Total Length (mm)", y = "Density") +
-  geom_text(label = "A", x = 310, y = 0.007) +
   theme(text = element_text(family = "Times"))
@@
   geom_density(fill = "gray", alpha = 0.5) +
-  theme_bw() +
-  ggExtra::removeGrid() +
+  theme_cowplot() +
   labs(x = "Total weight (gr)", y = "Density") +
-  geom_text(label = "B", x = 400, y = 0.017) +
   theme(text = element_text(family = "Times"))
 
-gridExtra::grid.arrange(length_hist, weight_hist)
+# Density distributions for A) Total length (mm) and B) Total weight (gr) for 109 lionfish sampled in the Central Mexican Caribbean.
+FigS1 <- cowplot::plot_grid(length_hist, weight_hist, ncol = 1, labels = "AUTO")
+ggsave(FigS1, file="FigS1.png", width = 5.5, height = 6, dpi = 600)
 ```
@@
 test_slope_3 <- 2*pt(abs((coef(model)[[2]]-3)/robust_se[[2]]), df = 107, lower.tail = F)
-```
-
-*Length-weight relationship*
-
-The model adjusted to eq.
-3 estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
-Thus, TW (gr) can be calculated from TL (mm) as a linear equation: $log_{10}(TW) = `r coef(model)[[2]]`\times log_{10}(TL) `r coef(model)[[1]]`$, or its exponential form: $TW = `r 10^coef(model)[[1]]`\times TL^{`r coef(model)[[2]]`}$.
-The intercept ($c$) and slope $(b)$ were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.01$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.01$, respectively), rejecting the null hypothesis of no change.
-Additionally, the allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.01$), indicating that lionfish present allometric growth.
-More information on model fit and confidence intervals for the estimated coefficients is presented in Table II.
-The relationship between Total Length and Total Weight is presented in Figure 3.
-
-```{r scatter plot, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit."}
 
@@
   mutate(Weight = 10^a*Length^b)
+```
 
-plot_fit_this_study <-  ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
+```{r}
+Predicted_biomass <- review %>% 
+  mutate(Length = list(fish$Length),
+         Weight = list(fish$Weight)) %>% 
+  unnest() %>% 
+  mutate(Biomass_ratio = (a*(Length^b))/Weight)
+
+anova <- aov(Biomass_ratio ~ Study_id, Predicted_biomass)
+groups <- HSD.test(y = anova, trt = "Study_id")
+```
+
+# Results
+
+The model adjusted to \ref{eq:log-alo-trans} estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
+Thus, TW (gr) can be calculated from TL (mm) as a linear equation: $log_{10}(TW) = `r coef(model)[[2]]`\times log_{10}(TL) `r coef(model)[[1]]`$, or its exponential form: $TW = `r 10^coef(model)[[1]]`\times TL^{`r coef(model)[[2]]`}$.
+The intercept ($c$) and slope $(b)$ were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.001$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.001$, respectively), rejecting the null hypothesis of no change.
+Additionally, the allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), indicating that lionfish present allometric growth.
+More information on model fit and confidence intervals for the estimated coefficients is presented in TableS2.
+The relationship between Total Length and Total Weight is presented in Figure \ref{fig:l-w-carib}.
+
+From the 11 peer-reviewed studies including information on growth parameters for *P.
+volitans* and the additional calculated for the central Mexican Caribbean, `r dim(review)[1]` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
+Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
+The smallest coefficient of determination was presented by \citet{chin_2016} with $R^2 = `r min(review[,13], na.rm = T)`$, while \citet{sabidoitza_2016} reported the highest value at $R^2 = `r max(review[,13], na.rm = T)`$.
+Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
+Three studies \citep{aguilarperera_2016,chin_2016,dahl_2014} explicitly stated that their organisms were sampled with pole spears.
+Five studies \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014} mentioned that some of their organisms were obtained with pole spears (or other type of harpoon), but also hand-held nets or fish traps.
+Two studies \citep{deleon_2013,darling_2011} did not specify how organisms were sampled.
+
+Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
+In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for pooled genders.
+Figure \ref{fig:all_allo} shows the weight-at-length relationships with parameters from all studies.
+
+There were significant differences in expected-to-observed weight ratios estimated for each pair of parameters (F(15, 1728) = 38.26; p < 0.001).
+From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
+On the other hand,\citet{barbour_2011} yielded the highest weight estimates, with a mean ($\pm$ SD) expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
+Predicted-to-observed weight ratios and groups identified by Tukey's HSD ($\alpha = 0.05$) are presented in Figure \ref{fig:bio_ratio}.
+
+\clearpage
+
+```{r, fig.height = 3.5, fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the Central Mexican Caribbean.
+Points indicate samples, solid line indicates curve of best fit (See Table S1)."}
+
+ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
   geom_line(data = predicted_this_study, mapping = aes(x = Length, y = Weight), size = 1) +
   geom_point(size = 2, alpha = 0.25, color = "black") +
-  theme_bw() +
+  theme_cowplot() +
   labs(x = "Total length (mm)", y = "Total Weight (gr)") +
@@
   theme(text=element_text(family="Times"))
-
-plot_fit_this_study
 ```
 
-```{r, results = "asis"}
-
-ci_c <- c("95\\% CI for c", paste0("(", formatC(a-(1.96*robust_se[[1]]), digits = 3, format = "f"),"-", formatC(a+(1.96*robust_se[[1]]), digits = 3, format = "f"),")"))
-
-ci_b <- c("85\\% CI for b", paste0("(", formatC(b-(1.96*robust_se[[2]]), digits = 3, format = "f"),"-", formatC(b+(1.96*robust_se[[2]]), digits = 3, format = "f"),")"))
-
-regression_table <- stargazer(model,
-          header = F,
-          se = list(robust_se),
-          type = "latex",
-          t.auto = T,
-          p.auto = T,
-          intercept.bottom = F,
-          single.row = T,
-          report = "vcs*",
-          omit.stat = c("rsq", "f"),
-          add.lines = list(ci_c, ci_b, f_string),
-          covariate.labels = c("c", "b"),
-          dep.var.labels = "log10(TW)", title = "Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
-Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.")
-```
-
-```{r, results = "asis"}
-review <- read_csv("biometric_review.csv", col_types = cols(), na = "-")
-
-my.df <- data.frame(Study = unique(review$Study), Reference_no = seq(1 : length(unique(review$Study))), stringsAsFactors = F)
-
-review_table <- review %>% 
-  left_join(my.df, by = "Study") %>% 
-  select(Reference = Reference_no, Region = Study_site, Sex = Gender, n = N, a, c, b, r2, minD, maxD, Spear) %>% 
+```{r}
+review %>% 
+  select(Study_site, Gender2, N, a, b, r2, Study) %>% 
+  filter(!Study == "Fishbase") %>% 
+  arrange(Study_site) %>% 
   mutate(r2 = ifelse(is.na(r2), "-", r2),
-         minD = ifelse(is.na(minD), "-", minD),
-         maxD = ifelse(is.na(maxD), "-", maxD)) %>% 
-  knitr::kable(format = "latex",
-               row.names = F,
-               digits =  c(1, 0, 6, 4, 4, 4, 0, 1, 1),
+         N = ifelse(is.na(N), "-", N)) %>% 
+  knitr::kable(row.names = F,
+               digits =  c(0, 0, 0, 7, 2),
                booktabs = T,
-               col.names = c("Reference", "Region", "Sex", "a", "c", "b", "R2", "n", "mDepth", "MDepth", "Spear"),
-               caption = c("Summary of 13 allometric growth parameters available for lionfish in the invaded range from eight peer-reviewed papers, Fishbase \\citep{froese_website_2016}, and this study.
+               col.names = c("Region", "Sex", "n", "a", "b", "R2", "Reference"),
+               caption = c("\\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
@@
 3, respectively.
-The R^2^ column indicates reported model fit.
-mDepth and MDepth indicate minimum and maximum depths (m), respectively, at which organisms were sampled.
-The Spear column indicates if the study collected organisms with pole spears.
-An asterisk indicates that some portion of organisms were sampled with pole spears.
-1 = \\citet{aguilarperera_2016}, 2 = \\citet{sandel_2015}, 3 = \\citet{chin_2016}, 4 = \\citet{barbour_2011}, 5 = \\citet{deleon_2013}, 6 = \\citet{fogg_2013}, 7 = \\citet{edwards_2014}, 8 = \\citet{sabidoitza_2016}, 9 = \\citet{froese_website_2016}, 10 = This study.")) %>%
-  kableExtra::kable_styling(latex_options = c("scale_down"))
+The $R^2$ column indicates reported model fit."))
 ```
 
-*Comparison of allometric parameters*
+\clearpage
 
-From the eight peer-reviewed studies including information on growth parameters for *P.
-volitans* and Fishbase \citep{froese_website_2016}, `r dim(review)[1]-1` parameters were identified (Table III).
-Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
-The smallest coefficient of determination was presented by \citet{chin_2016} with $R^2 = `r min(review[,13], na.rm = T)`$, while \citet{sabidoitza_2016} reported the highest value at $R^2 = `r max(review[,13], na.rm = T)`$.
-Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
-Two studies \citep{aguilarperera_2016,chin_2016} explicitly stated that their organisms were sampled with pole spears.
-Five studies \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016} mentioned that some of their organisms were obtained with pole spears (or other type of harpoon).
-A single study \citep{deleon_2013} did not specify how organisms were sampled.
-
-Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
-In the case of the ponderal index ($a$) and its $log_{10}$ transformed parameter ($c$), values were higher for parameters for pooled genders.
-Figure 4 shows the predicted weights for organisms within the size range of these study using the 14 parameters previously described.
-
-```{r review plots, fig.height = 4.5, fig.width = 6, fig.cap = "Length-weight relationships (n = 14) for eight studies, this study, and Fishbase.
+```{r, fig.height = 3.8, fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 16) for eight studies, this study, and Fishbase.
 Colors indicate studies from which the parameters were extracted.
@@
 
-predicted_all <- data.frame(Length = seq(1, 300, by = 1)) %>% 
-  mutate(This = review$a[14] * (Length^review$b[14]), 
-         APA = review$a[1] * (Length^review$b[1]),
-         APF = review$a[2] * (Length^review$b[2]),
-         APM = review$a[3] * (Length^review$b[3]),
-         Sandel = review$a[4] * (Length^review$b[4]),
-         Chin = review$a[5] * (Length^review$b[4]),
-         Barbour = review$a[6] * (Length^review$b[6]),
-         deLeon = review$a[7] * (Length^review$b[7]),
-         FoggA = review$a[8] * (Length^review$b[8]),
-         FoggM = review$a[9] * (Length^review$b[9]),
-         FoggF = review$a[10] * (Length^review$b[10]),
-         Edwards = review$a[11] * (Length^review$b[11]),
-         Sabido = review$a[12] * (Length^review$b[12]),
-         FishBase = review$a[13] * (Length^review$b[13])) %>%
-  gather(Study_id, Weight, -Length) %>% 
-  left_join(review, by ="Study_id")
-
-plot_fit_all_studies <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
-  geom_line(data = predicted_all, mapping = aes(x = Length, y = Weight, linetype = Gender, color = Study), size = 1) +
-  theme_bw() +
+review %>% 
+  mutate(Length = list(seq(1, 400))) %>% 
+  unnest() %>% 
+  mutate(Weight = a*(Length^b)) %>% 
+  ggplot(aes(x = Length, y = Weight, color = Study, linetype = Gender)) +
+  geom_line() +
   labs(x = "Total length (mm)", y = "Total Weight (gr)") +
+  theme_cowplot() +
   theme(text = element_text(family = "Times"),
         legend.justification=c(0,1),
-        legend.position=c(0.01, 0.99),
-        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted")) +
-  guides(color = guide_legend(title=NULL)) +
+        legend.position=c(0.01, 1),
+        legend.background = element_rect(fill = "transparent"),
+        legend.box = "horizontal",
+        legend.text = element_text(size = 10),
+        legend.title = element_text(size = 10)) +
+  guides(color = guide_legend(order = 1),
+         linetype = guide_legend(order = 0, ncol = 2)) +
   scale_color_brewer(palette = "Paired")
-
-plot_fit_all_studies
 ```
 
-```{r}
-Predicted_biomass <- fish %>% 
-  select(Length, Weight) %>% 
-  mutate(This = review$a[14] * (Length^review$b[14])/Weight, 
-         APA = review$a[1] * (Length^review$b[1])/Weight,
-         APF = review$a[2] * (Length^review$b[2])/Weight,
-         APM = review$a[3] * (Length^review$b[3])/Weight,
-         Sandel = review$a[4] * (Length^review$b[4])/Weight,
-         Chin = review$a[5] * (Length^review$b[4])/Weight,
-         Barbour = review$a[6] * (Length^review$b[6])/Weight,
-         deLeon = review$a[7] * (Length^review$b[7])/Weight,
-         FoggA = review$a[8] * (Length^review$b[8])/Weight,
-         FoggM = review$a[9] * (Length^review$b[9])/Weight,
-         FoggF = review$a[10] * (Length^review$b[10])/Weight,
-         Edwards = review$a[11] * (Length^review$b[11])/Weight,
-         Sabido = review$a[12] * (Length^review$b[12])/Weight,
-         FishBase = review$a[13] * (Length^review$b[13])/Weight) %>% 
-  gather(Study_id, Biomass_ratio, -c(Length, Weight)) %>% 
-  left_join(review, by ="Study_id")
-
-anova <- aov(Biomass_ratio ~ Study_id, Predicted_biomass)
-groups <- HSD.test(y = anova, trt = "Study_id")
-
+```{r, fig.height = 3.5, fig.cap = "\\label{fig:bio_ratio}Violin plot showing the distribution of predicted to observed biomass ratios for 16 pairs of allometric parameters.
+Red and blue circles indicate median and mean values, respectively.
+Like letters indicate values that do not differ significantly (Tukey's HSD; p < 0.05)."}
 groups$groups%<>%
@@
   left_join(groups$groups, by = "Study_id")
-```
 
-There were significant differences in expected-to-observed weight ratios estimated for each pair of parameters (F(13, 1512) = 39.28; p < 0.05).
-From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-On the other hand,barbour_2011 yielded the highest weight estimates, with a mean ($\pm$ SD) expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
-Predicted-to-observed weight ratios and groups identified by Tukey's HSD ($\alpha = 0.05$) are presented in Figure 5.
-
-```{r plot comparing predictions, fig.height = 4.5, fig.width = 6, fig.cap = ".
-Box and whiskers plot showing the distribution of predicted to observed biomass ratios for 14 pairs of allometric parameters.
-Lines indicate median values, circles indicate mean values, notches represent 95% confidence intervals arround the median, lower and upper hinges correspond to the first and third quartiles, whiskers extend to the largest and lowes values within 1.5 inter-quartile range of the hinge, small points represent outliers further away than the whiskers.
-Like letters indicate values that do not differ significantly (Tukey's HSD; p < 0.05)."}
-Predicted_biomass_plot <- Predicted_biomass %>% 
+Predicted_biomass %>% 
   mutate(Study = paste0(Study, " (", Gender, ")")) %>%
   transform(Study= reorder(Study, -Biomass_ratio)) %>%
+  rename(Sex = Gender) %>% 
   ggplot(aes(x = Study, y = Biomass_ratio)) +
-  geom_boxplot(aes(fill = Gender), outlier.size = 1, notch = T) +
-  stat_summary(geom = "point", fun.y = "mean", size = 3) +
+  geom_violin(aes(fill = Sex), alpha = 0.8) +
+  stat_summary(geom = "point", fun.y = "mean", size = 1, color = "blue") +
+  stat_summary(geom = "point", fun.y = "median", size = 1, color = "red") +
   geom_hline(yintercept = 1, linetype = "dashed") +
-  labs(y = "Biomass (Predicted / Observed)", x = "Study") +
+  labs(y = "Biomass (Predicted / Observed)", x = "") +
   coord_flip() +
-  theme_bw() +
+  theme_cowplot() +
   theme(text = element_text(family = "Times")) +
@@
   theme(text = element_text(family = "Times"),
-        legend.justification=c(1,1),
-        legend.position=c(0.9, 0.99),
-        legend.background = element_rect(fill = "transparent", size=.5, linetype="dotted")) +
-  geom_text(aes(y = 3.6, label = groups), family = "Times", fontface = "plain") +
-  scale_y_continuous(limits = c(NA, 3.6))
+        legend.justification=c(1, 1),
+        legend.position=c(-0.85, 1),
+        legend.background = element_rect(fill = "transparent"),
+        axis.text = element_text(size = 10)) +
+  geom_text(aes(y = 3.7, label = groups), family = "Times", fontface = "plain", size = 3) +
+  scale_y_continuous(limits = c(NA, 3.7))
+```
 
-Predicted_biomass_plot
-```
+\clearpage
 
@@
 
-This study provides the first pair of allometric growth parameters specific to the Central Mexican Caribbean, complementing other studies performed in Mexican waters in the Alacranes Reef \citep{aguilarperera_2016} and Xcalak National Park \citep{sabidoitza_2016}.
-By using hand nets instead of spears, we are able to sample a wider range of sizes often ignored by pole spear samples, allowing us to include smaller organisms.
-Estimating parameters by including smaller organisms ensures better estimation of weight for smaller sizes.
-This is especially important when biomass is calculated from visual census, where small organisms can be registered.
-Thus, this study also increases certainty in weight estimation of small organisms.
+\citet{fogg_2013} uses Spine-less weight
+
+\citet{toledohernndez_2014} compares young and wold growth
+
+A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided.
+This compliments existing literature for other sites in the north (*i.e.* Alacranes Reef \citep{aguilarperera_2016}) and South (Xcalak \citep{sabidoitza_2016}) of the Mexican Caribbean.
+Additionally, the study identifies regional differences in length-weight relationships.
+Here, we focus the discussion on plausible causes of these differences.
 
@@
 Yet, for larger organisms (TL > 270 mm) parameters from Costa Rica \citep{sandel_2015} and Bonaire \citep{deleon_2013} provide similar estimates to those from this study.
-Conversely, these same studies tend to estimate higher weights ---as compared to the ones reported here--- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
-When ever possible, future works should consider the use of hand nets to obtain the samples not only for studies on weight-at-length, but also diet, behavior and life history, where length can be an important factor.
+Conversely, these same studies tend to estimate higher weights --as compared to the ones reported here-- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
 
 There are evident differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
-Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic \citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016} tend to be higher than those from the Caribbean \citep{edwards_2014,chin_2016,deleon_2013,sandel_2015}, except for the ones from Xcalak National Park, Mexico \citep{sabidoitza_2016}.
+Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic tend to be higher than those from the Caribbean.
 This indicates that there are differences between lionfish across the invasion range.
-Similar regional variation exist for age-at-length relationships of lionfish \citep{fogg_2015}.
+Similar regional variation has been reported for age-at-length relationships of this species \citep{fogg_2015,pusack_2016}.
+
+Causas de las diferencias...
+
 These differences can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
@@
 At the same time, this highlights the need for more basic research that furthers our understanding of lionfish biology.
-To better manageme the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range \citep{johnson_2016}.
-
-While performing the literature review, it was often unclear if parameters were presented for eq.1 or eq.
-3.
-Sometimes, they were even mislabeled and yielded senseless results when using the suggested conversion equation.
-On other cases, parameters were said to be reported for mm-to-gr conversions, when they were actually reported as cm-to-gr conversions.
-Perhaps these minor discrepancies can be easily solved by the trained eye, but why should they exist in the first place?
-It is important that we report our information in a standard way, making it readily available for other researchers and managers.
-In this particular case, I provide my humble opinion through 5 guidelines to report allometric parameters:
-
-1.
-Be explicit in the methods section.
-What may seem obvious to you as an author ---because you have been deeply immersed throughout the process--- may not be clear to the reader.
-Specify any transformation performed on the data.
-When using log-transformations, mention the base used to transform.
-Do not assume that "data were log-transformed" means $log_{10}(X)$.
-These assumptions vary across disciplines and software and can be a source of confusion.
-For example, in biology we often assume "log-transformed" indicates the use of base 10, however in R the proper command is `log10()` and not `log()`, which uses base $e$.
-
-2.
-Use mm and gr to measure TL and TW, respectively.
-While conversion is always possible, we should aim at using standard units to report these parameters.
-If you prefer to use cm to gr conversions, that is certainly valid, but make sure to explicitly mention units when presenting the parameters.
-
-3.
-Specify the equation for which parameters are presented by including an explicit example with the parameters substituted into it, as done by some of the papers reviewed \citep{chin_2016,sandel_2015,deleon_2013,sabidoitza_2016}.
-If possible, present the relationship in their exponential (eq.
-1) and linear (eq.
-3) forms.
-
-4.
-Report standard errors and/or confidence intervals around the obtained estimates.
-Given that small changes in $a$, $c$, and $b$ can result in important changes in estimated weight, it is important that we report uncertainty around each parameter and not just general model fit and coefficient significance.
-Reporting uncertainty around parameters allows researchers and managers to include upper and lower bounds in their predictions.
-
-5.
-Make your data and code available.
-Even if this is not requited by the journal or publisher, you can use free cloud data storage services or third-party repositories to make your research accessible to others.
-Resources will always be limited and budget will rarely be enough.
-It is important that we take advantage of open science tools that promote the advancement of knowledge and foster collaboration.
-Ultimately, this promotes transparency, allows replicability of research, and advances science.
-
-This study provides a new pair of allometric growth parameters for lionfish from the central Mexican Caribbean, where they exhibit different weight-at-length.
-Furthermore, regional differences in length-weight relationships were identified, highlighting the importance of using site-specific parameters.
+To better manage the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range \citep{johnson_2016}.
 
@@
 I would like to thank thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
-I would also like to (anticipatedly) thank the editor and reviewers, who significantly improved the quality of this work.
-This research was partially funded by the "Consejo Nacional de Ciencias y Tecnología" (CONACyT) and the Latin American Fisheries Fellowship Program.
 

### 2018-02-25 Manuscript.tex
Added new version of manuscript

@@
 
-\title{Allometric growth parameters for invasive lionfish \emph{Pterois
-volitans} (Actinopterygii, Scorpaenidae) in the Western Atlantic}
+\title{Invasive lionfish present region-wide variation of allometric growth in
+the Western Atlantic}
 
@@
 length-weight relationships of the invasive lionfish through the
-invasion range and reports the length--weight relationship for lionfish
-in the Central Mexican Caribbean. A review of 13 length--weight
-relationships reported in eight peer-reviewed studies and FishBase is
-provided. These parameters were used to identify spatial variation in
-weight-at-length. For a given length, parameters from the Caribbean
-yielded lower weights than those from the Gulf of Mexico and Atlantic,
-indicating that weight-at-length is spatially variable. This highlights
-the importance of using site-specific parameters to estimate biomass
-from length observations. This study also reports a new pair of
-length-weight parameters (\(a = 3.2056 imes 10^{-6}; b = 3.235\)) for
-organisms sampled in the Central Mexican Caribbean. Findings from this
-work can aid managers and decision makers to better select length-weight
-parameters when these are not available for their region of interest.
+invasion with the addition of parameters for the Central Mexican
+Caribbean. A review of 15 length-weight relationships reported in 10
+peer-reviewed studies shows that lionfish exhibit spatial variation in
+weight-at-length. The reviewed parameters indicate that, for the same
+length, lionfish in the Caribbean have lower body mass than in the
+Atlantic or Gulf of Mexico. This highlights the importance of using
+site-specific parameters to estimate biomass from length observations.
+This study also reports a new pair of length-weight parameters
+(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
+Central Mexican Caribbean. Findings from this work can aid managers and
+decision makers to better select length-weight parameters when these are
+not available for their region of interest.
 \end{abstract}
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[section]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 At least 84\% of the marine eco-regions have reported the presence of an
-invasive species \citep{molnar_2008}. These represent a major threat to
-local biodiversity and the economic activities that depend on it, like
-tourism or fisheries \citep{bax_2003}. Invasive species may also
-threaten native species through competition \citep{davis_2003} or
-predation. By 2005, the economic cost of invasive species to the United
-States was estimated at \$120 billion per year and nearly 42\% of
-species that have been included in the Endangered or Threatened species
-list have been labeled as such due to presence of invasive species
-\citep{pimentel_2005}. This highlights the importance of understanding,
-managing, and preventing ecological invasions.
+invasive species \citep{molnar_2008}, which represent a major threat to
+local biodiversity and the economic activities that depend on it
+\citep{bax_2003}. Invasive species may threaten native species through
+predation, competition, or indirect habitat effects
+\citep{davis_2003, gurevitch_2004}. By 2005, the economic cost of
+invasive species to the United States was estimated at USD\$120 billion
+per year\citep{pimentel_2005}.
 
 Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
-in the North-Western Atlantic and the Caribbean, likely introduced
-through liberation of aquarium-kept organisms \citep{betancurr_2011}.
-They are the first marine vertebrates to establish in North Atlantic
+in the Western Atlantic and the Caribbean, likely introduced through
+liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
+the first marine vertebrates to establish in North Atlantic
 \citep{schofield_2009,schofield_2010} and Caribbean coasts
@@
 hard-bottoms \citep{muoz_2011}, and mesophotic reefs
-\citep{andradibrown_2017}. Due to its threat to local biodiversity, the
-speed of their spread, and its difficulty of management, their presence
+\citep{andradibrown_2017}. Due to their threat to local biodiversity,
+the speed of their spread, and difficulty of management, their presence
 in these waters has been labeled as a major marine invasion
@@
 case where there was no evidence that lionfish affected the density,
-richness, or composition of prey fishes). Major efforts have also been
-made to understand the possible impacts of the invasion by keeping track
-of its range through time \citep{schofield_2009,schofield_2010} and
-predicting invasion ranges under climate change scenarios
+richness, or community composition of prey fishes). Major efforts have
+been made to understand the possible impacts of the invasion by keeping
+track of its range through time \citep{schofield_2009,schofield_2010}
+and predicting invasion ranges under future climates
 \citep{grieve_2016}. By combining information from these disciplines,
@@
 consumption \citep{chin_2016}. In some cases, these have shown to
-significantly reduce -but not quite eliminate- lionfish abundances at
+significantly reduce --but not quite eliminate-- lionfish abundances at
 local scales \citep{sandel_2015,chin_2016,deleon_2013}. The rapid
@@
 persistent populations in mesophotic coral ecosystems
-\citep{andradibrown_2017} -which can contribute with recruitment to
-shallow-water populations- make of complete eradication through fishing
+\citep{andradibrown_2017} --which can contribute with recruitment to
+shallow-water populations-- make of complete eradication through fishing
 effort an unlikely solution. However, further incentivizing its
@@
 stable fishery \citep{chin_2016}, which can reduce local abundances and
-control -not eradicate- the invasion while providing alternative
-livelihoods.
+control the invasion while providing alternative livelihoods.
 
@@
 empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}. The
-latter measure changes in biomass or density
-\citep{barbour_2011,johnston_2015} in response to increased mortality
-(\emph{i.e.} lionfish removal). In this case, biomass represents the sum
-of all fish's individual weight. Total Weight (TW) can be estimated from
-Total Length (TL) observations using the allometric growth equation
-(\(TW = aTL^b\)). Parameters \(a\) and \(b\) for this equation exist for
-North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013} and
-Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican
-Caribbean \citep{sabidoitza_2016}, Little Cayman \citep{edwards_2014},
-Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} and Costa Rica
-\citep{sandel_2015}, but remain unavailable for the central Mexican
+latter approeach models changes in biomass in response to changes in
+mortality (\emph{i.e.} culling). In this case, biomass represents the
+sum of all fish's individual weight. The individual weight of an
+organism (Total Weight; TW) can be estimated from its Total Length (TL)
+using the allometric growth equation (\(TW = aTL^b\)). Parameters \(a\)
+and \(b\) for this equation exist for North Carolina
+\citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern
+Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican
+Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little
+Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire
+\citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa
+Rica \citep{sandel_2015}, but remain unavailable for the central Mexican
 Caribbean. The weight-at-length of a species can vary across regions as
@@
 (\emph{e.g.} water temperature) conditions \citep{johnson_2016}. Thus,
-when using biomass-informed models or estimating biomass from length
-observations, it is important to use site-specific parameters to obtain
-an accurate estimate. This is especially important when research
-involves identifying the total biomass available for harvest by fishers
-\citep{chin_2016} or the efficacy of lionfish removals
+when using biomass-informed models or estimating weights from length
+observations, it is important to use site-specific parameters. This is
+especially important when research involves identifying the total
+biomass available for harvest by fishers \citep{chin_2016} or the
+efficacy of lionfish removals
 \citep{barbour_2011,morris_2011,johnston_2015}.
 
-Here, I provide the first allometric growth parameters for the invasive
-lionfish in the central Mexican Caribbean region. At the same time, I
-highlight the importance of using site-specific parameters by estimating
-biomass with parameters from other regions across the invasion range and
-comparing them to observed biomass. I also provide other 13 standardized
-parameters from eight studies through the invasion range, making them
-readily accessible for future research. Finally, I discuss the way in
-which allometric parameters are reported, and call for standardization
-to facilitate their use.
-
-\clearpage
+This study reviews lionfish allometric growth throughout the invasion
+range, and provides a new pair of parameters specific to the central
+Meixcan Caribbean. The results suggest there are important
+regional-scale variations in allometric growth patterns of lionfish. The
+observed differences highlight the importance of using site-specific
+parameters, especially when informing invasion management strategies.
 
@@
 
-\emph{Area of study}
+The main objective of this work was to compare allometric growth of
+lionfish throughout the invasion range. Allometric parameters were
+retreived from scientific literature, and an additional pair of
+parameters was calculated from filed observations in the central Mexican
+Caribbean.
 
-The study took place off the coasts of Playa del Carmen, in the Mexican
-Caribbean Figure \ref{fig:map}. The region represents the northernmost
-section of the Mesoamerican Barrier Reef System \citep{ruizzarate_2004}.
-Coral reefs and mangroves are locally important habitats that represent
-important sources of income in terms of extractive (\emph{e.g.}
-recreational fishing) and non-extractive (\emph{e.g.} SCUBA diving)
-activities related to tourism, the main source of income to the local
-economy \citep{murray_2007}.
+Length-weight relationships (n = 15) identified in literature were
+obtained for North Carolina (n = 1, \citet{barbour_2011}), Northern (n =
+3, \citet{fogg_2013}) and Southern Gulf of Mexico (n = 3,
+\citet{aguilarperera_2016}), the Southern Mexican Caribbean (n = 1,
+\citet{sabidoitza_2016}), Little Cayman (n = 1,\citet{edwards_2014}),
+Jamaica (n = 1, \citet{chin_2016}), Bonaire (n = 1, \citet{deleon_2013})
+and Costa Rica (n = 1, \citet{sandel_2015}). Locations with allometric
+parameters are shown in Figure \ref{fig:map}. When available,
+information on sampling methods, gender differentiation, location, and
+depth ranges of each study was retrieved. Whenever gender was not
+specified, it was assumed that the results were presented for pooled
+genders.
 
-The reef profile has been described by \citet{ariasgonzalez_1998},
-indicating that the reef lagoon extends about 500 m from the coast,
-until the reef crest is reached. The reef becomes deeper, leading to the
-reef front often found at 700 m from the coastline and extends for an
-additional 300 m. At approximately 1000 m away from shore and 30 - 40 m
-depth, the reef leads to a drop-off. Along a perpendicular profile to
-the coast, bands of reef are interrupted by sand patches at 8 - 12 m
-deep and 16-18 m deep. Along the coast, these reefs have been reported
-to be under significant anthropogenic pressure, likely causing a shift
-in structure and function \citep{bozec_2008}.
+Parameters from the central Mexican Caribbean were obtaines from data
+collected in 10 sampling sites along the Mexican Caribbean coast in 2010
+(Table S1). Sampling locations included wall and carpet reefs at depths
+between 5.7 m and 38.1 m. All observed lionfish (n = 109) were collected
+using hand nets and numbered collection bottles. The use of hand nets
+prevented any weight loss due to bleeding and allowed a better
+representation of small sizes by eliminating gear selectivity. Organisms
+were euthanized (via pithing) and Total Length (TL; mm) and Total Weight
+(TW; gr) were recorded before freezing organisms.
+
+\clearpage
 
@@
 \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\label{fig:map}Map of the study area.
-The black inset on the left (Yucatan Peninsula) indicates the location
-where study sites are distributed. On the right, circular markers
-indicate sampling sites and the black romboid indicates location of
-Puerto Aventuras, Mexico.}
+\caption{\label{fig:unnamed-chunk-1}\label{fig:map}Locations where
+allometric growth of lionfish (\emph{Pterois spp}) have been reported.
+Sizes indicate sample size of each study, colors indicate the b
+coefficient in Eq \ref{eq:allometric}}
 \end{figure}
 
-\emph{Fish sampling}
-
-A total of 33 SCUBA immersions were performed in 10 sampling sites along
-the coast in 2010 (Fig. 1, Table I). Sampling locations included wall
-and carpet reefs at depths between 5.7 m and 38.1 m. All observed
-organisms (n = 109) were collected using hand nets and numbered
-collection bottles. The use of hand nets prevented any weight loss due
-to bleeding and allowed a better representation of small sizes, often
-ignored due to gear selectivity when spearing. Organisms were euthanized
-and frozen within 30 minutes of completing the dive and stored for
-posterior analysis. Total Length (TL; mm) and Total Weight (TW; gr) were
-recorded for all organisms.
-
-\begin{table}
-
-\caption{(\#tab:table of locations)Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.}
-\centering
-\begin{tabular}[t]{llllllr}
-\toprule
-Location & Lat. & Long. & Min. Depth & Max. Depth & Mean Depth & n\\
-\midrule
-Canones & 20.477 & -87.233 & 15.0 & 31.2 & 21.6 & 11\\
-Castillo & 20.496 & -87.220 & 12.5 & 30.5 & 27.5 & 18\\
-Cuevitas & 20.478 & -87.244 & 7.4 & 12.8 & 11.2 & 4\\
-Islas & 20.490 & -87.228 & 14.0 & 19.4 & 16.7 & 10\\
-Paamul & 20.513 & -87.192 & 9.9 & 22.7 & 15.5 & 31\\
-\addlinespace
-Paraiso & 20.484 & -87.226 & 9.4 & 38.1 & 17.7 & 16\\
-Pared & 20.502 & -87.212 & 12.1 & 21.0 & 16.3 & 12\\
-Pedregal & 20.507 & -87.204 & 14.4 & 14.9 & 14.7 & 3\\
-Santos & 20.493 & -87.222 & 5.7 & 26.6 & 16.2 & 2\\
-Tzimin-Ha & 20.393 & -87.307 & 21.2 & 24.6 & 22.9 & 2\\
-Total &  &  & 5.7 & 38.1 & 18.6 & 109\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\emph{Data analysis}
-
-The weight at length relationship between the observed variables is
-described by the allometric growth function:
+The weight at length relationship for lionfish in the central Mexican
+Caribbean was calculated with the allometric growth function:
 
@@
 estimated with an Ordinary Least Square Regression and
-heteroskedastic-robust standard error correction was performed. Both
-coefficients were tested against the null hypothesis of no change
+heteroskedastic-robust standard error correction \citep{zeileis_2004}.
+Both coefficients were tested against the null hypothesis of no change
 (\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)). Additionally, the
@@
 
-Other length-weight relationships (n = 13) were extracted from
-peer-reviewed literature. Parameters were obtained for North Carolina
-{[}n = 1,barbour\_2011{]}, Northern {[}n = 3,fogg\_2013{]} and Southern
-Gulf of Mexico {[}n = 3,aguilarperera\_2016{]}, the Southern Mexican
-Caribbean {[}n = 1,sabidoitza\_2016{]}, Little Cayman {[}n =
-1,edwards\_2014{]}, Jamaica {[}n = 1,chin\_2016{]}, Bonaire {[}n =
-1,deleon\_2013{]} and Costa Rica {[}n = 1,sandel\_2015{]} and Fishbase
-{[}n = 1,froese\_website\_2016{]} were also included. When available,
-information on sampling methods, gender differentiation, location, and
-depth ranges of each study was retrieved. Whenever gender was not
-specified, it was assumed that the results were presented for pooled
-genders.
-
-During the review process, some papers indistinctly used \(a\) to report
-either the ponderal index in eq. 1 or the y-intercept (\(c\)) in eq. 3,
-which might sometimes be overlooked. Furthermore, some studies reported
-their parameters as mm-to-gr conversions, but a rapid evaluation of such
+During the review process, some studies indistinctly used \(a\) to
+report either the ponderal index in \ref{eq:allometric} or the
+y-intercept (\(c\)) in \ref{eq:log-alo-trans}. Others reported their
+parameters as mm-to-gr conversions, but a rapid evaluation of such
 parameters indicated that they were estimated as cm-to-gr conversions.
@@
 
-Since uncertainty arround estimated relationships was not reported in
+Since uncertainty around estimated relationships was not reported in
 some of the reviewed studies, it was not possible to test for
-statistical differences between relationships. Instead, the 13
-length-weight relationships were usd to calculate expected weight for
-the organisms sampled in the Central Mexican Caribbean (n = 109).
-Expected weights were divided by the observed weights to obtain a ratio.
-Difference in mean weight ratios across studies were tested with a
-one-way Analysis of Variance (ANOVA).
+statistical differences between relationships. Instead, the 16
+length-weight relationships were used to calculate expected weight
+length observations of the organisms sampled from the Central Mexican
+Caribbean (n = 109). Expected weights were divided by the observed
+weights to obtain a ratio. Difference in mean weight ratios across
+studies were tested with a one-way Analysis of Variance (ANOVA).
 
 All hypothesis testing was performed with an \emph{a priori} confidence
-level of \(\alpha = 0.01\) in R version 3.4.0 \citep{rcore_2017}. Data
-wrangling was done with the tidyverse package \citep{tidyverse_2017}.
-Maps were created with a mix of functions from the sp \citep{sp_2017},
-rgdal \citep{rgdal_2017}, tmap \citep{tmap_2017}, and tmaptools
-\citep{tmaptools_2017} packages. Heteroskedastic-robust standard errors
-were calculated with the sandwich \citep{sandwich_2014} and lmtest
-\citep{lmtest_2002} packages. Models were manipulated with the broom
-package \citep{broom_2017}. Raw data and code used in this work is
-available at github.com/jcvdav/lionfish\_biometry.
+level of \(\alpha = 0.01\) in R version 3.4.0 \citep{rcore_2017}. Raw
+data and code used in this work is available at dryad.org.
 
@@
 
-Organism TL ranged between 34 and 310 mm and TW between 0.3 and 397.7
-gr. The smallest organism (TL = 34.00 mm) was also the lightest organism
-(TW = 0.30 gr). However, the largest organism (TL = 310.00 mm) was not
-the heaviest (TW = 303.70 gr), and the heaviest organism (TW = 397.70
-gr) was 292.00 mm in total length. Kernell density plots (Fig. 2) show
-the distribution for TL and TW for all sampled organisms. Both measures
-were positively skewed, with skewness of 0.87 for TL and 2.25 for TW.
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/histogram figures-1.pdf}
-\caption{(\#fig:histogram figures)Kernell density plots for a) Total
-length (mm) and b) Total weight (gr) for 109 lionfish sampled in the
-central Mexican Caribbean.}
-\end{figure}
-
-\emph{Length-weight relationship}
-
-The model adjusted to eq. 3 estimated the coefficient values at
-\(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
+The model adjusted to \ref{eq:log-alo-trans} estimated the coefficient
+values at \(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
 calculated from TL (mm) as a linear equation:
@@
 The intercept (\(c\)) and slope \((b)\) were significantly different
-from zero (\(t(107) = -66.17; p<0.01\) and \(t(107) = 83.24; p<0.01\),
+from zero (\(t(107) = -66.17; p<0.001\) and \(t(107) = 83.24; p<0.001\),
 respectively), rejecting the null hypothesis of no change. Additionally,
 the allometric factor (\(b\)) was significantly different from the value
-of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.01\)), indicating
-that lionfish present allometric growth. More information on model fit
-and confidence intervals for the estimated coefficients is presented in
-Table II. The relationship between Total Length and Total Weight is
-presented in Figure 3.
+of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.001\)),
+indicating that lionfish present allometric growth. More information on
+model fit and confidence intervals for the estimated coefficients is
+presented in TableS2. The relationship between Total Length and Total
+Weight is presented in Figure \ref{fig:l-w-carib}.
 
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/scatter plot-1.pdf}
-\caption{(\#fig:scatter plot)Length-weight relationship for 109 lionfish
-sampled in the central Mexican Caribbean. Points indicate samples, solid
-line indicates curve of best fit.}
-\end{figure}
-
-\begin{table}[!htbp] \centering 
-  \caption{Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
-Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.}
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-2} 
-\\[-1.8ex] & log10(TW) \\ 
-\hline \\[-1.8ex] 
- c & $-$5.494 (0.083)$^{***}$ \\ 
-  b & 3.235 (0.039)$^{***}$ \\ 
- \hline \\[-1.8ex] 
-95\% CI for c & (-5.657--5.331) \\ 
-85\% CI for b & (3.159-3.311) \\ 
-F Statistic & 6928.67*** (df = 1; 107) \\ 
-Observations & 109 \\ 
-Adjusted R$^{2}$ & 0.976 \\ 
-Residual Std. Error & 0.096 (df = 107) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\emph{Comparison of allometric parameters}
-
-From the eight peer-reviewed studies including information on growth
-parameters for \emph{P. volitans} and Fishbase
-\citep{froese_website_2016}, 13 parameters were identified (Table III).
-Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level
-and pooled parameters, while the rest presented pooled results. The
-smallest coefficient of determination was presented by \citet{chin_2016}
-with \(R^2 = 0.8715\), while \citet{sabidoitza_2016} reported the
-highest value at \(R^2 = 0.9907\). Reviewed studies presented
-information for organisms obtained at depths between 0.5 and 57 m. Two
-studies \citep{aguilarperera_2016,chin_2016} explicitly stated that
+From the 11 peer-reviewed studies including information on growth
+parameters for \emph{P. volitans} and the additional calculated for the
+central Mexican Caribbean, 16 parameters were identified (Table
+\ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies
+\citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled
+parameters, while the rest presented pooled results. The smallest
+coefficient of determination was presented by \citet{chin_2016} with
+\(R^2 = 0.8715\), while \citet{sabidoitza_2016} reported the highest
+value at \(R^2 = 0.9907\). Reviewed studies presented information for
+organisms obtained at depths between 0.5 and 57 m. Three studies
+\citep{aguilarperera_2016,chin_2016,dahl_2014} explicitly stated that
 their organisms were sampled with pole spears. Five studies
-\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016}
+\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014}
 mentioned that some of their organisms were obtained with pole spears
-(or other type of harpoon). A single study \citep{deleon_2013} did not
-specify how organisms were sampled.
+(or other type of harpoon), but also hand-held nets or fish traps. Two
+studies \citep{deleon_2013,darling_2011} did not specify how organisms
+were sampled.
 
@@
 parameters from models for pooled genders with a mean \(\pm\) standard
-deviation value of \(b = 3.09 \pm 0.22\). In the case of the ponderal
-index (\(a\)) and its \(log_{10}\) transformed parameter (\(c\)), values
-were higher for parameters for pooled genders. Figure 4 shows the
-predicted weights for organisms within the size range of these study
-using the 14 parameters previously described.
+deviation value of \(b = 3.13 \pm 0.22\). In the case of the ponderal
+index (\(a\)) and its \(log_{10}\) transformation (\(c\)), values were
+higher for parameters for pooled genders. Figure \ref{fig:all_allo}
+shows the weight-at-length relationships with parameters from all
+studies.
+
+There were significant differences in expected-to-observed weight ratios
+estimated for each pair of parameters (F(15, 1728) = 38.26; p
+\textless{} 0.001). From all allometric parameters reviewed, those of
+\citet{edwards_2014} provided the lowest weight estimates, with an
+expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
+SD). On the other hand,\citet{barbour_2011} yielded the highest weight
+estimates, with a mean (\(\pm\) SD) expected-to-observed weight ratio of
+1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
+identified by Tukey's HSD (\(\alpha = 0.05\)) are presented in Figure
+\ref{fig:bio_ratio}.
+
+\clearpage
 
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/review plots-1.pdf}
-\caption{(\#fig:review plots)Length-weight relationships (n = 14) for
-eight studies, this study, and Fishbase. Colors indicate studies from
-which the parameters were extracted. Solid lines indicate that the fit
-was performed for males and females pooled together. Dotted lines
-indicate that the regression was performed on females, and dashed lines
-indicate it was performed for males.}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
+\caption{\label{fig:unnamed-chunk-4}\label{fig:l-w-carib}Length-weight
+relationship for 109 lionfish sampled in the Central Mexican Caribbean.
+Points indicate samples, solid line indicates curve of best fit (See
+Table S1).}
 \end{figure}
 
-There were significant differences in expected-to-observed weight ratios
-estimated for each pair of parameters (F(13, 1512) = 39.28; p
-\textless{} 0.05). From all allometric parameters reviewed, those of
-\citet{edwards_2014} provided the lowest weight estimates, with an
-expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
-SD). On the other hand,barbour\_2011 yielded the highest weight
-estimates, with a mean (\(\pm\) SD) expected-to-observed weight ratio of
-1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
-identified by Tukey's HSD (\(\alpha = 0.05\)) are presented in Figure 5.
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, a = scaling parameter for eq.
+1, c = y-intercept for eq.
+3, b = exponent or slope for eq.
+1 or eq.
+3, respectively.
+The $R^2$ column indicates reported model fit.}
+\centering
+\begin{tabular}[t]{lllrrll}
+\toprule
+Region & Sex & n & a & b & R2 & Reference\\
+\midrule
+Alacranes Reef, Mexico & B & 472 & 2.90e-06 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+Alacranes Reef, Mexico & F & 67 & 1.20e-06 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+Alacranes Reef, Mexico & M & 59 & 4.20e-06 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+Bahamas & B & - & 2.50e-06 & 3.29 & - & Darling et al., 2011\\
+Bonaire & B & 1450 & 2.28e-05 & 2.89 & 0.96 & de Leon et al., 2013\\
+\addlinespace
+Costa Rica & B & 458 & 3.64e-05 & 2.81 & - & Sandel et al., 2015\\
+Discovery Bay, Jamaica & B & 419 & 2.75e-05 & 2.85 & 0.8715 & Chin et al 2016\\
+Little Cayman & B & 1887 & 3.00e-06 & 3.24 & 0.97 & Edwards et al., 2014\\
+North Carolina & B & 774 & 2.89e-05 & 2.89 & - & Brbour et al 2011\\
+Northern Gulf of Mexico & B & 934 & 2.10e-06 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
+\addlinespace
+Northern Gulf of Mexico & B & 582 & 1.40e-06 & 3.43 & 0.99 & Fogg et al., 2013\\
+Northern Gulf of Mexico & M & 119 & 2.70e-06 & 3.31 & 0.97 & Fogg et al., 2013\\
+Northern Gulf of Mexico & F & 115 & 6.80e-06 & 3.14 & 0.94 & Fogg et al., 2013\\
+Puerto Aventuras, Mexico & B & 109 & 3.20e-06 & 3.23 & 0.9766 & This study\\
+Puerto Rico & B & 227 & 8.00e-06 & 3.11 & 0.958 & Toledo-Hernández et al., 2014\\
+Xcalak, Mexico & B & 2143 & 5.20e-06 & 3.18 & 0.9907 & Sabido-Itza et al., 2016\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\clearpage
 
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/plot comparing predictions-1.pdf}
-\caption{(\#fig:plot comparing predictions). Box and whiskers plot
-showing the distribution of predicted to observed biomass ratios for 14
-pairs of allometric parameters. Lines indicate median values, circles
-indicate mean values, notches represent 95\% confidence intervals
-arround the median, lower and upper hinges correspond to the first and
-third quartiles, whiskers extend to the largest and lowes values within
-1.5 inter-quartile range of the hinge, small points represent outliers
-further away than the whiskers. Like letters indicate values that do not
-differ significantly (Tukey's HSD; p \textless{} 0.05).}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{\label{fig:unnamed-chunk-6}\label{fig:all_allo}Length-weight
+relationships (n = 16) for eight studies, this study, and Fishbase.
+Colors indicate studies from which the parameters were extracted. Solid
+lines indicate that the fit was performed for males and females pooled
+together. Dotted lines indicate that the regression was performed on
+females, and dashed lines indicate it was performed for males.}
 \end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\label{fig:unnamed-chunk-7}\label{fig:bio_ratio}Violin plot showing
+the distribution of predicted to observed biomass ratios for 16 pairs of
+allometric parameters. Red and blue circles indicate median and mean
+values, respectively. Like letters indicate values that do not differ
+significantly (Tukey's HSD; p \textless{} 0.05).}
+\end{figure}
+
+\clearpage
 
@@
 
-This study provides the first pair of allometric growth parameters
-specific to the Central Mexican Caribbean, complementing other studies
-performed in Mexican waters in the Alacranes Reef
-\citep{aguilarperera_2016} and Xcalak National Park
-\citep{sabidoitza_2016}. By using hand nets instead of spears, we are
-able to sample a wider range of sizes often ignored by pole spear
-samples, allowing us to include smaller organisms. Estimating parameters
-by including smaller organisms ensures better estimation of weight for
-smaller sizes. This is especially important when biomass is calculated
-from visual census, where small organisms can be registered. Thus, this
-study also increases certainty in weight estimation of small organisms.
+\citet{fogg_2013} uses Spine-less weight
+
+\citet{toledohernndez_2014} compares young and wold growth
+
+A new pair of allometric growth parameters for lionfish in the central
+Mexican Caribbean are provided. This compliments existing literature for
+other sites in the north (\emph{i.e.} Alacranes Reef
+\citep{aguilarperera_2016}) and South (Xcalak \citep{sabidoitza_2016})
+of the Mexican Caribbean. Additionally, the study identifies regional
+differences in length-weight relationships. Here, we focus the
+discussion on plausible causes of these differences.
 
@@
 \citep{deleon_2013} provide similar estimates to those from this study.
-Conversely, these same studies tend to estimate higher weights ---as
-compared to the ones reported here--- for smaller organisms, likely due
+Conversely, these same studies tend to estimate higher weights --as
+compared to the ones reported here-- for smaller organisms, likely due
 to the lack of small organisms in the samples used to estimate their
-parameters. When ever possible, future works should consider the use of
-hand nets to obtain the samples not only for studies on
-weight-at-length, but also diet, behavior and life history, where length
-can be an important factor.
+parameters.
 
@@
 estimates with parameters from the Gulf of Mexico and North-Western
-Atlantic
-\citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016} tend
-to be higher than those from the Caribbean
-\citep{edwards_2014,chin_2016,deleon_2013,sandel_2015}, except for the
-ones from Xcalak National Park, Mexico \citep{sabidoitza_2016}. This
-indicates that there are differences between lionfish across the
-invasion range. Similar regional variation exist for age-at-length
-relationships of lionfish \citep{fogg_2015}. These differences can have
-major implications in management, especially when estimating biomass
-available for harvest or predicting effects on local ecosystems, or
-evaluating the effectiveness of removal programs. Using site-specific
-values provides a more accurate estimate of fish biomass. Future
-research should try to use, to the extent possible, parameters
-calculated for their region, or use different parameters to provide
-upper and lower bounds in their results. At the same time, this
+Atlantic tend to be higher than those from the Caribbean. This indicates
+that there are differences between lionfish across the invasion range.
+Similar regional variation has been reported for age-at-length
+relationships of this species \citep{fogg_2015,pusack_2016}.
+
+Causas de las diferencias\ldots{}
+
+These differences can have major implications in management, especially
+when estimating biomass available for harvest or predicting effects on
+local ecosystems, or evaluating the effectiveness of removal programs.
+Using site-specific values provides a more accurate estimate of fish
+biomass. Future research should try to use, to the extent possible,
+parameters calculated for their region, or use different parameters to
+provide upper and lower bounds in their results. At the same time, this
 highlights the need for more basic research that furthers our
-understanding of lionfish biology. To better manageme the invasion, we
+understanding of lionfish biology. To better manage the invasion, we
 must perform research that can describe biologically important
@@
 \citep{johnson_2016}.
-
-While performing the literature review, it was often unclear if
-parameters were presented for eq.1 or eq. 3. Sometimes, they were even
-mislabeled and yielded senseless results when using the suggested
-conversion equation. On other cases, parameters were said to be reported
-for mm-to-gr conversions, when they were actually reported as cm-to-gr
-conversions. Perhaps these minor discrepancies can be easily solved by
-the trained eye, but why should they exist in the first place? It is
-important that we report our information in a standard way, making it
-readily available for other researchers and managers. In this particular
-case, I provide my humble opinion through 5 guidelines to report
-allometric parameters:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  Be explicit in the methods section. What may seem obvious to you as an
-  author ---because you have been deeply immersed throughout the
-  process--- may not be clear to the reader. Specify any transformation
-  performed on the data. When using log-transformations, mention the
-  base used to transform. Do not assume that ``data were
-  log-transformed'' means \(log_{10}(X)\). These assumptions vary across
-  disciplines and software and can be a source of confusion. For
-  example, in biology we often assume ``log-transformed'' indicates the
-  use of base 10, however in R the proper command is \texttt{log10()}
-  and not \texttt{log()}, which uses base \(e\).
-\item
-  Use mm and gr to measure TL and TW, respectively. While conversion is
-  always possible, we should aim at using standard units to report these
-  parameters. If you prefer to use cm to gr conversions, that is
-  certainly valid, but make sure to explicitly mention units when
-  presenting the parameters.
-\item
-  Specify the equation for which parameters are presented by including
-  an explicit example with the parameters substituted into it, as done
-  by some of the papers reviewed
-  \citep{chin_2016,sandel_2015,deleon_2013,sabidoitza_2016}. If
-  possible, present the relationship in their exponential (eq. 1) and
-  linear (eq. 3) forms.
-\item
-  Report standard errors and/or confidence intervals around the obtained
-  estimates. Given that small changes in \(a\), \(c\), and \(b\) can
-  result in important changes in estimated weight, it is important that
-  we report uncertainty around each parameter and not just general model
-  fit and coefficient significance. Reporting uncertainty around
-  parameters allows researchers and managers to include upper and lower
-  bounds in their predictions.
-\item
-  Make your data and code available. Even if this is not requited by the
-  journal or publisher, you can use free cloud data storage services or
-  third-party repositories to make your research accessible to others.
-  Resources will always be limited and budget will rarely be enough. It
-  is important that we take advantage of open science tools that promote
-  the advancement of knowledge and foster collaboration. Ultimately,
-  this promotes transparency, allows replicability of research, and
-  advances science.
-\end{enumerate}
-
-This study provides a new pair of allometric growth parameters for
-lionfish from the central Mexican Caribbean, where they exhibit
-different weight-at-length. Furthermore, regional differences in
-length-weight relationships were identified, highlighting the importance
-of using site-specific parameters.
 
@@
 Dive Aventuras as well as Guillermo Lotz-Cador who provided help to
-collect samples. I would also like to (anticipatedly) thank the editor
-and reviewers, who significantly improved the quality of this work. This
-research was partially funded by the ``Consejo Nacional de Ciencias y
-Tecnología'' (CONACyT) and the Latin American Fisheries Fellowship
-Program.
+collect samples.
 

### 2018-03-20 docs/Manuscript.Rmd
reorganized the repository

--- 2018-02-25 Manuscript.Rmd
@@
 ```{r load fish data, include = F}
-fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
+fish <- read_csv(here::here("data", "lionfish_data.csv"), col_types = cols()) %>%
   group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
@@
 
-review <- read.csv("biometric_review.csv", stringsAsFactors = F, strip.white = T, blank.lines.skip = T) %>% 
+review <- read.csv(here::here("data", "biometric_review.csv"), stringsAsFactors = F, strip.white = T, blank.lines.skip = T) %>% 
   mutate(c = log10(a),
@@
 # Load coastline for Mexico and World
-coastline <- ("./Spatial/coastline_mx.rds")
 
@@
 All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 \citep{rcore_2017}. Raw data and code used in this work is available at dryad.org.
-
-```{r, include = F}
-length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
-  geom_density(fill = "gray", alpha = 0.5) +
-  theme_cowplot() +
-  labs(x = "Total Length (mm)", y = "Density") +
-  theme(text = element_text(family = "Times"))
-
-weight_hist <- ggplot(data = fish, mapping = aes(x = Weight)) +
-  geom_density(fill = "gray", alpha = 0.5) +
-  theme_cowplot() +
-  labs(x = "Total weight (gr)", y = "Density") +
-  theme(text = element_text(family = "Times"))
-
-# Density distributions for A) Total length (mm) and B) Total weight (gr) for 109 lionfish sampled in the Central Mexican Caribbean.
-FigS1 <- cowplot::plot_grid(length_hist, weight_hist, ncol = 1, labels = "AUTO")
-ggsave(FigS1, file="FigS1.png", width = 5.5, height = 6, dpi = 600)
-```
 
@@
 \bibliography{references}
+
+# Supplementary materials
+
+## Figure S1
+
+```{r, include = F}
+length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
+  geom_density(fill = "gray", alpha = 0.5) +
+  theme_cowplot() +
+  labs(x = "Total Length (mm)", y = "Density") +
+  theme(text = element_text(family = "Times"))
+
+weight_hist <- ggplot(data = fish, mapping = aes(x = Weight)) +
+  geom_density(fill = "gray", alpha = 0.5) +
+  theme_cowplot() +
+  labs(x = "Total weight (gr)", y = "Density") +
+  theme(text = element_text(family = "Times"))
+
+# Density distributions for A) Total length (mm) and B) Total weight (gr) for 109 lionfish sampled in the Central Mexican Caribbean.
+FigS1 <- cowplot::plot_grid(length_hist, weight_hist, ncol = 1, labels = "AUTO")
+ggsave(FigS1, file="supplementary/FigS1.png", width = 5.5, height = 6, dpi = 600)
+```

### 2018-03-20 docs/Manuscript.tex
reorganized the repository

--- 2018-02-25 Manuscript.tex
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\label{fig:l-w-carib}Length-weight
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{\label{fig:unnamed-chunk-3}\label{fig:l-w-carib}Length-weight
 relationship for 109 lionfish sampled in the Central Mexican Caribbean.
@@
 
-\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+\caption{\label{tab:unnamed-chunk-4}\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:unnamed-chunk-6}\label{fig:all_allo}Length-weight
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
+\caption{\label{fig:unnamed-chunk-5}\label{fig:all_allo}Length-weight
 relationships (n = 16) for eight studies, this study, and Fishbase.
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:unnamed-chunk-7}\label{fig:bio_ratio}Violin plot showing
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{\label{fig:unnamed-chunk-6}\label{fig:bio_ratio}Violin plot showing
 the distribution of predicted to observed biomass ratios for 16 pairs of
@@
 
+\section{Supplementary materials}\label{supplementary-materials}
+
+\subsection{Figure S1}\label{figure-s1}
+
 \end{document}

### 2018-03-20 docs/peerj_template.tex
reorganized the repository

--- 2018-02-25 Manuscript.tex
@@
 
-\title{Invasive lionfish present region-wide variation of allometric growth in
-the Western Atlantic}
+\title{$title$}
 
-\author[1]{Juan Carlos Villaseñor-Derbez}
-\affil[1]{Bren School of Environmental Sciences and Management, University of
-California Santa Barbara, Santa Barbara, California, U.S.}
-\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@bren.ucsb.edu}
+\author[1]{$author$}
+\affil[1]{$institution$}
+\corrauthor[1]{$author$}{jvillasenor@bren.ucsb.edu}
 
@@
 \begin{abstract}
-Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
-North-Western Atlantic and the Caribbean. In order to better manage the
-invasion, inform lionfish removal programs, and estimate biomass
-available for harvest, we must be able to accurately estimate their
-total biomass, frequently from length observations. This work compares
-length-weight relationships of the invasive lionfish through the
-invasion with the addition of parameters for the Central Mexican
-Caribbean. A review of 15 length-weight relationships reported in 10
-peer-reviewed studies shows that lionfish exhibit spatial variation in
-weight-at-length. The reviewed parameters indicate that, for the same
-length, lionfish in the Caribbean have lower body mass than in the
-Atlantic or Gulf of Mexico. This highlights the importance of using
-site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters
-(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
-Central Mexican Caribbean. Findings from this work can aid managers and
-decision makers to better select length-weight parameters when these are
-not available for their region of interest.
+$abstract$
 \end{abstract}
@@
 
-\section{Introduction}\label{introduction}
-
-At least 84\% of the marine eco-regions have reported the presence of an
-invasive species \citep{molnar_2008}, which represent a major threat to
-local biodiversity and the economic activities that depend on it
-\citep{bax_2003}. Invasive species may threaten native species through
-predation, competition, or indirect habitat effects
-\citep{davis_2003, gurevitch_2004}. By 2005, the economic cost of
-invasive species to the United States was estimated at USD\$120 billion
-per year\citep{pimentel_2005}.
-
-Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
-in the Western Atlantic and the Caribbean, likely introduced through
-liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
-the first marine vertebrates to establish in North Atlantic
-\citep{schofield_2009,schofield_2010} and Caribbean coasts
-\citep{sabidoitza_2016}. Lionfish have been widely reported in coral
-reefs \citep{aguilarperera_2010}, but also in other habitats such as
-estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with
-hard-bottoms \citep{muoz_2011}, and mesophotic reefs
-\citep{andradibrown_2017}. Due to their threat to local biodiversity,
-the speed of their spread, and difficulty of management, their presence
-in these waters has been labeled as a major marine invasion
-\citep{hixon_2016}.
-
-A significant amount of research has been done to describe lionfish
-feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas
-\citep{morris_2009,cote_2013}, Northern Gulf of Mexico
-\citep{dahl_2014}, Mexican Caribbean
-\citep{valdezmoreno_2012,villaseorderbez_2014}, Belize
-\citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}. Their
-feeding behavior and high consumption rates can reduce recruitment
-\citep{albins_2008} and population sizes \citep{green_2012} of native
-reef-fish species, and further the endangerment of critically endangered
-reef fish \citep{rocha_2015}. (However, see \citet{hackerott_2017} for a
-case where there was no evidence that lionfish affected the density,
-richness, or community composition of prey fishes). Major efforts have
-been made to understand the possible impacts of the invasion by keeping
-track of its range through time \citep{schofield_2009,schofield_2010}
-and predicting invasion ranges under future climates
-\citep{grieve_2016}. By combining information from these disciplines,
-researchers have been able to predict the trophic impacts of lionfish
-\citep{ariasgonzalez_2011}, which can then be translated into
-ecosystem-level and economic impacts.
-
-Seeking to reduce lionfish densities, governments and non-profit
-organizations have promoted removal programs and incentivized its
-consumption \citep{chin_2016}. In some cases, these have shown to
-significantly reduce --but not quite eliminate-- lionfish abundances at
-local scales \citep{sandel_2015,chin_2016,deleon_2013}. The rapid
-recovery rates exhibited by lionfish \citep{barbour_2011} and the
-persistent populations in mesophotic coral ecosystems
-\citep{andradibrown_2017} --which can contribute with recruitment to
-shallow-water populations-- make of complete eradication through fishing
-effort an unlikely solution. However, further incentivizing its
-consumption might create a demand big enough to promote and sustain a
-stable fishery \citep{chin_2016}, which can reduce local abundances and
-control the invasion while providing alternative livelihoods.
-
-The feasibility of lionfish removal programs has been extensively
-evaluated through field
-observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and
-empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}. The
-latter approeach models changes in biomass in response to changes in
-mortality (\emph{i.e.} culling). In this case, biomass represents the
-sum of all fish's individual weight. The individual weight of an
-organism (Total Weight; TW) can be estimated from its Total Length (TL)
-using the allometric growth equation (\(TW = aTL^b\)). Parameters \(a\)
-and \(b\) for this equation exist for North Carolina
-\citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern
-Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican
-Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little
-Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire
-\citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa
-Rica \citep{sandel_2015}, but remain unavailable for the central Mexican
-Caribbean. The weight-at-length of a species can vary across regions as
-a response to biotic (\emph{e.g.} local food availability) and abiotic
-(\emph{e.g.} water temperature) conditions \citep{johnson_2016}. Thus,
-when using biomass-informed models or estimating weights from length
-observations, it is important to use site-specific parameters. This is
-especially important when research involves identifying the total
-biomass available for harvest by fishers \citep{chin_2016} or the
-efficacy of lionfish removals
-\citep{barbour_2011,morris_2011,johnston_2015}.
-
-This study reviews lionfish allometric growth throughout the invasion
-range, and provides a new pair of parameters specific to the central
-Meixcan Caribbean. The results suggest there are important
-regional-scale variations in allometric growth patterns of lionfish. The
-observed differences highlight the importance of using site-specific
-parameters, especially when informing invasion management strategies.
-
-\section{Materials and Methods}\label{materials-and-methods}
-
-The main objective of this work was to compare allometric growth of
-lionfish throughout the invasion range. Allometric parameters were
-retreived from scientific literature, and an additional pair of
-parameters was calculated from filed observations in the central Mexican
-Caribbean.
-
-Length-weight relationships (n = 15) identified in literature were
-obtained for North Carolina (n = 1, \citet{barbour_2011}), Northern (n =
-3, \citet{fogg_2013}) and Southern Gulf of Mexico (n = 3,
-\citet{aguilarperera_2016}), the Southern Mexican Caribbean (n = 1,
-\citet{sabidoitza_2016}), Little Cayman (n = 1,\citet{edwards_2014}),
-Jamaica (n = 1, \citet{chin_2016}), Bonaire (n = 1, \citet{deleon_2013})
-and Costa Rica (n = 1, \citet{sandel_2015}). Locations with allometric
-parameters are shown in Figure \ref{fig:map}. When available,
-information on sampling methods, gender differentiation, location, and
-depth ranges of each study was retrieved. Whenever gender was not
-specified, it was assumed that the results were presented for pooled
-genders.
-
-Parameters from the central Mexican Caribbean were obtaines from data
-collected in 10 sampling sites along the Mexican Caribbean coast in 2010
-(Table S1). Sampling locations included wall and carpet reefs at depths
-between 5.7 m and 38.1 m. All observed lionfish (n = 109) were collected
-using hand nets and numbered collection bottles. The use of hand nets
-prevented any weight loss due to bleeding and allowed a better
-representation of small sizes by eliminating gear selectivity. Organisms
-were euthanized (via pithing) and Total Length (TL; mm) and Total Weight
-(TW; gr) were recorded before freezing organisms.
-
-\clearpage
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\label{fig:map}Locations where
-allometric growth of lionfish (\emph{Pterois spp}) have been reported.
-Sizes indicate sample size of each study, colors indicate the b
-coefficient in Eq \ref{eq:allometric}}
-\end{figure}
-
-The weight at length relationship for lionfish in the central Mexican
-Caribbean was calculated with the allometric growth function:
-
-\begin{equation}
-\label{eq:allometric}
-TW = aTL^b
-\end{equation}
-
-Where \(TW\) is the Total Weight (gr), \(TL\) is the Total Length (mm),
-\(a\) is the ponderal index and \(b\) is the scaling exponent or
-allometric parameter. When \(b = 3\), it is said that the organism
-exhibits a perfect isometric growth. The dependent and independent
-variables were transformed via base-10 logarithms, thus the equation
-becomes:
-
-\begin{equation}
-\label{eq:log-alo}
-log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)
-\end{equation}
-
-This can be simplified and re-written as:
-
-\begin{equation}
-\label{eq:log-alo-trans}
-Y = mX + c
-\end{equation}
-
-Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), \(m = b\), and
-\(c = log_{10}(a)\). Since \(b = m\), we will only use \(b\) throughout
-the paper for simplicity. The coefficients (\(c\) and \(b\)) were
-estimated with an Ordinary Least Square Regression and
-heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-Both coefficients were tested against the null hypothesis of no change
-(\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)). Additionally, the
-allometric parameter was tested against the null hypothesis of isometric
-growth (\(H_0: b = 3\)). Coefficients were tested with a two-tailed
-Student's t-test. The significance of the regression was corroborated
-with an F-test.
-
-During the review process, some studies indistinctly used \(a\) to
-report either the ponderal index in \ref{eq:allometric} or the
-y-intercept (\(c\)) in \ref{eq:log-alo-trans}. Others reported their
-parameters as mm-to-gr conversions, but a rapid evaluation of such
-parameters indicated that they were estimated as cm-to-gr conversions.
-Here, all parameters are reported as TL(mm) to TW(gr) conversions. When
-required, values from other studies were transformed for consistency.
-
-Since uncertainty around estimated relationships was not reported in
-some of the reviewed studies, it was not possible to test for
-statistical differences between relationships. Instead, the 16
-length-weight relationships were used to calculate expected weight
-length observations of the organisms sampled from the Central Mexican
-Caribbean (n = 109). Expected weights were divided by the observed
-weights to obtain a ratio. Difference in mean weight ratios across
-studies were tested with a one-way Analysis of Variance (ANOVA).
-
-All hypothesis testing was performed with an \emph{a priori} confidence
-level of \(\alpha = 0.01\) in R version 3.4.0 \citep{rcore_2017}. Raw
-data and code used in this work is available at dryad.org.
-
-\section{Results}\label{results}
-
-The model adjusted to \ref{eq:log-alo-trans} estimated the coefficient
-values at \(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
-calculated from TL (mm) as a linear equation:
-\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
-exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
-The intercept (\(c\)) and slope \((b)\) were significantly different
-from zero (\(t(107) = -66.17; p<0.001\) and \(t(107) = 83.24; p<0.001\),
-respectively), rejecting the null hypothesis of no change. Additionally,
-the allometric factor (\(b\)) was significantly different from the value
-of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.001\)),
-indicating that lionfish present allometric growth. More information on
-model fit and confidence intervals for the estimated coefficients is
-presented in TableS2. The relationship between Total Length and Total
-Weight is presented in Figure \ref{fig:l-w-carib}.
-
-From the 11 peer-reviewed studies including information on growth
-parameters for \emph{P. volitans} and the additional calculated for the
-central Mexican Caribbean, 16 parameters were identified (Table
-\ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies
-\citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled
-parameters, while the rest presented pooled results. The smallest
-coefficient of determination was presented by \citet{chin_2016} with
-\(R^2 = 0.8715\), while \citet{sabidoitza_2016} reported the highest
-value at \(R^2 = 0.9907\). Reviewed studies presented information for
-organisms obtained at depths between 0.5 and 57 m. Three studies
-\citep{aguilarperera_2016,chin_2016,dahl_2014} explicitly stated that
-their organisms were sampled with pole spears. Five studies
-\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014}
-mentioned that some of their organisms were obtained with pole spears
-(or other type of harpoon), but also hand-held nets or fish traps. Two
-studies \citep{deleon_2013,darling_2011} did not specify how organisms
-were sampled.
-
-Parameters from models fit to males or females exclusively tend to have
-a higher steepness (\emph{i.e.} higher allometric parameter), with mean
-\(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
-\(b = 3.31 \pm 0.23\) for males and females respectively, compared to
-parameters from models for pooled genders with a mean \(\pm\) standard
-deviation value of \(b = 3.13 \pm 0.22\). In the case of the ponderal
-index (\(a\)) and its \(log_{10}\) transformation (\(c\)), values were
-higher for parameters for pooled genders. Figure \ref{fig:all_allo}
-shows the weight-at-length relationships with parameters from all
-studies.
-
-There were significant differences in expected-to-observed weight ratios
-estimated for each pair of parameters (F(15, 1728) = 38.26; p
-\textless{} 0.001). From all allometric parameters reviewed, those of
-\citet{edwards_2014} provided the lowest weight estimates, with an
-expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
-SD). On the other hand,\citet{barbour_2011} yielded the highest weight
-estimates, with a mean (\(\pm\) SD) expected-to-observed weight ratio of
-1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
-identified by Tukey's HSD (\(\alpha = 0.05\)) are presented in Figure
-\ref{fig:bio_ratio}.
-
-\clearpage
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:unnamed-chunk-4}\label{fig:l-w-carib}Length-weight
-relationship for 109 lionfish sampled in the Central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit (See
-Table S1).}
-\end{figure}
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, a = scaling parameter for eq.
-1, c = y-intercept for eq.
-3, b = exponent or slope for eq.
-1 or eq.
-3, respectively.
-The $R^2$ column indicates reported model fit.}
-\centering
-\begin{tabular}[t]{lllrrll}
-\toprule
-Region & Sex & n & a & b & R2 & Reference\\
-\midrule
-Alacranes Reef, Mexico & B & 472 & 2.90e-06 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-Alacranes Reef, Mexico & F & 67 & 1.20e-06 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-Alacranes Reef, Mexico & M & 59 & 4.20e-06 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-Bahamas & B & - & 2.50e-06 & 3.29 & - & Darling et al., 2011\\
-Bonaire & B & 1450 & 2.28e-05 & 2.89 & 0.96 & de Leon et al., 2013\\
-\addlinespace
-Costa Rica & B & 458 & 3.64e-05 & 2.81 & - & Sandel et al., 2015\\
-Discovery Bay, Jamaica & B & 419 & 2.75e-05 & 2.85 & 0.8715 & Chin et al 2016\\
-Little Cayman & B & 1887 & 3.00e-06 & 3.24 & 0.97 & Edwards et al., 2014\\
-North Carolina & B & 774 & 2.89e-05 & 2.89 & - & Brbour et al 2011\\
-Northern Gulf of Mexico & B & 934 & 2.10e-06 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
-\addlinespace
-Northern Gulf of Mexico & B & 582 & 1.40e-06 & 3.43 & 0.99 & Fogg et al., 2013\\
-Northern Gulf of Mexico & M & 119 & 2.70e-06 & 3.31 & 0.97 & Fogg et al., 2013\\
-Northern Gulf of Mexico & F & 115 & 6.80e-06 & 3.14 & 0.94 & Fogg et al., 2013\\
-Puerto Aventuras, Mexico & B & 109 & 3.20e-06 & 3.23 & 0.9766 & This study\\
-Puerto Rico & B & 227 & 8.00e-06 & 3.11 & 0.958 & Toledo-Hernández et al., 2014\\
-Xcalak, Mexico & B & 2143 & 5.20e-06 & 3.18 & 0.9907 & Sabido-Itza et al., 2016\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\clearpage
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:unnamed-chunk-6}\label{fig:all_allo}Length-weight
-relationships (n = 16) for eight studies, this study, and Fishbase.
-Colors indicate studies from which the parameters were extracted. Solid
-lines indicate that the fit was performed for males and females pooled
-together. Dotted lines indicate that the regression was performed on
-females, and dashed lines indicate it was performed for males.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:unnamed-chunk-7}\label{fig:bio_ratio}Violin plot showing
-the distribution of predicted to observed biomass ratios for 16 pairs of
-allometric parameters. Red and blue circles indicate median and mean
-values, respectively. Like letters indicate values that do not differ
-significantly (Tukey's HSD; p \textless{} 0.05).}
-\end{figure}
-
-\clearpage
-
-\section{Discussion}\label{discussion}
-
-\citet{fogg_2013} uses Spine-less weight
-
-\citet{toledohernndez_2014} compares young and wold growth
-
-A new pair of allometric growth parameters for lionfish in the central
-Mexican Caribbean are provided. This compliments existing literature for
-other sites in the north (\emph{i.e.} Alacranes Reef
-\citep{aguilarperera_2016}) and South (Xcalak \citep{sabidoitza_2016})
-of the Mexican Caribbean. Additionally, the study identifies regional
-differences in length-weight relationships. Here, we focus the
-discussion on plausible causes of these differences.
-
-The length-weight coefficients estimated in this study were within the
-range identified by studies in other regions
-\citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016,edwards_2014,chin_2016,deleon_2013,sandel_2015}.
-However, the ones presented here provide lower weight estimates for a
-same length. Until about TL = 200 mm, there are no appreciable
-differences between the parameters for organisms from the Mexican
-Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica
-\citep{chin_2016}. Yet, for larger organisms (TL \textgreater{} 270 mm)
-parameters from Costa Rica \citep{sandel_2015} and Bonaire
-\citep{deleon_2013} provide similar estimates to those from this study.
-Conversely, these same studies tend to estimate higher weights --as
-compared to the ones reported here-- for smaller organisms, likely due
-to the lack of small organisms in the samples used to estimate their
-parameters.
-
-There are evident differences in weight-at-length between organisms from
-the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight
-estimates with parameters from the Gulf of Mexico and North-Western
-Atlantic tend to be higher than those from the Caribbean. This indicates
-that there are differences between lionfish across the invasion range.
-Similar regional variation has been reported for age-at-length
-relationships of this species \citep{fogg_2015,pusack_2016}.
-
-Causas de las diferencias\ldots{}
-
-These differences can have major implications in management, especially
-when estimating biomass available for harvest or predicting effects on
-local ecosystems, or evaluating the effectiveness of removal programs.
-Using site-specific values provides a more accurate estimate of fish
-biomass. Future research should try to use, to the extent possible,
-parameters calculated for their region, or use different parameters to
-provide upper and lower bounds in their results. At the same time, this
-highlights the need for more basic research that furthers our
-understanding of lionfish biology. To better manage the invasion, we
-must perform research that can describe biologically important
-information of lionfish throughout its invasion range
-\citep{johnson_2016}.
-
-\section{Aknowledgements}\label{aknowledgements}
-
-I would like to thank thank Nils Van Der Haar and Michael Doodey from
-Dive Aventuras as well as Guillermo Lotz-Cador who provided help to
-collect samples.
-
-\bibliography{references}
+$body$
 

### 2018-03-20 docs/supplementary/S1Table.Rmd
reorganized the repository

---
title: "Supplementary Table S1"
author: "Juan Carlos Villaseñor-Derbez"
output: pdf_document
---

Coordinates, minimum, maximum and mean depth (m), and number of samples for each location.

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 5.5)

options(knitr.table.format = "latex")

windowsFonts(Times=windowsFont("TT Times New Roman"))
```

```{r load packages}
suppressPackageStartupMessages({
  library(stargazer)
  library(sandwich)
  library(lmtest)
  library(broom)
  library(knitr)
  library(tidyverse)
})
```

```{r}
fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
  summarize(Length = 10*mean(TotalLength_cm),
            Weight = mean(TotalWeigth_gr),
            Stomach = mean(StomachLength_cm)) %>% 
  ungroup()
```

```{r table of locations, results = "asis"}
total <- data.frame(Location = "Total", Latitude = "", Longitude = "", minD = min(fish$Depth_m), maxD = max(fish$Depth_m), meanD = formatC(mean(fish$Depth_m), digits = 1, format = "f"), n = 109, stringsAsFactors = F)

fish %>% 
  group_by(Location) %>% 
  summarize(Latitude = formatC(mean(Latitude), digits = 3, format = "f"),
            Longitude = formatC(mean(Longitude), digits = 3, format = "f"),
            minD = formatC(min(Depth_m), digits = 1, format = "f"),
            maxD = formatC(max(Depth_m), digits = 1, format = "f"),
            meanD = formatC(mean(Depth_m), digits = 1, format = "f"),
            n = n()) %>% 
  rbind(total) %>% 
  knitr::kable(row.names = F,
               col.names = c("Location", "Lat.", "Long.", "Min. Depth", "Max. Depth", "Mean Depth", "n"))
```

### 2018-03-20 docs/supplementary/S2Table.Rmd
reorganized the repository

---
title: "Supplementary Table S2"
author: "Juan Carlos Villaseñor-Derbez"
output: pdf_document
---

Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable). Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 5.5)

options(knitr.table.format = "latex")

windowsFonts(Times=windowsFont("TT Times New Roman"))
```

```{r load packages}
suppressPackageStartupMessages({
  # library(RColorBrewer)
  # library(colorRamps)
  library(stargazer)
  library(sandwich)
  library(lmtest)
  library(broom)
  library(tidyverse)
})
```

```{r}
fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
  summarize(Length = 10*mean(TotalLength_cm),
            Weight = mean(TotalWeigth_gr),
            Stomach = mean(StomachLength_cm)) %>% 
  ungroup()
```

```{r}
model <- lm(log10(Weight) ~ log10(Length), data = fish)

TidyModel <- model%>%
  lmtest::coeftest(vcov = sandwich::vcovHC(., type = "HC1")) %>%
  broom::tidy()

robust_se <- TidyModel$std.error %>%
  set_names(TidyModel$term)

wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))

f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))

a <- coefficients(model)[[1]]
b <- coefficients(model)[[2]]
```

```{r, results = "asis"}
ci_c <- c("95\\% CI for c", paste0("(", formatC(a-(1.96*robust_se[[1]]), digits = 3, format = "f"),"-", formatC(a+(1.96*robust_se[[1]]), digits = 3, format = "f"),")"))

ci_b <- c("95\\% CI for b", paste0("(", formatC(b-(1.96*robust_se[[2]]), digits = 3, format = "f"),"-", formatC(b+(1.96*robust_se[[2]]), digits = 3, format = "f"),")"))

stargazer(model,
          header = F,
          se = list(robust_se),
          type = "latex",
          t.auto = T,
          p.auto = T,
          intercept.bottom = F,
          single.row = T,
          report = "vcs*",
          omit.stat = c("f"),
          add.lines = list(ci_c, ci_b, f_string),
          covariate.labels = c("c", "b"),
          dep.var.labels = "log10(TW)")
```

### 2018-03-20 update_ref.R

@@ -1,13 +1,0 @@
-update_ref <- function(ref_name = "references.bib"){
-  
-  refs <- RefManageR::ReadBib(ref_name) %>% 
-    as.data.frame()
-  
-  ids <- substr(row.names(as.data.frame(refs)), 1, nchar(row.names(as.data.frame(refs)))-3)
-  
-  refs <- magrittr::set_rownames(refs, ids) %>% 
-    dplyr::mutate(key = ids) %>% 
-    RefManageR::as.BibEntry()
-  
-  RefManageR::WriteBib(bib = refs, file = ref_name)
-}

### 2018-03-20 docs/Manuscript.Rmd
Removed call to label from sf object in map

@@
 ggplot() +
-  geom_sf(data = W, aes(label = name)) +
+  geom_sf(data = W) +
   geom_point(data = review[review$Gender == "Both", ], aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
@@
   guides(colorbar = guide_legend(order = 0),
-         size = guide_legend(order = 1, direction = "horizontal", title.position = "top")) +
+         size = guide_legend(order = 1,
+                             direction = "horizontal",
+                             title.position = "top")) +
   lims(x = c(-106, -60), y = c(9, 36))

### 2018-04-09 docs/Manuscript.Rmd
Updated abstract

@@
 abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean.
-In order to better manage the invasion, inform lionfish removal programs, and estimate biomass available for harvest, we must be able to accurately estimate their total biomass, frequently from length observations.
-This work compares length-weight relationships of the invasive lionfish through the invasion with the addition of parameters for the Central Mexican Caribbean.
-A review of 15 length-weight relationships reported in 10 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length.
+In order to better manage the invasion, we must be able to accurately estimate their total biomass.
+This work compares length-weight relationships of the invasive lionfish through the invasion range.
+A review of 15 length-weight relationships reported in 11 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length.
 The reviewed parameters indicate that, for the same length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf of Mexico.
 This highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters ($a = 3.2056\\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean.
-Findings from this work can aid managers and decision makers to better select length-weight parameters when these are not available for their region of interest."
+This study also reports a new pair of length-weight parameters ($a = 3.2056\\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean region.
+These fidnings can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs."
 header-includes: #allows you to add in your own Latex packages
@@
     template: peerj_template.tex
+    number_sections: no
 ---

### 2018-04-09 docs/Manuscript.Rmd
Modified intro

@@
 
-# Introduction
+\section*{Introduction}
 
@@
 
-A significant amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
+A substantial amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
 Their feeding behavior and high consumption rates can reduce recruitment \citep{albins_2008} and population sizes \citep{green_2012} of native reef-fish species, and further the endangerment of critically endangered reef fish \citep{rocha_2015}.
@@
 Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean.
-The weight-at-length of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
+The length-weight of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
 Thus, when using biomass-informed models or estimating weights from length observations, it is important to use site-specific parameters.
@@
 
-# Materials and Methods
+\section*{Materials and Methods}
 

### 2018-04-09 docs/Manuscript.Rmd
Modified materials and methods

@@
 
-Length-weight relationships (n = 15) identified in literature were obtained for North Carolina (n = 1, \citet{barbour_2011}), Northern (n = 3, \citet{fogg_2013}) and Southern Gulf of Mexico (n = 3, \citet{aguilarperera_2016}), the Southern Mexican Caribbean (n = 1, \citet{sabidoitza_2016}), Little Cayman (n = 1,\citet{edwards_2014}), Jamaica (n = 1, \citet{chin_2016}), Bonaire (n = 1, \citet{deleon_2013}) and Costa Rica (n = 1, \citet{sandel_2015}).
-Locations with allometric parameters are shown in Figure \ref{fig:map}.
-When available, information on sampling methods, gender differentiation, location, and depth ranges of each study was retrieved.
+Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1, \citet{barbour_2011}), Gulf of Mexico (n = 7, \citet{aguilarperera_2016,fogg_2013,dahl_2014}), and Caribbean (n = 8, \citet{chin_2016,toledohernndez_2014,deleon_2013,edwards_2014,sabidoitza_2016,sandel_2015,darling_2011}).
+When available, information on sampling methods, sex differentiation, location, and depth ranges of each study was retrieved.
 Whenever gender was not specified, it was assumed that the results were presented for pooled genders.
-
-Parameters from the central Mexican Caribbean were obtaines from data collected in `r length(unique(fish$Location))` sampling sites along the Mexican Caribbean coast in 2010 (Table S1).
-Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
-All observed lionfish (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes by eliminating gear selectivity.
-Organisms were euthanized (via pithing) and Total Length (TL; mm) and Total Weight (TW; gr) were recorded before freezing organisms.
+Locations with allometric parameters are shown in Figure \ref{fig:map} and \ref{tab:all_params}.
 
@@
 ```{r, fig.cap = "\\label{fig:map}Locations where allometric growth of lionfish (*Pterois spp*) have been reported.
-Sizes indicate sample size of each study, colors indicate the b coefficient in Eq \\ref{eq:allometric}"}
+Sizes indicate sample size of each study, colors indicate the b coefficient in Eq.
+\\ref{eq:allometric}."}
 

### 2018-04-09 docs/Manuscript.Rmd
Modified map to include all points

@@
   geom_sf(data = W) +
-  geom_point(data = review[review$Gender == "Both", ], aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
+  geom_point(data = review %>%
+      mutate(N = ifelse(is.na(N), 1, N)),
+    aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
   theme_classic() +

### 2018-04-09 docs/Manuscript.Rmd
Modified methods section

@@
 
+Parameters from the central Mexican Caribbean were obtained from data collected in `r length(unique(fish$Location))` sampling sites along the Central Mexican Caribbean coast in 2010 (Table S1).
+Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
+All observed lionfish (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
+The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes by eliminating gear selectivity.
+Organisms were euthanized (via pithing) and Total Length (TL; mm) and Total Weight (TW; gr) were recorded before freezing organisms.
+
 The weight at length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function:
@@
 The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$).
-Additionally, the allometric parameter was tested against the null hypothesis of isometric growth ($H_0: b = 3$).
+Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$) and the null hypothesis of isometric growth ($H_0: b = 3$).
 Coefficients were tested with a two-tailed Student's t-test.
@@
 Since uncertainty around estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships.
-Instead, the 16 length-weight relationships were used to calculate expected weight length observations of the organisms sampled from the Central Mexican Caribbean (n = 109).
-Expected weights were divided by the observed weights to obtain a ratio.
+Instead, the 16 length-weight relationships were used to calculate predicted weight from length observations of the organisms sampled from the Central Mexican Caribbean.
+Predicted weights were divided by the observed weights to obtain a ratio.
 Difference in mean weight ratios across studies were tested with a one-way Analysis of Variance (ANOVA).
-
-All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 \citep{rcore_2017}. Raw data and code used in this work is available at dryad.org.
+All analyses were performed in R version 3.4.4 \citep{rcore_2018}.
+Raw data and code used in this work is available at dryad.org.
 
@@
   set_names(TidyModel$term)
-
-wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))
-
-f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))
-
 ```
@@
 b <- coefficients(model)[[2]]
-
-predicted_this_study <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
-  mutate(Weight = 10^a*Length^b)
 ```

### 2018-04-09 docs/Manuscript.Rmd
Updated results

@@
 
-# Results
+\section*{Results}
 
-The model adjusted to \ref{eq:log-alo-trans} estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
-Thus, TW (gr) can be calculated from TL (mm) as a linear equation: $log_{10}(TW) = `r coef(model)[[2]]`\times log_{10}(TL) `r coef(model)[[1]]`$, or its exponential form: $TW = `r 10^coef(model)[[1]]`\times TL^{`r coef(model)[[2]]`}$.
+This section presents a new length-weight relationship for lionfish in the Central Mexican Caribbean region.
+A summary of length-weight relationship is provided, and a comparison of predicted-to-observed weight is included.
+
+The model adjusted to Eq.
+\ref{eq:log-alo-trans} estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
 The intercept ($c$) and slope $(b)$ were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.001$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.001$, respectively), rejecting the null hypothesis of no change.
 Additionally, the allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), indicating that lionfish present allometric growth.
-More information on model fit and confidence intervals for the estimated coefficients is presented in TableS2.
+More information on model fit is presented in TableS2.
 The relationship between Total Length and Total Weight is presented in Figure \ref{fig:l-w-carib}.
 
-From the 11 peer-reviewed studies including information on growth parameters for *P.
-volitans* and the additional calculated for the central Mexican Caribbean, `r dim(review)[1]` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
+From the `r length(unique(review$Study))-1` peer-reviewed studies including information on growth parameters for *P.
+volitans* and the additional calculated for the central Mexican Caribbean, `r dim(review)[1]-1` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
 Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
@@
 Two studies \citep{deleon_2013,darling_2011} did not specify how organisms were sampled.
+\citep{fogg_2013} stated the use spine-less weight in the length-weight relationship estimation.
 
@@
 In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for pooled genders.
-Figure \ref{fig:all_allo} shows the weight-at-length relationships with parameters from all studies.
+Figure \ref{fig:all_allo} shows the length-weight relationships with parameters from all studies.
 
-There were significant differences in expected-to-observed weight ratios estimated for each pair of parameters (F(15, 1728) = 38.26; p < 0.001).
-From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-On the other hand,\citet{barbour_2011} yielded the highest weight estimates, with a mean ($\pm$ SD) expected-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
+There were significant differences in predicted-to-observed weight ratios estimated for each pair of parameters (F(15, 1728) = 38.26; p < 0.001).
+From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
+On the other hand,\citet{barbour_2011} yielded the highest weight estimates, with a mean ($\pm$ SD) predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
 Predicted-to-observed weight ratios and groups identified by Tukey's HSD ($\alpha = 0.05$) are presented in Figure \ref{fig:bio_ratio}.
 
-\clearpage
+```{r, fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the Central Mexican Caribbean.
+Points indicate samples, solid line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
 
-```{r, fig.height = 3.5, fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the Central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit (See Table S1)."}
-
-ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
-  geom_line(data = predicted_this_study, mapping = aes(x = Length, y = Weight), size = 1) +
-  geom_point(size = 2, alpha = 0.25, color = "black") +
+fit <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
+  geom_point(size = 3, shape = 21, fill = "steelblue", color = "black") +
   theme_cowplot() +
@@
   scale_color_brewer(palette = "Set3") +
-  theme(text=element_text(family="Times"))
+  theme(text=element_text(family = "Times")) +
+  geom_smooth(method = "lm", formula = y ~ I(a*x^b), color = "black", se = F)
+
+ggExtra::ggMarginal(p = fit,
+                    type = "density",
+                    margins = "both",
+                    fill = "steelblue",
+                    color = "black",
+                    alpha = 0.5)
 ```
@@
 review %>% 
-  select(Study_site, Gender2, N, a, b, r2, Study) %>% 
+  select(Region, Gender2, N, a, b, r2, Study) %>% 
   filter(!Study == "Fishbase") %>% 
-  arrange(Study_site) %>% 
+  arrange(Region) %>% 
   mutate(r2 = ifelse(is.na(r2), "-", r2),
@@
                col.names = c("Region", "Sex", "n", "a", "b", "R2", "Reference"),
-               caption = c("\\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+               caption = "\\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, a = scaling parameter for eq.
-1, c = y-intercept for eq.
-3, b = exponent or slope for eq.
-1 or eq.
+n = Sample size, Sex specifies if data is for pooled (B), females (F), or males (M), a = scaling parameter for Eq.
+1, c = y-intercept for Eq.
+3, b = exponent or slope for Eq.
+1 or Eq.
 3, respectively.
-The $R^2$ column indicates reported model fit."))
+The $R^2$ column indicates reported model fit.")
 ```
 
-\clearpage
-
-```{r, fig.height = 3.8, fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 16) for eight studies, this study, and Fishbase.
+```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 16) for 11 studies and this study.
 Colors indicate studies from which the parameters were extracted.
@@
 
-```{r, fig.height = 3.5, fig.cap = "\\label{fig:bio_ratio}Violin plot showing the distribution of predicted to observed biomass ratios for 16 pairs of allometric parameters.
+```{r, fig.height = 3.5, fig.cap = "\\label{fig:bio_ratio}Violin plot showing the distribution of predicted to observed weight ratios for 16 pairs of allometric parameters.
 Red and blue circles indicate median and mean values, respectively.
@@
 Predicted_biomass %<>% 
-  left_join(groups$groups, by = "Study_id")
+  left_join(groups$groups, by = "Study_id") %>% 
+  mutate(groups = as.character(groups),
+         groups = ifelse(Length == 34, groups, ""))
 
@@
   geom_hline(yintercept = 1, linetype = "dashed") +
-  labs(y = "Biomass (Predicted / Observed)", x = "") +
+  labs(y = "Weight (Predicted/Observed)", x = "") +
   coord_flip() +
@@
         axis.text = element_text(size = 10)) +
-  geom_text(aes(y = 3.7, label = groups), family = "Times", fontface = "plain", size = 3) +
+  geom_text(aes(y = 3.7, label = groups), family = "Times", fontface = "plain") +
   scale_y_continuous(limits = c(NA, 3.7))
@@
 
-\clearpage
-
-# Discussion
-
-\citet{fogg_2013} uses Spine-less weight
-
-\citet{toledohernndez_2014} compares young and wold growth
+\section*{Discussion}
 
@@
 
-The length-weight coefficients estimated in this study were within the range identified by studies in other regions \citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016,edwards_2014,chin_2016,deleon_2013,sandel_2015}.
+The length-weight coefficients estimated in this study were within the range identified by studies in other regions \ref{tab:all_params}.
 However, the ones presented here provide lower weight estimates for a same length.
@@
 This indicates that there are differences between lionfish across the invasion range.
-Similar regional variation has been reported for age-at-length relationships of this species \citep{fogg_2015,pusack_2016}.
+Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015} and compared to their native range \citep{pusack_2016}.
+These may be driven genetic differences or organisms being exposed to distinct environmental conditions.
+For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_201}.
+Alternatively, \citet{fogg_2015} suggest that differences observed in age-at-length "may bemore related to climate rather than other biological and ecological factors".
+Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both.
+Future research should focus on teasing appart these and other possible explanations.
 
-Causas de las diferencias...
-
-These differences can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
+The results presented in this paper can have major implications in management.
+Our results show that, for a given length, using one set of parameters or the other can result in a 3-fold increase in estimated weight.
+These becomes especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
 Using site-specific values provides a more accurate estimate of fish biomass.
@@
 
-# Aknowledgements
+\section*{Aknowledgements}
 
@@
 \bibliography{references}
-
-# Supplementary materials
-
-## Figure S1
-
-```{r, include = F}
-length_hist <- ggplot(data = fish, mapping = aes(x = Length)) +
-  geom_density(fill = "gray", alpha = 0.5) +
-  theme_cowplot() +
-  labs(x = "Total Length (mm)", y = "Density") +
-  theme(text = element_text(family = "Times"))
-
-weight_hist <- ggplot(data = fish, mapping = aes(x = Weight)) +
-  geom_density(fill = "gray", alpha = 0.5) +
-  theme_cowplot() +
-  labs(x = "Total weight (gr)", y = "Density") +
-  theme(text = element_text(family = "Times"))
-
-# Density distributions for A) Total length (mm) and B) Total weight (gr) for 109 lionfish sampled in the Central Mexican Caribbean.
-FigS1 <- cowplot::plot_grid(length_hist, weight_hist, ncol = 1, labels = "AUTO")
-ggsave(FigS1, file="supplementary/FigS1.png", width = 5.5, height = 6, dpi = 600)
-```

### 2018-04-09 docs/Manuscript.tex
Updated manuscript

@@
 North-Western Atlantic and the Caribbean. In order to better manage the
-invasion, inform lionfish removal programs, and estimate biomass
-available for harvest, we must be able to accurately estimate their
-total biomass, frequently from length observations. This work compares
-length-weight relationships of the invasive lionfish through the
-invasion with the addition of parameters for the Central Mexican
-Caribbean. A review of 15 length-weight relationships reported in 10
-peer-reviewed studies shows that lionfish exhibit spatial variation in
-weight-at-length. The reviewed parameters indicate that, for the same
-length, lionfish in the Caribbean have lower body mass than in the
-Atlantic or Gulf of Mexico. This highlights the importance of using
-site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters
-(\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms sampled in the
-Central Mexican Caribbean. Findings from this work can aid managers and
-decision makers to better select length-weight parameters when these are
-not available for their region of interest.
+invasion, we must be able to accurately estimate their total biomass.
+This work compares length-weight relationships of the invasive lionfish
+through the invasion range. A review of 15 length-weight relationships
+reported in 11 peer-reviewed studies shows that lionfish exhibit spatial
+variation in weight-at-length. The reviewed parameters indicate that,
+for the same length, lionfish in the Caribbean have lower body mass than
+in the Atlantic or Gulf of Mexico. This highlights the importance of
+using site-specific parameters to estimate biomass from length
+observations. This study also reports a new pair of length-weight
+parameters (\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms
+sampled in the Central Mexican Caribbean region. These fidnings can have
+major implications in management, especially when estimating biomass
+available for harvest or predicting effects on local ecosystems, or
+evaluating the effectiveness of removal programs.
 \end{abstract}
 
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+\theoremstyle{definition}
+\newtheorem{example}{Example}
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
 \begin{document}
@@
 
-\section{Introduction}\label{introduction}
+\section*{Introduction}
 
@@
 
-A significant amount of research has been done to describe lionfish
+A substantial amount of research has been done to describe lionfish
 feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas
@@
 Rica \citep{sandel_2015}, but remain unavailable for the central Mexican
-Caribbean. The weight-at-length of a species can vary across regions as
-a response to biotic (\emph{e.g.} local food availability) and abiotic
+Caribbean. The length-weight of a species can vary across regions as a
+response to biotic (\emph{e.g.} local food availability) and abiotic
 (\emph{e.g.} water temperature) conditions \citep{johnson_2016}. Thus,
@@
 
-\section{Materials and Methods}\label{materials-and-methods}
+\section*{Materials and Methods}
 
@@
 Length-weight relationships (n = 15) identified in literature were
-obtained for North Carolina (n = 1, \citet{barbour_2011}), Northern (n =
-3, \citet{fogg_2013}) and Southern Gulf of Mexico (n = 3,
-\citet{aguilarperera_2016}), the Southern Mexican Caribbean (n = 1,
-\citet{sabidoitza_2016}), Little Cayman (n = 1,\citet{edwards_2014}),
-Jamaica (n = 1, \citet{chin_2016}), Bonaire (n = 1, \citet{deleon_2013})
-and Costa Rica (n = 1, \citet{sandel_2015}). Locations with allometric
-parameters are shown in Figure \ref{fig:map}. When available,
-information on sampling methods, gender differentiation, location, and
-depth ranges of each study was retrieved. Whenever gender was not
-specified, it was assumed that the results were presented for pooled
-genders.
-
-Parameters from the central Mexican Caribbean were obtaines from data
-collected in 10 sampling sites along the Mexican Caribbean coast in 2010
-(Table S1). Sampling locations included wall and carpet reefs at depths
-between 5.7 m and 38.1 m. All observed lionfish (n = 109) were collected
-using hand nets and numbered collection bottles. The use of hand nets
-prevented any weight loss due to bleeding and allowed a better
-representation of small sizes by eliminating gear selectivity. Organisms
-were euthanized (via pithing) and Total Length (TL; mm) and Total Weight
-(TW; gr) were recorded before freezing organisms.
+obtained for the North Atlantic (n = 1, \citet{barbour_2011}), Gulf of
+Mexico (n = 7, \citet{aguilarperera_2016,fogg_2013,dahl_2014}), and
+Caribbean (n = 8,
+\citet{chin_2016,toledohernndez_2014,deleon_2013,edwards_2014,sabidoitza_2016,sandel_2015,darling_2011}).
+When available, information on sampling methods, sex differentiation,
+location, and depth ranges of each study was retrieved. Whenever gender
+was not specified, it was assumed that the results were presented for
+pooled genders. Locations with allometric parameters are shown in Figure
+\ref{fig:map} and \ref{tab:all_params}.
 
@@
 Sizes indicate sample size of each study, colors indicate the b
-coefficient in Eq \ref{eq:allometric}}
+coefficient in Eq. \ref{eq:allometric}.}
 \end{figure}
+
+Parameters from the central Mexican Caribbean were obtained from data
+collected in 10 sampling sites along the Central Mexican Caribbean coast
+in 2010 (Table S1). Sampling locations included wall and carpet reefs at
+depths between 5.7 m and 38.1 m. All observed lionfish (n = 109) were
+collected using hand nets and numbered collection bottles. The use of
+hand nets prevented any weight loss due to bleeding and allowed a better
+representation of small sizes by eliminating gear selectivity. Organisms
+were euthanized (via pithing) and Total Length (TL; mm) and Total Weight
+(TW; gr) were recorded before freezing organisms.
 
@@
 Both coefficients were tested against the null hypothesis of no change
-(\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)). Additionally, the
-allometric parameter was tested against the null hypothesis of isometric
-growth (\(H_0: b = 3\)). Coefficients were tested with a two-tailed
-Student's t-test. The significance of the regression was corroborated
-with an F-test.
+(\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)) and the null hypothesis
+of isometric growth (\(H_0: b = 3\)). Coefficients were tested with a
+two-tailed Student's t-test. The significance of the regression was
+corroborated with an F-test.
 
@@
 statistical differences between relationships. Instead, the 16
-length-weight relationships were used to calculate expected weight
+length-weight relationships were used to calculate predicted weight from
 length observations of the organisms sampled from the Central Mexican
-Caribbean (n = 109). Expected weights were divided by the observed
-weights to obtain a ratio. Difference in mean weight ratios across
-studies were tested with a one-way Analysis of Variance (ANOVA).
+Caribbean. Predicted weights were divided by the observed weights to
+obtain a ratio. Difference in mean weight ratios across studies were
+tested with a one-way Analysis of Variance (ANOVA). All analyses were
+performed in R version 3.4.4 \citep{rcore_2018}. Raw data and code used
+in this work is available at dryad.org.
 
-All hypothesis testing was performed with an \emph{a priori} confidence
-level of \(\alpha = 0.01\) in R version 3.4.0 \citep{rcore_2017}. Raw
-data and code used in this work is available at dryad.org.
+\section*{Results}
 
-\section{Results}\label{results}
+This section presents a new length-weight relationship for lionfish in
+the Central Mexican Caribbean region. A summary of length-weight
+relationship is provided, and a comparison of predicted-to-observed
+weight is included.
 
-The model adjusted to \ref{eq:log-alo-trans} estimated the coefficient
-values at \(b = 3.2347391\) and \(c = -5.4940866\). Thus, TW (gr) can be
-calculated from TL (mm) as a linear equation:
-\(log_{10}(TW) = 3.2347391\times log_{10}(TL) -5.4940866\), or its
-exponential form: \(TW = 3.2056297\times 10^{-6}\times TL^{3.2347391}\).
-The intercept (\(c\)) and slope \((b)\) were significantly different
-from zero (\(t(107) = -66.17; p<0.001\) and \(t(107) = 83.24; p<0.001\),
+The model adjusted to Eq. \ref{eq:log-alo-trans} estimated the
+coefficient values at \(b = 3.2347391\) and \(c = -5.4940866\). The
+intercept (\(c\)) and slope \((b)\) were significantly different from
+zero (\(t(107) = -66.17; p<0.001\) and \(t(107) = 83.24; p<0.001\),
 respectively), rejecting the null hypothesis of no change. Additionally,
@@
 indicating that lionfish present allometric growth. More information on
-model fit and confidence intervals for the estimated coefficients is
-presented in TableS2. The relationship between Total Length and Total
-Weight is presented in Figure \ref{fig:l-w-carib}.
+model fit is presented in TableS2. The relationship between Total Length
+and Total Weight is presented in Figure \ref{fig:l-w-carib}.
 
@@
 parameters for \emph{P. volitans} and the additional calculated for the
-central Mexican Caribbean, 16 parameters were identified (Table
+central Mexican Caribbean, 15 parameters were identified (Table
 \ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies
@@
 studies \citep{deleon_2013,darling_2011} did not specify how organisms
-were sampled.
+were sampled. \citep{fogg_2013} stated the use spine-less weight in the
+length-weight relationship estimation.
 
@@
 higher for parameters for pooled genders. Figure \ref{fig:all_allo}
-shows the weight-at-length relationships with parameters from all
-studies.
+shows the length-weight relationships with parameters from all studies.
 
-There were significant differences in expected-to-observed weight ratios
-estimated for each pair of parameters (F(15, 1728) = 38.26; p
+There were significant differences in predicted-to-observed weight
+ratios estimated for each pair of parameters (F(15, 1728) = 38.26; p
 \textless{} 0.001). From all allometric parameters reviewed, those of
 \citet{edwards_2014} provided the lowest weight estimates, with an
-expected-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
+predicted-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
 SD). On the other hand,\citet{barbour_2011} yielded the highest weight
-estimates, with a mean (\(\pm\) SD) expected-to-observed weight ratio of
-1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
+estimates, with a mean (\(\pm\) SD) predicted-to-observed weight ratio
+of 1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
 identified by Tukey's HSD (\(\alpha = 0.05\)) are presented in Figure
 \ref{fig:bio_ratio}.
-
-\clearpage
 
@@
 relationship for 109 lionfish sampled in the Central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit (See
-Table S1).}
+Points indicate samples, solid line indicates curve of best fit,
+marginal plots represent the density distribution of each variable.}
 \end{figure}
@@
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, a = scaling parameter for eq.
-1, c = y-intercept for eq.
-3, b = exponent or slope for eq.
-1 or eq.
+n = Sample size, Sex specifies if data is for pooled (B), females (F), or males (M), a = scaling parameter for Eq.
+1, c = y-intercept for Eq.
+3, b = exponent or slope for Eq.
+1 or Eq.
 3, respectively.
@@
 \midrule
-Alacranes Reef, Mexico & B & 472 & 2.90e-06 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-Alacranes Reef, Mexico & F & 67 & 1.20e-06 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-Alacranes Reef, Mexico & M & 59 & 4.20e-06 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-Bahamas & B & - & 2.50e-06 & 3.29 & - & Darling et al., 2011\\
-Bonaire & B & 1450 & 2.28e-05 & 2.89 & 0.96 & de Leon et al., 2013\\
+Caribbean & B & 458 & 3.64e-05 & 2.81 & - & Sandel et al., 2015\\
+Caribbean & B & 419 & 2.75e-05 & 2.85 & 0.8715 & Chin et al 2016\\
+Caribbean & B & 1450 & 2.28e-05 & 2.89 & 0.96 & de Leon et al., 2013\\
+Caribbean & B & 1887 & 3.00e-06 & 3.24 & 0.97 & Edwards et al., 2014\\
+Caribbean & B & - & 2.50e-06 & 3.29 & - & Darling et al., 2011\\
 \addlinespace
-Costa Rica & B & 458 & 3.64e-05 & 2.81 & - & Sandel et al., 2015\\
-Discovery Bay, Jamaica & B & 419 & 2.75e-05 & 2.85 & 0.8715 & Chin et al 2016\\
-Little Cayman & B & 1887 & 3.00e-06 & 3.24 & 0.97 & Edwards et al., 2014\\
-North Carolina & B & 774 & 2.89e-05 & 2.89 & - & Brbour et al 2011\\
-Northern Gulf of Mexico & B & 934 & 2.10e-06 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
+Caribbean & B & 2143 & 5.20e-06 & 3.18 & 0.9907 & Sabido-Itza et al., 2016\\
+Caribbean & B & 227 & 8.00e-06 & 3.11 & 0.958 & Toledo-Hernández et al., 2014\\
+Caribbean & B & 109 & 3.20e-06 & 3.23 & 0.9766 & This study\\
+GoM & B & 934 & 2.10e-06 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
+GoM & B & 472 & 2.90e-06 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
 \addlinespace
-Northern Gulf of Mexico & B & 582 & 1.40e-06 & 3.43 & 0.99 & Fogg et al., 2013\\
-Northern Gulf of Mexico & M & 119 & 2.70e-06 & 3.31 & 0.97 & Fogg et al., 2013\\
-Northern Gulf of Mexico & F & 115 & 6.80e-06 & 3.14 & 0.94 & Fogg et al., 2013\\
-Puerto Aventuras, Mexico & B & 109 & 3.20e-06 & 3.23 & 0.9766 & This study\\
-Puerto Rico & B & 227 & 8.00e-06 & 3.11 & 0.958 & Toledo-Hernández et al., 2014\\
-Xcalak, Mexico & B & 2143 & 5.20e-06 & 3.18 & 0.9907 & Sabido-Itza et al., 2016\\
+GoM & F & 67 & 1.20e-06 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & M & 59 & 4.20e-06 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & B & 582 & 1.40e-06 & 3.43 & 0.99 & Fogg et al., 2013\\
+GoM & M & 119 & 2.70e-06 & 3.31 & 0.97 & Fogg et al., 2013\\
+GoM & F & 115 & 6.80e-06 & 3.14 & 0.94 & Fogg et al., 2013\\
+NorthAtlantic & B & 774 & 2.89e-05 & 2.89 & - & Barbour et al 2011\\
 \bottomrule
@@
 \end{table}
-
-\clearpage
 
@@
 \caption{\label{fig:unnamed-chunk-5}\label{fig:all_allo}Length-weight
-relationships (n = 16) for eight studies, this study, and Fishbase.
-Colors indicate studies from which the parameters were extracted. Solid
-lines indicate that the fit was performed for males and females pooled
-together. Dotted lines indicate that the regression was performed on
-females, and dashed lines indicate it was performed for males.}
+relationships (n = 16) for 11 studies and this study. Colors indicate
+studies from which the parameters were extracted. Solid lines indicate
+that the fit was performed for males and females pooled together. Dotted
+lines indicate that the regression was performed on females, and dashed
+lines indicate it was performed for males.}
 \end{figure}
@@
 \caption{\label{fig:unnamed-chunk-6}\label{fig:bio_ratio}Violin plot showing
-the distribution of predicted to observed biomass ratios for 16 pairs of
+the distribution of predicted to observed weight ratios for 16 pairs of
 allometric parameters. Red and blue circles indicate median and mean
@@
 
-\clearpage
-
-\section{Discussion}\label{discussion}
-
-\citet{fogg_2013} uses Spine-less weight
-
-\citet{toledohernndez_2014} compares young and wold growth
+\section*{Discussion}
 
@@
 The length-weight coefficients estimated in this study were within the
-range identified by studies in other regions
-\citep{barbour_2011,fogg_2013,aguilarperera_2016,sabidoitza_2016,edwards_2014,chin_2016,deleon_2013,sandel_2015}.
+range identified by studies in other regions \ref{tab:all_params}.
 However, the ones presented here provide lower weight estimates for a
@@
 Similar regional variation has been reported for age-at-length
-relationships of this species \citep{fogg_2015,pusack_2016}.
+relationships of this species across the invaded region
+\citep{fogg_2015} and compared to their native range
+\citep{pusack_2016}. These may be driven genetic differences or
+organisms being exposed to distinct environmental conditions. For
+example, work on mitochondrial DNA has shown two distinct population
+groups, identified as the ``Caribbean group'' and ``Northern Group''
+\citep{betancurr_201}. Alternatively, \citet{fogg_2015} suggest that
+differences observed in age-at-length ``may bemore related to climate
+rather than other biological and ecological factors''. Differences in
+weight-at-length could also reflect differences in energy input
+(\emph{i.e.} in some regions, lionfish eat more) or differential usage
+of this energy (\emph{e.g.} regional differences in predator abundances
+lead to different usage of energy), or a combination of both. Future
+research should focus on teasing appart these and other possible
+explanations.
 
-Causas de las diferencias\ldots{}
-
-These differences can have major implications in management, especially
-when estimating biomass available for harvest or predicting effects on
-local ecosystems, or evaluating the effectiveness of removal programs.
-Using site-specific values provides a more accurate estimate of fish
-biomass. Future research should try to use, to the extent possible,
-parameters calculated for their region, or use different parameters to
-provide upper and lower bounds in their results. At the same time, this
+The results presented in this paper can have major implications in
+management. Our results show that, for a given length, using one set of
+parameters or the other can result in a 3-fold increase in estimated
+weight. These becomes especially relevant when estimating biomass
+available for harvest, predicting effects on local ecosystems, or
+evaluating the effectiveness of removal programs. Using site-specific
+values provides a more accurate estimate of fish biomass. Future
+research should try to use, to the extent possible, parameters
+calculated for their region, or use different parameters to provide
+upper and lower bounds in their results. At the same time, this
 highlights the need for more basic research that furthers our
@@
 
-\section{Aknowledgements}\label{aknowledgements}
+\section*{Aknowledgements}
 
@@
 
-\section{Supplementary materials}\label{supplementary-materials}
-
-\subsection{Figure S1}\label{figure-s1}
-
 \end{document}

### 2018-04-12 docs/Manuscript.Rmd
Incorporated Sean's comments

@@
 institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
-abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the North-Western Atlantic and the Caribbean.
+abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the Western Atlantic and the Caribbean.
 In order to better manage the invasion, we must be able to accurately estimate their total biomass.
@@
 This highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters ($a = 3.2056\\times 10^{-6}; b = 3.235$) for organisms sampled in the Central Mexican Caribbean region.
-These fidnings can have major implications in management, especially when estimating biomass available for harvest or predicting effects on local ecosystems, or evaluating the effectiveness of removal programs."
+This study also reports a new pair of length-weight parameters ($a = 3.2056\\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region.
+These findings can have major implications in management, especially when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs."
 header-includes: #allows you to add in your own Latex packages
@@
 output:
-  bookdown::pdf_document2:
+  pdf_document:
     keep_tex: yes
@@
 
-At least 84% of the marine eco-regions have reported the presence of an invasive species \citep{molnar_2008}, which represent a major threat to local biodiversity and the economic activities that depend on it \citep{bax_2003}.
+At least 84% of marine eco-regions have reported the presence of an invasive species \citep{molnar_2008}, which represent a major threat to local biodiversity and the economic activities that depend on it \citep{bax_2003}.
 Invasive species may threaten native species through predation, competition, or indirect habitat effects \citep{davis_2003, gurevitch_2004}.
-By 2005, the economic cost of invasive species to the United States was  estimated at USD\$120 billion per year\citep{pimentel_2005}.
+By 2005, the economic cost of invasive species to the United States was  estimated at USD \$120 billion per year \citep{pimentel_2005}.
 
-Lionfish (*Pterois volitans/miles* complex) are an invasive species in the Western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
-They are the first marine vertebrates to establish in North Atlantic \citep{schofield_2009,schofield_2010} and Caribbean coasts \citep{sabidoitza_2016}.
-Lionfish have been widely reported in coral reefs \citep{aguilarperera_2010}, but also in other habitats such as estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with hard-bottoms \citep{muoz_2011}, and mesophotic reefs \citep{andradibrown_2017}.
-Due to their threat to local biodiversity, the speed of their spread, and difficulty of management, their presence in these waters has been labeled as a major marine invasion  \citep{hixon_2016}.
+Lionfish (*Pterois volitans/miles* complex) are an invasive species in the western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
+They are the first invasive marine vertebrates established along the North Atlantic Caribbean coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}.
+Lionfish have been widely reported in coral reefs \citep{aguilarperera_2010}, but also in other habitats such as estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, hard-bottomed areas \citep{muoz_2011}, and mesophotic reefs \citep{andradibrown_2017}.
+Their presence in these waters has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
 
 A substantial amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
-Their feeding behavior and high consumption rates can reduce recruitment \citep{albins_2008} and population sizes \citep{green_2012} of native reef-fish species, and further the endangerment of critically endangered reef fish \citep{rocha_2015}.
+\citet{peake_2018} show that invasive lionfish prey on at least 167 different species across on the tropical and temperate North Atlantic.
+Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{albins_2008, green_2012,rocha_2015}.
 (However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes).
@@
 In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
-The rapid recovery rates exhibited by lionfish \citep{barbour_2011} and the persistent populations in mesophotic coral ecosystems \citep{andradibrown_2017} --which can contribute with recruitment to shallow-water populations-- make of complete eradication through fishing effort an unlikely solution.
+Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from their persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
 However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery \citep{chin_2016}, which can reduce local abundances and control the invasion while providing alternative livelihoods.
 
-The feasibility of lionfish removal programs has been extensively evaluated through field observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}.
-The latter approeach models changes in biomass in response to changes in mortality (*i.e.* culling).
+The feasibility of lionfish removal programs has been extensively evaluated through field observations \citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}.
+The latter approach models changes in biomass in response to changes in mortality (*i.e.* culling).
 In this case, biomass represents the sum of all fish's individual weight.
-The individual weight of an organism (Total Weight; TW) can be estimated from its Total Length (TL) using the allometric growth equation ($TW = aTL^b$).
-Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean.
+The individual weight of an organism can be estimated from its length using the allometric growth equation.
+Parameters for this equation exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
 The length-weight of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
 Thus, when using biomass-informed models or estimating weights from length observations, it is important to use site-specific parameters.
-This is especially important when research involves identifying the total biomass available for harvest by fishers \citep{chin_2016} or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015}.
+This is especially important when research involves identifying the total biomass available for harvest by fishers or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015,chin_2016}.
 
 This study reviews lionfish allometric growth throughout the invasion range, and provides a new pair of parameters specific to the central Meixcan Caribbean.
-The results suggest there are important regional-scale variations in allometric growth patterns of lionfish.
+Results suggest there are important regional-scale variations in allometric growth patterns of lionfish.
 The observed differences highlight the importance of using site-specific parameters, especially when informing invasion management strategies.
+
+<!-- make this last paragraph a bit longer to talk about literature on spatial differences in fish populations -->
 
@@
 
-The main objective of this work was to compare allometric growth of lionfish throughout the invasion range.
+The main objective of this work was to compare allometric growth of lionfish throughout their invasion range.
 Allometric parameters were retreived from scientific literature, and an additional pair of parameters was calculated from filed observations in the central Mexican Caribbean.
 
-Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1, \citet{barbour_2011}), Gulf of Mexico (n = 7, \citet{aguilarperera_2016,fogg_2013,dahl_2014}), and Caribbean (n = 8, \citet{chin_2016,toledohernndez_2014,deleon_2013,edwards_2014,sabidoitza_2016,sandel_2015,darling_2011}).
-When available, information on sampling methods, sex differentiation, location, and depth ranges of each study was retrieved.
-Whenever gender was not specified, it was assumed that the results were presented for pooled genders.
-Locations with allometric parameters are shown in Figure \ref{fig:map} and \ref{tab:all_params}.
+Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 8).
+Information on sampling methods, sex differentiation, location, and depth ranges of each study was retrieved when available.
+Studies were assumed to include both genders if gender was unspecified.
+Locations where allometric studies were performed are shown in Figure \ref{fig:map} and \ref{tab:all_params}.
 
@@
 
-```{r, fig.cap = "\\label{fig:map}Locations where allometric growth of lionfish (*Pterois spp*) have been reported.
-Sizes indicate sample size of each study, colors indicate the b coefficient in Eq.
+```{r, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
+Circle sizes indicate sample size from each study, colors indicate the $b$ coefficient from Eq.
 \\ref{eq:allometric}."}
@@
   scale_fill_gradientn(colors = colorRamps::matlab.like(20)) +
-  theme(legend.justification = c(0, 1),
-        legend.position = c(0, 1),
-        legend.background = element_blank()) +
-  guides(colorbar = guide_legend(order = 0),
-         size = guide_legend(order = 1,
-                             direction = "horizontal",
-                             title.position = "top")) +
-  lims(x = c(-106, -60), y = c(9, 36))
+  theme(legend.background = element_blank(),
+        panel.grid.major = element_line(colour = "transparent")) +
+  # guides(colorbar = guide_legend(order = 0),
+  #        size = guide_legend(order = 1,
+  #                            direction = "horizontal",
+  #                            title.position = "top")) +
+  lims(x = c(-100, -60), y = c(9, 36)) +
+  labs(x = "longitude", y = "latitude") +
+  geom_text(aes(x = -70, y = 30), label = "North Atlantic\nOcean") +
+  geom_text(aes(x = -90, y = 25), label = "Gulf of Mexico") +
+  geom_text(aes(x = -75, y = 15), label = "Caribbean\nSea")
+
 ```
 
-Parameters from the central Mexican Caribbean were obtained from data collected in `r length(unique(fish$Location))` sampling sites along the Central Mexican Caribbean coast in 2010 (Table S1).
+Parameters from the central Mexican Caribbean were obtained from data collected in `r length(unique(fish$Location))` sampling sites along the central Mexican Caribbean coast in 2010 (Table S1).
 Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
 All observed lionfish (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes by eliminating gear selectivity.
-Organisms were euthanized (via pithing) and Total Length (TL; mm) and Total Weight (TW; gr) were recorded before freezing organisms.
+The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by eliminating gear selectivity.
+Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded before freezing organisms.
 
@@
 
-Where $TW$ is the Total Weight (gr), $TL$ is the Total Length (mm), $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
+Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
 When $b = 3$, it is said that the organism exhibits a perfect isometric growth.
-The dependent and independent variables were transformed via base-10 logarithms, thus the equation becomes:
+Transforming this equation via base-10 logarithms:
 
@@
 \label{eq:log-alo}
-log_{10}(TW) = b\times log_{10}(TL) + log{10}(a)
+log_{10}(TW) = b\times log_{10}(TL) + log_{10}(a)
 \end{equation}
@@
 
-Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$.
+Where $Y = log_{10}(TW)$, $m = b$, $X = log_{10}(TL)$, and $c = log_{10}(a)$.
 Since $b = m$, we will only use $b$ throughout the paper for simplicity.
-The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$) and the null hypothesis of isometric growth ($H_0: b = 3$).
-Coefficients were tested with a two-tailed Student's t-test.
-The significance of the regression was corroborated with an F-test.
+The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Squares Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
+The $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$).
+Coefficients were tested with a two-tailed Student's t, and the significance of the regression was corroborated with an F-test.
 
-During the review process, some studies indistinctly used $a$ to report either the ponderal index in \ref{eq:allometric} or the y-intercept ($c$) in \ref{eq:log-alo-trans}.
-Others reported their parameters as mm-to-gr conversions, but a rapid evaluation of such parameters indicated that they were estimated as cm-to-gr conversions.
+Studies inconsistently defined a as either the ponderal index from Eq.
+\ref{eq:allometric} or the y-intercept ($c$) from Eq.
+\ref{eq:log-alo-trans}.
+Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
 Here, all parameters are reported as TL(mm) to TW(gr) conversions.
@@
 
+<!-- Make this part more clear. Explain that the goal is to show "how far off" the estimates would be -->
+
 Since uncertainty around estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships.
-Instead, the 16 length-weight relationships were used to calculate predicted weight from length observations of the organisms sampled from the Central Mexican Caribbean.
+Instead, the 16 length-weight relationships were used to calculate predicted weight from length observations of the organisms sampled from the central Mexican Caribbean.
 Predicted weights were divided by the observed weights to obtain a ratio.
@@
 All analyses were performed in R version 3.4.4 \citep{rcore_2018}.
-Raw data and code used in this work is available at dryad.org.
+Raw data and code used in this work are available at dryad.org.
 
@@
 groups <- HSD.test(y = anova, trt = "Study_id")
+
+Rsq <- formatC(summary(model)$r.sq, digits = 3, format = "f")
+Fstring <- waldtest(model, vcov = vcovHC(model, type = "HC1")) %>% 
+  tidy()
+
+Fstring <- paste0("F(df = 1; ",nobs(model)-2, ") = ", formatC(Fstring$statistic[2], digits = 2, format = "f"))
 ```
@@
 
-This section presents a new length-weight relationship for lionfish in the Central Mexican Caribbean region.
+<!-- This section presents a new length-weight relationship for lionfish in the central Mexican Caribbean region.
 A summary of length-weight relationship is provided, and a comparison of predicted-to-observed weight is included.
+-->
 
 The model adjusted to Eq.
-\ref{eq:log-alo-trans} estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$.
-The intercept ($c$) and slope $(b)$ were significantly different from zero ($t(107) = `r formatC(coef(model)[[1]]/robust_se[[1]], digits = 2, format = "f")`; p<0.001$ and $t(107) = `r formatC(coef(model)[[2]]/robust_se[[2]], digits = 2, format = "f")`; p<0.001$, respectively), rejecting the null hypothesis of no change.
-Additionally, the allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), indicating that lionfish present allometric growth.
+\ref{eq:log-alo-trans} estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
+The allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), indicating that lionfish present allometric growth.
 More information on model fit is presented in TableS2.
-The relationship between Total Length and Total Weight is presented in Figure \ref{fig:l-w-carib}.
+The relationship between TL and TW is presented in Figure \ref{fig:l-w-carib}.
 
-From the `r length(unique(review$Study))-1` peer-reviewed studies including information on growth parameters for *P.
-volitans* and the additional calculated for the central Mexican Caribbean, `r dim(review)[1]-1` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
+From this study in the central Mexican Caribbean and the `r length(unique(review$Study))-1` peer-reviewed studies that reported length-weight parameters for *P.
+volitans* `r dim(review)[1]-1` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
 Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
-The smallest coefficient of determination was presented by \citet{chin_2016} with $R^2 = `r min(review[,13], na.rm = T)`$, while \citet{sabidoitza_2016} reported the highest value at $R^2 = `r max(review[,13], na.rm = T)`$.
 Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
-Three studies \citep{aguilarperera_2016,chin_2016,dahl_2014} explicitly stated that their organisms were sampled with pole spears.
-Five studies \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014} mentioned that some of their organisms were obtained with pole spears (or other type of harpoon), but also hand-held nets or fish traps.
-Two studies \citep{deleon_2013,darling_2011} did not specify how organisms were sampled.
-\citep{fogg_2013} stated the use spine-less weight in the length-weight relationship estimation.
+Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
+\citet{fogg_2013} use spine-less weight in the length-weight relationship estimation.
 
@@
 
-There were significant differences in predicted-to-observed weight ratios estimated for each pair of parameters (F(15, 1728) = 38.26; p < 0.001).
+There were significant differences in predicted-to-observed weight ratios estimated for each pair of parameters (F(df = 15; 1728) = 38.26; p < 0.001).
 From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
@@
 
-```{r, fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the Central Mexican Caribbean.
+```{r}
+get_eqn <- function(model){
+  substitute(italic(TW) == a %*% italic(TL)^b,
+             list(a = format(10^coef(model)[1], digits = 3),
+                  b = format(coef(model)[2], digits = 3))) %>% 
+    as.expression() %>% 
+    as.character()
+}
+
+get_rsq <- function(model){
+  substitute(italic(R)^2~"="~r2,
+             list(r2 = format(summary(model)$r.squared, digits = 3))) %>% 
+    as.expression() %>% 
+    as.character()
+}
+```
+
+```{r, fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
 Points indicate samples, solid line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
@@
   theme(text=element_text(family = "Times")) +
-  geom_smooth(method = "lm", formula = y ~ I(a*x^b), color = "black", se = F)
+  geom_smooth(method = "lm", formula = y ~ I(a*x^b), color = "black", se = F) +
+  geom_text(aes(x = 120, y = 390), label = get_eqn(model), parse = T, size = 4, family="Times", face="italic") +
+  geom_text(aes(x = 120, y = 350), label = get_rsq(model), parse = T, size = 4, family="Times", face="italic")
 
@@
 review %>% 
-  select(Region, Gender2, N, a, b, r2, Study) %>% 
+  select(Region, Gender2, N, a, b, c, r2, Study) %>% 
   filter(!Study == "Fishbase") %>% 
@@
   mutate(r2 = ifelse(is.na(r2), "-", r2),
-         N = ifelse(is.na(N), "-", N)) %>% 
-  knitr::kable(row.names = F,
-               digits =  c(0, 0, 0, 7, 2),
+         N = ifelse(is.na(N), "-", N),
+         a = formatC((a*1e5), digits = 2)) %>% 
+  knitr::kable(format = "latex",
+               row.names = F,
+               digits =  c(0, 0, 0, 0, 2, 2),
                booktabs = T,
-               col.names = c("Region", "Sex", "n", "a", "b", "R2", "Reference"),
-               caption = "\\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+               col.names = c("Region", "Sex", "n", "a", "b", "c", "R^2", "Reference"),
+               caption = "\\label{tab:all_params}Summary of 16 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies if data is for pooled (B), females (F), or males (M), a = scaling parameter for Eq.
-1, c = y-intercept for Eq.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
+1 (presented in $\\times 10^{-5}$), c = y-intercept for Eq.
 3, b = exponent or slope for Eq.
@@
   unnest() %>% 
-  mutate(Weight = a*(Length^b)) %>% 
+  mutate(Weight = a*(Length^b),
+         this = ifelse(Study == "This study", T, F)) %>%
   ggplot(aes(x = Length, y = Weight, color = Study, linetype = Gender)) +
-  geom_line() +
+  # geom_point(aes(x = Length, y = Weight2), color = "black", size = 1) +
+  geom_line(aes(size = this)) +
   labs(x = "Total length (mm)", y = "Total Weight (gr)") +
@@
   guides(color = guide_legend(order = 1),
-         linetype = guide_legend(order = 0, ncol = 2)) +
-  scale_color_brewer(palette = "Paired")
+         linetype = guide_legend(order = 0, ncol = 2),
+         size = "none") +
+  scale_color_brewer(palette = "Paired", direction = -1) +
+  scale_linetype_manual(values=c("solid", "longdash", "dotted")) +
+  scale_size_manual(values = c(1, 1.5))
 ```
@@
 A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided.
-This compliments existing literature for other sites in the north (*i.e.* Alacranes Reef \citep{aguilarperera_2016}) and South (Xcalak \citep{sabidoitza_2016}) of the Mexican Caribbean.
+This compliments existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016}.
 Additionally, the study identifies regional differences in length-weight relationships.
-Here, we focus the discussion on plausible causes of these differences.
 
-The length-weight coefficients estimated in this study were within the range identified by studies in other regions \ref{tab:all_params}.
-However, the ones presented here provide lower weight estimates for a same length.
+The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
+However, the ones presented here provide lower weight estimates for similar lenmgths.
 Until about TL = 200 mm, there are no appreciable differences between the parameters for organisms from the Mexican Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica \citep{chin_2016}.
@@
 Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic tend to be higher than those from the Caribbean.
-This indicates that there are differences between lionfish across the invasion range.
-Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015} and compared to their native range \citep{pusack_2016}.
-These may be driven genetic differences or organisms being exposed to distinct environmental conditions.
+Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015}, or when comparing populations from the invasion and native ranges \citep{pusack_2016}.
+These may be driven by genetic differences or organisms being exposed to distinct environmental conditions.
 For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_201}.
@@
 Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both.
-Future research should focus on teasing appart these and other possible explanations.
+Future research should focus on identifying which occurs here.
 
-The results presented in this paper can have major implications in management.
-Our results show that, for a given length, using one set of parameters or the other can result in a 3-fold increase in estimated weight.
-These becomes especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
+The results presented in this paper can have major implications for management.
+Our results show that, for a given length, using one set of parameters or the other can result in a threefold increase in estimated weight.
+This becomes especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
 Using site-specific values provides a more accurate estimate of fish biomass.

### 2018-04-12 docs/Manuscript.tex
Incorporated Sean's comments

@@
 Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
-North-Western Atlantic and the Caribbean. In order to better manage the
+Western Atlantic and the Caribbean. In order to better manage the
 invasion, we must be able to accurately estimate their total biomass.
@@
 parameters (\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms
-sampled in the Central Mexican Caribbean region. These fidnings can have
+sampled in the central Mexican Caribbean region. These findings can have
 major implications in management, especially when estimating biomass
-available for harvest or predicting effects on local ecosystems, or
+available for harvest, predicting effects on local ecosystems, or
 evaluating the effectiveness of removal programs.
@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{example}{Example}
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 
-At least 84\% of the marine eco-regions have reported the presence of an
+At least 84\% of marine eco-regions have reported the presence of an
 invasive species \citep{molnar_2008}, which represent a major threat to
@@
 \citep{davis_2003, gurevitch_2004}. By 2005, the economic cost of
-invasive species to the United States was estimated at USD\$120 billion
-per year\citep{pimentel_2005}.
+invasive species to the United States was estimated at USD \$120 billion
+per year \citep{pimentel_2005}.
 
 Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
-in the Western Atlantic and the Caribbean, likely introduced through
+in the western Atlantic and the Caribbean, likely introduced through
 liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
-the first marine vertebrates to establish in North Atlantic
-\citep{schofield_2009,schofield_2010} and Caribbean coasts
-\citep{sabidoitza_2016}. Lionfish have been widely reported in coral
-reefs \citep{aguilarperera_2010}, but also in other habitats such as
-estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, areas with
-hard-bottoms \citep{muoz_2011}, and mesophotic reefs
-\citep{andradibrown_2017}. Due to their threat to local biodiversity,
-the speed of their spread, and difficulty of management, their presence
-in these waters has been labeled as a major marine invasion
+the first invasive marine vertebrates established along the North
+Atlantic Caribbean coasts
+\citep{schofield_2009,schofield_2010,sabidoitza_2016}. Lionfish have
+been widely reported in coral reefs \citep{aguilarperera_2010}, but also
+in other habitats such as estuaries \citep{jud_2011}, mangroves
+\citep{barbour_2010}, hard-bottomed areas \citep{muoz_2011}, and
+mesophotic reefs \citep{andradibrown_2017}. Their presence in these
+waters has been labeled as a major marine invasion because they threaten
+local biodiversity, spread rapidly, and are difficult to manage
 \citep{hixon_2016}.
@@
 \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize
-\citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}. Their
-feeding behavior and high consumption rates can reduce recruitment
-\citep{albins_2008} and population sizes \citep{green_2012} of native
-reef-fish species, and further the endangerment of critically endangered
-reef fish \citep{rocha_2015}. (However, see \citet{hackerott_2017} for a
-case where there was no evidence that lionfish affected the density,
-richness, or community composition of prey fishes). Major efforts have
-been made to understand the possible impacts of the invasion by keeping
-track of its range through time \citep{schofield_2009,schofield_2010}
-and predicting invasion ranges under future climates
-\citep{grieve_2016}. By combining information from these disciplines,
-researchers have been able to predict the trophic impacts of lionfish
-\citep{ariasgonzalez_2011}, which can then be translated into
-ecosystem-level and economic impacts.
+\citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
+\citet{peake_2018} show that invasive lionfish prey on at least 167
+different species across on the tropical and temperate North Atlantic.
+Their feeding behavior and high consumption rates can reduce recruitment
+and population sizes of native reef-fish species, and can further
+endanger reef fish \citep{albins_2008, green_2012,rocha_2015}. (However,
+see \citet{hackerott_2017} for a case where there was no evidence that
+lionfish affected the density, richness, or community composition of
+prey fishes). Major efforts have been made to understand the possible
+impacts of the invasion by keeping track of its range through time
+\citep{schofield_2009,schofield_2010} and predicting invasion ranges
+under future climates \citep{grieve_2016}. By combining information from
+these disciplines, researchers have been able to predict the trophic
+impacts of lionfish \citep{ariasgonzalez_2011}, which can then be
+translated into ecosystem-level and economic impacts.
 
@@
 significantly reduce --but not quite eliminate-- lionfish abundances at
-local scales \citep{sandel_2015,chin_2016,deleon_2013}. The rapid
-recovery rates exhibited by lionfish \citep{barbour_2011} and the
-persistent populations in mesophotic coral ecosystems
-\citep{andradibrown_2017} --which can contribute with recruitment to
-shallow-water populations-- make of complete eradication through fishing
-effort an unlikely solution. However, further incentivizing its
-consumption might create a demand big enough to promote and sustain a
-stable fishery \citep{chin_2016}, which can reduce local abundances and
-control the invasion while providing alternative livelihoods.
+local scales \citep{sandel_2015,chin_2016,deleon_2013}. Complete
+eradication of lionfish through fishing is unlikely because of their
+rapid recovery rates and ongoing recruitment to shallow-water areas from
+their persistent populations in mesophotic coral ecosystems
+\citep{barbour_2011,andradibrown_2017}. However, further incentivizing
+its consumption might create a demand big enough to promote and sustain
+a stable fishery \citep{chin_2016}, which can reduce local abundances
+and control the invasion while providing alternative livelihoods.
 
 The feasibility of lionfish removal programs has been extensively
-evaluated through field
-observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and
-empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}. The
-latter approeach models changes in biomass in response to changes in
-mortality (\emph{i.e.} culling). In this case, biomass represents the
-sum of all fish's individual weight. The individual weight of an
-organism (Total Weight; TW) can be estimated from its Total Length (TL)
-using the allometric growth equation (\(TW = aTL^b\)). Parameters \(a\)
-and \(b\) for this equation exist for North Carolina
-\citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern
-Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican
-Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little
-Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire
-\citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa
-Rica \citep{sandel_2015}, but remain unavailable for the central Mexican
-Caribbean. The length-weight of a species can vary across regions as a
-response to biotic (\emph{e.g.} local food availability) and abiotic
-(\emph{e.g.} water temperature) conditions \citep{johnson_2016}. Thus,
-when using biomass-informed models or estimating weights from length
-observations, it is important to use site-specific parameters. This is
-especially important when research involves identifying the total
-biomass available for harvest by fishers \citep{chin_2016} or the
-efficacy of lionfish removals
-\citep{barbour_2011,morris_2011,johnston_2015}.
+evaluated through field observations
+\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical
+modeling \citep{barbour_2011,morris_2011,johnston_2015}. The latter
+approach models changes in biomass in response to changes in mortality
+(\emph{i.e.} culling). In this case, biomass represents the sum of all
+fish's individual weight. The individual weight of an organism can be
+estimated from its length using the allometric growth equation.
+Parameters for this equation exist for North Carolina, Northern and
+Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little
+Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain
+unavailable for the central Mexican Caribbean
+\citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+The length-weight of a species can vary across regions as a response to
+biotic (\emph{e.g.} local food availability) and abiotic (\emph{e.g.}
+water temperature) conditions \citep{johnson_2016}. Thus, when using
+biomass-informed models or estimating weights from length observations,
+it is important to use site-specific parameters. This is especially
+important when research involves identifying the total biomass available
+for harvest by fishers or the efficacy of lionfish removals
+\citep{barbour_2011,morris_2011,johnston_2015,chin_2016}.
 
@@
 range, and provides a new pair of parameters specific to the central
-Meixcan Caribbean. The results suggest there are important
-regional-scale variations in allometric growth patterns of lionfish. The
-observed differences highlight the importance of using site-specific
-parameters, especially when informing invasion management strategies.
+Meixcan Caribbean. Results suggest there are important regional-scale
+variations in allometric growth patterns of lionfish. The observed
+differences highlight the importance of using site-specific parameters,
+especially when informing invasion management strategies.
 
@@
 The main objective of this work was to compare allometric growth of
-lionfish throughout the invasion range. Allometric parameters were
+lionfish throughout their invasion range. Allometric parameters were
 retreived from scientific literature, and an additional pair of
@@
 Length-weight relationships (n = 15) identified in literature were
-obtained for the North Atlantic (n = 1, \citet{barbour_2011}), Gulf of
-Mexico (n = 7, \citet{aguilarperera_2016,fogg_2013,dahl_2014}), and
-Caribbean (n = 8,
-\citet{chin_2016,toledohernndez_2014,deleon_2013,edwards_2014,sabidoitza_2016,sandel_2015,darling_2011}).
-When available, information on sampling methods, sex differentiation,
-location, and depth ranges of each study was retrieved. Whenever gender
-was not specified, it was assumed that the results were presented for
-pooled genders. Locations with allometric parameters are shown in Figure
+obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and
+Caribbean (n = 8). Information on sampling methods, sex differentiation,
+location, and depth ranges of each study was retrieved when available.
+Studies were assumed to include both genders if gender was unspecified.
+Locations where allometric studies were performed are shown in Figure
 \ref{fig:map} and \ref{tab:all_params}.
@@
 \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:unnamed-chunk-1}\label{fig:map}Locations where
-allometric growth of lionfish (\emph{Pterois spp}) have been reported.
-Sizes indicate sample size of each study, colors indicate the b
-coefficient in Eq. \ref{eq:allometric}.}
+\caption{\label{fig:map}Locations where allometric growth parameters of
+lionfish (\emph{Pterois spp}) have been reported. Circle sizes indicate
+sample size from each study, colors indicate the \(b\) coefficient from
+Eq. \ref{eq:allometric}.}
 \end{figure}
@@
 Parameters from the central Mexican Caribbean were obtained from data
-collected in 10 sampling sites along the Central Mexican Caribbean coast
+collected in 10 sampling sites along the central Mexican Caribbean coast
 in 2010 (Table S1). Sampling locations included wall and carpet reefs at
@@
 collected using hand nets and numbered collection bottles. The use of
-hand nets prevented any weight loss due to bleeding and allowed a better
+hand nets prevented any weight loss due to bleeding and allowed better
 representation of small sizes by eliminating gear selectivity. Organisms
-were euthanized (via pithing) and Total Length (TL; mm) and Total Weight
-(TW; gr) were recorded before freezing organisms.
+were euthanized via pithing and Total Length (TL; mm) and Total Weight
+(TW; g) were recorded before freezing organisms.
 
@@
 
-Where \(TW\) is the Total Weight (gr), \(TL\) is the Total Length (mm),
-\(a\) is the ponderal index and \(b\) is the scaling exponent or
+Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
 allometric parameter. When \(b = 3\), it is said that the organism
-exhibits a perfect isometric growth. The dependent and independent
-variables were transformed via base-10 logarithms, thus the equation
-becomes:
+exhibits a perfect isometric growth. Transforming this equation via
+base-10 logarithms:
 
@@
 
-Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), \(m = b\), and
+Where \(Y = log_{10}(TW)\), \(m = b\), \(X = log_{10}(TL)\), and
 \(c = log_{10}(a)\). Since \(b = m\), we will only use \(b\) throughout
 the paper for simplicity. The coefficients (\(c\) and \(b\)) were
-estimated with an Ordinary Least Square Regression and
+estimated with an Ordinary Least Squares Regression and
 heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-Both coefficients were tested against the null hypothesis of no change
-(\emph{i.e.} \(H_0: c = 0\) and \(H_0: b = 0\)) and the null hypothesis
-of isometric growth (\(H_0: b = 3\)). Coefficients were tested with a
-two-tailed Student's t-test. The significance of the regression was
-corroborated with an F-test.
+The \(b\) coefficient was tested against the null hypothesis of
+isometric growth (\emph{i.e.} \(H_0: b = 3\)). Coefficients were tested
+with a two-tailed Student's t, and the significance of the regression
+was corroborated with an F-test.
 
-During the review process, some studies indistinctly used \(a\) to
-report either the ponderal index in \ref{eq:allometric} or the
-y-intercept (\(c\)) in \ref{eq:log-alo-trans}. Others reported their
-parameters as mm-to-gr conversions, but a rapid evaluation of such
-parameters indicated that they were estimated as cm-to-gr conversions.
-Here, all parameters are reported as TL(mm) to TW(gr) conversions. When
+Studies inconsistently defined a as either the ponderal index from Eq.
+\ref{eq:allometric} or the y-intercept (\(c\)) from Eq.
+\ref{eq:log-alo-trans}. Other studies incorrectly reported parameters as
+mm-to-g conversions when they were in fact cm-to-g conversions. Here,
+all parameters are reported as TL(mm) to TW(gr) conversions. When
 required, values from other studies were transformed for consistency.
@@
 length-weight relationships were used to calculate predicted weight from
-length observations of the organisms sampled from the Central Mexican
+length observations of the organisms sampled from the central Mexican
 Caribbean. Predicted weights were divided by the observed weights to
@@
 performed in R version 3.4.4 \citep{rcore_2018}. Raw data and code used
-in this work is available at dryad.org.
+in this work are available at dryad.org.
 
@@
 
-This section presents a new length-weight relationship for lionfish in
-the Central Mexican Caribbean region. A summary of length-weight
-relationship is provided, and a comparison of predicted-to-observed
-weight is included.
+The model adjusted to Eq. \ref{eq:log-alo-trans} estimated the
+coefficient values at \(b = 3.2347391\) and \(c = -5.4940866\)
+(\(R^2 = 0.977\), F(df = 1; 107) = 6928.67, \(p < 0.001\)). The
+allometric factor (\(b\)) was significantly different from the value of
+isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.001\)), indicating
+that lionfish present allometric growth. More information on model fit
+is presented in TableS2. The relationship between TL and TW is presented
+in Figure \ref{fig:l-w-carib}.
 
-The model adjusted to Eq. \ref{eq:log-alo-trans} estimated the
-coefficient values at \(b = 3.2347391\) and \(c = -5.4940866\). The
-intercept (\(c\)) and slope \((b)\) were significantly different from
-zero (\(t(107) = -66.17; p<0.001\) and \(t(107) = 83.24; p<0.001\),
-respectively), rejecting the null hypothesis of no change. Additionally,
-the allometric factor (\(b\)) was significantly different from the value
-of isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.001\)),
-indicating that lionfish present allometric growth. More information on
-model fit is presented in TableS2. The relationship between Total Length
-and Total Weight is presented in Figure \ref{fig:l-w-carib}.
-
-From the 11 peer-reviewed studies including information on growth
-parameters for \emph{P. volitans} and the additional calculated for the
-central Mexican Caribbean, 15 parameters were identified (Table
+From this study in the central Mexican Caribbean and the 11
+peer-reviewed studies that reported length-weight parameters for
+\emph{P. volitans} 15 parameters were identified (Table
 \ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies
 \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled
-parameters, while the rest presented pooled results. The smallest
-coefficient of determination was presented by \citet{chin_2016} with
-\(R^2 = 0.8715\), while \citet{sabidoitza_2016} reported the highest
-value at \(R^2 = 0.9907\). Reviewed studies presented information for
-organisms obtained at depths between 0.5 and 57 m. Three studies
-\citep{aguilarperera_2016,chin_2016,dahl_2014} explicitly stated that
-their organisms were sampled with pole spears. Five studies
-\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014}
-mentioned that some of their organisms were obtained with pole spears
-(or other type of harpoon), but also hand-held nets or fish traps. Two
-studies \citep{deleon_2013,darling_2011} did not specify how organisms
-were sampled. \citep{fogg_2013} stated the use spine-less weight in the
-length-weight relationship estimation.
+parameters, while the rest presented pooled results. Reviewed studies
+presented information for organisms obtained at depths between 0.5 and
+57 m. Three studies explicitly stated that their organisms were sampled
+with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014}, and
+five studies mentioned that some of their organisms were obtained with
+pole spears (or other type of harpoon) but also hand-held nets or fish
+traps
+\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014},
+and two studies did not specify how organisms were sampled
+\citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less
+weight in the length-weight relationship estimation.
 
@@
 There were significant differences in predicted-to-observed weight
-ratios estimated for each pair of parameters (F(15, 1728) = 38.26; p
-\textless{} 0.001). From all allometric parameters reviewed, those of
+ratios estimated for each pair of parameters (F(df = 15; 1728) = 38.26;
+p \textless{} 0.001). From all allometric parameters reviewed, those of
 \citet{edwards_2014} provided the lowest weight estimates, with an
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}\label{fig:l-w-carib}Length-weight
-relationship for 109 lionfish sampled in the Central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit,
-marginal plots represent the density distribution of each variable.}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
+\caption{\label{fig:l-w-carib}Length-weight relationship for 109
+lionfish sampled in the central Mexican Caribbean. Points indicate
+samples, solid line indicates curve of best fit, marginal plots
+represent the density distribution of each variable.}
 \end{figure}
@@
 
-\caption{\label{tab:unnamed-chunk-4}\label{tab:all_params}Summary of 13 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 16 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies if data is for pooled (B), females (F), or males (M), a = scaling parameter for Eq.
-1, c = y-intercept for Eq.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
+1 (presented in $\times 10^{-5}$), c = y-intercept for Eq.
 3, b = exponent or slope for Eq.
@@
 \centering
-\begin{tabular}[t]{lllrrll}
+\begin{tabular}[t]{llllrrll}
 \toprule
-Region & Sex & n & a & b & R2 & Reference\\
+Region & Sex & n & a & b & c & R\textasciicircum{}2 & Reference\\
 \midrule
-Caribbean & B & 458 & 3.64e-05 & 2.81 & - & Sandel et al., 2015\\
-Caribbean & B & 419 & 2.75e-05 & 2.85 & 0.8715 & Chin et al 2016\\
-Caribbean & B & 1450 & 2.28e-05 & 2.89 & 0.96 & de Leon et al., 2013\\
-Caribbean & B & 1887 & 3.00e-06 & 3.24 & 0.97 & Edwards et al., 2014\\
-Caribbean & B & - & 2.50e-06 & 3.29 & - & Darling et al., 2011\\
+Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
+Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
+Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
+Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
+Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
 \addlinespace
-Caribbean & B & 2143 & 5.20e-06 & 3.18 & 0.9907 & Sabido-Itza et al., 2016\\
-Caribbean & B & 227 & 8.00e-06 & 3.11 & 0.958 & Toledo-Hernández et al., 2014\\
-Caribbean & B & 109 & 3.20e-06 & 3.23 & 0.9766 & This study\\
-GoM & B & 934 & 2.10e-06 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
-GoM & B & 472 & 2.90e-06 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
+Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
+Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
+GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
+GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
 \addlinespace
-GoM & F & 67 & 1.20e-06 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & M & 59 & 4.20e-06 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & B & 582 & 1.40e-06 & 3.43 & 0.99 & Fogg et al., 2013\\
-GoM & M & 119 & 2.70e-06 & 3.31 & 0.97 & Fogg et al., 2013\\
-GoM & F & 115 & 6.80e-06 & 3.14 & 0.94 & Fogg et al., 2013\\
-NorthAtlantic & B & 774 & 2.89e-05 & 2.89 & - & Barbour et al 2011\\
+GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
+GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
+GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
+NorthAtlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al.,2011\\
 \bottomrule
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{\label{fig:unnamed-chunk-5}\label{fig:all_allo}Length-weight
-relationships (n = 16) for 11 studies and this study. Colors indicate
-studies from which the parameters were extracted. Solid lines indicate
-that the fit was performed for males and females pooled together. Dotted
-lines indicate that the regression was performed on females, and dashed
-lines indicate it was performed for males.}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{\label{fig:all_allo}Length-weight relationships (n = 16) for 11
+studies and this study. Colors indicate studies from which the
+parameters were extracted. Solid lines indicate that the fit was
+performed for males and females pooled together. Dotted lines indicate
+that the regression was performed on females, and dashed lines indicate
+it was performed for males.}
 \end{figure}
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:unnamed-chunk-6}\label{fig:bio_ratio}Violin plot showing
-the distribution of predicted to observed weight ratios for 16 pairs of
-allometric parameters. Red and blue circles indicate median and mean
-values, respectively. Like letters indicate values that do not differ
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\label{fig:bio_ratio}Violin plot showing the distribution of
+predicted to observed weight ratios for 16 pairs of allometric
+parameters. Red and blue circles indicate median and mean values,
+respectively. Like letters indicate values that do not differ
 significantly (Tukey's HSD; p \textless{} 0.05).}
@@
 Mexican Caribbean are provided. This compliments existing literature for
-other sites in the north (\emph{i.e.} Alacranes Reef
-\citep{aguilarperera_2016}) and South (Xcalak \citep{sabidoitza_2016})
-of the Mexican Caribbean. Additionally, the study identifies regional
-differences in length-weight relationships. Here, we focus the
-discussion on plausible causes of these differences.
+other sites in the Mexican Caribbean \citep{sabidoitza_2016}.
+Additionally, the study identifies regional differences in length-weight
+relationships.
 
 The length-weight coefficients estimated in this study were within the
-range identified by studies in other regions \ref{tab:all_params}.
-However, the ones presented here provide lower weight estimates for a
-same length. Until about TL = 200 mm, there are no appreciable
-differences between the parameters for organisms from the Mexican
-Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica
-\citep{chin_2016}. Yet, for larger organisms (TL \textgreater{} 270 mm)
-parameters from Costa Rica \citep{sandel_2015} and Bonaire
-\citep{deleon_2013} provide similar estimates to those from this study.
-Conversely, these same studies tend to estimate higher weights --as
-compared to the ones reported here-- for smaller organisms, likely due
-to the lack of small organisms in the samples used to estimate their
-parameters.
+range identified by studies in other regions (Table
+\ref{tab:all_params}). However, the ones presented here provide lower
+weight estimates for similar lenmgths. Until about TL = 200 mm, there
+are no appreciable differences between the parameters for organisms from
+the Mexican Caribbean and those for little Cayman \citep{edwards_2014}
+and Jamaica \citep{chin_2016}. Yet, for larger organisms (TL
+\textgreater{} 270 mm) parameters from Costa Rica \citep{sandel_2015}
+and Bonaire \citep{deleon_2013} provide similar estimates to those from
+this study. Conversely, these same studies tend to estimate higher
+weights --as compared to the ones reported here-- for smaller organisms,
+likely due to the lack of small organisms in the samples used to
+estimate their parameters.
 
@@
 estimates with parameters from the Gulf of Mexico and North-Western
-Atlantic tend to be higher than those from the Caribbean. This indicates
-that there are differences between lionfish across the invasion range.
-Similar regional variation has been reported for age-at-length
-relationships of this species across the invaded region
-\citep{fogg_2015} and compared to their native range
-\citep{pusack_2016}. These may be driven genetic differences or
+Atlantic tend to be higher than those from the Caribbean. Similar
+regional variation has been reported for age-at-length relationships of
+this species across the invaded region \citep{fogg_2015}, or when
+comparing populations from the invasion and native ranges
+\citep{pusack_2016}. These may be driven by genetic differences or
 organisms being exposed to distinct environmental conditions. For
@@
 lead to different usage of energy), or a combination of both. Future
-research should focus on teasing appart these and other possible
-explanations.
+research should focus on identifying which occurs here.
 
-The results presented in this paper can have major implications in
+The results presented in this paper can have major implications for
 management. Our results show that, for a given length, using one set of
-parameters or the other can result in a 3-fold increase in estimated
-weight. These becomes especially relevant when estimating biomass
+parameters or the other can result in a threefold increase in estimated
+weight. This becomes especially relevant when estimating biomass
 available for harvest, predicting effects on local ecosystems, or

### 2018-04-13 docs/Manuscript.Rmd
Added Sean's name to list of authors

@@
 title: "Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic"
-author: "Juan Carlos Villaseñor-Derbez"
+author: "Juan Carlos Villaseñor-Derbez, Sean Fitzgerald"
 institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."

### 2018-04-20 docs/Manuscript.tex
Added Sean's name to list of authors
Introduction changes, adding paper folder with some references

@@
 
-\author[1]{Juan Carlos Villaseñor-Derbez}
+\author[1]{Juan Carlos VillaseÃƒÂ±or-Derbez, Sean Fitzgerald}
 \affil[1]{Bren School of Environmental Sciences and Management, University of
 California Santa Barbara, Santa Barbara, California, U.S.}
-\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@bren.ucsb.edu}
+\corrauthor[1]{Juan Carlos VillaseÃƒÂ±or-Derbez, Sean Fitzgerald}{jvillasenor@bren.ucsb.edu}
 
@@
 \citet{peake_2018} show that invasive lionfish prey on at least 167
-different species across on the tropical and temperate North Atlantic.
+different species across the tropical and temperate North Atlantic.
 Their feeding behavior and high consumption rates can reduce recruitment
@@
 
-Seeking to reduce lionfish densities, governments and non-profit
-organizations have promoted removal programs and incentivized its
-consumption \citep{chin_2016}. In some cases, these have shown to
-significantly reduce --but not quite eliminate-- lionfish abundances at
-local scales \citep{sandel_2015,chin_2016,deleon_2013}. Complete
+Governments and non-profit organizations have sought to reduce lionfish
+densities through removal programs and incentivizing its consumption
+\citep{chin_2016}. In some cases, these have shown to significantly
+reduce --but not quite eliminate-- lionfish abundances at local scales
+\citep{sandel_2015,chin_2016,deleon_2013}. In addition, culling programs
+can help stabilize or grow native prey fish populations (Cote et al.
+2014 - \url{https://peerj.com/preprints/398v1.pdf}). Complete
 eradication of lionfish through fishing is unlikely because of their
@@
 their persistent populations in mesophotic coral ecosystems
-\citep{barbour_2011,andradibrown_2017}. However, further incentivizing
-its consumption might create a demand big enough to promote and sustain
-a stable fishery \citep{chin_2016}, which can reduce local abundances
-and control the invasion while providing alternative livelihoods.
+\citep{barbour_2011,andradibrown_2017}. However, promoting its
+consumption might create a level of demand capable of sustaining a
+stable fishery, which can help control invasive populations while
+providing alternative livelihoods \citep{chin_2016}.
 
-The feasibility of lionfish removal programs has been extensively
-evaluated through field observations
-\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical
-modeling \citep{barbour_2011,morris_2011,johnston_2015}. The latter
-approach models changes in biomass in response to changes in mortality
-(\emph{i.e.} culling). In this case, biomass represents the sum of all
-fish's individual weight. The individual weight of an organism can be
-estimated from its length using the allometric growth equation.
-Parameters for this equation exist for North Carolina, Northern and
-Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little
-Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain
-unavailable for the central Mexican Caribbean
+The feasibility \textbf{of establishing fisheries} (I think this is what
+we should focus on as our selling point - may mean you have fewer papers
+to cite but that's okay) through lionfish removal programs has been
+extensively evaluated through field observations and empirical modeling
+\citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
+One contributing factor to the success of many removal programs is the
+sedentary nature of adult lionfish (Jud \& Layman 2012 -
+\url{http://craiglaymanlab.com/wp-content/uploads/Jud-and-Layman-2012-JEMBE.pdf}).
+Culling programs are effective in reducing adult populations largely
+because lionfish exhibit high levels of site fidelity and rarely leave
+their home range in most cases (Fishelson 1997, Kochzius \& Blohm 2005,
+Cote et al. 2014). As a result of this sedentary behavior, lionfish are
+also likely to exhibit high levels of spatial variation in important
+life history characterstics such as growth or natural mortality rate
+(Hutchinson 2008, Wilson et al. 2012). The importance of considering
+spatial heterogeneity is well-documented in terms of assessing and
+managing sedentary species (Gunderson et al. 2008, Guan et al. 2013),
+and such variation should be accounted for when evaluating the
+feasibility of establishing lionfish fisheries as well.
+
+Empirical modeling efforts examining the feasibility of establishing
+fisheries for lionfish involve modeling changes in biomass in response
+to changes in mortality (\emph{i.e.} culling - \textbf{cite some of the
+papers from above paragraph}). In this case, biomass represents the sum
+of all individual fish weights. The individual weight (\emph{W}) of an
+organism can be estimated from its length using the allometric growth
+equation, \(W = aL^b\), where \emph{L} is an organism's length and
+\emph{a} and \emph{b} are constants \textbf{(I know it sems a little
+weird to put this in the intro, but since it's the whole crux of the
+paper I think it's okay - more details still follow later and it didn't
+take much space\ldots{})}. This length-weight relationship for any given
+species is an essential component of biomass-based modeling, and can
+vary across regions as a response to biotic (\emph{e.g.} local food
+availability) and abiotic (\emph{e.g.} water temperature) conditions
+\citep{johnson_2016}. Site-specific parameters are therefore necessary
+in order to obtain accurate biomass estimates in a given region,
+especially when research involves identifying the total biomass
+available for harvest by fishers
+\citep{barbour_2011,morris_2011,johnston_2015,chin_2016}. Equation
+parameters for lionfish exist for North Carolina, Northern and Southern
+Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman,
+Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable
+for the central Mexican Caribbean
 \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
-The length-weight of a species can vary across regions as a response to
-biotic (\emph{e.g.} local food availability) and abiotic (\emph{e.g.}
-water temperature) conditions \citep{johnson_2016}. Thus, when using
-biomass-informed models or estimating weights from length observations,
-it is important to use site-specific parameters. This is especially
-important when research involves identifying the total biomass available
-for harvest by fishers or the efficacy of lionfish removals
-\citep{barbour_2011,morris_2011,johnston_2015,chin_2016}.
 
-This study reviews lionfish allometric growth throughout the invasion
-range, and provides a new pair of parameters specific to the central
-Meixcan Caribbean. Results suggest there are important regional-scale
-variations in allometric growth patterns of lionfish. The observed
-differences highlight the importance of using site-specific parameters,
-especially when informing invasion management strategies.
+Here, we review lionfish allometric growth parameters throughout its
+invasion range and examine spatial differences in the equation
+constants. We also provide a new pair of parameters specific to the
+central Meixcan Caribbean. Results suggest there are important
+regional-scale variations in allometric growth patterns of lionfish, and
+these differences highlight the importance of using site-specific
+parameters when developing or informing invasion management strategies.
 

### 2018-04-20 docs/Manuscript.Rmd
Fixed YAML mettadata with name and abstract

--- 2018-04-12 docs/Manuscript.Rmd
@@
 ---
-title: "Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic"
-author: "Juan Carlos Villaseñor-Derbez"
+title: Invasive lionfish present region-wide variation of allometric growth in the
+  Western Atlantic
+author: "Juan Carlos Villaseñor-Derbez$^1$, Sean Fitzgerald"
+header-includes:
+- \usepackage{float}
+- \floatplacement{figure}{H}
+output:
+  pdf_document:
+    keep_tex: yes
+    number_sections: no
+    template: peerj_template.tex
 institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
@@
 This highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters ($a = 3.2056\\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region.
+This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region.
 These findings can have major implications in management, especially when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs."
-header-includes: #allows you to add in your own Latex packages
-- \usepackage{float} #use the 'float' package
-- \floatplacement{figure}{H} #make every figure with caption = h
-output:
-  pdf_document:
-    keep_tex: yes
-    template: peerj_template.tex
-    number_sections: no
+keywords: "A, B, C"
 ---
@@
 A substantial amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
-\citet{peake_2018} show that invasive lionfish prey on at least 167 different species across on the tropical and temperate North Atlantic.
+\citet{peake_2018} show that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
 Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{albins_2008, green_2012,rocha_2015}.
@@
 
-Seeking to reduce lionfish densities, governments and non-profit organizations have promoted removal programs and incentivized its consumption \citep{chin_2016}.
+Governments and non-profit organizations have sought to reduce lionfish densities through removal programs and incentivizing its consumption \citep{chin_2016}.
 In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
+In addition, culling programs can help stabilize or grow native prey fish populations (Cote et al.
+2014 - https://peerj.com/preprints/398v1.pdf).
 Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from their persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
-However, further incentivizing its consumption might create a demand big enough to promote and sustain a stable fishery \citep{chin_2016}, which can reduce local abundances and control the invasion while providing alternative livelihoods.
+However, promoting its consumption might create a level of demand capable of sustaining a stable fishery, which can help control invasive populations while providing alternative livelihoods \citep{chin_2016}.
 
-The feasibility of lionfish removal programs has been extensively evaluated through field observations \citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}.
-The latter approach models changes in biomass in response to changes in mortality (*i.e.* culling).
-In this case, biomass represents the sum of all fish's individual weight.
-The individual weight of an organism can be estimated from its length using the allometric growth equation.
-Parameters for this equation exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
-The length-weight of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Thus, when using biomass-informed models or estimating weights from length observations, it is important to use site-specific parameters.
-This is especially important when research involves identifying the total biomass available for harvest by fishers or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015,chin_2016}.
+The feasibility **of establishing fisheries** (I think this is what we should focus on as our selling point - may mean you have fewer papers to cite but that's okay) through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
+One contributing factor to the success of many removal programs is the sedentary nature of adult lionfish (Jud & Layman 2012 - http://craiglaymanlab.com/wp-content/uploads/Jud-and-Layman-2012-JEMBE.pdf).
+Culling programs are effective in reducing adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range in most cases (Fishelson 1997, Kochzius & Blohm 2005, Cote et al.
+2014).
+As a result of this sedentary behavior, lionfish are also likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rate (Hutchinson 2008, Wilson et al.
+2012).
+The importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species (Gunderson et al.
+2008, Guan et al.
+2013), and such variation should be accounted for when evaluating the feasibility of establishing lionfish fisheries as well.
 
-This study reviews lionfish allometric growth throughout the invasion range, and provides a new pair of parameters specific to the central Meixcan Caribbean.
-Results suggest there are important regional-scale variations in allometric growth patterns of lionfish.
-The observed differences highlight the importance of using site-specific parameters, especially when informing invasion management strategies.
+Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling - **cite some of the papers from above paragraph**).
+In this case, biomass represents the sum of all individual fish weights.
+The individual weight (*W*) of an organism can be estimated from its length using the allometric growth equation, $W = aL^b$, where *L* is an organism's length and *a* and *b* are constants **(I know it sems a little weird to put this in the intro, but since it's the whole crux of the paper I think it's okay - more details still follow later and it didn't take much space...)**.
+This length-weight relationship for any given species is an essential component of biomass-based modeling, and can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
+Site-specific parameters are therefore necessary in order to obtain accurate biomass estimates in a given region, especially when research involves identifying the total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016}.
+Equation parameters for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
 
-<!-- make this last paragraph a bit longer to talk about literature on spatial differences in fish populations -->
+Here, we review lionfish allometric growth parameters throughout its invasion range and examine spatial differences in the equation constants.
+We also provide a new pair of parameters specific to the central Meixcan Caribbean.
+Results suggest there are important regional-scale variations in allometric growth patterns of lionfish, and these differences highlight the importance of using site-specific parameters when developing or informing invasion management strategies.
 

### 2018-04-20 docs/Manuscript.Rmd
Commented cryptic, unused e1017 package

@@
   # library(colorRamps)
-  library(e1071)
+  # library(e1071)
   library(stringr)

### 2018-04-20 docs/Manuscript.Rmd
Added references by Sean

@@
 In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
-In addition, culling programs can help stabilize or grow native prey fish populations (Cote et al.
-2014 - https://peerj.com/preprints/398v1.pdf).
+In addition, culling programs can help stabilize or grow native prey fish populations \citep{cote_2014}.
 Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from their persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
@@
 
-The feasibility **of establishing fisheries** (I think this is what we should focus on as our selling point - may mean you have fewer papers to cite but that's okay) through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
-One contributing factor to the success of many removal programs is the sedentary nature of adult lionfish (Jud & Layman 2012 - http://craiglaymanlab.com/wp-content/uploads/Jud-and-Layman-2012-JEMBE.pdf).
-Culling programs are effective in reducing adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range in most cases (Fishelson 1997, Kochzius & Blohm 2005, Cote et al.
-2014).
-As a result of this sedentary behavior, lionfish are also likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rate (Hutchinson 2008, Wilson et al.
-2012).
-The importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species (Gunderson et al.
-2008, Guan et al.
-2013), and such variation should be accounted for when evaluating the feasibility of establishing lionfish fisheries as well.
+The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
+One contributing factor to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}.
+Culling programs are effective in reducing adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005}.
+As a result of this sedentary behavior, lionfish are also likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rate \citep{hutchinson_2008,wilson_2012}.
+The importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,guan_2013}, and such variation should be accounted for when evaluating the feasibility of establishing lionfish fisheries as well.
 
-Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling - **cite some of the papers from above paragraph**).
+Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling \citep{cote_2014,barbour_2011,andradibrown_2017}).
 In this case, biomass represents the sum of all individual fish weights.
-The individual weight (*W*) of an organism can be estimated from its length using the allometric growth equation, $W = aL^b$, where *L* is an organism's length and *a* and *b* are constants **(I know it sems a little weird to put this in the intro, but since it's the whole crux of the paper I think it's okay - more details still follow later and it didn't take much space...)**.
+The individual weight ($W$) of an organism can be estimated from its length using the allometric growth equation, $W = aL^b$, where $L$ is an organism's length and $a$ and $b$ are constants.
 This length-weight relationship for any given species is an essential component of biomass-based modeling, and can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.

### 2018-04-20 docs/Manuscript.Rmd
Added tag to Table 1
Deleted code that had been commented, no longer needed

@@
 Studies were assumed to include both genders if gender was unspecified.
-Locations where allometric studies were performed are shown in Figure \ref{fig:map} and \ref{tab:all_params}.
+Locations where allometric studies were performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
 
-\clearpage
+<!-- \clearpage -->
 
@@
         panel.grid.major = element_line(colour = "transparent")) +
-  # guides(colorbar = guide_legend(order = 0),
-  #        size = guide_legend(order = 1,
-  #                            direction = "horizontal",
-  #                            title.position = "top")) +
   lims(x = c(-100, -60), y = c(9, 36)) +

### 2018-04-20 docs/Manuscript.Rmd
Changed geom_text to geom_annotate to have a better annotation of the equation

@@
 get_eqn <- function(model){
-  substitute(italic(TW) == a %*% italic(TL)^b,
-             list(a = format(10^coef(model)[1], digits = 3),
+  substitute(italic(TW) == a %*% "10"^"-6" ~ italic(TL)^b,
+             list(a = "3.2",
                   b = format(coef(model)[2], digits = 3))) %>% 
@@
   geom_smooth(method = "lm", formula = y ~ I(a*x^b), color = "black", se = F) +
-  geom_text(aes(x = 120, y = 390), label = get_eqn(model), parse = T, size = 4, family="Times", face="italic") +
-  geom_text(aes(x = 120, y = 350), label = get_rsq(model), parse = T, size = 4, family="Times", face="italic")
+  annotate(geom = "text",
+            x = 120, y = 390,
+            label = get_eqn(model),
+            parse = T,
+            size = 4,
+            family="Times",
+            face="italic") +
+  annotate(geom = "text",
+            x = 120, y = 350, 
+            label = get_rsq(model),
+            parse = T,
+            size = 4,
+            family="Times",
+            face="italic")
 

### 2018-04-20 docs/Manuscript.tex
New manuscript ready

@@
 
-\author[1]{Juan Carlos VillaseÃƒÂ±or-Derbez, Sean Fitzgerald}
+\author[1]{Juan Carlos Villaseñor-Derbez\(^1\), Sean Fitzgerald}
 \affil[1]{Bren School of Environmental Sciences and Management, University of
 California Santa Barbara, Santa Barbara, California, U.S.}
-\corrauthor[1]{Juan Carlos VillaseÃƒÂ±or-Derbez, Sean Fitzgerald}{jvillasenor@bren.ucsb.edu}
+\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@bren.ucsb.edu}
 
-% \keywords{Keyword1, Keyword2, Keyword3}
+% \keywords{A, B, C}
 
@@
 observations. This study also reports a new pair of length-weight
-parameters (\(a = 3.2056\times 10^{-6}; b = 3.235\)) for organisms
+parameters (\(a = 3.2056 imes 10^{-6}; b = 3.235\)) for organisms
 sampled in the central Mexican Caribbean region. These findings can have
@@
 \citep{sandel_2015,chin_2016,deleon_2013}. In addition, culling programs
-can help stabilize or grow native prey fish populations (Cote et al.
-2014 - \url{https://peerj.com/preprints/398v1.pdf}). Complete
-eradication of lionfish through fishing is unlikely because of their
-rapid recovery rates and ongoing recruitment to shallow-water areas from
-their persistent populations in mesophotic coral ecosystems
-\citep{barbour_2011,andradibrown_2017}. However, promoting its
-consumption might create a level of demand capable of sustaining a
-stable fishery, which can help control invasive populations while
-providing alternative livelihoods \citep{chin_2016}.
+can help stabilize or grow native prey fish populations
+\citep{cote_2014}. Complete eradication of lionfish through fishing is
+unlikely because of their rapid recovery rates and ongoing recruitment
+to shallow-water areas from their persistent populations in mesophotic
+coral ecosystems \citep{barbour_2011,andradibrown_2017}. However,
+promoting its consumption might create a level of demand capable of
+sustaining a stable fishery, which can help control invasive populations
+while providing alternative livelihoods \citep{chin_2016}.
 
-The feasibility \textbf{of establishing fisheries} (I think this is what
-we should focus on as our selling point - may mean you have fewer papers
-to cite but that's okay) through lionfish removal programs has been
-extensively evaluated through field observations and empirical modeling
+The feasibility of establishing fisheries through lionfish removal
+programs has been extensively evaluated through field observations and
+empirical modeling
 \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
 One contributing factor to the success of many removal programs is the
-sedentary nature of adult lionfish (Jud \& Layman 2012 -
-\url{http://craiglaymanlab.com/wp-content/uploads/Jud-and-Layman-2012-JEMBE.pdf}).
-Culling programs are effective in reducing adult populations largely
-because lionfish exhibit high levels of site fidelity and rarely leave
-their home range in most cases (Fishelson 1997, Kochzius \& Blohm 2005,
-Cote et al. 2014). As a result of this sedentary behavior, lionfish are
-also likely to exhibit high levels of spatial variation in important
-life history characterstics such as growth or natural mortality rate
-(Hutchinson 2008, Wilson et al. 2012). The importance of considering
+sedentary nature of adult lionfish \citep{jud_2012}. Culling programs
+are effective in reducing adult populations largely because lionfish
+exhibit high levels of site fidelity and rarely leave their home range
+in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005}. As a
+result of this sedentary behavior, lionfish are also likely to exhibit
+high levels of spatial variation in important life history
+characterstics such as growth or natural mortality rate
+\citep{hutchinson_2008,wilson_2012}. The importance of considering
 spatial heterogeneity is well-documented in terms of assessing and
-managing sedentary species (Gunderson et al. 2008, Guan et al. 2013),
-and such variation should be accounted for when evaluating the
-feasibility of establishing lionfish fisheries as well.
+managing sedentary species \citep{gunderson_2008,guan_2013}, and such
+variation should be accounted for when evaluating the feasibility of
+establishing lionfish fisheries as well.
 
@@
 fisheries for lionfish involve modeling changes in biomass in response
-to changes in mortality (\emph{i.e.} culling - \textbf{cite some of the
-papers from above paragraph}). In this case, biomass represents the sum
-of all individual fish weights. The individual weight (\emph{W}) of an
-organism can be estimated from its length using the allometric growth
-equation, \(W = aL^b\), where \emph{L} is an organism's length and
-\emph{a} and \emph{b} are constants \textbf{(I know it sems a little
-weird to put this in the intro, but since it's the whole crux of the
-paper I think it's okay - more details still follow later and it didn't
-take much space\ldots{})}. This length-weight relationship for any given
-species is an essential component of biomass-based modeling, and can
-vary across regions as a response to biotic (\emph{e.g.} local food
-availability) and abiotic (\emph{e.g.} water temperature) conditions
-\citep{johnson_2016}. Site-specific parameters are therefore necessary
-in order to obtain accurate biomass estimates in a given region,
-especially when research involves identifying the total biomass
-available for harvest by fishers
+to changes in mortality (\emph{i.e.} culling
+\citep{cote_2014,barbour_2011,andradibrown_2017}). In this case, biomass
+represents the sum of all individual fish weights. The individual weight
+(\(W\)) of an organism can be estimated from its length using the
+allometric growth equation, \(W = aL^b\), where \(L\) is an organism's
+length and \(a\) and \(b\) are constants. This length-weight
+relationship for any given species is an essential component of
+biomass-based modeling, and can vary across regions as a response to
+biotic (\emph{e.g.} local food availability) and abiotic (\emph{e.g.}
+water temperature) conditions \citep{johnson_2016}. Site-specific
+parameters are therefore necessary in order to obtain accurate biomass
+estimates in a given region, especially when research involves
+identifying the total biomass available for harvest by fishers
 \citep{barbour_2011,morris_2011,johnston_2015,chin_2016}. Equation
@@
 Locations where allometric studies were performed are shown in Figure
-\ref{fig:map} and \ref{tab:all_params}.
-
-\clearpage
+\ref{fig:map} and Table \ref{tab:all_params}.
 

### 2018-05-09 docs/Manuscript.Rmd
Updated numbers across manuscript and added more discussion

@@
 This work compares length-weight relationships of the invasive lionfish through the invasion range.
-A review of 15 length-weight relationships reported in 11 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length.
+A review of 17 length-weight relationships reported in 12 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length.
 The reviewed parameters indicate that, for the same length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf of Mexico.
@@
 Site-specific parameters are therefore necessary in order to obtain accurate biomass estimates in a given region, especially when research involves identifying the total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016}.
-Equation parameters for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+Equation parameters for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
 
@@
 Results suggest there are important regional-scale variations in allometric growth patterns of lionfish, and these differences highlight the importance of using site-specific parameters when developing or informing invasion management strategies.
+
+\clearpage
 
@@
 
-Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 8).
+Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 10).
 Information on sampling methods, sex differentiation, location, and depth ranges of each study was retrieved when available.
@@
 Locations where allometric studies were performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
-
-<!-- \clearpage -->
 
@@
 
-Studies inconsistently defined a as either the ponderal index from Eq.
+Studies inconsistently defined $a$ as either the ponderal index from Eq.
 \ref{eq:allometric} or the y-intercept ($c$) from Eq.
@@
 
-Since uncertainty around estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships.
-Instead, the 16 length-weight relationships were used to calculate predicted weight from length observations of the organisms sampled from the central Mexican Caribbean.
+We compare observed TW to TW estimated with the 18 length-weight relationsips to quantify the extent to which using *ex situ* this leads to over- or underestimation.
 Predicted weights were divided by the observed weights to obtain a ratio.
 Difference in mean weight ratios across studies were tested with a one-way Analysis of Variance (ANOVA).
-All analyses were performed in R version 3.4.4 \citep{rcore_2018}.
+All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
 Raw data and code used in this work are available at dryad.org.
@@
 
-a <- coefficients(model)[[1]]
+c <- coefficients(model)[[1]]
 b <- coefficients(model)[[2]]
@@
 Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
-Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
+Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
 \citet{fogg_2013} use spine-less weight in the length-weight relationship estimation.
@@
 There were significant differences in predicted-to-observed weight ratios estimated for each pair of parameters (F(df = 15; 1728) = 38.26; p < 0.001).
-From all allometric parameters reviewed, those of \citet{edwards_2014} provided the lowest weight estimates, with an predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Edwards") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Edwards") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-On the other hand,\citet{barbour_2011} yielded the highest weight estimates, with a mean ($\pm$ SD) predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
-Predicted-to-observed weight ratios and groups identified by Tukey's HSD ($\alpha = 0.05$) are presented in Figure \ref{fig:bio_ratio}.
+From all allometric parameters reviewed, those of \citet{sabidoitz_2016} in Banco Chinchorro, (Caribbean) provided the lowest weight estimates, with a predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
+On the other hand, \citet{barbour_2011} in the Northern Atlantic yielded the highest weight estimates, with a mean ($\pm$ SD) predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
+Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
 
@@
   substitute(italic(TW) == a %*% "10"^"-6" ~ italic(TL)^b,
-             list(a = "3.2",
-                  b = format(coef(model)[2], digits = 3))) %>% 
+             list(a = "3.2056",
+                  b = "3.2347")) %>% 
+    as.expression() %>% 
+    as.character()
+}
+
+get_eqn2 <- function(model){
+  substitute(italic(log[10](TW)) == b %*% italic(log[10](TL)) ~ a,
+             list(a = "-5.4940",
+                  b = "3.2347")) %>% 
     as.expression() %>% 
@@
   substitute(italic(R)^2~"="~r2,
-             list(r2 = format(summary(model)$r.squared, digits = 3))) %>% 
+             list(r2 = formatC(summary(model)$r.squared, digits = 4))) %>% 
     as.expression() %>% 
@@
 ```{r, fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, solid line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
+Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
 
@@
   theme(text=element_text(family = "Times")) +
-  geom_smooth(method = "lm", formula = y ~ I(a*x^b), color = "black", se = F) +
+  geom_smooth(method = "lm", formula = y ~ I(c*x^b), se = F, color = "black", linetype = "dashed") +
   annotate(geom = "text",
@@
             x = 120, y = 350,
+            label = get_eqn2(model),
+            parse = T,
+            size = 4,
+            family="Times",
+            face="italic") +
+  annotate(geom = "text",
+            x = 120, y = 310, 
             label = get_rsq(model),
@@
                booktabs = T, 
-               col.names = c("Region", "Sex", "n", "a", "b", "c", "R^2", "Reference"),
-               caption = "\\label{tab:all_params}Summary of 16 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+               col.names = c("Region", "Sex", "n", "a", "b", "c", "$R^2$", "Reference"),
+               caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
@@
 
-```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 16) for 11 studies and this study.
+```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
 Colors indicate studies from which the parameters were extracted.
 Solid lines indicate that the fit was performed for males and females pooled together.
-Dotted lines indicate that the regression was performed on females, and dashed lines indicate it was performed for males."}
+Dotted lines indicate that the regression was performed on females, and dashed lines indicate it was performed for males.
+The dashed black line represents the relationship estimated in this study."}
 
 review %>% 
+  filter(!Study == "This study") %>% 
   mutate(Length = list(seq(1, 400))) %>% 
@@
   mutate(Weight = a*(Length^b),
-         this = ifelse(Study == "This study", T, F)) %>%
-  ggplot(aes(x = Length, y = Weight, color = Study, linetype = Gender)) +
-  # geom_point(aes(x = Length, y = Weight2), color = "black", size = 1) +
-  geom_line(aes(size = this)) +
+         This = 10^(coefficients(model)[1] + coefficients(model)[2]*log10(Length))) %>%
+  group_by(Length) %>% 
+  mutate(min = min(Weight),
+         max = max(Weight)) %>% 
+  ungroup() %>% 
+  ggplot(aes(x = Length)) +
+  geom_line(aes(y = Weight, color = Study, linetype = Gender, group = Study_id), size = 1) +
+  # geom_ribbon(aes(ymin = min, ymax = max), color = "gray", alpha = 0.1) +
+  geom_line(aes(y = This), size = 1.2, color = "black", linetype = "dashed") +
   labs(x = "Total length (mm)", y = "Total Weight (gr)") +
@@
         legend.box = "horizontal",
-        legend.text = element_text(size = 10),
+        legend.text = element_text(size = 9),
         legend.title = element_text(size = 10)) +
@@
 
-```{r, fig.height = 3.5, fig.cap = "\\label{fig:bio_ratio}Violin plot showing the distribution of predicted to observed weight ratios for 16 pairs of allometric parameters.
+```{r, fig.height = 4.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot showing the distribution of predicted to observed weight ratios for 18 pairs of allometric parameters.
 Red and blue circles indicate median and mean values, respectively.
@@
 Predicted_biomass %>% 
-  mutate(Study = paste0(Study, " (", Gender, ")")) %>%
-  transform(Study= reorder(Study, -Biomass_ratio)) %>%
+  mutate(Study = paste0(Study, " (", Gender_site, ")")) %>%
+  transform(Study = reorder(Study, -Biomass_ratio),
+            Study_id = reorder(Study_id, -Biomass_ratio)) %>%
   rename(Sex = Gender) %>% 
-  ggplot(aes(x = Study, y = Biomass_ratio)) +
+  ggplot(aes(x = Study, y = Biomass_ratio, group = Study_id)) +
   geom_violin(aes(fill = Sex), alpha = 0.8) +
@@
   theme(text = element_text(family = "Times"),
-        legend.justification=c(1, 1),
-        legend.position=c(-0.85, 1),
+        legend.position = "top",
+        legend.text = element_text(size = 10),
         legend.background = element_rect(fill = "transparent"),
@@
 
+\clearpage
+
 \section*{Discussion}
 
-A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided.
-This compliments existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016}.
+A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided, complimenting existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016,sabidoitz_2016}.
 Additionally, the study identifies regional differences in length-weight relationships.
@@
 Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic tend to be higher than those from the Caribbean.
-Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015}, or when comparing populations from the invasion and native ranges \citep{pusack_2016}.
+Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015,edwards_2014}, or when comparing populations from the invasion and native ranges \citep{pusack_2016}.
 These may be driven by genetic differences or organisms being exposed to distinct environmental conditions.
-For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_201}.
+For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_2011}.
 Alternatively, \citet{fogg_2015} suggest that differences observed in age-at-length "may bemore related to climate rather than other biological and ecological factors".
@@
 Our results show that, for a given length, using one set of parameters or the other can result in a threefold increase in estimated weight.
+Using site-specific values provides a more accurate estimate of fish biomass.
 This becomes especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
-Using site-specific values provides a more accurate estimate of fish biomass.
+\citet{edwards_2014} simulated lionfish culling using parameters from North Carolina and Little Cayman, and identify that the difference in time required for the population to recover to 90% of its initial biomass after removals cease was of up to four years.
 Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results.

### 2018-05-09 docs/Manuscript.tex
Updated numbers across manuscript and added more discussion

@@
 This work compares length-weight relationships of the invasive lionfish
-through the invasion range. A review of 15 length-weight relationships
-reported in 11 peer-reviewed studies shows that lionfish exhibit spatial
+through the invasion range. A review of 17 length-weight relationships
+reported in 12 peer-reviewed studies shows that lionfish exhibit spatial
 variation in weight-at-length. The reviewed parameters indicate that,
@@
 for the central Mexican Caribbean
-\citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+\citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
 
@@
 
+\clearpage
+
 \section*{Materials and Methods}
@@
 
-Length-weight relationships (n = 15) identified in literature were
+Length-weight relationships (n = 17) identified in literature were
 obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and
-Caribbean (n = 8). Information on sampling methods, sex differentiation,
-location, and depth ranges of each study was retrieved when available.
-Studies were assumed to include both genders if gender was unspecified.
-Locations where allometric studies were performed are shown in Figure
-\ref{fig:map} and Table \ref{tab:all_params}.
+Caribbean (n = 10). Information on sampling methods, sex
+differentiation, location, and depth ranges of each study was retrieved
+when available. Studies were assumed to include both genders if gender
+was unspecified. Locations where allometric studies were performed are
+shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
 
@@
 
-Studies inconsistently defined a as either the ponderal index from Eq.
-\ref{eq:allometric} or the y-intercept (\(c\)) from Eq.
+Studies inconsistently defined \(a\) as either the ponderal index from
+Eq. \ref{eq:allometric} or the y-intercept (\(c\)) from Eq.
 \ref{eq:log-alo-trans}. Other studies incorrectly reported parameters as
@@
 
-Since uncertainty around estimated relationships was not reported in
-some of the reviewed studies, it was not possible to test for
-statistical differences between relationships. Instead, the 16
-length-weight relationships were used to calculate predicted weight from
-length observations of the organisms sampled from the central Mexican
-Caribbean. Predicted weights were divided by the observed weights to
-obtain a ratio. Difference in mean weight ratios across studies were
-tested with a one-way Analysis of Variance (ANOVA). All analyses were
-performed in R version 3.4.4 \citep{rcore_2018}. Raw data and code used
-in this work are available at dryad.org.
+We compare observed TW to TW estimated with the 18 length-weight
+relationsips to quantify the extent to which using \emph{ex situ} this
+leads to over- or underestimation. Predicted weights were divided by the
+observed weights to obtain a ratio. Difference in mean weight ratios
+across studies were tested with a one-way Analysis of Variance (ANOVA).
+All analyses were performed in R version 3.5.0 \citep{rcore_2018}. Raw
+data and code used in this work are available at dryad.org.
 
@@
 
-From this study in the central Mexican Caribbean and the 11
+From this study in the central Mexican Caribbean and the 12
 peer-reviewed studies that reported length-weight parameters for
-\emph{P. volitans} 15 parameters were identified (Table
+\emph{P. volitans} 17 parameters were identified (Table
 \ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies
@@
 57 m. Three studies explicitly stated that their organisms were sampled
-with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014}, and
-five studies mentioned that some of their organisms were obtained with
-pole spears (or other type of harpoon) but also hand-held nets or fish
-traps
-\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,toledohernndez_2014},
+with pole spears
+\citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five
+studies mentioned that some of their organisms were obtained with pole
+spears (or other type of harpoon) but also hand-held nets or fish traps
+\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014},
 and two studies did not specify how organisms were sampled
@@
 parameters from models for pooled genders with a mean \(\pm\) standard
-deviation value of \(b = 3.13 \pm 0.22\). In the case of the ponderal
+deviation value of \(b = 3.14 \pm 0.20\). In the case of the ponderal
 index (\(a\)) and its \(log_{10}\) transformation (\(c\)), values were
@@
 p \textless{} 0.001). From all allometric parameters reviewed, those of
-\citet{edwards_2014} provided the lowest weight estimates, with an
-predicted-to-observed weight ratio of 0.98 \(\pm\) 0.23 (mean \(\pm\)
-SD). On the other hand,\citet{barbour_2011} yielded the highest weight
+\citet{sabidoitz_2016} in Banco Chinchorro, (Caribbean) provided the
+lowest weight estimates, with a predicted-to-observed weight ratio of
+0.80 \(\pm\) 0.19 (mean \(\pm\) SD). On the other hand,
+\citet{barbour_2011} in the Northern Atlantic yielded the highest weight
 estimates, with a mean (\(\pm\) SD) predicted-to-observed weight ratio
-of 1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios and groups
-identified by Tukey's HSD (\(\alpha = 0.05\)) are presented in Figure
-\ref{fig:bio_ratio}.
+of 1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios are presented
+in Figure \ref{fig:bio_ratio}.
 
@@
 lionfish sampled in the central Mexican Caribbean. Points indicate
-samples, solid line indicates curve of best fit, marginal plots
+samples, dashed black line indicates curve of best fit, marginal plots
 represent the density distribution of each variable.}
@@
 
-\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 16 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
@@
 \toprule
-Region & Sex & n & a & b & c & R\textasciicircum{}2 & Reference\\
+Region & Sex & n & a & b & c & \$R\textasciicircum{}2\$ & Reference\\
 \midrule
@@
 Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
+Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
+Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
 Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
+\addlinespace
 GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
 GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-\addlinespace
 GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
@@
 GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
+\addlinespace
 GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
@@
 \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:all_allo}Length-weight relationships (n = 16) for 11
+\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
 studies and this study. Colors indicate studies from which the
@@
 that the regression was performed on females, and dashed lines indicate
-it was performed for males.}
+it was performed for males. The dashed black line represents the
+relationship estimated in this study.}
 \end{figure}
@@
 \caption{\label{fig:bio_ratio}Violin plot showing the distribution of
-predicted to observed weight ratios for 16 pairs of allometric
+predicted to observed weight ratios for 18 pairs of allometric
 parameters. Red and blue circles indicate median and mean values,
@@
 
+\clearpage
+
 \section*{Discussion}
@@
 A new pair of allometric growth parameters for lionfish in the central
-Mexican Caribbean are provided. This compliments existing literature for
-other sites in the Mexican Caribbean \citep{sabidoitza_2016}.
-Additionally, the study identifies regional differences in length-weight
-relationships.
+Mexican Caribbean are provided, complimenting existing literature for
+other sites in the Mexican Caribbean
+\citep{sabidoitza_2016,sabidoitz_2016}. Additionally, the study
+identifies regional differences in length-weight relationships.
 
@@
 regional variation has been reported for age-at-length relationships of
-this species across the invaded region \citep{fogg_2015}, or when
-comparing populations from the invasion and native ranges
+this species across the invaded region \citep{fogg_2015,edwards_2014},
+or when comparing populations from the invasion and native ranges
 \citep{pusack_2016}. These may be driven by genetic differences or
@@
 groups, identified as the ``Caribbean group'' and ``Northern Group''
-\citep{betancurr_201}. Alternatively, \citet{fogg_2015} suggest that
+\citep{betancurr_2011}. Alternatively, \citet{fogg_2015} suggest that
 differences observed in age-at-length ``may bemore related to climate
@@
 parameters or the other can result in a threefold increase in estimated
-weight. This becomes especially relevant when estimating biomass
+weight. Using site-specific values provides a more accurate estimate of
+fish biomass. This becomes especially relevant when estimating biomass
 available for harvest, predicting effects on local ecosystems, or
-evaluating the effectiveness of removal programs. Using site-specific
-values provides a more accurate estimate of fish biomass. Future
-research should try to use, to the extent possible, parameters
-calculated for their region, or use different parameters to provide
-upper and lower bounds in their results. At the same time, this
-highlights the need for more basic research that furthers our
-understanding of lionfish biology. To better manage the invasion, we
-must perform research that can describe biologically important
-information of lionfish throughout its invasion range
+evaluating the effectiveness of removal programs. \citet{edwards_2014}
+simulated lionfish culling using parameters from North Carolina and
+Little Cayman, and identify that the difference in time required for the
+population to recover to 90\% of its initial biomass after removals
+cease was of up to four years. Future research should try to use, to the
+extent possible, parameters calculated for their region, or use
+different parameters to provide upper and lower bounds in their results.
+At the same time, this highlights the need for more basic research that
+furthers our understanding of lionfish biology. To better manage the
+invasion, we must perform research that can describe biologically
+important information of lionfish throughout its invasion range
 \citep{johnson_2016}.

### 2018-05-09 docs/Manuscript.Rmd
Ups, forgot to stash and commit the discussion changes

@@
 The results presented in this paper can have major implications for management.
+For example, \citet{edwards_2014} simulate lionfish culling using parameters from North Carolina and Little Cayman, and identify that the difference in time required for the population to recover to 90% of its initial biomass after removals cease was of up to four years.
 Our results show that, for a given length, using one set of parameters or the other can result in a threefold increase in estimated weight.
-Using site-specific values provides a more accurate estimate of fish biomass.
-This becomes especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
-\citet{edwards_2014} simulated lionfish culling using parameters from North Carolina and Little Cayman, and identify that the difference in time required for the population to recover to 90% of its initial biomass after removals cease was of up to four years.
+This differences become especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
 Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results.

### 2018-05-09 docs/Manuscript.tex
Ups, forgot to stash and commit the discussion changes

@@
 The results presented in this paper can have major implications for
-management. Our results show that, for a given length, using one set of
+management. For example, \citet{edwards_2014} simulate lionfish culling
+using parameters from North Carolina and Little Cayman, and identify
+that the difference in time required for the population to recover to
+90\% of its initial biomass after removals cease was of up to four
+years. Our results show that, for a given length, using one set of
 parameters or the other can result in a threefold increase in estimated
-weight. Using site-specific values provides a more accurate estimate of
-fish biomass. This becomes especially relevant when estimating biomass
-available for harvest, predicting effects on local ecosystems, or
-evaluating the effectiveness of removal programs. \citet{edwards_2014}
-simulated lionfish culling using parameters from North Carolina and
-Little Cayman, and identify that the difference in time required for the
-population to recover to 90\% of its initial biomass after removals
-cease was of up to four years. Future research should try to use, to the
-extent possible, parameters calculated for their region, or use
-different parameters to provide upper and lower bounds in their results.
-At the same time, this highlights the need for more basic research that
-furthers our understanding of lionfish biology. To better manage the
-invasion, we must perform research that can describe biologically
-important information of lionfish throughout its invasion range
-\citep{johnson_2016}.
+weight. This differences become especially relevant when estimating
+biomass available for harvest, predicting effects on local ecosystems,
+or evaluating the effectiveness of removal programs. Future research
+should try to use, to the extent possible, parameters calculated for
+their region, or use different parameters to provide upper and lower
+bounds in their results. At the same time, this highlights the need for
+more basic research that furthers our understanding of lionfish biology.
+To better manage the invasion, we must perform research that can
+describe biologically important information of lionfish throughout its
+invasion range \citep{johnson_2016}.
 

### 2018-05-24 docs/Manuscript.Rmd
Close #2 : Added changes to the introduction

@@
 
-Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling \citep{cote_2014,barbour_2011,andradibrown_2017}).
-In this case, biomass represents the sum of all individual fish weights.
-The individual weight ($W$) of an organism can be estimated from its length using the allometric growth equation, $W = aL^b$, where $L$ is an organism's length and $a$ and $b$ are constants.
-This length-weight relationship for any given species is an essential component of biomass-based modeling, and can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Site-specific parameters are therefore necessary in order to obtain accurate biomass estimates in a given region, especially when research involves identifying the total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016}.
-Equation parameters for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling).
+A common way to model this is via age- or length-structured population models \citep{cote_2014,barbour_2011,andradibrown_2017}, which convert fish length or age to weight to then calculate total biomass.
+Therefore, length-weight relationships are an essential component of biomass-based modeling.
+However, this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
+Literature suggests that when length-weight relationships are spatially variable, Site-specific parameters are necessary to obtain accurate biomass estimates.
+This becomes ingreasingly important when estimating the potential effectiveness (and resources neded) of lionfish culling programs or identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
+Genetic analysis of invasive lionfish suggest that two distinct population groups exist \citep{betancurr_2011}, and as such we would expect their biology to differ.
+Despite the large number of studies reporting site-specific length-weight relationships, no studies have described region-wide differences in these.
 
-Here, we review lionfish allometric growth parameters throughout its invasion range and examine spatial differences in the equation constants.
-We also provide a new pair of parameters specific to the central Meixcan Caribbean.
-Results suggest there are important regional-scale variations in allometric growth patterns of lionfish, and these differences highlight the importance of using site-specific parameters when developing or informing invasion management strategies.
+The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish in the Caribbean and Western Atlantic and identify wether these differences are trivial.
+Length-weight relationships for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+This study also provides the first length-weight relationship for this region.
 
@@
   annotate(geom = "text",
-            x = 120, y = 390,
+            x = 125, y = 390,
             label = get_eqn(model),
@@
   annotate(geom = "text",
-            x = 120, y = 350,
+            x = 125, y = 350,
             label = get_eqn2(model),
@@
   annotate(geom = "text",
-            x = 120, y = 310, 
+            x = 125, y = 310, 
             label = get_rsq(model),

### 2018-05-24 docs/Manuscript.tex
Close #2 : Added changes to the introduction

@@
 fisheries for lionfish involve modeling changes in biomass in response
-to changes in mortality (\emph{i.e.} culling
-\citep{cote_2014,barbour_2011,andradibrown_2017}). In this case, biomass
-represents the sum of all individual fish weights. The individual weight
-(\(W\)) of an organism can be estimated from its length using the
-allometric growth equation, \(W = aL^b\), where \(L\) is an organism's
-length and \(a\) and \(b\) are constants. This length-weight
-relationship for any given species is an essential component of
-biomass-based modeling, and can vary across regions as a response to
-biotic (\emph{e.g.} local food availability) and abiotic (\emph{e.g.}
-water temperature) conditions \citep{johnson_2016}. Site-specific
-parameters are therefore necessary in order to obtain accurate biomass
-estimates in a given region, especially when research involves
-identifying the total biomass available for harvest by fishers
-\citep{barbour_2011,morris_2011,johnston_2015,chin_2016}. Equation
-parameters for lionfish exist for North Carolina, Northern and Southern
-Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman,
-Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable
-for the central Mexican Caribbean
+to changes in mortality (\emph{i.e.} culling). A common way to model
+this is via age- or length-structured population models
+\citep{cote_2014,barbour_2011,andradibrown_2017}, which convert fish
+length or age to weight to then calculate total biomass. Therefore,
+length-weight relationships are an essential component of biomass-based
+modeling. However, this relationship can vary across regions as a
+response to biotic (\emph{e.g.} local food availability) and abiotic
+(\emph{e.g.} water temperature) conditions \citep{johnson_2016}.
+Literature suggests that when length-weight relationships are spatially
+variable, Site-specific parameters are necessary to obtain accurate
+biomass estimates. This becomes ingreasingly important when estimating
+the potential effectiveness (and resources neded) of lionfish culling
+programs or identifying total biomass available for harvest by fishers
+\citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
+Genetic analysis of invasive lionfish suggest that two distinct
+population groups exist \citep{betancurr_2011}, and as such we would
+expect their biology to differ. Despite the large number of studies
+reporting site-specific length-weight relationships, no studies have
+described region-wide differences in these.
+
+The objective of this paper is to describe the spatial pattern of
+length-weight relationships of lionfish in the Caribbean and Western
+Atlantic and identify wether these differences are trivial.
+Length-weight relationships for lionfish exist for North Carolina,
+Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean,
+Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica,
+but remain unavailable for the central Mexican Caribbean
 \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
-
-Here, we review lionfish allometric growth parameters throughout its
-invasion range and examine spatial differences in the equation
-constants. We also provide a new pair of parameters specific to the
-central Meixcan Caribbean. Results suggest there are important
-regional-scale variations in allometric growth patterns of lionfish, and
-these differences highlight the importance of using site-specific
-parameters when developing or informing invasion management strategies.
+This study also provides the first length-weight relationship for this
+region.
 

### 2018-05-24 docs/Manuscript.Rmd
Close #3 : Added changes to MnM

@@
 Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from their persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
-However, promoting its consumption might create a level of demand capable of sustaining a stable fishery, which can help control invasive populations while providing alternative livelihoods \citep{chin_2016}.
+However, promoting its consumption might create a level of demand capable of sustaining a stable fishery, which can help control shallow-water populations while providing alternative livelihoods and avoiding further impacts to local reef biota \citep{chin_2016}.
 
@@
 A common way to model this is via age- or length-structured population models \citep{cote_2014,barbour_2011,andradibrown_2017}, which convert fish length or age to weight to then calculate total biomass.
-Therefore, length-weight relationships are an essential component of biomass-based modeling.
-However, this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Literature suggests that when length-weight relationships are spatially variable, Site-specific parameters are necessary to obtain accurate biomass estimates.
+Therefore, length-weight relationships are an essential component of these models.
+However, the length-weight relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
+Literature suggests that site-specific parameters are necessary to obtain accurate biomass estimates when length-weight relationships present spatial variation.
 This becomes ingreasingly important when estimating the potential effectiveness (and resources neded) of lionfish culling programs or identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
@@
 The main objective of this work was to compare allometric growth of lionfish throughout their invasion range.
-Allometric parameters were retreived from scientific literature, and an additional pair of parameters was calculated from filed observations in the central Mexican Caribbean.
+Allometric parameters were retreived from scientific literature, and an additional pair of parameters were calculated from filed observations in the central Mexican Caribbean.
 
@@
 Studies were assumed to include both genders if gender was unspecified.
-Locations where allometric studies were performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
+Studies inconsistently defined $a$ as either the ponderal index from Eq.
+\ref{eq:allometric} or the y-intercept ($c$) from Eq.
+\ref{eq:log-alo-trans}.
+Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
+Here, all parameters are reported as TL(mm) to TW(gr) conversions.
+When required, values from other studies were transformed for consistency.
+Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
 
@@
 
-Studies inconsistently defined $a$ as either the ponderal index from Eq.
-\ref{eq:allometric} or the y-intercept ($c$) from Eq.
-\ref{eq:log-alo-trans}.
-Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
-Here, all parameters are reported as TL(mm) to TW(gr) conversions.
-When required, values from other studies were transformed for consistency.
+<!-- Still having trouble to explain this paragraph.
+Perhaps you can make it better?
+The idea is that we test wether the differences are trivial by taking all 109 lionfish and calculating TW with each of the 18 available relationships.
+We then take those, and divide them by the true weights, and obtain a ratio that is easy to interpret if theres an over or under estimation...
+andwe do some bassic stats on them -->
 
-<!-- Make this part more clear. Explain that the goal is to show "how far off" the estimates would be -->
-
-We compare observed TW to TW estimated with the 18 length-weight relationsips to quantify the extent to which using *ex situ* this leads to over- or underestimation.
-Predicted weights were divided by the observed weights to obtain a ratio.
-Difference in mean weight ratios across studies were tested with a one-way Analysis of Variance (ANOVA).
+Combining the length-weight parameters extracted from the literature and the additional pair calculated here, we obtain a total of `r dim(review)[1]` pairs.
+We test wether using *ex situ* parameters produces differences in weight estimates by estimating TW for the 109 length observations of lionfish from the central Mexican Caribbean with each of the `r dim(review)[1]` relationships.
+Predicted weights were divided by know observed weights to obtain a simple measurement of over- or underestimation.
+Difference in mean weight ratios across studies were tested with a one-way analysis of variance (ANOVA).
 All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.

### 2018-05-24 docs/Manuscript.tex
Close #3 : Added changes to MnM

@@
 promoting its consumption might create a level of demand capable of
-sustaining a stable fishery, which can help control invasive populations
-while providing alternative livelihoods \citep{chin_2016}.
+sustaining a stable fishery, which can help control shallow-water
+populations while providing alternative livelihoods and avoiding further
+impacts to local reef biota \citep{chin_2016}.
 
@@
 length or age to weight to then calculate total biomass. Therefore,
-length-weight relationships are an essential component of biomass-based
-modeling. However, this relationship can vary across regions as a
+length-weight relationships are an essential component of these models.
+However, the length-weight relationship can vary across regions as a
 response to biotic (\emph{e.g.} local food availability) and abiotic
 (\emph{e.g.} water temperature) conditions \citep{johnson_2016}.
-Literature suggests that when length-weight relationships are spatially
-variable, Site-specific parameters are necessary to obtain accurate
-biomass estimates. This becomes ingreasingly important when estimating
-the potential effectiveness (and resources neded) of lionfish culling
-programs or identifying total biomass available for harvest by fishers
+Literature suggests that site-specific parameters are necessary to
+obtain accurate biomass estimates when length-weight relationships
+present spatial variation. This becomes ingreasingly important when
+estimating the potential effectiveness (and resources neded) of lionfish
+culling programs or identifying total biomass available for harvest by
+fishers
 \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
@@
 when available. Studies were assumed to include both genders if gender
-was unspecified. Locations where allometric studies were performed are
-shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
+was unspecified. Locations where allometric studies have been performed
+are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
+
+Studies inconsistently defined \(a\) as either the ponderal index from
+Eq. \ref{eq:allometric} or the y-intercept (\(c\)) from Eq.
+\ref{eq:log-alo-trans}. Other studies incorrectly reported parameters as
+mm-to-g conversions when they were in fact cm-to-g conversions. Here,
+all parameters are reported as TL(mm) to TW(gr) conversions. When
+required, values from other studies were transformed for consistency.
 
@@
 
-Studies inconsistently defined \(a\) as either the ponderal index from
-Eq. \ref{eq:allometric} or the y-intercept (\(c\)) from Eq.
-\ref{eq:log-alo-trans}. Other studies incorrectly reported parameters as
-mm-to-g conversions when they were in fact cm-to-g conversions. Here,
-all parameters are reported as TL(mm) to TW(gr) conversions. When
-required, values from other studies were transformed for consistency.
-
-We compare observed TW to TW estimated with the 18 length-weight
-relationsips to quantify the extent to which using \emph{ex situ} this
-leads to over- or underestimation. Predicted weights were divided by the
-observed weights to obtain a ratio. Difference in mean weight ratios
-across studies were tested with a one-way Analysis of Variance (ANOVA).
-All analyses were performed in R version 3.5.0 \citep{rcore_2018}. Raw
-data and code used in this work are available at dryad.org.
+Combining the length-weight parameters extracted from the literature and
+the additional pair calculated here, we obtain a total of 18 pairs. We
+test wether using \emph{ex situ} parameters produces differences in
+weight estimates by estimating TW from the 109 length observations of
+lionfish from the central Mexican Caribbean with each ot the 18
+relationships. Predicted weights were divided by know observed weights
+to obtain a simple measurement of over- or underestimation. Difference
+in mean weight ratios across studies were tested with a one-way analysis
+of variance (ANOVA). All analyses were performed in R version 3.5.0
+\citep{rcore_2018}. Raw data and code used in this work are available at
+dryad.org.
 

### 2018-05-24 docs/Manuscript.Rmd
Close #4 : Added to the discussion

@@
 
-A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided, complimenting existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016,sabidoitz_2016}.
+<!-- A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided, complimenting existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016,sabidoitz_2016}.
 Additionally, the study identifies regional differences in length-weight relationships.
+-->
 
@@
 For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_2011}.
-Alternatively, \citet{fogg_2015} suggest that differences observed in age-at-length "may bemore related to climate rather than other biological and ecological factors".
+Alternatively, \citet{fogg_2015} suggest that differences observed in age-at-length may be driven by climate, and not by ecological processes.
 Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both.
 Future research should focus on identifying which occurs here.
+
+Differences in length-weight relationships have traditionally been highlighted as potential pitfalls to fishery management.
+For example, \citet{wilson_2012} shows that small-scale variations in other Scorpaeniformes (*Sebastes rastrelliger*) translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
+The lionfish case poses the opposite scenario, where the manager desires to erradicate species.
+To accurately estimate lionfish removal efforts and allocate resources to manage the invasion, we must aknowledge and understand the regional biological differences.
 

### 2018-05-24 docs/Manuscript.tex
Close #4 : Added to the discussion

@@
 retreived from scientific literature, and an additional pair of
-parameters was calculated from filed observations in the central Mexican
-Caribbean.
+parameters were calculated from filed observations in the central
+Mexican Caribbean.
 
@@
 when available. Studies were assumed to include both genders if gender
-was unspecified. Locations where allometric studies have been performed
+was unspecified. Studies inconsistently defined \(a\) as either the
+ponderal index from Eq. \ref{eq:allometric} or the y-intercept (\(c\))
+from Eq. \ref{eq:log-alo-trans}. Other studies incorrectly reported
+parameters as mm-to-g conversions when they were in fact cm-to-g
+conversions. Here, all parameters are reported as TL(mm) to TW(gr)
+conversions. When required, values from other studies were transformed
+for consistency. Locations where allometric studies have been performed
 are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
-
-Studies inconsistently defined \(a\) as either the ponderal index from
-Eq. \ref{eq:allometric} or the y-intercept (\(c\)) from Eq.
-\ref{eq:log-alo-trans}. Other studies incorrectly reported parameters as
-mm-to-g conversions when they were in fact cm-to-g conversions. Here,
-all parameters are reported as TL(mm) to TW(gr) conversions. When
-required, values from other studies were transformed for consistency.
 
@@
 test wether using \emph{ex situ} parameters produces differences in
-weight estimates by estimating TW from the 109 length observations of
-lionfish from the central Mexican Caribbean with each ot the 18
+weight estimates by estimating TW for the 109 length observations of
+lionfish from the central Mexican Caribbean with each of the 18
 relationships. Predicted weights were divided by know observed weights
@@
 
-A new pair of allometric growth parameters for lionfish in the central
-Mexican Caribbean are provided, complimenting existing literature for
-other sites in the Mexican Caribbean
-\citep{sabidoitza_2016,sabidoitz_2016}. Additionally, the study
-identifies regional differences in length-weight relationships.
-
 The length-weight coefficients estimated in this study were within the
@@
 \citep{betancurr_2011}. Alternatively, \citet{fogg_2015} suggest that
-differences observed in age-at-length ``may bemore related to climate
-rather than other biological and ecological factors''. Differences in
-weight-at-length could also reflect differences in energy input
-(\emph{i.e.} in some regions, lionfish eat more) or differential usage
-of this energy (\emph{e.g.} regional differences in predator abundances
-lead to different usage of energy), or a combination of both. Future
-research should focus on identifying which occurs here.
+differences observed in age-at-length may be driven by climate, and not
+by ecological processes. Differences in weight-at-length could also
+reflect differences in energy input (\emph{i.e.} in some regions,
+lionfish eat more) or differential usage of this energy (\emph{e.g.}
+regional differences in predator abundances lead to different usage of
+energy), or a combination of both. Future research should focus on
+identifying which occurs here.
+
+Differences in length-weight relationships have traditionally been
+highlighted as potential pitfalls to fishery management. For example,
+\citet{wilson_2012} shows that small-scale variations in other
+Scorpaeniformes (\emph{Sebastes rastrelliger}) translate to differential
+landings, effort, and catch per unit effort in the live fish fishery of
+California, and that these differences must be taken into account in
+management plans. The lionfish case poses the opposite scenario, where
+the manager desires to erradicate species. To accurately estimate
+lionfish removal efforts and allocate resources to manage the invasion,
+we must aknowledge and understand the regional biological differences.
 

### 2018-05-25 docs/Manuscript.Rmd
All you need to look at is ManuscriptSF.doc
I think I added like one comment to the Manuscript.Rmd file.

@@
     template: peerj_template.tex
-institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
-abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the Western Atlantic and the Caribbean.
-In order to better manage the invasion, we must be able to accurately estimate their total biomass.
-This work compares length-weight relationships of the invasive lionfish through the invasion range.
-A review of 17 length-weight relationships reported in 12 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length.
-The reviewed parameters indicate that, for the same length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf of Mexico.
-This highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region.
-These findings can have major implications in management, especially when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs."
-keywords: "A, B, C"
+  word_document: default
+keywords: A, B, C
+institution: Bren School of Environmental Sciences and Management, University of California
+  Santa Barbara, Santa Barbara, California, U.S.
+abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the Western
+  Atlantic and the Caribbean. In order to better manage the invasion, we must be able
+  to accurately estimate their total biomass. This work compares length-weight relationships
+  of the invasive lionfish through the invasion range. A review of 17 length-weight
+  relationships reported in 12 peer-reviewed studies shows that lionfish exhibit spatial
+  variation in weight-at-length. The reviewed parameters indicate that, for the same
+  length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf
+  of Mexico. This highlights the importance of using site-specific parameters to estimate
+  biomass from length observations. This study also reports a new pair of length-weight
+  parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) <!--fix formatting --> for organisms
+  sampled in the central Mexican Caribbean region. These findings can have major implications
+  in management, especially when estimating biomass available for harvest, predicting
+  effects on local ecosystems, or evaluating the effectiveness of removal programs."
 ---
@@
 volitans* `r dim(review)[1]-1` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
-Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
+Two studies reported gender-level and pooled parameters \citep{aguilarperera_2016,fogg_2013}, while the rest presented pooled results.
 Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
@@
 
+<!-- I thought you said the new pair of parameters was LESS interesting to you than the regional differences in length-weight, right?
+So I think the "additional" part would be this study, not the regional differences?
+-->
+
 The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).

### 2018-05-29 docs/Manuscript.Rmd
Incorporated Sean's comments

--- 2018-05-24 docs/Manuscript.Rmd
@@
     template: peerj_template.tex
-institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
+keywords: A, B, C
+institution: Bren School of Environmental Sciences and Management, University of California
+  Santa Barbara, Santa Barbara, California, USA
 abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the Western Atlantic and the Caribbean.
-In order to better manage the invasion, we must be able to accurately estimate their total biomass.
-This work compares length-weight relationships of the invasive lionfish through the invasion range.
-A review of 17 length-weight relationships reported in 12 peer-reviewed studies shows that lionfish exhibit spatial variation in weight-at-length.
-The reviewed parameters indicate that, for the same length, lionfish in the Caribbean have lower body mass than in the Atlantic or Gulf of Mexico.
-This highlights the importance of using site-specific parameters to estimate biomass from length observations.
-This study also reports a new pair of length-weight parameters ($a = 3.2056\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region.
-These findings can have major implications in management, especially when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs."
-keywords: "A, B, C"
+Improving management of invasive lionfish populations requires accurate estimates of total biomass, which in turn depend on accurate definition of the length-weight relationship.
+Here, we reviewed published length-weight relationships of lionfish taken from throughout their invasive range and found that lionfish of equal lengths have lower body mass in the Caribbean than in the Atlantic or Gulf of Mexico.
+Additionally, we report a new pair of length-weight parameters ($a = 3.2056 \\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region.
+The substantial spatial variation  in length-weight parameters highlights the importance of using site-specific information when estimating lionfish biomass using length observations.
+These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest."
 ---
@@
 
-At least 84% of marine eco-regions have reported the presence of an invasive species \citep{molnar_2008}, which represent a major threat to local biodiversity and the economic activities that depend on it \citep{bax_2003}.
-Invasive species may threaten native species through predation, competition, or indirect habitat effects \citep{davis_2003, gurevitch_2004}.
-By 2005, the economic cost of invasive species to the United States was  estimated at USD \$120 billion per year \citep{pimentel_2005}.
+Lionfish (*Pterois volitans/miles* complex) are an invasive species in the western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
+They are the first invasive marine vertebrates established along the North Atlantic Caribbean coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
+Invasive lionfish are primarily studied in coral reef ecosystems, where their impacts are far-reaching.
+For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida, and increased lionfish biomass coincided with a 65% reduction in the biomass of native prey fishes along Bahamian coral reefs in just two years \citep{green_2012}.
+Lionfish have also established invasive populations in other habitats such as estuaries, mangroves , hard-bottomed areas , and mesophotic reefs \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
 
-Lionfish (*Pterois volitans/miles* complex) are an invasive species in the western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
-They are the first invasive marine vertebrates established along the North Atlantic Caribbean coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}.
-Lionfish have been widely reported in coral reefs \citep{aguilarperera_2010}, but also in other habitats such as estuaries \citep{jud_2011}, mangroves \citep{barbour_2010}, hard-bottomed areas \citep{muoz_2011}, and mesophotic reefs \citep{andradibrown_2017}.
-Their presence in these waters has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
-
-A substantial amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
-\citet{peake_2018} show that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
+A substantial amount of research describes lionfish feeding ecology from North Carolina to Costa Rica \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
+A meta-analysis by  \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
 Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{albins_2008, green_2012,rocha_2015}.
 (However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes).
-Major efforts have been made to understand the possible impacts of the invasion by keeping track of its range through time \citep{schofield_2009,schofield_2010} and predicting invasion ranges under future climates \citep{grieve_2016}.
-By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish \citep{ariasgonzalez_2011}, which can then be translated into ecosystem-level and economic impacts.
+Major efforts have been made to understand the possible impacts of the invasion by tracking the spread of established lionfish populations through time \citep{schofield_2009,schofield_2010} and by predicting invasion ranges under future climates \citep{grieve_2016}.
+Trophic impacts of lionfish can be minimized if local lionfish biomass is controled by by culling \citep{ariasgonzalez_2011}.
+However, the feasability of controling local populations remains a topic of debate \citep{cote_2014}.
 
@@
 Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from their persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
-However, promoting its consumption might create a level of demand capable of sustaining a stable fishery, which can help control shallow-water populations while providing alternative livelihoods and avoiding further impacts to local reef biota \citep{chin_2016}.
+However, promoting lionfish consumption might create a level of demand capable of sustaining a stable fishery, which can help control shallow-water populations while providing alternative livelihoods and avoiding further impacts to local reef biota \citep{chin_2016}.
 
@@
 One contributing factor to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}.
-Culling programs are effective in reducing adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005}.
-As a result of this sedentary behavior, lionfish are also likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rate \citep{hutchinson_2008,wilson_2012}.
+Culling programs are effective in reducing adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005} -- But see \citet{andradibrown_2017} for cases when deep-water populations maintain shallow-water populations.
+Fish with this sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rate \citep{hutchinson_2008,wilson_2012}.
 The importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,guan_2013}, and such variation should be accounted for when evaluating the feasibility of establishing lionfish fisheries as well.
@@
 Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling).
-A common way to model this is via age- or length-structured population models \citep{cote_2014,barbour_2011,andradibrown_2017}, which convert fish length or age to weight to then calculate total biomass.
-Therefore, length-weight relationships are an essential component of these models.
-However, the length-weight relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Literature suggests that site-specific parameters are necessary to obtain accurate biomass estimates when length-weight relationships present spatial variation.
-This becomes ingreasingly important when estimating the potential effectiveness (and resources neded) of lionfish culling programs or identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
-Genetic analysis of invasive lionfish suggest that two distinct population groups exist \citep{betancurr_2011}, and as such we would expect their biology to differ.
-Despite the large number of studies reporting site-specific length-weight relationships, no studies have described region-wide differences in these.
+A common way to model this is via length-structured population models, where fish lengths are converted to  weight in order to calculate total biomass \citep{cote_2014,barbour_2011,andradibrown_2017}.
+The length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (e.g.
+local food availability) and abiotic (e.g.
+water temperature) conditions \citep{johnson_2016}.
+Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when length-weight relationships are spatially variable , and this variability becomes increasingly important when estimating the potential effectiveness of (and resources needed for)  lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
+In addition to environmentally-driven spatial variation, genetic analysis of invasive lionfish suggest biological differences due to the existence of two genetically distinct subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
+To date, no studies have examined region-wide differences in length-weight parameters despite the large number of studies reporting this relationship for lionfish.
 
-The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish in the Caribbean and Western Atlantic and identify wether these differences are trivial.
-Length-weight relationships for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
-This study also provides the first length-weight relationship for this region.
+The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish in the Caribbean and Western Atlantic and evaluate the implications of these spatial differences.
+Length-weight relationships for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+This study also provides the first length-weight relationship for the central Mexican Caribbean.
 
@@
 
-The main objective of this work was to compare allometric growth of lionfish throughout their invasion range.
-Allometric parameters were retreived from scientific literature, and an additional pair of parameters were calculated from filed observations in the central Mexican Caribbean.
+We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 10, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
+We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available, and assumed both genders were included in a study if gender was unspecified.
+Two studies reported parameters for genders combined an separated \citep{aguilarperera_2016,fogg_2013}, while the rest presented pooled results.
+Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
+Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
+\citet{fogg_2013} use spine-less weight in the length-weight relationship estimation, and thus their parameters likely underestimate whole wieght.
+Since no spine-less to whole weight conversions were available, these parameters were taken as reported.
 
-Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 10).
-Information on sampling methods, sex differentiation, location, and depth ranges of each study was retrieved when available.
-Studies were assumed to include both genders if gender was unspecified.
-Studies inconsistently defined $a$ as either the ponderal index from Eq.
-\ref{eq:allometric} or the y-intercept ($c$) from Eq.
-\ref{eq:log-alo-trans}.
-Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
-Here, all parameters are reported as TL(mm) to TW(gr) conversions.
-When required, values from other studies were transformed for consistency.
-Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
+We also collected data from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Table S1).
+Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
+All observed lionfish (n = 109) were collected using hand nets and numbered collection bottles.
+The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by eliminating gear selectivity.
+Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
 
@@
 
-Parameters from the central Mexican Caribbean were obtained from data collected in `r length(unique(fish$Location))` sampling sites along the central Mexican Caribbean coast in 2010 (Table S1).
-Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.
-All observed lionfish (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by eliminating gear selectivity.
-Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded before freezing organisms.
-
 The weight at length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function:
@@
 \label{eq:log-alo-trans}
-Y = mX + c
+Y = bX + c
 \end{equation}
 
-Where $Y = log_{10}(TW)$, $m = b$, $X = log_{10}(TL)$, and $c = log_{10}(a)$.
-Since $b = m$, we will only use $b$ throughout the paper for simplicity.
+Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, and $c = log_{10}(a)$.
 The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Squares Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
@@
 Coefficients were tested with a two-tailed Student's t, and the significance of the regression was corroborated with an F-test.
+
+Some of the reviewed studies inconsistently defined $a$ as either the ponderal index from Eq.
+\ref{eq:allometric} or the y-intercept ($c$) from Eq.
+\ref{eq:log-alo-trans}.
+Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
+We standardized each study by converting coefficients and report all parameters as TL(mm) to TW (gr) conversions.
+Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
 
@@
 
-Combining the length-weight parameters extracted from the literature and the additional pair calculated here, we obtain a total of `r dim(review)[1]` pairs.
-We test wether using *ex situ* parameters produces differences in weight estimates by estimating TW for the 109 length observations of lionfish from the central Mexican Caribbean with each of the `r dim(review)[1]` relationships.
-Predicted weights were divided by know observed weights to obtain a simple measurement of over- or underestimation.
-Difference in mean weight ratios across studies were tested with a one-way analysis of variance (ANOVA).
-All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
+Combining the length-weight parameters extracted from the literature and the additional pair calculated here, we obtain a total of 18 pairs.
+We use the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
+We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
+Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA).
+All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018} .
 Raw data and code used in this work are available at dryad.org.
@@
 
-<!-- This section presents a new length-weight relationship for lionfish in the central Mexican Caribbean region.
-A summary of length-weight relationship is provided, and a comparison of predicted-to-observed weight is included.
--->
-
-The model adjusted to Eq.
-\ref{eq:log-alo-trans} estimated the coefficient values at $b = `r coef(model)[[2]]`$ and $c = `r coef(model)[[1]]`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
-The allometric factor ($b$) was significantly different from the value of isometric growth of $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), indicating that lionfish present allometric growth.
-More information on model fit is presented in TableS2.
-The relationship between TL and TW is presented in Figure \ref{fig:l-w-carib}.
-
-From this study in the central Mexican Caribbean and the `r length(unique(review$Study))-1` peer-reviewed studies that reported length-weight parameters for *P.
-volitans* `r dim(review)[1]-1` parameters were identified (Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
-Two studies \citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled parameters, while the rest presented pooled results.
-Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
-Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
-\citet{fogg_2013} use spine-less weight in the length-weight relationship estimation.
+Inserting TL observations for the central Mexican Caribbean into \ref{eq:log-alo} Eq.
+2 and converting to \ref{eq:log-alo-trans} resulted in the coefficient values $b = `r b`$ and $c = `r c`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
+The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
+The significant difference between this allometric factor ($b$) and the isometric growth factor $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) indicated that lionfish present allometric growth, which is consistent with other studies.
+Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region, and more information on model fit is presented in Table S2.
 
@@
 
-There were significant differences in predicted-to-observed weight ratios estimated for each pair of parameters (F(df = 15; 1728) = 38.26; p < 0.001).
-From all allometric parameters reviewed, those of \citet{sabidoitz_2016} in Banco Chinchorro, (Caribbean) provided the lowest weight estimates, with a predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-On the other hand, \citet{barbour_2011} in the Northern Atlantic yielded the highest weight estimates, with a mean ($\pm$ SD) predicted-to-observed weight ratio of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")`.
+There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 15; 1728) = 38.26; p < 0.001$).
+The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic\citet{barbour_2011}.
+The calculated ratio of predicted-to-observed weight  ranged from `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
+Spine-less weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight rations > 1.
 
@@
   geom_line(aes(y = Weight, color = Study, linetype = Gender, group = Study_id), size = 1) +
-  # geom_ribbon(aes(ymin = min, ymax = max), color = "gray", alpha = 0.1) +
   geom_line(aes(y = This), size = 1.2, color = "black", linetype = "dashed") +
@@
 
-```{r, fig.height = 4.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot showing the distribution of predicted to observed weight ratios for 18 pairs of allometric parameters.
+```{r, fig.height = 4.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted to observed weight ratios for 18 pairs of allometric parameters.
 Red and blue circles indicate median and mean values, respectively.
@@
 
-A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided, complimenting existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016,sabidoitz_2016}.
-Additionally, the study identifies regional differences in length-weight relationships.
+We  detected substantial differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
+Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean.
+The average predicted-to-observed weight ratios from these three regions were insert 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and Caribbean 1.17 $\pm$ 0.398, respectively.
+These length-weight differences mirror similar findings of regional variability in age-at-length relationships of lionfish across both their invaded and native regions \citep{pusack_2016}.
+These differences may be driven by genetic variation or by organisms being exposed to distinct environmental conditions.
+For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be driven by climate.
+Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both.
+Future research is needed to determine which processes are at work here.
 
-The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
-However, the ones presented here provide lower weight estimates for similar lenmgths.
-Until about TL = 200 mm, there are no appreciable differences between the parameters for organisms from the Mexican Caribbean and those for little Cayman \citep{edwards_2014} and Jamaica \citep{chin_2016}.
-Yet, for larger organisms (TL > 270 mm) parameters from Costa Rica \citep{sandel_2015} and Bonaire \citep{deleon_2013} provide similar estimates to those from this study.
-Conversely, these same studies tend to estimate higher weights --as compared to the ones reported here-- for smaller organisms, likely due to the lack of small organisms in the samples used to estimate their parameters.
+Differences in length-weight relationships have traditionally been highlighted as potential pitfalls to fishery management.
+For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes (*Sebastes rastrelliger*) translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
+The lionfish case poses the opposite scenario, where the manager desires to erradicate species.
+To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.
 
-There are evident differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
-Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic tend to be higher than those from the Caribbean.
-Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015,edwards_2014}, or when comparing populations from the invasion and native ranges \citep{pusack_2016}.
-These may be driven by genetic differences or organisms being exposed to distinct environmental conditions.
-For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_2011}.
-Alternatively, \citet{fogg_2015} suggest that differences observed in age-at-length "may bemore related to climate rather than other biological and ecological factors".
-Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both.
-Future research should focus on identifying which occurs here.
-
-The results presented in this paper can have major implications for management.
-For example, \citet{edwards_2014} simulate lionfish culling using parameters from North Carolina and Little Cayman, and identify that the difference in time required for the population to recover to 90% of its initial biomass after removals cease was of up to four years.
-Our results show that, for a given length, using one set of parameters or the other can result in a threefold increase in estimated weight.
-This differences become especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs.
-Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results.
-At the same time, this highlights the need for more basic research that furthers our understanding of lionfish biology.
-To better manage the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range \citep{johnson_2016}.
+The results presented here have major implications for management.
+For example, \citet{edwards_2014} simulated a lionfish culling program under two scenarios, one using length-at-age and length-to-weight parameters from North Carolina and one using parameters from Little Cayman.
+They showed that using the different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased.
+Here, we show that using one set of length-weight parameters versus another for a given length can result in up to a threefold TW overestimation.
+These differences become especially important when allocating resources for removal programs, incentivizing its fishery as alternative livelihoods, or estimating ecosystem impacts.
+Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or at least use reasonable sets of different parameters that provide upper and lower bounds in their results.
+This work additionally highlights the need for more basic research that furthers our understanding of the invasive lionfish.
 
@@
 
-I would like to thank thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
+The authors would like to thank thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
 

### 2018-05-29 docs/Manuscript.tex
Incorporated Sean's comments

@@
 \affil[1]{Bren School of Environmental Sciences and Management, University of
-California Santa Barbara, Santa Barbara, California, U.S.}
+California Santa Barbara, Santa Barbara, California, USA}
 \corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@bren.ucsb.edu}
@@
 Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
-Western Atlantic and the Caribbean. In order to better manage the
-invasion, we must be able to accurately estimate their total biomass.
-This work compares length-weight relationships of the invasive lionfish
-through the invasion range. A review of 17 length-weight relationships
-reported in 12 peer-reviewed studies shows that lionfish exhibit spatial
-variation in weight-at-length. The reviewed parameters indicate that,
-for the same length, lionfish in the Caribbean have lower body mass than
-in the Atlantic or Gulf of Mexico. This highlights the importance of
-using site-specific parameters to estimate biomass from length
-observations. This study also reports a new pair of length-weight
-parameters (\(a = 3.2056 imes 10^{-6}; b = 3.235\)) for organisms
-sampled in the central Mexican Caribbean region. These findings can have
-major implications in management, especially when estimating biomass
-available for harvest, predicting effects on local ecosystems, or
-evaluating the effectiveness of removal programs.
+Western Atlantic and the Caribbean. Improving management of invasive
+lionfish populations requires accurate estimates of total biomass, which
+in turn depend on accurate definition of the length-weight relationship.
+Here, we reviewed published length-weight relationships of lionfish
+taken from throughout their invasive range and found that lionfish of
+equal lengths have lower body mass in the Caribbean than in the Atlantic
+or Gulf of Mexico. Additionally, we report a new pair of length-weight
+parameters (\(a = 3.2056 \times 10^{-6}; b = 3.235\)) for organisms
+sampled in the central Mexican Caribbean region. The substantial spatial
+variation in length-weight parameters highlights the importance of using
+site-specific information when estimating lionfish biomass using length
+observations. These findings can have major implications for management
+in terms of predicting effects on local ecosystems, evaluating the
+effectiveness of removal programs, or estimating biomass available for
+harvest.
 \end{abstract}
@@
 
-At least 84\% of marine eco-regions have reported the presence of an
-invasive species \citep{molnar_2008}, which represent a major threat to
-local biodiversity and the economic activities that depend on it
-\citep{bax_2003}. Invasive species may threaten native species through
-predation, competition, or indirect habitat effects
-\citep{davis_2003, gurevitch_2004}. By 2005, the economic cost of
-invasive species to the United States was estimated at USD \$120 billion
-per year \citep{pimentel_2005}.
-
 Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
@@
 Atlantic Caribbean coasts
-\citep{schofield_2009,schofield_2010,sabidoitza_2016}. Lionfish have
-been widely reported in coral reefs \citep{aguilarperera_2010}, but also
-in other habitats such as estuaries \citep{jud_2011}, mangroves
-\citep{barbour_2010}, hard-bottomed areas \citep{muoz_2011}, and
-mesophotic reefs \citep{andradibrown_2017}. Their presence in these
-waters has been labeled as a major marine invasion because they threaten
-local biodiversity, spread rapidly, and are difficult to manage
-\citep{hixon_2016}.
+\citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence
+has been labeled as a major marine invasion because they threaten local
+biodiversity, spread rapidly, and are difficult to manage
+\citep{hixon_2016}. Invasive lionfish are primarily studied in coral
+reef ecosystems, where their impacts are far-reaching. For example,
+field experiments by \citet{albins_2008} showed that lionfish
+establishment led to reduced recruitment of native fishes by nearly 80\%
+over a five week period in Florida, and increased lionfish biomass
+coincided with a 65\% reduction in the biomass of native prey fishes
+along Bahamian coral reefs in just two years \citep{green_2012}.
+Lionfish have also established invasive populations in other habitats
+such as estuaries, mangroves , hard-bottomed areas , and mesophotic
+reefs
+\citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
 
-A substantial amount of research has been done to describe lionfish
-feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas
-\citep{morris_2009,cote_2013}, Northern Gulf of Mexico
-\citep{dahl_2014}, Mexican Caribbean
-\citep{valdezmoreno_2012,villaseorderbez_2014}, Belize
-\citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}.
-\citet{peake_2018} show that invasive lionfish prey on at least 167
-different species across the tropical and temperate North Atlantic.
-Their feeding behavior and high consumption rates can reduce recruitment
-and population sizes of native reef-fish species, and can further
-endanger reef fish \citep{albins_2008, green_2012,rocha_2015}. (However,
-see \citet{hackerott_2017} for a case where there was no evidence that
+A substantial amount of research describes lionfish feeding ecology from
+North Carolina to Costa Rica
+\citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
+A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey
+on at least 167 different species across the tropical and temperate
+North Atlantic. Their feeding behavior and high consumption rates can
+reduce recruitment and population sizes of native reef-fish species, and
+can further endanger reef fish
+\citep{albins_2008, green_2012,rocha_2015}. (However, see
+\citet{hackerott_2017} for a case where there was no evidence that
 lionfish affected the density, richness, or community composition of
 prey fishes). Major efforts have been made to understand the possible
-impacts of the invasion by keeping track of its range through time
-\citep{schofield_2009,schofield_2010} and predicting invasion ranges
-under future climates \citep{grieve_2016}. By combining information from
-these disciplines, researchers have been able to predict the trophic
-impacts of lionfish \citep{ariasgonzalez_2011}, which can then be
-translated into ecosystem-level and economic impacts.
+impacts of the invasion by tracking the spread of established lionfish
+populations through time \citep{schofield_2009,schofield_2010} and by
+predicting invasion ranges under future climates \citep{grieve_2016}.
+Trophic impacts of lionfish can be minimized if local lionfish biomass
+is controled by by culling \citep{ariasgonzalez_2011}. However, the
+feasability of controling local populations remains a topic of debate
+\citep{cote_2014}.
 
@@
 coral ecosystems \citep{barbour_2011,andradibrown_2017}. However,
-promoting its consumption might create a level of demand capable of
+promoting lionfish consumption might create a level of demand capable of
 sustaining a stable fishery, which can help control shallow-water
@@
 exhibit high levels of site fidelity and rarely leave their home range
-in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005}. As a
-result of this sedentary behavior, lionfish are also likely to exhibit
-high levels of spatial variation in important life history
+in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005} -- But see
+\citet{andradibrown_2017} for cases when deep-water populations maintain
+shallow-water populations. Fish with this sedentary behavior are likely
+to exhibit high levels of spatial variation in important life history
 characterstics such as growth or natural mortality rate
@@
 to changes in mortality (\emph{i.e.} culling). A common way to model
-this is via age- or length-structured population models
-\citep{cote_2014,barbour_2011,andradibrown_2017}, which convert fish
-length or age to weight to then calculate total biomass. Therefore,
-length-weight relationships are an essential component of these models.
-However, the length-weight relationship can vary across regions as a
-response to biotic (\emph{e.g.} local food availability) and abiotic
-(\emph{e.g.} water temperature) conditions \citep{johnson_2016}.
-Literature suggests that site-specific parameters are necessary to
-obtain accurate biomass estimates when length-weight relationships
-present spatial variation. This becomes ingreasingly important when
-estimating the potential effectiveness (and resources neded) of lionfish
-culling programs or identifying total biomass available for harvest by
-fishers
-\citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
-Genetic analysis of invasive lionfish suggest that two distinct
-population groups exist \citep{betancurr_2011}, and as such we would
-expect their biology to differ. Despite the large number of studies
-reporting site-specific length-weight relationships, no studies have
-described region-wide differences in these.
+this is via length-structured population models, where fish lengths are
+converted to weight in order to calculate total biomass
+\citep{cote_2014,barbour_2011,andradibrown_2017}. The length-weight
+relationship is therefore an essential component of these models, but
+this relationship can vary across regions as a response to biotic
+(e.g.~local food availability) and abiotic (e.g.~water temperature)
+conditions \citep{johnson_2016}. Literature suggests that site-specific
+parameters are necessary in order to accurately estimate biomass when
+length-weight relationships are spatially variable , and this
+variability becomes increasingly important when estimating the potential
+effectiveness of (and resources needed for) lionfish culling programs or
+when identifying total biomass available for harvest by fishers
+\citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}. In
+addition to environmentally-driven spatial variation, genetic analysis
+of invasive lionfish suggest biological differences due to the existence
+of two genetically distinct subpopulations between the northwest
+Atlantic and the Caribbean \citep{betancurr_2011}. To date, no studies
+have examined region-wide differences in length-weight parameters
+despite the large number of studies reporting this relationship for
+lionfish.
 
@@
 length-weight relationships of lionfish in the Caribbean and Western
-Atlantic and identify wether these differences are trivial.
+Atlantic and evaluate the implications of these spatial differences.
 Length-weight relationships for lionfish exist for North Carolina,
 Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean,
-Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica,
-but remain unavailable for the central Mexican Caribbean
+Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica
 \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
-This study also provides the first length-weight relationship for this
-region.
+This study also provides the first length-weight relationship for the
+central Mexican Caribbean.
 
@@
 
-The main objective of this work was to compare allometric growth of
-lionfish throughout their invasion range. Allometric parameters were
-retreived from scientific literature, and an additional pair of
-parameters were calculated from filed observations in the central
-Mexican Caribbean.
+We reviewed 12 published studies and obtained 17 length-weight
+relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7,),
+and Caribbean (n = 10, Table \ref{tab:all_params}, Fig
+\ref{fig:all_allo}). We collected information on sampling methods, sex
+differentiation, location, and depth ranges from each study when
+available, and assumed both genders were included in a study if gender
+was unspecified. Two studies reported parameters for genders combined an
+separated \citep{aguilarperera_2016,fogg_2013}, while the rest presented
+pooled results. Reviewed studies presented information for organisms
+obtained at depths between 0.5 and 57 m. Three studies explicitly stated
+that their organisms were sampled with pole spears
+\citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five
+studies mentioned that some of their organisms were obtained with pole
+spears (or other type of harpoon) but also hand-held nets or fish traps
+\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014},
+and two studies did not specify how organisms were sampled
+\citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less
+weight in the length-weight relationship estimation, and thus their
+parameters likely underestimate whole wieght. Since no spine-less to
+whole weight conversions were available, these parameters were taken as
+reported.
 
-Length-weight relationships (n = 17) identified in literature were
-obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and
-Caribbean (n = 10). Information on sampling methods, sex
-differentiation, location, and depth ranges of each study was retrieved
-when available. Studies were assumed to include both genders if gender
-was unspecified. Studies inconsistently defined \(a\) as either the
-ponderal index from Eq. \ref{eq:allometric} or the y-intercept (\(c\))
-from Eq. \ref{eq:log-alo-trans}. Other studies incorrectly reported
-parameters as mm-to-g conversions when they were in fact cm-to-g
-conversions. Here, all parameters are reported as TL(mm) to TW(gr)
-conversions. When required, values from other studies were transformed
-for consistency. Locations where allometric studies have been performed
-are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
+We also collected data from 10 sampling sites along the central Mexican
+Caribbean coast in 2010 (Table S1). Sampling locations included wall and
+carpet reefs at depths between 5.7 m and 38.1 m. All observed lionfish
+(n = 109) were collected using hand nets and numbered collection
+bottles. The use of hand nets prevented any weight loss due to bleeding
+and allowed better representation of small sizes by eliminating gear
+selectivity. Organisms were euthanized via pithing and Total Length (TL;
+mm) and Total Weight (TW; g) were recorded.
 
@@
 \end{figure}
-
-Parameters from the central Mexican Caribbean were obtained from data
-collected in 10 sampling sites along the central Mexican Caribbean coast
-in 2010 (Table S1). Sampling locations included wall and carpet reefs at
-depths between 5.7 m and 38.1 m. All observed lionfish (n = 109) were
-collected using hand nets and numbered collection bottles. The use of
-hand nets prevented any weight loss due to bleeding and allowed better
-representation of small sizes by eliminating gear selectivity. Organisms
-were euthanized via pithing and Total Length (TL; mm) and Total Weight
-(TW; g) were recorded before freezing organisms.
 
@@
 \label{eq:log-alo-trans}
-Y = mX + c
+Y = bX + c
 \end{equation}
 
-Where \(Y = log_{10}(TW)\), \(m = b\), \(X = log_{10}(TL)\), and
-\(c = log_{10}(a)\). Since \(b = m\), we will only use \(b\) throughout
-the paper for simplicity. The coefficients (\(c\) and \(b\)) were
-estimated with an Ordinary Least Squares Regression and
-heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-The \(b\) coefficient was tested against the null hypothesis of
-isometric growth (\emph{i.e.} \(H_0: b = 3\)). Coefficients were tested
-with a two-tailed Student's t, and the significance of the regression
-was corroborated with an F-test.
+Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), and
+\(c = log_{10}(a)\). The coefficients (\(c\) and \(b\)) were estimated
+with an Ordinary Least Squares Regression and heteroskedastic-robust
+standard error correction \citep{zeileis_2004}. The \(b\) coefficient
+was tested against the null hypothesis of isometric growth (\emph{i.e.}
+\(H_0: b = 3\)). Coefficients were tested with a two-tailed Student's t,
+and the significance of the regression was corroborated with an F-test.
+
+Some of the reviewed studies inconsistently defined \(a\) as either the
+ponderal index from Eq. \ref{eq:allometric} or the y-intercept (\(c\))
+from Eq. \ref{eq:log-alo-trans}. Other studies incorrectly reported
+parameters as mm-to-g conversions when they were in fact cm-to-g
+conversions. We standardized each study by converting coefficients and
+report all parameters as TL(mm) to TW (gr) conversions. Locations where
+allometric studies have been performed are shown in Figure \ref{fig:map}
+and Table \ref{tab:all_params}.
 
@@
 the additional pair calculated here, we obtain a total of 18 pairs. We
-test wether using \emph{ex situ} parameters produces differences in
-weight estimates by estimating TW for the 109 length observations of
-lionfish from the central Mexican Caribbean with each of the 18
-relationships. Predicted weights were divided by know observed weights
-to obtain a simple measurement of over- or underestimation. Difference
-in mean weight ratios across studies were tested with a one-way analysis
-of variance (ANOVA). All analyses were performed in R version 3.5.0
-\citep{rcore_2018}. Raw data and code used in this work are available at
-dryad.org.
+use the central Mexican Caribbean as a case study of how the use of
+\emph{ex situ} parameters influences the accuracy of weight estimates
+for lionfish. We estimated TW from the TL observations we collected in
+the central Mexican Caribbean (n = 109) using each of the 18 parameter
+pairs and divided predicted weights by known observed weights to obtain
+a simple measure of over- or underestimation. Difference in mean weight
+ratios across the different parameter pairs were tested with a one-way
+analysis of variance (ANOVA). All analyses were performed in R version
+3.5.0 \citep{rcore_2018} . Raw data and code used in this work are
+available at dryad.org.
 
@@
 
-The model adjusted to Eq. \ref{eq:log-alo-trans} estimated the
-coefficient values at \(b = 3.2347391\) and \(c = -5.4940866\)
+Inserting TL observations for the central Mexican Caribbean into
+\ref{eq:log-alo} Eq. 2 and converting to \ref{eq:log-alo-trans} resulted
+in the coefficient values \(b = 3.2347391\) and \(c = -5.4940866\)
 (\(R^2 = 0.977\), F(df = 1; 107) = 6928.67, \(p < 0.001\)). The
-allometric factor (\(b\)) was significantly different from the value of
-isometric growth of \(b = 3\) (\(t(107) = 6.04; p<0.001\)), indicating
-that lionfish present allometric growth. More information on model fit
-is presented in TableS2. The relationship between TL and TW is presented
-in Figure \ref{fig:l-w-carib}.
-
-From this study in the central Mexican Caribbean and the 12
-peer-reviewed studies that reported length-weight parameters for
-\emph{P. volitans} 17 parameters were identified (Table
-\ref{tab:all_params}, Fig \ref{fig:all_allo}). Two studies
-\citep{aguilarperera_2016,fogg_2013} reported gender-level and pooled
-parameters, while the rest presented pooled results. Reviewed studies
-presented information for organisms obtained at depths between 0.5 and
-57 m. Three studies explicitly stated that their organisms were sampled
-with pole spears
-\citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five
-studies mentioned that some of their organisms were obtained with pole
-spears (or other type of harpoon) but also hand-held nets or fish traps
-\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014},
-and two studies did not specify how organisms were sampled
-\citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less
-weight in the length-weight relationship estimation.
+length-weight coefficients estimated in this study were within the range
+identified by studies in other regions (Table \ref{tab:all_params}). The
+significant difference between this allometric factor (\(b\)) and the
+isometric growth factor \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicated
+that lionfish present allometric growth, which is consistent with other
+studies. Figure \ref{fig:l-w-carib} shows the relationship between TL
+and TW for this region, and more information on model fit is presented
+in Table S2.
 
@@
 
-There were significant differences in predicted-to-observed weight
-ratios estimated for each pair of parameters (F(df = 15; 1728) = 38.26;
-p \textless{} 0.001). From all allometric parameters reviewed, those of
-\citet{sabidoitz_2016} in Banco Chinchorro, (Caribbean) provided the
-lowest weight estimates, with a predicted-to-observed weight ratio of
-0.80 \(\pm\) 0.19 (mean \(\pm\) SD). On the other hand,
-\citet{barbour_2011} in the Northern Atlantic yielded the highest weight
-estimates, with a mean (\(\pm\) SD) predicted-to-observed weight ratio
-of 1.76 \(\pm\) 0.50. Predicted-to-observed weight ratios are presented
-in Figure \ref{fig:bio_ratio}.
+There were significant differences in our predicted weights for the
+central Mexican Caribbean when using the different pairs of parameters
+(\(F(df = 15; 1728) = 38.26; p < 0.001\)). The lowest weight estimates
+resulted from using the allometric parameters from Banco Chinchorro in
+the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates
+came from the Northern Atlantic\citet{barbour_2011}. The calculated
+ratio of predicted-to-observed weight ranged from 0.80 \(\pm\) 0.19 to
+1.76 \(\pm\) 0.50 (mean \(\pm\) SD). Predicted-to-observed weight ratios
+are presented in Figure \ref{fig:bio_ratio}. Spine-less weight
+parameters from \citet{fogg_2013} still produced predicted-to-observed
+weight rations \textgreater{} 1.
 
@@
 \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:bio_ratio}Violin plot showing the distribution of
-predicted to observed weight ratios for 18 pairs of allometric
-parameters. Red and blue circles indicate median and mean values,
-respectively. Like letters indicate values that do not differ
-significantly (Tukey's HSD; p \textless{} 0.05).}
+\caption{\label{fig:bio_ratio}Violin plot of predicted to observed
+weight ratios for 18 pairs of allometric parameters. Red and blue
+circles indicate median and mean values, respectively. Like letters
+indicate values that do not differ significantly (Tukey's HSD; p
+\textless{} 0.05).}
 \end{figure}
@@
 
-The length-weight coefficients estimated in this study were within the
-range identified by studies in other regions (Table
-\ref{tab:all_params}). However, the ones presented here provide lower
-weight estimates for similar lenmgths. Until about TL = 200 mm, there
-are no appreciable differences between the parameters for organisms from
-the Mexican Caribbean and those for little Cayman \citep{edwards_2014}
-and Jamaica \citep{chin_2016}. Yet, for larger organisms (TL
-\textgreater{} 270 mm) parameters from Costa Rica \citep{sandel_2015}
-and Bonaire \citep{deleon_2013} provide similar estimates to those from
-this study. Conversely, these same studies tend to estimate higher
-weights --as compared to the ones reported here-- for smaller organisms,
-likely due to the lack of small organisms in the samples used to
-estimate their parameters.
-
-There are evident differences in weight-at-length between organisms from
-the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight
-estimates with parameters from the Gulf of Mexico and North-Western
-Atlantic tend to be higher than those from the Caribbean. Similar
-regional variation has been reported for age-at-length relationships of
-this species across the invaded region \citep{fogg_2015,edwards_2014},
-or when comparing populations from the invasion and native ranges
-\citep{pusack_2016}. These may be driven by genetic differences or
-organisms being exposed to distinct environmental conditions. For
-example, work on mitochondrial DNA has shown two distinct population
-groups, identified as the ``Caribbean group'' and ``Northern Group''
-\citep{betancurr_2011}. Alternatively, \citet{fogg_2015} suggest that
-differences observed in age-at-length may be driven by climate, and not
-by ecological processes. Differences in weight-at-length could also
-reflect differences in energy input (\emph{i.e.} in some regions,
-lionfish eat more) or differential usage of this energy (\emph{e.g.}
-regional differences in predator abundances lead to different usage of
-energy), or a combination of both. Future research should focus on
-identifying which occurs here.
+We detected substantial differences in weight-at-length between
+organisms from the Caribbean and Gulf of Mexico / North-Western
+Atlantic. Weight estimates using parameters from the Gulf of Mexico and
+North-Western Atlantic were higher on average than those from the
+Caribbean. The average predicted-to-observed weight ratios from these
+three regions were insert 1.24 \(\pm\) 0.309, 1.76 \(\pm\) 0.496, and
+Caribbean 1.17 \(\pm\) 0.398, respectively. These length-weight
+differences mirror similar findings of regional variability in
+age-at-length relationships of lionfish across both their invaded and
+native regions \citep{pusack_2016}. These differences may be driven by
+genetic variation or by organisms being exposed to distinct
+environmental conditions. For example, \citet{betancurr_2011} used
+mitochondrial DNA to demonstrate the existence of two distinct
+population groups, identified as the ``Caribbean group'' and ``Northern
+Group'', and \citet{fogg_2015} alternatively suggested that
+age-at-length differences may be driven by climate. Differences in
+weight-at-length could also reflect differences in energy input
+(\emph{i.e.} in some regions, lionfish eat more) or differential usage
+of this energy (\emph{e.g.} regional differences in predator abundances
+lead to different usage of energy), or a combination of both. Future
+research is needed to determine which processes are at work here.
 
@@
 highlighted as potential pitfalls to fishery management. For example,
-\citet{wilson_2012} shows that small-scale variations in other
-Scorpaeniformes (\emph{Sebastes rastrelliger}) translate to differential
-landings, effort, and catch per unit effort in the live fish fishery of
-California, and that these differences must be taken into account in
-management plans. The lionfish case poses the opposite scenario, where
-the manager desires to erradicate species. To accurately estimate
-lionfish removal efforts and allocate resources to manage the invasion,
-we must aknowledge and understand the regional biological differences.
+\citet{wilson_2012} show that small-scale variations in length-at-age
+and fishing mortality in other Scorpaeniformes (\emph{Sebastes
+rastrelliger}) translate to differential landings, effort, and catch per
+unit effort in the live fish fishery of California, and that these
+differences must be taken into account in management plans. The lionfish
+case poses the opposite scenario, where the manager desires to
+erradicate species. To accurately gauge both the effectiveness of
+lionfish removal efforts and the resources needed to successfully manage
+an invasion, we must acknowledge and understand regional biological
+differences in important variables such as allometric growth parameters.
 
-The results presented in this paper can have major implications for
-management. For example, \citet{edwards_2014} simulate lionfish culling
-using parameters from North Carolina and Little Cayman, and identify
-that the difference in time required for the population to recover to
-90\% of its initial biomass after removals cease was of up to four
-years. Our results show that, for a given length, using one set of
-parameters or the other can result in a threefold increase in estimated
-weight. This differences become especially relevant when estimating
-biomass available for harvest, predicting effects on local ecosystems,
-or evaluating the effectiveness of removal programs. Future research
-should try to use, to the extent possible, parameters calculated for
-their region, or use different parameters to provide upper and lower
-bounds in their results. At the same time, this highlights the need for
-more basic research that furthers our understanding of lionfish biology.
-To better manage the invasion, we must perform research that can
-describe biologically important information of lionfish throughout its
-invasion range \citep{johnson_2016}.
+The results presented here have major implications for management. For
+example, \citet{edwards_2014} simulated a lionfish culling program under
+two scenarios, one using length-at-age and length-to-weight parameters
+from North Carolina and one using parameters from Little Cayman. They
+showed that using the different parameters caused up to a four-year
+difference in the time required for the simulated lionfish population to
+recover to 90\% of its initial biomass after removals ceased. Here, we
+show that using one set of length-weight parameters versus another for a
+given length can result in up to a threefold TW overestimation. These
+differences become especially important when allocating resources for
+removal programs, incentivizing its fishery as alternative livelihoods,
+or estimating ecosystem impacts. Research efforts focused on invasive
+lionfish populations need to use parameters calculated for their region
+to the extent possible, or at least use reasonable sets of different
+parameters that provide upper and lower bounds in their results. This
+work additionally highlights the need for more basic research that
+furthers our understanding of the invasive lionfish.
 
@@
 
-I would like to thank thank Nils Van Der Haar and Michael Doodey from
-Dive Aventuras as well as Guillermo Lotz-Cador who provided help to
-collect samples.
+The authors would like to thank thank Nils Van Der Haar and Michael
+Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided
+help to collect samples.
 

### 2018-06-01 docs/Manuscript.Rmd
Updated manuscript, ready for (last?) round of revision with Sean

@@
 ---
-title: Invasive lionfish present region-wide variation of allometric growth in the
-  Western Atlantic
-author: "Juan Carlos Villaseñor-Derbez$^1$, Sean Fitzgerald"
-header-includes:
-- \usepackage{float}
-- \floatplacement{figure}{H}
+title: Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic
+abstract: "Lionfish (*Pterois volitans / miles*) are an invasive species in the Western Atlantic and the Caribbean.
+Improving management of invasive lionfish populations requires accurate estimates of total biomass, which depend on accurate estimates of the length-weight relationship.
+Lionfish exhibit a sedentary behavior that is likely to result in high levels of spatial variation in some life history characterstics, such as the length-weight relationship.
+We review 12 published length-weight relationships of lionfish taken throughout their invasive range and describe the spatial variation and implications of these differences.
+The spatial pattern observed here is consistent with those reported in genetic studies or age-at-length studies.
+We show that the use of *ex situ* parameters can result in up to a three-fold overestimation of Total Weight, but that using parameters obtained nearby reduces this error.
+These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest."
 output:
@@
     template: peerj_template.tex
-keywords: A, B, C
-institution: Bren School of Environmental Sciences and Management, University of California
-  Santa Barbara, Santa Barbara, California, USA
-abstract: "Lionfish (*Pterois volitans/miles*) are an invasive species in the Western Atlantic and the Caribbean.
-Improving management of invasive lionfish populations requires accurate estimates of total biomass, which in turn depend on accurate definition of the length-weight relationship.
-Here, we reviewed published length-weight relationships of lionfish taken from throughout their invasive range and found that lionfish of equal lengths have lower body mass in the Caribbean than in the Atlantic or Gulf of Mexico.
-Additionally, we report a new pair of length-weight parameters ($a = 3.2056 \\times 10^{-6}; b = 3.235$) for organisms sampled in the central Mexican Caribbean region.
-The substantial spatial variation  in length-weight parameters highlights the importance of using site-specific information when estimating lionfish biomass using length observations.
-These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest."
 ---
+
+<!-- Alternative titles: -->
+<!-- Region-wide variation of allometric growth in invasive lionfish -->
 
@@
 suppressPackageStartupMessages({
-  # library(RColorBrewer)
-  # library(colorRamps)
-  # library(e1071)
   library(stringr)
@@
 
-Lionfish (*Pterois volitans/miles* complex) are an invasive species in the western Atlantic and the Caribbean, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
+Lionfish (*Pterois volitans/miles* complex) are an invasive species in the western Atlantic and Caribbean Sea, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
 They are the first invasive marine vertebrates established along the North Atlantic Caribbean coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
+
 Invasive lionfish are primarily studied in coral reef ecosystems, where their impacts are far-reaching.
-For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida, and increased lionfish biomass coincided with a 65% reduction in the biomass of native prey fishes along Bahamian coral reefs in just two years \citep{green_2012}.
-Lionfish have also established invasive populations in other habitats such as estuaries, mangroves , hard-bottomed areas , and mesophotic reefs \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
+For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida.
+\citet{green_2012} report that prey fish biomass declined 65% over two years as lionfish biomass increased along Bahamian coral reefs.
+Lionfish have also established invasive populations in other habitats such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
 
-A substantial amount of research describes lionfish feeding ecology from North Carolina to Costa Rica \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
+A substantial amount of research describes lionfish feeding ecology throughout the invaded range \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
 A meta-analysis by  \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
@@
 Major efforts have been made to understand the possible impacts of the invasion by tracking the spread of established lionfish populations through time \citep{schofield_2009,schofield_2010} and by predicting invasion ranges under future climates \citep{grieve_2016}.
-Trophic impacts of lionfish can be minimized if local lionfish biomass is controled by by culling \citep{ariasgonzalez_2011}.
-However, the feasability of controling local populations remains a topic of debate \citep{cote_2014}.
+It{s been proposed that trophic impacts of lionfish can be minimized if local lionfish biomass is controled by culling \citep{ariasgonzalez_2011}.
 
@@
 One contributing factor to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}.
-Culling programs are effective in reducing adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005} -- But see \citet{andradibrown_2017} for cases when deep-water populations maintain shallow-water populations.
-Fish with this sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rate \citep{hutchinson_2008,wilson_2012}.
+Culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range \citep{Fishelson_1997,cote_2014,kochzius_2005}.
+Fish with this sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates \citep{hutchinson_2008,wilson_2012}.
 The importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,guan_2013}, and such variation should be accounted for when evaluating the feasibility of establishing lionfish fisheries as well.
 
-Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling).
-A common way to model this is via length-structured population models, where fish lengths are converted to  weight in order to calculate total biomass \citep{cote_2014,barbour_2011,andradibrown_2017}.
-The length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (e.g.
-local food availability) and abiotic (e.g.
-water temperature) conditions \citep{johnson_2016}.
-Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when length-weight relationships are spatially variable , and this variability becomes increasingly important when estimating the potential effectiveness of (and resources needed for)  lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
+Determining the feasibility of such initiatives require modeling changes in biomass in response to changes in mortality (*i.e.* culling).
+A common way to model this is via length-structured population models, where fish lengths are converted to  weight to calculate total biomass \citep{cote_2014,barbour_2011,andradibrown_2017}.
+The length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
+Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when length-weight relationships are spatially variable, and this variability becomes increasingly important when estimating the potential effectiveness and feasability of lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
 In addition to environmentally-driven spatial variation, genetic analysis of invasive lionfish suggest biological differences due to the existence of two genetically distinct subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
@@
 
-We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 10, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
+We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7), and Caribbean (n = 10, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
 We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available, and assumed both genders were included in a study if gender was unspecified.
-Two studies reported parameters for genders combined an separated \citep{aguilarperera_2016,fogg_2013}, while the rest presented pooled results.
-Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` and `r max(review$maxD, na.rm = T)` m.
+Only two studies reported parameters for each gender \citep{aguilarperera_2016,fogg_2013}.
+Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
 Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
-\citet{fogg_2013} use spine-less weight in the length-weight relationship estimation, and thus their parameters likely underestimate whole wieght.
-Since no spine-less to whole weight conversions were available, these parameters were taken as reported.
+\citet{fogg_2013} use spine-less weight in the length-weight relationship estimation, and thus their parameters likely underestimate total wieght.
+Since no spine-less to total weight conversions were available, these parameters were taken as reported.
 
@@
 Circle sizes indicate sample size from each study, colors indicate the $b$ coefficient from Eq.
-\\ref{eq:allometric}."}
+\\ref{eq:allometric}.", fig.height = 3.5}
 
@@
 
-#Small shapefile for region of interest
-xy1 <- data.frame(X = mean(-87.30662, -87.19194), Y = mean(20.39283, 20.51278))
-coordinates(xy1) <- c("X", "Y")
-proj4string(xy1) <- proj
-res1 <- spTransform(xy1, proj) %>% 
-  st_as_sf()
-
-#Create shapefile for sampling locations
-sample_points <- fish %>%
-  group_by(Location) %>%
-  summarize(latitude = mean(Latitude, na.rm = T),
-            longitude = mean(Longitude, na.rm = T)) %>%
-  ungroup()
-
-xy <- data.frame(X = -1*abs(sample_points$longitude), Y = sample_points$latitude)
-coordinates(xy) <- c("X", "Y")
-proj4string(xy) <- proj  ## for example
-res <- spTransform(xy, proj)
-b <- SpatialPointsDataFrame(coords = res, data = sample_points, proj4string = proj)
-
-# Create shapefile for relevant communities
-Communities <- data.frame(Longitude = c(-87.24),
-                           Latitude = c(20.5),
-                           Location = c("Pto. Aventuras"),
-                           stringsAsFactors = F)
-
-xy2 <- data.frame(X = -1*abs(Communities$Longitude), Y = Communities$Latitude)
-coordinates(xy2) <- c("X", "Y")
-proj4string(xy2) <- proj  ## for example
-res2 <- spTransform(xy2, proj)
-c <- SpatialPointsDataFrame(coords = res2, data = Communities, proj4string = proj)
-
 # Map with SF
-
 ggplot() +
@@
 
-<!-- Still having trouble to explain this paragraph.
-Perhaps you can make it better?
-The idea is that we test wether the differences are trivial by taking all 109 lionfish and calculating TW with each of the 18 available relationships.
-We then take those, and divide them by the true weights, and obtain a ratio that is easy to interpret if theres an over or under estimation...
-andwe do some bassic stats on them -->
-
 Combining the length-weight parameters extracted from the literature and the additional pair calculated here, we obtain a total of 18 pairs.
@@
 We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA).
-All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018} .
+Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tuskey's test was used for post-hoc tests.
+All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
 Raw data and code used in this work are available at dryad.org.
@@
 
-Inserting TL observations for the central Mexican Caribbean into \ref{eq:log-alo} Eq.
-2 and converting to \ref{eq:log-alo-trans} resulted in the coefficient values $b = `r b`$ and $c = `r c`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
+The length-weight relationship for organisms from the central Mexican Caribbean resulted in the coefficient values $a = `r 10^c`$, $b = `r b`$ and $c = `r c`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
+The allometric factor ($b$) was significantly different from $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) indicating that lionfish present allometric growth.
 The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
-The significant difference between this allometric factor ($b$) and the isometric growth factor $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) indicated that lionfish present allometric growth, which is consistent with other studies.
 Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region, and more information on model fit is presented in Table S2.
 
-Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for pooled genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
-In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for pooled genders.
 Figure \ref{fig:all_allo} shows the length-weight relationships with parameters from all studies.
+Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for combined genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
+In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for combined genders.
 
 There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 15; 1728) = 38.26; p < 0.001$).
-The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic\citet{barbour_2011}.
+Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean.
+The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
+The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic \citep{barbour_2011}.
 The calculated ratio of predicted-to-observed weight  ranged from `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
+Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not differnt from those obntained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
-Spine-less weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight rations > 1.
+Spine-less weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.
 
@@
                booktabs = T,
+               # longtable = T,
                col.names = c("Region", "Sex", "n", "a", "b", "c", "$R^2$", "Reference"),
@@
 
-```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
+```{r, fig.height = 3.6, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
 Colors indicate studies from which the parameters were extracted.
-Solid lines indicate that the fit was performed for males and females pooled together.
-Dotted lines indicate that the regression was performed on females, and dashed lines indicate it was performed for males.
+Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
 The dashed black line represents the relationship estimated in this study."}
@@
         legend.justification=c(0,1),
-        legend.position=c(0.01, 1),
+        legend.position=c(0.01, 1.05),
         legend.background = element_rect(fill = "transparent"),
@@
   scale_color_brewer(palette = "Paired", direction = -1) +
-  scale_linetype_manual(values=c("solid", "longdash", "dotted")) +
+  scale_linetype_manual(values=c("solid", "dashed", "dotted"), name = "Sex") +
   scale_size_manual(values = c(1, 1.5))
@@
 
-```{r, fig.height = 4.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted to observed weight ratios for 18 pairs of allometric parameters.
+```{r, fig.height = 4, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
 Red and blue circles indicate median and mean values, respectively.
-Like letters indicate values that do not differ significantly (Tukey's HSD; p < 0.05)."}
+Like letters indicate values that do not differ significantly."}
 groups$groups%<>%
@@
 We  detected substantial differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
-Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean.
-The average predicted-to-observed weight ratios from these three regions were insert 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and Caribbean 1.17 $\pm$ 0.398, respectively.
+The groupings of predicted-to-observed weight ratios were consistent with the spatial distribution of the studies, suggesting that these differences are mediated by space.
 These length-weight differences mirror similar findings of regional variability in age-at-length relationships of lionfish across both their invaded and native regions \citep{pusack_2016}.
-These differences may be driven by genetic variation or by organisms being exposed to distinct environmental conditions.
+These patterns may be driven by genetic variation or by organisms being exposed to distinct environmental conditions.
 For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be driven by climate.
-Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both.
+Differences in weight-at-length could also reflect differences in energy input or differential usage of this energy, or a combination of both.
 Future research is needed to determine which processes are at work here.
@@
 Differences in length-weight relationships have traditionally been highlighted as potential pitfalls to fishery management.
-For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes (*Sebastes rastrelliger*) translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
+For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
 The lionfish case poses the opposite scenario, where the manager desires to erradicate species.
@@
 For example, \citet{edwards_2014} simulated a lionfish culling program under two scenarios, one using length-at-age and length-to-weight parameters from North Carolina and one using parameters from Little Cayman.
-They showed that using the different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased.
+Their results show that using different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased.
 Here, we show that using one set of length-weight parameters versus another for a given length can result in up to a threefold TW overestimation.
-These differences become especially important when allocating resources for removal programs, incentivizing its fishery as alternative livelihoods, or estimating ecosystem impacts.
+These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing its fishery as a source of alternative livelihoods, or estimating ecosystem impacts.
 Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or at least use reasonable sets of different parameters that provide upper and lower bounds in their results.
-This work additionally highlights the need for more basic research that furthers our understanding of the invasive lionfish.
 

### 2018-06-01 docs/Manuscript.tex
Updated manuscript, ready for (last?) round of revision with Sean

@@
 
-\author[1]{Juan Carlos Villaseñor-Derbez\(^1\), Sean Fitzgerald}
-\affil[1]{Bren School of Environmental Sciences and Management, University of
-California Santa Barbara, Santa Barbara, California, USA}
-\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@bren.ucsb.edu}
+\author[1]{Juan Carlos Villaseñor-Derbez}
+\author[1]{Sean Fitzgerald}
+\affil[1]{Bren School of Environmental Sciences and Management, University of California
+  Santa Barbara, Santa Barbara, California, USA}
+\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@ucsb.edu}
 
-% \keywords{A, B, C}
+% \keywords{Keyword1, Keyword2, Keyword3}
 
 \begin{abstract}
-Lionfish (\emph{Pterois volitans/miles}) are an invasive species in the
-Western Atlantic and the Caribbean. Improving management of invasive
+Lionfish (\emph{Pterois volitans / miles}) are an invasive species in
+the Western Atlantic and the Caribbean. Improving management of invasive
 lionfish populations requires accurate estimates of total biomass, which
-in turn depend on accurate definition of the length-weight relationship.
-Here, we reviewed published length-weight relationships of lionfish
-taken from throughout their invasive range and found that lionfish of
-equal lengths have lower body mass in the Caribbean than in the Atlantic
-or Gulf of Mexico. Additionally, we report a new pair of length-weight
-parameters (\(a = 3.2056 \times 10^{-6}; b = 3.235\)) for organisms
-sampled in the central Mexican Caribbean region. The substantial spatial
-variation in length-weight parameters highlights the importance of using
-site-specific information when estimating lionfish biomass using length
-observations. These findings can have major implications for management
-in terms of predicting effects on local ecosystems, evaluating the
-effectiveness of removal programs, or estimating biomass available for
-harvest.
+depend on accurate estimates of the length-weight relationship. Lionfish
+exhibit a sedentary behavior that is likely to result in high levels of
+spatial variation in some life history characterstics, such as the
+length-weight relationship. We review 12 published length-weight
+relationships of lionfish taken throughout their invasive range and
+describe the spatial variation and implications of these differences.
+The spatial pattern observed here is consistent with those reported in
+genetic studies or age-at-length studies. We show that the use of
+\emph{ex situ} parameters can result in up to a three-fold
+overestimation of Total Weight, but that using parameters obtained
+nearby reduces this error. These findings can have major implications
+for management in terms of predicting effects on local ecosystems,
+evaluating the effectiveness of removal programs, or estimating biomass
+available for harvest.
 \end{abstract}
@@
 Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
-in the western Atlantic and the Caribbean, likely introduced through
+in the western Atlantic and Caribbean Sea, likely introduced through
 liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
@@
 biodiversity, spread rapidly, and are difficult to manage
-\citep{hixon_2016}. Invasive lionfish are primarily studied in coral
-reef ecosystems, where their impacts are far-reaching. For example,
-field experiments by \citet{albins_2008} showed that lionfish
-establishment led to reduced recruitment of native fishes by nearly 80\%
-over a five week period in Florida, and increased lionfish biomass
-coincided with a 65\% reduction in the biomass of native prey fishes
-along Bahamian coral reefs in just two years \citep{green_2012}.
+\citep{hixon_2016}.
+
+Invasive lionfish are primarily studied in coral reef ecosystems, where
+their impacts are far-reaching. For example, field experiments by
+\citet{albins_2008} showed that lionfish establishment led to reduced
+recruitment of native fishes by nearly 80\% over a five week period in
+Florida. \citet{green_2012} report that prey fish biomass declined 65\%
+over two years as lionfish biomass increased along Bahamian coral reefs.
 Lionfish have also established invasive populations in other habitats
-such as estuaries, mangroves , hard-bottomed areas , and mesophotic
-reefs
+such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs
 \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
 
-A substantial amount of research describes lionfish feeding ecology from
-North Carolina to Costa Rica
+A substantial amount of research describes lionfish feeding ecology
+throughout the invaded range
 \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
@@
 predicting invasion ranges under future climates \citep{grieve_2016}.
-Trophic impacts of lionfish can be minimized if local lionfish biomass
-is controled by by culling \citep{ariasgonzalez_2011}. However, the
-feasability of controling local populations remains a topic of debate
-\citep{cote_2014}.
+It\{s been proposed that trophic impacts of lionfish can be minimized if
+local lionfish biomass is controled by culling
+\citep{ariasgonzalez_2011}.
 
@@
 sedentary nature of adult lionfish \citep{jud_2012}. Culling programs
-are effective in reducing adult populations largely because lionfish
-exhibit high levels of site fidelity and rarely leave their home range
-in most cases \citep{Fishelson_1997,cote_2014,kochzius_2005} -- But see
-\citet{andradibrown_2017} for cases when deep-water populations maintain
-shallow-water populations. Fish with this sedentary behavior are likely
-to exhibit high levels of spatial variation in important life history
-characterstics such as growth or natural mortality rate
-\citep{hutchinson_2008,wilson_2012}. The importance of considering
-spatial heterogeneity is well-documented in terms of assessing and
-managing sedentary species \citep{gunderson_2008,guan_2013}, and such
-variation should be accounted for when evaluating the feasibility of
-establishing lionfish fisheries as well.
+are effective in reducing local adult populations largely because
+lionfish exhibit high levels of site fidelity and rarely leave their
+home range \citep{Fishelson_1997,cote_2014,kochzius_2005}. Fish with
+this sedentary behavior are likely to exhibit high levels of spatial
+variation in important life history characterstics such as growth or
+natural mortality rates \citep{hutchinson_2008,wilson_2012}. The
+importance of considering spatial heterogeneity is well-documented in
+terms of assessing and managing sedentary species
+\citep{gunderson_2008,guan_2013}, and such variation should be accounted
+for when evaluating the feasibility of establishing lionfish fisheries
+as well.
 
-Empirical modeling efforts examining the feasibility of establishing
-fisheries for lionfish involve modeling changes in biomass in response
-to changes in mortality (\emph{i.e.} culling). A common way to model
-this is via length-structured population models, where fish lengths are
-converted to weight in order to calculate total biomass
+Determining the feasibility of such initiatives require modeling changes
+in biomass in response to changes in mortality (\emph{i.e.} culling). A
+common way to model this is via length-structured population models,
+where fish lengths are converted to weight to calculate total biomass
 \citep{cote_2014,barbour_2011,andradibrown_2017}. The length-weight
@@
 this relationship can vary across regions as a response to biotic
-(e.g.~local food availability) and abiotic (e.g.~water temperature)
-conditions \citep{johnson_2016}. Literature suggests that site-specific
-parameters are necessary in order to accurately estimate biomass when
-length-weight relationships are spatially variable , and this
-variability becomes increasingly important when estimating the potential
-effectiveness of (and resources needed for) lionfish culling programs or
+(\emph{e.g.} local food availability) and abiotic (\emph{e.g.} water
+temperature) conditions \citep{johnson_2016}. Literature suggests that
+site-specific parameters are necessary in order to accurately estimate
+biomass when length-weight relationships are spatially variable, and
+this variability becomes increasingly important when estimating the
+potential effectiveness and feasability of lionfish culling programs or
 when identifying total biomass available for harvest by fishers
@@
 We reviewed 12 published studies and obtained 17 length-weight
-relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7,),
+relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7),
 and Caribbean (n = 10, Table \ref{tab:all_params}, Fig
@@
 available, and assumed both genders were included in a study if gender
-was unspecified. Two studies reported parameters for genders combined an
-separated \citep{aguilarperera_2016,fogg_2013}, while the rest presented
-pooled results. Reviewed studies presented information for organisms
-obtained at depths between 0.5 and 57 m. Three studies explicitly stated
-that their organisms were sampled with pole spears
+was unspecified. Only two studies reported parameters for each gender
+\citep{aguilarperera_2016,fogg_2013}. Reviewed studies presented
+information for organisms obtained at depths between 0.5 m and 57 m.
+Three studies explicitly stated that their organisms were sampled with
+pole spears
 \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five
@@
 weight in the length-weight relationship estimation, and thus their
-parameters likely underestimate whole wieght. Since no spine-less to
-whole weight conversions were available, these parameters were taken as
+parameters likely underestimate total wieght. Since no spine-less to
+total weight conversions were available, these parameters were taken as
 reported.
@@
 ratios across the different parameter pairs were tested with a one-way
-analysis of variance (ANOVA). All analyses were performed in R version
-3.5.0 \citep{rcore_2018} . Raw data and code used in this work are
-available at dryad.org.
+analysis of variance (ANOVA) and Tuskey's test was used for post-hoc
+tests. All analyses were performed in R version 3.5.0
+\citep{rcore_2018}. Raw data and code used in this work are available at
+dryad.org.
 
@@
 
-Inserting TL observations for the central Mexican Caribbean into
-\ref{eq:log-alo} Eq. 2 and converting to \ref{eq:log-alo-trans} resulted
-in the coefficient values \(b = 3.2347391\) and \(c = -5.4940866\)
-(\(R^2 = 0.977\), F(df = 1; 107) = 6928.67, \(p < 0.001\)). The
-length-weight coefficients estimated in this study were within the range
-identified by studies in other regions (Table \ref{tab:all_params}). The
-significant difference between this allometric factor (\(b\)) and the
-isometric growth factor \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicated
-that lionfish present allometric growth, which is consistent with other
-studies. Figure \ref{fig:l-w-carib} shows the relationship between TL
-and TW for this region, and more information on model fit is presented
-in Table S2.
+The length-weight relationship for organisms from the central Mexican
+Caribbean resulted in the coefficient values
+\(a = 3.2056297\times 10^{-6}\), \(b = 3.2347391\) and
+\(c = -5.4940866\) (\(R^2 = 0.977\), F(df = 1; 107) = 6928.67,
+\(p < 0.001\)). The allometric factor (\(b\)) was significantly
+different from \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicating that
+lionfish present allometric growth. The length-weight coefficients
+estimated in this study were within the range identified by studies in
+other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
+shows the relationship between TL and TW for this region, and more
+information on model fit is presented in Table S2.
 
-Parameters from models fit to males or females exclusively tend to have
-a higher steepness (\emph{i.e.} higher allometric parameter), with mean
-\(\pm\) standard deviation values of \(b = 3.27 \pm 0.06\) and
-\(b = 3.31 \pm 0.23\) for males and females respectively, compared to
-parameters from models for pooled genders with a mean \(\pm\) standard
-deviation value of \(b = 3.14 \pm 0.20\). In the case of the ponderal
-index (\(a\)) and its \(log_{10}\) transformation (\(c\)), values were
-higher for parameters for pooled genders. Figure \ref{fig:all_allo}
-shows the length-weight relationships with parameters from all studies.
+Figure \ref{fig:all_allo} shows the length-weight relationships with
+parameters from all studies. Parameters from models fit to males or
+females exclusively tend to have a higher steepness (\emph{i.e.} higher
+allometric parameter), with mean \(\pm\) standard deviation values of
+\(b = 3.27 \pm 0.06\) and \(b = 3.31 \pm 0.23\) for males and females
+respectively, compared to parameters from models for combined genders
+with a mean \(\pm\) standard deviation value of \(b = 3.14 \pm 0.20\).
+In the case of the ponderal index (\(a\)) and its \(log_{10}\)
+transformation (\(c\)), values were higher for parameters for combined
+genders.
 
@@
 central Mexican Caribbean when using the different pairs of parameters
-(\(F(df = 15; 1728) = 38.26; p < 0.001\)). The lowest weight estimates
-resulted from using the allometric parameters from Banco Chinchorro in
-the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates
-came from the Northern Atlantic\citet{barbour_2011}. The calculated
-ratio of predicted-to-observed weight ranged from 0.80 \(\pm\) 0.19 to
-1.76 \(\pm\) 0.50 (mean \(\pm\) SD). Predicted-to-observed weight ratios
-are presented in Figure \ref{fig:bio_ratio}. Spine-less weight
-parameters from \citet{fogg_2013} still produced predicted-to-observed
-weight rations \textgreater{} 1.
+(\(F(df = 15; 1728) = 38.26; p < 0.001\)). Weight estimates using
+parameters from the Gulf of Mexico and North-Western Atlantic were
+higher on average than those from the Caribbean. The average (\(\pm\)
+SD) predicted-to-observed weight ratios from these three regions were
+1.24 \(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398,
+respectively. The lowest weight estimates resulted from using the
+allometric parameters from Banco Chinchorro in the Caribbean
+\citet{sabidoitz_2016}, and the highest weight estimates came from the
+Northern Atlantic \citep{barbour_2011}. The calculated ratio of
+predicted-to-observed weight ranged from 0.80 \(\pm\) 0.19 to 1.76
+\(\pm\) 0.50 (mean \(\pm\) SD). Tukey's post-hoc test suggests that
+weight ratios for the central Mexican Caribbean were not differnt from
+those obntained with parameters from Little Cayman, the Bahamas, and
+some sites in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)).
+Predicted-to-observed weight ratios are presented in Figure
+\ref{fig:bio_ratio}. Spine-less weight parameters from \citet{fogg_2013}
+still produced predicted-to-observed weight ratios \textgreater{} 1.
 
@@
 GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
-NorthAtlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al.,2011\\
+North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al.,2011\\
 \bottomrule
@@
 studies and this study. Colors indicate studies from which the
-parameters were extracted. Solid lines indicate that the fit was
-performed for males and females pooled together. Dotted lines indicate
-that the regression was performed on females, and dashed lines indicate
-it was performed for males. The dashed black line represents the
-relationship estimated in this study.}
+parameters were extracted. Dotted, dashed and solid lines show models
+for males, females, and combined sexes, respectively. The dashed black
+line represents the relationship estimated in this study.}
 \end{figure}
@@
 \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:bio_ratio}Violin plot of predicted to observed
+\caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
 weight ratios for 18 pairs of allometric parameters. Red and blue
 circles indicate median and mean values, respectively. Like letters
-indicate values that do not differ significantly (Tukey's HSD; p
-\textless{} 0.05).}
+indicate values that do not differ significantly.}
 \end{figure}
@@
 organisms from the Caribbean and Gulf of Mexico / North-Western
-Atlantic. Weight estimates using parameters from the Gulf of Mexico and
-North-Western Atlantic were higher on average than those from the
-Caribbean. The average predicted-to-observed weight ratios from these
-three regions were insert 1.24 \(\pm\) 0.309, 1.76 \(\pm\) 0.496, and
-Caribbean 1.17 \(\pm\) 0.398, respectively. These length-weight
-differences mirror similar findings of regional variability in
-age-at-length relationships of lionfish across both their invaded and
-native regions \citep{pusack_2016}. These differences may be driven by
-genetic variation or by organisms being exposed to distinct
-environmental conditions. For example, \citet{betancurr_2011} used
-mitochondrial DNA to demonstrate the existence of two distinct
-population groups, identified as the ``Caribbean group'' and ``Northern
-Group'', and \citet{fogg_2015} alternatively suggested that
-age-at-length differences may be driven by climate. Differences in
-weight-at-length could also reflect differences in energy input
-(\emph{i.e.} in some regions, lionfish eat more) or differential usage
-of this energy (\emph{e.g.} regional differences in predator abundances
-lead to different usage of energy), or a combination of both. Future
-research is needed to determine which processes are at work here.
+Atlantic. The groupings of predicted-to-observed weight ratios were
+consistent with the spatial distribution of the studies, suggesting that
+these differences are mediated by space. These length-weight differences
+mirror similar findings of regional variability in age-at-length
+relationships of lionfish across both their invaded and native regions
+\citep{pusack_2016}. These patterns may be driven by genetic variation
+or by organisms being exposed to distinct environmental conditions. For
+example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate
+the existence of two distinct population groups, identified as the
+``Caribbean group'' and ``Northern Group'', and \citet{fogg_2015}
+alternatively suggested that age-at-length differences may be driven by
+climate. Differences in weight-at-length could also reflect differences
+in energy input or differential usage of this energy, or a combination
+of both. Future research is needed to determine which processes are at
+work here.
 
@@
 \citet{wilson_2012} show that small-scale variations in length-at-age
-and fishing mortality in other Scorpaeniformes (\emph{Sebastes
-rastrelliger}) translate to differential landings, effort, and catch per
-unit effort in the live fish fishery of California, and that these
-differences must be taken into account in management plans. The lionfish
-case poses the opposite scenario, where the manager desires to
-erradicate species. To accurately gauge both the effectiveness of
-lionfish removal efforts and the resources needed to successfully manage
-an invasion, we must acknowledge and understand regional biological
-differences in important variables such as allometric growth parameters.
+and fishing mortality in other Scorpaeniformes translate to differential
+landings, effort, and catch per unit effort in the live fish fishery of
+California, and that these differences must be taken into account in
+management plans. The lionfish case poses the opposite scenario, where
+the manager desires to erradicate species. To accurately gauge both the
+effectiveness of lionfish removal efforts and the resources needed to
+successfully manage an invasion, we must acknowledge and understand
+regional biological differences in important variables such as
+allometric growth parameters.
 
@@
 two scenarios, one using length-at-age and length-to-weight parameters
-from North Carolina and one using parameters from Little Cayman. They
-showed that using the different parameters caused up to a four-year
+from North Carolina and one using parameters from Little Cayman. Their
+results show that using different parameters caused up to a four-year
 difference in the time required for the simulated lionfish population to
@@
 given length can result in up to a threefold TW overestimation. These
-differences become especially important when allocating resources for
-removal programs, incentivizing its fishery as alternative livelihoods,
-or estimating ecosystem impacts. Research efforts focused on invasive
-lionfish populations need to use parameters calculated for their region
-to the extent possible, or at least use reasonable sets of different
-parameters that provide upper and lower bounds in their results. This
-work additionally highlights the need for more basic research that
-furthers our understanding of the invasive lionfish.
+spatially-driven differences become especially important when allocating
+resources for lionfish removal programs, incentivizing its fishery as a
+source of alternative livelihoods, or estimating ecosystem impacts.
+Research efforts focused on invasive lionfish populations need to use
+parameters calculated for their region to the extent possible, or at
+least use reasonable sets of different parameters that provide upper and
+lower bounds in their results.
 

### 2018-06-05 docs/Manuscript.Rmd
Mostly minor changes.  One "major" comment in line 184.
Other notes:

Put citations in chronological order (or alphabetical - whatever the journal does. But they need to be in order).

Reduce the number of citations per parentheses (line 50).

@@
 ---
-title: Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic
+title: Allometric growth of invasive lionfish varies by region in the Western Atlantic
 abstract: "Lionfish (*Pterois volitans / miles*) are an invasive species in the Western Atlantic and the Caribbean.
-Improving management of invasive lionfish populations requires accurate estimates of total biomass, which depend on accurate estimates of the length-weight relationship.
-Lionfish exhibit a sedentary behavior that is likely to result in high levels of spatial variation in some life history characterstics, such as the length-weight relationship.
-We review 12 published length-weight relationships of lionfish taken throughout their invasive range and describe the spatial variation and implications of these differences.
-The spatial pattern observed here is consistent with those reported in genetic studies or age-at-length studies.
-We show that the use of *ex situ* parameters can result in up to a three-fold overestimation of Total Weight, but that using parameters obtained nearby reduces this error.
+Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
+Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics, so we review 12 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
+The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
+We show that the use of *ex situ* parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error.
 These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest."
@@
 For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida.
-\citet{green_2012} report that prey fish biomass declined 65% over two years as lionfish biomass increased along Bahamian coral reefs.
+\citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs.
 Lionfish have also established invasive populations in other habitats such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
 
-A substantial amount of research describes lionfish feeding ecology throughout the invaded range \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
+<!-- You need to put references in chronological order -->
+
+A substantial amount of research describes lionfish feeding ecology throughout its invaded range \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
 A meta-analysis by  \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
-Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{albins_2008, green_2012,rocha_2015}.
-(However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes).
-Major efforts have been made to understand the possible impacts of the invasion by tracking the spread of established lionfish populations through time \citep{schofield_2009,schofield_2010} and by predicting invasion ranges under future climates \citep{grieve_2016}.
-It{s been proposed that trophic impacts of lionfish can be minimized if local lionfish biomass is controled by culling \citep{ariasgonzalez_2011}.
+Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{green_2012,rocha_2015}.
+However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes.
+Major efforts have been made to understand possible impacts of the lionfish invasion by tracking the spread of established populations through time and by predicting invasion ranges under future climates \citep{schofield_2009,schofield_2010,grieve_2016}.
+Also, \citet{ariasgonzalez_2011} proposed that trophic impacts of lionfish can be minimized if local lionfish biomass is controlled by culling.
+
+<!-- You cite the same papers over and over.
+It's good to have them all in there at least once, but you don't need to cite every paper every time.
+For example, you cite Chin 2016 6 times in the introduction.
+You can probably take half of those out.
+When you over-list references, it makes it seems like you're overcompensating for a lack of info in your own work or that you're too lazy to figure out which 2-3 references are actually the most relevant to the point you're making -->
 
@@
 In addition, culling programs can help stabilize or grow native prey fish populations \citep{cote_2014}.
-Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from their persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
+Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
 However, promoting lionfish consumption might create a level of demand capable of sustaining a stable fishery, which can help control shallow-water populations while providing alternative livelihoods and avoiding further impacts to local reef biota \citep{chin_2016}.
@@
 The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
-One contributing factor to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}.
+One factor contributing to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}.
 Culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range \citep{Fishelson_1997,cote_2014,kochzius_2005}.
-Fish with this sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates \citep{hutchinson_2008,wilson_2012}.
-The importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,guan_2013}, and such variation should be accounted for when evaluating the feasibility of establishing lionfish fisheries as well.
+Fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates, and the importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
+Such variation should be accounted for when evaluating the viability of establishing lionfish fisheries as well.
 
-Determining the feasibility of such initiatives require modeling changes in biomass in response to changes in mortality (*i.e.* culling).
+Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in mortality (*i.e.* culling).
 A common way to model this is via length-structured population models, where fish lengths are converted to  weight to calculate total biomass \citep{cote_2014,barbour_2011,andradibrown_2017}.
-The length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when length-weight relationships are spatially variable, and this variability becomes increasingly important when estimating the potential effectiveness and feasability of lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
-In addition to environmentally-driven spatial variation, genetic analysis of invasive lionfish suggest biological differences due to the existence of two genetically distinct subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
-To date, no studies have examined region-wide differences in length-weight parameters despite the large number of studies reporting this relationship for lionfish.
+The allometric length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
+Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when allometric relationships are spatially variable, and this variability is increasingly important when estimating the potential effectiveness of lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
+Genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
+However, no studies have examined region-wide differences in allometric growth parameters despite the large number of studies reporting the length-weight relationship for lionfish.
 
-The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish in the Caribbean and Western Atlantic and evaluate the implications of these spatial differences.
-Length-weight relationships for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
-This study also provides the first length-weight relationship for the central Mexican Caribbean.
+Here, we compare previously published length-weight relationships for lionfish populations in North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+We also collected lionfish length and weight data in the central Mexican Caribbean and report the first allometric growth equation for this region.
+The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish across the Caribbean and Western Atlantic and to discuss implications of these spatial differences.
 
@@
 
-We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7), and Caribbean (n = 10, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
-We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available, and assumed both genders were included in a study if gender was unspecified.
-Only two studies reported parameters for each gender \citep{aguilarperera_2016,fogg_2013}.
+We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7), and Caribbean (n = 9, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
+We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available.
+Only two studies reported parameters for each gender \citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were included in a study if gender was unspecified.
 Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
 Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
-\citet{fogg_2013} use spine-less weight in the length-weight relationship estimation, and thus their parameters likely underestimate total wieght.
-Since no spine-less to total weight conversions were available, these parameters were taken as reported.
+\citet{fogg_2013} use spineless weight in their calculations, so their parameters likely underestimated total wieght.
+Since no spineless to total weight conversions were available, these parameters were taken as reported.
 
@@
 
-Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
-When $b = 3$, it is said that the organism exhibits a perfect isometric growth.
-Transforming this equation via base-10 logarithms:
+Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter. Transforming this equation via base-10 logarithms:
 
@@
 The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Squares Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-The $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$).
+When the $b = 3$, it is said that the organism exhibits a perfect isometric growth, so the $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$).
 Coefficients were tested with a two-tailed Student's t, and the significance of the regression was corroborated with an F-test.
@@
 
-Combining the length-weight parameters extracted from the literature and the additional pair calculated here, we obtain a total of 18 pairs.
-We use the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
+We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here.
+We used the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
 We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tuskey's test was used for post-hoc tests.
+Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tukey's test was used for post-hoc tests.
 All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
@@
 
-Figure \ref{fig:all_allo} shows the length-weight relationships with parameters from all studies.
+Figure \ref{fig:all_allo} shows all 18 weight-at-length relationships.
 Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for combined genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
 In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for combined genders.
+
+<!-- In the above paragraph, I don't understand why we care whether individual gender coefficients are different than the pooled genders.
+You need to explain why that matters somewhere in the discussion or something.
+Could pooling samples together be a mistake?
+If there are substantially more males or females in a given study, could that skew the results?
+How much?
+Enough to make the equation unreliable?
+Or are these gender differences fairly minor?
+I don't think you can just say "pooling genders leads to lower steepness" and then gloss over it/ ignore ift for the rest of the paper -->
 
@@
 The calculated ratio of predicted-to-observed weight  ranged from `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not differnt from those obntained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
+Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
-Spine-less weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.
+Spineless weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.
+
+<!-- Include the actual mean values (+/- SD) in the sentence "The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic \citep{barbour_2011}" -->
 
@@
 
-We  detected substantial differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic.
-The groupings of predicted-to-observed weight ratios were consistent with the spatial distribution of the studies, suggesting that these differences are mediated by space.
-These length-weight differences mirror similar findings of regional variability in age-at-length relationships of lionfish across both their invaded and native regions \citep{pusack_2016}.
-These patterns may be driven by genetic variation or by organisms being exposed to distinct environmental conditions.
-For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be driven by climate.
-Differences in weight-at-length could also reflect differences in energy input or differential usage of this energy, or a combination of both.
+We  detected substantial differences in weight-at-length between organisms from the Caribbean, Gulf of Mexico, and North-Western Atlantic.
+Groupings of predicted-to-observed weight ratios aligned with the spatial distribution of the examined studies, suggesting that these differences are mediated by space.
+These regional allometric differences mirror similar patterns in age-at-length of lionfish across both their invaded and native regions \citep{pusack_2016}.
+Variation may be driven by genetics or by organisms' exposure to distinct environmental conditions.
+For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be climate-driven.
+Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both.
 Future research is needed to determine which processes are at work here.
@@
 For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
-The lionfish case poses the opposite scenario, where the manager desires to erradicate species.
+The lionfish case poses the opposite scenario, where the manager desires to eradicate species.
 To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.
@@
 Their results show that using different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased.
-Here, we show that using one set of length-weight parameters versus another for a given length can result in up to a threefold TW overestimation.
-These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing its fishery as a source of alternative livelihoods, or estimating ecosystem impacts.
+Here, we show that using one set of length-weight parameters versus another for a given length can result in up to a threefold overestimation of TW.
+These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts.
 Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or at least use reasonable sets of different parameters that provide upper and lower bounds in their results.
 
-\section*{Aknowledgements}
+\section*{Acknowledgements}
 

### 2018-06-13 docs/Manuscript.Rmd
Incoporated Sean's comments, but still need to proof-read

@@
 ---
-title: Allometric growth of invasive lionfish varies by region in the Western Atlantic
-abstract: "Lionfish (*Pterois volitans / miles*) are an invasive species in the Western Atlantic and the Caribbean.
-Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
-Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics, so we review 12 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
-The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
-We show that the use of *ex situ* parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error.
-These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest."
+header-includes:
+  - \usepackage{natbib}
+  - \usepackage{setspace}
+  - \doublespacing
+  - \usepackage{lineno}
+  - \linenumbers
+  - \usepackage{float}
+  - \floatplacement{figure}{H}
+title: \LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region in the Western Atlantic}
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     keep_tex: yes
     number_sections: no
-    template: peerj_template.tex
+    toc: no
+bibliography: references.bib
+csl: elsevier-harvard.csl
 ---
 
-<!-- Alternative titles: -->
-<!-- Region-wide variation of allometric growth in invasive lionfish -->
+Juan Carlos Villaseñor-Derbez^1^*, Sean Fitzgerald^1^
+
+^1^ Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States
+
+*jvillasenor\@bren.ucsb.edu
+
+---
+
+\begin{abstract}
+Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean.
+Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
+Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics, so we review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
+The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
+We show that the use of \textit{ex situ} parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error.
+These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
+\end{abstract}
+
+---
 
@@
 
-\section*{Introduction}
+# Introduction
 
@@
 
-Invasive lionfish are primarily studied in coral reef ecosystems, where their impacts are far-reaching.
-For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida.
+A substantial amount of research describes lionfish impacts throughout its invaded range.For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida.
 \citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs.
-Lionfish have also established invasive populations in other habitats such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
-
-<!-- You need to put references in chronological order -->
-
-A substantial amount of research describes lionfish feeding ecology throughout its invaded range \citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
 A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
-Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{green_2012,rocha_2015}.
-However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes.
-Major efforts have been made to understand possible impacts of the lionfish invasion by tracking the spread of established populations through time and by predicting invasion ranges under future climates \citep{schofield_2009,schofield_2010,grieve_2016}.
-Also, \citet{ariasgonzalez_2011} proposed that trophic impacts of lionfish can be minimized if local lionfish biomass is controlled by culling.
-
-<!-- You cite the same papers over and over.
-It's good to have them all in there at least once, but you don't need to cite every paper every time.
-For example, you cite Chin 2016 6 times in the introduction.
-You can probably take half of those out.
-When you over-list references, it makes it seems like you're overcompensating for a lack of info in your own work or that you're too lazy to figure out which 2-3 references are actually the most relevant to the point you're making -->
+Lionfish have also established invasive populations in other habitats such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017}.
+Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}).
+These trophic impacts can be minimized if local lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
 
 Governments and non-profit organizations have sought to reduce lionfish densities through removal programs and incentivizing its consumption \citep{chin_2016}.
-In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{sandel_2015,chin_2016,deleon_2013}.
-In addition, culling programs can help stabilize or grow native prey fish populations \citep{cote_2014}.
-Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from persistent populations in mesophotic coral ecosystems \citep{barbour_2011,andradibrown_2017}.
-However, promoting lionfish consumption might create a level of demand capable of sustaining a stable fishery, which can help control shallow-water populations while providing alternative livelihoods and avoiding further impacts to local reef biota \citep{chin_2016}.
+In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{deleon_2013,sandel_2015}.
+Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from persistent populations in mesophotic ecosystems \citep{barbour_2011,andradibrown_2017}.
+However, promoting lionfish consumption might create a level of demand capable of incentivizing a stable fishery while controlling shallow-water populations, thus creating alternative livelihoods and avoiding further impacts to local biota.
 
-The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
-One factor contributing to the success of many removal programs is the sedentary nature of adult lionfish \citep{jud_2012}.
-Culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and rarely leave their home range \citep{Fishelson_1997,cote_2014,kochzius_2005}.
-Fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates, and the importance of considering spatial heterogeneity is well-documented in terms of assessing and managing sedentary species \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
-Such variation should be accounted for when evaluating the viability of establishing lionfish fisheries as well.
+The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,usseglio_2017}.
+Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in mortality (*i.e.* culling).
+A common way to model this is via length-structured population models, where fish lengths are converted to  weight to calculate total biomass \citep{barbour_2011,cote_2014,andradibrown_2017}.
+The allometric length-weight relationship is thus an essential component of these models, but this relationship can vary across regions as a response to biotic and abiotic conditions \citep{johnson_2016}.
 
-Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in mortality (*i.e.* culling).
-A common way to model this is via length-structured population models, where fish lengths are converted to  weight to calculate total biomass \citep{cote_2014,barbour_2011,andradibrown_2017}.
-The allometric length-weight relationship is therefore an essential component of these models, but this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}.
-Literature suggests that site-specific parameters are necessary in order to accurately estimate biomass when allometric relationships are spatially variable, and this variability is increasingly important when estimating the potential effectiveness of lionfish culling programs or when identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
-Genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
-However, no studies have examined region-wide differences in allometric growth parameters despite the large number of studies reporting the length-weight relationship for lionfish.
+Outcomes of previous studies suggest lionfish are likely to exhibit spatial heterogeneity in the length-weight relationship, which we summarize in two main causes.
+First, culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and small home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
+It is know that fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
+Second, genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
+Site-specific parameters are necessary to accurately estimate biomass when allometric relationships are spatially variable, and this variability is increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
+However, the region-wide differences in allometric growth parameters has remained unexplored for lionfish, despite the large number of site-specific studies reporting the length-weight relationship.
 
-Here, we compare previously published length-weight relationships for lionfish populations in North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
+Here, we compare previously published length-weight relationships for lionfish populations in North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
 We also collected lionfish length and weight data in the central Mexican Caribbean and report the first allometric growth equation for this region.
@@
 
-\clearpage
-
-\section*{Materials and Methods}
+# Materials and Methods
 
@@
 Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
-Three studies explicitly stated that their organisms were sampled with pole spears \citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014}, and two studies did not specify how organisms were sampled \citep{deleon_2013,darling_2011}.
+Three studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016,sabidoitz_2016}, and two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
 \citet{fogg_2013} use spineless weight in their calculations, so their parameters likely underestimated total wieght.
@@
 
-We also collected data from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Table S1).
-Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
-All observed lionfish (n = 109) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by eliminating gear selectivity.
-Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
-
-```{r, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
-Circle sizes indicate sample size from each study, colors indicate the $b$ coefficient from Eq.
-\\ref{eq:allometric}.", fig.height = 3.5}
+```{r}
 
@@
 # Map with SF
-ggplot() +
+fig_map <- ggplot() +
   geom_sf(data = W) +
@@
 ```
+
+We also collected data from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Table S1).
+Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
+All observed lionfish (n = 109) were collected using hand nets and numbered collection bottles.
+The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by eliminating gear selectivity.
+Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
 
@@
   unnest() %>% 
-  mutate(Biomass_ratio = (a*(Length^b))/Weight)
+  mutate(pWeight = a*(Length^b),
+    Biomass_ratio = pWeight / Weight)
 
@@
 
-Fstring <- paste0("F(df = 1; ",nobs(model)-2, ") = ", formatC(Fstring$statistic[2], digits = 2, format = "f"))
+Fstring <- paste0("F(df = 1; ", nobs(model)-2, ") = ", formatC(Fstring$statistic[2], digits = 2, format = "f"))
 ```
 
-\section*{Results}
+# Results
 
@@
 The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
-Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region, and more information on model fit is presented in Table S2.
+Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region, and model fit statistics is presented in Table \ref{tab:reg_table}.
 
-Figure \ref{fig:all_allo} shows all 18 weight-at-length relationships.
-Parameters from models fit to males or females exclusively tend to have a higher steepness (*i.e.* higher allometric parameter), with mean $\pm$ standard deviation values of $b = `r formatC(mean(review$b[review$Gender == "Male"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Male"]), digits = 2, format = "f")`$ and $b = `r formatC(mean(review$b[review$Gender == "Female"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Female"]), digits = 2, format = "f")`$ for males and females respectively, compared to parameters from models for combined genders with a mean $\pm$ standard deviation value of $b = `r formatC(mean(review$b[review$Gender == "Both"]), digits = 2, format = "f")` \pm `r formatC(sd(review$b[review$Gender == "Both"]), digits = 2, format = "f")`$.
-In the case of the ponderal index ($a$) and its $log_{10}$ transformation ($c$), values were higher for parameters for combined genders.
+```{r}
+TidyModel <- model%>%
+  lmtest::coeftest(vcov = sandwich::vcovHC(., type = "HC1")) %>%
+  broom::tidy()
 
-<!-- In the above paragraph, I don't understand why we care whether individual gender coefficients are different than the pooled genders.
-You need to explain why that matters somewhere in the discussion or something.
-Could pooling samples together be a mistake?
-If there are substantially more males or females in a given study, could that skew the results?
-How much?
-Enough to make the equation unreliable?
-Or are these gender differences fairly minor?
-I don't think you can just say "pooling genders leads to lower steepness" and then gloss over it/ ignore ift for the rest of the paper -->
-
-There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 15; 1728) = 38.26; p < 0.001$).
-Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean.
-The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
-The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic \citep{barbour_2011}.
-The calculated ratio of predicted-to-observed weight  ranged from `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD).
-Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
-Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
-Spineless weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.
-
-<!-- Include the actual mean values (+/- SD) in the sentence "The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean \citet{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic \citep{barbour_2011}" -->
+robust_se <- TidyModel$std.error %>%
+  set_names(TidyModel$term)
+wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))
+f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))
+```
 
@@
   substitute(italic(R)^2~"="~r2,
-             list(r2 = formatC(summary(model)$r.squared, digits = 4))) %>% 
+             list(r2 = formatC(summary(model)$r.squared, digits = 3))) %>% 
     as.expression() %>% 
@@
 
-```{r, fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
-
+```{r}
 fit <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
@@
 
-ggExtra::ggMarginal(p = fit,
+fig_l_w_carib <- ggExtra::ggMarginal(p = fit,
                                      type = "density",
@@
 
+There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 17; 1944) = 61.55; p < 0.001$).
+The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{barbour_2011}.
+To put this in context, true observed weights were `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` gr.
+These correspond to predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
+
+The calculated ratio of predicted-to-observed weight ranged from `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")`, indicating that *ex situ* parameters can result in major under- and overestimations.
+Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
+Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}).
+The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
+Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
+Spineless weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.
+
 ```{r}
-review %>% 
-  select(Region, Gender2, N, a, b, c, r2, Study) %>% 
-  filter(!Study == "Fishbase") %>% 
-  arrange(Region) %>% 
-  mutate(r2 = ifelse(is.na(r2), "-", r2),
-         N = ifelse(is.na(N), "-", N),
-         a = formatC((a*1e5), digits = 2)) %>% 
-  knitr::kable(format = "latex",
-               row.names = F,
-               digits =  c(0, 0, 0, 0, 2, 2),
-               booktabs = T,
-               # longtable = T,
-               col.names = c("Region", "Sex", "n", "a", "b", "c", "$R^2$", "Reference"),
-               caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
-1 (presented in $\\times 10^{-5}$), c = y-intercept for Eq.
-3, b = exponent or slope for Eq.
-1 or Eq.
-3, respectively.
-The $R^2$ column indicates reported model fit.")
-```
-
-```{r, fig.height = 3.6, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
-Colors indicate studies from which the parameters were extracted.
-Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
-The dashed black line represents the relationship estimated in this study."}
-
-review %>% 
+fig_all_allo <- review %>% 
   filter(!Study == "This study") %>% 
@@
 
-```{r, fig.height = 4, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
-Red and blue circles indicate median and mean values, respectively.
-Like letters indicate values that do not differ significantly."}
+```{r}
 groups$groups%<>%
@@
 
-Predicted_biomass %>% 
+fig_bio_ratio <- Predicted_biomass %>% 
   mutate(Study = paste0(Study, " (", Gender_site, ")")) %>%
@@
   geom_hline(yintercept = 1, linetype = "dashed") +
-  labs(y = "Weight (Predicted/Observed)", x = "") +
+  labs(y = "Weight ratio (Predicted/Observed)", x = "") +
   coord_flip() +
@@
         legend.background = element_rect(fill = "transparent"),
-        axis.text = element_text(size = 10)) +
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12)) +
   geom_text(aes(y = 3.7, label = groups), family = "Times", fontface = "plain") +
@@
 
-\clearpage
-
-\section*{Discussion}
+# Discussion
 
@@
 
-\section*{Acknowledgements}
+# Acknowledgements
 
@@
 \bibliography{references}
+
+\clearpage
+
+# Figures and Tables
+
+```{r, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
+Circle sizes indicate sample size from each study, colors indicate the $b$ coefficient from Eq.
+\\ref{eq:allometric}.", fig.height = 3.5}
+fig_map
+```
+
+```{r, results = "asis"}
+stargazer(model,
+          dep.var.caption = "$log_{10}(TW)$",
+          dep.var.labels.include = F,
+          header = F,
+          se = list(robust_se),
+          type = "latex",
+          t.auto = T,
+          p.auto = T,
+          intercept.bottom = F,
+          single.row = T,
+          report = "vcs*",
+          omit.stat = c("f", "rsq"),
+          add.lines = list(f_string),
+          covariate.labels = c("c", "b"),
+          dep.var.labels = "log10(TW)", title = "\\label{tab:reg_table}Coefficients of the linear model fit to Eq \\ref{eq:log-alo-trans}.
+Numbers in parenthesees represent heteroskedastic-robust standard errors.")
+```
+
+```{r,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
+Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
+fig_l_w_carib
+```
+
+```{r}
+review %>% 
+  select(Region, Gender2, N, a, b, c, r2, Study) %>% 
+  filter(!Study == "Fishbase") %>% 
+  arrange(Region) %>% 
+  mutate(r2 = ifelse(is.na(r2), "-", r2),
+         N = ifelse(is.na(N), "-", N),
+         a = formatC((a*1e5), digits = 2)) %>% 
+  knitr::kable(format = "latex",
+               row.names = F,
+               digits =  c(0, 0, 0, 0, 2, 2),
+               booktabs = T,
+               # longtable = T,
+               col.names = c("Region", "Sex", "n", "a", "b", "c", "$R^2$", "Reference"),
+               caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
+1 (presented in $\\times 10^{-5}$), c = y-intercept for Eq.
+3, b = exponent or slope for Eq.
+1 or Eq.
+3, respectively.
+The $R^2$ column indicates reported model fit.")
+```
+
+```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
+Colors indicate studies from which the parameters were extracted.
+Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
+The dashed black line represents the relationship estimated in this study."}
+fig_all_allo
+```
+
+```{r, fig.height = 5, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
+Red and blue circles indicate median and mean values, respectively.
+Like letters indicate values that do not differ significantly."}
+fig_bio_ratio
+```

### 2018-06-13 docs/Manuscript.tex
Incoporated Sean's comments, but still need to proof-read

@@
-%% Submissions for peer-review must enable line-numbering 
-%% using the lineno option in the \documentclass command.
-%%
-%% Preprints and camera-ready submissions do not need 
-%% line numbers, and should have this option removed.
-%%
-%% Please note that the line numbering option requires
-%% version 1.1 or newer of the wlpeerj.cls file, and
-%% the corresponding author info requires v1.2
+\documentclass[]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{longtable,booktabs}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-\documentclass[fleqn,10pt,lineno]{wlpeerj} % for journal submissions
-% \documentclass[fleqn,10pt]{wlpeerj} % for preprint submissions
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-\title{Invasive lionfish present region-wide variation of allometric growth in
-the Western Atlantic}
+%%% Change title format to be more compact
+\usepackage{titling}
 
-\author[1]{Juan Carlos Villaseñor-Derbez}
-\author[1]{Sean Fitzgerald}
-\affil[1]{Bren School of Environmental Sciences and Management, University of California
-  Santa Barbara, Santa Barbara, California, USA}
-\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@ucsb.edu}
+% Create subtitle command for use in maketitle
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
 
-% \keywords{Keyword1, Keyword2, Keyword3}
+\setlength{\droptitle}{-2em}
+  \title{\LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region in the Western Atlantic}}
+  \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+  \author{}
+  \preauthor{}\postauthor{}
+  \date{}
+  \predate{}\postdate{}
+
+\usepackage{natbib}
+\usepackage{setspace}
+\doublespacing
+\usepackage{lineno}
+\linenumbers
+\usepackage{float}
+\floatplacement{figure}{H}
+
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+\theoremstyle{definition}
+\newtheorem{example}{Example}
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
+\maketitle
+
+Juan Carlos Villaseñor-Derbez\textsuperscript{1}*, Sean
+Fitzgerald\textsuperscript{1}
+
+\textsuperscript{1} Bren School of Environmental Science and Management,
+University of California Santa Barbara, Santa Barbara, California,
+United States
+
+*jvillasenor@bren.ucsb.edu
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
 \begin{abstract}
-Lionfish (\emph{Pterois volitans / miles}) are an invasive species in
-the Western Atlantic and the Caribbean. Improving management of invasive
-lionfish populations requires accurate estimates of total biomass, which
-depend on accurate estimates of the length-weight relationship. Lionfish
-exhibit a sedentary behavior that is likely to result in high levels of
-spatial variation in some life history characterstics, such as the
-length-weight relationship. We review 12 published length-weight
-relationships of lionfish taken throughout their invasive range and
-describe the spatial variation and implications of these differences.
-The spatial pattern observed here is consistent with those reported in
-genetic studies or age-at-length studies. We show that the use of
-\emph{ex situ} parameters can result in up to a three-fold
-overestimation of Total Weight, but that using parameters obtained
-nearby reduces this error. These findings can have major implications
-for management in terms of predicting effects on local ecosystems,
-evaluating the effectiveness of removal programs, or estimating biomass
-available for harvest.
+Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean.
+Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
+Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics, so we review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
+The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
+We show that the use of \textit{ex situ} parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error.
+These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
 \end{abstract}
 
-\begin{document}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-\flushbottom
-\maketitle
-\thispagestyle{empty}
-
-\section*{Introduction}
+\section{Introduction}\label{introduction}
 
@@
 
-Invasive lionfish are primarily studied in coral reef ecosystems, where
-their impacts are far-reaching. For example, field experiments by
-\citet{albins_2008} showed that lionfish establishment led to reduced
-recruitment of native fishes by nearly 80\% over a five week period in
-Florida. \citet{green_2012} report that prey fish biomass declined 65\%
-over two years as lionfish biomass increased along Bahamian coral reefs.
-Lionfish have also established invasive populations in other habitats
-such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs
-\citep{jud_2011,barbour_2010,muoz_2011,andradibrown_2017,claydon_2012}.
-
-A substantial amount of research describes lionfish feeding ecology
-throughout the invaded range
-\citep{muoz_2011,morris_2009,cote_2013,dahl_2014,valdezmoreno_2012,villaseorderbez_2014,hackerott_2017,sandel_2015}.
-A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey
+A substantial amount of research describes lionfish impacts throughout
+its invaded range.For example, field experiments by \citet{albins_2008}
+showed that lionfish establishment led to reduced recruitment of native
+fishes by nearly 80\% over a five week period in Florida.
+\citet{green_2012} reported that prey fish biomass declined by 65\% over
+two years as lionfish biomass increased along Bahamian coral reefs. A
+meta-analysis by \citet{peake_2018} showed that invasive lionfish prey
 on at least 167 different species across the tropical and temperate
-North Atlantic. Their feeding behavior and high consumption rates can
-reduce recruitment and population sizes of native reef-fish species, and
-can further endanger reef fish
-\citep{albins_2008, green_2012,rocha_2015}. (However, see
-\citet{hackerott_2017} for a case where there was no evidence that
-lionfish affected the density, richness, or community composition of
-prey fishes). Major efforts have been made to understand the possible
-impacts of the invasion by tracking the spread of established lionfish
-populations through time \citep{schofield_2009,schofield_2010} and by
-predicting invasion ranges under future climates \citep{grieve_2016}.
-It\{s been proposed that trophic impacts of lionfish can be minimized if
-local lionfish biomass is controled by culling
-\citep{ariasgonzalez_2011}.
+North Atlantic. Lionfish have also established invasive populations in
+other habitats such as estuaries, mangroves, hard-bottomed areas, and
+mesophotic reefs
+\citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017}.
+Their feeding behavior and high consumption rates can reduce recruitment
+and population sizes of native reef-fish species, and can further
+endanger reef fish (\citet{green_2012,rocha_2015}; but see
+\citet{hackerott_2017}). These trophic impacts can be minimized if local
+lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
 
@@
 reduce --but not quite eliminate-- lionfish abundances at local scales
-\citep{sandel_2015,chin_2016,deleon_2013}. In addition, culling programs
-can help stabilize or grow native prey fish populations
-\citep{cote_2014}. Complete eradication of lionfish through fishing is
-unlikely because of their rapid recovery rates and ongoing recruitment
-to shallow-water areas from their persistent populations in mesophotic
-coral ecosystems \citep{barbour_2011,andradibrown_2017}. However,
-promoting lionfish consumption might create a level of demand capable of
-sustaining a stable fishery, which can help control shallow-water
-populations while providing alternative livelihoods and avoiding further
-impacts to local reef biota \citep{chin_2016}.
+\citep{deleon_2013,sandel_2015}. Complete eradication of lionfish
+through fishing is unlikely because of their rapid recovery rates and
+ongoing recruitment to shallow-water areas from persistent populations
+in mesophotic ecosystems \citep{barbour_2011,andradibrown_2017}.
+However, promoting lionfish consumption might create a level of demand
+capable of incentivizing a stable fishery while controlling
+shallow-water populations, thus creating alternative livelihoods and
+avoiding further impacts to local biota.
 
@@
 empirical modeling
-\citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,chin_2016,usseglio_2017}.
-One contributing factor to the success of many removal programs is the
-sedentary nature of adult lionfish \citep{jud_2012}. Culling programs
-are effective in reducing local adult populations largely because
-lionfish exhibit high levels of site fidelity and rarely leave their
-home range \citep{Fishelson_1997,cote_2014,kochzius_2005}. Fish with
-this sedentary behavior are likely to exhibit high levels of spatial
-variation in important life history characterstics such as growth or
-natural mortality rates \citep{hutchinson_2008,wilson_2012}. The
-importance of considering spatial heterogeneity is well-documented in
-terms of assessing and managing sedentary species
-\citep{gunderson_2008,guan_2013}, and such variation should be accounted
-for when evaluating the feasibility of establishing lionfish fisheries
-as well.
+\citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,usseglio_2017}.
+Determining the feasibility of such initiatives requires modeling the
+change in biomass in response to changes in mortality (\emph{i.e.}
+culling). A common way to model this is via length-structured population
+models, where fish lengths are converted to weight to calculate total
+biomass \citep{barbour_2011,cote_2014,andradibrown_2017}. The allometric
+length-weight relationship is thus an essential component of these
+models, but this relationship can vary across regions as a response to
+biotic and abiotic conditions \citep{johnson_2016}.
 
-Determining the feasibility of such initiatives require modeling changes
-in biomass in response to changes in mortality (\emph{i.e.} culling). A
-common way to model this is via length-structured population models,
-where fish lengths are converted to weight to calculate total biomass
-\citep{cote_2014,barbour_2011,andradibrown_2017}. The length-weight
-relationship is therefore an essential component of these models, but
-this relationship can vary across regions as a response to biotic
-(\emph{e.g.} local food availability) and abiotic (\emph{e.g.} water
-temperature) conditions \citep{johnson_2016}. Literature suggests that
-site-specific parameters are necessary in order to accurately estimate
-biomass when length-weight relationships are spatially variable, and
-this variability becomes increasingly important when estimating the
-potential effectiveness and feasability of lionfish culling programs or
-when identifying total biomass available for harvest by fishers
-\citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}. In
-addition to environmentally-driven spatial variation, genetic analysis
-of invasive lionfish suggest biological differences due to the existence
-of two genetically distinct subpopulations between the northwest
-Atlantic and the Caribbean \citep{betancurr_2011}. To date, no studies
-have examined region-wide differences in length-weight parameters
-despite the large number of studies reporting this relationship for
-lionfish.
+Outcomes of previous studies suggest lionfish are likely to exhibit
+spatial heterogeneity in the length-weight relationship, which we
+summarize in two main causes. First, culling programs are effective in
+reducing local adult populations largely because lionfish exhibit high
+levels of site fidelity and small home ranges
+\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. It is know that
+fish with sedentary behavior are likely to exhibit high levels of
+spatial variation in important life history characterstics such as
+growth or natural mortality rates
+\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. Second,
+genetic analysis of lionfish suggests biological differences due to the
+existence of two genetically distinct invasive subpopulations between
+the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
+Site-specific parameters are necessary to accurately estimate biomass
+when allometric relationships are spatially variable, and this
+variability is increasingly important when estimating the potential
+effectiveness of lionfish culling programs
+\citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
+region-wide differences in allometric growth parameters has remained
+unexplored for lionfish, despite the large number of site-specific
+studies reporting the length-weight relationship.
 
-The objective of this paper is to describe the spatial pattern of
-length-weight relationships of lionfish in the Caribbean and Western
-Atlantic and evaluate the implications of these spatial differences.
-Length-weight relationships for lionfish exist for North Carolina,
-Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean,
-Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica
-\citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
-This study also provides the first length-weight relationship for the
-central Mexican Caribbean.
+Here, we compare previously published length-weight relationships for
+lionfish populations in North Carolina, Northern and Southern Gulf of
+Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica,
+Bonaire, Puerto Rico, and Costa Rica
+\citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
+We also collected lionfish length and weight data in the central Mexican
+Caribbean and report the first allometric growth equation for this
+region. The objective of this paper is to describe the spatial pattern
+of length-weight relationships of lionfish across the Caribbean and
+Western Atlantic and to discuss implications of these spatial
+differences.
 
-\clearpage
-
-\section*{Materials and Methods}
+\section{Materials and Methods}\label{materials-and-methods}
 
@@
 relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7),
-and Caribbean (n = 10, Table \ref{tab:all_params}, Fig
+and Caribbean (n = 9, Table \ref{tab:all_params}, Fig
 \ref{fig:all_allo}). We collected information on sampling methods, sex
 differentiation, location, and depth ranges from each study when
-available, and assumed both genders were included in a study if gender
-was unspecified. Only two studies reported parameters for each gender
-\citep{aguilarperera_2016,fogg_2013}. Reviewed studies presented
-information for organisms obtained at depths between 0.5 m and 57 m.
-Three studies explicitly stated that their organisms were sampled with
-pole spears
-\citep{aguilarperera_2016,chin_2016,dahl_2014,sabidoitz_2016}, and five
+available. Only two studies reported parameters for each gender
+\citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were
+included in a study if gender was unspecified. Reviewed studies
+presented information for organisms obtained at depths between 0.5 m and
+57 m. Three studies explicitly stated that their organisms were sampled
+with pole spears
+\citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and five
 studies mentioned that some of their organisms were obtained with pole
 spears (or other type of harpoon) but also hand-held nets or fish traps
-\citep{sandel_2015,barbour_2011,fogg_2013,edwards_2014,sabidoitza_2016,sabidoitz_2016,toledohernndez_2014},
+\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016,sabidoitz_2016},
 and two studies did not specify how organisms were sampled
-\citep{deleon_2013,darling_2011}. \citet{fogg_2013} use spine-less
-weight in the length-weight relationship estimation, and thus their
-parameters likely underestimate total wieght. Since no spine-less to
-total weight conversions were available, these parameters were taken as
-reported.
+\citep{darling_2011,deleon_2013}. \citet{fogg_2013} use spineless weight
+in their calculations, so their parameters likely underestimated total
+wieght. Since no spineless to total weight conversions were available,
+these parameters were taken as reported.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}
-\caption{\label{fig:map}Locations where allometric growth parameters of
-lionfish (\emph{Pterois spp}) have been reported. Circle sizes indicate
-sample size from each study, colors indicate the \(b\) coefficient from
-Eq. \ref{eq:allometric}.}
-\end{figure}
-
 The weight at length relationship for lionfish in the central Mexican
@@
 Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
-allometric parameter. When \(b = 3\), it is said that the organism
-exhibits a perfect isometric growth. Transforming this equation via
-base-10 logarithms:
+allometric parameter. Transforming this equation via base-10 logarithms:
 
@@
 with an Ordinary Least Squares Regression and heteroskedastic-robust
-standard error correction \citep{zeileis_2004}. The \(b\) coefficient
-was tested against the null hypothesis of isometric growth (\emph{i.e.}
-\(H_0: b = 3\)). Coefficients were tested with a two-tailed Student's t,
-and the significance of the regression was corroborated with an F-test.
+standard error correction \citep{zeileis_2004}. When the \(b = 3\), it
+is said that the organism exhibits a perfect isometric growth, so the
+\(b\) coefficient was tested against the null hypothesis of isometric
+growth (\emph{i.e.} \(H_0: b = 3\)). Coefficients were tested with a
+two-tailed Student's t, and the significance of the regression was
+corroborated with an F-test.
 
@@
 
-Combining the length-weight parameters extracted from the literature and
-the additional pair calculated here, we obtain a total of 18 pairs. We
-use the central Mexican Caribbean as a case study of how the use of
-\emph{ex situ} parameters influences the accuracy of weight estimates
-for lionfish. We estimated TW from the TL observations we collected in
-the central Mexican Caribbean (n = 109) using each of the 18 parameter
-pairs and divided predicted weights by known observed weights to obtain
-a simple measure of over- or underestimation. Difference in mean weight
-ratios across the different parameter pairs were tested with a one-way
-analysis of variance (ANOVA) and Tuskey's test was used for post-hoc
-tests. All analyses were performed in R version 3.5.0
-\citep{rcore_2018}. Raw data and code used in this work are available at
-dryad.org.
+We obtained a total of 18 parameter pairs by combining length-weight
+parameters extracted from the literature and the additional pair
+calculated here. We used the central Mexican Caribbean as a case study
+of how the use of \emph{ex situ} parameters influences the accuracy of
+weight estimates for lionfish. We estimated TW from the TL observations
+we collected in the central Mexican Caribbean (n = 109) using each of
+the 18 parameter pairs and divided predicted weights by known observed
+weights to obtain a simple measure of over- or underestimation.
+Difference in mean weight ratios across the different parameter pairs
+were tested with a one-way analysis of variance (ANOVA) and Tukey's test
+was used for post-hoc tests. All analyses were performed in R version
+3.5.0 \citep{rcore_2018}. Raw data and code used in this work are
+available at dryad.org.
 
-\section*{Results}
+\section{Results}\label{results}
 
@@
 other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
-shows the relationship between TL and TW for this region, and more
-information on model fit is presented in Table S2.
-
-Figure \ref{fig:all_allo} shows the length-weight relationships with
-parameters from all studies. Parameters from models fit to males or
-females exclusively tend to have a higher steepness (\emph{i.e.} higher
-allometric parameter), with mean \(\pm\) standard deviation values of
-\(b = 3.27 \pm 0.06\) and \(b = 3.31 \pm 0.23\) for males and females
-respectively, compared to parameters from models for combined genders
-with a mean \(\pm\) standard deviation value of \(b = 3.14 \pm 0.20\).
-In the case of the ponderal index (\(a\)) and its \(log_{10}\)
-transformation (\(c\)), values were higher for parameters for combined
-genders.
+shows the relationship between TL and TW for this region, and model fit
+statistics is presented in Table \ref{tab:reg_table}.
 
@@
 central Mexican Caribbean when using the different pairs of parameters
-(\(F(df = 15; 1728) = 38.26; p < 0.001\)). Weight estimates using
+(\(F(df = 17; 1944) = 61.55; p < 0.001\)). The lowest weight estimates
+resulted from using the allometric parameters from Banco Chinchorro in
+the Caribbean, with mean \(\pm\) SD of 40.37 \(\pm\) 58.74 gr
+\citep{sabidoitz_2016}, and the highest weight estimates came from the
+Northern Atlantic 73.76 \(\pm\) 96.11 gr \citep{barbour_2011}. To put
+this in context, true observed weights were 52.56 \(\pm\) 76.58 gr.
+These correspond to predicted-to-observed weights ratios of 0.80 \(\pm\)
+0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.
+
+The calculated ratio of predicted-to-observed weight ranged from 0.36 to
+3.51, indicating that \emph{ex situ} parameters can result in major
+under- and overestimations. Tukey's post-hoc test suggests that weight
+ratios for the central Mexican Caribbean were not different from those
+obtained with parameters from Little Cayman, the Bahamas, and some sites
+in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)). Weight estimates using
 parameters from the Gulf of Mexico and North-Western Atlantic were
-higher on average than those from the Caribbean. The average (\(\pm\)
-SD) predicted-to-observed weight ratios from these three regions were
-1.24 \(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398,
-respectively. The lowest weight estimates resulted from using the
-allometric parameters from Banco Chinchorro in the Caribbean
-\citet{sabidoitz_2016}, and the highest weight estimates came from the
-Northern Atlantic \citep{barbour_2011}. The calculated ratio of
-predicted-to-observed weight ranged from 0.80 \(\pm\) 0.19 to 1.76
-\(\pm\) 0.50 (mean \(\pm\) SD). Tukey's post-hoc test suggests that
-weight ratios for the central Mexican Caribbean were not differnt from
-those obntained with parameters from Little Cayman, the Bahamas, and
-some sites in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)).
+higher on average than those from the Caribbean (Fig
+\ref{fig:all_allo}). The average (\(\pm\) SD) predicted-to-observed
+weight ratios from these three regions were 1.24 \(\pm\) 0.309, 1.76
+\(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
 Predicted-to-observed weight ratios are presented in Figure
-\ref{fig:bio_ratio}. Spine-less weight parameters from \citet{fogg_2013}
+\ref{fig:bio_ratio}. Spineless weight parameters from \citet{fogg_2013}
 still produced predicted-to-observed weight ratios \textgreater{} 1.
+
+\section{Discussion}\label{discussion}
+
+We detected substantial differences in weight-at-length between
+organisms from the Caribbean, Gulf of Mexico, and North-Western
+Atlantic. Groupings of predicted-to-observed weight ratios aligned with
+the spatial distribution of the examined studies, suggesting that these
+differences are mediated by space. These regional allometric differences
+mirror similar patterns in age-at-length of lionfish across both their
+invaded and native regions \citep{pusack_2016}. Variation may be driven
+by genetics or by organisms' exposure to distinct environmental
+conditions. For example, \citet{betancurr_2011} used mitochondrial DNA
+to demonstrate the existence of two distinct population groups,
+identified as the ``Caribbean group'' and ``Northern Group'', and
+\citet{fogg_2015} alternatively suggested that age-at-length differences
+may be climate-driven. Differences in weight-at-length could also
+reflect differential energy input or usage, or a combination of both.
+Future research is needed to determine which processes are at work here.
+
+Differences in length-weight relationships have traditionally been
+highlighted as potential pitfalls to fishery management. For example,
+\citet{wilson_2012} show that small-scale variations in length-at-age
+and fishing mortality in other Scorpaeniformes translate to differential
+landings, effort, and catch per unit effort in the live fish fishery of
+California, and that these differences must be taken into account in
+management plans. The lionfish case poses the opposite scenario, where
+the manager desires to eradicate species. To accurately gauge both the
+effectiveness of lionfish removal efforts and the resources needed to
+successfully manage an invasion, we must acknowledge and understand
+regional biological differences in important variables such as
+allometric growth parameters.
+
+The results presented here have major implications for management. For
+example, \citet{edwards_2014} simulated a lionfish culling program under
+two scenarios, one using length-at-age and length-to-weight parameters
+from North Carolina and one using parameters from Little Cayman. Their
+results show that using different parameters caused up to a four-year
+difference in the time required for the simulated lionfish population to
+recover to 90\% of its initial biomass after removals ceased. Here, we
+show that using one set of length-weight parameters versus another for a
+given length can result in up to a threefold overestimation of TW. These
+spatially-driven differences become especially important when allocating
+resources for lionfish removal programs, incentivizing lionfish
+fisheries as a source of alternative livelihoods, or estimating
+ecosystem impacts. Research efforts focused on invasive lionfish
+populations need to use parameters calculated for their region to the
+extent possible, or at least use reasonable sets of different parameters
+that provide upper and lower bounds in their results.
+
+\section{Acknowledgements}\label{acknowledgements}
+
+The authors would like to thank thank Nils Van Der Haar and Michael
+Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided
+help to collect samples.
+
+\bibliography{references}
+
+\clearpage
+
+\section{Figures and Tables}\label{figures-and-tables}
 
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{\label{fig:l-w-carib}Length-weight relationship for 109
-lionfish sampled in the central Mexican Caribbean. Points indicate
-samples, dashed black line indicates curve of best fit, marginal plots
-represent the density distribution of each variable.}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
+\caption{\label{fig:unnamed-chunk-8}\label{fig:map}Locations where
+allometric growth parameters of lionfish (\emph{Pterois spp}) have been
+reported. Circle sizes indicate sample size from each study, colors
+indicate the \(b\) coefficient from Eq. \ref{eq:allometric}.}
+\end{figure}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:reg_table}Coefficients of the linear model fit to Eq \ref{eq:log-alo-trans}. Numbers in parenthesees represent heteroskedastic-robust standard errors.} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{$log_{10}(TW)$} \\ 
+\cline{2-2} 
+\hline \\[-1.8ex] 
+ c & $-$5.494 (0.083)$^{***}$ \\ 
+  b & 3.235 (0.039)$^{***}$ \\ 
+ \hline \\[-1.8ex] 
+F Statistic & 6928.67*** (df = 1; 107) \\ 
+Observations & 109 \\ 
+Adjusted R$^{2}$ & 0.976 \\ 
+Residual Std. Error & 0.096 (df = 107) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\label{fig:unnamed-chunk-10}\label{fig:l-w-carib}Length-weight
+relationship for 109 lionfish sampled in the central Mexican Caribbean.
+Points indicate samples, dashed black line indicates curve of best fit,
+marginal plots represent the density distribution of each variable.}
 \end{figure}
@@
 
-\caption{\label{tab:unnamed-chunk-5}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+\caption{\label{tab:unnamed-chunk-11}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
@@
 GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
-North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al.,2011\\
+North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al., 2011\\
 \bottomrule
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
-studies and this study. Colors indicate studies from which the
-parameters were extracted. Dotted, dashed and solid lines show models
-for males, females, and combined sexes, respectively. The dashed black
-line represents the relationship estimated in this study.}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{\label{fig:unnamed-chunk-12}\label{fig:all_allo}Length-weight
+relationships (n = 18) for 12 studies and this study. Colors indicate
+studies from which the parameters were extracted. Dotted, dashed and
+solid lines show models for males, females, and combined sexes,
+respectively. The dashed black line represents the relationship
+estimated in this study.}
 \end{figure}
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
-weight ratios for 18 pairs of allometric parameters. Red and blue
-circles indicate median and mean values, respectively. Like letters
-indicate values that do not differ significantly.}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:unnamed-chunk-13}\label{fig:bio_ratio}Violin plot of
+predicted-to-observed weight ratios for 18 pairs of allometric
+parameters. Red and blue circles indicate median and mean values,
+respectively. Like letters indicate values that do not differ
+significantly.}
 \end{figure}
 
-\clearpage
-
-\section*{Discussion}
-
-We detected substantial differences in weight-at-length between
-organisms from the Caribbean and Gulf of Mexico / North-Western
-Atlantic. The groupings of predicted-to-observed weight ratios were
-consistent with the spatial distribution of the studies, suggesting that
-these differences are mediated by space. These length-weight differences
-mirror similar findings of regional variability in age-at-length
-relationships of lionfish across both their invaded and native regions
-\citep{pusack_2016}. These patterns may be driven by genetic variation
-or by organisms being exposed to distinct environmental conditions. For
-example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate
-the existence of two distinct population groups, identified as the
-``Caribbean group'' and ``Northern Group'', and \citet{fogg_2015}
-alternatively suggested that age-at-length differences may be driven by
-climate. Differences in weight-at-length could also reflect differences
-in energy input or differential usage of this energy, or a combination
-of both. Future research is needed to determine which processes are at
-work here.
-
-Differences in length-weight relationships have traditionally been
-highlighted as potential pitfalls to fishery management. For example,
-\citet{wilson_2012} show that small-scale variations in length-at-age
-and fishing mortality in other Scorpaeniformes translate to differential
-landings, effort, and catch per unit effort in the live fish fishery of
-California, and that these differences must be taken into account in
-management plans. The lionfish case poses the opposite scenario, where
-the manager desires to erradicate species. To accurately gauge both the
-effectiveness of lionfish removal efforts and the resources needed to
-successfully manage an invasion, we must acknowledge and understand
-regional biological differences in important variables such as
-allometric growth parameters.
-
-The results presented here have major implications for management. For
-example, \citet{edwards_2014} simulated a lionfish culling program under
-two scenarios, one using length-at-age and length-to-weight parameters
-from North Carolina and one using parameters from Little Cayman. Their
-results show that using different parameters caused up to a four-year
-difference in the time required for the simulated lionfish population to
-recover to 90\% of its initial biomass after removals ceased. Here, we
-show that using one set of length-weight parameters versus another for a
-given length can result in up to a threefold TW overestimation. These
-spatially-driven differences become especially important when allocating
-resources for lionfish removal programs, incentivizing its fishery as a
-source of alternative livelihoods, or estimating ecosystem impacts.
-Research efforts focused on invasive lionfish populations need to use
-parameters calculated for their region to the extent possible, or at
-least use reasonable sets of different parameters that provide upper and
-lower bounds in their results.
-
-\section*{Aknowledgements}
-
-The authors would like to thank thank Nils Van Der Haar and Michael
-Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided
-help to collect samples.
-
-\bibliography{references}
-
 \end{document}

### 2018-06-13 docs/supplementary/S2Figure.Rmd
Incoporated Sean's comments, but still need to proof-read

---
title: "Supplementary Figure S2"
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 5.5)

options(knitr.table.format = "latex")

windowsFonts(Times=windowsFont("TT Times New Roman"))
```

```{r load packages}
suppressPackageStartupMessages({
  library(ggridges)
  library(here)
  library(tidyverse)
})
```

```{r}
fish <- read_csv(here("data","lionfish_data.csv"), col_types = cols()) %>% 
  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
  summarize(Length = 10*mean(TotalLength_cm),
            Weight = mean(TotalWeigth_gr),
            Stomach = mean(StomachLength_cm)) %>% 
  ungroup()

review <- read.csv(here::here("data", "biometric_review.csv"),
                   stringsAsFactors = F,
                   strip.white = T,
                   blank.lines.skip = T) %>% 
  mutate(c = log10(a),
         Gender2 = case_when(Gender == "Male" ~ "M",
                             Gender == "Female" ~ "F",
                             TRUE ~ "B"))
```

```{r}
review %>% 
  mutate(Length = list(fish$Length),
         Weight = list(fish$Weight)) %>% 
  unnest() %>% 
  mutate(pWeight = a*(Length^b),
    Biomass_ratio = pWeight / Weight) %>% 
  mutate(Study = paste0(Study, " (", Gender_site, ")")) %>%
  transform(Study = reorder(Study, -Biomass_ratio),
            Study_id = reorder(Study_id, -Biomass_ratio)) %>%
  ggplot(aes(x = Biomass_ratio, y = Study, fill = Study)) +
  geom_density_ridges(alpha = 0.5, size = 1) +
  geom_vline(xintercept = 1, linetype = "dashed", size = 1, color = "red") +
  theme_bw() +
  theme(text = element_text(family = "Times"),
        legend.position = "none",
        legend.text = element_text(size = 10),
        legend.background = element_rect(fill = "transparent"),
        axis.text = element_text(size = 10)) +
    labs(x = "Weight ratio (Predicted/Observed)", y = "") +
  scale_fill_viridis_d()
```

### 2018-07-07 docs/Manuscript.Rmd
Added final version ready for submission

@@
   - \floatplacement{figure}{H}
-title: \LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region in the Western Atlantic}
+  - \usepackage{fancyhdr}
+  - \pagestyle{fancy}
+  - \fancyhf{}
+  - \rhead{Lionfish allometric growth}
+  - \cfoot{\thepage}
+title: \LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region}
+abstract:
 output:
@@
     number_sections: no
+    # template: peerj_template.tex
     toc: no
@@
 csl: elsevier-harvard.csl
+fontsize: 12pt
 ---
@@
 
-^1^ Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States
-
-*jvillasenor\@bren.ucsb.edu
+^1^ Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States, 93117
 
@@
 Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
-Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics, so we review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
+Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics.
+We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
 The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
@@
 ---
+
+**Keywords:** Lionfish, invasive species, length-weight, allometric, regional variations
+
+*jvillasenor\@bren.ucsb.edu
 
@@
 They are the first invasive marine vertebrates established along the North Atlantic Caribbean coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
+Lionfish have established invasive populations in coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
 
-A substantial amount of research describes lionfish impacts throughout its invaded range.For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida.
+A substantial amount of research describes lionfish impacts throughout its invaded range.
+A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
+Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}).
+For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida.
 \citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs.
-A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
-Lionfish have also established invasive populations in other habitats such as estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017}.
-Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}).
-These trophic impacts can be minimized if local lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
+Their trophic impacts can be minimized if local lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
 
@@
 The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,usseglio_2017}.
-Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in mortality (*i.e.* culling).
+Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in fishing mortality (*i.e.* culling).
 A common way to model this is via length-structured population models, where fish lengths are converted to  weight to calculate total biomass \citep{barbour_2011,cote_2014,andradibrown_2017}.
@@
 
-The weight at length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function:
+The weight-at-length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function:
 
@@
 
-Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter. Transforming this equation via base-10 logarithms:
+Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter. Transforming this equation via base-10 logarithms we obtain:
 
@@
 We standardized each study by converting coefficients and report all parameters as TL(mm) to TW (gr) conversions.
-Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.
+Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and summarized in Table \ref{tab:all_params}.
 
@@
 We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tukey's test was used for post-hoc tests.
+Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tukey's test was used for *post-hoc* tests.
 All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
-Raw data and code used in this work are available at dryad.org.
+Raw data and code used in this work are available on github.
 
@@
 The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
-Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region, and model fit statistics is presented in Table \ref{tab:reg_table}.
+Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region, and model fit statistics are presented in Table \ref{tab:reg_table}.
 
@@
 There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 17; 1944) = 61.55; p < 0.001$).
-The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{barbour_2011}.
+The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic with `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{barbour_2011}.
 To put this in context, true observed weights were `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` gr.
@@
 The calculated ratio of predicted-to-observed weight ranged from `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")`, indicating that *ex situ* parameters can result in major under- and overestimations.
-Tukey's post-hoc test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
+Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
 Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}).
@@
 Their results show that using different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased.
-Here, we show that using one set of length-weight parameters versus another for a given length can result in up to a threefold overestimation of TW.
+Here, we show that using one set of length-weight parameters versus another for a given length can result in more than a threefold overestimation of TW.
 These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts.
@@
 
-\clearpage
-
 # Figures and Tables
@@
 fig_map
+```
+
+```{r,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
+Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
+fig_l_w_carib
 ```
@@
 
-```{r,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
-fig_l_w_carib
-```
-
 ```{r}
@@
          a = formatC((a*1e5), digits = 2)) %>% 
-  knitr::kable(format = "latex",
-               row.names = F,
+  knitr::kable(row.names = F,
                digits =  c(0, 0, 0, 0, 2, 2),
@@
                # longtable = T,
-               col.names = c("Region", "Sex", "n", "a", "b", "c", "$R^2$", "Reference"),
+               col.names = c("Region", "Sex", "n", "a", "b", "c", "Fit", "Reference"),
                caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
@@
 3, respectively.
-The $R^2$ column indicates reported model fit.")
+The Fit column contains the reported $R^2$ of the model fit.", escape = T)
 ```

### 2018-07-07 docs/Manuscript.tex
Added final version ready for submission

@@
-\documentclass[]{article}
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
 \setlength{\droptitle}{-2em}
-  \title{\LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region in the Western Atlantic}}
+  \title{\LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region}}
   \pretitle{\vspace{\droptitle}\centering\huge}
@@
 \floatplacement{figure}{H}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\rhead{Lionfish allometric growth}
+\cfoot{\thepage}
 
@@
 University of California Santa Barbara, Santa Barbara, California,
-United States
-
-*jvillasenor@bren.ucsb.edu
+United States, 93117
 
@@
 \begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\textbf{Keywords:} Lionfish, invasive species, length-weight,
+allometric, regional variations
+
+*jvillasenor@bren.ucsb.edu
 
@@
 biodiversity, spread rapidly, and are difficult to manage
-\citep{hixon_2016}.
+\citep{hixon_2016}. Lionfish have established invasive populations in
+coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic
+reefs
+\citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
 
 A substantial amount of research describes lionfish impacts throughout
-its invaded range.For example, field experiments by \citet{albins_2008}
-showed that lionfish establishment led to reduced recruitment of native
-fishes by nearly 80\% over a five week period in Florida.
-\citet{green_2012} reported that prey fish biomass declined by 65\% over
-two years as lionfish biomass increased along Bahamian coral reefs. A
-meta-analysis by \citet{peake_2018} showed that invasive lionfish prey
-on at least 167 different species across the tropical and temperate
-North Atlantic. Lionfish have also established invasive populations in
-other habitats such as estuaries, mangroves, hard-bottomed areas, and
-mesophotic reefs
-\citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017}.
-Their feeding behavior and high consumption rates can reduce recruitment
-and population sizes of native reef-fish species, and can further
-endanger reef fish (\citet{green_2012,rocha_2015}; but see
-\citet{hackerott_2017}). These trophic impacts can be minimized if local
-lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
+its invaded range. A meta-analysis by \citet{peake_2018} showed that
+invasive lionfish prey on at least 167 different species across the
+tropical and temperate North Atlantic. Their feeding behavior and high
+consumption rates can reduce recruitment and population sizes of native
+reef-fish species, and can further endanger reef fish
+(\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}). For
+example, field experiments by \citet{albins_2008} showed that lionfish
+establishment led to reduced recruitment of native fishes by nearly 80\%
+over a five week period in Florida. \citet{green_2012} reported that
+prey fish biomass declined by 65\% over two years as lionfish biomass
+increased along Bahamian coral reefs. Their trophic impacts can be
+minimized if local lionfish biomass is controlled by culling
+\citep{ariasgonzalez_2011}.
 
@@
 Determining the feasibility of such initiatives requires modeling the
-change in biomass in response to changes in mortality (\emph{i.e.}
-culling). A common way to model this is via length-structured population
-models, where fish lengths are converted to weight to calculate total
-biomass \citep{barbour_2011,cote_2014,andradibrown_2017}. The allometric
+change in biomass in response to changes in fishing mortality
+(\emph{i.e.} culling). A common way to model this is via
+length-structured population models, where fish lengths are converted to
+weight to calculate total biomass
+\citep{barbour_2011,cote_2014,andradibrown_2017}. The allometric
 length-weight relationship is thus an essential component of these
@@
 
-The weight at length relationship for lionfish in the central Mexican
+The weight-at-length relationship for lionfish in the central Mexican
 Caribbean was calculated with the allometric growth function:
@@
 Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
-allometric parameter. Transforming this equation via base-10 logarithms:
+allometric parameter. Transforming this equation via base-10 logarithms
+we obtain:
 
@@
 allometric studies have been performed are shown in Figure \ref{fig:map}
-and Table \ref{tab:all_params}.
+and summarized in Table \ref{tab:all_params}.
 
@@
 were tested with a one-way analysis of variance (ANOVA) and Tukey's test
-was used for post-hoc tests. All analyses were performed in R version
-3.5.0 \citep{rcore_2018}. Raw data and code used in this work are
-available at dryad.org.
+was used for \emph{post-hoc} tests. All analyses were performed in R
+version 3.5.0 \citep{rcore_2018}. Raw data and code used in this work
+are available on github.
 
@@
 shows the relationship between TL and TW for this region, and model fit
-statistics is presented in Table \ref{tab:reg_table}.
+statistics are presented in Table \ref{tab:reg_table}.
 
@@
 \citep{sabidoitz_2016}, and the highest weight estimates came from the
-Northern Atlantic 73.76 \(\pm\) 96.11 gr \citep{barbour_2011}. To put
-this in context, true observed weights were 52.56 \(\pm\) 76.58 gr.
+Northern Atlantic with 73.76 \(\pm\) 96.11 gr \citep{barbour_2011}. To
+put this in context, true observed weights were 52.56 \(\pm\) 76.58 gr.
 These correspond to predicted-to-observed weights ratios of 0.80 \(\pm\)
@@
 3.51, indicating that \emph{ex situ} parameters can result in major
-under- and overestimations. Tukey's post-hoc test suggests that weight
-ratios for the central Mexican Caribbean were not different from those
-obtained with parameters from Little Cayman, the Bahamas, and some sites
-in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)). Weight estimates using
-parameters from the Gulf of Mexico and North-Western Atlantic were
+under- and overestimations. Tukey's \emph{post-hoc} test suggests that
+weight ratios for the central Mexican Caribbean were not different from
+those obtained with parameters from Little Cayman, the Bahamas, and some
+sites in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)). Weight estimates
+using parameters from the Gulf of Mexico and North-Western Atlantic were
 higher on average than those from the Caribbean (Fig
@@
 show that using one set of length-weight parameters versus another for a
-given length can result in up to a threefold overestimation of TW. These
-spatially-driven differences become especially important when allocating
-resources for lionfish removal programs, incentivizing lionfish
-fisheries as a source of alternative livelihoods, or estimating
+given length can result in more than a threefold overestimation of TW.
+These spatially-driven differences become especially important when
+allocating resources for lionfish removal programs, incentivizing
+lionfish fisheries as a source of alternative livelihoods, or estimating
 ecosystem impacts. Research efforts focused on invasive lionfish
@@
 
-\clearpage
-
 \section{Figures and Tables}\label{figures-and-tables}
@@
 indicate the \(b\) coefficient from Eq. \ref{eq:allometric}.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{\label{fig:unnamed-chunk-9}\label{fig:l-w-carib}Length-weight
+relationship for 109 lionfish sampled in the central Mexican Caribbean.
+Points indicate samples, dashed black line indicates curve of best fit,
+marginal plots represent the density distribution of each variable.}
 \end{figure}
@@
 
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}\label{fig:l-w-carib}Length-weight
-relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, dashed black line indicates curve of best fit,
-marginal plots represent the density distribution of each variable.}
-\end{figure}
-
 \begin{table}
@@
 3, respectively.
-The $R^2$ column indicates reported model fit.}
+The Fit column contains the reported $R^2$ of the model fit.}
 \centering
@@
 \toprule
-Region & Sex & n & a & b & c & \$R\textasciicircum{}2\$ & Reference\\
+Region & Sex & n & a & b & c & Fit & Reference\\
 \midrule

### 2018-07-13 docs/Manuscript.Rmd
Changed formatting to submit to BioInv

@@
 ---
-header-includes:
-  - \usepackage{natbib}
-  - \usepackage{setspace}
-  - \doublespacing
-  - \usepackage{lineno}
-  - \linenumbers
-  - \usepackage{float}
-  - \floatplacement{figure}{H}
-  - \usepackage{fancyhdr}
-  - \pagestyle{fancy}
-  - \fancyhf{}
-  - \rhead{Lionfish allometric growth}
-  - \cfoot{\thepage}
-title: \LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region}
-abstract:
-output:
-  bookdown::pdf_document2:
-    keep_tex: yes
-    number_sections: no
-    # template: peerj_template.tex
-    toc: no
-bibliography: references.bib
-csl: elsevier-harvard.csl
-fontsize: 12pt
----
+title: Spatial variation in allometric growth of invasive lionfish has management implications
+titlerunning: Lionfish allometric growth
+authorrunning: Villaseñor-Derbez & Fitzgerald
+authors: 
+- name: Juan Carlos Villaseñor-Derbez
+  address: "Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States, 93117 | ORCID: 0000-0003-1245-589X"
+  email: jvillasenor@bren.ucsb.edu
+- name: Sean Fitzgerald
+  address: Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States, 93117
 
-Juan Carlos Villaseñor-Derbez^1^*, Sean Fitzgerald^1^
+keywords:
+  - Lionfish
+  - invasive species
+  - length-weight
+  - allometric growht
+  - regional variations
 
-^1^ Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States, 93117
-
----
-
-\begin{abstract}
+abstract: |
   Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean.
@@
 The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
-We show that the use of \textit{ex situ} parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error.
+We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight, but using parameters from nearby regions reduces this error.
 These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
-\end{abstract}
 
+bibliography: references.bib
+output: rticles::springer_article
+header-includes:
+   - \journalname{Biological Invasions}
+   - \usepackage{natbib}
+   - \usepackage{float}
+   - \floatplacement{figure}{H}
+   # - \restylefloat{table}
 ---
-
-**Keywords:** Lionfish, invasive species, length-weight, allometric, regional variations
-
-*jvillasenor\@bren.ucsb.edu
 
@@
 
-We also collected data from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Table S1).
+```{r, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
+Circle sizes indicate sample size from each study, colors indicate the $b$ coefficient from Eq.
+\\ref{eq:allometric}.", fig.height = 3.5}
+fig_map
+```
+
+We also collected data from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Supplementary Table 1).
 Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
@@
 
+<!-- \clearpage -->
+
 # Results
@@
 
+```{r,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
+Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
+fig_l_w_carib
+```
+
+```{r, results = "asis"}
+stargazer(model,
+          dep.var.caption = "$log_{10}(TW)$",
+          dep.var.labels.include = F,
+          header = F,
+          se = list(robust_se),
+          type = "latex",
+          t.auto = T,
+          p.auto = T,
+          intercept.bottom = F,
+          single.row = T,
+          report = "vcs*",
+          omit.stat = c("f", "rsq"),
+          add.lines = list(f_string),
+          covariate.labels = c("c", "b"),
+          dep.var.labels = "log10(TW)", title = "\\label{tab:reg_table}Coefficients of the linear model fit to Eq \\ref{eq:log-alo-trans}.
+Numbers in parenthesees represent heteroskedastic-robust standard errors.")
+```
+
 There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 17; 1944) = 61.55; p < 0.001$).
@@
 Spineless weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.
+
+```{r}
+review %>% 
+  select(Region, Gender2, N, a, b, c, r2, Study) %>% 
+  filter(!Study == "Fishbase") %>% 
+  arrange(Region) %>% 
+  mutate(r2 = ifelse(is.na(r2), "-", r2),
+         N = ifelse(is.na(N), "-", N),
+         a = formatC((a*1e5), digits = 2)) %>% 
+  knitr::kable(row.names = F,
+               digits =  c(0, 0, 0, 0, 2, 2),
+               # longtable = T,
+               col.names = c("Region", "Sex", "n", "a", "b", "c", "Fit", "Reference"),
+               caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
+1 (presented in $\\times 10^{-5}$), c = y-intercept for Eq.
+3, b = exponent or slope for Eq.
+1 or Eq.
+3, respectively.
+The Fit column contains the reported $R^2$ of the model fit.", escape = T)
+```
 
@@
 
+```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
+Colors indicate studies from which the parameters were extracted.
+Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
+The dashed black line represents the relationship estimated in this study."}
+fig_all_allo
+```
+
 ```{r}
@@
   geom_violin(aes(fill = Sex), alpha = 0.8) +
-  stat_summary(geom = "point", fun.y = "mean", size = 1, color = "blue") +
-  stat_summary(geom = "point", fun.y = "median", size = 1, color = "red") +
+  stat_summary(geom = "point", fun.y = "median", size = 2, color = "black", fill = "steelblue", shape = 21) +
   geom_hline(yintercept = 1, linetype = "dashed") +
@@
   geom_text(aes(y = 3.7, label = groups), family = "Times", fontface = "plain") +
-  scale_y_continuous(limits = c(NA, 3.7))
+  scale_y_continuous(limits = c(NA, 3.7)) +
+  guides(fill = guide_legend(title.position = "top"))
 ```
+
+```{r, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
+Blue circles indicate median values and Like letters indicate values that do not differ significantly."}
+fig_bio_ratio
+```
+
+\clearpage
 
@@
 Their results show that using different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased.
-Here, we show that using one set of length-weight parameters versus another for a given length can result in more than a threefold overestimation of TW.
+Here, we show that using one set of length-weight parameters versus another for a given length can result in more than a threefold under- or overestimation of total weight.
 These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts.
@@
 
-\bibliography{references}
+Conflict of Interest: The authors declare that they have no conflict of interest.
 
-# Figures and Tables
-
-```{r, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
-Circle sizes indicate sample size from each study, colors indicate the $b$ coefficient from Eq.
-\\ref{eq:allometric}.", fig.height = 3.5}
-fig_map
-```
-
-```{r,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
-fig_l_w_carib
-```
-
-```{r, results = "asis"}
-stargazer(model,
-          dep.var.caption = "$log_{10}(TW)$",
-          dep.var.labels.include = F,
-          header = F,
-          se = list(robust_se),
-          type = "latex",
-          t.auto = T,
-          p.auto = T,
-          intercept.bottom = F,
-          single.row = T,
-          report = "vcs*",
-          omit.stat = c("f", "rsq"),
-          add.lines = list(f_string),
-          covariate.labels = c("c", "b"),
-          dep.var.labels = "log10(TW)", title = "\\label{tab:reg_table}Coefficients of the linear model fit to Eq \\ref{eq:log-alo-trans}.
-Numbers in parenthesees represent heteroskedastic-robust standard errors.")
-```
-
-```{r}
-review %>% 
-  select(Region, Gender2, N, a, b, c, r2, Study) %>% 
-  filter(!Study == "Fishbase") %>% 
-  arrange(Region) %>% 
-  mutate(r2 = ifelse(is.na(r2), "-", r2),
-         N = ifelse(is.na(N), "-", N),
-         a = formatC((a*1e5), digits = 2)) %>% 
-  knitr::kable(row.names = F,
-               digits =  c(0, 0, 0, 0, 2, 2),
-               booktabs = T,
-               # longtable = T,
-               col.names = c("Region", "Sex", "n", "a", "b", "c", "Fit", "Reference"),
-               caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
-1 (presented in $\\times 10^{-5}$), c = y-intercept for Eq.
-3, b = exponent or slope for Eq.
-1 or Eq.
-3, respectively.
-The Fit column contains the reported $R^2$ of the model fit.", escape = T)
-```
-
-```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
-Colors indicate studies from which the parameters were extracted.
-Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
-The dashed black line represents the relationship estimated in this study."}
-fig_all_allo
-```
-
-```{r, fig.height = 5, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
-Red and blue circles indicate median and mean values, respectively.
-Like letters indicate values that do not differ significantly."}
-fig_bio_ratio
-```
+<!-- \bibliography{references} -->

### 2018-07-13 docs/Manuscript.tex
Changed formatting to submit to BioInv

@@
-\documentclass[12pt,]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
+% !TeX program = pdfLaTeX
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1in]{geometry}
+
+\usepackage[hyphens]{url} % not crucial - just used below for the URL
 \usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{longtable,booktabs}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+%
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
 
-%%% Change title format to be more compact
-\usepackage{titling}
+%% load any required packages here
 
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
+\journalname{Biological Invasions}
+\usepackage{natbib}
+\usepackage{float}
+\floatplacement{figure}{H}
+
+\begin{document}
+
+\title{Spatial variation in allometric growth of invasive lionfish has
+management implications }
+
+    \titlerunning{Lionfish allometric growth}
+
+\author{  Juan Carlos Villaseñor-Derbez \and  Sean Fitzgerald \and  }
+
+    \authorrunning{ Villaseñor-Derbez \& Fitzgerald }
+
+\institute{
+        Juan Carlos Villaseñor-Derbez \at
+     Bren School of Environmental Science and Management, University of
+ California Santa Barbara, Santa Barbara, California, United States,
+ 93117 \textbar{} ORCID: 0000-0003-1245-589X \\
+     \email{\href{mailto:jvillasenor@bren.ucsb.edu}{\nolinkurl{jvillasenor@bren.ucsb.edu}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Sean Fitzgerald \at
+     Bren School of Environmental Science and Management, University of
+ California Santa Barbara, Santa Barbara, California, United States,
+ 93117 \\
+     %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
     }
 
-\setlength{\droptitle}{-2em}
-  \title{\LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region}}
-  \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-  \author{}
-  \preauthor{}\postauthor{}
-  \date{}
-  \predate{}\postdate{}
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
 
-\usepackage{natbib}
-\usepackage{setspace}
-\doublespacing
-\usepackage{lineno}
-\linenumbers
-\usepackage{float}
-\floatplacement{figure}{H}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Lionfish allometric growth}
-\cfoot{\thepage}
-
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{example}{Example}
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
-\begin{document}
 \maketitle
 
-Juan Carlos Villaseñor-Derbez\textsuperscript{1}*, Sean
-Fitzgerald\textsuperscript{1}
+\begin{abstract}
+Lionfish (\textit{Pterois volitans / miles}) are an invasive species in
+the Western Atlantic and the Caribbean. Improving management of invasive
+lionfish populations requires accurate total biomass estimates, which
+depend on accurate estimates of allometric growth. Sedentary species
+like lionfish often exhibit high levels of spatial variation in life
+history characterstics. We review 17 published length-weight
+relationships for lionfish taken throughout their invasive range and
+found substantial regional differences in allometric growth parameters.
+The spatial pattern we observed is consistent with findings from other
+studies focusing on genetics or age-at-length. We show that the use of
+\textit{ex situ} parameters can result in up to a threefold under- or
+overestimation of total weight, but using parameters from nearby regions
+reduces this error. These findings can have major implications for
+management in terms of predicting effects on local ecosystems,
+evaluating the effectiveness of removal programs, or estimating biomass
+available for harvest.
+\\
+\keywords{
+        Lionfish \and
+        invasive species \and
+        length-weight \and
+        allometric growht \and
+        regional variations \and
+    }
 
-\textsuperscript{1} Bren School of Environmental Science and Management,
-University of California Santa Barbara, Santa Barbara, California,
-United States, 93117
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-\begin{abstract}
-Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean.
-Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
-Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics.
-We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
-The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
-We show that the use of \textit{ex situ} parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error.
-These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
 \end{abstract}
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-\textbf{Keywords:} Lionfish, invasive species, length-weight,
-allometric, regional variations
-
-*jvillasenor@bren.ucsb.edu
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{\label{fig:map}Locations where allometric growth parameters of
+lionfish (\emph{Pterois spp}) have been reported. Circle sizes indicate
+sample size from each study, colors indicate the \(b\) coefficient from
+Eq. \ref{eq:allometric}.}
+\end{figure}
+
 We also collected data from 10 sampling sites along the central Mexican
-Caribbean coast in 2010 (Table S1). Sampling locations included wall and
-carpet reefs at depths between 5.7 m and 38.1 m. All observed lionfish
-(n = 109) were collected using hand nets and numbered collection
-bottles. The use of hand nets prevented any weight loss due to bleeding
-and allowed better representation of small sizes by eliminating gear
-selectivity. Organisms were euthanized via pithing and Total Length (TL;
-mm) and Total Weight (TW; g) were recorded.
+Caribbean coast in 2010 (Supplementary Table 1). Sampling locations
+included wall and carpet reefs at depths between 5.7 m and 38.1 m. All
+observed lionfish (n = 109) were collected using hand nets and numbered
+collection bottles. The use of hand nets prevented any weight loss due
+to bleeding and allowed better representation of small sizes by
+eliminating gear selectivity. Organisms were euthanized via pithing and
+Total Length (TL; mm) and Total Weight (TW; g) were recorded.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\label{fig:l-w-carib}Length-weight relationship for 109
+lionfish sampled in the central Mexican Caribbean. Points indicate
+samples, dashed black line indicates curve of best fit, marginal plots
+represent the density distribution of each variable.}
+\end{figure}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:reg_table}Coefficients of the linear model fit to Eq \ref{eq:log-alo-trans}. Numbers in parenthesees represent heteroskedastic-robust standard errors.} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{$log_{10}(TW)$} \\ 
+\cline{2-2} 
+\hline \\[-1.8ex] 
+ c & $-$5.494 (0.083)$^{***}$ \\ 
+  b & 3.235 (0.039)$^{***}$ \\ 
+ \hline \\[-1.8ex] 
+F Statistic & 6928.67*** (df = 1; 107) \\ 
+Observations & 109 \\ 
+Adjusted R$^{2}$ & 0.976 \\ 
+Residual Std. Error & 0.096 (df = 107) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
 There were significant differences in our predicted weights for the
@@
 still produced predicted-to-observed weight ratios \textgreater{} 1.
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-9}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
+1 (presented in $\times 10^{-5}$), c = y-intercept for Eq.
+3, b = exponent or slope for Eq.
+1 or Eq.
+3, respectively.
+The Fit column contains the reported $R^2$ of the model fit.}
+\centering
+\begin{tabular}[t]{l|l|l|l|r|r|l|l}
+\hline
+Region & Sex & n & a & b & c & Fit & Reference\\
+\hline
+Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
+\hline
+Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
+\hline
+Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
+\hline
+Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
+\hline
+Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
+\hline
+Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
+\hline
+Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
+\hline
+Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
+\hline
+Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
+\hline
+Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
+\hline
+GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
+\hline
+GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+\hline
+GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+\hline
+GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+\hline
+GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
+\hline
+GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
+\hline
+GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
+\hline
+North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al., 2011\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
+studies and this study. Colors indicate studies from which the
+parameters were extracted. Dotted, dashed and solid lines show models
+for males, females, and combined sexes, respectively. The dashed black
+line represents the relationship estimated in this study.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
+weight ratios for 18 pairs of allometric parameters. Blue circles
+indicate median values and Like letters indicate values that do not
+differ significantly.}
+\end{figure}
+
+\clearpage
 
@@
 show that using one set of length-weight parameters versus another for a
-given length can result in more than a threefold overestimation of TW.
-These spatially-driven differences become especially important when
-allocating resources for lionfish removal programs, incentivizing
-lionfish fisheries as a source of alternative livelihoods, or estimating
-ecosystem impacts. Research efforts focused on invasive lionfish
-populations need to use parameters calculated for their region to the
-extent possible, or at least use reasonable sets of different parameters
-that provide upper and lower bounds in their results.
+given length can result in more than a threefold under- or
+overestimation of total weight. These spatially-driven differences
+become especially important when allocating resources for lionfish
+removal programs, incentivizing lionfish fisheries as a source of
+alternative livelihoods, or estimating ecosystem impacts. Research
+efforts focused on invasive lionfish populations need to use parameters
+calculated for their region to the extent possible, or at least use
+reasonable sets of different parameters that provide upper and lower
+bounds in their results.
 
@@
 
-\bibliography{references}
+Conflict of Interest: The authors declare that they have no conflict of
+interest.
 
-\section{Figures and Tables}\label{figures-and-tables}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{\label{fig:unnamed-chunk-8}\label{fig:map}Locations where
-allometric growth parameters of lionfish (\emph{Pterois spp}) have been
-reported. Circle sizes indicate sample size from each study, colors
-indicate the \(b\) coefficient from Eq. \ref{eq:allometric}.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{\label{fig:unnamed-chunk-9}\label{fig:l-w-carib}Length-weight
-relationship for 109 lionfish sampled in the central Mexican Caribbean.
-Points indicate samples, dashed black line indicates curve of best fit,
-marginal plots represent the density distribution of each variable.}
-\end{figure}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:reg_table}Coefficients of the linear model fit to Eq \ref{eq:log-alo-trans}. Numbers in parenthesees represent heteroskedastic-robust standard errors.} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{$log_{10}(TW)$} \\ 
-\cline{2-2} 
-\hline \\[-1.8ex] 
- c & $-$5.494 (0.083)$^{***}$ \\ 
-  b & 3.235 (0.039)$^{***}$ \\ 
- \hline \\[-1.8ex] 
-F Statistic & 6928.67*** (df = 1; 107) \\ 
-Observations & 109 \\ 
-Adjusted R$^{2}$ & 0.976 \\ 
-Residual Std. Error & 0.096 (df = 107) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-11}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
-1 (presented in $\times 10^{-5}$), c = y-intercept for Eq.
-3, b = exponent or slope for Eq.
-1 or Eq.
-3, respectively.
-The Fit column contains the reported $R^2$ of the model fit.}
-\centering
-\begin{tabular}[t]{llllrrll}
-\toprule
-Region & Sex & n & a & b & c & Fit & Reference\\
-\midrule
-Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
-Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
-Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
-Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
-Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
-\addlinespace
-Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
-Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
-Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
-Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
-Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
-\addlinespace
-GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
-GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
-\addlinespace
-GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
-GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
-North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al., 2011\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{\label{fig:unnamed-chunk-12}\label{fig:all_allo}Length-weight
-relationships (n = 18) for 12 studies and this study. Colors indicate
-studies from which the parameters were extracted. Dotted, dashed and
-solid lines show models for males, females, and combined sexes,
-respectively. The dashed black line represents the relationship
-estimated in this study.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\label{fig:unnamed-chunk-13}\label{fig:bio_ratio}Violin plot of
-predicted-to-observed weight ratios for 18 pairs of allometric
-parameters. Red and blue circles indicate median and mean values,
-respectively. Like letters indicate values that do not differ
-significantly.}
-\end{figure}
+\bibliographystyle{spbasic}
+\bibliography{references.bib}
 

### 2018-07-13 docs/supplementary/S1Table.Rmd
Changed formatting to submit to BioInv

@@
 ---
-title: "Supplementary Table S1"
-author: "Juan Carlos Villaseñor-Derbez"
-output: pdf_document
+title: Spatial variation in allometric growth of invasive lionfish has management implications
+subtitle: "Supplementary Table 1"
+author: "Villaseñor-Derbez & Fitzgerald"
+output: bookdown::pdf_document2
+fontsize: 12pt
 ---
@@
 ```{r}
-fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
+fish <- read_csv(here::here("data", "lionfish_data.csv"), col_types = cols()) %>% 
   group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
@@
   knitr::kable(row.names = F,
+               booktabs = T,
                col.names = c("Location", "Lat.", "Long.", "Min. Depth", "Max. Depth", "Mean Depth", "n"))

### 2018-11-07 docs/Manuscript.Rmd
Updated manuscript for PeerJ

@@
 ---
-title: Spatial variation in allometric growth of invasive lionfish has management implications
-titlerunning: Lionfish allometric growth
-authorrunning: Villaseñor-Derbez & Fitzgerald
-authors: 
-- name: Juan Carlos Villaseñor-Derbez
-  address: "Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States, 93117 | ORCID: 0000-0003-1245-589X"
-  email: jvillasenor@bren.ucsb.edu
-- name: Sean Fitzgerald
-  address: Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, California, United States, 93117
-
+title: "Spatial variation in allometric growth of invasive lionfish has management implications"
+author: "Juan Carlos Villaseñor-Derbez, Sean Fitzgerald"
+institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
+abstract: |
+  Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean.
+Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
+Sedentary species like lionfish often exhibit high levels of spatial variation in life history characteristics.
+We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
+The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
+We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight, but using parameters from nearby regions reduces this error.
+These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
 keywords:
@@
   - length-weight
-  - allometric growht
+  - allometric growth
   - regional variations
-
-abstract: |
-  Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean.
-Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
-Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics.
-We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
-The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
-We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight, but using parameters from nearby regions reduces this error.
-These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
-
 bibliography: references.bib
-output: rticles::springer_article
+output:
+  pdf_document:
+    keep_tex: yes
+    number_sections: no
+    template: peerj_template.tex
 header-includes:
-   - \journalname{Biological Invasions}
-   - \usepackage{natbib}
    - \usepackage{float}
    - \floatplacement{figure}{H}
-   # - \restylefloat{table}
+   - \restylefloat{table}
 ---
@@
 Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}).
-For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five week period in Florida.
+For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five-week period in Florida.
 \citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs.
@@
 First, culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and small home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
-It is know that fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characterstics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
+It is know that fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characteristics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
 Second, genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
@@
 
-# Materials and Methods
+\clearpage
+
+\section*{Methods}
 
@@
                              TRUE ~"B"))
-
 ```
@@
 Three studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016,sabidoitz_2016}, and two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
-\citet{fogg_2013} use spineless weight in their calculations, so their parameters likely underestimated total wieght.
+\citet{fogg_2013} use spineless weight in their calculations, so their parameters likely underestimated total weight.
 Since no spineless to total weight conversions were available, these parameters were taken as reported.
@@
 
-Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter. Transforming this equation via base-10 logarithms we obtain:
+Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
+
+\clearpage
+
+Transforming this equation via base-10 logarithms we obtain:
 
@@
 We used the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
-We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
+We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109, with $TL \in (34, 310)$) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
 Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tukey's test was used for *post-hoc* tests.
@@
 
-<!-- \clearpage -->
-
-# Results
+\section*{Results}
 
@@
 ```{r}
-TidyModel <- model%>%
+TidyModel <- model %>%
   lmtest::coeftest(vcov = sandwich::vcovHC(., type = "HC1")) %>%
@@
 
-The calculated ratio of predicted-to-observed weight ranged from `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")`, indicating that *ex situ* parameters can result in major under- and overestimations.
-Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukeys HSD $p > 0.05$).
+The calculated ratio of predicted-to-observed weight ranged from `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")`, indicating that *ex situ* parameters can result in major under- and overestimation.
+Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
 Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}).
@@
                digits =  c(0, 0, 0, 0, 2, 2),
-               # longtable = T,
+               booktabs = T,
                col.names = c("Region", "Sex", "n", "a", "b", "c", "Fit", "Reference"),
@@
 
-# Discussion
+\section*{Discussion}
+
+Our results suggest that lionfish exhibit highly variable allometric relationships across the invaded range, and that this variation is related to space.
+Moreover, we shot that the use of *ex situ* parameters may lead to highly biased weight estimates.
+Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight can be overestimated by more than a three-fold, and highlights the need to use local information.
+Here we discuss the implications of our findings and highlight potential future research directions.
 
@@
 For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
-The lionfish case poses the opposite scenario, where the manager desires to eradicate species.
+The lionfish case poses the opposite scenario, where the manager desires to eradicate the species.
 To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.
@@
 
-# Acknowledgements
+\section*{Acknowledgements}
 
@@
 
-<!-- \bibliography{references} -->
+\bibliography{references}

### 2018-11-07 docs/Manuscript.tex
Updated manuscript for PeerJ

@@
-% !TeX program = pdfLaTeX
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[utf8]{inputenc}
+%% Submissions for peer-review must enable line-numbering 
+%% using the lineno option in the \documentclass command.
+%%
+%% Preprints and camera-ready submissions do not need 
+%% line numbers, and should have this option removed.
+%%
+%% Please note that the line numbering option requires
+%% version 1.1 or newer of the wlpeerj.cls file, and
+%% the corresponding author info requires v1.2
 
-\usepackage[hyphens]{url} % not crucial - just used below for the URL
-\usepackage{hyperref}
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
-
-%% load any required packages here
-
-\journalname{Biological Invasions}
-\usepackage{natbib}
-\usepackage{float}
-\floatplacement{figure}{H}
-
-\begin{document}
+\documentclass[fleqn,10pt,lineno]{wlpeerj} % for journal submissions
+% \documentclass[fleqn,10pt]{wlpeerj} % for preprint submissions
 
 \title{Spatial variation in allometric growth of invasive lionfish has
-management implications }
+management implications}
 
-    \titlerunning{Lionfish allometric growth}
+\author[1]{Juan Carlos Villaseñor-Derbez}
+\author[1]{Sean Fitzgerald}
+\affil[1]{Bren School of Environmental Sciences and Management, University of California
+  Santa Barbara, Santa Barbara, California, USA}
+\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@ucsb.edu}
 
-\author{  Juan Carlos Villaseñor-Derbez \and  Sean Fitzgerald \and  }
-
-    \authorrunning{ Villaseñor-Derbez \& Fitzgerald }
-
-\institute{
-        Juan Carlos Villaseñor-Derbez \at
-     Bren School of Environmental Science and Management, University of
- California Santa Barbara, Santa Barbara, California, United States,
- 93117 \textbar{} ORCID: 0000-0003-1245-589X \\
-     \email{\href{mailto:jvillasenor@bren.ucsb.edu}{\nolinkurl{jvillasenor@bren.ucsb.edu}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Sean Fitzgerald \at
-     Bren School of Environmental Science and Management, University of
- California Santa Barbara, Santa Barbara, California, United States,
- 93117 \\
-     %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-    }
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
+\keywords{Lionfish, invasive species, length-weight, allometric, regional variations}
 
@@
 like lionfish often exhibit high levels of spatial variation in life
-history characterstics. We review 17 published length-weight
+history characteristics. We review 17 published length-weight
 relationships for lionfish taken throughout their invasive range and
@@
 available for harvest.
-\\
-\keywords{
-        Lionfish \and
-        invasive species \and
-        length-weight \and
-        allometric growht \and
-        regional variations \and
-    }
-
 \end{abstract}
 
-\def\spacingset#1{\renewcommand{\baselinestretch}%
-{#1}\small\normalsize} \spacingset{1}
+\begin{document}
 
-\section{Introduction}\label{introduction}
+\flushbottom
+\maketitle
+\thispagestyle{empty}
+
+\section*{Introduction}
 
@@
 establishment led to reduced recruitment of native fishes by nearly 80\%
-over a five week period in Florida. \citet{green_2012} reported that
+over a five-week period in Florida. \citet{green_2012} reported that
 prey fish biomass declined by 65\% over two years as lionfish biomass
@@
 
-\section{Materials and Methods}\label{materials-and-methods}
+\clearpage
+
+\section*{Methods}
 
@@
 Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
-allometric parameter. Transforming this equation via base-10 logarithms
-we obtain:
+allometric parameter.
+
+\clearpage
+
+Transforming this equation via base-10 logarithms we obtain:
 
@@
 weight estimates for lionfish. We estimated TW from the TL observations
-we collected in the central Mexican Caribbean (n = 109) using each of
-the 18 parameter pairs and divided predicted weights by known observed
-weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios across the different parameter pairs
-were tested with a one-way analysis of variance (ANOVA) and Tukey's test
-was used for \emph{post-hoc} tests. All analyses were performed in R
-version 3.5.0 \citep{rcore_2018}. Raw data and code used in this work
-are available on github.
+we collected in the central Mexican Caribbean (n = 109, with
+\(TL \in (34, 310)\)) using each of the 18 parameter pairs and divided
+predicted weights by known observed weights to obtain a simple measure
+of over- or underestimation. Difference in mean weight ratios across the
+different parameter pairs were tested with a one-way analysis of
+variance (ANOVA) and Tukey's test was used for \emph{post-hoc} tests.
+All analyses were performed in R version 3.5.1 \citep{rcore_2018}. Raw
+data and code used in this work are available on github.
 
-\section{Results}\label{results}
+\section*{Results}
 
@@
 \centering
-\begin{tabular}[t]{l|l|l|l|r|r|l|l}
-\hline
+\begin{tabular}[t]{llllrrll}
+\toprule
 Region & Sex & n & a & b & c & Fit & Reference\\
-\hline
+\midrule
 Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
-\hline
 Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
-\hline
 Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
-\hline
 Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
-\hline
 Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
-\hline
+\addlinespace
 Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
-\hline
 Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
-\hline
 Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
-\hline
 Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
-\hline
 Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
-\hline
+\addlinespace
 GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
-\hline
 GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-\hline
 GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-\hline
 GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-\hline
 GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
-\hline
+\addlinespace
 GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
-\hline
 GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
-\hline
 North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al., 2011\\
-\hline
+\bottomrule
 \end{tabular}
@@
 
-\section{Discussion}\label{discussion}
+\section*{Discussion}
+
+Our results suggest that lionfish exhibit highly variable allometric
+relationships across the invaded range, and that this variation is
+related to space. Moreover, we shot that the use of \emph{ex situ}
+parameters may lead to highly biased weight estimates. Our comparison of
+observed weights to those predicted with locally-informed parameters and
+\emph{ex situ} parameters showed that weight can be overestimated by
+more than a three-fold, and highlights the need to use local
+information. Here we discuss the implications of our findings and
+highlight potential future research directions.
 
@@
 management plans. The lionfish case poses the opposite scenario, where
-the manager desires to eradicate species. To accurately gauge both the
-effectiveness of lionfish removal efforts and the resources needed to
-successfully manage an invasion, we must acknowledge and understand
+the manager desires to eradicate the species. To accurately gauge both
+the effectiveness of lionfish removal efforts and the resources needed
+to successfully manage an invasion, we must acknowledge and understand
 regional biological differences in important variables such as
@@
 
-\section{Acknowledgements}\label{acknowledgements}
+\section*{Aknowledgements}
 
@@
 
-\bibliographystyle{spbasic}
-\bibliography{references.bib}
+\bibliography{references}
 

### 2019-01-15 docs/Manuscript.Rmd
Added reviews

@@
 
-```{r, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
+```{r map, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
 Circle sizes indicate sample size from each study, colors indicate the $b$ coefficient from Eq.
@@
 
-We also collected data from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Supplementary Table 1).
+We also used data from \citet{villaseorderbez_2014}, who collected organisms from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Supplementary Table 1).
 Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
@@
 
-```{r,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
+```{r fit1,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
 Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
@@
 
-```{r, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
+```{r fit2, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
 Colors indicate studies from which the parameters were extracted.
@@
 
-```{r, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
+```{r pred_obs, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
 Blue circles indicate median values and Like letters indicate values that do not differ significantly."}

### 2019-01-15 docs/Manuscript.tex
Added reviews

@@
 fish with sedentary behavior are likely to exhibit high levels of
-spatial variation in important life history characterstics such as
+spatial variation in important life history characteristics such as
 growth or natural mortality rates
@@
 in their calculations, so their parameters likely underestimated total
-wieght. Since no spineless to total weight conversions were available,
+weight. Since no spineless to total weight conversions were available,
 these parameters were taken as reported.
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/map-1.pdf}
 \caption{\label{fig:map}Locations where allometric growth parameters of
@@
 
-We also collected data from 10 sampling sites along the central Mexican
-Caribbean coast in 2010 (Supplementary Table 1). Sampling locations
-included wall and carpet reefs at depths between 5.7 m and 38.1 m. All
-observed lionfish (n = 109) were collected using hand nets and numbered
+We also used data from \citet{villaseorderbez_2014}, who collected
+organisms from 10 sampling sites along the central Mexican Caribbean
+coast in 2010 (Supplementary Table 1). Sampling locations included wall
+and carpet reefs at depths between 5.7 m and 38.1 m. All observed
+lionfish (n = 109) were collected using hand nets and numbered
 collection bottles. The use of hand nets prevented any weight loss due
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/fit1-1.pdf}
 \caption{\label{fig:l-w-carib}Length-weight relationship for 109
@@
 3.51, indicating that \emph{ex situ} parameters can result in major
-under- and overestimations. Tukey's \emph{post-hoc} test suggests that
+under- and overestimation. Tukey's \emph{post-hoc} test suggests that
 weight ratios for the central Mexican Caribbean were not different from
 those obtained with parameters from Little Cayman, the Bahamas, and some
-sites in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)). Weight estimates
+sites in the Gulf of Mexico (Tukey's HSD \(p > 0.05\)). Weight estimates
 using parameters from the Gulf of Mexico and North-Western Atlantic were
@@
 
-\caption{\label{tab:unnamed-chunk-9}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+\caption{\label{tab:unnamed-chunk-7}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
 All parameters have been adjusted to convert from millimeters to grams.
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/fit2-1.pdf}
 \caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/pred_obs-1.pdf}
 \caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
@@
 
-\section*{Aknowledgements}
+\section*{Acknowledgements}
 

### 2019-01-15 docs/reviews.Rmd
Added reviews

---
title: "Reviews"
output: pdf_document
---

# Editor (Joseph Pawlik)

Dear Juan Carlos,

Thank you for your submission to PeerJ.

It is my opinion as the Academic Editor for your article - Spatial variation in allometric growth of invasive lionfish has management implications - that it requires a number of Major Revisions.

My suggested changes and reviewer comments are shown below and on your article 'Overview' screen.

If you address these changes and resubmit, there's a good chance your article will be accepted (although this isn't guaranteed).

Both reviewers noted a need to consider different or additional analyses and to improve the writing of this contribution. Along with your revised ms., please include the text of both reviews in you point-by-point responses to the reviewers' comments.

Although not a hard deadline, we expect you to submit your revision within the next 55 days (received Dec 18).

With kind regards,

Joseph Pawlik

Academic Editor, PeerJ

# Reviewer 1 (Anonymous)

## Basic reporting

The word choice needs to be consistent throughout the paper when referring to various items (see below). The word "major" is a subjective term and not appropriate to use in this manuscript. There is not a test for major or non"majorness", rather let the reader decide what is major. There are a few other word choice comments or clarity questions that I have, see below.

L 19: Using the word “major” is a subjective word and elicits an emotional response usually in those that read it. Please choose a less loaded word. Major to one person is not necessarily major to all people. Instead use substantial, significant, etc. Please make the appropriate changes throughout the manuscript as well (results L142; discussion: L 175).

### Introduction:

- Line (L) 23: Capitalized “western” as was written in the Abstract and insert Ocean after “Atlantic”. As it reads now it sounds like the Atlantic Sea.

- L24: replace “liberation” with “release”.

- L 37: Albins and Hixon (2008) did their research in the Bahamas not Florida. Please correct.

- L47: Replace impacts with “negative effects”.

- L61: replace “know” with “known”.

- Fig 1. To stay consistent throughout the manuscript please refer to the general region of the Atlantic ocean the same way. Throughout the manuscript it is referred to as the Wester Atlantic, North Atlantic, North-Western Atlantic. Choose one way to refer to this throughout all text and figures (see lines: 11, 23, 23, 81, 145 158). Not sure I found them all.

### Methods:

- L 82: The Bahamas are actually part of the Western Atlantic Ocean, not the Caribbean, please update your sample sizes.

- L 115: You changed how you refer to grams, here you use (gr) where as you used (g) before (see lines 100, 113). For all references to grams, both in the text and figures, please use (g).

- L 121: It is not clear to me what the TL (34,310) means. Can you re-write or clarify what is meant by this?

- L125: Will you add the github URL so the readers can find the data and code. It was not clear where the raw data would be shared either.

### Results:

- L 134-135: Did you use all of the “different pairs of parameters” from all of the studies individually? Do I understand the right? If so can you adjust the words to be “each of the different pairs of parameters”?

- L 134-135: It is not clear what you mean by the lowest and highest weight estimates. For what size did you estimate these? These are pretty low weights so It must have been a small length, why just do it for a small length? Would you assume the effect to be the same among at all lengths? I suspect not with the exponential relationship.

- Fig. 3. Why are there two solid light green lines for the Sabido-Itza et al. 2016b? IN the legend for sex make sure that there are two dashed lines for female not just one short dashed line.

- Fig. 4. In the caption please indicate what “BC” and “PNAX” mean for the Sabido-Itza 2016b refer to. It is not clear to the reader.

### Discussion:

- L 152: The phrase “variation is related to space” does not really say much. What do you mean by related to space? Do you mean that the is spatial heterogeneity in the parameters?

- L 152: I am not sure what word you mean to use when you said: “we shot that”. Please choose a different word.

## Experimental design

- L 82-92: The authors do a good job indicating many of the differences among the studies, I wonder about the time of year, which might have a large effect on lionfish growth. One would expect both temperature and food availability to change. What time of year were these collected?

- L 92-94: Why include the Fogg et al. (2013) data when you already know that it is likely to underestimate the weight due to the use of spineless weight. What effect did this have on the analysis using data that you know to be different than the other data? Interestingly, Fig. 3 shows that the Fogg data has some of the largest weights-at-length, not the smallest.

## Validity of the findings

- L 107-108: There appear to be quite a few differences in the sampling and processing methods among all of the studies (lines 82-92). Which the authors rightly discuss and support the conclusion that using local in situ, not ex situ parameters are critical to use. However, I wonder how this affects the data analysis. To use an ordinary least squares regression when all of the locations and study methods are likely to have an effect does not seem appropriate. I suggest using a mixed modeling technique with "study" as a random effect and the other parameters from equation (3) as the fixed effects, so running a LMM. If the error is not normal, as I suspect because you used a standard error correction you could then use a GLMM with a Gamma error distribution since the response variables are continuous and strictly positive. Doing this type of analysis would allow you to talk more specifically about the amount of variation the occurs based on the ex situ parameters to a site.

- L175: Remove the word major from the main conclusion. Use either key, central, or fundamental. Major seems to be too strong and subjective of a word.

## Comments for the Author

Overall this study is a nice review of the existing data on allometric growth of lionfish. I like using new data as a case study to show local and regional differences and highlights the need to collect data at the local level to understand how this invasion manifest across the invaded region. I am interested to see how using a different statistical test might be able to shed some light on what the actual variation is among sights and using a mixed-model method should help you estimate this.

# Reviewer 2

In this manuscript, the authors present an analysis of 17 previously published weight-length relationships for lionfish throughout the species invasive range, along with new data on the weightlength relationship for a population along the central Mexican coast. The authors report important differences in allometric scaling among studies and highlight the effects of applying mis-specified growth parameters to stocks lacking this information. The overall question is relevant to fisheries management and control of invasive lionfish populations, and the paper is well referenced. However, there are several aspects of the paper that would improve the contribution, both in their methodological approach and discussion of their findings. I outline areas for major improvement below.

1. The authors don’t compare the weight-length relationships statistically; instead they compare mean ratios of predicted to observed weight when the estimated parameters from each different study are applied to the range of body lengths they collected in their central Mexican regional study. The violin plot (Fig. 4) that shows these ratios is illustrative, but this isn’t the best approach for several reasons. First, ratio data isn’t distributed normally, and has unqiue behaviors near the tails of the distribution. It should always be transformed, preferably using a logit transformation, prior to analysis. Second, the parameter estimates from other studies are being applied to lengths of fish outside of the range of lengths that were used to generate the parameters. ANCOVA is the most powerful approach for comparing multiple linear relationships, as it specifically accounts for variation in the covariate (total length) among groups. The application of ANCOVA to the logtransformed weight-length relationships would identify if the beta (b) coefficient varied significantly among populations, and then which populations differed could be discerned using post-hoc tests.

2. The second major improvement would be inclusion in Table 2 of relevant information that would most likely have contributed to any differences in the weight-length relationships among the regions. Most importantly, this Table should include the range of total lengths that each study included, sex (which the authors already include), the depth at which most fish were captured (if reported in the original study), and the range of months (or seasons) during which fish were captured. The size range is likely a major factor in driving differences, since most of the differences are observed at the largest total lengths, where data is likely sparse for many studies. Importantly, the authors should include a plot of the log-transformed data (reflecting the ANCOVA), with the plotted lines for each study only extending across the range of total lengths included in that study. Figure 3, showing the untransformed data, should be amended so that each fitted curve extends across the range of total lengths specific to that study. Fish occupying shallow versus deep habitats could demonstrate differences in growth and condition. Similarly, growth can vary considerably among seasonal periods, particularly seasons just prior to or during spawning.

3. The recommendation for major improvement is in the Discussion, related to the interpretation of their findings. The authors focus mainly on the implications of their findings, in a general way, but offer no potential explanations for the results they observed. Do the patterns of variation in weightlength relationships for invasive lionfish align with the genetic results that have been published? Are they aligned spatially…..do populations that are closer geographically have more similar growth relationships? Are there potential effects of depth/season? Did any studies demonstrate a sufficient lack of contrast in total length data to generate a weight-length relationships representative of the entire population in that region? A paragraph or two of Discussion on plausible explanations for the patterns they observed would be a valuable addition.

## Minor edits

1. In the Abstract, I would recommend changing the word ‘substantial’ to ‘significant’, assuming the ANCOVA detects differences in the beta coefficient. Also, ‘age-at-length’ should be ‘length-at-age’.

2. In the Methods section, the authors should refer to Tables and Figures in the order they are mentioned in the text. In the first sentence, they should refer to Fig. 1, not Fig. 3.

3. Methods lines 86 and 88: the authors refer to three and five studies in the text, but actually cite 4 and 7.

4. Methods lines 98-100: the authors refer to reduced gear selectivity of hand nets; it’s not clear how substantial this is, but is more reason to include details about sampling methods, size ranges included, depth, and month/season in the table that details the previous studies.

5. Methods: There is no need to include equation (3). The weight-length relationship in fishes is simply modeled as a power function, which can be log-transformed to generate a linear relationship. This is clear from equations (1) and (2), in fact, the log-transformation of this power function is standard enough that equation (2) does not likely need to appear in the manuscript, instead simply state the function was linearized using log-transformation.

6. Table 1 is not necessary as all of the included information is presented in Figure 2 or in the body of the text. Related to this, only include information on the weight-length relationship from the central Mexican coast in the text that is not already presented in Figure 2; there is no need to include it in two places.

7. Results line 140: stated predicted/observed ratios were 0.36 – 3.51, but in the sentences above the authors state the lowest was 0.80 and the highest was 1.76; if the above are means and the 0.36 – 3.51 refers to individual fish, this needs to be made clear, but I think reporting the means is sufficient, and most appropriate; particularly if the ANCOVA applied to the full relationships makes the analysis of the predicted/observed ratios redundant, and it is removed. Reporting the range in mean ratios would be sufficient along with an illustrative figure.

8. Remove the column for parameter c from Table 2. a = 10c, so there is no need to show both a and c in the Table. Change Fit to R2 in the Table heading, so it doesn’t need to be defined in the caption.

9. Figure 3 caption: Why do the authors only show the relationship for 12 studies instead of all 18
that are included in Figure 4?

### 2019-01-19 docs/Manuscript.Rmd
Modified text and included suggestions from both reviewrs

@@
 We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
-The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length.
+The spatial pattern we observed is consistent with findings from other studies focusing on genetics or length-at-age.
 We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight, but using parameters from nearby regions reduces this error.
-These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
+These findings can have substantial implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
 keywords:
@@
 
-Lionfish (*Pterois volitans/miles* complex) are an invasive species in the western Atlantic and Caribbean Sea, likely introduced through liberation of aquarium-kept organisms \citep{betancurr_2011}.
+Lionfish (*Pterois volitans/miles* complex) are an invasive species in the Western Atlantic Ocean and Caribbean Sea, likely introduced through release of aquarium-kept organisms \citep{betancurr_2011}.
 They are the first invasive marine vertebrates established along the North Atlantic Caribbean coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
@@
 A substantial amount of research describes lionfish impacts throughout its invaded range.
-A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate North Atlantic.
+A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate Western Atlantic.
 Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}).
-For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five-week period in Florida.
+For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five-week period in the Bahamas.
 \citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs.
@@
 Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from persistent populations in mesophotic ecosystems \citep{barbour_2011,andradibrown_2017}.
-However, promoting lionfish consumption might create a level of demand capable of incentivizing a stable fishery while controlling shallow-water populations, thus creating alternative livelihoods and avoiding further impacts to local biota.
+However, promoting lionfish consumption might create a level of demand capable of incentivizing a stable fishery while controlling shallow-water populations, thus creating alternative livelihoods and avoiding further negative effects to local biota.
 
@@
 First, culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and small home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
-It is know that fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characteristics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
-Second, genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
+It is known that fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characteristics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
+Second, genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the Western Atlantic and the Caribbean \citep{betancurr_2011}.
 Site-specific parameters are necessary to accurately estimate biomass when allometric relationships are spatially variable, and this variability is increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
@@
 
-review <- read.csv(here::here("data", "biometric_review.csv"), stringsAsFactors = F, strip.white = T, blank.lines.skip = T) %>% 
+review <- read.csv(here::here("data", "biometric_review.csv"), 
+                  stringsAsFactors = F,
+                  strip.white = T,
+                  blank.lines.skip = T) %>% 
   mutate(c = log10(a),
@@
 
-We reviewed 12 published studies and obtained 17 length-weight relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7), and Caribbean (n = 9, Table \ref{tab:all_params}, Fig \ref{fig:all_allo}).
+We reviewed 12 published studies and obtained 17 length-weight relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7), and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}).
 We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available.
@@
 Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
-Three studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and five studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016,sabidoitz_2016}, and two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
+Four studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}, and two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
 \citet{fogg_2013} use spineless weight in their calculations, so their parameters likely underestimated total weight.
 Since no spineless to total weight conversions were available, these parameters were taken as reported.
+Recall that the objective is not to describe population-level variations, but rather to exemplify how the use of *ex situ* parameters influences estimates.
+We therefore still use parameters by \citet{fogg_2013}, and raise cautions whenever relevant.
 
@@
   labs(x = "longitude", y = "latitude") +
-  geom_text(aes(x = -70, y = 30), label = "North Atlantic\nOcean") +
+  geom_text(aes(x = -70, y = 30), label = "Western Atlantic") +
   geom_text(aes(x = -90, y = 25), label = "Gulf of Mexico") +
-  geom_text(aes(x = -75, y = 15), label = "Caribbean\nSea")
+  geom_text(aes(x = -75, y = 15), label = "Caribbean")
 
@@
 All observed lionfish (n = 109) were collected using hand nets and numbered collection bottles.
-The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by eliminating gear selectivity.
+The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by avoiding gear selectivity.
 Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
@@
 The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Squares Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-When the $b = 3$, it is said that the organism exhibits a perfect isometric growth, so the $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$).
+When $b = 3$, it is said that the organism exhibits a perfect isometric growth, so the $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$).
 Coefficients were tested with a two-tailed Student's t, and the significance of the regression was corroborated with an F-test.
@@
 Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
-We standardized each study by converting coefficients and report all parameters as TL(mm) to TW (gr) conversions.
+We standardized each study by converting coefficients and report all parameters as TL(mm) to TW (g) conversions.
 Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and summarized in Table \ref{tab:all_params}.
@@
 We used the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
-We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109, with $TL \in (34, 310)$) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
+We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 to 310 mm).
+using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
 Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tukey's test was used for *post-hoc* tests.
 All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
-Raw data and code used in this work are available on github.
+Raw data and code used in this work are available on github at [https://github.com/jcvdav/lionfish_biometry](https://github.com/jcvdav/lionfish_biometry).
 
@@
 
-anova <- aov(Biomass_ratio ~ Study_id, Predicted_biomass)
+anova <- aov(Biomass_ratio ~ Study_id, data = Predicted_biomass)
+ancova_ratios <- aov(car::logit(Biomass_ratio) ~ Study_id + Length, data = Predicted_biomass)
+
+ancova <- aov(formula = log10(Weight / max(Weight)) ~ Study_id * log10(Length / max(Length)), data = Predicted_biomass)
+
 groups <- HSD.test(y = anova, trt = "Study_id")
@@
   theme_cowplot() +
-  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
+  labs(x = "Total length (mm)", y = "Total Weight (g)") +
   theme(text = element_text(family = "Times")) +
@@
 
-```{r, results = "asis"}
+```{r, results = "asis", eval = F}
 stargazer(model,
@@
 
-There were significant differences in our predicted weights for the central Mexican Caribbean when using the different pairs of parameters ($F(df = 17; 1944) = 61.55; p < 0.001$).
-The lowest weight estimates resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{sabidoitz_2016}, and the highest weight estimates came from the Northern Atlantic with `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` gr \citep{barbour_2011}.
-To put this in context, true observed weights were `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` gr.
-These correspond to predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
+There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F(df = 17; 1944) = 61.55; p < 0.001$).
+The lowest weight estimates for the observed lengths resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{sabidoitz_2016}.
+In contrast, the highest weight estimates came from the Western Atlantic with `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{barbour_2011}.
+To put this in context, true observed weights have a mean of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
+Weigths predicted from these extreme parameters correspond to predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
 
-The calculated ratio of predicted-to-observed weight ranged from `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")`, indicating that *ex situ* parameters can result in major under- and overestimation.
+The calculated ratio of predicted-to-observed weight ranged from `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")`, indicating that *ex situ* parameters can result in substantial weight under- and overestimation.
 Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
-Weight estimates using parameters from the Gulf of Mexico and North-Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}).
+Weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}).
 The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
@@
 review %>% 
-  select(Region, Gender2, N, a, b, c, r2, Study) %>% 
+  select(Region, Gender2, N, a, b, r2, Study) %>% 
   filter(!Study == "Fishbase") %>% 
-  arrange(Region) %>% 
+  arrange(desc(Region)) %>% 
   mutate(r2 = ifelse(is.na(r2), "-", r2),
@@
                booktabs = T,
-               col.names = c("Region", "Sex", "n", "a", "b", "c", "Fit", "Reference"),
+               col.names = c("Region", "Sex", "n", "a", "b", "$R^2$", "Reference"),
                caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
@@
 n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
-1 (presented in $\\times 10^{-5}$), c = y-intercept for Eq.
-3, b = exponent or slope for Eq.
+1 (presented in $\\times 10^{-5}$), b = exponent or slope for Eq.
 1 or Eq.
-3, respectively.
-The Fit column contains the reported $R^2$ of the model fit.", escape = T)
+3, respectively.",
+               escape = T)
 ```
@@
   geom_line(aes(y = This), size = 1.2, color = "black", linetype = "dashed") +
-  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
+  labs(x = "Total length (mm)", y = "Total Weight (g)") +
   theme_cowplot() +
@@
   guides(color = guide_legend(order = 1),
-         linetype = guide_legend(order = 0, ncol = 2),
+         linetype = guide_legend(order = 0, ncol = 2, override.aes = list(size = 0.5)),
          size = "none") +
@@
 Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
-The dashed black line represents the relationship estimated in this study."}
+The dashed black line represents the relationship estimated in this study.
+There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters."}
 fig_all_allo
@@
 ```{r pred_obs, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
-Blue circles indicate median values and Like letters indicate values that do not differ significantly."}
+Blue circles indicate median values and like letters indicate values that do not differ significantly.
+For Sabido-Itza et al, 2016b, BC and PNAX make reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites for which they report parameters."}
 fig_bio_ratio
@@
 
-Our results suggest that lionfish exhibit highly variable allometric relationships across the invaded range, and that this variation is related to space.
-Moreover, we shot that the use of *ex situ* parameters may lead to highly biased weight estimates.
+Our results suggest that lionfish exhibit highly variable allometric relationships across the invaded range, and that this variation is spatially heterogeneous.
+Moreover, we show that the use of *ex situ* parameters may lead to highly biased weight estimates.
 Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight can be overestimated by more than a three-fold, and highlights the need to use local information.
@@
 
-We detected substantial differences in weight-at-length between organisms from the Caribbean, Gulf of Mexico, and North-Western Atlantic.
+We detected substantial differences in weight-at-length between organisms from the Caribbean, Gulf of Mexico, and Western Atlantic.
 Groupings of predicted-to-observed weight ratios aligned with the spatial distribution of the examined studies, suggesting that these differences are mediated by space.
@@
 
-The results presented here have major implications for management.
+The results presented here have fundamental implications for management.
 For example, \citet{edwards_2014} simulated a lionfish culling program under two scenarios, one using length-at-age and length-to-weight parameters from North Carolina and one using parameters from Little Cayman.

### 2019-01-30 docs/Manuscript.Rmd
Added all comments from reviewers, must proof read and send to Sean

@@
 Sedentary species like lionfish often exhibit high levels of spatial variation in life history characteristics.
-We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters.
+We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found significant regional differences in allometric growth parameters.
 The spatial pattern we observed is consistent with findings from other studies focusing on genetics or length-at-age.
@@
 Lionfish (*Pterois volitans/miles* complex) are an invasive species in the Western Atlantic Ocean and Caribbean Sea, likely introduced through release of aquarium-kept organisms \citep{betancurr_2011}.
-They are the first invasive marine vertebrates established along the North Atlantic Caribbean coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
+They are the first invasive marine vertebrates established along these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
 Lionfish have established invasive populations in coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
@@
 A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate Western Atlantic.
-Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}).
+Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{green_2012,rocha_2015}; but see \citet{hackerott_2017}.
 For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five-week period in the Bahamas.
 \citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs.
-Their trophic impacts can be minimized if local lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
+However, their trophic impacts can be minimized if local lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
 
@@
 Second, genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the Western Atlantic and the Caribbean \citep{betancurr_2011}.
-Site-specific parameters are necessary to accurately estimate biomass when allometric relationships are spatially variable, and this variability is increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
-However, the region-wide differences in allometric growth parameters has remained unexplored for lionfish, despite the large number of site-specific studies reporting the length-weight relationship.
+The large number of site-specific studies reporting the length-weight relationship of lionfish provide variable estimates.
+These differences may be increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
+However, the extent to which using *ex situ* parameters to estimate total weight from length observations remains unexplored.
 
-Here, we compare previously published length-weight relationships for lionfish populations in North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
-We also collected lionfish length and weight data in the central Mexican Caribbean and report the first allometric growth equation for this region.
-The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish across the Caribbean and Western Atlantic and to discuss implications of these spatial differences.
+Here, we use previously published length-weight relationships for lionfish populations in North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica to quantify the magnitude of the error caused by using *ex situ* parameters to estimate lionfish weight from length observations.
+We also collected lionfish length and weight data in the central Mexican Caribbean and report the first length-weight relationship for this region.
+
+<!-- \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016} -->
 
@@
                              Gender == "Female" ~ "F",
-                             TRUE ~"B"))
+                             TRUE ~"B"),
+         tl_min = ifelse(is.na(tl_min), 34, tl_min),
+         tl_max = ifelse(is.na(tl_max), 310, tl_max))
 ```
@@
 Four studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}, and two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
-\citet{fogg_2013} use spineless weight in their calculations, so their parameters likely underestimated total weight.
-Since no spineless to total weight conversions were available, these parameters were taken as reported.
-Recall that the objective is not to describe population-level variations, but rather to exemplify how the use of *ex situ* parameters influences estimates.
-We therefore still use parameters by \citet{fogg_2013}, and raise cautions whenever relevant.
 
@@
 
-proj <- CRS("+proj=longlat +datum=NAD27")
+proj <- c("+proj=longlat +datum=NAD27")
 
@@
 data(World)
-W <- spTransform(World, proj) %>% 
-  st_as_sf()
+W <- st_transform(World, proj)
 
@@
   lims(x = c(-100, -60), y = c(9, 36)) +
-  labs(x = "longitude", y = "latitude") +
+  labs(x = "Longitude", y = "Latitude") +
   geom_text(aes(x = -70, y = 30), label = "Western Atlantic") +
@@
 
-We also used data from \citet{villaseorderbez_2014}, who collected organisms from 10 sampling sites along the central Mexican Caribbean coast in 2010 (Supplementary Table 1).
+We also used data from \citet{villaseorderbez_2014}, who collected organisms from 10 sampling sites along the central Mexican Caribbean coast in the Summer of 2010 (Supplementary Table 1).
 Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
@@
 Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
+
+\clearpage
 
@@
 
-\clearpage
+<!-- Transforming this equation via base-10 logarithms we obtain: -->
 
-Transforming this equation via base-10 logarithms we obtain:
+<!-- \begin{equation} -->
+<!-- \label{eq:log-alo} -->
+<!-- log_{10}(TW) = b\times log_{10}(TL) + log_{10}(a) -->
+<!-- \end{equation} -->
 
-\begin{equation}
-\label{eq:log-alo}
-log_{10}(TW) = b\times log_{10}(TL) + log_{10}(a)
-\end{equation}
+<!-- This can be simplified and re-written as: -->
 
-This can be simplified and re-written as:
+<!-- \begin{equation} -->
+<!-- \label{eq:log-alo-trans} -->
+<!-- Y = bX + c -->
+<!-- \end{equation} -->
 
-\begin{equation}
-\label{eq:log-alo-trans}
-Y = bX + c
-\end{equation}
+<!-- Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, and $c = log_{10}(a)$. -->
 
-Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, and $c = log_{10}(a)$.
-The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Squares Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}.
+The above equation was linearized using $log_{10}$-transformation.
+The coefficients were estimated with an Ordinary Least Squares Regression, and heteroskedastic-robust standard error correction was applied \citep{zeileis_2004}.
 When $b = 3$, it is said that the organism exhibits a perfect isometric growth, so the $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$).
@@
 Some of the reviewed studies inconsistently defined $a$ as either the ponderal index from Eq.
-\ref{eq:allometric} or the y-intercept ($c$) from Eq.
-\ref{eq:log-alo-trans}.
+\ref{eq:allometric} or the y-intercept from the linearized log-transformed equation.
 Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
@@
 We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here.
+Recall that the objective of this study is not to describe population-level variations, but rather to estimate how the use of *ex situ* parameters influences weight estimates.
 We used the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
-We estimated TW from the TL observations we collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 to 310 mm).
-using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios across the different parameter pairs were tested with a one-way analysis of variance (ANOVA) and Tukey's test was used for *post-hoc* tests.
+We estimated $TW$ from the $TL$ observations we collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 mm to 310 mm) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
+Difference in mean weight ratios were tested with an analysis of covariance (ANCOVA) using study and $TL$ as covariates.
+Ratios were logit-transformed prior to analysis, and a *post-hoc* Tukey's test was used to identify groups where mean ratios did not differ.
 All analyses were performed in R version `r paste(version$major, version$minor, sep = ".")` \citep{rcore_2018}.
-Raw data and code used in this work are available on github at [https://github.com/jcvdav/lionfish_biometry](https://github.com/jcvdav/lionfish_biometry).
+Raw data and code used in this work are available on github at github.com/jcvdav/lionfish_biometry.
 
@@
   mutate(pWeight = a*(Length^b),
-    Biomass_ratio = pWeight / Weight)
+    Biomass_ratio = pWeight / Weight,
+    logit_biomass_ratio = car::logit(Biomass_ratio))
 
 anova <- aov(Biomass_ratio ~ Study_id, data = Predicted_biomass)
-ancova_ratios <- aov(car::logit(Biomass_ratio) ~ Study_id + Length, data = Predicted_biomass)
+ancova <- aov(logit_biomass_ratio ~ Study_id + Length, data = Predicted_biomass)
 
-ancova <- aov(formula = log10(Weight / max(Weight)) ~ Study_id * log10(Length / max(Length)), data = Predicted_biomass)
-
-groups <- HSD.test(y = anova, trt = "Study_id")
+groups <- HSD.test(y = ancova, trt = "Study_id")
 
@@
 The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
-Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region, and model fit statistics are presented in Table \ref{tab:reg_table}.
+Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region.
 
@@
           covariate.labels = c("c", "b"),
-          dep.var.labels = "log10(TW)", title = "\\label{tab:reg_table}Coefficients of the linear model fit to Eq \\ref{eq:log-alo-trans}.
-Numbers in parenthesees represent heteroskedastic-robust standard errors.")
+          dep.var.labels = "log10(TW)", title = "\\label{tab:reg_table}Coefficients of the linear model fit to Eq 1. Numbers in parenthesees represent heteroskedastic-robust standard errors.")
 ```
@@
 To put this in context, true observed weights have a mean of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
-Weigths predicted from these extreme parameters correspond to predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
+Weigths predicted from these extreme parameters correspond to mean $\pm$ SD predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
+At its extremes, other parameters resulted in under- and overestimations in the order of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` of the actual observed weight, indicating that *ex situ* parameters can result in substantial weight under- and overestimation.
 
-The calculated ratio of predicted-to-observed weight ranged from `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")`, indicating that *ex situ* parameters can result in substantial weight under- and overestimation.
 Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
@@
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
-Spineless weight parameters from \citet{fogg_2013} still produced predicted-to-observed weight ratios > 1.
 
@@
   arrange(desc(Region)) %>% 
-  mutate(r2 = ifelse(is.na(r2), "-", r2),
+  mutate(r2 = formatC(r2, digits = 2),
+         r2 = ifelse(r2 == " NA", "-", r2),
          N = ifelse(is.na(N), "-", N),
@@
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
-1 (presented in $\\times 10^{-5}$), b = exponent or slope for Eq.
-1 or Eq.
-3, respectively.",
-               escape = T)
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter (presented in $\\times 10^{-5}$), b = exponent.")
 ```
@@
 ```{r}
+This <- data.frame(Length = c(34:310)) %>% 
+  mutate(Weight = 10^(coefficients(model)[1] + coefficients(model)[2]*log10(Length)))
+
 fig_all_allo <- review %>% 
@@
   unnest() %>% 
-  mutate(Weight = a*(Length^b),
-         This = 10^(coefficients(model)[1] + coefficients(model)[2]*log10(Length))) %>%
+  filter(Length > tl_min & Length < tl_max) %>% 
+  mutate(Weight = a*(Length^b)) %>%
   group_by(Length) %>% 
@@
   geom_line(aes(y = Weight, color = Study, linetype = Gender, group = Study_id), size = 1) +
-  geom_line(aes(y = This), size = 1.2, color = "black", linetype = "dashed") +
+  geom_line(data = This, aes(x = Length, y = Weight),
+            size = 1.2, color = "black", linetype = "dashed") +
   labs(x = "Total length (mm)", y = "Total Weight (g)") +
@@
 
-```{r fit2, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
+```{r fit2, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}log-log transformation of the length-weight relationships (n = 18) for 12 studies and this study.
+The curves are shown for the range of lengths reported in each study (See Supplementary Table 2); when ranges were not present, we use the ones found in this study (34mm - 310 mm).
 Colors indicate studies from which the parameters were extracted.
@@
 The dashed black line represents the relationship estimated in this study.
-There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters."}
+There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters.
+A log-log version of this figure is presented in Figure S4."}
 fig_all_allo
@@
   mutate(Study_id = rownames(.)) %>% 
-  select(-Biomass_ratio)
+  select(-logit_biomass_ratio)
 
@@
         axis.title = element_text(size = 12)) +
-  geom_text(aes(y = 3.7, label = groups), family = "Times", fontface = "plain") +
+  geom_text(aes(y = 3.5, label = groups), family = "Times", fontface = "plain") +
   scale_y_continuous(limits = c(NA, 3.7)) +
@@
 
-Our results suggest that lionfish exhibit highly variable allometric relationships across the invaded range, and that this variation is spatially heterogeneous.
+Our results suggest that lionfish exhibit highly variable allometric relationships across the invaded range, and that this variation is spatially heterogeneous and relevant for management of the invasion.
 Moreover, we show that the use of *ex situ* parameters may lead to highly biased weight estimates.
@@
 Here we discuss the implications of our findings and highlight potential future research directions.
-
-We detected substantial differences in weight-at-length between organisms from the Caribbean, Gulf of Mexico, and Western Atlantic.
-Groupings of predicted-to-observed weight ratios aligned with the spatial distribution of the examined studies, suggesting that these differences are mediated by space.
-These regional allometric differences mirror similar patterns in age-at-length of lionfish across both their invaded and native regions \citep{pusack_2016}.
-Variation may be driven by genetics or by organisms' exposure to distinct environmental conditions.
-For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be climate-driven.
-Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both.
-Future research is needed to determine which processes are at work here.
 
@@
 To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.
+
+We detected substantial differences in weight-at-length between organisms from the Caribbean, Gulf of Mexico, and Western Atlantic.
+Groupings of predicted-to-observed weight ratios identified in our *post hoc* testing aligned with the spatial distribution of the examined studies, suggesting that these differences may be mediated by space.
+These regional allometric differences mirror similar patterns in age-at-length of lionfish across both their invaded and native regions \citep{pusack_2016}.
+Variation may be driven by genetics or by organisms' exposure to distinct environmental conditions.
+For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be driven by the environment.
+
+We might be inclined to attribute all variation to the spatial origin of these parameters.
+However, these were not only collected for different locations, but also using a range of different sampling methods and for different points in time (See Supplementary Table 2 for an extended version of Table 1).
+While we are not able to evaluate how these factors influence previous estimates (raw data from all studies would be needed), it is certain that the lack of locally-calculated parameters may induce significant bias when calculating weight from length observations.
+Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both.
+The magnitude of the bias and our lack of understanding of the source of variation hihglights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and link these to previously suggested environmental and genetic structures.
+Such an endeavor would provide insights into lionfish biology and better inform management.
+
+Applying parameters estimates to lengths that may be outside the range of lengths originally used to estimate the parameters may also induce variation lead to over- and underestimation.
+Our smallest observed length was for an organism 34 mm in TL.
+However, only two studies estimated parametrs with smaller organisms \citep{sabidoitza_2016,edwards_2014}.
+On the other hand, our largest organism had a TL of 310 mm, which is well within the range of all other studies (maximum observed lengths varied from 325 mm to 475 mm; See Supplementary Table 2).
+Due to the exponential nature of the allometric relationship, the error is higher when extrapolation is done for TLs that are larger than the maximum.
+This means that not only must managers use locally-informed data, but that these local data must also include the full range of lengths present in the region to reduce error caused by extrapolation.
 
@@
 
-The authors would like to thank thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
+The thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
+We are greateful for comments raised by the editor and two anonimous reviewers, which significantly increased the quality of this work.
 

### 2019-01-30 docs/Manuscript.tex
Added all comments from reviewers, must proof read and send to Sean

@@
   Santa Barbara, Santa Barbara, California, USA}
-\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{jvillasenor@ucsb.edu}
+\corrauthor[1]{Juan Carlos Villaseñor-Derbez}{juancarlos@ucsb.edu}
 
@@
 relationships for lionfish taken throughout their invasive range and
-found substantial regional differences in allometric growth parameters.
+found significant regional differences in allometric growth parameters.
 The spatial pattern we observed is consistent with findings from other
-studies focusing on genetics or age-at-length. We show that the use of
+studies focusing on genetics or length-at-age. We show that the use of
 \textit{ex situ} parameters can result in up to a threefold under- or
 overestimation of total weight, but using parameters from nearby regions
-reduces this error. These findings can have major implications for
+reduces this error. These findings can have substantial implications for
 management in terms of predicting effects on local ecosystems,
@@
 Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
-in the western Atlantic and Caribbean Sea, likely introduced through
-liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
-the first invasive marine vertebrates established along the North
-Atlantic Caribbean coasts
+in the Western Atlantic Ocean and Caribbean Sea, likely introduced
+through release of aquarium-kept organisms \citep{betancurr_2011}. They
+are the first invasive marine vertebrates established along these coasts
 \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence
@@
 invasive lionfish prey on at least 167 different species across the
-tropical and temperate North Atlantic. Their feeding behavior and high
+tropical and temperate Western Atlantic. Their feeding behavior and high
 consumption rates can reduce recruitment and population sizes of native
 reef-fish species, and can further endanger reef fish
-(\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}). For
+\citep{green_2012,rocha_2015}; but see \citet{hackerott_2017}. For
 example, field experiments by \citet{albins_2008} showed that lionfish
 establishment led to reduced recruitment of native fishes by nearly 80\%
-over a five-week period in Florida. \citet{green_2012} reported that
+over a five-week period in the Bahamas. \citet{green_2012} reported that
 prey fish biomass declined by 65\% over two years as lionfish biomass
-increased along Bahamian coral reefs. Their trophic impacts can be
-minimized if local lionfish biomass is controlled by culling
+increased along Bahamian coral reefs. However, their trophic impacts can
+be minimized if local lionfish biomass is controlled by culling
 \citep{ariasgonzalez_2011}.
@@
 shallow-water populations, thus creating alternative livelihoods and
-avoiding further impacts to local biota.
+avoiding further negative effects to local biota.
 
@@
 levels of site fidelity and small home ranges
-\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. It is know that
-fish with sedentary behavior are likely to exhibit high levels of
+\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. It is known
+that fish with sedentary behavior are likely to exhibit high levels of
 spatial variation in important life history characteristics such as
@@
 existence of two genetically distinct invasive subpopulations between
-the northwest Atlantic and the Caribbean \citep{betancurr_2011}.
-Site-specific parameters are necessary to accurately estimate biomass
-when allometric relationships are spatially variable, and this
-variability is increasingly important when estimating the potential
-effectiveness of lionfish culling programs
+the Western Atlantic and the Caribbean \citep{betancurr_2011}. The large
+number of site-specific studies reporting the length-weight relationship
+of lionfish provide variable estimates. These differences may be
+increasingly important when estimating the potential effectiveness of
+lionfish culling programs
 \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
-region-wide differences in allometric growth parameters has remained
-unexplored for lionfish, despite the large number of site-specific
-studies reporting the length-weight relationship.
+extent to which using \emph{ex situ} parameters to estimate total weight
+from length observations remains unexplored.
 
-Here, we compare previously published length-weight relationships for
+Here, we use previously published length-weight relationships for
 lionfish populations in North Carolina, Northern and Southern Gulf of
 Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica,
-Bonaire, Puerto Rico, and Costa Rica
-\citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
-We also collected lionfish length and weight data in the central Mexican
-Caribbean and report the first allometric growth equation for this
-region. The objective of this paper is to describe the spatial pattern
-of length-weight relationships of lionfish across the Caribbean and
-Western Atlantic and to discuss implications of these spatial
-differences.
+Bonaire, Puerto Rico, and Costa Rica to quantify the magnitude of the
+error caused by using \emph{ex situ} parameters to estimate lionfish
+weight from length observations. We also collected lionfish length and
+weight data in the central Mexican Caribbean and report the first
+length-weight relationship for this region.
 
@@
 We reviewed 12 published studies and obtained 17 length-weight
-relationships for the North Atlantic (n = 1), Gulf of Mexico (n = 7),
-and Caribbean (n = 9, Table \ref{tab:all_params}, Fig
-\ref{fig:all_allo}). We collected information on sampling methods, sex
-differentiation, location, and depth ranges from each study when
-available. Only two studies reported parameters for each gender
+relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
+and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}). We
+collected information on sampling methods, sex differentiation,
+location, and depth ranges from each study when available. Only two
+studies reported parameters for each gender
 \citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were
@@
 presented information for organisms obtained at depths between 0.5 m and
-57 m. Three studies explicitly stated that their organisms were sampled
+57 m. Four studies explicitly stated that their organisms were sampled
 with pole spears
-\citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and five
+\citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six
 studies mentioned that some of their organisms were obtained with pole
 spears (or other type of harpoon) but also hand-held nets or fish traps
-\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016,sabidoitz_2016},
+\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016},
 and two studies did not specify how organisms were sampled
-\citep{darling_2011,deleon_2013}. \citet{fogg_2013} use spineless weight
-in their calculations, so their parameters likely underestimated total
-weight. Since no spineless to total weight conversions were available,
-these parameters were taken as reported.
+\citep{darling_2011,deleon_2013}.
 
@@
 organisms from 10 sampling sites along the central Mexican Caribbean
-coast in 2010 (Supplementary Table 1). Sampling locations included wall
-and carpet reefs at depths between 5.7 m and 38.1 m. All observed
-lionfish (n = 109) were collected using hand nets and numbered
+coast in the Summer of 2010 (Supplementary Table 1). Sampling locations
+included wall and carpet reefs at depths between 5.7 m and 38.1 m. All
+observed lionfish (n = 109) were collected using hand nets and numbered
 collection bottles. The use of hand nets prevented any weight loss due
-to bleeding and allowed better representation of small sizes by
-eliminating gear selectivity. Organisms were euthanized via pithing and
-Total Length (TL; mm) and Total Weight (TW; g) were recorded.
+to bleeding and allowed better representation of small sizes by avoiding
+gear selectivity. Organisms were euthanized via pithing and Total Length
+(TL; mm) and Total Weight (TW; g) were recorded.
+
+\clearpage
 
@@
 
-\clearpage
-
-Transforming this equation via base-10 logarithms we obtain:
-
-\begin{equation}
-\label{eq:log-alo}
-log_{10}(TW) = b\times log_{10}(TL) + log_{10}(a)
-\end{equation}
-
-This can be simplified and re-written as:
-
-\begin{equation}
-\label{eq:log-alo-trans}
-Y = bX + c
-\end{equation}
-
-Where \(Y = log_{10}(TW)\), \(X = log_{10}(TL)\), and
-\(c = log_{10}(a)\). The coefficients (\(c\) and \(b\)) were estimated
-with an Ordinary Least Squares Regression and heteroskedastic-robust
-standard error correction \citep{zeileis_2004}. When the \(b = 3\), it
-is said that the organism exhibits a perfect isometric growth, so the
-\(b\) coefficient was tested against the null hypothesis of isometric
-growth (\emph{i.e.} \(H_0: b = 3\)). Coefficients were tested with a
-two-tailed Student's t, and the significance of the regression was
-corroborated with an F-test.
+The above equation was linearized using \(log_{10}\)-transformation. The
+coefficients were estimated with an Ordinary Least Squares Regression,
+and heteroskedastic-robust standard error correction was applied
+\citep{zeileis_2004}. When \(b = 3\), it is said that the organism
+exhibits a perfect isometric growth, so the \(b\) coefficient was tested
+against the null hypothesis of isometric growth (\emph{i.e.}
+\(H_0: b = 3\)). Coefficients were tested with a two-tailed Student's t,
+and the significance of the regression was corroborated with an F-test.
 
 Some of the reviewed studies inconsistently defined \(a\) as either the
-ponderal index from Eq. \ref{eq:allometric} or the y-intercept (\(c\))
-from Eq. \ref{eq:log-alo-trans}. Other studies incorrectly reported
+ponderal index from Eq. \ref{eq:allometric} or the y-intercept from the
+linearized log-transformed equation. Other studies incorrectly reported
 parameters as mm-to-g conversions when they were in fact cm-to-g
 conversions. We standardized each study by converting coefficients and
-report all parameters as TL(mm) to TW (gr) conversions. Locations where
+report all parameters as TL(mm) to TW (g) conversions. Locations where
 allometric studies have been performed are shown in Figure \ref{fig:map}
@@
 parameters extracted from the literature and the additional pair
-calculated here. We used the central Mexican Caribbean as a case study
-of how the use of \emph{ex situ} parameters influences the accuracy of
-weight estimates for lionfish. We estimated TW from the TL observations
-we collected in the central Mexican Caribbean (n = 109, with
-\(TL \in (34, 310)\)) using each of the 18 parameter pairs and divided
-predicted weights by known observed weights to obtain a simple measure
-of over- or underestimation. Difference in mean weight ratios across the
-different parameter pairs were tested with a one-way analysis of
-variance (ANOVA) and Tukey's test was used for \emph{post-hoc} tests.
-All analyses were performed in R version 3.5.1 \citep{rcore_2018}. Raw
-data and code used in this work are available on github.
+calculated here. Recall that the objective of this study is not to
+describe population-level variations, but rather to estimate how the use
+of \emph{ex situ} parameters influences weight estimates. We used the
+central Mexican Caribbean as a case study of how the use of \emph{ex
+situ} parameters influences the accuracy of weight estimates for
+lionfish. We estimated \(TW\) from the \(TL\) observations we collected
+in the central Mexican Caribbean (n = 109, with \(TL\) ranging from 34
+mm to 310 mm) using each of the 18 parameter pairs and divided predicted
+weights by known observed weights to obtain a simple measure of over- or
+underestimation. Difference in mean weight ratios were tested with an
+analysis of covariance (ANCOVA) using study and \(TL\) as covariates.
+Ratios were logit-transformed prior to analysis, and a \emph{post-hoc}
+Tukey's test was used to identify groups where mean ratios did not
+differ. All analyses were performed in R version 3.5.2
+\citep{rcore_2018}. Raw data and code used in this work are available on
+github at github.com/jcvdav/lionfish\_biometry.
 
@@
 other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
-shows the relationship between TL and TW for this region, and model fit
-statistics are presented in Table \ref{tab:reg_table}.
+shows the relationship between TL and TW for this region.
 
@@
 
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:reg_table}Coefficients of the linear model fit to Eq \ref{eq:log-alo-trans}. Numbers in parenthesees represent heteroskedastic-robust standard errors.} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{$log_{10}(TW)$} \\ 
-\cline{2-2} 
-\hline \\[-1.8ex] 
- c & $-$5.494 (0.083)$^{***}$ \\ 
-  b & 3.235 (0.039)$^{***}$ \\ 
- \hline \\[-1.8ex] 
-F Statistic & 6928.67*** (df = 1; 107) \\ 
-Observations & 109 \\ 
-Adjusted R$^{2}$ & 0.976 \\ 
-Residual Std. Error & 0.096 (df = 107) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
+There were significant differences in our predicted weights for the
+central Mexican Caribbean when using each of the different pairs of
+parameters (\(F(df = 17; 1944) = 61.55; p < 0.001\)). The lowest weight
+estimates for the observed lengths resulted from using the allometric
+parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
+of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
+highest weight estimates came from the Western Atlantic with 73.76
+\(\pm\) 96.11 g \citep{barbour_2011}. To put this in context, true
+observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weigths predicted
+from these extreme parameters correspond to mean \(\pm\) SD
+predicted-to-observed weights ratios of 0.80 \(\pm\) 0.19 and 1.76
+\(\pm\) 0.50 (mean \(\pm\) SD), respectively. At its extremes, other
+parameters resulted in under- and overestimations in the order of 0.36
+to 3.51 of the actual observed weight, indicating that \emph{ex situ}
+parameters can result in substantial weight under- and overestimation.
 
-There were significant differences in our predicted weights for the
-central Mexican Caribbean when using the different pairs of parameters
-(\(F(df = 17; 1944) = 61.55; p < 0.001\)). The lowest weight estimates
-resulted from using the allometric parameters from Banco Chinchorro in
-the Caribbean, with mean \(\pm\) SD of 40.37 \(\pm\) 58.74 gr
-\citep{sabidoitz_2016}, and the highest weight estimates came from the
-Northern Atlantic with 73.76 \(\pm\) 96.11 gr \citep{barbour_2011}. To
-put this in context, true observed weights were 52.56 \(\pm\) 76.58 gr.
-These correspond to predicted-to-observed weights ratios of 0.80 \(\pm\)
-0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.
+Tukey's \emph{post-hoc} test suggests that weight ratios for the central
+Mexican Caribbean were not different from those obtained with parameters
+from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico
+(Tukey's HSD \(p > 0.05\)). Weight estimates using parameters from the
+Gulf of Mexico and Western Atlantic were higher on average than those
+from the Caribbean (Fig \ref{fig:all_allo}). The average (\(\pm\) SD)
+predicted-to-observed weight ratios from these three regions were 1.24
+\(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
+Predicted-to-observed weight ratios are presented in Figure
+\ref{fig:bio_ratio}.
 
-The calculated ratio of predicted-to-observed weight ranged from 0.36 to
-3.51, indicating that \emph{ex situ} parameters can result in major
-under- and overestimation. Tukey's \emph{post-hoc} test suggests that
-weight ratios for the central Mexican Caribbean were not different from
-those obtained with parameters from Little Cayman, the Bahamas, and some
-sites in the Gulf of Mexico (Tukey's HSD \(p > 0.05\)). Weight estimates
-using parameters from the Gulf of Mexico and North-Western Atlantic were
-higher on average than those from the Caribbean (Fig
-\ref{fig:all_allo}). The average (\(\pm\) SD) predicted-to-observed
-weight ratios from these three regions were 1.24 \(\pm\) 0.309, 1.76
-\(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
-Predicted-to-observed weight ratios are presented in Figure
-\ref{fig:bio_ratio}. Spineless weight parameters from \citet{fogg_2013}
-still produced predicted-to-observed weight ratios \textgreater{} 1.
-
-\begin{table}
+\begin{table}[t]
 
@@
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq.
-1 (presented in $\times 10^{-5}$), c = y-intercept for Eq.
-3, b = exponent or slope for Eq.
-1 or Eq.
-3, respectively.
-The Fit column contains the reported $R^2$ of the model fit.}
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
 \centering
-\begin{tabular}[t]{llllrrll}
+\begin{tabular}{llllrll}
 \toprule
-Region & Sex & n & a & b & c & Fit & Reference\\
+Region & Sex & n & a & b & \$R\textasciicircum{}2\$ & Reference\\
 \midrule
-Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
-Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
-Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
-Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
-Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
+Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
+Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
+GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
+GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
 \addlinespace
-Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
-Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
-Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
-Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
-Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
+GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
+GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
+GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
+Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
 \addlinespace
-GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
-GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
+Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
+Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
+Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
+Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
+Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
 \addlinespace
-GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
-GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
-North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al., 2011\\
+Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
+Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
+Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
 \bottomrule
@@
 \includegraphics{Manuscript_files/figure-latex/fit2-1.pdf}
-\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
-studies and this study. Colors indicate studies from which the
-parameters were extracted. Dotted, dashed and solid lines show models
-for males, females, and combined sexes, respectively. The dashed black
-line represents the relationship estimated in this study.}
+\caption{\label{fig:all_allo}log-log transformation of the length-weight
+relationships (n = 18) for 12 studies and this study. The curves are
+shown for the range of lengths reported in each study (See Supplementary
+Table 2); when ranges were not present, we use the ones found in this
+study (34mm - 310 mm). Colors indicate studies from which the parameters
+were extracted. Dotted, dashed and solid lines show models for males,
+females, and combined sexes, respectively. The dashed black line
+represents the relationship estimated in this study. There are two solid
+green lines for Sabido-Itza et al, 2016b, one for each of the two sites
+for which they report parameters. A log-log version of this figure is
+presented in Figure S4.}
 \end{figure}
@@
 weight ratios for 18 pairs of allometric parameters. Blue circles
-indicate median values and Like letters indicate values that do not
-differ significantly.}
+indicate median values and like letters indicate values that do not
+differ significantly. For Sabido-Itza et al, 2016b, BC and PNAX make
+reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak,
+two sites for which they report parameters.}
 \end{figure}
@@
 relationships across the invaded range, and that this variation is
-related to space. Moreover, we shot that the use of \emph{ex situ}
-parameters may lead to highly biased weight estimates. Our comparison of
-observed weights to those predicted with locally-informed parameters and
-\emph{ex situ} parameters showed that weight can be overestimated by
-more than a three-fold, and highlights the need to use local
-information. Here we discuss the implications of our findings and
-highlight potential future research directions.
-
-We detected substantial differences in weight-at-length between
-organisms from the Caribbean, Gulf of Mexico, and North-Western
-Atlantic. Groupings of predicted-to-observed weight ratios aligned with
-the spatial distribution of the examined studies, suggesting that these
-differences are mediated by space. These regional allometric differences
-mirror similar patterns in age-at-length of lionfish across both their
-invaded and native regions \citep{pusack_2016}. Variation may be driven
-by genetics or by organisms' exposure to distinct environmental
-conditions. For example, \citet{betancurr_2011} used mitochondrial DNA
-to demonstrate the existence of two distinct population groups,
-identified as the ``Caribbean group'' and ``Northern Group'', and
-\citet{fogg_2015} alternatively suggested that age-at-length differences
-may be climate-driven. Differences in weight-at-length could also
-reflect differential energy input or usage, or a combination of both.
-Future research is needed to determine which processes are at work here.
+spatially heterogeneous and relevant for management of the invasion.
+Moreover, we show that the use of \emph{ex situ} parameters may lead to
+highly biased weight estimates. Our comparison of observed weights to
+those predicted with locally-informed parameters and \emph{ex situ}
+parameters showed that weight can be overestimated by more than a
+three-fold, and highlights the need to use local information. Here we
+discuss the implications of our findings and highlight potential future
+research directions.
 
@@
 
-The results presented here have major implications for management. For
-example, \citet{edwards_2014} simulated a lionfish culling program under
-two scenarios, one using length-at-age and length-to-weight parameters
-from North Carolina and one using parameters from Little Cayman. Their
-results show that using different parameters caused up to a four-year
-difference in the time required for the simulated lionfish population to
-recover to 90\% of its initial biomass after removals ceased. Here, we
-show that using one set of length-weight parameters versus another for a
-given length can result in more than a threefold under- or
-overestimation of total weight. These spatially-driven differences
-become especially important when allocating resources for lionfish
-removal programs, incentivizing lionfish fisheries as a source of
-alternative livelihoods, or estimating ecosystem impacts. Research
+We detected substantial differences in weight-at-length between
+organisms from the Caribbean, Gulf of Mexico, and Western Atlantic.
+Groupings of predicted-to-observed weight ratios identified in our
+\emph{post hoc} testing aligned with the spatial distribution of the
+examined studies, suggesting that these differences may be mediated by
+space. These regional allometric differences mirror similar patterns in
+age-at-length of lionfish across both their invaded and native regions
+\citep{pusack_2016}. Variation may be driven by genetics or by
+organisms' exposure to distinct environmental conditions. For example,
+\citet{betancurr_2011} used mitochondrial DNA to demonstrate the
+existence of two distinct population groups, identified as the
+``Caribbean group'' and ``Northern Group'', and \citet{fogg_2015}
+alternatively suggested that age-at-length differences may be driven by
+the environment.
+
+We might be inclined to attribute all variation to the spatial origin of
+these parameters. However, these were not only collected for different
+locations, but also using a range of different sampling methods and for
+different points in time (See Supplementary Table 2 for an extended
+version of Table 1). While we are not able to evaluate how these factors
+influence previous estimates (raw data from all studies would be
+needed), it is certain that the lack of locally-calculated parameters
+may induce significant bias when calculating weight from length
+observations. Differences in weight-at-length could also reflect
+differential energy input or usage, or a combination of both. The
+magnitude of the bias and our lack of understanding of the source of
+variation hihglights the need to simultaneously collect length-weight
+information across the invaded range to test for spatially-induced
+patterns and link these to previously suggested environmental and
+genetic structures. Such an endeavor would provide insights into
+lionfish biology and better inform management.
+
+Applying parameters estimates to lengths that may be outside the range
+of lengths originally used to estimate the parameters may also induce
+variation lead to over- and underestimation. Our smallest observed
+length was for an organism 34 mm in TL. However, only two studies
+estimated parametrs with smaller organisms
+\citep{sabidoitza_2016,edwards_2014}. On the other hand, our largest
+organism had a TL of 310 mm, which is well within the range of all other
+studies (maximum observed lengths varied from 325 mm to 475 mm; See
+Supplementary Table 2). Due to the exponential nature of the allometric
+relationship, the error is higher when extrapolation is done for TLs
+that are larger than the maximum. This means that not only must managers
+use locally-informed data, but that these local data must also include
+the full range of lengths present in the region to reduce error caused
+by extrapolation.
+
+The results presented here have fundamental implications for management.
+For example, \citet{edwards_2014} simulated a lionfish culling program
+under two scenarios, one using length-at-age and length-to-weight
+parameters from North Carolina and one using parameters from Little
+Cayman. Their results show that using different parameters caused up to
+a four-year difference in the time required for the simulated lionfish
+population to recover to 90\% of its initial biomass after removals
+ceased. Here, we show that using one set of length-weight parameters
+versus another for a given length can result in more than a threefold
+under- or overestimation of total weight. These spatially-driven
+differences become especially important when allocating resources for
+lionfish removal programs, incentivizing lionfish fisheries as a source
+of alternative livelihoods, or estimating ecosystem impacts. Research
 efforts focused on invasive lionfish populations need to use parameters
@@
 
-The authors would like to thank thank Nils Van Der Haar and Michael
-Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided
-help to collect samples.
+The thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as
+well as Guillermo Lotz-Cador who provided help to collect samples. We
+are greateful for comments raised by the editor and two anonimous
+reviewers, which significantly increased the quality of this work.
 

### 2019-01-30 docs/reviews.Rmd
Added all comments from reviewers, must proof read and send to Sean

@@
 ---
-title: "Reviews"
+title: "Revision of MS #2018:11:32569:0:0:REVIEW"
 output: pdf_document
@@
 
-# Editor (Joseph Pawlik)
+Dear Dr. Pawlik
 
-Dear Juan Carlos,
+Enclosed please find our revised manuscript “Spatial variation in allometric growth of invasive lionfish has management implications”(#2018:11:32569:0:0:REVIEW).
 
-Thank you for your submission to PeerJ.
+We appreciate the professional way in which our manuscript has been handled.
+Here we address the issues, suggestions, and comments raised by you and the reviewers.
+We include the original comment in plain text, and our responses in itallics.
 
-It is my opinion as the Academic Editor for your article - Spatial variation in allometric growth of invasive lionfish has management implications - that it requires a number of Major Revisions.
+We believe that we have fully addressed questions and incorporated all comments. The quality of our manuscript has significantly improved thanks to the feedback from everyone.
 
-My suggested changes and reviewer comments are shown below and on your article 'Overview' screen.
+Our revised submission includes an updated manuscript and a marked-up version highlighting the changes.
 
-If you address these changes and resubmit, there's a good chance your article will be accepted (although this isn't guaranteed).
+Best regards,
+
+\vskip 1in
+
+Juan Carlos Villaseñor-Derbez
+
+Bren School of Environmental Science and Management
+
+University of California Santa Barbara
+
+jvillasenor@bren.ucsb.edu
+
+---
+
+# Editor
 
 Both reviewers noted a need to consider different or additional analyses and to improve the writing of this contribution.
-Along with your revised ms., please include the text of both reviews in you point-by-point responses to the reviewers' comments.
 
-Although not a hard deadline, we expect you to submit your revision within the next 55 days (received Dec 18).
+*As suggested by Rev2, we have logit-transformed our ratios and now evaluate them using an ANCOVA with study and total length as sources of variation.*
 
-With kind regards,
-
-Joseph Pawlik
-
-Academic Editor, PeerJ
+\clearpage
 
@@
 
+*We have changed the word from "major" to "substantial" in L19 and L142 and "fundamental" in L175 (now L183).*
+
 ### Introduction:
 
-- Line (L) 23: Capitalized “western” as was written in the Abstract and insert Ocean after “Atlantic”. As it reads now it sounds like the Atlantic Sea.
+Line (L) 23: Capitalized “western” as was written in the Abstract and insert Ocean after “Atlantic”. As it reads now it sounds like the Atlantic Sea.
 
-- L24: replace “liberation” with “release”.
+*"Western" is now capitalized.*
 
-- L 37: Albins and Hixon (2008) did their research in the Bahamas not Florida. Please correct.
+L24: replace “liberation” with “release”.
 
-- L47: Replace impacts with “negative effects”.
+*"liberation" has been replaced with "release"*
 
-- L61: replace “know” with “known”.
+L 37: Albins and Hixon (2008) did their research in the Bahamas not Florida. Please correct.
 
-- Fig 1.
+*The text now states the research was performed in the Bahamas.*
+
+L47: Replace impacts with “negative effects”.
+
+*"impacts" has been replaced with "negative effects" in L47, now L48*
+
+L61: replace “know” with “known”.
+
+*This has been fixed, now in L62.*
+
+Fig 1.
 To stay consistent throughout the manuscript please refer to the general region of the Atlantic ocean the same way.
@@
 
+*Figure 1 has been updated to show the appropriate label. Likewise we have standardized all references to this region as "Western Atlantic".*
+
 ### Methods:
 
-- L 82: The Bahamas are actually part of the Western Atlantic Ocean, not the Caribbean, please update your sample sizes.
+L 82: The Bahamas are actually part of the Western Atlantic Ocean, not the Caribbean, please update your sample sizes.
 
-- L 115: You changed how you refer to grams, here you use (gr) where as you used (g) before (see lines 100, 113). For all references to grams, both in the text and figures, please use (g).
+*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L78-79) and Table 2 (now Table 1) reflect these changes.*
 
-- L 121: It is not clear to me what the TL (34,310) means. Can you re-write or clarify what is meant by this?
+L 115: You changed how you refer to grams, here you use (gr) where as you used (g) before (see lines 100, 113). For all references to grams, both in the text and figures, please use (g).
 
-- L125: Will you add the github URL so the readers can find the data and code. It was not clear where the raw data would be shared either.
+*We have modified all instances and use "g" to refer to grams throughout the text.*
+
+L 121: It is not clear to me what the TL (34,310) means. Can you re-write or clarify what is meant by this?
+
+*We have modified this so it reads "with T L ranging from 34 mm to 310 mm" in what is now L120.*
+
+L125: Will you add the github URL so the readers can find the data and code. It was not clear where the raw data would be shared either.
+
+*We have included the url in the main text, but the decission to leave it there depends on the editorial formatting.
+However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the url to be incuded.*
 
@@
 
-- L 134-135: Did you use all of the “different pairs of parameters” from all of the studies individually?
+L 134-135: Did you use all of the “different pairs of parameters” from all of the studies individually?
 Do I understand the right?
@@
 
-- L 134-135: It is not clear what you mean by the lowest and highest weight estimates.
+*That is correct. We have modified the text to that it reads "each of the different pairs of parameters".*
+
+L 134-135: It is not clear what you mean by the lowest and highest weight estimates.
 For what size did you estimate these?
@@
 
+*Here we report the mean $\pm$ standard deviation of the estimated weights for the 109 organisms from the central Mexican Caribbean. We have modified the text to clearify our point.*
+
 - Fig. 3. Why are there two solid light green lines for the Sabido-Itza et al. 2016b? IN the legend for sex make sure that there are two dashed lines for female not just one short dashed line.
+
+*abido-Itza et al.
+2016b report parameters from two locations in their study.
+We have included that information in the figure caption ("There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters").
+The legend for Sex now shows distinct linetypes for Female and Males.*
 
@@
 
+*The figure caption now includes the following sentence: For Sabido-Itza et al, 2016b, BC and PNAX make reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites for which they report parameters.*
+
 ### Discussion:
 
-- L 152: The phrase “variation is related to space” does not really say much. What do you mean by related to space? Do you mean that the is spatial heterogeneity in the parameters?
+L 152: The phrase “variation is related to space” does not really say much. What do you mean by related to space? Do you mean that the is spatial heterogeneity in the parameters?
 
-- L 152: I am not sure what word you mean to use when you said: “we shot that”. Please choose a different word.
+*Yes, we refer to the spatial heterogeneity. We have modified the text so it reads "...is spatially heterogeneous and relevant for management of the invasion."*
+
+L 152: I am not sure what word you mean to use when you said: “we shot that”. Please choose a different word.
+
+*This was meant to say "We show that", and has now been corrected.*
+
+\clearpage
 
@@
 
-- L 82-92: The authors do a good job indicating many of the differences among the studies, I wonder about the time of year, which might have a large effect on lionfish growth.
+L 82-92: The authors do a good job indicating many of the differences among the studies, I wonder about the time of year, which might have a large effect on lionfish growth.
 One would expect both temperature and food availability to change.
@@
 
-- L 92-94: Why include the Fogg et al.
+*Other studies do not report the time of the year when these were collected.
+However, we recognize this is an important factor influencing length-weight relationships.
+We have mentioned that our parameters for the Central Mexican Caribbean are from organisms collected during the Summer (L94), and have devoted a paragraph in the discussion (L175) to highlight the importance of collection methods and timing when estimating length-weight relationships.*
+
+L 92-94: Why include the Fogg et al.
 (2013) data when you already know that it is likely to underestimate the weight due to the use of spineless weight.
@@
 
+*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and data from Fogg et al.
+(2013) produced some of the largest estimates.
+After a careful evaulation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders.
+The corresponding modifications have been made in the text.
+Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*
+
 ## Validity of the findings
 
-- L 107-108: There appear to be quite a few differences in the sampling and processing methods among all of the studies (lines 82-92).
+L 107-108: There appear to be quite a few differences in the sampling and processing methods among all of the studies (lines 82-92).
 Which the authors rightly discuss and support the conclusion that using local in situ, not ex situ parameters are critical to use.
@@
 
-- L175: Remove the word major from the main conclusion. Use either key, central, or fundamental. Major seems to be too strong and subjective of a word.
+*As stated above, we have expanded on the role of these different sampling and processing methods and devoted a paragraph in the duscission (L175).
+We must clarify, however, that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2).
+The fact that similar comments were raised by Rev2 suggests that the text needed further clarification from our side.
+The objective of our study is not to describe the biological differences in length-weight relationshisp, but to estimate the effect that using ex situ parameter has and determine if this results in large errors.*
 
-## Comments for the Author
+*We agree, however, that to estimate the "location effect" of the length-weight relationship, these should be modeled as a random effect.
+The GLMM would not only identify if differences exis, but also tell us the magnitude of these differences.
+This is a common approach in population biology and would in fact identify the random effect of the location in shaping the length-weight relationship.
+However, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data.
+We believe that after modifying the text to clearly state our objectives and including a discussion paragraph about this, we have addressed this concern.*
 
-Overall this study is a nice review of the existing data on allometric growth of lionfish.
-I like using new data as a case study to show local and regional differences and highlights the need to collect data at the local level to understand how this invasion manifest across the invaded region.
-I am interested to see how using a different statistical test might be able to shed some light on what the actual variation is among sights and using a mixed-model method should help you estimate this.
+L175: Remove the word major from the main conclusion. Use either key, central, or fundamental. Major seems to be too strong and subjective of a word.
+
+*We now use the word "fundamental".*
 
@@
 
-1.
 The authors don’t compare the weight-length relationships statistically; instead they compare mean ratios of predicted to observed weight when the estimated parameters from each different study are applied to the range of body lengths they collected in their central Mexican regional study.
@@
 4) that shows these ratios is illustrative, but this isn’t the best approach for several reasons.
-First, ratio data isn’t distributed normally, and has unqiue behaviors near the tails of the distribution.
-It should always be transformed, preferably using a logit transformation, prior to analysis.
+
+*We agree with the comments raised above and answer the two main points here.*
+
+First, ratio data isn’t distributed normally, and has unqiue behaviors near the tails of the distribution. It should always be transformed, preferably using a logit transformation, prior to analysis.
+
+*Our analyses of ratios now uses logit-transformed ratios.
+Additionally, and in recognition of the second point, we now use an ANCOVA with site and total length as sources of variation.
+Our results remain the same: using ex-situ parameters produces significantly different weight estimates.
+In fact, our post hoc test identifies even more groupings, suggesting that our previous attempt underestimated the differences.*
+
 Second, the parameter estimates from other studies are being applied to lengths of fish outside of the range of lengths that were used to generate the parameters.
@@
 
-2.
+*The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters.
+We have included a paragraph in the discussion that touches on this (L 185).*
+
+*As for the use of ANCOVA, this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates.
+As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations.
+However, we do not have the raw thata from other studies and applying this to the predicted estimates would not help us answer this question.
+In a sense, we would be asking if the lines in Fig 3 (whith no variation around them) have significantly different slopes and intercepts.
+As mentioned in the response to R1, we have included a discussion paragraph (L175) highlighting this.*
+
 The second major improvement would be inclusion in Table 2 of relevant information that would most likely have contributed to any differences in the weight-length relationships among the regions.
 Most importantly, this Table should include the range of total lengths that each study included, sex (which the authors already include), the depth at which most fish were captured (if reported in the original study), and the range of months (or seasons) during which fish were captured.
+
+*We have included all the information we collected from other studies in a supplementary table (Supplementary Table 2), an extention of Table 2, where other relevant variables are mentioned.
+Table 2 is now Table 1 after removing the regression table.*
+
 The size range is likely a major factor in driving differences, since most of the differences are observed at the largest total lengths, where data is likely sparse for many studies.
 Importantly, the authors should include a plot of the log-transformed data (reflecting the ANCOVA), with the plotted lines for each study only extending across the range of total lengths included in that study.
+
+*We have included the log-log version of Figure 3 in the appendices as Supplementary Figure 1. We reference such figure in the caption to Figure 3.*
+
 Figure 3, showing the untransformed data, should be amended so that each fitted curve extends across the range of total lengths specific to that study.
+
+*Figure 3 has been modified to show curves extending across the range of TLs specified by each study. The caption for this figure has also been modified to reflect this change.*
+
 Fish occupying shallow versus deep habitats could demonstrate differences in growth and condition.
@@
 
-3.
 The recommendation for major improvement is in the Discussion, related to the interpretation of their findings.
@@
 Do the patterns of variation in weightlength relationships for invasive lionfish align with the genetic results that have been published?
-Are they aligned spatially…..do populations that are closer geographically have more similar growth relationships?
+Are they aligned spatially...
+do populations that are closer geographically have more similar growth relationships?
 Are there potential effects of depth/season?
@@
 A paragraph or two of Discussion on plausible explanations for the patterns they observed would be a valuable addition.
+
+*As stated above, these were also raised by Rev1.
+We believe that our modifications to the discussion now explicitly mention these issues.
+And while we can not test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*
 
@@
 
+*We have modified the abstract to include both suggestions.*
+
 2. In the Methods section, the authors should refer to Tables and Figures in the order they are mentioned in the text. In the first sentence, they should refer to Fig. 1, not Fig. 3.
+
+*The first sentence now correctly references Figure 1, not Figure 3.*
 
@@
 
+*We have corrected this and now refer to four and six studies. These are now in L83 and L85.*
+
 4.
 Methods lines 98-100: the authors refer to reduced gear selectivity of hand nets; it’s not clear how substantial this is, but is more reason to include details about sampling methods, size ranges included, depth, and month/season in the table that details the previous studies.
+
+*We believe that gear selectivity is effectively eliminated because all observed organisms were collected.
+When pole spears are used, it is difficult to sample organisms that are smaller than 50 mm.
+This might explain why most of the studies show higher minimum lengths.
+We believe that the Supplementary Table 2 now addresses this and makes all the reviewed information available to future readers.*
 
@@
 
+*We have modified the text and now only include Eq 1.*
+
 6.
@@
 
+*We agree, and have now removed Table 1.*
+
 7.
@@
 Reporting the range in mean ratios would be sufficient along with an illustrative figure.
+
+*That is correct, the 0.80 and 1.76 values make refrence to the mean ratios.
+We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51.
+We believe the new text now justifies including these extremes.*
 
@@
 
+*We have removed parameter c from Table 2 (Now Table 1) and modified the header so it has $R^2$.*
+
 9. Figure 3 caption: Why do the authors only show the relationship for 12 studies instead of all 18
 that are included in Figure 4?
+
+*Figure 3 shows a total of 18 lines. This is because from the 12 reviewed papers, a total of 17 relationships were identified. The additional relationship is the one estimated in this study.*

### 2019-01-30 docs/supplementary/S1Figure.Rmd
Added all comments from reviewers, must proof read and send to Sean

---
title: Spatial variation in allometric growth of invasive lionfish has management implications
subtitle: "Supplementary Figure 1"
author: "Villaseñor-Derbez & Fitzgerald"
output:
  bookdown::pdf_document2:
    toc: no
fontsize: 12pt
header-includes:
   - \usepackage{float}
   - \floatplacement{figure}{H}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 5.5)

options(knitr.table.format = "latex")

windowsFonts(Times=windowsFont("TT Times New Roman"))
```

```{r load packages}
suppressPackageStartupMessages({
  library(stargazer)
  library(sandwich)
  library(lmtest)
  library(broom)
  library(knitr)
  library(cowplot)
  library(tidyverse)
})
```

```{r load data}
fish <- read_csv(here::here("data", "lionfish_data.csv"), col_types = cols()) %>%
  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
  summarize(Length = 10*mean(TotalLength_cm),
            Weight = mean(TotalWeigth_gr),
            Stomach = mean(StomachLength_cm)) %>% 
  ungroup()

review <- read.csv(here::here("data", "biometric_review.csv"), 
                  stringsAsFactors = F,
                  strip.white = T,
                  blank.lines.skip = T) %>% 
  mutate(c = log10(a),
         Gender2 = case_when(Gender == "Male" ~ "M",
                             Gender == "Female" ~ "F",
                             TRUE ~"B"),
         tl_min = ifelse(is.na(tl_min), 34, tl_min),
         tl_max = ifelse(is.na(tl_max), 310, tl_max))
```

```{r}
model <- lm(log10(Weight) ~ log10(Length), data = fish)

This <- data.frame(Length = c(34:310)) %>% 
  mutate(Weight = 10^(coefficients(model)[1] + coefficients(model)[2]*log10(Length)))

fig_all_allo <- review %>% 
  filter(!Study == "This study") %>%
  mutate(Length = list(seq(1, 400))) %>% 
  unnest() %>% 
  filter(Length > tl_min & Length < tl_max) %>% 
  mutate(Weight = a*(Length^b)) %>%
  group_by(Length) %>% 
  mutate(min = min(Weight),
         max = max(Weight)) %>% 
  ungroup() %>% 
  ggplot(aes(x = Length)) +
  geom_line(aes(y = Weight, color = Study, linetype = Gender, group = Study_id), size = 1) +
  geom_line(data = This, aes(x = Length, y = Weight),
            size = 1.2, color = "black", linetype = "dashed") +
  labs(x = "Total length (mm)", y = "Total Weight (g)") +
  theme_cowplot() +
  theme(text = element_text(family = "Times"),
        legend.justification = c(0,1),
        legend.position = c(0.01, 1.05),
        legend.background = element_rect(fill = "transparent"),
        legend.box = "horizontal",
        legend.text = element_text(size = 9),
        legend.title = element_text(size = 10)) +
  guides(color = guide_legend(order = 1),
         linetype = guide_legend(order = 0, ncol = 2, override.aes = list(size = 0.5)),
         size = "none") +
  scale_color_brewer(palette = "Paired", direction = -1) +
  scale_linetype_manual(values=c("solid", "dashed", "dotted"), name = "Sex") +
  scale_size_manual(values = c(1, 1.5)) +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10")
```

```{r fit2, fig.width = 8, fig.height = 4.5, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study. The curves are shown for the range of lengths reported in each study (See Supplementary Table 2); when ranges were not present, we use the ones found in this study (34mm - 310 mm). Colors indicate studies from which the parameters were extracted. Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively. The dashed black line represents the relationship estimated in this study. There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters. A linear-linear version of this figure is presented in Figure 3 of the main text."}
fig_all_allo
```

### 2019-01-30 docs/supplementary/S1Table.Rmd
Added all comments from reviewers, must proof read and send to Sean

@@
 author: "Villaseñor-Derbez & Fitzgerald"
-output: bookdown::pdf_document2
+output:
+  bookdown::pdf_document2:
+    toc: no
 fontsize: 12pt

### 2019-01-30 docs/supplementary/S2Table.Rmd
Added all comments from reviewers, must proof read and send to Sean

@@
 ---
-title: "Supplementary Table S2"
-author: "Juan Carlos Villaseñor-Derbez"
-output: pdf_document
+title: Spatial variation in allometric growth of invasive lionfish has management implications
+subtitle: "Supplementary Table 2"
+author: "Villaseñor-Derbez & Fitzgerald"
+output:
+  bookdown::pdf_document2:
+    toc: no
+    keep_tex: yes
+fontsize: 12pt
 ---
 
-Regression table for the linear model fit between log10-transformed Total Weight (dependent variable) and Total Length (independent variable).
-Numbers in parentheses next to coefficient estimates indicate heteroskedastic-robust standard errors.
+Extension of data from Table 1 in the main text. This table includes all the variables collected in each study.
 
@@
 suppressPackageStartupMessages({
-  # library(RColorBrewer)
-  # library(colorRamps)
   library(stargazer)
@@
   library(broom)
+  library(knitr)
   library(tidyverse)
@@
 
-```{r}
-fish <- read_csv("./lionfish_data.csv", col_types = cols()) %>% 
-  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
-  summarize(Length = 10*mean(TotalLength_cm),
-            Weight = mean(TotalWeigth_gr),
-            Stomach = mean(StomachLength_cm)) %>% 
-  ungroup()
+```{r load data}
+review <- read.csv(here::here("data", "biometric_review.csv"), 
+                  stringsAsFactors = F,
+                  strip.white = T,
+                  blank.lines.skip = T) %>% 
+  mutate(c = log10(a),
+         Gender2 = case_when(Gender == "Male" ~ "M",
+                             Gender == "Female" ~ "F",
+                             TRUE ~"B"))
 ```
@@
 ```{r}
-model <- lm(log10(Weight) ~ log10(Length), data = fish)
-
-TidyModel <- model%>%
-  lmtest::coeftest(vcov = sandwich::vcovHC(., type = "HC1")) %>%
-  broom::tidy()
-
-robust_se <- TidyModel$std.error %>%
-  set_names(TidyModel$term)
-
-wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))
-
-f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))
-
-a <- coefficients(model)[[1]]
-b <- coefficients(model)[[2]]
+review %>% 
+  filter(!Study == "Fishbase") %>% 
+  arrange(desc(Region)) %>% 
+  mutate(r2 = ifelse(is.na(r2), "-", r2),
+         N = ifelse(is.na(N), "-", N),
+         a = formatC((a*1e5), digits = 2),
+         tl_range = paste(tl_min, tl_max, sep = " - "),
+         tl_range = ifelse(is.na(tl_min), "-", tl_range),
+         d_range = paste(minD, maxD, sep = " - "),
+         d_range = ifelse(is.na(minD), "-", d_range)) %>% 
+  select(Region, Gender2, N, tl_range, a, b, r2, d_range, Years, Spear, Study) %>% 
+  knitr::kable(row.names = F,
+               digits =  c(0, 0, 0, 0, 2, 2, 2, 0, 0, 0, 0),
+               booktabs = T,
+               col.names = c("Region",
+                             "Sex",
+                             "n",
+                             "TL range (mm)",
+                             "a",
+                             "b",
+                             "$R^2$",
+                             "Depth range (m)",
+                             "Years",
+                             "Spear",
+                             "Study"),
+               caption = "Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter, b = exponent.
+Total Lenth ranges for Barbour et al (2011) and Sandel et al (2015) were estimated from figures since they did not explicitly report these parameters.
+An asterisk (*) in the Spear column indicates that at least some samples were obtained with pole spears.",
+               escape = T) %>% 
+  kableExtra::kable_styling(font_size = 10) %>% 
+  kableExtra::landscape()
 ```
-
-```{r, results = "asis"}
-ci_c <- c("95\\% CI for c", paste0("(", formatC(a-(1.96*robust_se[[1]]), digits = 3, format = "f"),"-", formatC(a+(1.96*robust_se[[1]]), digits = 3, format = "f"),")"))
-
-ci_b <- c("95\\% CI for b", paste0("(", formatC(b-(1.96*robust_se[[2]]), digits = 3, format = "f"),"-", formatC(b+(1.96*robust_se[[2]]), digits = 3, format = "f"),")"))
-
-stargazer(model,
-          header = F,
-          se = list(robust_se),
-          type = "latex",
-          t.auto = T,
-          p.auto = T,
-          intercept.bottom = F,
-          single.row = T,
-          report = "vcs*",
-          omit.stat = c("f"),
-          add.lines = list(ci_c, ci_b, f_string),
-          covariate.labels = c("c", "b"),
-          dep.var.labels = "log10(TW)")
-```

### 2019-01-30 docs/supplementary/S2Table.tex
Added all comments from reviewers, must proof read and send to Sean

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Spatial variation in allometric growth of invasive lionfish has management implications},
            pdfauthor={Villaseñor-Derbez \& Fitzgerald},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{Spatial variation in allometric growth of invasive lionfish has management implications}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Supplementary Table 2}
  \author{Villaseñor-Derbez \& Fitzgerald}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
    \date{}
    \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\begin{document}
\maketitle

Extension of data from Table 1 in the main text. This table includes all the variables collected in each study.

\begin{landscape}\begin{table}[t]

\caption{\label{tab:unnamed-chunk-1}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter, b = exponent. Total Lenth ranges for Barbour et al (2011) and Sandel et al (2015) were estimated from figures since they did not explicitly report these parameters. An asterisk (*) in the Spear column indicates that at least some samples were obtained with pole spears.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}{lllllrlllll}
\toprule
Region & Sex & n & TL range (mm) & a & b & $R^2$ & Depth range (m) & Years & Spear & Study\\
\midrule
Western Atlantic & B & 774 & 75 - 475 & 2.9 & 2.89 & - & 27 - 45 & 2004 - 2009 & Yes* & Barbour et al., 2011\\
Western Atlantic & B & - & - & 0.25 & 3.29 & - & - & NA & NA & Darling et al., 2011\\
GoM & B & 934 & 67 - 377 & 0.21 & 3.34 & 0.98 & - & 2013 - 2014 & Yes & Dahl \& Patterson, 2014\\
GoM & B & 472 & 98 - 358 & 0.29 & 3.30 & 0.95 & 5 - 20 & 2011 - 2013 & Yes & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 152 - 345 & 0.12 & 3.47 & 0.95 & 5 - 20 & 2011 - 2013 & Yes & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & M & 59 & 151 - 325 & 0.42 & 3.23 & 0.95 & 5 - 20 & 2011 - 2013 & Yes & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 80 - 385 & 0.14 & 3.43 & 0.99 & - & 2012 & Yes* & Fogg et al., 2013\\
GoM & M & 119 & 126 - 385 & 0.27 & 3.31 & 0.97 & - & 2012 & Yes* & Fogg et al., 2013\\
GoM & F & 115 & 157 - 337 & 0.68 & 3.14 & 0.94 & - & 2012 & Yes* & Fogg et al., 2013\\
Caribbean & B & 458 & 60 - 380 & 3.6 & 2.81 & - & - & 2011 & Yes* & Sandel et al., 2015\\
Caribbean & B & 419 & 93 - 410 & 2.8 & 2.85 & 0.8715 & 18.3 - 18.3 & 2012 - 2014 & Yes & Chin et al., 2016\\
Caribbean & B & 1450 & - & 2.3 & 2.89 & 0.9216 & - & - & - & de Leon et al., 2013\\
Caribbean & B & 1887 & 27 - 391 & 0.3 & 3.24 & 0.97 & 15 - 30 & 2011 & Yes* & Edwards et al., 2014\\
Caribbean & B & 2143 & 25 - 375 & 0.52 & 3.18 & 0.9907 & 0.5 - 57 & 2009-2012 & Yes* & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 57.09 - 349 & 0.8 & 3.11 & 0.958 & 1 - 30 & 2010 - 2011 & Yes* & Toledo-Hernández et al., 2014\\
Caribbean & B & 449 & 100 - 395 & 0.23 & 3.25 & 0.97 & - & 2012-2013 & Yes & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 60 - 380 & 0.32 & 3.19 & 0.98 & - & 2012-2013 & Yes & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 34 - 310 & 0.32 & 3.23 & 0.9766 & 5.7 - 38.1 & 2010 & No & This study\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

\end{document}

### 2019-01-30 docs/Manuscript.Rmd
Proof-read and added the LaTexDiff version of the marked up MS

@@
 Sedentary species like lionfish often exhibit high levels of spatial variation in life history characteristics.
-We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found significant regional differences in allometric growth parameters.
+We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found regional differences that led to significant under- and overestimation of weight estimates.
 The spatial pattern we observed is consistent with findings from other studies focusing on genetics or length-at-age.
@@
 These differences may be increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
-However, the extent to which using *ex situ* parameters to estimate total weight from length observations remains unexplored.
+However, the magnitude of the error caused by using *ex situ* parameters to estimate total weight from length observations remains unexplored.
 
@@
 We reviewed 12 published studies and obtained 17 length-weight relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7), and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}).
-We collected information on sampling methods, sex differentiation, location, and depth ranges from each study when available.
+We collected information on sex differentiation, location, length and depth ranges and sampling methods from each study when available.
 Only two studies reported parameters for each gender \citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were included in a study if gender was unspecified.
-Reviewed studies presented information for organisms obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
+Reviewed studies presented information for organisms ranging between `r min(review$tl_min, na.rm = T)` mm and `r max(review$tl_max, na.rm = T)` mm in Total Length ($TL$), and that were obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
 Four studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}, and two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
@@
 Other studies incorrectly reported parameters as mm-to-g conversions when they were in fact cm-to-g conversions.
-We standardized each study by converting coefficients and report all parameters as TL(mm) to TW (g) conversions.
+We standardized each study by converting coefficients and report all parameters as TL (mm) to TW (g) conversions.
 Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and summarized in Table \ref{tab:all_params}.
@@
 We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here.
-Recall that the objective of this study is not to describe population-level variations, but rather to estimate how the use of *ex situ* parameters influences weight estimates.
+Recall that the objective of this study is not to describe variations between populations, but rather to estimate how the use of *ex situ* parameters influences weight estimates.
 We used the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
 We estimated $TW$ from the $TL$ observations we collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 mm to 310 mm) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios were tested with an analysis of covariance (ANCOVA) using study and $TL$ as covariates.
+Difference in mean weight ratios were tested with an analysis of covariance (ANCOVA), where the sources of variation were the study and $TL$.
 Ratios were logit-transformed prior to analysis, and a *post-hoc* Tukey's test was used to identify groups where mean ratios did not differ.
@@
 
-The length-weight relationship for organisms from the central Mexican Caribbean resulted in the coefficient values $a = `r 10^c`$, $b = `r b`$ and $c = `r c`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
-The allometric factor ($b$) was significantly different from $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) indicating that lionfish present allometric growth.
+The length-weight relationship for organisms from the central Mexican Caribbean resulted in coefficient values of $a = `r 10^c`$ and $b = `r b`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
+The allometric factor ($b$) was significantly different from $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) corroborating that lionfish present allometric growth.
 The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
@@
 
-There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F(df = 17; 1944) = 61.55; p < 0.001$).
+There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F(df = 17; 1943) = 24.96; p < 0.001$).
 The lowest weight estimates for the observed lengths resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{sabidoitz_2016}.
@@
 To put this in context, true observed weights have a mean of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
-Weigths predicted from these extreme parameters correspond to mean $\pm$ SD predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
-At its extremes, other parameters resulted in under- and overestimations in the order of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` to `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` of the actual observed weight, indicating that *ex situ* parameters can result in substantial weight under- and overestimation.
+Weights predicted from these extreme parameters correspond to mean $\pm$ SD predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
+The largest under- and overestimations resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` of the actual observed weight, indicating that *ex situ* parameters can result in substantial weight under- and overestimation.
 
@@
 The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
+This suggest that the smallest errors are observed when using parameters other locations in the Caribbean.
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
@@
 
-```{r fit2, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}log-log transformation of the length-weight relationships (n = 18) for 12 studies and this study.
-The curves are shown for the range of lengths reported in each study (See Supplementary Table 2); when ranges were not present, we use the ones found in this study (34mm - 310 mm).
+```{r fit2, fig.height = 3.8, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
+The curves are shown for the range of lengths reported in each study (See Supplementary Table 2); when ranges were not present, we use the ones found in this study (34 mm - 310 mm).
 Colors indicate studies from which the parameters were extracted.
-Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
+Dotted, dashed, and solid lines show models for males, females, and combined sexes, respectively.
 The dashed black line represents the relationship estimated in this study.
@@
 Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight can be overestimated by more than a three-fold, and highlights the need to use local information.
-Here we discuss the implications of our findings and highlight potential future research directions.
+Here we discuss the implications of our findings, possible shortcommings in our analyses, and highlight potential future research directions.
 
@@
 Groupings of predicted-to-observed weight ratios identified in our *post hoc* testing aligned with the spatial distribution of the examined studies, suggesting that these differences may be mediated by space.
-These regional allometric differences mirror similar patterns in age-at-length of lionfish across both their invaded and native regions \citep{pusack_2016}.
+These regional allometric differences mirror similar patterns in length-at-age of lionfish across both their invaded and native regions \citep{pusack_2016}.
 Variation may be driven by genetics or by organisms' exposure to distinct environmental conditions.
-For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that age-at-length differences may be driven by the environment.
+For example, \citet{betancurr_2011} used mitochondrial DNA to demonstrate the existence of two distinct population groups, identified as the “Caribbean group” and “Northern Group”, and \citet{fogg_2015} alternatively suggested that length-at-age differences may be driven by the environment.
 
 We might be inclined to attribute all variation to the spatial origin of these parameters.
-However, these were not only collected for different locations, but also using a range of different sampling methods and for different points in time (See Supplementary Table 2 for an extended version of Table 1).
+However, these were not only collected for different locations, but also using a range of different sampling methods and at different points in time (See Supplementary Table 2 for an extended version of Table 1).
 While we are not able to evaluate how these factors influence previous estimates (raw data from all studies would be needed), it is certain that the lack of locally-calculated parameters may induce significant bias when calculating weight from length observations.
 Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both.
-The magnitude of the bias and our lack of understanding of the source of variation hihglights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and link these to previously suggested environmental and genetic structures.
+The magnitude of the bias and our lack of understanding of the source of variation highlights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and link these to previously suggested environmental and genetic structures.
 Such an endeavor would provide insights into lionfish biology and better inform management.
 
-Applying parameters estimates to lengths that may be outside the range of lengths originally used to estimate the parameters may also induce variation lead to over- and underestimation.
-Our smallest observed length was for an organism 34 mm in TL.
-However, only two studies estimated parametrs with smaller organisms \citep{sabidoitza_2016,edwards_2014}.
-On the other hand, our largest organism had a TL of 310 mm, which is well within the range of all other studies (maximum observed lengths varied from 325 mm to 475 mm; See Supplementary Table 2).
-Due to the exponential nature of the allometric relationship, the error is higher when extrapolation is done for TLs that are larger than the maximum.
+Applying parameters estimates to lengths outside the range of lengths originally used to estimate the parameters may also induce error.
+Our smallest observed organism was 34 mm in $TL$, and only two studies estimated parametrs with smaller organisms \citep{sabidoitza_2016,edwards_2014}.
+On the other hand, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (maximum observed lengths varied from 325 mm to 475 mm; See Supplementary Table 2).
+Due to the power-function describing the allometric relationship, the error is higher when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
 This means that not only must managers use locally-informed data, but that these local data must also include the full range of lengths present in the region to reduce error caused by extrapolation.
@@
 Here, we show that using one set of length-weight parameters versus another for a given length can result in more than a threefold under- or overestimation of total weight.
-These spatially-driven differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts.
+These differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts.
 Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or at least use reasonable sets of different parameters that provide upper and lower bounds in their results.

### 2019-01-30 docs/Manuscript.tex
Proof-read and added the LaTexDiff version of the marked up MS

@@
 relationships for lionfish taken throughout their invasive range and
-found significant regional differences in allometric growth parameters.
-The spatial pattern we observed is consistent with findings from other
-studies focusing on genetics or length-at-age. We show that the use of
-\textit{ex situ} parameters can result in up to a threefold under- or
-overestimation of total weight, but using parameters from nearby regions
-reduces this error. These findings can have substantial implications for
-management in terms of predicting effects on local ecosystems,
-evaluating the effectiveness of removal programs, or estimating biomass
-available for harvest.
+found regional differences that led to significant under- and
+overestimation of weight estimates. The spatial pattern we observed is
+consistent with findings from other studies focusing on genetics or
+length-at-age. We show that the use of \textit{ex situ} parameters can
+result in up to a threefold under- or overestimation of total weight,
+but using parameters from nearby regions reduces this error. These
+findings can have substantial implications for management in terms of
+predicting effects on local ecosystems, evaluating the effectiveness of
+removal programs, or estimating biomass available for harvest.
 \end{abstract}
@@
 \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
-extent to which using \emph{ex situ} parameters to estimate total weight
-from length observations remains unexplored.
+magnitude of the error caused by using \emph{ex situ} parameters to
+estimate total weight from length observations remains unexplored.
 
@@
 and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}). We
-collected information on sampling methods, sex differentiation,
-location, and depth ranges from each study when available. Only two
+collected information on sex differentiation, location, length and depth
+ranges and sampling methods from each study when available. Only two
 studies reported parameters for each gender
@@
 included in a study if gender was unspecified. Reviewed studies
-presented information for organisms obtained at depths between 0.5 m and
-57 m. Four studies explicitly stated that their organisms were sampled
-with pole spears
+presented information for organisms ranging between 25 mm and 475 mm in
+Total Length (\(TL\)), and that were obtained at depths between 0.5 m
+and 57 m. Four studies explicitly stated that their organisms were
+sampled with pole spears
 \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six
@@
 conversions. We standardized each study by converting coefficients and
-report all parameters as TL(mm) to TW (g) conversions. Locations where
+report all parameters as TL (mm) to TW (g) conversions. Locations where
 allometric studies have been performed are shown in Figure \ref{fig:map}
@@
 calculated here. Recall that the objective of this study is not to
-describe population-level variations, but rather to estimate how the use
-of \emph{ex situ} parameters influences weight estimates. We used the
-central Mexican Caribbean as a case study of how the use of \emph{ex
+describe variations between populations, but rather to estimate how the
+use of \emph{ex situ} parameters influences weight estimates. We used
+the central Mexican Caribbean as a case study of how the use of \emph{ex
 situ} parameters influences the accuracy of weight estimates for
@@
 underestimation. Difference in mean weight ratios were tested with an
-analysis of covariance (ANCOVA) using study and \(TL\) as covariates.
-Ratios were logit-transformed prior to analysis, and a \emph{post-hoc}
-Tukey's test was used to identify groups where mean ratios did not
-differ. All analyses were performed in R version 3.5.2
+analysis of covariance (ANCOVA), where the sources of variation were the
+study and \(TL\). Ratios were logit-transformed prior to analysis, and a
+\emph{post-hoc} Tukey's test was used to identify groups where mean
+ratios did not differ. All analyses were performed in R version 3.5.2
 \citep{rcore_2018}. Raw data and code used in this work are available on
@@
 The length-weight relationship for organisms from the central Mexican
-Caribbean resulted in the coefficient values
-\(a = 3.2056297\times 10^{-6}\), \(b = 3.2347391\) and
-\(c = -5.4940866\) (\(R^2 = 0.977\), F(df = 1; 107) = 6928.67,
-\(p < 0.001\)). The allometric factor (\(b\)) was significantly
-different from \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicating that
-lionfish present allometric growth. The length-weight coefficients
-estimated in this study were within the range identified by studies in
-other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
-shows the relationship between TL and TW for this region.
+Caribbean resulted in coefficient values of
+\(a = 3.2056297\times 10^{-6}\) and \(b = 3.2347391\) (\(R^2 = 0.977\),
+F(df = 1; 107) = 6928.67, \(p < 0.001\)). The allometric factor (\(b\))
+was significantly different from \(b = 3\) (\(t(107) = 6.04; p<0.001\))
+corroborating that lionfish present allometric growth. The length-weight
+coefficients estimated in this study were within the range identified by
+studies in other regions (Table \ref{tab:all_params}). Figure
+\ref{fig:l-w-carib} shows the relationship between TL and TW for this
+region.
 
@@
 central Mexican Caribbean when using each of the different pairs of
-parameters (\(F(df = 17; 1944) = 61.55; p < 0.001\)). The lowest weight
+parameters (\(F(df = 17; 1943) = 24.96; p < 0.001\)). The lowest weight
 estimates for the observed lengths resulted from using the allometric
@@
 \(\pm\) 96.11 g \citep{barbour_2011}. To put this in context, true
-observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weigths predicted
+observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weights predicted
 from these extreme parameters correspond to mean \(\pm\) SD
 predicted-to-observed weights ratios of 0.80 \(\pm\) 0.19 and 1.76
-\(\pm\) 0.50 (mean \(\pm\) SD), respectively. At its extremes, other
-parameters resulted in under- and overestimations in the order of 0.36
-to 3.51 of the actual observed weight, indicating that \emph{ex situ}
-parameters can result in substantial weight under- and overestimation.
+\(\pm\) 0.50 (mean \(\pm\) SD), respectively. The largest under- and
+overestimations resulted in ratios of 0.36 and 3.51 of the actual
+observed weight, indicating that \emph{ex situ} parameters can result in
+substantial weight under- and overestimation.
 
@@
 \(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
-Predicted-to-observed weight ratios are presented in Figure
-\ref{fig:bio_ratio}.
+This suggest that the smallest errors are observed when using parameters
+other locations in the Caribbean. Predicted-to-observed weight ratios
+are presented in Figure \ref{fig:bio_ratio}.
 
@@
 \toprule
-Region & Sex & n & a & b & \$R\textasciicircum{}2\$ & Reference\\
+Region & Sex & n & a & b & $R^2$ & Reference\\
 \midrule
@@
 \includegraphics{Manuscript_files/figure-latex/fit2-1.pdf}
-\caption{\label{fig:all_allo}log-log transformation of the length-weight
-relationships (n = 18) for 12 studies and this study. The curves are
-shown for the range of lengths reported in each study (See Supplementary
-Table 2); when ranges were not present, we use the ones found in this
-study (34mm - 310 mm). Colors indicate studies from which the parameters
-were extracted. Dotted, dashed and solid lines show models for males,
-females, and combined sexes, respectively. The dashed black line
-represents the relationship estimated in this study. There are two solid
-green lines for Sabido-Itza et al, 2016b, one for each of the two sites
-for which they report parameters. A log-log version of this figure is
-presented in Figure S4.}
+\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
+studies and this study. The curves are shown for the range of lengths
+reported in each study (See Supplementary Table 2); when ranges were not
+present, we use the ones found in this study (34 mm - 310 mm). Colors
+indicate studies from which the parameters were extracted. Dotted,
+dashed, and solid lines show models for males, females, and combined
+sexes, respectively. The dashed black line represents the relationship
+estimated in this study. There are two solid green lines for Sabido-Itza
+et al, 2016b, one for each of the two sites for which they report
+parameters. A log-log version of this figure is presented in Figure S4.}
 \end{figure}
@@
 three-fold, and highlights the need to use local information. Here we
-discuss the implications of our findings and highlight potential future
-research directions.
+discuss the implications of our findings, possible shortcommings in our
+analyses, and highlight potential future research directions.
 
@@
 space. These regional allometric differences mirror similar patterns in
-age-at-length of lionfish across both their invaded and native regions
+length-at-age of lionfish across both their invaded and native regions
 \citep{pusack_2016}. Variation may be driven by genetics or by
@@
 ``Caribbean group'' and ``Northern Group'', and \citet{fogg_2015}
-alternatively suggested that age-at-length differences may be driven by
+alternatively suggested that length-at-age differences may be driven by
 the environment.
@@
 these parameters. However, these were not only collected for different
-locations, but also using a range of different sampling methods and for
+locations, but also using a range of different sampling methods and at
 different points in time (See Supplementary Table 2 for an extended
@@
 magnitude of the bias and our lack of understanding of the source of
-variation hihglights the need to simultaneously collect length-weight
+variation highlights the need to simultaneously collect length-weight
 information across the invaded range to test for spatially-induced
@@
 
-Applying parameters estimates to lengths that may be outside the range
-of lengths originally used to estimate the parameters may also induce
-variation lead to over- and underestimation. Our smallest observed
-length was for an organism 34 mm in TL. However, only two studies
+Applying parameters estimates to lengths outside the range of lengths
+originally used to estimate the parameters may also induce error. Our
+smallest observed organism was 34 mm in \(TL\), and only two studies
 estimated parametrs with smaller organisms
 \citep{sabidoitza_2016,edwards_2014}. On the other hand, our largest
-organism had a TL of 310 mm, which is well within the range of all other
-studies (maximum observed lengths varied from 325 mm to 475 mm; See
-Supplementary Table 2). Due to the exponential nature of the allometric
-relationship, the error is higher when extrapolation is done for TLs
-that are larger than the maximum. This means that not only must managers
-use locally-informed data, but that these local data must also include
-the full range of lengths present in the region to reduce error caused
-by extrapolation.
+organism had a \(TL\) of 310 mm, which is well within the range of all
+other studies (maximum observed lengths varied from 325 mm to 475 mm;
+See Supplementary Table 2). Due to the power-function describing the
+allometric relationship, the error is higher when extrapolation is done
+for lengths that are larger than the maximum length used to estimate the
+parameters. This means that not only must managers use locally-informed
+data, but that these local data must also include the full range of
+lengths present in the region to reduce error caused by extrapolation.
 
@@
 versus another for a given length can result in more than a threefold
-under- or overestimation of total weight. These spatially-driven
-differences become especially important when allocating resources for
-lionfish removal programs, incentivizing lionfish fisheries as a source
-of alternative livelihoods, or estimating ecosystem impacts. Research
-efforts focused on invasive lionfish populations need to use parameters
-calculated for their region to the extent possible, or at least use
-reasonable sets of different parameters that provide upper and lower
-bounds in their results.
+under- or overestimation of total weight. These differences become
+especially important when allocating resources for lionfish removal
+programs, incentivizing lionfish fisheries as a source of alternative
+livelihoods, or estimating ecosystem impacts. Research efforts focused
+on invasive lionfish populations need to use parameters calculated for
+their region to the extent possible, or at least use reasonable sets of
+different parameters that provide upper and lower bounds in their
+results.
 

### 2019-01-30 docs/reviews.Rmd
Proof-read and added the LaTexDiff version of the marked up MS

@@
 Here we address the issues, suggestions, and comments raised by you and the reviewers.
-We include the original comment in plain text, and our responses in itallics.
+We include the original comment in plain text, and our responses in italics.
 
@@
 ---
+
+\vskip 1in
 
@@
 
-*We have included the url in the main text, but the decission to leave it there depends on the editorial formatting.
-However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the url to be incuded.*
+*We have included the URL in the main text, but the decision to leave it there depends on the editorial formatting.
+However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*
 
@@
 
-*Here we report the mean $\pm$ standard deviation of the estimated weights for the 109 organisms from the central Mexican Caribbean. We have modified the text to clearify our point.*
+*Here we report the mean $\pm$ standard deviation of the estimated weights for the 109 organisms from the central Mexican Caribbean. We have modified the text to clarify our point.*
 
@@
 
-*abido-Itza et al.
+*Sabido-Itza et al.
 2016b report parameters from two locations in their study.
 We have included that information in the figure caption ("There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters").
-The legend for Sex now shows distinct linetypes for Female and Males.*
+The legend for Sex now shows distinct line types for Female and Males.*
 
@@
 (2013) produced some of the largest estimates.
-After a careful evaulation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders.
+After a careful evaluation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders.
 The corresponding modifications have been made in the text.
@@
 
-*As stated above, we have expanded on the role of these different sampling and processing methods and devoted a paragraph in the duscission (L175).
+*As stated above, we have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L175).
 We must clarify, however, that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2).
 The fact that similar comments were raised by Rev2 suggests that the text needed further clarification from our side.
-The objective of our study is not to describe the biological differences in length-weight relationshisp, but to estimate the effect that using ex situ parameter has and determine if this results in large errors.*
+The objective of our study is not to describe the biological differences in length-weight relationships, but to estimate the effect that using ex situ parameter has and determine if this results in large errors.*
 
 *We agree, however, that to estimate the "location effect" of the length-weight relationship, these should be modeled as a random effect.
-The GLMM would not only identify if differences exis, but also tell us the magnitude of these differences.
+The GLMM would not only identify if differences exist, but also tell us the magnitude of these differences.
 This is a common approach in population biology and would in fact identify the random effect of the location in shaping the length-weight relationship.
@@
 
-In this manuscript, the authors present an analysis of 17 previously published weight-length relationships for lionfish throughout the species invasive range, along with new data on the weightlength relationship for a population along the central Mexican coast.
+In this manuscript, the authors present an analysis of 17 previously published weight-length relationships for lionfish throughout the species invasive range, along with new data on the length-weight relationship for a population along the central Mexican coast.
 The authors report important differences in allometric scaling among studies and highlight the effects of applying mis-specified growth parameters to stocks lacking this information.
@@
 ANCOVA is the most powerful approach for comparing multiple linear relationships, as it specifically accounts for variation in the covariate (total length) among groups.
-The application of ANCOVA to the logtransformed weight-length relationships would identify if the beta (b) coefficient varied significantly among populations, and then which populations differed could be discerned using post-hoc tests.
+The application of ANCOVA to the log-transformed weight-length relationships would identify if the beta (b) coefficient varied significantly among populations, and then which populations differed could be discerned using post-hoc tests.
 
@@
 As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations.
-However, we do not have the raw thata from other studies and applying this to the predicted estimates would not help us answer this question.
-In a sense, we would be asking if the lines in Fig 3 (whith no variation around them) have significantly different slopes and intercepts.
+However, we do not have the raw data from other studies and applying this to the predicted estimates would not help us answer this question.
+In a sense, we would be asking if the lines in Fig 3 (with no variation around them) have significantly different slopes and intercepts.
 As mentioned in the response to R1, we have included a discussion paragraph (L175) highlighting this.*
@@
 
-*We have included all the information we collected from other studies in a supplementary table (Supplementary Table 2), an extention of Table 2, where other relevant variables are mentioned.
+*We have included all the information we collected from other studies in a supplementary table (Supplementary Table 2), an extension of Table 2, where other relevant variables are mentioned.
 Table 2 is now Table 1 after removing the regression table.*
@@
 
-*That is correct, the 0.80 and 1.76 values make refrence to the mean ratios.
+*That is correct, the 0.80 and 1.76 values make reference to the mean ratios.
 We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51.

### 2019-01-30 docs/supplementary/S1Figure.Rmd
Proof-read and added the LaTexDiff version of the marked up MS

@@
 
-```{r fit2, fig.width = 8, fig.height = 4.5, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Length-weight relationships (n = 18) for 12 studies and this study.
-The curves are shown for the range of lengths reported in each study (See Supplementary Table 2); when ranges were not present, we use the ones found in this study (34mm - 310 mm).
+```{r fit2, fig.width = 8, fig.height = 4.5, fig.pos = "H", fig.cap = "\\label{fig:all_allo}Log-log transformation of the length-weight relationships (n = 18) for 12 studies and this study.
+The curves are shown for the range of lengths reported in each study (See Supplementary Table 2); when ranges were not present, we use the ones found in this study (34 mm - 310 mm).
 Colors indicate studies from which the parameters were extracted.
-Dotted, dashed and solid lines show models for males, females, and combined sexes, respectively.
+Dotted, dashed, and solid lines show models for males, females, and combined sexes, respectively.
 The dashed black line represents the relationship estimated in this study.

### 2019-01-30 docs/Manuscript.Rmd
SF Just intro so far

@@
   Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean.
-Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth.
-Sedentary species like lionfish often exhibit high levels of spatial variation in life history characteristics.
-We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found regional differences that led to significant under- and overestimation of weight estimates.
-The spatial pattern we observed is consistent with findings from other studies focusing on genetics or length-at-age.
-We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight, but using parameters from nearby regions reduces this error.
-These findings can have substantial implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
+Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth, but sedentary species like lionfish often exhibit high levels of spatial variation in life history characteristics.
+We reviewed 17 published length-weight relationships for lionfish taken throughout their invasive range and found regional differences that led to significant under- and overestimation of weight estimates.
+The spatial pattern we observed is consistent with findings from other studies focused on genetics or length-at-age.
+We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight, but using parameters from nearby regions substantially reduces this error.
+These findings can have implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
 keywords:
@@
 A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate Western Atlantic.
-Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep{green_2012,rocha_2015}; but see \citet{hackerott_2017}.
-For example, field experiments by \citet{albins_2008} showed that lionfish establishment led to reduced recruitment of native fishes by nearly 80% over a five-week period in the Bahamas.
-\citet{green_2012} reported that prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs.
-However, their trophic impacts can be minimized if local lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.
+Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (Green et al., 2012; Rocha et al., 2015; but see Hackerott et al., 2017 for a counterexample).<!-- need to avoid having those parentheses close prematurely - don't think it's possible using the citation code -->  For example, field experiments showed that lionfish establishment in the Bahamas led to reduced recruitment of native fishes by nearly 80% over a five-week period \citet{albins_2008}, and prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs \citet{green_2012}.
+However, trophic impacts of lionfish can be minimized if their local biomass is controlled by culling \citep{ariasgonzalez_2011}.
 
 Governments and non-profit organizations have sought to reduce lionfish densities through removal programs and incentivizing its consumption \citep{chin_2016}.
-In some cases, these have shown to significantly reduce --but not quite eliminate-- lionfish abundances at local scales \citep{deleon_2013,sandel_2015}.
+In some cases, these have shown to significantly reduce -- but not quite eliminate -- lionfish abundances at local scales \citep{deleon_2013,sandel_2015}.
 Complete eradication of lionfish through fishing is unlikely because of their rapid recovery rates and ongoing recruitment to shallow-water areas from persistent populations in mesophotic ecosystems \citep{barbour_2011,andradibrown_2017}.
@@
 
-Outcomes of previous studies suggest lionfish are likely to exhibit spatial heterogeneity in the length-weight relationship, which we summarize in two main causes.
-First, culling programs are effective in reducing local adult populations largely because lionfish exhibit high levels of site fidelity and small home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
-It is known that fish with sedentary behavior are likely to exhibit high levels of spatial variation in important life history characteristics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
+Outcomes of previous studies suggest lionfish are likely to exhibit spatial heterogeneity in the length-weight relationship for two main reasons.
+First, fish with sedentary behavior such as lionfish often exhibit high levels of spatial variation in important life history characteristics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
+In fact, culling programs are effective in reducing local adult populations largely because lionfish have high levels of site fidelity and small home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
 Second, genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the Western Atlantic and the Caribbean \citep{betancurr_2011}.
-The large number of site-specific studies reporting the length-weight relationship of lionfish provide variable estimates.
-These differences may be increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
-However, the magnitude of the error caused by using *ex situ* parameters to estimate total weight from length observations remains unexplored.
+Site-specific studies that calculate the length-weight relationship of lionfish report variable estimates, and these differences may be increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
+However, the influence of using *ex situ* parameters when estimating the length-weight relationship remains unexplored.
 
-Here, we use previously published length-weight relationships for lionfish populations in North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica to quantify the magnitude of the error caused by using *ex situ* parameters to estimate lionfish weight from length observations.
-We also collected lionfish length and weight data in the central Mexican Caribbean and report the first length-weight relationship for this region.
+Here, our objective was to quantify the magnitude of error caused by using *ex situ* parameter values when estimating lionfish weight from length observations.
+In this study, we collected length and weight data for 109 lionfish in the central Mexican Caribbean and report the first length-weight relationship for this region.
+We then estimated lionfish weight in this area using previously published length-weight relationships for lionfish populations in North Carolina, the Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica.
+By comparing these weight estimates to the *in situ* length-weight observations collected in this study, we then showed that using *ex situ* parameter values can result in up to a threefold under- or overestimation of lionfish weight.
 
 <!-- \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016} -->
+
+<!-- What's the deal with all these citations?  Did you mean to put them back in at the end of the paragraph? -->
 

### 2019-01-30 docs/reviews.Rmd
SF Just intro so far

@@
 ---
-
+<!-- BE REALLY CAREFUL to go through this and make sure the lines actually match up with the lines in the new manuscript - double check every one --> 
 Dear Dr. Pawlik
@@
 
-*We have changed the word from "major" to "substantial" in L19 and L142 and "fundamental" in L175 (now L183).*
+*We have changed the word from "major" to "substantial" in L19 and L142 (now L139) and "fundamental" in L175 (now L193).*
 
@@
 *As stated above, these were also raised by Rev1.
-We believe that our modifications to the discussion now explicitly mention these issues.
+We believe that our modifications to the discussion in lines...
+now explicitly mention these issues.
 And while we can not test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*
+<!-- modification in which lines? -->
 

### 2019-01-31 docs/Manuscript.Rmd
Revisions are great, I have a decent amount of edits too.  Will email JC

@@
 Here, our objective was to quantify the magnitude of error caused by using *ex situ* parameter values when estimating lionfish weight from length observations.
-In this study, we collected length and weight data for 109 lionfish in the central Mexican Caribbean and report the first length-weight relationship for this region.
+In this study, we calculated and reported the first length-weight relationship for lionfish in the central Mexican Caribbean (n = 109).
 We then estimated lionfish weight in this area using previously published length-weight relationships for lionfish populations in North Carolina, the Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica.
-By comparing these weight estimates to the *in situ* length-weight observations collected in this study, we then showed that using *ex situ* parameter values can result in up to a threefold under- or overestimation of lionfish weight.
+By comparing these weight estimates to the *in situ* length-weight observations, we showed that using *ex situ* parameter values resulted in up to a threefold under- or overestimation of lionfish weight.
 
@@
 We reviewed 12 published studies and obtained 17 length-weight relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7), and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}).
-We collected information on sex differentiation, location, length and depth ranges and sampling methods from each study when available.
-Only two studies reported parameters for each gender \citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were included in a study if gender was unspecified.
-Reviewed studies presented information for organisms ranging between `r min(review$tl_min, na.rm = T)` mm and `r max(review$tl_max, na.rm = T)` mm in Total Length ($TL$), and that were obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
-Four studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}, and two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
+We collected information on sex differentiation, location, length and depth ranges, and sampling methods from each study when available.
+Only two studies reported parameters for each sex \citep{aguilarperera_2016,fogg_2013}, so we assumed data from both sexes were combined in a study if sex was unspecified.
+Reviewed studies presented information for organisms ranging from `r min(review$tl_min, na.rm = T)`-`r max(review$tl_max, na.rm = T)` mm in Total Length ($TL$) and were obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
+Four studies explicitly stated that their organisms were sampled with pole spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six studies mentioned that some of their organisms were obtained with pole spears (or other type of harpoon) but also hand-held nets or fish traps \citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}.
+Two studies did not specify how organisms were sampled \citep{darling_2011,deleon_2013}.
 
@@
 
+<!-- Shouldn't the figure go after it's introduced in the text? I'm not sure why it knitted above the METHODS header in the actual manuscript. -->
+
 ```{r map, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
@@
 
-We also used data from \citet{villaseorderbez_2014}, who collected organisms from 10 sampling sites along the central Mexican Caribbean coast in the Summer of 2010 (Supplementary Table 1).
+We also used data from 109 lionfish sampled by \citet{villaseorderbez_2014}, who used hand nets and numbered bottles to collect organisms from 10 sampling sites along the central Mexican Caribbean coast in the Summer of 2010 (Supplementary Table 1).
 Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
-All observed lionfish (n = 109) were collected using hand nets and numbered collection bottles.
 The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by avoiding gear selectivity.
@@
 
-The weight-at-length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function:
+The weight-at-length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function
 
@@
 TW = aTL^b
-\end{equation}
+\end{equation},
 
-Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
+where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
+We linearized the equation using $log_{10}$-transformation and estimated the coefficients using an Ordinary Least Squares Regression with a heteroskedastic-robust standard error correction \citep{zeileis_2004}.
+Organisms exhibit perfect isometric growth when $b = 3$, so we tested the $b$ coefficient against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$) **to determine...
+WHAT???
+whether the organism displayed isometric or allometric growth?
+What is the point of that?
+Not saying we shouldn't have it in there, but we should say why we're doing it.
+Ostensibly is it to be sure that the lionfish L-W relationship DOES significantlt differ from isometric growth?
+(even though we basically already know that from the other studies?)**.
+Coefficients were tested with a two-tailed Student's t-test, and the significance of the regression was corroborated with an F-test.
 
@@
 
-The above equation was linearized using $log_{10}$-transformation.
-The coefficients were estimated with an Ordinary Least Squares Regression, and heteroskedastic-robust standard error correction was applied \citep{zeileis_2004}.
-When $b = 3$, it is said that the organism exhibits a perfect isometric growth, so the $b$ coefficient was tested against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$).
-Coefficients were tested with a two-tailed Student's t, and the significance of the regression was corroborated with an F-test.
-
 Some of the reviewed studies inconsistently defined $a$ as either the ponderal index from Eq.
@@
 
+<!-- Shouldn't we move Table 1 up in the paper?
+Maybe at the end of methods or something?
+Seems really weird to have it all the way at the end, especially when mentioned so early on.
+I always thought you want to have things appear in the text in the same order they are written.
+-->
+
 We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here.
-Recall that the objective of this study is not to describe variations between populations, but rather to estimate how the use of *ex situ* parameters influences weight estimates.
-We used the central Mexican Caribbean as a case study of how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish.
-We estimated $TW$ from the $TL$ observations we collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 mm to 310 mm) using each of the 18 parameter pairs and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
+Recall that the objective of this study is not to describe variations between populations, but rather to estimate how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish, using the central Mexican Caribbean as a case study.
+Using each of the 18 parameter pairs, we estimated $TW$ from the $TL$ observations collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 mm to 310 mm) and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
 Difference in mean weight ratios were tested with an analysis of covariance (ANCOVA), where the sources of variation were the study and $TL$.
@@
 The allometric factor ($b$) was significantly different from $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) corroborating that lionfish present allometric growth.
-The length-weight coefficients estimated in this study were within the range identified by studies in other regions (Table \ref{tab:all_params}).
+The length-weight coefficients estimated here were within the range identified by studies from other regions (Table \ref{tab:all_params}).
 Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region.
+
+<!-- I think we should reduce the number of decimal points, maybe make it consistent with the figure? (4 decimal points?)  Up to you though.  Also good figure placement for Fig. 2 -->
 
@@
 
+<!-- Some notes on reporting F-statistic: 1) If you're going to do it the way you have it currently, make sure "df" is either always italicized.
+However, 2) the better way to report F-test results is to put the degrees of freedom as a subscript on F, then you don't have to write df and have extra parentheses that look bad - e.g.
+see https://www.yorku.ca/mack/RN-HowToReportAnFStatistic.html -->
+
 There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F(df = 17; 1943) = 24.96; p < 0.001$).
@@
 To put this in context, true observed weights have a mean of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
-Weights predicted from these extreme parameters correspond to mean $\pm$ SD predicted-to-observed weights ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
-The largest under- and overestimations resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` of the actual observed weight, indicating that *ex situ* parameters can result in substantial weight under- and overestimation.
+Weights predicted from these extreme parameters correspond to predicted-to-observed weight ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
+The largest under- and overestimations resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` of the actual observed weight, indicating that *ex situ* parameters can result in highly erroneous weight estimates.
+
+<!-- Question - do you think we should report standard error instead of standard deviation?
+Since we're interested in comparing the different estimates (not describing the spread of the data), standard error is probably better (plus it'll be a lot smaller so the differences will look more meaningful upon first glance).
+I think that's the way to go, but I'm a little wary to do so since the reviewers didn't flag it and I suppose it's possible they might not like the change...
+-->
 
 Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
-Weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}).
-The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
-This suggest that the smallest errors are observed when using parameters other locations in the Caribbean.
+Weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}) **GOTTA HAVE SOME STATS HERRE TO BACK THIS UP - DIDN'T TUKEY'S SHOW THAT WEIGHT RATIOS HERE WERE DIFFERENT??
+If p > 0.05 for Little Cayman/Bahamas/some GoM, wasn't p < 0.05 for every other site?
+If so, definitely say that.** The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
+This suggests that the smallest errors are observed when using parameters from other locations in the Caribbean.
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
+
+<!-- Unfortunately, I think we should make a change to Figures 3 and 4 (it won't take long).I think we should do something like put "WA", "C", or "GoM" next to each study depending on their location (Western Atlantic, Caribbean, Gulf of Mexico).
+We have to give some way to indicate what region each set of observations is from.
+I know it's in Table 1, but right now it's impossible for the reader to draw any conclusion that there's a pattern in that sites in the Caribbean were more similar to this study than sites in the Gulf or Western Atlantic.
+Alternatively, maybe we could just substitute superscripted numbers for writing out the reference citation?
+I.e.
+GoM^1 would be Aguilar, WA^2 would be Barbour...
+Then in figure 3 caption we say what footnote corresponds to what study and in Figure 4 just say numbers correspond to same references as figure 3 caption.
+Lmk if you see what I mean, happy to discuss more.
+-->
 
@@
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter (presented in $\\times 10^{-5}$), b = exponent.")
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\\times 10^{-5}$), b = exponent.")
 ```
@@
 
+<!-- Shouldn't everything should go to 2 decimal points in Table 1? I.e. 2.90 instead of 2.9?  -->
+
 \clearpage
@@
 
-Our results suggest that lionfish exhibit highly variable allometric relationships across the invaded range, and that this variation is spatially heterogeneous and relevant for management of the invasion.
-Moreover, we show that the use of *ex situ* parameters may lead to highly biased weight estimates.
-Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight can be overestimated by more than a three-fold, and highlights the need to use local information.
+Our results suggest that lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and that this variation is relevant for managing invasions.
+Moreover, we show that the use of *ex situ* parameter values may lead to highly biased weight estimates.
+Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight can be overestimated by more than threefold, highlighting the need to use local information.
 Here we discuss the implications of our findings, possible shortcommings in our analyses, and highlight potential future research directions.
@@
 To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.
+<!-- That's a damn excellent paragraph.  Nice. -->
 
@@
 
-We might be inclined to attribute all variation to the spatial origin of these parameters.
-However, these were not only collected for different locations, but also using a range of different sampling methods and at different points in time (See Supplementary Table 2 for an extended version of Table 1).
-While we are not able to evaluate how these factors influence previous estimates (raw data from all studies would be needed), it is certain that the lack of locally-calculated parameters may induce significant bias when calculating weight from length observations.
-Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both.
-The magnitude of the bias and our lack of understanding of the source of variation highlights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and link these to previously suggested environmental and genetic structures.
-Such an endeavor would provide insights into lionfish biology and better inform management.
+We might be inclined to attribute all variation in the lionfish length-weight relationship to the spatial origin of these parameters.
+However, samples from the 12 studies included here were not only collected in different locations, but also at different points in time and across different depth and size ranges (See Supplementary Table 2 for an extended version of Table 1 that incorporates these variables when available).
+While we could not evaluate how these factors influence previous estimates without the necessary raw data from every study, we still show that the lack of locally-calculated parameters can induce significant bias when calculating weight from length observations.
+Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both **CITATION EXAMPLE?**.
+The magnitude of the bias discovered in this study and our lack of understanding the sources driving spatial variation for lionfish highlights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and to link these findings to previously suggested environmental and genetic structures.
+Such an endeavor would provide insight into lionfish biology and better inform management.
 
 Applying parameters estimates to lengths outside the range of lengths originally used to estimate the parameters may also induce error.
-Our smallest observed organism was 34 mm in $TL$, and only two studies estimated parametrs with smaller organisms \citep{sabidoitza_2016,edwards_2014}.
-On the other hand, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (maximum observed lengths varied from 325 mm to 475 mm; See Supplementary Table 2).
-Due to the power-function describing the allometric relationship, the error is higher when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
+Our smallest observed organism was 34 mm in $TL$, and only two studies estimated parametrs with smaller organisms \citep{edwards_2014,sabidoitza_2016}.
+On the other hand, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (maximum observed lengths varied from 325 mm to 475 mm; See Supplementary Table 2) **I know this isn't what you mean to say, but it looks like you're saying 310 mm is within the range of 325-475 mm.
+Just figure out how to rephrase/rewrite**.
+Due to the power function describing the allometric relationship (i.e., Eq.
+1), the error is higher when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
 This means that not only must managers use locally-informed data, but that these local data must also include the full range of lengths present in the region to reduce error caused by extrapolation.
+<!-- I'm not sure what, but I think we need a little bit more here to convince the reader that this isn't a significant issue for what we're trying to do.
+How to convince the reader that it doesn't matter that our organism TLs cover a different size range and end at 310 mm?
+Gotta figure that out I think -->
 
-The results presented here have fundamental implications for management.
+The results presented here have important implications for management.
 For example, \citet{edwards_2014} simulated a lionfish culling program under two scenarios, one using length-at-age and length-to-weight parameters from North Carolina and one using parameters from Little Cayman.
@@
 These differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts.
-Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or at least use reasonable sets of different parameters that provide upper and lower bounds in their results.
+Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or use different sets of parameters that provide appropriate upper and lower bounds in their results.
+<!-- I feel like the word "fundamental" is really weird here (I know the reviewer suggested it, not you) so I used "important".
+If you want to use something the reviewer suggested, I like "key" better than "fundamental".
+Can't tell you why, it just seems strange haha -->
 
@@
 
-The thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
-We are greateful for comments raised by the editor and two anonimous reviewers, which significantly increased the quality of this work.
+We thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as well as Guillermo Lotz-Cador who provided help to collect samples.
+We are grateful for comments raised by the editor and two anonymous reviewers, which significantly increased the quality of this work.
 

### 2019-02-05 docs/Manuscript.Rmd
Added changes by Sean

@@
 A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate Western Atlantic.
-Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish (Green et al., 2012; Rocha et al., 2015; but see Hackerott et al., 2017 for a counterexample).<!-- need to avoid having those parentheses close prematurely - don't think it's possible using the citation code --> For example, field experiments showed that lionfish establishment in the Bahamas led to reduced recruitment of native fishes by nearly 80% over a five-week period \citet{albins_2008}, and prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs \citet{green_2012}.
+Their feeding behavior and high consumption rates can reduce recruitment and population sizes of native reef-fish species, and can further endanger reef fish \citep[][but see \citealt{hackerott_2017} for a counterexample]{green_2012,rocha_2015}.
+For example, field experiments showed that lionfish establishment in the Bahamas led to reduced recruitment of native fishes by nearly 80% over a five-week period \citep{albins_2008}, and prey fish biomass declined by 65% over two years as lionfish biomass increased along Bahamian coral reefs \citep{green_2012}.
 However, trophic impacts of lionfish can be minimized if their local biomass is controlled by culling \citep{ariasgonzalez_2011}.
@@
 
-Here, our objective was to quantify the magnitude of error caused by using *ex situ* parameter values when estimating lionfish weight from length observations.
+Our objective was to quantify the magnitude of error caused by using *ex situ* parameter values when estimating lionfish weight from length observations.
 In this study, we calculated and reported the first length-weight relationship for lionfish in the central Mexican Caribbean (n = 109).
@@
 
-<!-- What's the deal with all these citations? Did you mean to put them back in at the end of the paragraph? -->
-
-\clearpage
+<!-- I don't like how the citations cut this paragraph, which is one of the most important ones.
+I don't think we have to explicitly cite them here, since they are cited in the table and basically all figures, as well as in instances when we touch on each region.
+If you agree, let's delete them.
+Otherwise, we can put them right after Costa Rica / before "...
+By comparing these...".
+-->
 
@@
 
+We also used data from 109 lionfish sampled by \citet{villaseorderbez_2014}, who used hand nets and numbered bottles to collect organisms from 10 sampling sites along the central Mexican Caribbean coast in the Summer of 2010 (Supplementary Table 1).
+Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
+The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by avoiding gear selectivity.
+Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
+
+\clearpage
+
 ```{r}
@@
 
-<!-- Shouldn't the figure go after it's introduced in the text? I'm not sure why it knitted above the METHODS header in the actual manuscript. -->
-
 ```{r map, fig.cap = "\\label{fig:map}Locations where allometric growth parameters of lionfish (*Pterois spp*) have been reported.
@@
 
-We also used data from 109 lionfish sampled by \citet{villaseorderbez_2014}, who used hand nets and numbered bottles to collect organisms from 10 sampling sites along the central Mexican Caribbean coast in the Summer of 2010 (Supplementary Table 1).
-Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
-The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by avoiding gear selectivity.
-Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
-
-\clearpage
-
 The weight-at-length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function
@@
 TW = aTL^b
-\end{equation},
+\end{equation}
 
@@
 We linearized the equation using $log_{10}$-transformation and estimated the coefficients using an Ordinary Least Squares Regression with a heteroskedastic-robust standard error correction \citep{zeileis_2004}.
-Organisms exhibit perfect isometric growth when $b = 3$, so we tested the $b$ coefficient against the null hypothesis of isometric growth (*i.e.* $H_0: b = 3$) **to determine...
-WHAT???
-whether the organism displayed isometric or allometric growth?
-What is the point of that?
-Not saying we shouldn't have it in there, but we should say why we're doing it.
-Ostensibly is it to be sure that the lionfish L-W relationship DOES significantlt differ from isometric growth?
-(even though we basically already know that from the other studies?)**.
 Coefficients were tested with a two-tailed Student's t-test, and the significance of the regression was corroborated with an F-test.
-
-<!-- Transforming this equation via base-10 logarithms we obtain: -->
-
-<!-- \begin{equation} -->
-<!-- \label{eq:log-alo} -->
-<!-- log_{10}(TW) = b\times log_{10}(TL) + log_{10}(a) -->
-<!-- \end{equation} -->
-
-<!-- This can be simplified and re-written as: -->
-
-<!-- \begin{equation} -->
-<!-- \label{eq:log-alo-trans} -->
-<!-- Y = bX + c -->
-<!-- \end{equation} -->
-
-<!-- Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, and $c = log_{10}(a)$. -->
 
@@
 Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and summarized in Table \ref{tab:all_params}.
-
-<!-- Shouldn't we move Table 1 up in the paper?
-Maybe at the end of methods or something?
-Seems really weird to have it all the way at the end, especially when mentioned so early on.
-I always thought you want to have things appear in the text in the same order they are written.
--->
 
@@
 Raw data and code used in this work are available on github at github.com/jcvdav/lionfish_biometry.
+
+```{r}
+review %>% 
+  select(Region, Gender2, N, a, b, r2, Study) %>% 
+  filter(!Study == "Fishbase") %>% 
+  arrange(desc(Region)) %>% 
+  mutate(r2 = formatC(r2, digits = 2),
+         r2 = ifelse(r2 == " NA", "-", r2),
+         N = ifelse(is.na(N), "-", N),
+         a = formatC((a*1e5), digits = 2)) %>% 
+  knitr::kable(row.names = F,
+               digits =  c(0, 0, 0, 0, 2, 2),
+               booktabs = T,
+               col.names = c("Region", "Sex", "n", "a", "b", "$R^2$", "Reference"),
+               caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\\times 10^{-5}$), b = exponent.")
+```
 
@@
 c <- coefficients(model)[[1]]
+a <- formatC(10^c, digits = 4)
 b <- coefficients(model)[[2]]
+bs <- formatC(b, digits = 4)
 ```
@@
 
-The length-weight relationship for organisms from the central Mexican Caribbean resulted in coefficient values of $a = `r 10^c`$ and $b = `r b`$ ($R^2 = `r Rsq`$, `r Fstring`, $p < 0.001$).
-The allometric factor ($b$) was significantly different from $b = 3$ ($t(107) = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) corroborating that lionfish present allometric growth.
+The length-weight relationship for organisms from the central Mexican Caribbean resulted in coefficient values of $a = `r a`$ and $b = `r bs`$ ($R^2 = `r Rsq`$, $F_{1, 107} = 6928.67; p < 0.001$).
+The allometric factor ($b$) was significantly different from $b = 3$ ($t_{107} = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) corroborating that lionfish present allometric growth.
 The length-weight coefficients estimated here were within the range identified by studies from other regions (Table \ref{tab:all_params}).
 Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region.
-
-<!-- I think we should reduce the number of decimal points, maybe make it consistent with the figure? (4 decimal points?)  Up to you though.  Also good figure placement for Fig. 2 -->
 
@@
 
-<!-- Some notes on reporting F-statistic: 1) If you're going to do it the way you have it currently, make sure "df" is either always italicized.
-However, 2) the better way to report F-test results is to put the degrees of freedom as a subscript on F, then you don't have to write df and have extra parentheses that look bad - e.g.
-see https://www.yorku.ca/mack/RN-HowToReportAnFStatistic.html -->
-
-There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F(df = 17; 1943) = 24.96; p < 0.001$).
+There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$).
 The lowest weight estimates for the observed lengths resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{sabidoitz_2016}.
@@
 
-<!-- Question - do you think we should report standard error instead of standard deviation?
-Since we're interested in comparing the different estimates (not describing the spread of the data), standard error is probably better (plus it'll be a lot smaller so the differences will look more meaningful upon first glance).
-I think that's the way to go, but I'm a little wary to do so since the reviewers didn't flag it and I suppose it's possible they might not like the change...
--->
-
 Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
-Weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher on average than those from the Caribbean (Fig \ref{fig:all_allo}) **GOTTA HAVE SOME STATS HERRE TO BACK THIS UP - DIDN'T TUKEY'S SHOW THAT WEIGHT RATIOS HERE WERE DIFFERENT??
-If p > 0.05 for Little Cayman/Bahamas/some GoM, wasn't p < 0.05 for every other site?
-If so, definitely say that.** The average ($\pm$ SD) predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.76 $\pm$ 0.496, and 1.17 $\pm$ 0.398, respectively.
+All weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher than observed values, and only parameters from the Caribbean produced weights smaller than observed (Fig \ref{fig:bio_ratio}).
+The regional average ($\pm$ SD) of predicted-to-observed weight ratios from these three regions were 1.24 $\pm$ 0.309, 1.41 $\pm$ 0.523, and 1.20 $\pm$ 0.423 for the Gulf of Mexico, Western Atlantic, and Caribbean, respectively.
 This suggests that the smallest errors are observed when using parameters from other locations in the Caribbean.
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
-
-<!-- Unfortunately, I think we should make a change to Figures 3 and 4 (it won't take long).I think we should do something like put "WA", "C", or "GoM" next to each study depending on their location (Western Atlantic, Caribbean, Gulf of Mexico).
-We have to give some way to indicate what region each set of observations is from.
-I know it's in Table 1, but right now it's impossible for the reader to draw any conclusion that there's a pattern in that sites in the Caribbean were more similar to this study than sites in the Gulf or Western Atlantic.
-Alternatively, maybe we could just substitute superscripted numbers for writing out the reference citation?
-I.e.
-GoM^1 would be Aguilar, WA^2 would be Barbour...
-Then in figure 3 caption we say what footnote corresponds to what study and in Figure 4 just say numbers correspond to same references as figure 3 caption.
-Lmk if you see what I mean, happy to discuss more.
--->
-
-```{r}
-review %>% 
-  select(Region, Gender2, N, a, b, r2, Study) %>% 
-  filter(!Study == "Fishbase") %>% 
-  arrange(desc(Region)) %>% 
-  mutate(r2 = formatC(r2, digits = 2),
-         r2 = ifelse(r2 == " NA", "-", r2),
-         N = ifelse(is.na(N), "-", N),
-         a = formatC((a*1e5), digits = 2)) %>% 
-  knitr::kable(row.names = F,
-               digits =  c(0, 0, 0, 0, 2, 2),
-               booktabs = T,
-               col.names = c("Region", "Sex", "n", "a", "b", "$R^2$", "Reference"),
-               caption = "\\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\\times 10^{-5}$), b = exponent.")
-```
 
@@
   mutate(min = min(Weight),
-         max = max(Weight)) %>% 
+         max = max(Weight),
+         Region = case_when(Region == "Western Atlantic" ~ "WA",
+                            Region == "Caribbean" ~ "Ca",
+                            T ~ "GoM"),
+         Study_Region = paste0(Study, " (", Region, ")")) %>% 
   ungroup() %>% 
   ggplot(aes(x = Length)) +
-  geom_line(aes(y = Weight, color = Study, linetype = Gender, group = Study_id), size = 1) +
+  geom_line(aes(y = Weight, color = Study_Region,
+                linetype = Gender, group = Study_id), size = 1) +
   geom_line(data = This, aes(x = Length, y = Weight),
@@
   guides(color = guide_legend(order = 1),
-         linetype = guide_legend(order = 0, ncol = 2, override.aes = list(size = 0.5)),
+         linetype = guide_legend(order = 0, ncol = 1, override.aes = list(size = 0.5)),
          size = "none") +
@@
 Dotted, dashed, and solid lines show models for males, females, and combined sexes, respectively.
+Letters in parentheses indicate if the study comes from the Gulf of Mexico (GoM), Western Atlantic (WA), or Caribbean (Ca).
 The dashed black line represents the relationship estimated in this study.
@@
 fig_bio_ratio <- Predicted_biomass %>% 
-  mutate(Study = paste0(Study, " (", Gender_site, ")")) %>%
+  mutate(Study = paste0(Study, " (", Gender_site, ")"),
+         Region = case_when(Region == "Western Atlantic" ~ "WA",
+                            Region == "Caribbean" ~ "Ca",
+                            T ~ "GoM")) %>%
   transform(Study = reorder(Study, -Biomass_ratio),
@@
   ggplot(aes(x = Study, y = Biomass_ratio, group = Study_id)) +
-  geom_violin(aes(fill = Sex), alpha = 0.8) +
-  stat_summary(geom = "point", fun.y = "median", size = 2, color = "black", fill = "steelblue", shape = 21) +
+  geom_violin(aes(fill = Region), alpha = 0.8) +
+  stat_summary(geom = "point",
+               fun.y = "median",
+               size = 2,
+               color = "black",
+               fill = "steelblue",
+               shape = 21) +
   geom_hline(yintercept = 1, linetype = "dashed") +
@@
   theme(text = element_text(family = "Times")) +
-  scale_fill_brewer(palette = "Greys") +
+  scale_fill_brewer(palette = "Set1") +
   theme(text = element_text(family = "Times"),
@@
 
-<!-- Shouldn't everything should go to 2 decimal points in Table 1? I.e. 2.90 instead of 2.9?  -->
-
 \clearpage
@@
 To accurately gauge both the effectiveness of lionfish removal efforts and the resources needed to successfully manage an invasion, we must acknowledge and understand regional biological differences in important variables such as allometric growth parameters.
-<!-- That's a damn excellent paragraph.  Nice. -->
 
@@
 While we could not evaluate how these factors influence previous estimates without the necessary raw data from every study, we still show that the lack of locally-calculated parameters can induce significant bias when calculating weight from length observations.
-Differences in weight-at-length could also reflect differential energy input or usage, or a combination of both **CITATION EXAMPLE?**.
 The magnitude of the bias discovered in this study and our lack of understanding the sources driving spatial variation for lionfish highlights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and to link these findings to previously suggested environmental and genetic structures.
@@
 Our smallest observed organism was 34 mm in $TL$, and only two studies estimated parametrs with smaller organisms \citep{edwards_2014,sabidoitza_2016}.
-On the other hand, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (maximum observed lengths varied from 325 mm to 475 mm; See Supplementary Table 2) **I know this isn't what you mean to say, but it looks like you're saying 310 mm is within the range of 325-475 mm.
-Just figure out how to rephrase/rewrite**.
-Due to the power function describing the allometric relationship (i.e., Eq.
-1), the error is higher when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
-This means that not only must managers use locally-informed data, but that these local data must also include the full range of lengths present in the region to reduce error caused by extrapolation.
-<!-- I'm not sure what, but I think we need a little bit more here to convince the reader that this isn't a significant issue for what we're trying to do.
-How to convince the reader that it doesn't matter that our organism TLs cover a different size range and end at 310 mm?
-Gotta figure that out I think -->
+However, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (the next smallest maximum length was 325 mm; See Supplementary Table 2).
+Due to the power function describing the allometric relationship (*i.e.* Eq.
+1), the error is larger when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
 
-The results presented here have important implications for management.
+<!-- I modified the paragraph above a bit, and think its a bit more clear, but please change it if you think there are better ways to explain it.
+I think the central idea is that we do not extrapolate from other predictions, so we are safe in that sense.
+-->
+
+The results presented here have key implications for management.
 For example, \citet{edwards_2014} simulated a lionfish culling program under two scenarios, one using length-at-age and length-to-weight parameters from North Carolina and one using parameters from Little Cayman.
@@
 Research efforts focused on invasive lionfish populations need to use parameters calculated for their region to the extent possible, or use different sets of parameters that provide appropriate upper and lower bounds in their results.
-<!-- I feel like the word "fundamental" is really weird here (I know the reviewer suggested it, not you) so I used "important".
-If you want to use something the reviewer suggested, I like "key" better than "fundamental".
-Can't tell you why, it just seems strange haha -->
 

### 2019-02-05 docs/Manuscript.tex
Added changes by Sean

@@
 lionfish populations requires accurate total biomass estimates, which
-depend on accurate estimates of allometric growth. Sedentary species
+depend on accurate estimates of allometric growth, but sedentary species
 like lionfish often exhibit high levels of spatial variation in life
-history characteristics. We review 17 published length-weight
+history characteristics. We reviewed 17 published length-weight
 relationships for lionfish taken throughout their invasive range and
@@
 overestimation of weight estimates. The spatial pattern we observed is
-consistent with findings from other studies focusing on genetics or
+consistent with findings from other studies focused on genetics or
 length-at-age. We show that the use of \textit{ex situ} parameters can
 result in up to a threefold under- or overestimation of total weight,
-but using parameters from nearby regions reduces this error. These
-findings can have substantial implications for management in terms of
+but using parameters from nearby regions substantially reduces this
+error. These findings can have implications for management in terms of
 predicting effects on local ecosystems, evaluating the effectiveness of
@@
 reef-fish species, and can further endanger reef fish
-\citep{green_2012,rocha_2015}; but see \citet{hackerott_2017}. For
-example, field experiments by \citet{albins_2008} showed that lionfish
-establishment led to reduced recruitment of native fishes by nearly 80\%
-over a five-week period in the Bahamas. \citet{green_2012} reported that
-prey fish biomass declined by 65\% over two years as lionfish biomass
-increased along Bahamian coral reefs. However, their trophic impacts can
-be minimized if local lionfish biomass is controlled by culling
+\citep[][but see \citealt{hackerott_2017} for a counterexample]{green_2012,rocha_2015}.
+For example, field experiments showed that lionfish establishment in the
+Bahamas led to reduced recruitment of native fishes by nearly 80\% over
+a five-week period \citep{albins_2008}, and prey fish biomass declined
+by 65\% over two years as lionfish biomass increased along Bahamian
+coral reefs \citep{green_2012}. However, trophic impacts of lionfish can
+be minimized if their local biomass is controlled by culling
 \citep{ariasgonzalez_2011}.
@@
 \citep{chin_2016}. In some cases, these have shown to significantly
-reduce --but not quite eliminate-- lionfish abundances at local scales
+reduce -- but not quite eliminate -- lionfish abundances at local scales
 \citep{deleon_2013,sandel_2015}. Complete eradication of lionfish
@@
 Outcomes of previous studies suggest lionfish are likely to exhibit
-spatial heterogeneity in the length-weight relationship, which we
-summarize in two main causes. First, culling programs are effective in
-reducing local adult populations largely because lionfish exhibit high
-levels of site fidelity and small home ranges
-\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. It is known
-that fish with sedentary behavior are likely to exhibit high levels of
-spatial variation in important life history characteristics such as
-growth or natural mortality rates
-\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. Second,
-genetic analysis of lionfish suggests biological differences due to the
-existence of two genetically distinct invasive subpopulations between
-the Western Atlantic and the Caribbean \citep{betancurr_2011}. The large
-number of site-specific studies reporting the length-weight relationship
-of lionfish provide variable estimates. These differences may be
+spatial heterogeneity in the length-weight relationship for two main
+reasons. First, fish with sedentary behavior such as lionfish often
+exhibit high levels of spatial variation in important life history
+characteristics such as growth or natural mortality rates
+\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. In fact,
+culling programs are effective in reducing local adult populations
+largely because lionfish have high levels of site fidelity and small
+home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
+Second, genetic analysis of lionfish suggests biological differences due
+to the existence of two genetically distinct invasive subpopulations
+between the Western Atlantic and the Caribbean \citep{betancurr_2011}.
+Site-specific studies that calculate the length-weight relationship of
+lionfish report variable estimates, and these differences may be
 increasingly important when estimating the potential effectiveness of
@@
 \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
-magnitude of the error caused by using \emph{ex situ} parameters to
-estimate total weight from length observations remains unexplored.
+influence of using \emph{ex situ} parameters when estimating the
+length-weight relationship remains unexplored.
 
-Here, we use previously published length-weight relationships for
-lionfish populations in North Carolina, Northern and Southern Gulf of
-Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica,
-Bonaire, Puerto Rico, and Costa Rica to quantify the magnitude of the
-error caused by using \emph{ex situ} parameters to estimate lionfish
-weight from length observations. We also collected lionfish length and
-weight data in the central Mexican Caribbean and report the first
-length-weight relationship for this region.
-
-\clearpage
+Our objective was to quantify the magnitude of error caused by using
+\emph{ex situ} parameter values when estimating lionfish weight from
+length observations. In this study, we calculated and reported the first
+length-weight relationship for lionfish in the central Mexican Caribbean
+(n = 109). We then estimated lionfish weight in this area using
+previously published length-weight relationships for lionfish
+populations in North Carolina, the Northern and Southern Gulf of Mexico,
+the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica,
+Bonaire, Puerto Rico, and Costa Rica. By comparing these weight
+estimates to the \emph{in situ} length-weight observations, we showed
+that using \emph{ex situ} parameter values resulted in up to a threefold
+under- or overestimation of lionfish weight.
 
@@
 collected information on sex differentiation, location, length and depth
-ranges and sampling methods from each study when available. Only two
-studies reported parameters for each gender
-\citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were
-included in a study if gender was unspecified. Reviewed studies
-presented information for organisms ranging between 25 mm and 475 mm in
-Total Length (\(TL\)), and that were obtained at depths between 0.5 m
-and 57 m. Four studies explicitly stated that their organisms were
-sampled with pole spears
-\citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six
-studies mentioned that some of their organisms were obtained with pole
-spears (or other type of harpoon) but also hand-held nets or fish traps
-\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016},
-and two studies did not specify how organisms were sampled
+ranges, and sampling methods from each study when available. Only two
+studies reported parameters for each sex
+\citep{aguilarperera_2016,fogg_2013}, so we assumed data from both sexes
+were combined in a study if sex was unspecified. Reviewed studies
+presented information for organisms ranging from 25-475 mm in Total
+Length (\(TL\)) and were obtained at depths between 0.5 m and 57 m. Four
+studies explicitly stated that their organisms were sampled with pole
+spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016},
+and six studies mentioned that some of their organisms were obtained
+with pole spears (or other type of harpoon) but also hand-held nets or
+fish traps
+\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}.
+Two studies did not specify how organisms were sampled
 \citep{darling_2011,deleon_2013}.
+
+We also used data from 109 lionfish sampled by
+\citet{villaseorderbez_2014}, who used hand nets and numbered bottles to
+collect organisms from 10 sampling sites along the central Mexican
+Caribbean coast in the Summer of 2010 (Supplementary Table 1). Sampling
+locations included wall and carpet reefs at depths between 5.7 m and
+38.1 m. The use of hand nets prevented any weight loss due to bleeding
+and allowed better representation of small sizes by avoiding gear
+selectivity. Organisms were euthanized via pithing and Total Length (TL;
+mm) and Total Weight (TW; g) were recorded.
+
+\clearpage
 
@@
 
-We also used data from \citet{villaseorderbez_2014}, who collected
-organisms from 10 sampling sites along the central Mexican Caribbean
-coast in the Summer of 2010 (Supplementary Table 1). Sampling locations
-included wall and carpet reefs at depths between 5.7 m and 38.1 m. All
-observed lionfish (n = 109) were collected using hand nets and numbered
-collection bottles. The use of hand nets prevented any weight loss due
-to bleeding and allowed better representation of small sizes by avoiding
-gear selectivity. Organisms were euthanized via pithing and Total Length
-(TL; mm) and Total Weight (TW; g) were recorded.
-
-\clearpage
-
 The weight-at-length relationship for lionfish in the central Mexican
-Caribbean was calculated with the allometric growth function:
+Caribbean was calculated with the allometric growth function
 
@@
 
-Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
-allometric parameter.
-
-The above equation was linearized using \(log_{10}\)-transformation. The
-coefficients were estimated with an Ordinary Least Squares Regression,
-and heteroskedastic-robust standard error correction was applied
-\citep{zeileis_2004}. When \(b = 3\), it is said that the organism
-exhibits a perfect isometric growth, so the \(b\) coefficient was tested
-against the null hypothesis of isometric growth (\emph{i.e.}
-\(H_0: b = 3\)). Coefficients were tested with a two-tailed Student's t,
-and the significance of the regression was corroborated with an F-test.
+where \(a\) is the ponderal index and \(b\) is the scaling exponent or
+allometric parameter. We linearized the equation using
+\(log_{10}\)-transformation and estimated the coefficients using an
+Ordinary Least Squares Regression with a heteroskedastic-robust standard
+error correction \citep{zeileis_2004}. Coefficients were tested with a
+two-tailed Student's t-test, and the significance of the regression was
+corroborated with an F-test.
 
@@
 describe variations between populations, but rather to estimate how the
-use of \emph{ex situ} parameters influences weight estimates. We used
-the central Mexican Caribbean as a case study of how the use of \emph{ex
-situ} parameters influences the accuracy of weight estimates for
-lionfish. We estimated \(TW\) from the \(TL\) observations we collected
-in the central Mexican Caribbean (n = 109, with \(TL\) ranging from 34
-mm to 310 mm) using each of the 18 parameter pairs and divided predicted
+use of \emph{ex situ} parameters influences the accuracy of weight
+estimates for lionfish, using the central Mexican Caribbean as a case
+study. Using each of the 18 parameter pairs, we estimated \(TW\) from
+the \(TL\) observations collected in the central Mexican Caribbean (n =
+109, with \(TL\) ranging from 34 mm to 310 mm) and divided predicted
 weights by known observed weights to obtain a simple measure of over- or
@@
 
+\begin{table}[t]
+
+\caption{\label{tab:unnamed-chunk-2}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
+All parameters have been adjusted to convert from millimeters to grams.
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
+\centering
+\begin{tabular}{llllrll}
+\toprule
+Region & Sex & n & a & b & $R^2$ & Reference\\
+\midrule
+Western Atlantic & B & 774 & 2.90 & 2.89 & - & Barbour et al., 2011\\
+Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
+GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
+GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+\addlinespace
+GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
+GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
+GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
+GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
+Caribbean & B & 458 & 3.60 & 2.81 & - & Sandel et al., 2015\\
+\addlinespace
+Caribbean & B & 419 & 2.80 & 2.85 & 0.87 & Chin et al., 2016\\
+Caribbean & B & 1450 & 2.30 & 2.89 & 0.92 & de Leon et al., 2013\\
+Caribbean & B & 1887 & 0.30 & 3.24 & 0.97 & Edwards et al., 2014\\
+Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
+Caribbean & B & 227 & 0.80 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
+\addlinespace
+Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
+Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
+Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \section*{Results}
@@
 The length-weight relationship for organisms from the central Mexican
-Caribbean resulted in coefficient values of
-\(a = 3.2056297\times 10^{-6}\) and \(b = 3.2347391\) (\(R^2 = 0.977\),
-F(df = 1; 107) = 6928.67, \(p < 0.001\)). The allometric factor (\(b\))
-was significantly different from \(b = 3\) (\(t(107) = 6.04; p<0.001\))
-corroborating that lionfish present allometric growth. The length-weight
-coefficients estimated in this study were within the range identified by
-studies in other regions (Table \ref{tab:all_params}). Figure
-\ref{fig:l-w-carib} shows the relationship between TL and TW for this
-region.
+Caribbean resulted in coefficient values of \(a = 3.206e-06\) and
+\(b = 3.235\) (\(R^2 = 0.977\), \(F_{1, 107} = 6928.67; p < 0.001\)).
+The allometric factor (\(b\)) was significantly different from \(b = 3\)
+(\(t_{107} = 6.04; p<0.001\)) corroborating that lionfish present
+allometric growth. The length-weight coefficients estimated here were
+within the range identified by studies from other regions (Table
+\ref{tab:all_params}). Figure \ref{fig:l-w-carib} shows the relationship
+between TL and TW for this region.
 
@@
 central Mexican Caribbean when using each of the different pairs of
-parameters (\(F(df = 17; 1943) = 24.96; p < 0.001\)). The lowest weight
+parameters (\(F_{17, 1943} = 24.96; p < 0.001\)). The lowest weight
 estimates for the observed lengths resulted from using the allometric
@@
 observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weights predicted
-from these extreme parameters correspond to mean \(\pm\) SD
-predicted-to-observed weights ratios of 0.80 \(\pm\) 0.19 and 1.76
-\(\pm\) 0.50 (mean \(\pm\) SD), respectively. The largest under- and
-overestimations resulted in ratios of 0.36 and 3.51 of the actual
-observed weight, indicating that \emph{ex situ} parameters can result in
-substantial weight under- and overestimation.
+from these extreme parameters correspond to predicted-to-observed weight
+ratios of 0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD),
+respectively. The largest under- and overestimations resulted in ratios
+of 0.36 and 3.51 of the actual observed weight, indicating that \emph{ex
+situ} parameters can result in highly erroneous weight estimates.
 
@@
 from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico
-(Tukey's HSD \(p > 0.05\)). Weight estimates using parameters from the
-Gulf of Mexico and Western Atlantic were higher on average than those
-from the Caribbean (Fig \ref{fig:all_allo}). The average (\(\pm\) SD)
-predicted-to-observed weight ratios from these three regions were 1.24
-\(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
-This suggest that the smallest errors are observed when using parameters
-other locations in the Caribbean. Predicted-to-observed weight ratios
-are presented in Figure \ref{fig:bio_ratio}.
-
-\begin{table}[t]
-
-\caption{\label{tab:unnamed-chunk-7}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study.
-All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
-\centering
-\begin{tabular}{llllrll}
-\toprule
-Region & Sex & n & a & b & $R^2$ & Reference\\
-\midrule
-Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
-Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
-GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
-GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-\addlinespace
-GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
-GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
-GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
-Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
-\addlinespace
-Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
-Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
-Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
-Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
-Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
-\addlinespace
-Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
-Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
-Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
-\bottomrule
-\end{tabular}
-\end{table}
+(Tukey's HSD \(p > 0.05\)). All weight estimates using parameters from
+the Gulf of Mexico and Western Atlantic were higher than observed
+values, and only parameters from the Caribbean produced weights smaller
+than observed (Fig \ref{fig:bio_ratio}). The regional average (\(\pm\)
+SD) of predicted-to-observed weight ratios from these three regions were
+1.24 \(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\) 0.423 for the
+Gulf of Mexico, Western Atlantic, and Caribbean, respectively. This
+suggests that the smallest errors are observed when using parameters
+from other locations in the Caribbean. Predicted-to-observed weight
+ratios are presented in Figure \ref{fig:bio_ratio}.
 
@@
 dashed, and solid lines show models for males, females, and combined
-sexes, respectively. The dashed black line represents the relationship
-estimated in this study. There are two solid green lines for Sabido-Itza
-et al, 2016b, one for each of the two sites for which they report
-parameters. A log-log version of this figure is presented in Figure S4.}
+sexes, respectively. Letters in parentheses indicate if the study comes
+from the Gulf of Mexico (GoM), Western Atlantic (WA), or Caribbean (Ca).
+The dashed black line represents the relationship estimated in this
+study. There are two solid green lines for Sabido-Itza et al, 2016b, one
+for each of the two sites for which they report parameters. A log-log
+version of this figure is presented in Figure S4.}
 \end{figure}
@@
 
-Our results suggest that lionfish exhibit highly variable allometric
-relationships across the invaded range, and that this variation is
-spatially heterogeneous and relevant for management of the invasion.
-Moreover, we show that the use of \emph{ex situ} parameters may lead to
-highly biased weight estimates. Our comparison of observed weights to
-those predicted with locally-informed parameters and \emph{ex situ}
-parameters showed that weight can be overestimated by more than a
-three-fold, and highlights the need to use local information. Here we
-discuss the implications of our findings, possible shortcommings in our
-analyses, and highlight potential future research directions.
+Our results suggest that lionfish exhibit highly variable, spatially
+heterogeneous allometric relationships across their invaded range, and
+that this variation is relevant for managing invasions. Moreover, we
+show that the use of \emph{ex situ} parameter values may lead to highly
+biased weight estimates. Our comparison of observed weights to those
+predicted with locally-informed parameters and \emph{ex situ} parameters
+showed that weight can be overestimated by more than threefold,
+highlighting the need to use local information. Here we discuss the
+implications of our findings, possible shortcommings in our analyses,
+and highlight potential future research directions.
 
@@
 
-We might be inclined to attribute all variation to the spatial origin of
-these parameters. However, these were not only collected for different
-locations, but also using a range of different sampling methods and at
-different points in time (See Supplementary Table 2 for an extended
-version of Table 1). While we are not able to evaluate how these factors
-influence previous estimates (raw data from all studies would be
-needed), it is certain that the lack of locally-calculated parameters
-may induce significant bias when calculating weight from length
-observations. Differences in weight-at-length could also reflect
-differential energy input or usage, or a combination of both. The
-magnitude of the bias and our lack of understanding of the source of
-variation highlights the need to simultaneously collect length-weight
-information across the invaded range to test for spatially-induced
-patterns and link these to previously suggested environmental and
-genetic structures. Such an endeavor would provide insights into
-lionfish biology and better inform management.
+We might be inclined to attribute all variation in the lionfish
+length-weight relationship to the spatial origin of these parameters.
+However, samples from the 12 studies included here were not only
+collected in different locations, but also at different points in time
+and across different depth and size ranges (See Supplementary Table 2
+for an extended version of Table 1 that incorporates these variables
+when available). While we could not evaluate how these factors influence
+previous estimates without the necessary raw data from every study, we
+still show that the lack of locally-calculated parameters can induce
+significant bias when calculating weight from length observations. The
+magnitude of the bias discovered in this study and our lack of
+understanding the sources driving spatial variation for lionfish
+highlights the need to simultaneously collect length-weight information
+across the invaded range to test for spatially-induced patterns and to
+link these findings to previously suggested environmental and genetic
+structures. Such an endeavor would provide insight into lionfish biology
+and better inform management.
 
@@
 estimated parametrs with smaller organisms
-\citep{sabidoitza_2016,edwards_2014}. On the other hand, our largest
-organism had a \(TL\) of 310 mm, which is well within the range of all
-other studies (maximum observed lengths varied from 325 mm to 475 mm;
-See Supplementary Table 2). Due to the power-function describing the
-allometric relationship, the error is higher when extrapolation is done
-for lengths that are larger than the maximum length used to estimate the
-parameters. This means that not only must managers use locally-informed
-data, but that these local data must also include the full range of
-lengths present in the region to reduce error caused by extrapolation.
+\citep{edwards_2014,sabidoitza_2016}. However, our largest organism had
+a \(TL\) of 310 mm, which is well within the range of all other studies
+(the next smallest maximum length was 325 mm; See Supplementary Table
+2). Due to the power function describing the allometric relationship
+(\emph{i.e.} Eq. 1), the error is larger when extrapolation is done for
+lengths that are larger than the maximum length used to estimate the
+parameters.
 
-The results presented here have fundamental implications for management.
-For example, \citet{edwards_2014} simulated a lionfish culling program
-under two scenarios, one using length-at-age and length-to-weight
-parameters from North Carolina and one using parameters from Little
-Cayman. Their results show that using different parameters caused up to
-a four-year difference in the time required for the simulated lionfish
-population to recover to 90\% of its initial biomass after removals
-ceased. Here, we show that using one set of length-weight parameters
-versus another for a given length can result in more than a threefold
-under- or overestimation of total weight. These differences become
-especially important when allocating resources for lionfish removal
-programs, incentivizing lionfish fisheries as a source of alternative
-livelihoods, or estimating ecosystem impacts. Research efforts focused
-on invasive lionfish populations need to use parameters calculated for
-their region to the extent possible, or at least use reasonable sets of
-different parameters that provide upper and lower bounds in their
-results.
+The results presented here have key implications for management. For
+example, \citet{edwards_2014} simulated a lionfish culling program under
+two scenarios, one using length-at-age and length-to-weight parameters
+from North Carolina and one using parameters from Little Cayman. Their
+results show that using different parameters caused up to a four-year
+difference in the time required for the simulated lionfish population to
+recover to 90\% of its initial biomass after removals ceased. Here, we
+show that using one set of length-weight parameters versus another for a
+given length can result in more than a threefold under- or
+overestimation of total weight. These differences become especially
+important when allocating resources for lionfish removal programs,
+incentivizing lionfish fisheries as a source of alternative livelihoods,
+or estimating ecosystem impacts. Research efforts focused on invasive
+lionfish populations need to use parameters calculated for their region
+to the extent possible, or use different sets of parameters that provide
+appropriate upper and lower bounds in their results.
 
@@
 
-The thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as
+We thank Nils Van Der Haar and Michael Doodey from Dive Aventuras as
 well as Guillermo Lotz-Cador who provided help to collect samples. We
-are greateful for comments raised by the editor and two anonimous
+are grateful for comments raised by the editor and two anonymous
 reviewers, which significantly increased the quality of this work.

### 2019-02-07 docs/Manuscript.Rmd
Intro through results

@@
 title: "Spatial variation in allometric growth of invasive lionfish has management implications"
-author: "Juan Carlos Villaseñor-Derbez, Sean Fitzgerald"
+author: "Juan Carlos Villaseñor-Derbez, Sean P. Fitzgerald"
 institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
@@
 Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth, but sedentary species like lionfish often exhibit high levels of spatial variation in life history characteristics.
-We reviewed 17 published length-weight relationships for lionfish taken throughout their invasive range and found regional differences that led to significant under- and overestimation of weight estimates.
+We reviewed 17 published length-weight relationships for lionfish taken throughout their invasive range and found regional differences that led to significant misestimates when calculating weight from length observations.
 The spatial pattern we observed is consistent with findings from other studies focused on genetics or length-at-age.
@@
 These findings can have implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
+# I'm not sure I like the word "misestimates" but I want to avoid repeating the phrase "under- or overestimation" twice in the abstract; if you can come up with something that sounds better, go for it.
 keywords:
@@
 Lionfish (*Pterois volitans/miles* complex) are an invasive species in the Western Atlantic Ocean and Caribbean Sea, likely introduced through release of aquarium-kept organisms \citep{betancurr_2011}.
-They are the first invasive marine vertebrates established along these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
-Lionfish have established invasive populations in coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
+Lionfish are the first invasive marine vertebrates established along these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}, and they have established invasive populations in coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
+Their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
 
-A substantial amount of research describes lionfish impacts throughout its invaded range.
+A substantial amount of research describes lionfish impacts throughout their invaded range.
 A meta-analysis by \citet{peake_2018} showed that invasive lionfish prey on at least 167 different species across the tropical and temperate Western Atlantic.
@@
 
-Outcomes of previous studies suggest lionfish are likely to exhibit spatial heterogeneity in the length-weight relationship for two main reasons.
-First, fish with sedentary behavior such as lionfish often exhibit high levels of spatial variation in important life history characteristics such as growth or natural mortality rates \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}.
-In fact, culling programs are effective in reducing local adult populations largely because lionfish have high levels of site fidelity and small home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
-Second, genetic analysis of lionfish suggests biological differences due to the existence of two genetically distinct invasive subpopulations between the Western Atlantic and the Caribbean \citep{betancurr_2011}.
+Outcomes of previous studies suggest lionfish are likely to exhibit spatial heterogeneity in the length-weight relationship for both behavioral and biological reasons.
+Important life history characteristics such as growth or natural mortality rates are often  spatially variable for fish that exhibit sedentary behavior  \citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}, and in fact, high levels of site fidelity and small home ranges are two primary reasons why culling programs are effective in reducing local adult lionfish populations \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
+Genetic analysis of lionfish also identified two genetically distinct invasive subpopulations between the Western Atlantic and the Caribbean, suggesting the existence of spatially explicit biological differences between populations as well \citep{betancurr_2011}.
 Site-specific studies that calculate the length-weight relationship of lionfish report variable estimates, and these differences may be increasingly important when estimating the potential effectiveness of lionfish culling programs \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}.
@@
 Our objective was to quantify the magnitude of error caused by using *ex situ* parameter values when estimating lionfish weight from length observations.
-In this study, we calculated and reported the first length-weight relationship for lionfish in the central Mexican Caribbean (n = 109).
-We then estimated lionfish weight in this area using previously published length-weight relationships for lionfish populations in North Carolina, the Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica.
-By comparing these weight estimates to the *in situ* length-weight observations, we showed that using *ex situ* parameter values resulted in up to a threefold under- or overestimation of lionfish weight.
-
-<!-- \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016} -->
-
-<!-- I don't like how the citations cut this paragraph, which is one of the most important ones.
-I don't think we have to explicitly cite them here, since they are cited in the table and basically all figures, as well as in instances when we touch on each region.
-If you agree, let's delete them.
-Otherwise, we can put them right after Costa Rica / before "...
-By comparing these...".
--->
+In this study, we calculated and reported the first length-weight relationship for lionfish in the central Mexican Caribbean using previously collected *in situ* observations (n = 109; \citep{villaseorderbez_2014}).
+We then estimated lionfish weight in this area using previously published length-weight relationships for lionfish populations from ten locations across the Western Atlantic, Gulf of Mexico, and Caribbean.
+By comparing these weight estimates to our *in situ* length-weight observations, we showed that using *ex situ* parameter values resulted in up to a threefold under- or overestimation of lionfish weight.
 
@@
 We reviewed 12 published studies and obtained 17 length-weight relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7), and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}).
+Study sites included North Carolina, the Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
+Unfortunately, we have access only to the summarized information published in these studies - not the raw data used to make length-weight calculations.
 We collected information on sex differentiation, location, length and depth ranges, and sampling methods from each study when available.
-Only two studies reported parameters for each sex \citep{aguilarperera_2016,fogg_2013}, so we assumed data from both sexes were combined in a study if sex was unspecified.
+Only two studies reported sex-specific length-weight parameters \citep{aguilarperera_2016,fogg_2013}, so we assumed data were reported for both sexes combined in all other studies.
 Reviewed studies presented information for organisms ranging from `r min(review$tl_min, na.rm = T)`-`r max(review$tl_max, na.rm = T)` mm in Total Length ($TL$) and were obtained at depths between `r min(review$minD, na.rm = T)` m and `r max(review$maxD, na.rm = T)` m.
@@
 
-We also used data from 109 lionfish sampled by \citet{villaseorderbez_2014}, who used hand nets and numbered bottles to collect organisms from 10 sampling sites along the central Mexican Caribbean coast in the Summer of 2010 (Supplementary Table 1).
+We also used data from 109 lionfish sampled by \citet{villaseorderbez_2014}, who used hand nets and numbered bottles to collect Total Length (TL; mm) and Total Weight (TW; g) for organisms from 10 sampling sites along the central Mexican Caribbean coast in the Summer of 2010 (Supplementary Table 1).
 Sampling locations included wall and carpet reefs at depths between 5.7 m and 38.1 m.
 The use of hand nets prevented any weight loss due to bleeding and allowed better representation of small sizes by avoiding gear selectivity.
-Organisms were euthanized via pithing and Total Length (TL; mm) and Total Weight (TW; g) were recorded.
+Organisms were euthanized via pithing.
 
@@
 Coefficients were tested with a two-tailed Student's t-test, and the significance of the regression was corroborated with an F-test.
-
-Some of the reviewed studies inconsistently defined $a$ as either the ponderal index from Eq.
+Some of the reviewed studies (Table \ref{tab:all_params}, Fig \ref{fig:map}) inconsistently defined $a$ as either the ponderal index from Eq.
 \ref{eq:allometric} or the y-intercept from the linearized log-transformed equation.
@@
 We standardized each study by converting coefficients and report all parameters as TL (mm) to TW (g) conversions.
-Locations where allometric studies have been performed are shown in Figure \ref{fig:map} and summarized in Table \ref{tab:all_params}.
 
 We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here.
-Recall that the objective of this study is not to describe variations between populations, but rather to estimate how the use of *ex situ* parameters influences the accuracy of weight estimates for lionfish, using the central Mexican Caribbean as a case study.
+Recall that the objective of this study is not to describe variations between populations (which would require access to raw data), but rather to assess how *ex situ* parameter values influence the accuracy of weight estimates for lionfish, using the central Mexican Caribbean as a case study.
 Using each of the 18 parameter pairs, we estimated $TW$ from the $TL$ observations collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 mm to 310 mm) and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
@@
 Raw data and code used in this work are available on github at github.com/jcvdav/lionfish_biometry.
+
+<!-- I think we need to write the ANCOVA model as an equation and include it in the text - will make it seem more robust; check out these slides http://users.stat.umn.edu/~helwig/notes/acov-Notes.pdf -->
 
@@
 The length-weight relationship for organisms from the central Mexican Caribbean resulted in coefficient values of $a = `r a`$ and $b = `r bs`$ ($R^2 = `r Rsq`$, $F_{1, 107} = 6928.67; p < 0.001$).
-The allometric factor ($b$) was significantly different from $b = 3$ ($t_{107} = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$) corroborating that lionfish present allometric growth.
+The allometric factor ($b$) was significantly different from $b = 3$ ($t_{107} = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), corroborating that lionfish present allometric growth.
 The length-weight coefficients estimated here were within the range identified by studies from other regions (Table \ref{tab:all_params}).
 Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region.
+
+<!-- Careful: the e-06 is being printed for the a value in the manuscript -->
 
@@
 In contrast, the highest weight estimates came from the Western Atlantic with `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{barbour_2011}.
-To put this in context, true observed weights have a mean of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
+True observed weights had a mean of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
 Weights predicted from these extreme parameters correspond to predicted-to-observed weight ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
@@
 
-Tukey's *post-hoc* test suggests that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
+<!-- By "The largest under- and overestimations" in the paragraph above, do you mean the estimates at the far end of the size spectrum?
+I.e., the estimates for the lionfish with the longest TL?
+Need to clarify that.
+It's confusing how the ratio goes from 0.8 and 1.76 to 0.36 and 3.51 -->
+
+Tukey's *post-hoc* test suggested that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
 All weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher than observed values, and only parameters from the Caribbean produced weights smaller than observed (Fig \ref{fig:bio_ratio}).

### 2019-02-08 docs/Manuscript.Rmd
Manuscript feedback - no reviews yet

@@
 We might be inclined to attribute all variation in the lionfish length-weight relationship to the spatial origin of these parameters.
-However, samples from the 12 studies included here were not only collected in different locations, but also at different points in time and across different depth and size ranges (See Supplementary Table 2 for an extended version of Table 1 that incorporates these variables when available).
-While we could not evaluate how these factors influence previous estimates without the necessary raw data from every study, we still show that the lack of locally-calculated parameters can induce significant bias when calculating weight from length observations.
+However, samples from the 12 studies included here were not only collected in different locations, but also at different points in time and across different depth and size ranges (See Supplementary Table 2 for an extended version of Table 1).
+While we could not evaluate how these factors influenced length-weight estimates from previous studies without raw data, we still show that a lack of locally-calculated parameters can induce significant bias when calculating weight from length observations.
 The magnitude of the bias discovered in this study and our lack of understanding the sources driving spatial variation for lionfish highlights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and to link these findings to previously suggested environmental and genetic structures.
@@
 
-Applying parameters estimates to lengths outside the range of lengths originally used to estimate the parameters may also induce error.
+Applying parameter estimates to lengths outside the range of lengths originally used to estimate the parameters may also induce error.
 Our smallest observed organism was 34 mm in $TL$, and only two studies estimated parametrs with smaller organisms \citep{edwards_2014,sabidoitza_2016}.
-However, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (the next smallest maximum length was 325 mm; See Supplementary Table 2).
+By contrast, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (the next smallest maximum length was 325 mm; See Supplementary Table 2).
 Due to the power function describing the allometric relationship (*i.e.* Eq.
-1), the error is larger when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
+1), the error in weight estimates is larger when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
 
@@
 I think the central idea is that we do not extrapolate from other predictions, so we are safe in that sense.
+-->
+
+<!-- Looks good.
+There's one more thing that's really important for us to clarify - do we only make projections for lionfish up to 310 mm in size?
+Like, the threefold over/underestimation isn't for a hypothetical lionfish that's 500 mm TL or something, right?
+If so, we should tack on a sentence saying "we were conservative in our estimates in that we only used parameter pairs from other studies to estimate weights for lionfish up to 310mm in the Central Mexican Caribbean".
+Or something like that.
+Lmk if that makes sense.
 -->

### 2019-02-08 docs/Manuscript.tex
Manuscript feedback - no reviews yet

@@
 relationships for lionfish taken throughout their invasive range and
-found regional differences that led to significant under- and
-overestimation of weight estimates. The spatial pattern we observed is
-consistent with findings from other studies focused on genetics or
-length-at-age. We show that the use of \textit{ex situ} parameters can
-result in up to a threefold under- or overestimation of total weight,
-but using parameters from nearby regions substantially reduces this
-error. These findings can have implications for management in terms of
-predicting effects on local ecosystems, evaluating the effectiveness of
-removal programs, or estimating biomass available for harvest.
+found regional differences that led to significant misestimates when
+calculating weight from length observations. The spatial pattern we
+observed is consistent with findings from other studies focused on
+genetics or length-at-age. We show that the use of \textit{ex situ}
+parameters can result in up to a threefold under- or overestimation of
+total weight, but using parameters from nearby regions substantially
+reduces this error. These findings can have implications for management
+in terms of predicting effects on local ecosystems, evaluating the
+effectiveness of removal programs, or estimating biomass available for
+harvest.
 \end{abstract}
@@
 in the Western Atlantic Ocean and Caribbean Sea, likely introduced
-through release of aquarium-kept organisms \citep{betancurr_2011}. They
-are the first invasive marine vertebrates established along these coasts
-\citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence
-has been labeled as a major marine invasion because they threaten local
-biodiversity, spread rapidly, and are difficult to manage
-\citep{hixon_2016}. Lionfish have established invasive populations in
-coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic
-reefs
+through release of aquarium-kept organisms \citep{betancurr_2011}.
+Lionfish are the first invasive marine vertebrates established along
+these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}, and
+they have established invasive populations in coral reefs, estuaries,
+mangroves, hard-bottomed areas, and mesophotic reefs
 \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
+Their presence has been labeled as a major marine invasion because they
+threaten local biodiversity, spread rapidly, and are difficult to manage
+\citep{hixon_2016}.
 
 A substantial amount of research describes lionfish impacts throughout
-its invaded range. A meta-analysis by \citet{peake_2018} showed that
+their invaded range. A meta-analysis by \citet{peake_2018} showed that
 invasive lionfish prey on at least 167 different species across the
@@
 Outcomes of previous studies suggest lionfish are likely to exhibit
-spatial heterogeneity in the length-weight relationship for two main
-reasons. First, fish with sedentary behavior such as lionfish often
-exhibit high levels of spatial variation in important life history
-characteristics such as growth or natural mortality rates
-\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. In fact,
-culling programs are effective in reducing local adult populations
-largely because lionfish have high levels of site fidelity and small
-home ranges \citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}.
-Second, genetic analysis of lionfish suggests biological differences due
-to the existence of two genetically distinct invasive subpopulations
-between the Western Atlantic and the Caribbean \citep{betancurr_2011}.
-Site-specific studies that calculate the length-weight relationship of
-lionfish report variable estimates, and these differences may be
-increasingly important when estimating the potential effectiveness of
-lionfish culling programs
+spatial heterogeneity in the length-weight relationship for both
+behavioral and biological reasons. Important life history
+characteristics such as growth or natural mortality rates are often
+spatially variable for fish that exhibit sedentary behavior
+\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}, and in
+fact, high levels of site fidelity and small home ranges are two primary
+reasons why culling programs are effective in reducing local adult
+lionfish populations
+\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. Genetic
+analysis of lionfish also identified two genetically distinct invasive
+subpopulations between the Western Atlantic and the Caribbean,
+suggesting the existence of spatially explicit biological differences
+between populations as well \citep{betancurr_2011}. Site-specific
+studies that calculate the length-weight relationship of lionfish report
+variable estimates, and these differences may be increasingly important
+when estimating the potential effectiveness of lionfish culling programs
 \citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
@@
 length-weight relationship for lionfish in the central Mexican Caribbean
-(n = 109). We then estimated lionfish weight in this area using
-previously published length-weight relationships for lionfish
-populations in North Carolina, the Northern and Southern Gulf of Mexico,
-the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica,
-Bonaire, Puerto Rico, and Costa Rica. By comparing these weight
-estimates to the \emph{in situ} length-weight observations, we showed
-that using \emph{ex situ} parameter values resulted in up to a threefold
-under- or overestimation of lionfish weight.
+using previously collected \emph{in situ} observations (n = 109;
+\citep{villaseorderbez_2014}). We then estimated lionfish weight in this
+area using previously published length-weight relationships for lionfish
+populations from ten locations across the Western Atlantic, Gulf of
+Mexico, and Caribbean. By comparing these weight estimates to our
+\emph{in situ} length-weight observations, we showed that using \emph{ex
+situ} parameter values resulted in up to a threefold under- or
+overestimation of lionfish weight.
 
@@
 relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
-and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}). We
-collected information on sex differentiation, location, length and depth
-ranges, and sampling methods from each study when available. Only two
-studies reported parameters for each sex
-\citep{aguilarperera_2016,fogg_2013}, so we assumed data from both sexes
-were combined in a study if sex was unspecified. Reviewed studies
+and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}).
+Study sites included North Carolina, the Northern and Southern Gulf of
+Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman,
+Jamaica, Bonaire, Puerto Rico, and Costa Rica
+\citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
+Unfortunately, we have access only to the summarized information
+published in these studies - not the raw data used to make length-weight
+calculations. We collected information on sex differentiation, location,
+length and depth ranges, and sampling methods from each study when
+available. Only two studies reported sex-specific length-weight
+parameters \citep{aguilarperera_2016,fogg_2013}, so we assumed data were
+reported for both sexes combined in all other studies. Reviewed studies
 presented information for organisms ranging from 25-475 mm in Total
@@
 \citet{villaseorderbez_2014}, who used hand nets and numbered bottles to
-collect organisms from 10 sampling sites along the central Mexican
-Caribbean coast in the Summer of 2010 (Supplementary Table 1). Sampling
-locations included wall and carpet reefs at depths between 5.7 m and
-38.1 m. The use of hand nets prevented any weight loss due to bleeding
-and allowed better representation of small sizes by avoiding gear
-selectivity. Organisms were euthanized via pithing and Total Length (TL;
-mm) and Total Weight (TW; g) were recorded.
+collect Total Length (TL; mm) and Total Weight (TW; g) for organisms
+from 10 sampling sites along the central Mexican Caribbean coast in the
+Summer of 2010 (Supplementary Table 1). Sampling locations included wall
+and carpet reefs at depths between 5.7 m and 38.1 m. The use of hand
+nets prevented any weight loss due to bleeding and allowed better
+representation of small sizes by avoiding gear selectivity. Organisms
+were euthanized via pithing.
 
@@
 two-tailed Student's t-test, and the significance of the regression was
-corroborated with an F-test.
-
-Some of the reviewed studies inconsistently defined \(a\) as either the
-ponderal index from Eq. \ref{eq:allometric} or the y-intercept from the
-linearized log-transformed equation. Other studies incorrectly reported
-parameters as mm-to-g conversions when they were in fact cm-to-g
-conversions. We standardized each study by converting coefficients and
-report all parameters as TL (mm) to TW (g) conversions. Locations where
-allometric studies have been performed are shown in Figure \ref{fig:map}
-and summarized in Table \ref{tab:all_params}.
+corroborated with an F-test. Some of the reviewed studies (Table
+\ref{tab:all_params}, Fig \ref{fig:map}) inconsistently defined \(a\) as
+either the ponderal index from Eq. \ref{eq:allometric} or the
+y-intercept from the linearized log-transformed equation. Other studies
+incorrectly reported parameters as mm-to-g conversions when they were in
+fact cm-to-g conversions. We standardized each study by converting
+coefficients and report all parameters as TL (mm) to TW (g) conversions.
 
@@
 calculated here. Recall that the objective of this study is not to
-describe variations between populations, but rather to estimate how the
-use of \emph{ex situ} parameters influences the accuracy of weight
-estimates for lionfish, using the central Mexican Caribbean as a case
-study. Using each of the 18 parameter pairs, we estimated \(TW\) from
-the \(TL\) observations collected in the central Mexican Caribbean (n =
-109, with \(TL\) ranging from 34 mm to 310 mm) and divided predicted
-weights by known observed weights to obtain a simple measure of over- or
-underestimation. Difference in mean weight ratios were tested with an
-analysis of covariance (ANCOVA), where the sources of variation were the
-study and \(TL\). Ratios were logit-transformed prior to analysis, and a
+describe variations between populations (which would require access to
+raw data), but rather to assess how \emph{ex situ} parameter values
+influence the accuracy of weight estimates for lionfish, using the
+central Mexican Caribbean as a case study. Using each of the 18
+parameter pairs, we estimated \(TW\) from the \(TL\) observations
+collected in the central Mexican Caribbean (n = 109, with \(TL\) ranging
+from 34 mm to 310 mm) and divided predicted weights by known observed
+weights to obtain a simple measure of over- or underestimation.
+Difference in mean weight ratios were tested with an analysis of
+covariance (ANCOVA), where the sources of variation were the study and
+\(TL\). Ratios were logit-transformed prior to analysis, and a
 \emph{post-hoc} Tukey's test was used to identify groups where mean
@@
 \toprule
-Region & Sex & n & a & b & $R^2$ & Reference\\
+Region & Sex & n & a & b & \$R\textasciicircum{}2\$ & Reference\\
 \midrule
-Western Atlantic & B & 774 & 2.90 & 2.89 & - & Barbour et al., 2011\\
+Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
 Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
@@
 GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
-Caribbean & B & 458 & 3.60 & 2.81 & - & Sandel et al., 2015\\
+Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
 \addlinespace
-Caribbean & B & 419 & 2.80 & 2.85 & 0.87 & Chin et al., 2016\\
-Caribbean & B & 1450 & 2.30 & 2.89 & 0.92 & de Leon et al., 2013\\
-Caribbean & B & 1887 & 0.30 & 3.24 & 0.97 & Edwards et al., 2014\\
+Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
+Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
+Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
 Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
-Caribbean & B & 227 & 0.80 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
+Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
 \addlinespace
@@
 The allometric factor (\(b\)) was significantly different from \(b = 3\)
-(\(t_{107} = 6.04; p<0.001\)) corroborating that lionfish present
+(\(t_{107} = 6.04; p<0.001\)), corroborating that lionfish present
 allometric growth. The length-weight coefficients estimated here were
@@
 highest weight estimates came from the Western Atlantic with 73.76
-\(\pm\) 96.11 g \citep{barbour_2011}. To put this in context, true
-observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weights predicted
-from these extreme parameters correspond to predicted-to-observed weight
-ratios of 0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD),
-respectively. The largest under- and overestimations resulted in ratios
-of 0.36 and 3.51 of the actual observed weight, indicating that \emph{ex
-situ} parameters can result in highly erroneous weight estimates.
+\(\pm\) 96.11 g \citep{barbour_2011}. True observed weights had a mean
+of 52.56 \(\pm\) 76.58 g. Weights predicted from these extreme
+parameters correspond to predicted-to-observed weight ratios of 0.80
+\(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively. The
+largest under- and overestimations resulted in ratios of 0.36 and 3.51
+of the actual observed weight, indicating that \emph{ex situ} parameters
+can result in highly erroneous weight estimates.
 
-Tukey's \emph{post-hoc} test suggests that weight ratios for the central
-Mexican Caribbean were not different from those obtained with parameters
-from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico
-(Tukey's HSD \(p > 0.05\)). All weight estimates using parameters from
-the Gulf of Mexico and Western Atlantic were higher than observed
-values, and only parameters from the Caribbean produced weights smaller
-than observed (Fig \ref{fig:bio_ratio}). The regional average (\(\pm\)
-SD) of predicted-to-observed weight ratios from these three regions were
-1.24 \(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\) 0.423 for the
-Gulf of Mexico, Western Atlantic, and Caribbean, respectively. This
-suggests that the smallest errors are observed when using parameters
-from other locations in the Caribbean. Predicted-to-observed weight
-ratios are presented in Figure \ref{fig:bio_ratio}.
+Tukey's \emph{post-hoc} test suggested that weight ratios for the
+central Mexican Caribbean were not different from those obtained with
+parameters from Little Cayman, the Bahamas, and some sites in the Gulf
+of Mexico (Tukey's HSD \(p > 0.05\)). All weight estimates using
+parameters from the Gulf of Mexico and Western Atlantic were higher than
+observed values, and only parameters from the Caribbean produced weights
+smaller than observed (Fig \ref{fig:bio_ratio}). The regional average
+(\(\pm\) SD) of predicted-to-observed weight ratios from these three
+regions were 1.24 \(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\)
+0.423 for the Gulf of Mexico, Western Atlantic, and Caribbean,
+respectively. This suggests that the smallest errors are observed when
+using parameters from other locations in the Caribbean.
+Predicted-to-observed weight ratios are presented in Figure
+\ref{fig:bio_ratio}.
 
@@
 and across different depth and size ranges (See Supplementary Table 2
-for an extended version of Table 1 that incorporates these variables
-when available). While we could not evaluate how these factors influence
-previous estimates without the necessary raw data from every study, we
-still show that the lack of locally-calculated parameters can induce
-significant bias when calculating weight from length observations. The
-magnitude of the bias discovered in this study and our lack of
-understanding the sources driving spatial variation for lionfish
-highlights the need to simultaneously collect length-weight information
-across the invaded range to test for spatially-induced patterns and to
-link these findings to previously suggested environmental and genetic
-structures. Such an endeavor would provide insight into lionfish biology
-and better inform management.
+for an extended version of Table 1). While we could not evaluate how
+these factors influenced length-weight estimates from previous studies
+without raw data, we still show that a lack of locally-calculated
+parameters can induce significant bias when calculating weight from
+length observations. The magnitude of the bias discovered in this study
+and our lack of understanding the sources driving spatial variation for
+lionfish highlights the need to simultaneously collect length-weight
+information across the invaded range to test for spatially-induced
+patterns and to link these findings to previously suggested
+environmental and genetic structures. Such an endeavor would provide
+insight into lionfish biology and better inform management.
 
-Applying parameters estimates to lengths outside the range of lengths
+Applying parameter estimates to lengths outside the range of lengths
 originally used to estimate the parameters may also induce error. Our
@@
 estimated parametrs with smaller organisms
-\citep{edwards_2014,sabidoitza_2016}. However, our largest organism had
-a \(TL\) of 310 mm, which is well within the range of all other studies
-(the next smallest maximum length was 325 mm; See Supplementary Table
-2). Due to the power function describing the allometric relationship
-(\emph{i.e.} Eq. 1), the error is larger when extrapolation is done for
-lengths that are larger than the maximum length used to estimate the
-parameters.
+\citep{edwards_2014,sabidoitza_2016}. By contrast, our largest organism
+had a \(TL\) of 310 mm, which is well within the range of all other
+studies (the next smallest maximum length was 325 mm; See Supplementary
+Table 2). Due to the power function describing the allometric
+relationship (\emph{i.e.} Eq. 1), the error in weight estimates is
+larger when extrapolation is done for lengths that are larger than the
+maximum length used to estimate the parameters.
 

### 2019-02-08 docs/Manuscript.Rmd
One more manuscript change

@@
 
-There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$).
+There were significant differences in our predicted weight **RATIOS?**s for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$).
 The lowest weight estimates for the observed lengths resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{sabidoitz_2016}.
@@
 Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
+
+<!-- I think we need to explicitly say which results are referring to our ANCOVA outputs - it's the weight ratios at the beginning of the second paragraph in results, right?
+I.e., just say "ANCOVA results show that There were significant differences in our predicted weight **RATIOS?**s for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$)."  Then I think we should put the in-text reference to the violin plot right after that (provides a clear/concise link of here are our ANCOVA results; here's the plot showing them.) -->
 

### 2019-02-08 docs/Manuscript.tex
Complete SF feedback for manuscript and reviews

@@
 
-There were significant differences in our predicted weights for the
-central Mexican Caribbean when using each of the different pairs of
-parameters (\(F_{17, 1943} = 24.96; p < 0.001\)). The lowest weight
-estimates for the observed lengths resulted from using the allometric
-parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
-of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
-highest weight estimates came from the Western Atlantic with 73.76
-\(\pm\) 96.11 g \citep{barbour_2011}. True observed weights had a mean
-of 52.56 \(\pm\) 76.58 g. Weights predicted from these extreme
-parameters correspond to predicted-to-observed weight ratios of 0.80
-\(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively. The
-largest under- and overestimations resulted in ratios of 0.36 and 3.51
-of the actual observed weight, indicating that \emph{ex situ} parameters
-can result in highly erroneous weight estimates.
+There were significant differences in our predicted weight
+\textbf{RATIOS?}s for the central Mexican Caribbean when using each of
+the different pairs of parameters (\(F_{17, 1943} = 24.96; p < 0.001\)).
+The lowest weight estimates for the observed lengths resulted from using
+the allometric parameters from Banco Chinchorro in the Caribbean, with
+mean \(\pm\) SD of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In
+contrast, the highest weight estimates came from the Western Atlantic
+with 73.76 \(\pm\) 96.11 g \citep{barbour_2011}. True observed weights
+had a mean of 52.56 \(\pm\) 76.58 g. Weights predicted from these
+extreme parameters correspond to predicted-to-observed weight ratios of
+0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.
+The largest under- and overestimations resulted in ratios of 0.36 and
+3.51 of the actual observed weight, indicating that \emph{ex situ}
+parameters can result in highly erroneous weight estimates.
 

### 2019-02-08 docs/reviews.Rmd
Complete SF feedback for manuscript and reviews

@@
 We appreciate the professional way in which our manuscript has been handled.
-Here we address the issues, suggestions, and comments raised by you and the reviewers.
-We include the original comment in plain text, and our responses in italics.
+Here we address each issue, suggestion, and comment raised by yourself and both reviewers.
+We include the original comment in plain text, and present our responses in italics.
 
@@
 
+*We have improved our word choice throughout the manuscript, and addressed each specific comment or question below.*
+
 L 19: Using the word “major” is a subjective word and elicits an emotional response usually in those that read it.
@@
 
-*We have changed the word from "major" to "substantial" in L19 and L142 (now L139) and "fundamental" in L175 (now L193).*
+*We have changed the word from "major" to "substantial" in L19 and L142 (now L139) and "key" in L175 (now L193).
+We chose to keep the word "major" in L26 to maintain consistency with the authors' original wording.*
 
@@
 
-*"Western" is now capitalized.*
+*We now capitalize "Western" and inserted "Ocean" after "Atlantic".*
 
@@
 
-*"liberation" has been replaced with "release"*
+*We replaced "liberation" with "release"*
 
@@
 
-*The text now states the research was performed in the Bahamas.*
+*The text now correctly states the research was performed in the Bahamas.*
 
@@
 
-*This has been fixed, now in L62.*
+*We have improved the wording in the original sentence and no longer use the word "know"/"known".*
 
@@
 
-*Figure 1 has been updated to show the appropriate label. Likewise we have standardized all references to this region as "Western Atlantic".*
+*Figure 1 has been updated to show the appropriate label. Likewise we have standardized all references to this region as the "Western Atlantic".*
 
@@
 
-*We have modified all instances and use "g" to refer to grams throughout the text.*
+*We have changed all instances of "gr" to "g" to refer to grams throughout the text.*
 
@@
 
-*We have modified this so it reads "with T L ranging from 34 mm to 310 mm" in what is now L120.*
+*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120.*
 
@@
 
+<!-- OK I actually think this is still a very confusing paragraph.
+It still feels unclear what means +/- SDs we're reporting.
+Perhaps something like this will clarify: "There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters (F17;1943 = 24:96; p < 0:001).
+For example, the actual observed weights of the 109 lionfish from the Central Mexican Caribbean had a mean +/- SD of 52.56 +/- 76.58 g.
+However, if we used allometric parameter values from Banco Chinchorro in the Caribbean to predict weights from our observed length observations, we estimated a mean +/ SD of 40.37  58.74 g (Sabido-Itza´ et al., 2016).
+If we similarly used parameter values from NORTH CAROLINA (?) to estimate lionfish weights in the Central Mexican Caribbean, we found a mean +/- SD of 73.76  96.11 g (Barbour et al., 2011).
+These were the two most extreme sets of parameters, but results consistently varied across sites.
+Weights predicted from these extreme parameters corresponded to predicted-to-observed weight ratios of 0.80  0.19 and 1.76  0.50 (mean  SD), respectively, and the under- and overestimations FOR LIONFISH THAT WERE 310 MM IN TL (the maximum TL in this study) (??) resulted in ratios of 0.36 and 3.51 of the actual observed weight.
+Ex situ parameter use can therefore result in highly erroneous weight estimates for lionfish.
+-->
+
 - Fig. 3. Why are there two solid light green lines for the Sabido-Itza et al. 2016b? IN the legend for sex make sure that there are two dashed lines for female not just one short dashed line.
@@
 
+<!-- You gotta tell me how to pronouce Xcalak -->
 ### Discussion:
@@
 
-*Yes, we refer to the spatial heterogeneity. We have modified the text so it reads "...is spatially heterogeneous and relevant for management of the invasion."*
+*Yes, we refer to the spatial heterogeneity.
+We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and..."*
 
@@
 *Other studies do not report the time of the year when these were collected.
-However, we recognize this is an important factor influencing length-weight relationships.
+However, we recognize this may be a factor that influences weight or growth and therefore the length-weight relationship.
 We have mentioned that our parameters for the Central Mexican Caribbean are from organisms collected during the Summer (L94), and have devoted a paragraph in the discussion (L175) to highlight the importance of collection methods and timing when estimating length-weight relationships.*
@@
 
-*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and data from Fogg et al.
+*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and as you noted data from Fogg et al.
 (2013) produced some of the largest estimates.
@@
 Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*
+
+<!-- I don't think you satisfactorily answered this one - you kind of skirted the reviewer's question of how you adjusted for spineless weight (the answer is we didn't, right?).
+Don't think you can get away with just saying "The corresponding modifications have been made in the text." -->
 
@@
 
-*As stated above, we have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L175).
-We must clarify, however, that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2).
-The fact that similar comments were raised by Rev2 suggests that the text needed further clarification from our side.
-The objective of our study is not to describe the biological differences in length-weight relationships, but to estimate the effect that using ex situ parameter has and determine if this results in large errors.*
+*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L175).*
 
-*We agree, however, that to estimate the "location effect" of the length-weight relationship, these should be modeled as a random effect.
-The GLMM would not only identify if differences exist, but also tell us the magnitude of these differences.
-This is a common approach in population biology and would in fact identify the random effect of the location in shaping the length-weight relationship.
-However, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data.
-We believe that after modifying the text to clearly state our objectives and including a discussion paragraph about this, we have addressed this concern.*
+*In terms of the OLS regression versus a mixed modeling approach: in our original manuscript we failed to clearly articulate that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2).
+We agree that a GLMM with location modeled as a random effect would properly estimate the "location effect" of the length-weight relationship across the different study sites, both by identifying whether differences exist and by describing the magnitude of these differences.
+Unfortunately, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data - both of which were outside the scope of this study.
+The fact that similar comments were raised by Rev2 suggests that we did not adequately describe this limitation in our original manuscript.
+We now explicitly state that we did not have access to the raw data from the published studies (LINES).
+However, it is important to note that the objective of our study was not to describe the biological differences in length-weight relationships between site locations, rather to assess the effect of using ex situ vs.
+in situ parameter values to estimate lionfish weights from direct length observations (i.e., to assess whether ex situ parameter values result in large errors in weight estimates).
+We believe that after modifying the text to clearly state our objectives (LINES - WE MENTION RAW DATA A FEW TIMES NOW, SO INCLUDE EVERY INSTANCE SO IT LOOKS LIKE WE WERE REALLY THOROUGH) and including a discussion paragraph about the limitations of our study (LINES), we have satisfactorily addressed these concerns.*
 
@@
 
-*We now use the word "fundamental".*
+*We now use the word "key".*
 
@@
 
+*We appreciate and agree with your feedback - it greatly helped us improve the manuscript.*
+
 The authors don’t compare the weight-length relationships statistically; instead they compare mean ratios of predicted to observed weight when the estimated parameters from each different study are applied to the range of body lengths they collected in their central Mexican regional study.
@@
 
-*We agree with the comments raised above and answer the two main points here.*
+*We agree with the comments raised above and answer the two main points below*
 
@@
 Our results remain the same: using ex-situ parameters produces significantly different weight estimates.
-In fact, our post hoc test identifies even more groupings, suggesting that our previous attempt underestimated the differences.*
+In fact, our post hoc test identifies even more groupings, suggesting that our previous attempt underestimated the differences in weight estimates.*
 
 Second, the parameter estimates from other studies are being applied to lengths of fish outside of the range of lengths that were used to generate the parameters.
+
+*The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters.
+We have included a paragraph in the discussion that touches on this (L 185).*
+<!-- Be more specific than "touches on this" - quote exactly what you wrote to alleviate the reviewer's concerns -->
+
+<!-- Also I think I said "you" a lot instead of "the reviewer" - my bad.  Change it to whatever you want, but make it consistent -->
+
 ANCOVA is the most powerful approach for comparing multiple linear relationships, as it specifically accounts for variation in the covariate (total length) among groups.
@@
 
-*The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters.
-We have included a paragraph in the discussion that touches on this (L 185).*
-
-*As for the use of ANCOVA, this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates.
+*In terms of ANCOVA use: this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates.
 As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations.
@@
 In a sense, we would be asking if the lines in Fig 3 (with no variation around them) have significantly different slopes and intercepts.
-As mentioned in the response to R1, we have included a discussion paragraph (L175) highlighting this.*
+As mentioned in the response to R1, we originally failed to clearly state that we do not have the raw data required to perform such an analysis.
+We have included statements in the methods (LINES) and a discussion paragraph (L175) that highlight these limitations and clarify our objectives/analyses.*
+<!-- General point - never use the word "this" to end a sentence - you always want to follow "this" with another word (e.g., "highlighting this topic" instead of "highlighting this") -->
 
@@
 
-*We have included all the information we collected from other studies in a supplementary table (Supplementary Table 2), an extension of Table 2, where other relevant variables are mentioned.
-Table 2 is now Table 1 after removing the regression table.*
+*Again, this is similar to a concern raised by Rev1 and we agree this information should have been included.
+We collected all the information possible from other studies and included it in a supplementary table (Supplementary Table 2), an extension of Table 2 (which is now Table 1 after removing the regression table), where other relevant variables are mentioned.*
 
@@
 *We have included the log-log version of Figure 3 in the appendices as Supplementary Figure 1. We reference such figure in the caption to Figure 3.*
-
+<!-- Don't you think we should include the Central Mexican Caribbean in Fig 3 and Fig S1? -->
 Figure 3, showing the untransformed data, should be amended so that each fitted curve extends across the range of total lengths specific to that study.
@@
 now explicitly mention these issues.
-And while we can not test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*
+And while we cannot test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*
 <!-- modification in which lines? -->
+<!-- Alright we gotta do a better job on this one - s/he says this is THE area for major improvement.
+I think the text is mostly there in the manuscript now, but we need to specifically answer each of the questions the reviewer asks, preferably while quoting the text as well -->
 
@@
 
-*We have modified the abstract to include both suggestions.*
+*We have modified the abstract to include both suggestions (the assumption is correct that the ANCOVA detected significant differences in predicted weight values).*
 
@@
 We believe that the Supplementary Table 2 now addresses this and makes all the reviewed information available to future readers.*
-
+<!-- I don't understand the logic in the first sentence - why does collecting them elimiate gear selectivity concerns? -->
 5.
@@
 This is clear from equations (1) and (2), in fact, the log-transformation of this power function is standard enough that equation (2) does not likely need to appear in the manuscript, instead simply state the function was linearized using log-transformation.
-
+<!-- Maybe this reviewer would disagree with my idea to add the ANCOVA equation... What do you think? -->
 *We have modified the text and now only include Eq 1.*
@@
 Related to this, only include information on the weight-length relationship from the central Mexican coast in the text that is not already presented in Figure 2; there is no need to include it in two places.
-
+<!-- Ok well given this, I guess also ignore my comment that I thought we should include this study in Fig 3 and S1 -->
 *We agree, and have now removed Table 1.*
@@
 Reporting the range in mean ratios would be sufficient along with an illustrative figure.
-
+<!-- Already commented on this in the manuscript - but are those extremes (.36 and 3.51) for lionfish that are length 310 mm? Need to be clear about that -->
 *That is correct, the 0.80 and 1.76 values make reference to the mean ratios.
-We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51.
-We believe the new text now justifies including these extremes.*
+We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51 - especially because we are unable to assess the full length-weight relationships from all studies given our lack of raw data.
+We believe the new text justifies including these extremes.*
 
@@
 Change Fit to R2 in the Table heading, so it doesn’t need to be defined in the caption.
-
+<!-- I can't knit for some reason, so I can't tell if this was done but I assume you took care of it.  Also isn't it b, not c? -->
 *We have removed parameter c from Table 2 (Now Table 1) and modified the header so it has $R^2$.*
@@
 
-*Figure 3 shows a total of 18 lines. This is because from the 12 reviewed papers, a total of 17 relationships were identified. The additional relationship is the one estimated in this study.*
+*Figure 3 shows a total of 18 lines.
+This is because from the 12 reviewed papers, a total of 17 relationships were identified BECAUSE OF SEX-SPECIFIC REPORTING AND SOME STUDIES REPORTING MULTIPLE LOCATIONS??
+(if so, say that).
+The additional relationship is the one estimated in this study.*
+
+<!-- Oh wait - you do include this study in Fig 3 - so ignore BOTH of my previous comments haha- but the line for this study needs to be in the figure legend! -->

### 2019-02-09 docs/Manuscript.Rmd
Complete SF feedback for manuscript and reviews
Added comments by Sean, and new figure

--- 2019-02-08 docs/Manuscript.Rmd
@@
 The spatial pattern we observed is consistent with findings from other studies focused on genetics or length-at-age.
-We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight, but using parameters from nearby regions substantially reduces this error.
+We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight for an individual organism.
+When estimating total biomass, the use of other parameters may produce estimates between 76.2% and 140% of true observed biomass.
 These findings can have implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
-# I'm not sure I like the word "misestimates" but I want to avoid repeating the phrase "under- or overestimation" twice in the abstract; if you can come up with something that sounds better, go for it.
 keywords:
@@
     template: peerj_template.tex
-header-includes:
-   - \usepackage{float}
-   - \floatplacement{figure}{H}
-   - \restylefloat{table}
 ---
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 5.5)
+knitr::opts_chunk$set(echo = F,
+                      warning = F,
+                      message = F,
+                      fig.width = 5.5,
+                      fig.pos = "H")
 
@@
 Lionfish are the first invasive marine vertebrates established along these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}, and they have established invasive populations in coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic reefs \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
-Their presence has been labeled as a major marine invasion because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
+Their presence has been labeled as a "major marine invasion" because they threaten local biodiversity, spread rapidly, and are difficult to manage \citep{hixon_2016}.
 
@@
 Study sites included North Carolina, the Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
-Unfortunately, we have access only to the summarized information published in these studies - not the raw data used to make length-weight calculations.
+We have access only to the summarized information published in these studies - not the raw data authors used to make length-weight calculations.
 We collected information on sex differentiation, location, length and depth ranges, and sampling methods from each study when available.
@@
 Organisms were euthanized via pithing.
-
-\clearpage
 
@@
 
-We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here.
+We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here (Fig \ref{fig:all_allo}).
 Recall that the objective of this study is not to describe variations between populations (which would require access to raw data), but rather to assess how *ex situ* parameter values influence the accuracy of weight estimates for lionfish, using the central Mexican Caribbean as a case study.
 Using each of the 18 parameter pairs, we estimated $TW$ from the $TL$ observations collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 mm to 310 mm) and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios were tested with an analysis of covariance (ANCOVA), where the sources of variation were the study and $TL$.
+Difference in mean weight ratios were tested with an analysis of covariance (ANCOVA):
+
+\begin{equation}
+R_{i,j} = \tilde{\mu} + \alpha_j + \beta TL_{ij} + e_{ij}
+\end{equation}
+
+\clearpage
+
+Where $R_{ij}$ is the weight ratio for the $i$-th organism obtained with parameters from the $j$-th study, $\tilde{\mu}$ is a constant for all individuals, $a_j$ is the treatment effect (*i.e.* the difference induced by each study), $TL_{ij}$ is the covariate (*i.e.* Total Length) for the $i$-th subject in the $j$-th group with slope $\beta$, and $e_{ij}$ is the error term of the regression.
 Ratios were logit-transformed prior to analysis, and a *post-hoc* Tukey's test was used to identify groups where mean ratios did not differ.
@@
 Raw data and code used in this work are available on github at github.com/jcvdav/lionfish_biometry.
-
-<!-- I think we need to write the ANCOVA model as an equation and include it in the text - will make it seem more robust; check out these slides http://users.stat.umn.edu/~helwig/notes/acov-Notes.pdf -->
 
@@
 All parameters have been adjusted to convert from millimeters to grams.
-n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\\times 10^{-5}$), b = exponent.")
+n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\\times 10^{-5}$), b = exponent.") %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```
@@
 
-anova <- aov(Biomass_ratio ~ Study_id, data = Predicted_biomass)
+# anova <- aov(Biomass_ratio ~ Study_id, data = Predicted_biomass)
 ancova <- aov(logit_biomass_ratio ~ Study_id + Length, data = Predicted_biomass)
@@
 
+\clearpage
+
 \section*{Results}
 
-The length-weight relationship for organisms from the central Mexican Caribbean resulted in coefficient values of $a = `r a`$ and $b = `r bs`$ ($R^2 = `r Rsq`$, $F_{1, 107} = 6928.67; p < 0.001$).
+The length-weight relationship for organisms from the central Mexican Caribbean (\ref{fig:l-w-carib}) resulted in coefficient values of $a = 3.205 \times 10^{-6}$ and $b = `r bs`$ ($R^2 = `r Rsq`$, $F_{1, 107} = 6928.67; p < 0.001$).
 The allometric factor ($b$) was significantly different from $b = 3$ ($t_{107} = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), corroborating that lionfish present allometric growth.
 The length-weight coefficients estimated here were within the range identified by studies from other regions (Table \ref{tab:all_params}).
-Figure \ref{fig:l-w-carib} shows the relationship between TL and TW for this region.
-
-<!-- Careful: the e-06 is being printed for the a value in the manuscript -->
 
@@
   theme(text=element_text(family = "Times")) +
-  geom_smooth(method = "lm", formula = y ~ I(c*x^b), se = F, color = "black", linetype = "dashed") +
+  geom_smooth(method = "lm", formula = y ~ I(c*x^b),
+              se = F,
+              color = "black",
+              linetype = "dashed") +
   annotate(geom = "text",
@@
 
-```{r fit1,  fig.height = 3.5, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
+```{r fit1, fig.height = 3.2, fig.pos = "H", fig.cap = "\\label{fig:l-w-carib}Length-weight relationship for 109 lionfish sampled in the central Mexican Caribbean.
 Points indicate samples, dashed black line indicates curve of best fit, marginal plots represent the density distribution of each variable."}
@@
 
-```{r, results = "asis", eval = F}
-stargazer(model,
-          dep.var.caption = "$log_{10}(TW)$",
-          dep.var.labels.include = F,
-          header = F,
-          se = list(robust_se),
-          type = "latex",
-          t.auto = T,
-          p.auto = T,
-          intercept.bottom = F,
-          single.row = T,
-          report = "vcs*",
-          omit.stat = c("f", "rsq"),
-          add.lines = list(f_string),
-          covariate.labels = c("c", "b"),
-          dep.var.labels = "log10(TW)", title = "\\label{tab:reg_table}Coefficients of the linear model fit to Eq 1. Numbers in parenthesees represent heteroskedastic-robust standard errors.")
-```
-
-There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$).
-The lowest weight estimates for the observed lengths resulted from using the allometric parameters from Banco Chinchorro in the Caribbean, with mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{sabidoitz_2016}.
-In contrast, the highest weight estimates came from the Western Atlantic with `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{barbour_2011}.
-True observed weights had a mean of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
-Weights predicted from these extreme parameters correspond to predicted-to-observed weight ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
-The largest under- and overestimations resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` of the actual observed weight, indicating that *ex situ* parameters can result in highly erroneous weight estimates.
-
-<!-- By "The largest under- and overestimations" in the paragraph above, do you mean the estimates at the far end of the size spectrum?
-I.e., the estimates for the lionfish with the longest TL?
-Need to clarify that.
-It's confusing how the ratio goes from 0.8 and 1.76 to 0.36 and 3.51 -->
+ANCOVA results show that there were significant differences in our predicted weight ratios for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$; Fig \ref{fig:bio_ratio}).
+For example, the actual observed weights of the 109 lionfish from the Central Mexican Caribbean had a mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
+However, if we used allometric parameter values from Banco Chinchorro in the Caribbean to predict weights from our observed length observations, we estimated a mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{sabidoitz_2016}.
+If we similarly used parameter values from North Carolina in the Western Atlantic to estimate lionfish weights in the Central Mexican Caribbean, we found a mean $\pm$ SD `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{barbour_2011}.
+Weights predicted from these extreme parameters correspond to mean predicted-to-observed weight ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
+Furthermore, for individual organisms, the largest differences between predicted and observed values resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` (*i.e.* the tails of each violin in Fig \ref{fig:bio_ratio}).
+If instead of looking at the mean ratios we looked at the total biomass (*i.e.* summing across organisms), these cases would lead to estimated total biomasses of 76.2% (4,363.53 g) and 140% (8,039.96 g) of true observed biomass (5,729.34 g).
+These were the two most extreme sets of parameters, but results consistently varie Use of *ex situ* parameters can result in erroneous weight and total biomass estimates for lionfish.
 
@@
 This suggests that the smallest errors are observed when using parameters from other locations in the Caribbean.
-Predicted-to-observed weight ratios are presented in Figure \ref{fig:bio_ratio}.
 
@@
   ggplot(aes(x = Study, y = Biomass_ratio, group = Study_id)) +
-  geom_violin(aes(fill = Region), alpha = 0.8) +
+  geom_violin(aes(fill = Region),
+              alpha = 0.8,
+              color = "black") +
   stat_summary(geom = "point",
@@
         axis.title = element_text(size = 12)) +
-  geom_text(aes(y = 3.5, label = groups), family = "Times", fontface = "plain") +
+  geom_text(aes(y = 3.6, label = groups), family = "Times", fontface = "plain") +
   scale_y_continuous(limits = c(NA, 3.7)) +
@@
 ```{r pred_obs, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
+Sex is indicated in parentheses.
 Blue circles indicate median values and like letters indicate values that do not differ significantly.
@@
 fig_bio_ratio
+```
+
+```{r, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:errors}Estimated total biomas relative to observed biomass (5,729.34 g) for 18 pairs of allometric parameters.
+Sex is indicated in parentheses.
+For Sabido-Itza et al, 2016b, BC and PNAX make reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites for which they report parameters."}
+errors <- Predicted_biomass %>% 
+  mutate(Study = paste0(Study, " (", Gender_site, ")"),
+         Region = case_when(Region == "Western Atlantic" ~ "WA",
+                            Region == "Caribbean" ~ "Ca",
+                            T ~ "GoM")) %>% 
+  group_by(Region, Study) %>%
+  summarize(Wp = sum(pWeight),
+            W = sum(Weight)) %>%
+  ungroup() %>% 
+  mutate(error = Wp / W)  %>% 
+  transform(Study = reorder(Study, -error)) %>%
+  select(-W) %>%
+  ggplot(aes(x = Study, y = error)) +
+  geom_col(aes(fill = Region),
+           alpha = 0.8,
+           color = "black") +
+  coord_flip() +
+  geom_hline(yintercept = 1, linetype = "dashed") +
+  labs(y = "Total biomass relative to observed", x = "") +
+  theme_cowplot() +
+  theme(text = element_text(family = "Times")) +
+  scale_fill_brewer(palette = "Set1") +
+  theme(text = element_text(family = "Times"),
+        legend.position = "top",
+        legend.text = element_text(size = 10),
+        legend.background = element_rect(fill = "transparent"),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12)) +
+  guides(fill = guide_legend(title.position = "top")) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
+                     expand = c(0,0))
+
+errors
 ```
@@
 1), the error in weight estimates is larger when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.
-
-<!-- I modified the paragraph above a bit, and think its a bit more clear, but please change it if you think there are better ways to explain it.
-I think the central idea is that we do not extrapolate from other predictions, so we are safe in that sense.
--->
-
-<!-- Looks good.
-There's one more thing that's really important for us to clarify - do we only make projections for lionfish up to 310 mm in size?
-Like, the threefold over/underestimation isn't for a hypothetical lionfish that's 500 mm TL or something, right?
-If so, we should tack on a sentence saying "we were conservative in our estimates in that we only used parameter pairs from other studies to estimate weights for lionfish up to 310mm in the Central Mexican Caribbean".
-Or something like that.
-Lmk if that makes sense.
--->
+Our estimates are therefore conservative because we only used parameter pairs from other studies to estimate weights for lionfish up to 310 mm in the Central Mexican Caribbean, well within the range of lengths for which other parameters were estimated.
 
@@
 Their results show that using different parameters caused up to a four-year difference in the time required for the simulated lionfish population to recover to 90% of its initial biomass after removals ceased.
-Here, we show that using one set of length-weight parameters versus another for a given length can result in more than a threefold under- or overestimation of total weight.
+Here, we show that using one set of length-weight parameters versus another for a given length can result in more than a threefold under- or overestimation of total weight for individual fish, and that total biomass estimates may range between 76% and 140% of true observed biomass.
 These differences become especially important when allocating resources for lionfish removal programs, incentivizing lionfish fisheries as a source of alternative livelihoods, or estimating ecosystem impacts.

### 2019-02-09 docs/Manuscript.tex
Added comments by Sean, and new figure

--- 2019-02-08 docs/Manuscript.tex
@@
 
+\usepackage{float}
+\floatplacement{figure}{H}
 \title{Spatial variation in allometric growth of invasive lionfish has
@@
 parameters can result in up to a threefold under- or overestimation of
-total weight, but using parameters from nearby regions substantially
-reduces this error. These findings can have implications for management
-in terms of predicting effects on local ecosystems, evaluating the
-effectiveness of removal programs, or estimating biomass available for
-harvest.
+total weight for an individual organism. When estimating total biomass,
+the use of other parameters may produce estimates between 76.2\% and
+140\% of true observed biomass. These findings can have implications for
+management in terms of predicting effects on local ecosystems,
+evaluating the effectiveness of removal programs, or estimating biomass
+available for harvest.
 \end{abstract}
@@
 \citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
-Their presence has been labeled as a major marine invasion because they
-threaten local biodiversity, spread rapidly, and are difficult to manage
-\citep{hixon_2016}.
+Their presence has been labeled as a ``major marine invasion'' because
+they threaten local biodiversity, spread rapidly, and are difficult to
+manage \citep{hixon_2016}.
 
@@
 \citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
-Unfortunately, we have access only to the summarized information
-published in these studies - not the raw data used to make length-weight
+We have access only to the summarized information published in these
+studies - not the raw data authors used to make length-weight
 calculations. We collected information on sex differentiation, location,
@@
 were euthanized via pithing.
-
-\clearpage
 
@@
 parameters extracted from the literature and the additional pair
-calculated here. Recall that the objective of this study is not to
-describe variations between populations (which would require access to
-raw data), but rather to assess how \emph{ex situ} parameter values
-influence the accuracy of weight estimates for lionfish, using the
-central Mexican Caribbean as a case study. Using each of the 18
-parameter pairs, we estimated \(TW\) from the \(TL\) observations
-collected in the central Mexican Caribbean (n = 109, with \(TL\) ranging
-from 34 mm to 310 mm) and divided predicted weights by known observed
-weights to obtain a simple measure of over- or underestimation.
-Difference in mean weight ratios were tested with an analysis of
-covariance (ANCOVA), where the sources of variation were the study and
-\(TL\). Ratios were logit-transformed prior to analysis, and a
+calculated here (Fig \ref{fig:all_allo}). Recall that the objective of
+this study is not to describe variations between populations (which
+would require access to raw data), but rather to assess how \emph{ex
+situ} parameter values influence the accuracy of weight estimates for
+lionfish, using the central Mexican Caribbean as a case study. Using
+each of the 18 parameter pairs, we estimated \(TW\) from the \(TL\)
+observations collected in the central Mexican Caribbean (n = 109, with
+\(TL\) ranging from 34 mm to 310 mm) and divided predicted weights by
+known observed weights to obtain a simple measure of over- or
+underestimation. Difference in mean weight ratios were tested with an
+analysis of covariance (ANCOVA):
+
+\begin{equation}
+R_{i,j} = \tilde{\mu} + \alpha_j + \beta TL_{ij} + e_{ij}
+\end{equation}
+
+\clearpage
+
+Where \(R_{ij}\) is the weight ratio for the \(i\)-th organism obtained
+with parameters from the \(j\)-th study, \(\tilde{\mu}\) is a constant
+for all individuals, \(a_j\) is the treatment effect (\emph{i.e.} the
+difference induced by each study), \(TL_{ij}\) is the covariate
+(\emph{i.e.} Total Length) for the \(i\)-th subject in the \(j\)-th
+group with slope \(\beta\), and \(e_{ij}\) is the error term of the
+regression. Ratios were logit-transformed prior to analysis, and a
 \emph{post-hoc} Tukey's test was used to identify groups where mean
@@
 
-\begin{table}[t]
+\begin{table}[!h]
 
@@
 \toprule
-Region & Sex & n & a & b & \$R\textasciicircum{}2\$ & Reference\\
+Region & Sex & n & a & b & $R^2$ & Reference\\
 \midrule
-Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
+Western Atlantic & B & 774 & 2.90 & 2.89 & - & Barbour et al., 2011\\
 Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
@@
 GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
-\addlinespace
 GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
@@
 GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
-Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
-\addlinespace
-Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
-Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
-Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
+Caribbean & B & 458 & 3.60 & 2.81 & - & Sandel et al., 2015\\
+Caribbean & B & 419 & 2.80 & 2.85 & 0.87 & Chin et al., 2016\\
+Caribbean & B & 1450 & 2.30 & 2.89 & 0.92 & de Leon et al., 2013\\
+Caribbean & B & 1887 & 0.30 & 3.24 & 0.97 & Edwards et al., 2014\\
 Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
-Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
-\addlinespace
+Caribbean & B & 227 & 0.80 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
 Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
@@
 
+\clearpage
+
 \section*{Results}
@@
 The length-weight relationship for organisms from the central Mexican
-Caribbean resulted in coefficient values of \(a = 3.206e-06\) and
-\(b = 3.235\) (\(R^2 = 0.977\), \(F_{1, 107} = 6928.67; p < 0.001\)).
-The allometric factor (\(b\)) was significantly different from \(b = 3\)
-(\(t_{107} = 6.04; p<0.001\)), corroborating that lionfish present
-allometric growth. The length-weight coefficients estimated here were
-within the range identified by studies from other regions (Table
-\ref{tab:all_params}). Figure \ref{fig:l-w-carib} shows the relationship
-between TL and TW for this region.
+Caribbean (\ref{fig:l-w-carib}) resulted in coefficient values of
+\(a = 3.205 \times 10^{-6}\) and \(b = 3.235\) (\(R^2 = 0.977\),
+\(F_{1, 107} = 6928.67; p < 0.001\)). The allometric factor (\(b\)) was
+significantly different from \(b = 3\) (\(t_{107} = 6.04; p<0.001\)),
+corroborating that lionfish present allometric growth. The length-weight
+coefficients estimated here were within the range identified by studies
+from other regions (Table \ref{tab:all_params}).
 
@@
 
-There were significant differences in our predicted weights for the
-central Mexican Caribbean when using each of the different pairs of
-parameters (\(F_{17, 1943} = 24.96; p < 0.001\)). The lowest weight
-estimates for the observed lengths resulted from using the allometric
-parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
-of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
-highest weight estimates came from the Western Atlantic with 73.76
-\(\pm\) 96.11 g \citep{barbour_2011}. True observed weights had a mean
-of 52.56 \(\pm\) 76.58 g. Weights predicted from these extreme
-parameters correspond to predicted-to-observed weight ratios of 0.80
-\(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively. The
-largest under- and overestimations resulted in ratios of 0.36 and 3.51
-of the actual observed weight, indicating that \emph{ex situ} parameters
-can result in highly erroneous weight estimates.
+ANCOVA results show that there were significant differences in our
+predicted weight ratios for the central Mexican Caribbean when using
+each of the different pairs of parameters
+(\(F_{17, 1943} = 24.96; p < 0.001\); Fig \ref{fig:bio_ratio}). For
+example, the actual observed weights of the 109 lionfish from the
+Central Mexican Caribbean had a mean \(\pm\) SD of 52.56 \(\pm\) 76.58
+g. However, if we used allometric parameter values from Banco Chinchorro
+in the Caribbean to predict weights from our observed length
+observations, we estimated a mean \(\pm\) SD of 40.37 \(\pm\) 58.74 g
+\citep{sabidoitz_2016}. If we similarly used parameter values from North
+Carolina in the Western Atlantic to estimate lionfish weights in the
+Central Mexican Caribbean, we found a mean \(\pm\) SD 73.76 \(\pm\)
+96.11 g \citep{barbour_2011}. Weights predicted from these extreme
+parameters correspond to mean predicted-to-observed weight ratios of
+0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.
+Furthermore, for individual organisms, the largest differences between
+predicted and observed values resulted in ratios of 0.36 and 3.51
+(\emph{i.e.} the tails of each violin in Fig \ref{fig:bio_ratio}). If
+instead of looking at the mean ratios we looked at the total biomass
+(\emph{i.e.} summing across organisms), these cases would lead to
+estimated total biomasses of 76.2\% (4,363.53 g) and 140\% (8,039.96 g)
+of true observed biomass (5,729.34 g). These were the two most extreme
+sets of parameters, but results consistently varie Use of \emph{ex situ}
+parameters can result in erroneous weight and total biomass estimates
+for lionfish.
 
@@
 using parameters from other locations in the Caribbean.
-Predicted-to-observed weight ratios are presented in Figure
-\ref{fig:bio_ratio}.
 
@@
 \caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
-weight ratios for 18 pairs of allometric parameters. Blue circles
-indicate median values and like letters indicate values that do not
-differ significantly. For Sabido-Itza et al, 2016b, BC and PNAX make
+weight ratios for 18 pairs of allometric parameters. Sex is indicated in
+parentheses. Blue circles indicate median values and like letters
+indicate values that do not differ significantly. For Sabido-Itza et al,
+2016b, BC and PNAX make reference to Banco Chinchorro and Parque
+Nacional Arrecifes de Xcalak, two sites for which they report
+parameters.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{\label{fig:errors}Estimated total biomas relative to observed
+biomass (5,729.34 g) for 18 pairs of allometric parameters. Sex is
+indicated in parentheses. For Sabido-Itza et al, 2016b, BC and PNAX make
 reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak,
@@
 larger when extrapolation is done for lengths that are larger than the
-maximum length used to estimate the parameters.
+maximum length used to estimate the parameters. Our estimates are
+therefore conservative because we only used parameter pairs from other
+studies to estimate weights for lionfish up to 310 mm in the Central
+Mexican Caribbean, well within the range of lengths for which other
+parameters were estimated.
 
@@
 given length can result in more than a threefold under- or
-overestimation of total weight. These differences become especially
-important when allocating resources for lionfish removal programs,
-incentivizing lionfish fisheries as a source of alternative livelihoods,
-or estimating ecosystem impacts. Research efforts focused on invasive
-lionfish populations need to use parameters calculated for their region
-to the extent possible, or use different sets of parameters that provide
+overestimation of total weight for individual fish, and that total
+biomass estimates may range between 76\% and 140\% of true observed
+biomass. These differences become especially important when allocating
+resources for lionfish removal programs, incentivizing lionfish
+fisheries as a source of alternative livelihoods, or estimating
+ecosystem impacts. Research efforts focused on invasive lionfish
+populations need to use parameters calculated for their region to the
+extent possible, or use different sets of parameters that provide
 appropriate upper and lower bounds in their results.

### 2019-02-09 docs/reviews.Rmd
Added comments by Sean, and new figure

@@
 ---
-<!-- BE REALLY CAREFUL to go through this and make sure the lines actually match up with the lines in the new manuscript - double check every one --> 
 Dear Dr. Pawlik
@@
 
-*As suggested by Rev2, we have logit-transformed our ratios and now evaluate them using an ANCOVA with study and total length as sources of variation.*
+*As suggested by Rev2, we have logit-transformed our ratios and now evaluate them using an ANCOVA, with study and total length as sources of variation.*
 
@@
 
-*We have changed the word from "major" to "substantial" in L19 and L142 (now L139) and "key" in L175 (now L193).
-We chose to keep the word "major" in L26 to maintain consistency with the authors' original wording.*
+- *We have removed the word from "major" from L19 (now L20).*
+
+- *We chose to keep the word "major" in L26 to maintain consistency with the authors' original wording, but we have included quotations to denote this.*
+
+- *In L142 (Now L145) We now say that "ex situ parameters can result in erroneous weight estimates"*
+
+- *Ass suggested, we have changed "major" from L175 to "key" (now L201).*
 
@@
 
-*The text now correctly states the research was performed in the Bahamas.*
+*The text now correctly states the research was performed in the Bahamas (L38).*
 
@@
 
-*We have improved the wording in the original sentence and no longer use the word "know"/"known".*
+*We have improved the wording in the original sentence and no longer use the word "know"/"known" (L59).*
 
@@
 
-*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L78-79) and Table 2 (now Table 1) reflect these changes.*
+*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L80-81) and Table 2 (now Table 1) reflect these changes.*
 
@@
 
-*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120.*
+*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L119.*
 
@@
 
-*We have included the URL in the main text, but the decision to leave it there depends on the editorial formatting.
+*We have included the URL in the main text (L128), but the decision to leave it there depends on the editorial formatting.
 However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*

### 2019-02-09 docs/supplementary/S3Table.Rmd
Added comments by Sean, and new figure

---
title: Spatial variation in allometric growth of invasive lionfish has management implications
subtitle: "Supplementary Table 3"
author: "Villaseñor-Derbez & Fitzgerald"
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: yes
fontsize: 12pt
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 5.5)

options(knitr.table.format = "latex")

windowsFonts(Times=windowsFont("TT Times New Roman"))
```

```{r load packages}
suppressPackageStartupMessages({
  library(stargazer)
  library(sandwich)
  library(lmtest)
  library(broom)
  library(knitr)
  library(tidyverse)
})
```

```{r load data}
fish <- read_csv(here::here("data", "lionfish_data.csv"), col_types = cols()) %>%
  group_by(Id, Site, Location, Latitude, Longitude, Depth_m) %>% 
  summarize(Length = 10*mean(TotalLength_cm),
            Weight = mean(TotalWeigth_gr),
            Stomach = mean(StomachLength_cm)) %>% 
  ungroup()

review <- read.csv(here::here("data", "biometric_review.csv"), 
                  stringsAsFactors = F,
                  strip.white = T,
                  blank.lines.skip = T) %>% 
  mutate(c = log10(a),
         Gender2 = case_when(Gender == "Male" ~ "M",
                             Gender == "Female" ~ "F",
                             TRUE ~"B"))
```

```{r}
model <- lm(log10(Weight) ~ log10(Length), data = fish)
c <- coefficients(model)[[1]]
b <- coefficients(model)[[2]]
```

```{r}
Predicted_biomass <- review %>% 
  mutate(Length = list(fish$Length),
         Weight = list(fish$Weight)) %>% 
  unnest() %>% 
  mutate(pWeight = a*(Length^b),
    Biomass_ratio = pWeight / Weight,
    logit_biomass_ratio = car::logit(Biomass_ratio))
```

```{r}
Predicted_biomass %>% 
  mutate(Study = paste0(Study, " (", Gender_site, ")"),
         Region = case_when(Region == "Western Atlantic" ~ "WA",
                            Region == "Caribbean" ~ "Ca",
                            T ~ "GoM")) %>% 
  group_by(Region, Study) %>%
  summarize(Wp = sum(pWeight),
            W = sum(Weight)) %>%
  ungroup() %>%
  mutate(error = Wp / W * 100) %>%
  arrange(desc(error)) %>%
  select(-W) %>% 
  knitr::kable(col.names = c("Region", "Study", "Biomass (g)", "Percent of observed"),
               booktabs = T,
               digits = 2,
               caption = "\\label{tab:errors}Comparison of errors of total biomass estimation for each pair of parameters. Numeric columns show the estimated total biomass for each pair of parameters (summing across all 109 organisms) and how these compare to true observed total biomass (5729.34 g). Rows are arranged in according to the percentages, in descending order.") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

### 2019-02-09 docs/reviews.Rmd
Modified line numbers referenced in response to reviewrs

@@
 
-- *We chose to keep the word "major" in L26 to maintain consistency with the authors' original wording, but we have included quotations to denote this.*
+- *We chose to keep the word "major" in L26 (now L30) to maintain consistency with the authors' original wording, but we have included quotations to denote this.*
 
-- *In L142 (Now L145) We now say that "ex situ parameters can result in erroneous weight estimates"*
+- *In L142 (Now L150) We now say that "ex situ parameters can result in erroneous weight estimates"*
 
-- *Ass suggested, we have changed "major" from L175 to "key" (now L201).*
+- *Ass suggested, we have changed "major" from L175 to "key" (now L206).*
 
@@
 
-*The text now correctly states the research was performed in the Bahamas (L38).*
+*The text now correctly states the research was performed in the Bahamas (L37).*
 

### 2019-02-10 docs/reviews.Rmd
Updated line numbers and added all of Seans comments in responses to reviewers

@@
 
-*The text now correctly states the research was performed in the Bahamas (L37).*
+*The text now correctly states the research was performed in the Bahamas.*
 
@@
 
-*"impacts" has been replaced with "negative effects" in L47, now L48*
+*"impacts" has been replaced with "negative effects" in L47, now L49*
 
@@
 
-*We have improved the wording in the original sentence and no longer use the word "know"/"known" (L59).*
+*We have improved the wording in the original sentence and no longer use the word "know"/"known". The paragraph now starts in L59.*
 
@@
 
-*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L80-81) and Table 2 (now Table 1) reflect these changes.*
+*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L81-82) and Table 2 (now Table 1) reflect these changes.*
 
@@
 
-*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L119.*
+*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120.*
 
@@
 
-*We have included the URL in the main text (L128), but the decision to leave it there depends on the editorial formatting.
+*We have included the URL in the main text (L129), but the decision to leave it there depends on the editorial formatting.
 However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*
@@
 
-*That is correct. We have modified the text to that it reads "each of the different pairs of parameters".*
+*That is correct. We have modified the text to that it reads "each of the different pairs of parameters" (L137)*
 
@@
 
-*Here we report the mean $\pm$ standard deviation of the estimated weights for the 109 organisms from the central Mexican Caribbean. We have modified the text to clarify our point.*
-
-<!-- OK I actually think this is still a very confusing paragraph.
-It still feels unclear what means +/- SDs we're reporting.
-Perhaps something like this will clarify: "There were significant differences in our predicted weights for the central Mexican Caribbean when using each of the different pairs of parameters (F17;1943 = 24:96; p < 0:001).
-For example, the actual observed weights of the 109 lionfish from the Central Mexican Caribbean had a mean +/- SD of 52.56 +/- 76.58 g.
-However, if we used allometric parameter values from Banco Chinchorro in the Caribbean to predict weights from our observed length observations, we estimated a mean +/ SD of 40.37  58.74 g (Sabido-Itza´ et al., 2016).
-If we similarly used parameter values from NORTH CAROLINA (?) to estimate lionfish weights in the Central Mexican Caribbean, we found a mean +/- SD of 73.76  96.11 g (Barbour et al., 2011).
-These were the two most extreme sets of parameters, but results consistently varied across sites.
-Weights predicted from these extreme parameters corresponded to predicted-to-observed weight ratios of 0.80  0.19 and 1.76  0.50 (mean  SD), respectively, and the under- and overestimations FOR LIONFISH THAT WERE 310 MM IN TL (the maximum TL in this study) (??) resulted in ratios of 0.36 and 3.51 of the actual observed weight.
-Ex situ parameter use can therefore result in highly erroneous weight estimates for lionfish.
--->
+*We have reworded the paragraph to make it more clear.
+Specifically, we report the smallest and largest mean estimated weights for the 109 organisms from the central Mexican Caribbean.
+We then report their corresponding mean predicted-to-observed ratios, which are still averaged for each pair of parameters across all organisms.
+These correspond to the first and last "violins" in Fig 4.
+We then provide the extreme values of predicted-to-observed ratios for all organisms and all studies; In a sense, the worst relative over- and underestimations (the smallest and largest values shown in Fig.4 overall).
+Finally, we provide similar measures for estimated total biomass (that is, the summ of the 109 predicted weights) by study, relative to the actual true observed total biomas.
+This last measure is now presented in Fig 5.*
 
@@
 
-*The figure caption now includes the following sentence: For Sabido-Itza et al, 2016b, BC and PNAX make reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites for which they report parameters.*
+*The figure caption now includes the following sentence: For Sabido-Itza et al, 2016b, BC and PNAX make reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites for which they report parameters.
+We have also modified the graph so that colors represent regions.*
 
-<!-- You gotta tell me how to pronouce Xcalak -->
 ### Discussion:
@@
 *Yes, we refer to the spatial heterogeneity.
-We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and..."*
+We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and...".
+This is now L161.*
 
@@
 
-*This was meant to say "We show that", and has now been corrected.*
-
-\clearpage
+*This was meant to say "We show that", and has now been corrected in what is now L162.*
 
@@
 However, we recognize this may be a factor that influences weight or growth and therefore the length-weight relationship.
-We have mentioned that our parameters for the Central Mexican Caribbean are from organisms collected during the Summer (L94), and have devoted a paragraph in the discussion (L175) to highlight the importance of collection methods and timing when estimating length-weight relationships.*
+We have mentioned that our parameters for the central Mexican Caribbean are from organisms collected during the Summer (L101), and have devoted a paragraph in the discussion (L185) to highlight the importance of collection methods and timing when estimating length-weight relationships.*
 
@@
 
-*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and as you noted data from Fogg et al.
+*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and as Reviewer 2 noted, data from Fogg et al.
 (2013) produced some of the largest estimates.
 After a careful evaluation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders.
+That is, the wording in their paper confused us and made us think they reported spineless weight, but they report total weight.
 The corresponding modifications have been made in the text.
 Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*
-
-<!-- I don't think you satisfactorily answered this one - you kind of skirted the reviewer's question of how you adjusted for spineless weight (the answer is we didn't, right?).
-Don't think you can get away with just saying "The corresponding modifications have been made in the text." -->
 
@@
 
-*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L175).*
+*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L185).*
 
@@
 The fact that similar comments were raised by Rev2 suggests that we did not adequately describe this limitation in our original manuscript.
-We now explicitly state that we did not have access to the raw data from the published studies (LINES).
+We now explicitly state that we did not have access to the raw data from the published studies (L87, L117 and L189).
 However, it is important to note that the objective of our study was not to describe the biological differences in length-weight relationships between site locations, rather to assess the effect of using ex situ vs.
 in situ parameter values to estimate lionfish weights from direct length observations (i.e., to assess whether ex situ parameter values result in large errors in weight estimates).
-We believe that after modifying the text to clearly state our objectives (LINES - WE MENTION RAW DATA A FEW TIMES NOW, SO INCLUDE EVERY INSTANCE SO IT LOOKS LIKE WE WERE REALLY THOROUGH) and including a discussion paragraph about the limitations of our study (LINES), we have satisfactorily addressed these concerns.*
+We believe that after modifying the text to clearly state our objectives (L87, L117 and L189) and including discussion paragraphs about the limitations of our study (L185 and 196), we have satisfactorily addressed these concerns.*
 
@@
 
-*We now use the word "key".*
+*We now use the word "key" (L208).*
+
+\clearpage
 
@@
 *The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters.
-We have included a paragraph in the discussion that touches on this (L 185).*
-<!-- Be more specific than "touches on this" - quote exactly what you wrote to alleviate the reviewer's concerns -->
-
-<!-- Also I think I said "you" a lot instead of "the reviewer" - my bad.  Change it to whatever you want, but make it consistent -->
+We have included a paragraph in the discussion where we compare our range of TLs (34 - 310 mm) to the ranges used by different studies to estimate their parameters (Paragraph starts in L 196).
+We also make reference to a new supplementary table where we report all information recorded in other studies.*
 
@@
 However, we do not have the raw data from other studies and applying this to the predicted estimates would not help us answer this question.
-In a sense, we would be asking if the lines in Fig 3 (with no variation around them) have significantly different slopes and intercepts.
+In a sense, we would be asking if the lines in Fig 3 (with no variance / process error around them) have significantly different slopes and intercepts.
 As mentioned in the response to R1, we originally failed to clearly state that we do not have the raw data required to perform such an analysis.
-We have included statements in the methods (LINES) and a discussion paragraph (L175) that highlight these limitations and clarify our objectives/analyses.*
-<!-- General point - never use the word "this" to end a sentence - you always want to follow "this" with another word (e.g., "highlighting this topic" instead of "highlighting this") -->
+We have included statements in the methods (L87, L117 and L189) and a discussion paragraph (L185) that highlight these limitations and clarify our objectives/analyses.*
 
@@
 *We have included the log-log version of Figure 3 in the appendices as Supplementary Figure 1. We reference such figure in the caption to Figure 3.*
-<!-- Don't you think we should include the Central Mexican Caribbean in Fig 3 and Fig S1? -->
+
 Figure 3, showing the untransformed data, should be amended so that each fitted curve extends across the range of total lengths specific to that study.
@@
 *As stated above, these were also raised by Rev1.
-We believe that our modifications to the discussion in lines...
-now explicitly mention these issues.
+We believe that our modifications to the discussion in L185 and L196 now explicitly mention these issues.
 And while we cannot test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*
-<!-- modification in which lines? -->
-<!-- Alright we gotta do a better job on this one - s/he says this is THE area for major improvement.
-I think the text is mostly there in the manuscript now, but we need to specifically answer each of the questions the reviewer asks, preferably while quoting the text as well -->
+
+*More specifically, paragraph starting in L176 mentions that the spatial patterns in length-weight relationships i) ressemble those observed for length-at-age (Pusack et al 2016), ii) Groups identified by post hoc tests aligned with the spatial distribution of examined studyes and ii) These groups also correspond to genetic analyses (Betancur-R et al 2011).*
+
+*In the new paragraph starting in L185 we now mention that variation can also be caused by other factors that are not related to space.
+These include different sampling methods, seasonality, and depth ranges.*
 
@@
 
-*We have corrected this and now refer to four and six studies. These are now in L83 and L85.*
+*We have corrected this and now refer to four and six studies. The sentence now starts in L94.*
 
@@
 
-*We believe that gear selectivity is effectively eliminated because all observed organisms were collected.
-When pole spears are used, it is difficult to sample organisms that are smaller than 50 mm.
+*Hand nets allow us to sample all organisms, independent of their sizes.
+We believe that gear selectivity is effectively eliminated because all observed organisms were collected.
+When pole spears are used, it is difficult to sample organisms that are smaller than ~50 mm.
 This might explain why most of the studies show higher minimum lengths.
 We believe that the Supplementary Table 2 now addresses this and makes all the reviewed information available to future readers.*
-<!-- I don't understand the logic in the first sentence - why does collecting them elimiate gear selectivity concerns? -->
+
 5.
@@
 This is clear from equations (1) and (2), in fact, the log-transformation of this power function is standard enough that equation (2) does not likely need to appear in the manuscript, instead simply state the function was linearized using log-transformation.
-<!-- Maybe this reviewer would disagree with my idea to add the ANCOVA equation... What do you think? -->
-*We have modified the text and now only include Eq 1.*
+
+*We have modified the text and now only include Eq 1. when talking about allometric growth.*
 
@@
 Related to this, only include information on the weight-length relationship from the central Mexican coast in the text that is not already presented in Figure 2; there is no need to include it in two places.
-<!-- Ok well given this, I guess also ignore my comment that I thought we should include this study in Fig 3 and S1 -->
+
 *We agree, and have now removed Table 1.*
@@
 Reporting the range in mean ratios would be sufficient along with an illustrative figure.
-<!-- Already commented on this in the manuscript - but are those extremes (.36 and 3.51) for lionfish that are length 310 mm? Need to be clear about that -->
+
 *That is correct, the 0.80 and 1.76 values make reference to the mean ratios.
 We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51 - especially because we are unable to assess the full length-weight relationships from all studies given our lack of raw data.
-We believe the new text justifies including these extremes.*
+We believe the new text justifies including these extremes.
+The paragraph now starts in L136.*
 
@@
 Change Fit to R2 in the Table heading, so it doesn’t need to be defined in the caption.
-<!-- I can't knit for some reason, so I can't tell if this was done but I assume you took care of it.  Also isn't it b, not c? -->
+
 *We have removed parameter c from Table 2 (Now Table 1) and modified the header so it has $R^2$.*
@@
 *Figure 3 shows a total of 18 lines.
-This is because from the 12 reviewed papers, a total of 17 relationships were identified BECAUSE OF SEX-SPECIFIC REPORTING AND SOME STUDIES REPORTING MULTIPLE LOCATIONS??
-(if so, say that).
+This is because from the 12 reviewed papers, a total of 17 relationships were identified because of sex-specific reporting and some studies reporting multiple locations.
 The additional relationship is the one estimated in this study.*
-
-<!-- Oh wait - you do include this study in Fig 3 - so ignore BOTH of my previous comments haha- but the line for this study needs to be in the figure legend! -->

### 2019-02-11 docs/Manuscript.Rmd
SF final edit

@@
 The spatial pattern we observed is consistent with findings from other studies focused on genetics or length-at-age.
-We show that the use of \textit{ex situ} parameters can result in up to a threefold under- or overestimation of total weight for an individual organism.
-When estimating total biomass, the use of other parameters may produce estimates between 76.2% and 140% of true observed biomass.
+Here, the use of \textit{ex situ} parameter values resulted in total biomass estimates between 76.2% and 140% of true observed biomass, and up to a threefold under- or overestimation of total weight for an individual organism.
 These findings can have implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
@@
 The feasibility of establishing fisheries through lionfish removal programs has been extensively evaluated through field observations and empirical modeling \citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,usseglio_2017}.
-Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in fishing mortality (*i.e.* culling).
+Determining the feasibility of such initiatives requires modeling the change in biomass in response to changes in fishing mortality (*i.e.,* culling).
 A common way to model this is via length-structured population models, where fish lengths are converted to weight to calculate total biomass \citep{barbour_2011,cote_2014,andradibrown_2017}.
@@
 By comparing these weight estimates to our *in situ* length-weight observations, we showed that using *ex situ* parameter values resulted in up to a threefold under- or overestimation of lionfish weight.
+
+<!-- Is it possible to get rid of the double parentheses that appear in the .pdf? (e.g., line 75)  Or is this their format and they don't care and will fix it for us if/when it's published? -->
 
@@
 We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here (Fig \ref{fig:all_allo}).
-Recall that the objective of this study is not to describe variations between populations (which would require access to raw data), but rather to assess how *ex situ* parameter values influence the accuracy of weight estimates for lionfish, using the central Mexican Caribbean as a case study.
+Recall that the objective of this study is not to describe differences in the length-weight relationship between populations (which would require access to raw data), but rather to assess how *ex situ* parameter values influence the accuracy of weight estimates for lionfish, using the central Mexican Caribbean as a case study.
 Using each of the 18 parameter pairs, we estimated $TW$ from the $TL$ observations collected in the central Mexican Caribbean (n = 109, with $TL$ ranging from 34 mm to 310 mm) and divided predicted weights by known observed weights to obtain a simple measure of over- or underestimation.
@@
 
-Where $R_{ij}$ is the weight ratio for the $i$-th organism obtained with parameters from the $j$-th study, $\tilde{\mu}$ is a constant for all individuals, $a_j$ is the treatment effect (*i.e.* the difference induced by each study), $TL_{ij}$ is the covariate (*i.e.* Total Length) for the $i$-th subject in the $j$-th group with slope $\beta$, and $e_{ij}$ is the error term of the regression.
+Where $R_{ij}$ is the weight ratio for the $i$-th organism obtained with parameters from the $j$-th study, $\tilde{\mu}$ is a constant for all individuals, $a_j$ is the treatment effect (*i.e.,* the difference induced by each study), $TL_{ij}$ is the covariate (*i.e.,* Total Length) for the $i$-th subject in the $j$-th group with slope $\beta$, and $e_{ij}$ is the error term of the regression.
 Ratios were logit-transformed prior to analysis, and a *post-hoc* Tukey's test was used to identify groups where mean ratios did not differ.
@@
 
-ANCOVA results show that there were significant differences in our predicted weight ratios for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$; Fig \ref{fig:bio_ratio}).
+ANCOVA results revealed significant differences in our predicted weight ratios for the central Mexican Caribbean when using each of the different pairs of parameters ($F_{17, 1943} = 24.96; p < 0.001$; Fig \ref{fig:bio_ratio}).
 For example, the actual observed weights of the 109 lionfish from the Central Mexican Caribbean had a mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Weight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Weight) %>% formatC(digits = 2, format = "f")` g.
@@
 Weights predicted from these extreme parameters correspond to mean predicted-to-observed weight ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
-Furthermore, for individual organisms, the largest differences between predicted and observed values resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` (*i.e.* the tails of each violin in Fig \ref{fig:bio_ratio}).
-If instead of looking at the mean ratios we looked at the total biomass (*i.e.* summing across organisms), these cases would lead to estimated total biomasses of 76.2% (4,363.53 g) and 140% (8,039.96 g) of true observed biomass (5,729.34 g).
-These were the two most extreme sets of parameters, but results consistently varie Use of *ex situ* parameters can result in erroneous weight and total biomass estimates for lionfish.
+Furthermore, for the smallest and largest individual organisms collected in the central Mexican Caribbean (TL = 34 and 310 mm, respectively), the differences between predicted and observed values resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` (*i.e.,* the tails of each violin in Fig \ref{fig:bio_ratio}).
+If we examined biomass (*i.e.,* summing across all 109 organisms) instead of mean ratios, total biomass estimates were 76.2% (4,363.53 g) and 140% (8,039.96 g) of true observed biomass (5,729.34 g).
+We produced these misestimates using the two most extreme sets of parameters, but results varied consistently across locations.
+Overall, the use of *ex situ* parameters led to significantly erroneous estimates of individual weight and total biomass for lionfish.
 
-Tukey's *post-hoc* test suggested that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
+Tukey's *post-hoc* test showed that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
 All weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher than observed values, and only parameters from the Caribbean produced weights smaller than observed (Fig \ref{fig:bio_ratio}).
@@
 This suggests that the smallest errors are observed when using parameters from other locations in the Caribbean.
+
+<!-- One minor suggestion - instead of leading with where the differences AREN'T, start with where they ARE - e.g., "Tukey's *post-hoc* test showed that weight ratios for the central Mexican Caribbean differeed from those obtained with parameters from the Western Atlantic, and most sites in the Caribbean and the Gulf of Mexico (Tukey's HSD $p > 0.05$).
+The only sites where weight ratios did not differ from the central Mexican Caribbean were Little Cayman, the Bahamas, and some sites (WHICH ONES?) in the Gulf of Mexico (Tukey's HSD $p > 0.05$)." -->
 
@@
 
-```{r pred_obs, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios for 18 pairs of allometric parameters.
+```{r pred_obs, fig.height = 5.2, fig.width = 5.5, fig.cap = "\\label{fig:bio_ratio}Violin plot of predicted-to-observed weight ratios when applying each of 18 different pairs of allometric parameters to the 109 lionfish collected in the central Mexican Caribbean.
 Sex is indicated in parentheses.
@@
 Moreover, we show that the use of *ex situ* parameter values may lead to highly biased weight estimates.
-Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight can be overestimated by more than threefold, highlighting the need to use local information.
+Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight of an individual lionfish can be overestimated by more than threefold, highlighting the need to use local information.
 Here we discuss the implications of our findings, possible shortcommings in our analyses, and highlight potential future research directions.
@@
 Differences in length-weight relationships have traditionally been highlighted as potential pitfalls to fishery management.
-For example, \citet{wilson_2012} show that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
+For example, \citet{wilson_2012} showed that small-scale variations in length-at-age and fishing mortality in other Scorpaeniformes translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans.
 The lionfish case poses the opposite scenario, where the manager desires to eradicate the species.
@@
 However, samples from the 12 studies included here were not only collected in different locations, but also at different points in time and across different depth and size ranges (See Supplementary Table 2 for an extended version of Table 1).
-While we could not evaluate how these factors influenced length-weight estimates from previous studies without raw data, we still show that a lack of locally-calculated parameters can induce significant bias when calculating weight from length observations.
 The magnitude of the bias discovered in this study and our lack of understanding the sources driving spatial variation for lionfish highlights the need to simultaneously collect length-weight information across the invaded range to test for spatially-induced patterns and to link these findings to previously suggested environmental and genetic structures.
 Such an endeavor would provide insight into lionfish biology and better inform management.
+However, while we could not evaluate how these factors influenced length-weight estimates from previous studies without raw data, we still show that a lack of locally-calculated parameters can induce significant bias when calculating weight from length observations.
+We demonstrate the importance of using *in situ* parameters to obtain accurate weight estimates regardless of the underlying mechanisms driving variation between populations.
 
@@
 By contrast, our largest organism had a $TL$ of 310 mm, which is well within the range of all other studies (the next smallest maximum length was 325 mm; See Supplementary Table 2).
-Due to the power function describing the allometric relationship (*i.e.* Eq.
+Due to the power function describing the allometric relationship (*i.e.,* Eq.
 1), the error in weight estimates is larger when extrapolation is done for lengths that are larger than the maximum length used to estimate the parameters.

### 2019-02-11 docs/Manuscript.Rmd
Updated, ready to resubmit

@@
 author: "Juan Carlos Villaseñor-Derbez, Sean P. Fitzgerald"
-institution: "Bren School of Environmental Sciences and Management, University of California Santa Barbara, Santa Barbara, California, U.S."
+institution: "Bren School of Environmental Sciences & Management, University of California Santa Barbara, Santa Barbara, California, U.S."
 abstract: |
@@
 
-Governments and non-profit organizations have sought to reduce lionfish densities through removal programs and incentivizing its consumption \citep{chin_2016}.
+Governments and non-profit organizations have sought to reduce lionfish densities through removal programs and by incentivizing its consumption \citep{chin_2016}.
 In some cases, these have shown to significantly reduce -- but not quite eliminate -- lionfish abundances at local scales \citep{deleon_2013,sandel_2015}.
@@
 Our objective was to quantify the magnitude of error caused by using *ex situ* parameter values when estimating lionfish weight from length observations.
-In this study, we calculated and reported the first length-weight relationship for lionfish in the central Mexican Caribbean using previously collected *in situ* observations (n = 109; \citep{villaseorderbez_2014}).
+In this study, we calculated and reported the first length-weight relationship for lionfish in the central Mexican Caribbean using previously collected *in situ* observations (n = 109; \citet{villaseorderbez_2014}).
 We then estimated lionfish weight in this area using previously published length-weight relationships for lionfish populations from ten locations across the Western Atlantic, Gulf of Mexico, and Caribbean.
-By comparing these weight estimates to our *in situ* length-weight observations, we showed that using *ex situ* parameter values resulted in up to a threefold under- or overestimation of lionfish weight.
-
-<!-- Is it possible to get rid of the double parentheses that appear in the .pdf? (e.g., line 75)  Or is this their format and they don't care and will fix it for us if/when it's published? -->
+By comparing these weight estimates to our *in situ* length-weight observations, we showed that using *ex situ* parameter values resulted in up to a threefold under- or overestimation of lionfish weight and estimated of total biomass ranged between 76% and 140% of observed total biomass.
 
@@
 
-The weight-at-length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function
+The weight-at-length relationship for lionfish in the central Mexican Caribbean was calculated with the allometric growth function:
 
@@
 
-where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
+Where $a$ is the ponderal index and $b$ is the scaling exponent or allometric parameter.
 We linearized the equation using $log_{10}$-transformation and estimated the coefficients using an Ordinary Least Squares Regression with a heteroskedastic-robust standard error correction \citep{zeileis_2004}.
@@
 
-The length-weight relationship for organisms from the central Mexican Caribbean (\ref{fig:l-w-carib}) resulted in coefficient values of $a = 3.205 \times 10^{-6}$ and $b = `r bs`$ ($R^2 = `r Rsq`$, $F_{1, 107} = 6928.67; p < 0.001$).
+The length-weight relationship for organisms from the central Mexican Caribbean (Fig \ref{fig:l-w-carib}) resulted in coefficient values of $a = 3.205 \times 10^{-6}$ and $b = `r bs`$ ($R^2 = `r Rsq`$, $F_{1, 107} = 6928.67; p < 0.001$).
 The allometric factor ($b$) was significantly different from $b = 3$ ($t_{107} = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), corroborating that lionfish present allometric growth.
@@
 However, if we used allometric parameter values from Banco Chinchorro in the Caribbean to predict weights from our observed length observations, we estimated a mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{sabidoitz_2016}.
-If we similarly used parameter values from North Carolina in the Western Atlantic to estimate lionfish weights in the Central Mexican Caribbean, we found a mean $\pm$ SD `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{barbour_2011}.
+If we similarly used parameter values from North Carolina in the Western Atlantic to estimate lionfish weights in the Central Mexican Caribbean, we found a mean $\pm$ SD of `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(pWeight) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(pWeight) %>% formatC(digits = 2, format = "f")` g \citep{barbour_2011}.
 Weights predicted from these extreme parameters correspond to mean predicted-to-observed weight ratios of `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Sabido2BC") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r filter(Predicted_biomass, Study_id == "Barbour") %$% mean(Biomass_ratio) %>% formatC(digits = 2, format = "f")` $\pm$ `r filter(Predicted_biomass, Study_id == "Barbour") %$% sd(Biomass_ratio) %>% formatC(digits = 2, format = "f")` (mean $\pm$ SD), respectively.
-Furthermore, for the smallest and largest individual organisms collected in the central Mexican Caribbean (TL = 34 and 310 mm, respectively), the differences between predicted and observed values resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` (*i.e.,* the tails of each violin in Fig \ref{fig:bio_ratio}).
+Furthermore, largest errors for individual organisms collected in the central Mexican Caribbean resulted in ratios of `r min(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` and `r max(Predicted_biomass$Biomass_ratio) %>% formatC(digits = 2, format = "f")` (*i.e.,* the tails of each violin in Fig \ref{fig:bio_ratio}).
 If we examined biomass (*i.e.,* summing across all 109 organisms) instead of mean ratios, total biomass estimates were 76.2% (4,363.53 g) and 140% (8,039.96 g) of true observed biomass (5,729.34 g).
-We produced these misestimates using the two most extreme sets of parameters, but results varied consistently across locations.
+Parameters for this study estimate total biomass at 98% of observed biomass.
+These misestimates come from the two most extreme sets of parameters, but results varied consistently across locations (Figs \ref{fig:bio_ratio} and \ref{fig:errors}).
 Overall, the use of *ex situ* parameters led to significantly erroneous estimates of individual weight and total biomass for lionfish.
 
-Tukey's *post-hoc* test showed that weight ratios for the central Mexican Caribbean were not different from those obtained with parameters from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico (Tukey's HSD $p > 0.05$).
+Tukey's *post-hoc* test showed that weight ratios for the central Mexican Caribbean differeed from those obtained with parameters from the Western Atlantic, and most sites in the Caribbean and the Gulf of Mexico (Tukey's HSD $p > 0.05$).
+The only sites where weight ratios did not differ from the central Mexican Caribbean were Little Cayman \citep{edwards_2014}, Bahamas \citep{darling_2011}, and the Northern Gulf of Mexico (\citet{dahl_2014}; Tukey's HSD $p > 0.05$).
 All weight estimates using parameters from the Gulf of Mexico and Western Atlantic were higher than observed values, and only parameters from the Caribbean produced weights smaller than observed (Fig \ref{fig:bio_ratio}).
@@
 This suggests that the smallest errors are observed when using parameters from other locations in the Caribbean.
-
-<!-- One minor suggestion - instead of leading with where the differences AREN'T, start with where they ARE - e.g., "Tukey's *post-hoc* test showed that weight ratios for the central Mexican Caribbean differeed from those obtained with parameters from the Western Atlantic, and most sites in the Caribbean and the Gulf of Mexico (Tukey's HSD $p > 0.05$).
-The only sites where weight ratios did not differ from the central Mexican Caribbean were Little Cayman, the Bahamas, and some sites (WHICH ONES?) in the Gulf of Mexico (Tukey's HSD $p > 0.05$)." -->
 
@@
 Our results suggest that lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and that this variation is relevant for managing invasions.
-Moreover, we show that the use of *ex situ* parameter values may lead to highly biased weight estimates.
+Moreover, we show that the use of *ex situ* parameter values may lead to highly biased weight and total biomass estimates.
 Our comparison of observed weights to those predicted with locally-informed parameters and *ex situ* parameters showed that weight of an individual lionfish can be overestimated by more than threefold, highlighting the need to use local information.
@@
 
-We might be inclined to attribute all variation in the lionfish length-weight relationship to the spatial origin of these parameters.
+One might be inclined to attribute all variation in the lionfish length-weight relationship to the spatial origin of these parameters.
 However, samples from the 12 studies included here were not only collected in different locations, but also at different points in time and across different depth and size ranges (See Supplementary Table 2 for an extended version of Table 1).

### 2019-02-11 docs/Manuscript.tex
Updated, ready to resubmit

@@
 observed is consistent with findings from other studies focused on
-genetics or length-at-age. We show that the use of \textit{ex situ}
-parameters can result in up to a threefold under- or overestimation of
-total weight for an individual organism. When estimating total biomass,
-the use of other parameters may produce estimates between 76.2\% and
-140\% of true observed biomass. These findings can have implications for
-management in terms of predicting effects on local ecosystems,
-evaluating the effectiveness of removal programs, or estimating biomass
-available for harvest.
+genetics or length-at-age. Here, the use of \textit{ex situ} parameter
+values resulted in total biomass estimates between 76.2\% and 140\% of
+true observed biomass, and up to a threefold under- or overestimation of
+total weight for an individual organism. These findings can have
+implications for management in terms of predicting effects on local
+ecosystems, evaluating the effectiveness of removal programs, or
+estimating biomass available for harvest.
 \end{abstract}
@@
 Governments and non-profit organizations have sought to reduce lionfish
-densities through removal programs and incentivizing its consumption
+densities through removal programs and by incentivizing its consumption
 \citep{chin_2016}. In some cases, these have shown to significantly
@@
 change in biomass in response to changes in fishing mortality
-(\emph{i.e.} culling). A common way to model this is via
+(\emph{i.e.,} culling). A common way to model this is via
 length-structured population models, where fish lengths are converted to
@@
 using previously collected \emph{in situ} observations (n = 109;
-\citep{villaseorderbez_2014}). We then estimated lionfish weight in this
+\citet{villaseorderbez_2014}). We then estimated lionfish weight in this
 area using previously published length-weight relationships for lionfish
@@
 situ} parameter values resulted in up to a threefold under- or
-overestimation of lionfish weight.
+overestimation of lionfish weight and estimated of total biomass ranged
+between 76\% and 140\% of observed total biomass.
 
@@
 The weight-at-length relationship for lionfish in the central Mexican
-Caribbean was calculated with the allometric growth function
+Caribbean was calculated with the allometric growth function:
 
@@
 
-where \(a\) is the ponderal index and \(b\) is the scaling exponent or
+Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
 allometric parameter. We linearized the equation using
@@
 calculated here (Fig \ref{fig:all_allo}). Recall that the objective of
-this study is not to describe variations between populations (which
-would require access to raw data), but rather to assess how \emph{ex
-situ} parameter values influence the accuracy of weight estimates for
-lionfish, using the central Mexican Caribbean as a case study. Using
-each of the 18 parameter pairs, we estimated \(TW\) from the \(TL\)
-observations collected in the central Mexican Caribbean (n = 109, with
-\(TL\) ranging from 34 mm to 310 mm) and divided predicted weights by
-known observed weights to obtain a simple measure of over- or
-underestimation. Difference in mean weight ratios were tested with an
-analysis of covariance (ANCOVA):
+this study is not to describe differences in the length-weight
+relationship between populations (which would require access to raw
+data), but rather to assess how \emph{ex situ} parameter values
+influence the accuracy of weight estimates for lionfish, using the
+central Mexican Caribbean as a case study. Using each of the 18
+parameter pairs, we estimated \(TW\) from the \(TL\) observations
+collected in the central Mexican Caribbean (n = 109, with \(TL\) ranging
+from 34 mm to 310 mm) and divided predicted weights by known observed
+weights to obtain a simple measure of over- or underestimation.
+Difference in mean weight ratios were tested with an analysis of
+covariance (ANCOVA):
 
@@
 with parameters from the \(j\)-th study, \(\tilde{\mu}\) is a constant
-for all individuals, \(a_j\) is the treatment effect (\emph{i.e.} the
+for all individuals, \(a_j\) is the treatment effect (\emph{i.e.,} the
 difference induced by each study), \(TL_{ij}\) is the covariate
-(\emph{i.e.} Total Length) for the \(i\)-th subject in the \(j\)-th
+(\emph{i.e.,} Total Length) for the \(i\)-th subject in the \(j\)-th
 group with slope \(\beta\), and \(e_{ij}\) is the error term of the
@@
 The length-weight relationship for organisms from the central Mexican
-Caribbean (\ref{fig:l-w-carib}) resulted in coefficient values of
+Caribbean (Fig \ref{fig:l-w-carib}) resulted in coefficient values of
 \(a = 3.205 \times 10^{-6}\) and \(b = 3.235\) (\(R^2 = 0.977\),
@@
 
-ANCOVA results show that there were significant differences in our
-predicted weight ratios for the central Mexican Caribbean when using
-each of the different pairs of parameters
-(\(F_{17, 1943} = 24.96; p < 0.001\); Fig \ref{fig:bio_ratio}). For
-example, the actual observed weights of the 109 lionfish from the
-Central Mexican Caribbean had a mean \(\pm\) SD of 52.56 \(\pm\) 76.58
-g. However, if we used allometric parameter values from Banco Chinchorro
-in the Caribbean to predict weights from our observed length
-observations, we estimated a mean \(\pm\) SD of 40.37 \(\pm\) 58.74 g
-\citep{sabidoitz_2016}. If we similarly used parameter values from North
-Carolina in the Western Atlantic to estimate lionfish weights in the
-Central Mexican Caribbean, we found a mean \(\pm\) SD 73.76 \(\pm\)
-96.11 g \citep{barbour_2011}. Weights predicted from these extreme
-parameters correspond to mean predicted-to-observed weight ratios of
-0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.
-Furthermore, for individual organisms, the largest differences between
-predicted and observed values resulted in ratios of 0.36 and 3.51
-(\emph{i.e.} the tails of each violin in Fig \ref{fig:bio_ratio}). If
-instead of looking at the mean ratios we looked at the total biomass
-(\emph{i.e.} summing across organisms), these cases would lead to
-estimated total biomasses of 76.2\% (4,363.53 g) and 140\% (8,039.96 g)
-of true observed biomass (5,729.34 g). These were the two most extreme
-sets of parameters, but results consistently varie Use of \emph{ex situ}
-parameters can result in erroneous weight and total biomass estimates
-for lionfish.
+ANCOVA results revealed significant differences in our predicted weight
+ratios for the central Mexican Caribbean when using each of the
+different pairs of parameters (\(F_{17, 1943} = 24.96; p < 0.001\); Fig
+\ref{fig:bio_ratio}). For example, the actual observed weights of the
+109 lionfish from the Central Mexican Caribbean had a mean \(\pm\) SD of
+52.56 \(\pm\) 76.58 g. However, if we used allometric parameter values
+from Banco Chinchorro in the Caribbean to predict weights from our
+observed length observations, we estimated a mean \(\pm\) SD of 40.37
+\(\pm\) 58.74 g \citep{sabidoitz_2016}. If we similarly used parameter
+values from North Carolina in the Western Atlantic to estimate lionfish
+weights in the Central Mexican Caribbean, we found a mean \(\pm\) SD of
+73.76 \(\pm\) 96.11 g \citep{barbour_2011}. Weights predicted from these
+extreme parameters correspond to mean predicted-to-observed weight
+ratios of 0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD),
+respectively. Furthermore, largest errors for individual organisms
+collected in the central Mexican Caribbean resulted in ratios of 0.36
+and 3.51 (\emph{i.e.,} the tails of each violin in Fig
+\ref{fig:bio_ratio}). If we examined biomass (\emph{i.e.,} summing
+across all 109 organisms) instead of mean ratios, total biomass
+estimates were 76.2\% (4,363.53 g) and 140\% (8,039.96 g) of true
+observed biomass (5,729.34 g). Parameters for this study estimate total
+biomass at 98\% of observed biomass. These misestimates come from the
+two most extreme sets of parameters, but results varied consistently
+across locations (Figs \ref{fig:bio_ratio} and \ref{fig:errors}).
+Overall, the use of \emph{ex situ} parameters led to significantly
+erroneous estimates of individual weight and total biomass for lionfish.
 
-Tukey's \emph{post-hoc} test suggested that weight ratios for the
-central Mexican Caribbean were not different from those obtained with
-parameters from Little Cayman, the Bahamas, and some sites in the Gulf
-of Mexico (Tukey's HSD \(p > 0.05\)). All weight estimates using
-parameters from the Gulf of Mexico and Western Atlantic were higher than
-observed values, and only parameters from the Caribbean produced weights
-smaller than observed (Fig \ref{fig:bio_ratio}). The regional average
-(\(\pm\) SD) of predicted-to-observed weight ratios from these three
-regions were 1.24 \(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\)
-0.423 for the Gulf of Mexico, Western Atlantic, and Caribbean,
-respectively. This suggests that the smallest errors are observed when
-using parameters from other locations in the Caribbean.
+Tukey's \emph{post-hoc} test showed that weight ratios for the central
+Mexican Caribbean differeed from those obtained with parameters from the
+Western Atlantic, and most sites in the Caribbean and the Gulf of Mexico
+(Tukey's HSD \(p > 0.05\)). The only sites where weight ratios did not
+differ from the central Mexican Caribbean were Little Cayman
+\citep{edwards_2014}, Bahamas \citep{darling_2011},
+and the Northern Gulf of Mexico (\citet{dahl_2014}; Tukey's HSD
+\(p > 0.05\)). All weight estimates using parameters from the Gulf of
+Mexico and Western Atlantic were higher than observed values, and only
+parameters from the Caribbean produced weights smaller than observed
+(Fig \ref{fig:bio_ratio}). The regional average (\(\pm\) SD) of
+predicted-to-observed weight ratios from these three regions were 1.24
+\(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\) 0.423 for the Gulf
+of Mexico, Western Atlantic, and Caribbean, respectively. This suggests
+that the smallest errors are observed when using parameters from other
+locations in the Caribbean.
 
@@
 \caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
-weight ratios for 18 pairs of allometric parameters. Sex is indicated in
-parentheses. Blue circles indicate median values and like letters
-indicate values that do not differ significantly. For Sabido-Itza et al,
-2016b, BC and PNAX make reference to Banco Chinchorro and Parque
-Nacional Arrecifes de Xcalak, two sites for which they report
-parameters.}
+weight ratios when applying each of 18 different pairs of allometric
+parameters to the 109 lionfish collected in the central Mexican
+Caribbean. Sex is indicated in parentheses. Blue circles indicate median
+values and like letters indicate values that do not differ
+significantly. For Sabido-Itza et al, 2016b, BC and PNAX make reference
+to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak, two sites
+for which they report parameters.}
 \end{figure}
@@
 show that the use of \emph{ex situ} parameter values may lead to highly
-biased weight estimates. Our comparison of observed weights to those
-predicted with locally-informed parameters and \emph{ex situ} parameters
-showed that weight can be overestimated by more than threefold,
-highlighting the need to use local information. Here we discuss the
-implications of our findings, possible shortcommings in our analyses,
-and highlight potential future research directions.
+biased weight and total biomass estimates. Our comparison of observed
+weights to those predicted with locally-informed parameters and \emph{ex
+situ} parameters showed that weight of an individual lionfish can be
+overestimated by more than threefold, highlighting the need to use local
+information. Here we discuss the implications of our findings, possible
+shortcommings in our analyses, and highlight potential future research
+directions.
 
@@
 highlighted as potential pitfalls to fishery management. For example,
-\citet{wilson_2012} show that small-scale variations in length-at-age
+\citet{wilson_2012} showed that small-scale variations in length-at-age
 and fishing mortality in other Scorpaeniformes translate to differential
@@
 
-We might be inclined to attribute all variation in the lionfish
+One might be inclined to attribute all variation in the lionfish
 length-weight relationship to the spatial origin of these parameters.
@@
 and across different depth and size ranges (See Supplementary Table 2
-for an extended version of Table 1). While we could not evaluate how
-these factors influenced length-weight estimates from previous studies
-without raw data, we still show that a lack of locally-calculated
-parameters can induce significant bias when calculating weight from
-length observations. The magnitude of the bias discovered in this study
-and our lack of understanding the sources driving spatial variation for
-lionfish highlights the need to simultaneously collect length-weight
-information across the invaded range to test for spatially-induced
-patterns and to link these findings to previously suggested
-environmental and genetic structures. Such an endeavor would provide
-insight into lionfish biology and better inform management.
+for an extended version of Table 1). The magnitude of the bias
+discovered in this study and our lack of understanding the sources
+driving spatial variation for lionfish highlights the need to
+simultaneously collect length-weight information across the invaded
+range to test for spatially-induced patterns and to link these findings
+to previously suggested environmental and genetic structures. Such an
+endeavor would provide insight into lionfish biology and better inform
+management. However, while we could not evaluate how these factors
+influenced length-weight estimates from previous studies without raw
+data, we still show that a lack of locally-calculated parameters can
+induce significant bias when calculating weight from length
+observations. We demonstrate the importance of using \emph{in situ}
+parameters to obtain accurate weight estimates regardless of the
+underlying mechanisms driving variation between populations.
 
@@
 Table 2). Due to the power function describing the allometric
-relationship (\emph{i.e.} Eq. 1), the error in weight estimates is
+relationship (\emph{i.e.,} Eq. 1), the error in weight estimates is
 larger when extrapolation is done for lengths that are larger than the

### 2019-02-11 docs/reviews.Rmd
Updated, ready to resubmit

@@
 We include the original comment in plain text, and present our responses in italics.
+When relevant, we mention the new line numbers where changes have been made.
 
@@
 
-- *We chose to keep the word "major" in L26 (now L30) to maintain consistency with the authors' original wording, but we have included quotations to denote this.*
+- *We chose to keep the word "major" in L26 (now L29) to maintain consistency with the authors' original wording, but we have included quotations to denote this.*
 
-- *In L142 (Now L150) We now say that "ex situ parameters can result in erroneous weight estimates"*
+- *In L142 (Now L151) We now say that "the use of ex situ parameters led to significantly erroneous estimates of individual weight and total biomass for lionfish"*
 
-- *Ass suggested, we have changed "major" from L175 to "key" (now L206).*
+- *Ass suggested, we have changed "major" from L175 to "key" (now L211).*
 
@@
 
-*"impacts" has been replaced with "negative effects" in L47, now L49*
+*"impacts" has been replaced with "negative effects" in L47, now L48*
 
@@
 
-*We have improved the wording in the original sentence and no longer use the word "know"/"known". The paragraph now starts in L59.*
+*We have improved the wording in the original sentence and no longer use the word "know"/"known". The paragraph now starts in L58.*
 
@@
 
-*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L81-82) and Table 2 (now Table 1) reflect these changes.*
+*The Bahamas are now reported as part of the Western Atlantic Ocean. Sentence starting in L82 and Table 2 (now Table 1) reflect these changes.*
 
@@
 
-*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120.*
+*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120-121.*
 
@@
 
-*We have included the URL in the main text (L129), but the decision to leave it there depends on the editorial formatting.
+*We have included the URL in the main text (L130), but the decision to leave it there depends on the editorial formatting.
 However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*
@@
 
-*That is correct. We have modified the text to that it reads "each of the different pairs of parameters" (L137)*
+*That is correct. We have modified the text to that it reads "each of the different pairs of parameters" (L138)*
 
@@
 We then provide the extreme values of predicted-to-observed ratios for all organisms and all studies; In a sense, the worst relative over- and underestimations (the smallest and largest values shown in Fig.4 overall).
-Finally, we provide similar measures for estimated total biomass (that is, the summ of the 109 predicted weights) by study, relative to the actual true observed total biomas.
+Finally, we provide similar measures for estimated total biomass (that is, the sum of the 109 predicted weights) by study, relative to the actual true observed total biomass.
 This last measure is now presented in Fig 5.*
@@
 We have modified the text so it reads "...lionfish exhibit highly variable, spatially heterogeneous allometric relationships across their invaded range, and...".
-This is now L161.*
+This is now L164.*
 
@@
 
-*This was meant to say "We show that", and has now been corrected in what is now L162.*
+*This was meant to say "We show that", and has now been corrected in what is now L165-166.*
 
@@
 However, we recognize this may be a factor that influences weight or growth and therefore the length-weight relationship.
-We have mentioned that our parameters for the central Mexican Caribbean are from organisms collected during the Summer (L101), and have devoted a paragraph in the discussion (L185) to highlight the importance of collection methods and timing when estimating length-weight relationships.*
+We have mentioned that our parameters for the central Mexican Caribbean are from organisms collected during the Summer (L101), and have devoted a paragraph in the discussion (L188) to highlight the importance of collection methods and timing when estimating length-weight relationships.*
 
@@
 That is, the wording in their paper confused us and made us think they reported spineless weight, but they report total weight.
-The corresponding modifications have been made in the text.
+The corresponding modifications have been made in the text by deleting that sentence.
 Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*
@@
 
-*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L185).*
+*We have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L188).*
 
@@
 The fact that similar comments were raised by Rev2 suggests that we did not adequately describe this limitation in our original manuscript.
-We now explicitly state that we did not have access to the raw data from the published studies (L87, L117 and L189).
+We now explicitly state that we did not have access to the raw data from the published studies (L87, L117-118 and L195-198).
 However, it is important to note that the objective of our study was not to describe the biological differences in length-weight relationships between site locations, rather to assess the effect of using ex situ vs.
 in situ parameter values to estimate lionfish weights from direct length observations (i.e., to assess whether ex situ parameter values result in large errors in weight estimates).
-We believe that after modifying the text to clearly state our objectives (L87, L117 and L189) and including discussion paragraphs about the limitations of our study (L185 and 196), we have satisfactorily addressed these concerns.*
+We believe that after modifying the text to clearly state our objectives (L71 and L116-119) and including discussion paragraphs about the limitations of our study (L188 and 201), we have satisfactorily addressed these concerns.*
 
@@
 
-*We now use the word "key" (L208).*
+*We now use the word "key" (L211).*
 
@@
 
-First, ratio data isn’t distributed normally, and has unqiue behaviors near the tails of the distribution. It should always be transformed, preferably using a logit transformation, prior to analysis.
+First, ratio data isn’t distributed normally, and has unique behaviors near the tails of the distribution. It should always be transformed, preferably using a logit transformation, prior to analysis.
 
@@
 *The reviewer is correct in that we apply the parameters for lengths that may be outside the ranges originally used to estimate such parameters.
-We have included a paragraph in the discussion where we compare our range of TLs (34 - 310 mm) to the ranges used by different studies to estimate their parameters (Paragraph starts in L 196).
+We have included a paragraph in the discussion where we compare our range of TLs (34 - 310 mm) to the ranges used by different studies to estimate their parameters (Paragraph starts in L 201).
 We also make reference to a new supplementary table where we report all information recorded in other studies.*
@@
 As mentioned in the response to R1, we originally failed to clearly state that we do not have the raw data required to perform such an analysis.
-We have included statements in the methods (L87, L117 and L189) and a discussion paragraph (L185) that highlight these limitations and clarify our objectives/analyses.*
+We have included statements in the methods (L87, L117-118) and a discussion paragraph (L195-198) that highlight these limitations and clarify our objectives/analyses.*
 
@@
 The authors focus mainly on the implications of their findings, in a general way, but offer no potential explanations for the results they observed.
-Do the patterns of variation in weightlength relationships for invasive lionfish align with the genetic results that have been published?
+Do the patterns of variation in weight-length relationships for invasive lionfish align with the genetic results that have been published?
 Are they aligned spatially...
@@
 *As stated above, these were also raised by Rev1.
-We believe that our modifications to the discussion in L185 and L196 now explicitly mention these issues.
+We believe that our modifications to the discussion in L188 and L201 now explicitly mention these issues.
 And while we cannot test for the influence of all these factors on the length-weight relationship, we can still show that using ex situ parameters that follow different sampling collections and without a standardized collection date may lead to over- and underestimation of total weight.*
 
-*More specifically, paragraph starting in L176 mentions that the spatial patterns in length-weight relationships i) ressemble those observed for length-at-age (Pusack et al 2016), ii) Groups identified by post hoc tests aligned with the spatial distribution of examined studyes and ii) These groups also correspond to genetic analyses (Betancur-R et al 2011).*
+*More specifically, paragraph starting in L179 mentions that the spatial patterns in length-weight relationships i) resemble those observed for length-at-age (Pusack et al 2016), ii) Groups identified by post hoc tests aligned with the spatial distribution of examined studies and ii) These groups also correspond to genetic analyses (Betancur-R et al 2011).*
 
-*In the new paragraph starting in L185 we now mention that variation can also be caused by other factors that are not related to space.
+*In the new paragraph starting in L188 we now mention that variation can also be caused by other factors that are not related to space.
 These include different sampling methods, seasonality, and depth ranges.*
@@
 We believe the new text justifies including these extremes.
-The paragraph now starts in L136.*
+The paragraph now starts in L137.*
 

### 2019-04-02 docs/Manuscript.Rmd
Updated all, ready to release

@@
 author: "Juan Carlos Villaseñor-Derbez, Sean P. Fitzgerald"
-institution: "Bren School of Environmental Sciences & Management, University of California Santa Barbara, Santa Barbara, California, U.S."
+institution: "Bren School of Environmental Science and Management, University of California, Santa Barbara, Santa Barbara, CA, United States"
 abstract: |
@@
 
-We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here (Fig \ref{fig:all_allo}).
+We obtained a total of 18 parameter pairs by combining length-weight parameters extracted from the literature and the additional pair calculated here (Table \ref{tab:all_params}).
 Recall that the objective of this study is not to describe differences in the length-weight relationship between populations (which would require access to raw data), but rather to assess how *ex situ* parameter values influence the accuracy of weight estimates for lionfish, using the central Mexican Caribbean as a case study.
@@
 The allometric factor ($b$) was significantly different from $b = 3$ ($t_{107} = `r formatC((coef(model)[[2]]-3)/robust_se[[2]], digits = 2, format = "f")`; p<0.001$), corroborating that lionfish present allometric growth.
-The length-weight coefficients estimated here were within the range identified by studies from other regions (Table \ref{tab:all_params}).
+The length-weight coefficients estimated here were within the range identified by studies from other regions (Fig {fig:all_allo}, Table \ref{tab:all_params}).
 
@@
 If we examined biomass (*i.e.,* summing across all 109 organisms) instead of mean ratios, total biomass estimates were 76.2% (4,363.53 g) and 140% (8,039.96 g) of true observed biomass (5,729.34 g).
-Parameters for this study estimate total biomass at 98% of observed biomass.
+Parameters for this study estimate total biomass at 98% of observed biomass (Fig \ref{fig:errors}).
 These misestimates come from the two most extreme sets of parameters, but results varied consistently across locations (Figs \ref{fig:bio_ratio} and \ref{fig:errors}).
@@
 There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters.
-A log-log version of this figure is presented in Figure S4."}
+A log-log version of this figure is presented in Figure S1."}
 fig_all_allo
@@
 
+# Conclusions
+
 The results presented here have key implications for management.
@@
 
-Conflict of Interest: The authors declare that they have no conflict of interest.
-
 \bibliography{references}

### 2019-04-02 docs/Manuscript.tex
Updated all, ready to release

@@
 \author[1]{Sean Fitzgerald}
-\affil[1]{Bren School of Environmental Sciences and Management, University of California
-  Santa Barbara, Santa Barbara, California, USA}
+\affil[1]{Bren School of Environmental Science and Management, University of California, Santa Barbara, Santa Barbara, CA, United States}
 \corrauthor[1]{Juan Carlos Villaseñor-Derbez}{juancarlos@ucsb.edu}
@@
 these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}, and
-they have established invasive populations in coral reefs, estuaries,
+they have established populations in coral reefs, estuaries,
 mangroves, hard-bottomed areas, and mesophotic reefs
@@
 \citep[][but see \citealt{hackerott_2017} for a counterexample]{green_2012,rocha_2015}.
-For example, field experiments showed that lionfish establishment in the
+For example, field experiments showed that lionfish in the
 Bahamas led to reduced recruitment of native fishes by nearly 80\% over
@@
 parameters extracted from the literature and the additional pair
-calculated here (Fig \ref{fig:all_allo}). Recall that the objective of
+calculated here (Table \ref{tab:all_params}). Recall that the objective of
 this study is not to describe differences in the length-weight
@@
 coefficients estimated here were within the range identified by studies
-from other regions (Table \ref{tab:all_params}).
+from other regions (Fig \ref{fig:all_allo}, Table \ref{tab:all_params}).
 
@@
 observed biomass (5,729.34 g). Parameters for this study estimate total
-biomass at 98\% of observed biomass. These misestimates come from the
+biomass at 98\% of observed biomass (Fig \ref{fig:errors}). These misestimates come from the
 two most extreme sets of parameters, but results varied consistently
@@
 Tukey's \emph{post-hoc} test showed that weight ratios for the central
-Mexican Caribbean differeed from those obtained with parameters from the
-Western Atlantic, and most sites in the Caribbean and the Gulf of Mexico
+Mexican Caribbean differed from those obtained with parameters from the
+Western Atlantic in North Carolina \citep{barbour_2011},
+and most sites in the Caribbean and the Gulf of Mexico
 (Tukey's HSD \(p > 0.05\)). The only sites where weight ratios did not
@@
 for each of the two sites for which they report parameters. A log-log
-version of this figure is presented in Figure S4.}
+version of this figure is presented in Figure S1.}
 \end{figure}
@@
 heterogeneous allometric relationships across their invaded range, and
-that this variation is relevant for managing invasions. Moreover, we
+that this variation may be relevant for managing invasions. Moreover, we
 show that the use of \emph{ex situ} parameter values may lead to highly
@@
 examined studies, suggesting that these differences may be mediated by
-space. These regional allometric differences mirror similar patterns in
+location. These regional allometric differences mirror similar patterns in
 length-at-age of lionfish across both their invaded and native regions
@@
 However, samples from the 12 studies included here were not only
-collected in different locations, but also at different points in time
+collected in different locations, but also at different times of the year
 and across different depth and size ranges (See Supplementary Table 2
@@
 
+\section*{Conclusion}
+
 The results presented here have key implications for management. For
@@
 difference in the time required for the simulated lionfish population to
-recover to 90\% of its initial biomass after removals ceased. Here, we
-show that using one set of length-weight parameters versus another for a
+recover to 90\% of its initial biomass after removals ceased.
+
+Here, we show that using one set of length-weight parameters versus another for a
 given length can result in more than a threefold under- or
@@
 
-Conflict of Interest: The authors declare that they have no conflict of
-interest.
-
 \bibliography{references}
